### 2016-06-30 paper.tex
First commit of paper

\documentclass[a4paper,fleqn,usenatbib]{mn2e}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}   % Including figure files
\graphicspath{{Users/}{owenturner/}{Documents/}{PhD/}{KMOS/}{paper_1/}{Figures/}}
\usepackage{amsmath}    % Advanced maths commands
\usepackage{amssymb}    % Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$} % per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Spatially resolved dynamics at $z \sim 3.5$]{The KMOS Deep Survey: Resolved gas dynamics at $z \sim 3.5$}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[O.J. Turner et al.]{
Owen J. Turner,$^{1}$\thanks{E-mail: turner@roe.ac.uk (OJT)}
M. Cirasuolo,$^{1}$
J. Dunlop$^{1}$
R. J. McLure$^{1}$
\\
% List of institutions
$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2016}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
We present first results from the KMOS Deep Survey (KDS), which is an ESO guaranteed time survey of 80 star-forming galaxies in the redshift range $z = 3 - 3.8$.
From this sample we detect spatially resolved [OIII5007] emission in the K-band from 57 galaxies, allowing us to explore the fraction which show ordered rotational motions, presumably in a star-forming disk.
41 galaxies show a clear, smooth velocity gradient along the kinematic axis, meriting them for further investigation via dynamical modelling.
The ratio of maximum rotational velocity to intrinsic velocity dispersion, $v / \sigma _{int}$, is commonly used to indicate the extent to which the gas in disk galaxies is dominated by ordered rotation or random motions.
We find that 16 galaxies have $v / \sigma _{int} > 1$, in broad agreement with results found at similar and low redshift.
The mean values of $v / \sigma _{int}$ are substantially lower in this redshift range than are observed locally; since the measured rotational velocity values have remained roughly constant over cosmic time this suggests that turbulent gas motions within the disk become steadily more important with increasing redshift.
We investigate the causes for this, linking the increase in $\sigma _{int}$ to increasing gas fraction and decreasing galaxy size, following the virial theorem and a $(1 + z)^{-1}$ scaling.
Finally we look into correlations between the maximum rotational velocity of galaxies and their global properties, finding that galaxies with higher stellar mass tend to rotate faster.

\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
Integral Field Unit -- KMOS -- Dynamics -- Turbulence
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{INTRODUCTION}

Understanding the evolving dynamical state of disky star-forming galaxies (SFGs) throughout cosmic time is central to understanding the topics of galaxy formation and evolution.
In the equilibrium model of galaxy evolution e.g. \cite{Genel2008,Lilly2013,Bouche2010,Dave2011,Dave2011a,Dave2011b,Krumholz2012}, the gas content of SFGs regulates their Star Formation Rates (SFRs) and varies smoothly inside individual galaxies throughout their lifetimes.
The galactic gas budget is mediated by inflows of cold gas along cosmic web filaments CITE KERES, DEKEL, processing of the cold gas with steady, secular star formation and by outflows of gas from Active Galactic Nuclei (AGN) and stellar feedback.
SFGs locked in this cycle of gas consumption form a galactic `Main Sequence', which is a fairly tight relationship between the SFR and stellar mass $M_{*}$

Over the last decade there have been considerable advancements

\citep{Wisnioski2015} \citep{ForsterSchreiber2009} \citep{ForsterSchreiber2006} \citep{Stott2016} \citep{Gnerucci2011} \citep{Epinat2012} \citep{Epinat2009} \citep{Epinat2010} \citep{Lilly2013} \citep{Saintonge2013} \citep{Wisnioski2011} \citep{Wright2007} \citep{Wright2009} \citep{Genzel2008} \citep{Genzel2006} \citep{Shapiro2008} \citep{Jones2010a} \citep{Newman2013} \citep{Genel2008} \citep{Nesvadba2008} \citep{Queyrel2012} \citep{Law2007} \citep{Law2009}
\citep{Simons2016} \citep{Pelliccia2016} \citep{Genzel2011} \citep{Epinat2008} \citep{Epinat2008a} \citep{Puech2008} \citep{Puech2007} \cite{Holmberg1958} \citep{Kassin2012} \citep{Flores2006} \citep{Neichel2008} \citep{Miller2011} \citep{Nesvadba2006} \citep{Nesvadba2007} \citep{Livermore2015} \citep{Swinbank2006} \citep{Swinbank2007} \citep{Swinbank2009} \citep{Cortese2014}

\section{SURVEY \& DATA REDUCTION}

\subsection{The KMOS Deep Survey}
The KMOS Deep Survey (KDS) is a guaranteed time programme focussing on the spatially resolved properties of $z \sim 3.5$ galaxies.

\begin{itemize}
    \item Description of the instrument 
    \item plagued by poor weather, describe the time frame over which the observations are taken
    \item OSO observation pattern
    \item The different wavebands used and potential science that can come out of these observations
    \item 300s exposures
    \item describing all of the pointings 
    \item Different physical conditions in the different pointings
    \item Selection techniques 
\end{itemize}

\begin{figure}
\centering
\includegraphics[width=0.47\textwidth]{paper_distributions.png}
\caption{Distributions of the physical properties of KDS galaxies in both GOODS-S and SSA22}
\label{fig:distributions}
\end{figure}

Concluding with the pointings that we had, and a table summarising the name of the pointing, the number of galaxies observed in each of those, the combined exposure time and the seeing. All of that information is available so could have been able to do this for a while now.

\begin{table*}
    \centering
\begin{tabular}{ c c c c c c c }

 \hline
Field & Pointing & N$_{obs}$ & Coordinates & Band & Exp. Time (s) & Seeing (arcsec)  \\
 \hline
 GOODS-S & goodsp1 & 19 & 03:32:42 -27:48:58 & K, H & 32400 & 0.5 \\
GOODS-S & goodsp2 & 18 & 03:32:42 -27:49:08 & K, H & 31800 & 0.52 \\
SSA22 & ssap1 & 21 & 22:17:28 00:09:54 & HK & 38100 & 0.65 \\
SSA22 & ssap2 & 18 & 22:17:11 00:15:47 & HK & 27800 & 0.70 \\
 \hline
\end{tabular}
\caption{Summary of KDS statistics}
\label{tab:KDS}
\end{table*}

\subsection{Data reduction techniques}
The data reduction process relied heavily upon the Software Package for Astronomical Reduction with KMOS (SPARK), implemented using the ESO Recipe Execution Tool (ESOREX).
To augment the SPARK recipes, custom python scripts were built and run at different stages of the pipeline in an attempt to increase the S/N of the final, stacked datacubes.
These additional steps will be described throughout this section.

The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
The four pixel wide gaps between the IFU lenslets in the raw data are then used to correct for readout channel bias across each detector, which if left uncorrected lead to flux bandings over the spatial extent of the reduced cubes.
Standard star observations are processed to provide a flux calibration for each detector, which is necessary to account for varying sensitivity  
Following this pre-processing, each of the object-sky pairs are reduced independently to give more control over the way in which the final stacks are created for each galaxy.
Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxels, justified by the choice of dither pattern boosting the effective spatial resolution of the observations.
Sky subtraction is performed using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general we find the quality of the sky subtraction in the K-band to be excellent. 
Variations in sky subtraction quality are monitored over the course of the OBs which make up the final stacks, as we find that the subtraction performance becomes poorer as the telescope pointing approaches the zenith.
This is due to the telescope having to track faster whilst at zenith positions, hence scanning more rapidly over regions of sky with spatially and temporally varying OH emission.
In addition to this we monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames with unacceptable seeing and to measure the spatial shifts required for the final stack more precisely.
The telescope tends to drift from its acquired position over the course of an OB, and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
As part of this analysis, we tested whether the drift varies across the three KMOS detectors, finding typically that the difference is negligible, meaning that it is not necessary to sacrifice more than a single IFU for tracking purposes.

After stacking all 300s exposures which pass the sky subtraction and seeing criteria, we are left with a final, flux and wavelength calibrated datacube for each galaxy in the KDS sample.

\section{EXTRACTION OF PHYSICAL PROPERTIES}
\subsection{Spaxel Fitting}
Having produced stacked and calibrated datacubes for each of the galaxies in the sample, we aim to extract 2-dimensional maps of the flux, velocity and velocity dispersion.
These properties are extracted via modelling of the ionised gas emission line profiles at each spaxel, with a set of acceptance criteria to determine whether the fit quality is high enough to allow the inferred properties into the final 2D maps.
We concentrate solely on the [OIII5007] emission line which always has S/N higher than both [OIII4959] and H$\beta$, and therefore provides a tighter set of model constraints over a wider portion of the physical extent of each galaxy.
As a result, any reference to OIII emission will refer specifically to the [OIII5007] line unless otherwise stated.

We start by considering each 0.1$^{\prime\prime}$ spaxel across a datacube in turn

The process is automated and applied to each of the KDS galaxies.
We find 56 galaxies with spatially resolved OIII emission, with this defined as being those where the spatial extent of the OIII is equivalent to or greater than the seeing disk.

\subsection{Sample Statistics}

Fig.~\ref{fig:distributions}, Table~\ref{tab:KDS}.

\section{ANALYSIS \& RESULTS}

\section{DISCUSSION}

\begin{itemize}
    \item Surface brightness dimming
    \item beam smearing
    \item Different modelling techniques
    \item 
\end{itemize}

\section{SUMMARY}

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
\clearpage 
\bibliographystyle{apj.bst}
%\bibliography{/usr/local/texlive/texmf-local/bibtex/bib/ojt.bib}
\bibliography{/Users/owenturner/Documents/PhD/KMOS/Latex/Bibtex/library.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{combine_sci_reconstructed_bs006516_grid_fixed.png}
\includegraphics[width=\textwidth]{combine_sci_reconstructed_bs006541_grid_fixed.png}
\includegraphics[width=\textwidth]{combine_sci_reconstructed_bs008543_grid_fixed.png}
\caption{Distributions of the physical properties of KDS galaxies in both GOODS-S and SSA22}
\label{fig:grids}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp    % typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2016-09-22 paper.tex
Writing the introduction and other things properly

@@
 \documentclass[a4paper,fleqn,usenatbib]{mn2e}
+
+\usepackage[hyperfootnotes=false]{hyperref}
+\hypersetup{
+  colorlinks,
+  citecolor=blue,
+  linkcolor=red,
+  urlcolor=Violet}
 
@@
 \usepackage{ae,aecompl}
+
+% fancy section symbol
+\usepackage{cleveref}
+\crefname{section}{$\S$}{$\S\S$}
+\Crefname{section}{$\S$}{$\S\S$}
 
@@
 
-Understanding the evolving dynamical state of disky star-forming galaxies (SFGs) throughout cosmic time is central to understanding the topics of galaxy formation and evolution.
-In the equilibrium model of galaxy evolution e.g.
-\cite{Genel2008,Lilly2013,Bouche2010,Dave2011,Dave2011a,Dave2011b,Krumholz2012}, the gas content of SFGs regulates their Star Formation Rates (SFRs) and varies smoothly inside individual galaxies throughout their lifetimes.
-The galactic gas budget is mediated by inflows of cold gas along cosmic web filaments CITE KERES, DEKEL, processing of the cold gas with steady, secular star formation and by outflows of gas from Active Galactic Nuclei (AGN) and stellar feedback.
-SFGs locked in this cycle of gas consumption form a galactic `Main Sequence', which is a fairly tight relationship between the SFR and stellar mass $M_{*}$
+NO UNIVERSALLY DEFINED MEASURE OF THE CIRCULAR VELOCITY, OR THE POINT AT WHICH TO EXTRACT THAT VALUE.
 
-Over the last decade there have been considerable advancements
+% Check references here - exactly where does this scenario come from? 
+In the hierarchical collapse scenario \citep{Fall1980}, matter density perturbations, which originate from some set of cosmological initial conditions, grow over time before condensing out of the general expansion to form dark matter haloes (Lifshitz 1960) \cite{Silk1968,Peebles1970}.
+Mixed amongst this dark matter is baryonic gas, which is initially shock heated to the virial temperature of the halo during the gravitational collapse \citep{Birnboim2003,Keres2005,Dekel2006}.
+As the baryons collectively cool, they accumulate at the centre of the potential well of the host halo as dense and cold protogalactic gas.
+One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue.
 
-\citep{Wisnioski2015} \citep{ForsterSchreiber2009} \citep{ForsterSchreiber2006} \citep{Stott2016} \citep{Gnerucci2011} \citep{Epinat2012} \citep{Epinat2009} \citep{Epinat2010} \citep{Lilly2013} \citep{Saintonge2013} \citep{Wisnioski2011} \citep{Wright2007} \citep{Wright2009} \citep{Genzel2008} \citep{Genzel2006} \citep{Shapiro2008} \citep{Jones2010a} \citep{Newman2013} \citep{Genel2008} \citep{Nesvadba2008} \citep{Queyrel2012} \citep{Law2007} \citep{Law2009}
-\citep{Simons2016} \citep{Pelliccia2016} \citep{Genzel2011} \citep{Epinat2008} \citep{Epinat2008a} \citep{Puech2008} \citep{Puech2007} \cite{Holmberg1958} \citep{Kassin2012} \citep{Flores2006} \citep{Neichel2008} \citep{Miller2011} \citep{Nesvadba2006} \citep{Nesvadba2007} \citep{Livermore2015} \citep{Swinbank2006} \citep{Swinbank2007} \citep{Swinbank2009} \citep{Cortese2014}
+It is an observationally determined fact that the galaxy population is bimodal in many physical properties at each epoch after galaxies begin to form, with a preference for the most massive galaxies to lie in the red sequence, characterised by red colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies.
+\citep{Abramson2016,Abramson2016a}
+\citep{Pannella2009a}
 
-\section{SURVEY \& DATA REDUCTION}
+\citep{Baldry2006}
+simulations explaining the biodality in terms of AGN feedback and a cut at a characteristic mass scale.
+\citep{Birnboim2003,Dekel2006,Keres2005,Bower2006,Croton2006}
+Explaining the observed number densities of early and late type galaxies at different epochs in terms of their formation mechanisms and evolutionary histories is one of the key goals of modern astronomy.
+Two scenarii have emerged.
+The first highlights the importance of secular evolution, whereby cold gas accreted along cosmic web filaments `tops up' the existing baryon supply which fuels star formation, stellar mass within a galaxy is continually built up with in-situ star formation and the rate of star formation itself is regulated by both stellar and AGN feedback.
+In this picture there is a certain mass scale above which a galaxy becomes quenched - EXPAND UPON THAT
+The second suggests that environmental effects dominate the evolutionary demographic, with mass buildup predominantly occuring through minor mergers and major mergers triggering the cessation of star formation and building the red sequence at each epoch.
+Throughout the last few years both the results from simulations REF and observations have pushed the community towards the former picture, which downplays the significance of mergers in driving galaxy evolution.
 
-\subsection{The KMOS Deep Survey}
-The KMOS Deep Survey (KDS) is a guaranteed time programme focussing on the spatially resolved properties of $z \sim 3.5$ galaxies.
+%,Understanding the evolving dynamical state of disky star-forming galaxies (SFGs) throughout cosmic time is central to understanding the topics of galaxy formation and evolution.
+%There are two different evolutionary scenarii.
+%The first suggests that the buildup of stellar mass, $M_{*}$, over time within galaxies is hierarchical, with minor mergers steadily contributing to $M_{*}$ and major mergers bringing about the cessation of star formation by shock heating of the cold molecular gas.
+%The second is the equilibrium model of galaxy evolution e.g.
+\cite{Genel2008,Bouche2010,Dave2011,Dave2011a,Dave2011b,Krumholz2012,Lilly2013}, where the gas content of SFGs regulates their Star Formation Rates (SFRs) and varies smoothly inside individual galaxies throughout their lifetimes.
+%In this picture the galactic gas budget is mediated by inflows of cold gas along cosmic web filaments \citep{Keres2005,Dekel2006} processing of the cold gas with steady, secular star formation and by outflows of gas from Active Galactic Nuclei (AGN) and stellar feedback.
+%SFGs locked in this cycle of gas consumption form a galactic `Main Sequence', which is a fairly tight relationship between the SFR and stellar mass $M_{*}$  
+%Over the last decade there have been considerable advancements
+
+References for other things
+MAIN SEQUENCE
+\citep{Daddi2007} \citep{Elbaz2011a} \citep{Elbaz2007} \citep{Noeske2007a}
+
+These are all the references for kinematics, not all the references for other things and other aspects of galaxy evolution. 
+\citep{Wisnioski2015} \citep{ForsterSchreiber2009} \citep{ForsterSchreiber2006} \citep{Stott2016} \citep{Gnerucci2011} \citep{Epinat2012} ,\citep{Epinat2009} \citep{Epinat2010} \citep{Lilly2013} \citep{Saintonge2013} \citep{Wisnioski2011} \citep{Wright2007} \citep{Wright2009} \citep{Genzel2008} \citep{Genzel2006} \citep{Shapiro2008} \citep{Jones2010a} \citep{Newman2013} \citep{Genel2008} \citep{Nesvadba2008} \citep{Queyrel2012} \citep{Law2007} \citep{Law2009}
+\citep{Simons2016} \citep{Pelliccia2016} \citep{Genzel2011} \citep{Epinat2008} \citep{Epinat2008a} \citep{Puech2008} \citep{Puech2007} \cite{Holmberg1958} \citep{Kassin2012} \citep{Flores2006} \citep{Neichel2008} \citep{Miller2011} \citep{Nesvadba2006} \citep{Nesvadba2007} \citep{Livermore2015} \citep{Swinbank2006} \citep{Swinbank2007} \citep{Swinbank2009} \citep{Cortese2014} \citep{VanderWel2012} - for the PSF used when Galfitting F160W.
+
+MOTIVATING THE FOLLOWING SECTION
+
+The KMOS Deep Survey (KDS) is a guaranteed time programme focussing on the spatially resolved properties of star forming galaxies during a time where the universe is building to peak activity.
+There are still many open questions which we can begin to answer by studying the emission, or lack thereof, from regions of ionised gas within individual galaxies at these redshifts.
+For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high redshift?
+\textbf{(2)} What are the radial gradients in metal enrichment and would evidence for inverse gradients suggest infall of pristine gas to the central regions of these galaxies?
+\textbf{(3)} What are the connections between the chemical properties and the kinematics of the gas, particularly in terms of inflows and outflows of material?
+KMOS benefits from the ability to study many targets simultaneously, with 24 deployable IFUs patrolling a $7^{\prime}$ patch of sky.
+Attempting to spatially resolve the flux from emission lines at $z \sim 3.5$ necessarily requires on source integration times $>$ 6 hours, and so the multiplexing capability provides KMOS with an enormous advantage in terms of observing time over other instruments for this type of study.
+This has the knock-on effect of enabling a more general galaxy selection criteria, so that the KDS targets will be representative of the main sequence star forming population.
+
+Many of these questions have already been addressed at lower redshift, as described above \citep{ForsterSchreiber2009,Wisnioski2015,Stott2016}, and also in a similar redshift range \cite{Gnerucci2011}.
+The KDS will complement the lower redshift results by providing an additional data point on any plots showing evolutionary sequences of derived physical properties, therefore providing a more complete description of galaxy evolution starting from before cosmic high noon and running up to the present day.
+The high redshift results of \cite{Gnerucci2011} will be expanded upon by the KDS, which extends to lower stellar masses and will increase the sample size for which physical properties can be resolved by roughly a factor of three.
+
+In this paper we focus on deriving and interpreting the spatially resolved kinematics of KDS galaxies using the [OIII5007] emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$, and focussing on forming evolutionary links with lower redshift work.
+We combine our KMOS data with the high resolution and sensitivity of the Hubble Space Telescope (HST) WFC3 H-band imaging in a spectro-photometric analysis, so that the kinematics can also be understood in the context of galaxy morphology.
+In a future paper, (Turner \textit{et al.} in prep.), we will investigate the radial gradients in galaxy metallicity and hence the spatially resolved physical conditions within the ISM.
+
+The structure of the current paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction.
+In \cref{sec:extracting_properties} we explain how the two-dimensional maps of physical properties were extracted from our stacked datacubes and then describe the treatment of these maps and the modelling which leads to the final table of physical properties for the KDS galaxies.
+\cref{sec:results} presents our physical findings which are then discussed in \cref{sec:discussion}.
+We then conclude in \cref{sec:conclusions}.
+Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).
+
+\section{SURVEY \& DATA REDUCTION}\label{sec:Survey_and_data}
+
+\subsection{The KMOS Deep Survey: sample selection and strategy}
 
@@
 
+\subsection{Observations}
+
+\subsection{Ancillary data}
+
 \subsection{Data reduction techniques}
 The data reduction process relied heavily upon the Software Package for Astronomical Reduction with KMOS (SPARK), implemented using the ESO Recipe Execution Tool (ESOREX).
-To augment the SPARK recipes, custom python scripts were built and run at different stages of the pipeline in an attempt to increase the S/N of the final, stacked datacubes.
+In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline.
 These additional steps will be described throughout this section.
@@
 
-After stacking all 300s exposures which pass the sky subtraction and seeing criteria, we are left with a final, flux and wavelength calibrated datacube for each galaxy in the KDS sample.
+We stack all 300s exposures for each galaxy which pass the sky subtraction and seeing criteria using sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
 
-\section{EXTRACTION OF PHYSICAL PROPERTIES}
+\section{EXTRACTION OF PHYSICAL PROPERTIES}\label{sec:extracting_properties}
 \subsection{Spaxel Fitting}
@@
 We concentrate solely on the [OIII5007] emission line which always has S/N higher than both [OIII4959] and H$\beta$, and therefore provides a tighter set of model constraints over a wider portion of the physical extent of each galaxy.
-As a result, any reference to OIII emission will refer specifically to the [OIII5007] line unless otherwise stated.
+As a result, any reference to OIII emission points specifically to the [OIII5007] line unless otherwise stated.
 
-We start by considering each 0.1$^{\prime\prime}$ spaxel across a datacube in turn
+We start by considering each 0.1$^{\prime\prime}$ spaxel across a datacube in turn, and locate the wavelength of the redshifted OIII centre, $\lambda_{obs_{5007}}$, using either the literature redshift value, or the redshift determined from fitting the OIII line in the integrated galaxy spectrum.
+We have found that the thermal background is often undersubtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
+To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux, and then subtracted from each spaxel in turn.
+This assumes that there is no spatial variation in the required correction, which we have found to be valid for our current sample of galaxies.
+A benefit of this polymonial subtraction is that the object continuum is subtracted simultaneously, and so the subsequent fitting of emission lines is performed relative to zero flux. 
+During the fit, regions of the spectrum known to contain strong sky emission are masked.
+Following the subtraction of excess thermal noise and continuum emission, we search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
+This truncated spectrum is then used in the fitting procedure for each spaxel.
+The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by poor subtraction of the sky emission lines.
+A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the fitted parameters flux,$F_{g}$, central wavelength, $\lambda_{g}$ and standard deviation, $\sigma_{g}$.
+These parameters, along with the estimate of the noise in the datacube are used to assess whether the fitting of the OIII line is acceptable or not. 
+The noise in the cube is estimated in two different ways. 
+First, we take the root of the sum of the squares of the flux values in the noise cube over the same extraction region defined for the data cube.
+The noise cube is produced as part of the reduction process, taking into account instrumental effects and the noise reduction due to stacking many individual exposures.
+This is summarised by Equation~\ref{eq:cube_noise}, where $\sigma _{i}$ are the individual flux points in the noise cube and $N_{c}$ denotes noise estimated from the noise cube.
+
+\begin{equation}\label{eq:cube_noise}
+   N_{c} = \sum_{i}\sigma _{i}^{2}
+\end{equation}
+
+In the second method the datacube itself is used to estimate the noise.
+Again, all spaxels containing object flux are masked and the sum of the squares of the flux values in the extaction region is computed for all remaining spaxels inwards of 3 spaxels from the cube border.
+This last constraint is to mitigate edge effects, where the noise increases due to fewer individual exposures constituting the final stack in these regions.
+The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation~\ref{eq:mask_noise} where $F_{i}$ are the flux values across the extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
+Both noise estimates are quantitatively similar and the conclusions of the following analysis are not dependent on the choice.
+As default we use the noise estimate from masking throughout the rest of the section.
+
+\begin{equation}\label{eq:mask_noise}
+    N_{m} = STD\big(\sum_{i}F_{i}^{2}\big)
+\end{equation}
+
+The signal in each spaxel is taken as the sum of the flux values across the extraction region, as shown in Equation~\ref{eq:signal} where S denotes the signal.
+
+\begin{equation}\label{eq:signal}
+    S = \sum_{i}F_{i}
+\end{equation}
+
+The criteria for accepting the fit within a given spaxel are as follows.
+1) The uncertainties on the parameters of the gaussian fit must not exceed 30\%
+2) The ratio of the flux recovered from the gaussian fit to the OIII line to the sum of the fluxes within the extraction region must exceed 1.3 or drop below 0.7.
+This helps to minimise the number of spaxels erroneously accepted due to fitting of non-gaussian profiles.
+We found this was an important criterion for `cleaning up' accepted spaxels in the 2D maps which are clearly independent of the main body of the galaxy.
+3) The measured S/N must exceed three.
+If all three criteria are satisfied, the spaxel is accepted and the gaussian fit is repeated 1000 times with each flux value in the extraction region perturbed by the datacube flux error.
+This error is computed as the median of the standard deviations in the extraction regions of the unmasked spaxels, as shown in Equation~\ref{eq:cube_error} with $F_{e}$ denoting the flux error.
+
+\begin{equation}\label{eq:cube_error}
+   F_{e} = \big<STD(F _{i})\big>
+\end{equation}
+
+This Monte Carlo procedure gives the fit parameters and associated errors for the accepted spaxels.
+The velocity is computed from the gaussian centre, $\lambda_{g}$, using Equation~\ref{eq:velocity_comp} and the velocity dispersion is computed from the gaussian width, $\sigma_{g}$, using Equation~\ref{eq:dispersion_comp}, where $v_{obs}$ and $\sigma_{obs}$ are the observed rotational velocity and velocity dispersion respectively and c is the speed of light.
+
+\begin{equation}\label{eq:velocity_comp}
+   v_{obs} = \frac{\lambda_{c} - (1 + z)\lambda_{OIII}}{(1 + z)\lambda_{OIII}} \times c
+\end{equation}
+
+\begin{equation}\label{eq:dispersion_comp}
+   \sigma_{obs} = \frac{\sigma_{g}}{(1 + z)\lambda_{OIII}} \times c
+\end{equation}
+
+If a spaxel does not meet the criteria we bin with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
+This is done by median stacking the extraction region spectra in each of the neighbouring spaxels.
+The criteria are then re-examined and if satisfied the Monte-Carlo procedure is carried out. 
+If the binned spaxels fail the criteria, one final iteration is carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$.
+If after the widest binning the criteria aren't satisfied, the value of the spaxel in the 2D maps is set to nan.
+Spaxels which pass the criteria after binning are represented as a single spaxel in the 2D maps, and so a smoothing of the fields are expected in the lowest S/N regions.
 
 The process is automated and applied to each of the KDS galaxies.
-We find 56 galaxies with spatially resolved OIII emission, with this defined as being those where the spatial extent of the OIII is equivalent to or greater than the seeing disk.
+As mentioned previously, we find 56 galaxies with spatially resolved OIII emission, with this defined as being those where the spatial extent of the OIII is equivalent to or greater than the seeing disk of roughly $0.5^{\prime\prime}$.
+
+\subsection{Imaging Data}
+It is essential to make use of photometric data which cover the same fields as targetted by the KDS pointings.
+From these data the inclination with respect to line of sight, position angles and sizes of our galaxies can be constrained from single band fitting, and multi-band SPS modelling gives estimates of the global physical properties such as $M_{*}$ and SFR.
+The single band properties complement the observed kinematics from KMOS and provide the information required to estimate intrinsic velocity fields.
+As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $\alpha$ is the axial ratio of an edge-on system, and so is dependent upon an assumption about the `disk thickness'.
+
+\begin{equation}\label{eq:holmberg_i}
+   cos^{2}i = \frac{\left(\frac{b}{a}\right)^{2} - \alpha^{2}}{1 - \alpha^{2}}
+\end{equation}
+
+This inclination can then be used to correct the line of sight component of the observed velocity, to recover an intrinsic circular velocity, in the standard way.
+The discrepancy between morphologial and kinematic position angles is an important indicator of sub-structure in the morphology \citep{Queyrel2012,Wisnioski2015}.
+These values are expected to agree, particularly for low axial ratios, and deviations can indicate clumps or mergers, which may influence the underlying kinematics. 
+However for compact, unresolved morphologies there are cases where there is simply not enough information to predict the axis along which velocity gradient will be maximised. 
+First this provides a way to extract circular velocities at some fiducial distance from the centre of the galaxy.
+As discussed throughout the introduction, there is no universal definition of what the circular velocity is, and so to compare with previous work it is necessary to extract values consistently from the derived rotation curves.
+Connected to this is the issue of extrapolating model rotation curves or two-dimensional rotation maps beyond the last measured datapoints, which may not extend to the rotation curve plateau due to poor S/N in this regions.
+Knowledge of the effective radii gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made.
+Second, since beam smearing affects all of these measurements and tends to flatten velocity gradients, Durham have invested time into modelling the extent to which this can be corrected.
+The correction is a function of the ratio between $r_{e}$ and PSF size as shown in Figure DURHAM, and so accurately measuring the effective radius of a galaxy vindicates the use of this curve to recover intrinsic circular velocities.
+\\
+
+To support the KMOS GOODS-S pointings there is excellent ancillary data from both the ACS and WFC3 instruments aboard HST.
+In tandem with IRAC and spitzer, these provide photometric measurements across the optical and IR regions of the spectrum, from which reliable stellar masses and star formation rates can be derived.
+The high resolution single band images are not inhibited by atmospheric broadening of the PSF and so are rich in morphological information which is useful both to eyeball for interesting features and for constraining the parameters described above.
+The SSA22 pointings have less imaging data, all of which is ground-based, and so both the global physical properties and the single band properties are not constrained as well as in the GOODS-S case.
+Nonetheless, it is possible to determine morphological parameters by fitting the images using GALFIT, as described in section \ref{subsubsec:galfitting}.
+
+\subsubsection{Applying GALFIT to the imaging data}\label{subsubsec:galfitting}
+For the GOODS-S pointings we focus on the deep WFC3 F160W image of GOODS-S, this being the longest wavelength (and therefore least attenuated) measure of the stellar continuum, which traces the rest-frame optical and near-UV light at the median redshift of the KDS galaxies.
+
+INCLUDE TABLE OF THE GALFIT outputs
+HST vs. TENIS imaging of the same galaxies to confirm whether it is okay to report the physical properties of a sample taken from the ground and then GALFIT.
+
+To complement our KMOS data we make use of publicly available Hubble F160W imaging, which covers all galaxies in our two GOODS-S pointings.
+This imaging is useful not only as part of the ancillary data from which the galactic physical properties are derived, but also as a tool to constrain the size, centre, inclination angle and morphological axis of the galaxies.
+We use GALFIT \citep{Peng2010_galfit} to model the F160W light profile of each GOODS-S galaxy, which attempts to fit a
+
+\subsection{Dynamical Modelling}
+Constructing model 2D velocity fields and fitting these to the observed data is a powerful tool for determining the set of parameters which best describe the dynamical state of that galaxy.
+HERE IS WHERE TO MENTION SURVEYS WHICH HAVE DONE THIS IN THE PAST.
+
+\subsection{Beam Smearing Correction}
 
@@
 
-\section{ANALYSIS \& RESULTS}
+\section{ANALYSIS \& RESULTS}\label{sec:results}
 
-\section{DISCUSSION}
+\section{DISCUSSION}\label{sec:discussion}
 
@@
 
-\section{SUMMARY}
+\section{CONCLUSIONS}\label{sec:conclusions}
 

### 2016-09-28 paper.tex
September 28th Michele deadline ESO

@@
 \citep{Wisnioski2015} \citep{ForsterSchreiber2009} \citep{ForsterSchreiber2006} \citep{Stott2016} \citep{Gnerucci2011} \citep{Epinat2012} ,\citep{Epinat2009} \citep{Epinat2010} \citep{Lilly2013} \citep{Saintonge2013} \citep{Wisnioski2011} \citep{Wright2007} \citep{Wright2009} \citep{Genzel2008} \citep{Genzel2006} \citep{Shapiro2008} \citep{Jones2010a} \citep{Newman2013} \citep{Genel2008} \citep{Nesvadba2008} \citep{Queyrel2012} \citep{Law2007} \citep{Law2009}
-\citep{Simons2016} \citep{Pelliccia2016} \citep{Genzel2011} \citep{Epinat2008} \citep{Epinat2008a} \citep{Puech2008} \citep{Puech2007} \cite{Holmberg1958} \citep{Kassin2012} \citep{Flores2006} \citep{Neichel2008} \citep{Miller2011} \citep{Nesvadba2006} \citep{Nesvadba2007} \citep{Livermore2015} \citep{Swinbank2006} \citep{Swinbank2007} \citep{Swinbank2009} \citep{Cortese2014} \citep{VanderWel2012} - for the PSF used when Galfitting F160W.
+\citep{Simons2016} \citep{Pelliccia2016} \citep{Genzel2011} \citep{Epinat2008} \citep{Epinat2008a} \citep{Puech2008} \citep{Puech2007} \cite{Holmberg1958} \citep{Kassin2012} \citep{Flores2006} \citep{Neichel2008} \citep{Miller2011} \citep{Nesvadba2006} \citep{Nesvadba2007} \citep{Livermore2015} \citep{Swinbank2006} \citep{Swinbank2007} \citep{Swinbank2009} \citep{Cortese2014} \citep{VanderWel2012} \citep{Genzel2014a} \citep{Genzel2014} - for the PSF used when Galfitting F160W.
 
@@
 \textbf{(3)} What are the connections between the chemical properties and the kinematics of the gas, particularly in terms of inflows and outflows of material?
+\textbf{(4)} What role does formation environment play in shaping the dynamical and chemical evolution of galaxies? 
 KMOS benefits from the ability to study many targets simultaneously, with 24 deployable IFUs patrolling a $7^{\prime}$ patch of sky.
@@
 
-\subsection{The KMOS Deep Survey: sample selection and strategy}
+% note going to assume here that the KMOS targets were selected from 
+% from VVDS, COSMOS
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Notes for the sample selection plots
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 1. mstar vs sfr - must have full sample in the backgroud 
+% and also lines showing where the main sequence of star formation
+% should lie on this plot
+% 2. colour vs mass plots - showing again the general population in 
+% the background - will need to convert fluxes to magnitudes?
+% Maybe a redshift vs. magnitude plot or something similar, showing
+% how faint these targets are.
+
+\subsection{The KMOS Deep Survey: sample selection and observations}
+Our target selection for the KDS sample is designed to pick out star-forming galaxies at $z = 3-4$, supported by deep multi-wavelength ancillary data and probing both cluster and field environments.
+Within this redshift range the [OIII4959,5007] doublet and the $H_{beta}$ emission lines are visible in the K-band and the [OII3727,3729] doublet is visible in the H-band, both of which are observable with KMOS.
+We also want to draw galaxies covering a wide range in the SFR-$M_{*}$ relation, so that we are ultimately tracking the physical properties of a representative sample of the star-forming population at these redshifts.
+For these reasons, and to ensure a high detection rate of the ionised gas emission lines in the KDS galaxies, we select galaxies in well studied fields that have a previous spectroscopic detection.
+To avoid biasing the sample towards blue and highly star-forming galaxies we make no secondary cuts on the basis of mass and flux. %FIGURE REFERENCE%
+Predominantly, the galaxies have been selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
+However a subset of the selected cluster galaxies in SSA22 were blindly detected in Ly$\alpha$ emission, during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
+These `Lyman-Alpha Blobs' (LABs), which are extended and diffuse emission regions associated with but not centred on LBGs \citep{Steidel2000}, and especially LAB01, have been the subject of much previous study, e.g.
+\citep{Bower2004a}, \citep{Matsuda2004,Matsuda2007}, \citep{Geach2006,Geach2014}, \citep{Weijmans2010}, \citep{Hayes2011a} and LAB01 was the study of a recent campaign \citep{Geach2016} using data from MUSE, \citep{Bacon2010}, ALMA, \citep{Wootten2009}, and MOSFIRE, \citep{McLean2012}.
+These studies generally conclude that LABs are observed at the peaks of the cosmic density field and are therefore the progenitors of the most massive galaxy clusters, but the precise origin of the nebulous Ly$\alpha$ line emission is still unknown.
+
+The non-cluster environment galaxies are selected from the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 imaging with $\sim 0.1^{\prime\prime}$ angular resolution, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
+These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [OIII5007] or H$_{\beta}$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
+The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions of spatial overdensity in the south-east (goodsp1) and north-west (goodsp2) to fill the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
+
+% Add the programme ID for HST WFC3 imaging
+The cluster galaxies are all from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003}, \citep{Shapley2003}, which, as mentioned above, is an extreme overdensity of LBG candidates at $z \sim 3.09$.
+Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS, \citep{Shapley2003}, \citep{Nestor2013}, and when combined with deep B,V,R band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival HST ACS and WFC3 imaging covering large swathes of the field, the ancillary data is in excellent support of integral field spectroscopy.
+Spectroscopic data quality assessment and OH feature avoidance criteria are applied in the same way as discussed above, and we fill the KMOS IFUs with galaxies in two pointings spanning the SSA22$\_$a (ssap1) and SSA22$\_$b (ssap2) fields.
+
+% Mentioning the COSMOS field that we did not observe
+Additional pointings in the two fields listed above as well as in both the COSMOS and UDS fields were originally planned, but 50$\%$ of the GTO observing time was lost to bad weather.
+
+% Physical properties - Waiting on information from ROSS for writing this
+The wealth of ancillary data in both fields allows for a consistent treatment of the SED modelling, providing physical properties which are directly comparable between the cluster and field environments.
+We assume solar metallicity stars, the \cite{Calzetti2000} reddening law, and either constant or exponentially declining SFRs.
+The stellar masses and SFRs are extracted....
+
+% comparisons with the Holden paper - MUST EXPLAIN DIFFERENCES IN PHYSICAL PR
+Ten of the targets in goodsp1 have also been observed with the MOSFIRE spectrograph \citep{McLean2012}, and were the subject of a recent paper by \cite{Holden2016} concerning the ubiquitous nature of elevated [OIII]/H$\beta$ ratios in LBGs, and the consequences this observation has for the physical conditions of the ISM (in terms of electron density, ionisation parameter and hardness of radiation field).
+The results from the KDS will complement this study, in the sense that spatially resolved dynamical and chemical information provide key insights into the physical processes driving high redshift LBGs into regions of parameter space which only the most extreme galaxies broach in the local universe.
+
+\subsubsection{Survey Stategy}
+The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies, particularly the fraction of rotating disks and the degree of disk turbulence, and also to investigate the spatial distribution of metals within these galaxies.
+To achieve this we require very deep exposure times in excess of 8 hours on source for all galaxies, to reach the S/N required to detect line emission in the outskirts of the galaxies, where the rotation curves begin to flatten.
+We prioritise the kinematics goal, which requires spatially resolving the [OIII5007] emission line, and so plan to first reach the required K-band depth before observing in the H-band to complement the measurements with [OII3727,3729].
+After large amounts of time was lost to poor weather conditions we decided to observe the SSA22 galaxies with the HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
+This paper is concerned with the KDS kinematics and so for the remainder we focus only on the K-band observations, which took place over the first two years of the programme.
+
+\subsubsection{Observations}\label{subsub:Obs}
+KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
+It has 24 moveable IFUs whichpatrol a region 7.2$^{\prime}$ in diameter, providing considerable flexibility when selecting sources for a single pointing.
+Each set of 8
+
+The central coordinates of these pointings, the number of target galaxies observed, the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
 
@@
     \item Selection techniques
+    \item how physical properties such as stellar mass and SFR are measured
 \end{itemize}
@@
 
-\begin{table*}
+\begin{table*}\label{tab:pointings}
     \centering
-\begin{tabular}{ c c c c c c c }
+\begin{tabular}{ c c c c c c c c }
 
  \hline
-Field & Pointing & N$_{obs}$ & Coordinates & Band & Exp. Time (s) & Seeing (arcsec)  \\
+Field & Pointing & N$_{obs}$ & N$\_[OIII]_{res}$ & Coordinates & Band & Exp. Time (s) & Seeing (arcsec)  \\
  \hline
- GOODS-S & goodsp1 & 19 & 03:32:42 -27:48:58 & K, H & 32400 & 0.5 \\
-GOODS-S & goodsp2 & 18 & 03:32:42 -27:49:08 & K, H & 31800 & 0.52 \\
-SSA22 & ssap1 & 21 & 22:17:28 00:09:54 & HK & 38100 & 0.65 \\
-SSA22 & ssap2 & 18 & 22:17:11 00:15:47 & HK & 27800 & 0.70 \\
+ GOODS-S & goodsp1 & 21 & 16 & 03:32:22 -27:52:51 & K, H & 32400 & 0.5 \\
+GOODS-S & goodsp2 & 19 & 14 & 03:32:35 -27:43:15 & K, H & 31800 & 0.52 \\
+SSA22 & ssap1 & 21 & 13 & 22:17:28 00:09:54 & HK & 38100 & 0.65 \\
+SSA22 & ssap2 & 18 & 11 & 22:17:11 00:15:47 & HK & 27800 & 0.70 \\
  \hline
@@
 \caption{Summary of KDS statistics}
-\label{tab:KDS}
 \end{table*}

### 2016-09-29 paper.tex
29th september morning

@@
 KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
-It has 24 moveable IFUs whichpatrol a region 7.2$^{\prime}$ in diameter, providing considerable flexibility when selecting sources for a single pointing.
-Each set of 8
+The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
+The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RGHgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
+Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band filter has spectral resolution of $R \sim 4200$.
 
-The central coordinates of these pointings, the number of target galaxies observed, the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+We prepare each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsec:datareduction}).
+For both all four of the pointings described above we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating full pixel/half pixel dither pattern for increased spatial sampling around each of the target galaxies.
+This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spatial-pixels (spaxels) as described in \cref{subsec:datareduction}.
 
-\begin{itemize}
-    \item Description of the instrument 
-    \item plagued by poor weather, describe the time frame over which the observations are taken
-    \item OSO observation pattern
-    \item The different wavebands used and potential science that can come out of these observations
-    \item 300s exposures
-    \item describing all of the pointings 
-    \item Different physical conditions in the different pointings
-    \item Selection techniques
-    \item how physical properties such as stellar mass and SFR are measured
-\end{itemize}
+The observations were carried out during August and September of observing semester P92, during August and September of P93 and November of P94.
+The seeing conditions were excellent for goodsp1 and goodsp2, $\sim 0.5^{\prime\prime}$ where we observe 21 and 19 targets respectively, and ranged between $\sim 0.65-0.7^{\prime\prime}$ for ssap1 and ssap2 where 21 and 18 galaxies were observed.
+Note that these numbers are less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92 observing semester and our requirement to observe at least one control star throughout an Observing Block (OB).
+The central coordinates of these pointings, the number of target galaxies observed, N$_{obs}$, the number of galaxies with spatially resolved [OIII5007] emission, N$\_$[OIII]$_{res}$; see \cref{sec:extracting_properties}, the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+In Figure \ref{fig:distributions} we provide an overview of the sample space spanned by the observed galaxies, in relation to the larger population of LBGs within this redshift range.
 
@@
 \end{figure}
-
-Concluding with the pointings that we had, and a table summarising the name of the pointing, the number of galaxies observed in each of those, the combined exposure time and the seeing.
-All of that information is available so could have been able to do this for a while now.
 
@@
 
-\subsection{Observations}
-
-\subsection{Ancillary data}
-
-\subsection{Data reduction techniques}
-The data reduction process relied heavily upon the Software Package for Astronomical Reduction with KMOS (SPARK), implemented using the ESO Recipe Execution Tool (ESOREX).
-In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline.
-These additional steps will be described throughout this section.
+\subsection{Data reduction techniques}\label{subsec:datareduction}
+The data reduction process relied heavily upon the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
+In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.
 
@@
 The four pixel wide gaps between the IFU lenslets in the raw data are then used to correct for readout channel bias across each detector, which if left uncorrected lead to flux bandings over the spatial extent of the reduced cubes.
-Standard star observations are processed to provide a flux calibration for each detector, which is necessary to account for varying sensitivity  
-Following this pre-processing, each of the object-sky pairs are reduced independently to give more control over the way in which the final stacks are created for each galaxy.
-Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxels, justified by the choice of dither pattern boosting the effective spatial resolution of the observations.
-Sky subtraction is performed using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
+Standard star observations are processed to provide a flux calibration for each detector, which is necessary to account for varying sensitivity across the three independent KMOS modules. 
+Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
+Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsub:Obs} which boosts the effective spatial resolution of the observations.
+Sky subtraction is enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
 Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general we find the quality of the sky subtraction in the K-band to be excellent.
+% could insert figure to demonstrate
 Variations in sky subtraction quality are monitored over the course of the OBs which make up the final stacks, as we find that the subtraction performance becomes poorer as the telescope pointing approaches the zenith.
@@
 The telescope tends to drift from its acquired position over the course of an OB, and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
-As part of this analysis, we tested whether the drift varies across the three KMOS detectors, finding typically that the difference is negligible, meaning that it is not necessary to sacrifice more than a single IFU for tracking purposes.
+% insert figure here monitoring drift as function of time?
+Ask Michele here about level of detail
+As part of this analysis, we tested whether the drift varies across the three KMOS detectors, finding typically that the difference is negligible, suggesting that it is not necessary to sacrifice more than a single IFU for tracking purposes.
 
-We stack all 300s exposures for each galaxy which pass the sky subtraction and seeing criteria using sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
+We stack all 300s exposures for each galaxy which pass the sky subtraction and seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
 
-\section{EXTRACTION OF PHYSICAL PROPERTIES}\label{sec:extracting_properties}
+\section{MAPPING PHYSICAL PROPERTIES}\label{sec:extracting_properties}
 \subsection{Spaxel Fitting}

### 2016-09-29 paper.tex
Thursday 29th lunchtime

@@
 
+% Figure how to convert both 3dHST flux and ROSS flux to magnitudes, and then can make the sample and parent scatter plots in the same was as the mass sfr ones for this distribution of targets.
+
 \begin{figure}
@@
 \caption{Distributions of the physical properties of KDS galaxies in both GOODS-S and SSA22}
+\label{fig:distributions}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.47\textwidth]{main_sequence.png}
+\caption{star forming main sequence}
+\label{fig:distributions}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.47\textwidth]{KDS-k_mag_mass.png}
+\caption{Kmag and mass}
 \label{fig:distributions}
@@
 The process is automated and applied to each of the KDS galaxies.
-As mentioned previously, we find 56 galaxies with spatially resolved OIII emission, with this defined as being those where the spatial extent of the OIII is equivalent to or greater than the seeing disk of roughly $0.5^{\prime\prime}$.
+We find 54 galaxies with spatially resolved OIII emission, with this defined as being those where the spatial extent of the OIII is equivalent to or greater than the seeing disk, and the distribution of these galaxies across the pointings is shown in Table \ref{tab:pointings}.
 
-\subsection{Imaging Data}
-It is essential to make use of photometric data which cover the same fields as targetted by the KDS pointings.
-From these data the inclination with respect to line of sight, position angles and sizes of our galaxies can be constrained from single band fitting, and multi-band SPS modelling gives estimates of the global physical properties such as $M_{*}$ and SFR.
-The single band properties complement the observed kinematics from KMOS and provide the information required to estimate intrinsic velocity fields.
-As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $\alpha$ is the axial ratio of an edge-on system, and so is dependent upon an assumption about the `disk thickness'.
+\subsection{Deriving Morphological Properties}
+For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from the available high resolution photometry.
+The first of these properties is the galactic axis ratio, $A_{r}$.
+As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a} \equiv A_{r}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $\alpha$ is the axial ratio of an edge-on system, and so is dependent upon an assumption about the `disk thickness'.
 
@@
 
-This inclination can then be used to correct the line of sight component of the observed velocity, to recover an intrinsic circular velocity, in the standard way.
+A value for this parameter can be constrained by looking at the distribution of derived axis ratios, which for a draw from disk galaxies randomly orientated on the sky should be flat \citep{Sandage1970}.
+The value of $A_{r}$, then, at which this cuts off can be thought of a population disk thickness and used universally (ignoring variation in disk thickness throughout the sample).
+The inclination angle calculated for each galaxy can be used to correct the observed velocity field to the intrinsic, with this correction factor becoming larger as the galaxy becomes more `face-on'.
+The second important morphological parameter is the Position Angle (PA), which is the direction of the photometric major axis of the galaxy on the sky.
+This would be expected to coincide with the kinematic axis in the case of a rotating disk galaxy.
 The discrepancy between morphologial and kinematic position angles is an important indicator of sub-structure in the morphology \citep{Queyrel2012,Wisnioski2015}.
@@
 However for compact, unresolved morphologies there are cases where there is simply not enough information to predict the axis along which velocity gradient will be maximised.
-First this provides a way to extract circular velocities at some fiducial distance from the centre of the galaxy.
+
+The third essential morphological parameter we will use is the half-light radius, $r_{H}$, as this provides a way to extract circular velocities at some fiducial distance from the centre of the galaxy.
 As discussed throughout the introduction, there is no universal definition of what the circular velocity is, and so to compare with previous work it is necessary to extract values consistently from the derived rotation curves.
 Connected to this is the issue of extrapolating model rotation curves or two-dimensional rotation maps beyond the last measured datapoints, which may not extend to the rotation curve plateau due to poor S/N in this regions.
-Knowledge of the effective radii gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made.
-Second, since beam smearing affects all of these measurements and tends to flatten velocity gradients, Durham have invested time into modelling the extent to which this can be corrected.
-The correction is a function of the ratio between $r_{e}$ and PSF size as shown in Figure DURHAM, and so accurately measuring the effective radius of a galaxy vindicates the use of this curve to recover intrinsic circular velocities.
-\\
+Knowledge of the $r_{H}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made.
+Second, since beam smearing affects all of these measurements and tends to flatten velocity gradients, `Durham' (REFERENCE PROPERLY) have invested time into modelling the extent to which this can be corrected.
+The correction is a function of the ratio between $r_{H}$ and PSF size as shown in Figure DURHAM, and so accurately measuring the effective radius of a galaxy vindicates the use of this curve to recover intrinsic circular velocities.
 
-To support the KMOS GOODS-S pointings there is excellent ancillary data from both the ACS and WFC3 instruments aboard HST.
-In tandem with IRAC and spitzer, these provide photometric measurements across the optical and IR regions of the spectrum, from which reliable stellar masses and star formation rates can be derived.
-The high resolution single band images are not inhibited by atmospheric broadening of the PSF and so are rich in morphological information which is useful both to eyeball for interesting features and for constraining the parameters described above.
-The SSA22 pointings have less imaging data, all of which is ground-based, and so both the global physical properties and the single band properties are not constrained as well as in the GOODS-S case.
-Nonetheless, it is possible to determine morphological parameters by fitting the images using GALFIT, as described in section \ref{subsubsec:galfitting}.
+We use the longest wavelength, highest resolution imaging for the fitting of morphological parameters, which in this case is HST F160W band, and opt to use GALFIT \citep{Peng2010_galfit} to recover the parameters as described in section \ref{subsubsec:galfitting}.
 
 \subsubsection{Applying GALFIT to the imaging data}\label{subsubsec:galfitting}
-For the GOODS-S pointings we focus on the deep WFC3 F160W image of GOODS-S, this being the longest wavelength (and therefore least attenuated) measure of the stellar continuum, which traces the rest-frame optical and near-UV light at the median redshift of the KDS galaxies.
+We use GALFIT to fit 2-D analytic functions, convolved with the system PSF, to the observed HST F160W images in both GOODS-S and SSA22 in a consistent way.
+The adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012}.
+The full procedure involves fitting \citep{Bertin1996}
 
@@
 HST vs. TENIS imaging of the same galaxies to confirm whether it is okay to report the physical properties of a sample taken from the ground and then GALFIT.
-
-To complement our KMOS data we make use of publicly available Hubble F160W imaging, which covers all galaxies in our two GOODS-S pointings.
-This imaging is useful not only as part of the ancillary data from which the galactic physical properties are derived, but also as a tool to constrain the size, centre, inclination angle and morphological axis of the galaxies.
-We use GALFIT \citep{Peng2010_galfit} to model the F160W light profile of each GOODS-S galaxy, which attempts to fit a
 
@@
 \section{ANALYSIS \& RESULTS}\label{sec:results}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.4\textwidth]{tf_binned.png}
+\caption{star forming main sequence}
+\label{fig:distributions}
+\end{figure}
 

### 2016-11-19 paper.tex
19th November

@@
   linkcolor=red,
-  urlcolor=Violet}
+  urlcolor=cyan}
 
@@
 % out the following line
+\usepackage{pgfplotstable}
 \usepackage{newtxtext,newtxmath}
+\usepackage{caption}
+\usepackage{subcaption}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+\newcommand{\Sers}{S\'{e}rsic }
+\newcommand{\Lagr}{\mathcal{L}}
 
@@
 
+% TABLES TO INCLUDE
+% 1) MORPHOLOGICAL PROPERTIES
+% 2) SPECTRAL PROPERTIES
+% 3) PROPERTIES INFERRED FROM PHOTOMETRY
+% 4) TABLE OF FINALISED KINEMATIC MEASUREMENTS
+% SO THAT INCLUDES THE VELOCITY DISPERSION AND THE VELOCITY EXTRACTED
+% IN DIFFERENT WAYS FOR THE DIFFERENT POSITION ANGLES AND MODELLING APPROACHES
+
 NO UNIVERSALLY DEFINED MEASURE OF THE CIRCULAR VELOCITY, OR THE POINT AT WHICH TO EXTRACT THAT VALUE.
@@
 \citep{Simons2016} \citep{Pelliccia2016} \citep{Genzel2011} \citep{Epinat2008} \citep{Epinat2008a} \citep{Puech2008} \citep{Puech2007} \cite{Holmberg1958} \citep{Kassin2012} \citep{Flores2006} \citep{Neichel2008} \citep{Miller2011} \citep{Nesvadba2006} \citep{Nesvadba2007} \citep{Livermore2015} \citep{Swinbank2006} \citep{Swinbank2007} \citep{Swinbank2009} \citep{Cortese2014} \citep{VanderWel2012} \citep{Genzel2014a} \citep{Genzel2014} - for the PSF used when Galfitting F160W.
+\citep{Rodriguez-Gomez2016} \citep{Qu2016}
 
@@
 
-The non-cluster environment galaxies are selected from the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 imaging with $\sim 0.1^{\prime\prime}$ angular resolution, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+The non-cluster environment galaxies are selected from the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 F160W imaging with $ 0.13^{\prime\prime}$ pixel scale and $ 0.17^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
 We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
@@
 GOODS-S & goodsp2 & 19 & 14 & 03:32:35 -27:43:15 & K, H & 31800 & 0.52 \\
-SSA22 & ssap1 & 21 & 13 & 22:17:28 00:09:54 & HK & 38100 & 0.65 \\
-SSA22 & ssap2 & 18 & 11 & 22:17:11 00:15:47 & HK & 27800 & 0.70 \\
+SSA22 & ssap1 & 21 & 13 & 22:17:28 00:09:54 & HK & 38100 & 0.62 \\
+SSA22 & ssap2 & 18 & 11 & 22:17:11 00:15:47 & HK & 27800 & 0.57 \\
  \hline
@@
 The inclination angle calculated for each galaxy can be used to correct the observed velocity field to the intrinsic, with this correction factor becoming larger as the galaxy becomes more `face-on'.
-The second important morphological parameter is the Position Angle (PA), which is the direction of the photometric major axis of the galaxy on the sky.
+The second important parameter is the morphological Position Angle (PA), which is the direction of the photometric major axis of the galaxy on the sky.
 This would be expected to coincide with the kinematic axis in the case of a rotating disk galaxy.
@@
 We use GALFIT to fit 2-D analytic functions, convolved with the system PSF, to the observed HST F160W images in both GOODS-S and SSA22 in a consistent way.
-The adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012}.
-The full procedure involves fitting \citep{Bertin1996}
+The GOODS-S imaging data used is the latest release of the total field, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\tiny{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}}.
+For SSA22 we make use of archival HST imaging\footnote{\tiny{\url{https://archive.stsci.edu/hst/search.php}}} (Proposal ID 13844, P.I.
+Lehmer and Proposal ID 11735, P.I.
+Mannucci) covering the SSA22-a field.
+In both cases we first run SExtractor \citep{Bertin1996} across the full fields to recover initial input parameters and segmentation maps for running GALFIT, and then extract postage stamp regions around the galaxies in the KDS sample.
+We fit both single \Sers profiles with a floating \Sers index (n) and also attempt a bulge/disk decomposition by fitting two components; one with n = 1 and one with n = 4.
+The $\chi ^{2}$ of each fit is evaluated and the model with the lowest value is selected as the most suitable representation of the flux profile of the galaxy.
+In both cases the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012}, which has been shown to produce more reliable results than either the Tiny Tim model or an empirical stack alone.
+Crucially, what we gain from this analysis are our best guesses at the three morphological parameters we require to support the kinematic analysis of \cref{subsec:Kinematic Properties}, namely $r_{H}$, $A_{r}$ and the morphological PA.
+Another benefit of studying the high resolution imaging is to be able to interpret peculiarities in the velocity and velocity dispersion fields.
+These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam smearing (see \cref{subsubsec:beam smearing corr}) or in regions apart from the centre of the galaxy.
+Figure \ref{fig:morpho_kinematics} provides two such examples, where the Hubble imaging reveals counterparts to the central galaxy, providing two explanations for the patterns in the observed fields. 
+Either the counterpart object is spatially close to the main galaxy, but significantly offset in distance or the objects are close enough to be interacting gravitationally, thus disturbing the gas from circular motion and boosting the dispersion values.
+% is this a valid thing to say? 
+% is there any way to distinguish between these two different situations?  
+Regardless of which of these situations is really happening, the Hubble imaging enhances our ability to classify each of our targets as multiple component, isolated rotating or isolated disturbed.
+Classification into different categories is necessary to recognise the galaxies which have already formed a gravitationally supported and rotating disk of stars and gas.
+It is only for these galaxies that a maximum circular velocity has any meaning, the derivation of which is the primary concern of this paper.
+The other galaxies have either not yet formed a rotating disk and will do so at a later time, or gravitational interractions with another object have disrupted a disk that was already in place (and we may be witnessing a snapshot of a particular part of that process), or they were destined to never form a disk, probably due to a paucity of initial angular momentum, but yet we still detect OIII emission from ionised regions across the spatial extent of the galaxy.
+We present the morphologcial parameters in Table params, and also provide a classification flag for each object (or group of objects) based upon visual inspection of the Hubble imaging and the velocity fields.
+More details of the method used to classify our target galaxies are provided in Appendix \ref{app:morpho-kinematic}.
+For those galaxies which are classified as isolated rotators, we carry on to derive the kinematic properties as described in \cref{subsec:Kinematic Properties}.
+% Need to answer the question which has been raging for a long time - 
+% how do you classify a galaxy for the following section.
 
-INCLUDE TABLE OF THE GALFIT outputs
-HST vs. TENIS imaging of the same galaxies to confirm whether it is okay to report the physical properties of a sample taken from the ground and then GALFIT.
+\begin{figure*}
+\centering
+\includegraphics[width=0.8\textwidth]{morpho_kinematics.png}
+\caption{High resolution imaging is important not only for reliably recovering the morphological parameters, but also to explain peculiar features in the observed velocity and velocity dispersion fields.
+In the two examples above, multiple components in the HST imaging clearly correspond to marginally different OIII emission wavelengths, which manifest as velocity shifts in individual spaxels and broadens the observed dispersion pattern where the emission lines at different wavelengths merge.}
+\label{fig:morpho_kinematics}
+\end{figure*}
 
-\subsection{Dynamical Modelling}
-Constructing model 2D velocity fields and fitting these to the observed data is a powerful tool for determining the set of parameters which best describe the dynamical state of that galaxy.
-HERE IS WHERE TO MENTION SURVEYS WHICH HAVE DONE THIS IN THE PAST.
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5in]{axis_ratio_distributions.png}
+        \caption{axis ratio distributions}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5in]{size_distributions.png}
+        \caption{size distributions}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5in]{sersic_distributions.png}
+        \caption{sersic distributions}
+    \end{subfigure}
+    \caption{Comparison of physical properties with}
+\end{figure*}
 
-\subsection{Beam Smearing Correction}
+\subsection{Kinematic Properties}\label{subsec:Kinematic Properties}
+% WHEN WILL THE SAMPLE REFINEMENT HAPPEN? % 
+% i.e. should this be written in a way that suggests %
+% we attempt to extract the kinematic parameters for all % 
+% the galaxies in the sample? Or just the clear rotators? % 
+% need to have a clear statement about how that selection is done %
+% which is a combination of the morphology and the observed dynamics % 
+% we can afford to be eyeballing things here because of the small sample size %
+% some people would kill for this data - do the analysis justice and do % 
+% something sensible with the galaxies that don't make it into the kinematic % 
+% analysis part %
+
+As mentioned in the introduction, there is no universal standard for defining the maximum circular velocity, particularly when that value has been extrapolated from the data using a fitted model, of which there are two types.
+The first is something physically motivated, taking into account the potential-well of the galaxy through knowledge of the mass distribution (e.g.
+\citep{Gnerucci2011,Wisnioski2015,ForsterSchreiber2009}).
+The second is a phenomenological model, which assumes a fixed function known to well describe observed galactic rotation curves which flatten at large radii (e.g. \citep{Stott2016}).
+Our main concern when presenting the work carried out for this section is to clearly distinguish between observed velocities and those inferred from modelling.
+This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve and hence infer a maximum velocity.
+There are thus two clear reasons for constructing model velocity fields and fitting these to the observed data for the KDS rotating sample; the first is to extrapolate the observations smoothly to some fiducial radius from which a maximum velocity can be extracted; the second is to estimate the effect of beam smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
+We construct these models in two independent ways to understand the differences that arise from changes to the modelling procedure, these being the 1D and 3D fitting methods described in the following subsections.
+
+%What's the point in writing about the 2D and 1D modelling? 
+%Want to mention the extrapolation of the data where the S/N ratio is
+%too low to measure a value.
+%download barolo and download galpak - compare the two.
+%also compare with the Durham results and compare with my
+%own results from extracting the data using a gaussian fit.
+
+\subsubsection{3D Modelling}\label{subsubsec:3d modelling}
+By simulating a full datacube and fitting the measured quantities to the data, we can constrain both the shape of the velocity field in the spatial direction (in particular the maximum circular velocity) and also derive an estimate for the effect that beam smearing has on the velocity and velocity dispersion fields.
+For each galaxy in the isolated rotating sample we construct a model cube with the same spatial dimensions as the data and populate each spaxel with an OIII emission line that has central wavelength determined by the systemic velocity of the galaxy.
+This central wavelength is then shifted using the velocity derived at that spaxel from the velocity field model.  
+Following the procedure now of numerous authors \citep[e.g.]{Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along the KA determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe:
+
+\begin{equation}\label{eq:arctangent}
+   v_{r} = \frac{2}{\pi}v_{asym}arctan\left(\frac{r}{r_{t}}\right)
+\end{equation}
+
+\noindent
+with r measured as the distance from the centre of rotation, (xcen, ycen).
+This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
+The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
+If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam smearing, which is exactly what we want to correct for.
+The velocity decreases with a factor of cos($\phi$) from the KA, where $\phi$ is the angle measured clockwise from the KA, so that the KA points to the positive side of the velocity field.
+In principle then the model has 5 free parameters; $\{(xcen, ycen), KA, rt, v_{asym}$, rather than the 6 free parameters in previous works \citep[e.g.]{Stott2016} since the inclination to the morphological value.
+The intrinsic flux profile of these simulated OIII lines in the spatial direction is determined using the galfit model derived in section \cref{subsubsec:galfitting}, also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a flat distribution with a default width of 50kms$^{-1}$.
+This simulated intrinsic OIII cube is then convolved slice by slice with the atmospheric seeing profile determined from fitting the collapsed, stacked standard star cube in each pointing with an elliptical gaussian (the recovered seeing values are reported in table \ref{tab:pointings}).
+The velocity and velocity dispersion values are then re-measured in each spaxel and compared with the intrinsic model values to assess the beam smearing impact.
+Convolution with the seeing profile produces a peak in the modelled velocity dispersion field at the centre of rotation and flattens the observed velocity field perpendicular to the KA.
+This provides a beam smearing correction for the velocity dispersion in every spaxel which is equal to the difference between the assumed intrinsic velocity dispersion and the re-measured velocity dispersion after convolution, i.e.
+$\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
+This is computed for each spaxel to provide the 2D $\sigma_{bs}$ correction map.
+The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in section \cref{subsubsec:sigma_errors}.
+We fit the beam smeared velocity field to the observed velocity field, using MCMC sampling with the python `emcee' algorithm \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, and seek the combination of parameters which maximises the log-Likelihood function given by equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
+
+\begin{equation}\label{eq:likelihood}
+   ln\Lagr = \frac{-0.5\sum_{i=1}^{N}(d_{i} - M_{i})^{2}}{\sigma_{v}^{2}} - ln\left(\frac{1}{\sigma_{v}^{2}}\right)
+\end{equation}
+
+In practice we fix the (xcen,ycen) parameters of the galaxy to the location of the stellar continuum, a proxy for the centre of the gravitational potential well, recovered from the collapsed KMOS cube, leaving only 3 free parameters to vary in the MCMC sampling.
+This assumes that the gas and the stars in the galaxy share a common centre of mass, an assumption which is at least verified for the vast majority of SFGs in the local and intermediate redshift universe.
+Due to the faintness of the continuum, there are several galaxies for which we cannot reliably estimate the rotation centre using this method, and instead opt to set (xcen,ycen) to coincide with the peak OIII flux location.
+This differs from the method of fixing the rotation centre at the midpoint between the velocity extrema, described in \cite{Wisnioski2015} and \cite{Rodrigues2016}.
+In general the S/N of our sample is low at the galaxy outskirts and for many of the isolated rotating sample we don't observe the flattening of the velocity field.
+This suggests that the velocity midpoint may be biased towards the side of the galaxy which shows the higher velocity value and so we instead use the physically motivated continuum centre where possible.
+
+The MCMC sampling provides a distribution of parameter values around those which provide the maximum likelihood, an example of which is shown in Figure \ref{fig:8543_mcmc}.
+The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in \cref{subsubsec:model_errors}.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{8543_mcmc.png}
+\caption{Example parameter grid for 8543}
+\label{fig:8543_mcmc}
+\end{figure}
+
+The best fitting smeared and intrinsic models for the isolated rotating sample extracted along the KA, along with shaded uncertainty ranges, are plotted in Appendix A1 for the GOODS-S sample and Appendix A2 for the SSA sample.
+Overplotted onto the models are the data values and uncertainties extracted along the KA.
+This figure is accompanied by the HST imaging for each galaxy (HST F160W in GOODS-S and ACS F814W in SSA22\footnote{There are 2 galaxies in the SSA sample which did not have ACS F814W imaging, but had F160W imaging with lower integration time, and 3 galaxies not covered by either F160W or ACS 814W imaging, in which case we must resort to ground based SUBARU i-band imaging}), the best fit galfit model and residuals, the narrowband OIII image, 2D maps of the OIII Flux, observed velocity, observed dispersion, best fitting smeared model velocity, data - model residuals, intrinsic velocity dispersion (observed dispersion corrected for beam smearing and instrumental resolution as described in \cref{subsubsec:param_extraction}) as well as a plot of 1D extractions along the observed, intrinsic and beam smeared dispersion maps.
+After the modelling, the kinematic parameters must be extracted from the 2D intrinsic fields, as described in \cref{subsubsec:param_extraction}.
+
+\subsubsection{Kinematic Parameters Extraction}\label{subsubsec:param_extraction}
+The crucial information to extract for the model grids described above for each galaxy, both for this study and for comparison to previous studies, is a measure of the maximum intrinsic circular velocity, $V_{max}$, and a single measurement of the intrinsic velocity dispersion, $\sigma_{int}$.
+Previous studies have measured these quantities in several different ways:
+MENTION GNERUCCI, FS, WISNIOSKI, STOTT, LAW etc. 
+In some of the isolated rotating sample, the extracted $V_{max}$ value involves significant extrapolation ($> 40kms^{-1}$) above the last observed data point.
+This is a combination of the beam smearing effect leading to a flatter observed velocity field at small radii and the low S/N of this very high redshift sample limiting the radius at which the final observed data point can be extracted.
+We hope to be transparent about when large extrapolations are happening, usually as a consequence of a smaller ratio $\frac{R_{KMOS}}{R_{e}}$, where $R_{KMOS}$ is the radius of the last extracted KMOS datapoint and $R_{e}$ is the effective radius measured with GALFIT, by presenting the observed $V_{max}$ values, the beam smeared model $V_{max}$ and the intrinsic model $V_{max}$ in the table of kinematic properties.
+
+\subsubsection{3D modelling error estimates}\label{subsubsec:model_errors}
+
+\subsubsection{1D Modelling}\label{subsubsec:1d modelling}
+\subsubsection{Beam Smearing Correction}\label{subsubsec:beam smearing corr}
 
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA HST, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
 
@@
 
-\section{Some extra material}
+\section{Rotating Galaxies plots}
 
@@
 
+\section{Morpho-Kinematic Classification}\label{app:morpho-kinematic}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-07 paper.tex
About to start addressing Chris comments towards the end of ESO time 2017

--- 2016-09-29 paper.tex
@@
-\documentclass[a4paper,fleqn,usenatbib]{mn2e}
+\documentclass[fleqn,usenatbib]{mn2e}
 
@@
 \usepackage{newtxtext,newtxmath}
+\usepackage{subcaption}
+\usepackage{lscape}
+\usepackage[LGRgreek]{mathastext}
+
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 \usepackage{amssymb}    % Extra maths symbols
+\usepackage[flushleft]{threeparttable}
 
@@
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+\newcommand{\Sers}{S\'{e}rsic }
+\newcommand{\Lagr}{\mathcal{L}}
+\newcommand\tab[1][1cm]{\hspace*{#1}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%  PAGE %%%%%%%%%%%%%%%%%%%
 
@@
 % Keep the title short and informative.
-\title[Spatially resolved dynamics at $z \sim 3.5$]{The KMOS Deep Survey: Resolved gas dynamics at $z \sim 3.5$}
+\title[KDS: dynamical properties of z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
+Programme IDs: }}
 
@@
 \author[O.J. Turner et al.]{
-Owen J. Turner,$^{1}$\thanks{E-mail: turner@roe.ac.uk (OJT)}
-M. Cirasuolo,$^{1}$
-J. Dunlop$^{1}$
-R. J. McLure$^{1}$
+O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
+M. Cirasuolo,$^{1,2}$
+C. M. Harrison,$^{2,3}$
+J. Dunlop,$^{1}$
+R. J. McLure,$^{1}$\newauthor
+A. M. Swinbank$^{4,3}$
+H. L. Johnson$^{3,4}$
 \\
-% List of institutions
 $^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
+$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
+$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.
 }
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2016}
+\pubyear{2017}
 
@@
 \begin{abstract}
-We present first results from the KMOS Deep Survey (KDS), which is an ESO guaranteed time survey of 80 star-forming galaxies in the redshift range $z = 3 - 3.8$.
-From this sample we detect spatially resolved [OIII5007] emission in the K-band from 57 galaxies, allowing us to explore the fraction which show ordered rotational motions, presumably in a star-forming disk.
-41 galaxies show a clear, smooth velocity gradient along the kinematic axis, meriting them for further investigation via dynamical modelling.
-The ratio of maximum rotational velocity to intrinsic velocity dispersion, $v / \sigma _{int}$, is commonly used to indicate the extent to which the gas in disk galaxies is dominated by ordered rotation or random motions.
-We find that 16 galaxies have $v / \sigma _{int} > 1$, in broad agreement with results found at similar and low redshift.
-The mean values of $v / \sigma _{int}$ are substantially lower in this redshift range than are observed locally; since the measured rotational velocity values have remained roughly constant over cosmic time this suggests that turbulent gas motions within the disk become steadily more important with increasing redshift.
-We investigate the causes for this, linking the increase in $\sigma _{int}$ to increasing gas fraction and decreasing galaxy size, following the virial theorem and a $(1 + z)^{-1}$ scaling.
-Finally we look into correlations between the maximum rotational velocity of galaxies and their global properties, finding that galaxies with higher stellar mass tend to rotate faster.
-
+We present dynamical measurements of 44 O[III]$\lambda5007$ resolved main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
+These measurements push back the frontier of dynamical studies utilising Integral-Field Spectroscopy, and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$, and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
+The mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with previous studies which have reported increasing $\sigma_{int}$ values with redshift.
+We find that $39 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
+The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e.
+$V_{C}-M_{\star}$) relation (the inverse of the stellar mass Tully-Fisher relation), although a smaller fraction of the galaxies sit on the relation due to the increase in the dispersion dominated fraction.
+The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this evolution the result of the gradual size evolution of the star-forming population over cosmic time.
+Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
+To explore this further, we plot the S$_{0.5}$-stellar mass relation, finding that the slope and normalisation are consistent with measurements between $z=0-1.2$, however we caution that there is no clear connection between $\sigma_{int}$ and stellar mass.
+These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
+There is a very high merger fraction of 89\% in a pointing covering the centre of the $z\sim3.1$ protocluster in the SSA22-a field, and merger fraction of 15\% across the remaining pointings.
 \end{abstract}
@@
 \begin{keywords}
-Integral Field Unit -- KMOS -- Dynamics -- Turbulence
+galaxies:kinematics and dynamics -- galaxies:evolution -- galaxies:integral field spectroscopy
 \end{keywords}
@@
 
-NO UNIVERSALLY DEFINED MEASURE OF THE CIRCULAR VELOCITY, OR THE POINT AT WHICH TO EXTRACT THAT VALUE.
+In the hierarchical collapse scenario \citep{Rees1977,Fall1980}, matter density perturbations, which originate from some set of cosmological initial conditions, grow over time before condensing out of the general expansion to form dark matter halos \cite{Silk1968,Peebles1970}.
+It is at the centre of these halos that baryons collect, cool and begin to form stars (\cite{Birnboim2003,Keres2005,Dekel2006} and see e.g.
+\cite{Mo2010} for a recent review), with these systems constituting the first galaxies.
+One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue (e.g.
+\cite{Fall1983}).
 
-% Check references here - exactly where does this scenario come from? 
-In the hierarchical collapse scenario \citep{Fall1980}, matter density perturbations, which originate from some set of cosmological initial conditions, grow over time before condensing out of the general expansion to form dark matter haloes (Lifshitz 1960) \cite{Silk1968,Peebles1970}.
-Mixed amongst this dark matter is baryonic gas, which is initially shock heated to the virial temperature of the halo during the gravitational collapse \citep{Birnboim2003,Keres2005,Dekel2006}.
-As the baryons collectively cool, they accumulate at the centre of the potential well of the host halo as dense and cold protogalactic gas.
-One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue.
+It has been observationally determined that the galaxy population is bimodal in many physical properties at each redshift slice at which it is studied (e.g.
+as listed in \cite{Dekel2006}), with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies.
+For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
+This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, and outflows and accretion events maintain a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
+The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sparre2015,Lee2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic star formation rate density in this redshift range \citep{Madau_2014}.
+At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs, and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
+This assumes that high redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b}, and also assumes that something can be learned about galaxy evolution (i.e.
+how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
+The picture is complicated by the addition of major and minor mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014}, and the relative importance of in-situ, secular stellar mass growth vs.
+stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}.
+To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be some process which shuts off star-formation within main sequence galaxies (i.e.
+quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010}.
 
-It is an observationally determined fact that the galaxy population is bimodal in many physical properties at each epoch after galaxies begin to form, with a preference for the most massive galaxies to lie in the red sequence, characterised by red colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies.
-\citep{Abramson2016,Abramson2016a}
-\citep{Pannella2009a}
+Recent cosmological volume simulations are able to resolve the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
+Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations which must be reproduced across cosmic time.
+The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons, and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \cite[e.g.][]{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
+Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Bundy2015,Wisnioski2015,Stott2016} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope (HST) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
+In particular, in recent years the multiplexing capabilities of KMOS have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Harrison2016,Mason2016} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
 
-\citep{Baldry2006}
-simulations explaining the biodality in terms of AGN feedback and a cut at a characteristic mass scale.
-\citep{Birnboim2003,Dekel2006,Keres2005,Bower2006,Croton2006}
-Explaining the observed number densities of early and late type galaxies at different epochs in terms of their formation mechanisms and evolutionary histories is one of the key goals of modern astronomy.
-Two scenarii have emerged.
-The first highlights the importance of secular evolution, whereby cold gas accreted along cosmic web filaments `tops up' the existing baryon supply which fuels star formation, stellar mass within a galaxy is continually built up with in-situ star formation and the rate of star formation itself is regulated by both stellar and AGN feedback.
-In this picture there is a certain mass scale above which a galaxy becomes quenched - EXPAND UPON THAT
-The second suggests that environmental effects dominate the evolutionary demographic, with mass buildup predominantly occuring through minor mergers and major mergers triggering the cessation of star formation and building the red sequence at each epoch.
-Throughout the last few years both the results from simulations REF and observations have pushed the community towards the former picture, which downplays the significance of mergers in driving galaxy evolution.
+SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
+This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic Star Formation Rate Density (SFRD) \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
+There is also an increasing body of work measuring the relationship between the observed maximum rotational velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Tiley2016a,Harrison2017}.
+In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
 
-%,Understanding the evolving dynamical state of disky star-forming galaxies (SFGs) throughout cosmic time is central to understanding the topics of galaxy formation and evolution.
-%There are two different evolutionary scenarii.
-%The first suggests that the buildup of stellar mass, $M_{*}$, over time within galaxies is hierarchical, with minor mergers steadily contributing to $M_{*}$ and major mergers bringing about the cessation of star formation by shock heating of the cold molecular gas.
-%The second is the equilibrium model of galaxy evolution e.g.
-\cite{Genel2008,Bouche2010,Dave2011,Dave2011a,Dave2011b,Krumholz2012,Lilly2013}, where the gas content of SFGs regulates their Star Formation Rates (SFRs) and varies smoothly inside individual galaxies throughout their lifetimes.
-%In this picture the galactic gas budget is mediated by inflows of cold gas along cosmic web filaments \citep{Keres2005,Dekel2006} processing of the cold gas with steady, secular star formation and by outflows of gas from Active Galactic Nuclei (AGN) and stellar feedback.
-%SFGs locked in this cycle of gas consumption form a galactic `Main Sequence', which is a fairly tight relationship between the SFR and stellar mass $M_{*}$  
-%Over the last decade there have been considerable advancements
+In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focussing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
+There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts.
+For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high redshift?
+\textbf{(2)} What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
+\textbf{(3)} What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
+\textbf{(4)} What are the connections between the chemical properties and the kinematics of the gas, particularly in terms of inflows and outflows of material?
 
-References for other things
-MAIN SEQUENCE
-\citep{Daddi2007} \citep{Elbaz2011a} \citep{Elbaz2007} \citep{Noeske2007a}
+This study focusses on the final question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotational velocities and velocity dispersions, using the [OIII]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
+We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
+By making use of KMOS we have been able to spatially resolve [OIII]$\lambda$5007 emission in 44 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.
 
-These are all the references for kinematics, not all the references for other things and other aspects of galaxy evolution. 
-\citep{Wisnioski2015} \citep{ForsterSchreiber2009} \citep{ForsterSchreiber2006} \citep{Stott2016} \citep{Gnerucci2011} \citep{Epinat2012} ,\citep{Epinat2009} \citep{Epinat2010} \citep{Lilly2013} \citep{Saintonge2013} \citep{Wisnioski2011} \citep{Wright2007} \citep{Wright2009} \citep{Genzel2008} \citep{Genzel2006} \citep{Shapiro2008} \citep{Jones2010a} \citep{Newman2013} \citep{Genel2008} \citep{Nesvadba2008} \citep{Queyrel2012} \citep{Law2007} \citep{Law2009}
-\citep{Simons2016} \citep{Pelliccia2016} \citep{Genzel2011} \citep{Epinat2008} \citep{Epinat2008a} \citep{Puech2008} \citep{Puech2007} \cite{Holmberg1958} \citep{Kassin2012} \citep{Flores2006} \citep{Neichel2008} \citep{Miller2011} \citep{Nesvadba2006} \citep{Nesvadba2007} \citep{Livermore2015} \citep{Swinbank2006} \citep{Swinbank2007} \citep{Swinbank2009} \citep{Cortese2014} \citep{VanderWel2012} \citep{Genzel2014a} \citep{Genzel2014} - for the PSF used when Galfitting F160W.
-
-MOTIVATING THE FOLLOWING SECTION
-
-The KMOS Deep Survey (KDS) is a guaranteed time programme focussing on the spatially resolved properties of star forming galaxies during a time where the universe is building to peak activity.
-There are still many open questions which we can begin to answer by studying the emission, or lack thereof, from regions of ionised gas within individual galaxies at these redshifts.
-For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high redshift?
-\textbf{(2)} What are the radial gradients in metal enrichment and would evidence for inverse gradients suggest infall of pristine gas to the central regions of these galaxies?
-\textbf{(3)} What are the connections between the chemical properties and the kinematics of the gas, particularly in terms of inflows and outflows of material?
-\textbf{(4)} What role does formation environment play in shaping the dynamical and chemical evolution of galaxies? 
-KMOS benefits from the ability to study many targets simultaneously, with 24 deployable IFUs patrolling a $7^{\prime}$ patch of sky.
-Attempting to spatially resolve the flux from emission lines at $z \sim 3.5$ necessarily requires on source integration times $>$ 6 hours, and so the multiplexing capability provides KMOS with an enormous advantage in terms of observing time over other instruments for this type of study.
-This has the knock-on effect of enabling a more general galaxy selection criteria, so that the KDS targets will be representative of the main sequence star forming population.
-
-Many of these questions have already been addressed at lower redshift, as described above \citep{ForsterSchreiber2009,Wisnioski2015,Stott2016}, and also in a similar redshift range \cite{Gnerucci2011}.
-The KDS will complement the lower redshift results by providing an additional data point on any plots showing evolutionary sequences of derived physical properties, therefore providing a more complete description of galaxy evolution starting from before cosmic high noon and running up to the present day.
-The high redshift results of \cite{Gnerucci2011} will be expanded upon by the KDS, which extends to lower stellar masses and will increase the sample size for which physical properties can be resolved by roughly a factor of three.
-
-In this paper we focus on deriving and interpreting the spatially resolved kinematics of KDS galaxies using the [OIII5007] emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$, and focussing on forming evolutionary links with lower redshift work.
-We combine our KMOS data with the high resolution and sensitivity of the Hubble Space Telescope (HST) WFC3 H-band imaging in a spectro-photometric analysis, so that the kinematics can also be understood in the context of galaxy morphology.
-In a future paper, (Turner \textit{et al.} in prep.), we will investigate the radial gradients in galaxy metallicity and hence the spatially resolved physical conditions within the ISM.
-
-The structure of the current paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction.
-In \cref{sec:extracting_properties} we explain how the two-dimensional maps of physical properties were extracted from our stacked datacubes and then describe the treatment of these maps and the modelling which leads to the final table of physical properties for the KDS galaxies.
-\cref{sec:results} presents our physical findings which are then discussed in \cref{sec:discussion}.
-We then conclude in \cref{sec:conclusions}.
+The structure of the paper is as follows.
+In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
+In \cref{sec:extracting_properties} we explain how two-dimensional maps of physical properties were extracted from our stacked datacubes and the treatment of the HST imaging to derive the morphological properties of our galaxies.
+We also define a classification procedure which separates the KDS galaxies into a merger and modelling sample.
+In \cref{sec:Kinematic_Properties} we present the kinematic modelling applied to the KDS galaxies, including the beam smearing correction, and the method chosen to extract the kinematic properties following this modelling procedure.
+\cref{sec:results} presents an analysis of the derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
+We present our conclusions in \cref{sec:conclusion}.
 Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).
@@
 \section{SURVEY \& DATA REDUCTION}\label{sec:Survey_and_data}
-
-% note going to assume here that the KMOS targets were selected from 
-% from VVDS, COSMOS
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Notes for the sample selection plots
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 1. mstar vs sfr - must have full sample in the backgroud 
-% and also lines showing where the main sequence of star formation
-% should lie on this plot
-% 2. colour vs mass plots - showing again the general population in 
-% the background - will need to convert fluxes to magnitudes?
-% Maybe a redshift vs. magnitude plot or something similar, showing
-% how faint these targets are.
-
 \subsection{The KMOS Deep Survey: sample selection and observations}
 Our target selection for the KDS sample is designed to pick out star-forming galaxies at $z = 3-4$, supported by deep multi-wavelength ancillary data and probing both cluster and field environments.
-Within this redshift range the [OIII4959,5007] doublet and the $H_{beta}$ emission lines are visible in the K-band and the [OII3727,3729] doublet is visible in the H-band, both of which are observable with KMOS.
-We also want to draw galaxies covering a wide range in the SFR-$M_{*}$ relation, so that we are ultimately tracking the physical properties of a representative sample of the star-forming population at these redshifts.
+Within this redshift range the [OIII]$\lambda$4959,$\lambda$5007 doublet and the $H_{\beta}$ emission lines are visible in the K-band and the [OII$\lambda$3727,$\lambda$3729] doublet is visible in the H-band, both of which are observable with KMOS.
+We also want to draw galaxies covering a wide range in the SFR-$M_{\star}$ relation, so that we are ultimately tracking the physical properties of a representative sample of the star-forming population at these redshifts.
 For these reasons, and to ensure a high detection rate of the ionised gas emission lines in the KDS galaxies, we select galaxies in well studied fields that have a previous spectroscopic detection.
@@
 Predominantly, the galaxies have been selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
-However a subset of the selected cluster galaxies in SSA22 were blindly detected in Ly$\alpha$ emission, during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
+However, a subset of the selected cluster galaxies in SSA22 were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
 These `Lyman-Alpha Blobs' (LABs), which are extended and diffuse emission regions associated with but not centred on LBGs \citep{Steidel2000}, and especially LAB01, have been the subject of much previous study, e.g.
@@
 
-The non-cluster environment galaxies are selected from the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 imaging with $\sim 0.1^{\prime\prime}$ angular resolution, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+The low-density environment galaxies are selected from the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 F160W imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
 We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
-These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [OIII5007] or H$_{\beta}$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
-The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions of spatial overdensity in the south-east (goodsp1) and north-west (goodsp2) to fill the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
-
+These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [OIII]$\lambda$5007 or H$_{\beta}$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
+The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions of spatial overdensity in the south-east (GOODS-S-P1) and north-west (GOODS-S-P2) to fill the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
 % Add the programme ID for HST WFC3 imaging
-The cluster galaxies are all from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003}, \citep{Shapley2003}, which, as mentioned above, is an extreme overdensity of LBG candidates at $z \sim 3.09$.
-Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS, \citep{Shapley2003}, \citep{Nestor2013}, and when combined with deep B,V,R band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival HST ACS and WFC3 imaging covering large swathes of the field, the ancillary data is in excellent support of integral field spectroscopy.
-Spectroscopic data quality assessment and OH feature avoidance criteria are applied in the same way as discussed above, and we fill the KMOS IFUs with galaxies in two pointings spanning the SSA22$\_$a (ssap1) and SSA22$\_$b (ssap2) fields.
-
-% Mentioning the COSMOS field that we did not observe
-Additional pointings in the two fields listed above as well as in both the COSMOS and UDS fields were originally planned, but 50$\%$ of the GTO observing time was lost to bad weather.
-
+The cluster galaxies are selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an extreme overdensity of LBG candidates at $z \sim 3.09$.
+Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS, \citep{Shapley2003}, \citep{Nestor2013}, and when combined with deep B,V,R band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival HST ACS and WFC3 imaging covering large swathes of the field, the ancillary data is in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the CANDELS fields.
+Fortunately at $z \sim 3.09$ the [OIII]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so we also fill the KMOS IFUs with galaxies in two pointings spanning the SSA22 protocluster, one towards the centre of the cluster (SSA22-a) and one to the south (SSA22-b).
+Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during a poor year for Paranal.
 % Physical properties - Waiting on information from ROSS for writing this
 The wealth of ancillary data in both fields allows for a consistent treatment of the SED modelling, providing physical properties which are directly comparable between the cluster and field environments.
-We assume solar metallicity stars, the \cite{Calzetti2000} reddening law, and either constant or exponentially declining SFRs.
-The stellar masses and SFRs are extracted....
-
+During the SED modelling we assume solar metallicity stellar templates, and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs to compute stellar masses and SFRs for the galaxies in both GOODS-S and SSA22.
+We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
+The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
 % comparisons with the Holden paper - MUST EXPLAIN DIFFERENCES IN PHYSICAL PR
-Ten of the targets in goodsp1 have also been observed with the MOSFIRE spectrograph \citep{McLean2012}, and were the subject of a recent paper by \cite{Holden2016} concerning the ubiquitous nature of elevated [OIII]/H$\beta$ ratios in LBGs, and the consequences this observation has for the physical conditions of the ISM (in terms of electron density, ionisation parameter and hardness of radiation field).
+Ten of the targets in goodsp1 have also been observed with the MOSFIRE spectrograph and were the subject of a recent paper by \cite{Holden2016} concerning the ubiquitous nature of elevated [OIII]/H$\beta$ ratios in LBGs, and the consequences this observation has for the physical conditions of the ISM (in terms of electron density, ionisation parameter and hardness of radiation field).
 The results from the KDS will complement this study, in the sense that spatially resolved dynamical and chemical information provide key insights into the physical processes driving high redshift LBGs into regions of parameter space which only the most extreme galaxies broach in the local universe.
-
 \subsubsection{Survey Stategy}
-The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies, particularly the fraction of rotating disks and the degree of disk turbulence, and also to investigate the spatial distribution of metals within these galaxies.
-To achieve this we require very deep exposure times in excess of 8 hours on source for all galaxies, to reach the S/N required to detect line emission in the outskirts of the galaxies, where the rotation curves begin to flatten.
-We prioritise the kinematics goal, which requires spatially resolving the [OIII5007] emission line, and so plan to first reach the required K-band depth before observing in the H-band to complement the measurements with [OII3727,3729].
+The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks and the degree of disk turbulence, and also to investigate the spatial distribution of metals within these galaxies.
+This will add substantially to the sample of galaxies already observed in integral field spectroscopy at this epoch \citep{Cresci2010,Gnerucci2011}.
+To achieve this we require very deep exposure times in excess of 7 hours on source for all galaxies, to reach the S/N required to detect line emission in the outskirts of the galaxies, where the rotation curves begin to flatten, and to make measurements within individual spatial pixels (spaxels).
+This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the spatially resolved metallicities reserved for a future work.
+To measure the dynamics we must spatially resolve the [OIII]$\lambda$5007emission line, and so the observing strategy has been designed to first reach the required K-band depth before observing in the H-band to complement the [OIII]$\lambda$5007 and $H_{\beta}$ lines with [OII$\lambda$3727,$\lambda$3729] for metallicity measurements.
 After large amounts of time was lost to poor weather conditions we decided to observe the SSA22 galaxies with the HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
-This paper is concerned with the KDS kinematics and so for the remainder we focus only on the K-band observations, which took place over the first two years of the programme.
-
+For the remainder of the paper we focus only on the K-band observations, which took place over the first two years of the programme. 
 \subsubsection{Observations}\label{subsub:Obs}
@@
 
-We prepare each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsec:datareduction}).
-For both all four of the pointings described above we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating full pixel/half pixel dither pattern for increased spatial sampling around each of the target galaxies.
-This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spatial-pixels (spaxels) as described in \cref{subsec:datareduction}.
+We prepare each pointing using $PA_{kin}$RMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsec:datareduction}).
+For all four of the pointings described above, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
+This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsec:datareduction}.
 
 The observations were carried out during August and September of observing semester P92, during August and September of P93 and November of P94.
-The seeing conditions were excellent for goodsp1 and goodsp2, $\sim 0.5^{\prime\prime}$ where we observe 21 and 19 targets respectively, and ranged between $\sim 0.65-0.7^{\prime\prime}$ for ssap1 and ssap2 where 21 and 18 galaxies were observed.
+The seeing conditions were excellent for goodsp1 and goodsp2, $\sim 0.5^{\prime\prime}$ where we observe 20 and 19 targets respectively, and ranged between $\sim 0.55-0.65^{\prime\prime}$ for ssap1 and ssap2 where 21 and 19 galaxies were observed.
 Note that these numbers are less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92 observing semester and our requirement to observe at least one control star throughout an Observing Block (OB).
-The central coordinates of these pointings, the number of target galaxies observed, N$_{obs}$, the number of galaxies with spatially resolved [OIII5007] emission, N$\_$[OIII]$_{res}$; see \cref{sec:extracting_properties}, the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
-In Figure \ref{fig:distributions} we provide an overview of the sample space spanned by the observed galaxies, in relation to the larger population of LBGs within this redshift range.
-
-% Figure how to convert both 3dHST flux and ROSS flux to magnitudes, and then can make the sample and parent scatter plots in the same was as the mass sfr ones for this distribution of targets.
-
+In Figure \ref{fig:main_sequence} we plot the stellar mass (M$_{\star}$) and SFR `main sequence' of the KDS galaxies, in combination with the derived physical properties of $2 < z < 3$ SFGs (based upon the `z\_best classification flag') from the 3D-HST survey \citep{Brammer2012,Momcheva2015}.
+We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-HST data described in \cite{Whitaker2014} and note that the KDS galaxies scatter consistently above and below these lines, suggesting that they are mostly regular SFGs in the process of converting their gas into stars (i.e.
+they are not especially bursty, or devoid of star formation).
+There are fewer galaxies plotted in Figure \ref{fig:main_sequence} than observed due to the lack of deep, ground-based J and K-band photometry in SSA22 leaving the SFR unconstrained for several objects.
+We omit from this main sequence plot all objects in SSA22 that have J and K band detections lower than 2-$\sigma$ significance, leaving 64\% of the sample across all pointings, and note that the derived (M$_{\star}$) values for the galaxies which are not plotted are consistent with the distribution shown in figure \ref{fig:main_sequence}.
 \begin{figure}
 \centering
-\includegraphics[width=0.47\textwidth]{paper_distributions.png}
-\caption{Distributions of the physical properties of KDS galaxies in both GOODS-S and SSA22}
-\label{fig:distributions}
+\includegraphics[width=0.49\textwidth]{main_sequence.png}
+\caption{We plot the location of the KDS galaxies across the four pointings on the star forming `main sequence', with filled symbols showing galaxies detected in the [OIII]$\lambda$5007 emission line galaxies and open symbols those in which no detection has been made.
+Also plotted with the small grey points are individual SFGs from the 3D-HST survey at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
+The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in Whitaker+14.
+The KDS galaxies scatter evenly above and below, suggesting that these are typical SFGs which sample the main sequence of star formation between 9.5 $< log(M_{\star}[M_{\odot}]) <$ 10.5 and have mean $log(M_{\star}[M_{\odot}]) = 10.0$.
+There appears to be no connection between main sequence position and likelihood of detection, where we might have expected it would be harder to detect ionised emission in fainter galaxies that are either below the MS or with low $log(M_{\star}[M_{\odot}])$.
+There are fewer KDS galaxies represented on this plot than observed, due to our inability to constrain SFRs for 29/40 galaxies observed in SSA22 as a result of shorter wavelength baseline and shallower ancillary photometry.
+For these galaxies it is still possible to derive an $M_{\star}$ value and we note that the distribution is consistent with the galaxies plotted in this figure.}
+\label{fig:main_sequence}
 \end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.47\textwidth]{main_sequence.png}
-\caption{star forming main sequence}
-\label{fig:distributions}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.47\textwidth]{KDS-k_mag_mass.png}
-\caption{Kmag and mass}
-\label{fig:distributions}
-\end{figure}
-
-\begin{table*}\label{tab:pointings}
-    \centering
-\begin{tabular}{ c c c c c c c c }
-
- \hline
-Field & Pointing & N$_{obs}$ & N$\_[OIII]_{res}$ & Coordinates & Band & Exp. Time (s) & Seeing (arcsec)  \\
- \hline
- GOODS-S & goodsp1 & 21 & 16 & 03:32:22 -27:52:51 & K, H & 32400 & 0.5 \\
-GOODS-S & goodsp2 & 19 & 14 & 03:32:35 -27:43:15 & K, H & 31800 & 0.52 \\
-SSA22 & ssap1 & 21 & 13 & 22:17:28 00:09:54 & HK & 38100 & 0.65 \\
-SSA22 & ssap2 & 18 & 11 & 22:17:11 00:15:47 & HK & 27800 & 0.70 \\
- \hline
-\end{tabular}
-\caption{Summary of KDS statistics}
-\end{table*}
-
 \subsection{Data reduction techniques}\label{subsec:datareduction}
@@
 The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
-The four pixel wide gaps between the IFU lenslets in the raw data are then used to correct for readout channel bias across each detector, which if left uncorrected lead to flux bandings over the spatial extent of the reduced cubes.
+The four pixel wide gaps between the IFU lenslets in the raw data are then used to correct for readout channel bias across each detector, which if left uncorrected leads to flux bandings over the spatial extent of the reduced cubes.
 Standard star observations are processed to provide a flux calibration for each detector, which is necessary to account for varying sensitivity across the three independent KMOS modules. 
@@
 Sky subtraction is enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
-Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general we find the quality of the sky subtraction in the K-band to be excellent.
+Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general we find the quality of the sky-subtraction in the K-band to be excellent.
 % could insert figure to demonstrate
-Variations in sky subtraction quality are monitored over the course of the OBs which make up the final stacks, as we find that the subtraction performance becomes poorer as the telescope pointing approaches the zenith.
-This is due to the telescope having to track faster whilst at zenith positions, hence scanning more rapidly over regions of sky with spatially and temporally varying OH emission.
+Variations in sky-subtraction quality are monitored over the course of the OBs which constitute the final stacks, as we find that the sky-subtraction performance becomes poorer as the telescope pointing approaches the zenith.
+This is due to the telescope tracking faster whilst looking through very low airmasses, hence scanning more rapidly over regions of sky with spatially and temporally varying OH emission.
 In addition to this we monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames with unacceptable seeing and to measure the spatial shifts required for the final stack more precisely.
@@
 
-We stack all 300s exposures for each galaxy which pass the sky subtraction and seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
+We stack all 300s exposures for each galaxy which pass the sky-subtraction and seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
+The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [OIII]$\lambda$5007 detected across the stacked cubes from visual inspection using the QFitsView software \citep{Ott2012}, N$_{[OIII]_{Det}}$, the number with spatially resolved [OIII]$\lambda$5007 emission, N$_{[OIII]_{Res}}$ (see \cref{sec:extracting_properties}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+We note that in goodsp2 we later found that the redshifts for two of our targets, lbg$\_$40 and lbg$\_$64 were $z < 0.5$ and removing these from consideration would raise the genuine detection percentage to $82\%$, and the resolved percentage to $65\%$ in GOODS-S-P2.
+
+\begin{table*}
+\centering
+\caption{Summary of KDS pointing statistics}
+\label{tab:pointings}
+\begin{tabular}{c c c c c c c c c c c}
+
+ \hline
+Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res. & Band(s) & Exp. Time (s) & Seeing ($^{\prime\prime}$)  \\
+ \hline
+ GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & K, H & 32400 & 0.5 \\
+GOODS-S-P2 & 03:32:35 & -27:43:15 & 19 & 14 & 74 & 11 & 58 & K, H & 31800 & 0.52 \\
+SSA22-a & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 10 & 46 & HK & 38100 & 0.62 \\
+SSA22-b & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & HK & 27800 & 0.57 \\
+ \hline
+\end{tabular}
+\end{table*}
 
@@
 Having produced stacked and calibrated datacubes for each of the galaxies in the sample, we aim to extract 2-dimensional maps of the flux, velocity and velocity dispersion.
-These properties are extracted via modelling of the ionised gas emission line profiles at each spaxel, with a set of acceptance criteria to determine whether the fit quality is high enough to allow the inferred properties into the final 2D maps.
-We concentrate solely on the [OIII5007] emission line which always has S/N higher than both [OIII4959] and H$\beta$, and therefore provides a tighter set of model constraints over a wider portion of the physical extent of each galaxy.
-As a result, any reference to OIII emission points specifically to the [OIII5007] line unless otherwise stated.
-
-We start by considering each 0.1$^{\prime\prime}$ spaxel across a datacube in turn, and locate the wavelength of the redshifted OIII centre, $\lambda_{obs_{5007}}$, using either the literature redshift value, or the redshift determined from fitting the OIII line in the integrated galaxy spectrum.
-We have found that the thermal background is often undersubtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
+These properties are extracted via modelling of the ionised gas emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
+We concentrate solely on the [OIII]$\lambda$5007 emission line which always has S/N higher than both [OIII]$\lambda$4959 and H$\beta$ and typically extends over a larger area of each IFU.
+Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn, within which we locate the systemic wavelength of the redshifted [OIII]$\lambda$5007 centre, $\lambda_{obs_{5007}}$, using the redshift value determined from fitting the [OIII]$\lambda$5007 line in the integrated galaxy spectrum.
+We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
 To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux, and then subtracted from each spaxel in turn.
 This assumes that there is no spatial variation in the required correction, which we have found to be valid for our current sample of galaxies.
-A benefit of this polymonial subtraction is that the object continuum is subtracted simultaneously, and so the subsequent fitting of emission lines is performed relative to zero flux. 
-During the fit, regions of the spectrum known to contain strong sky emission are masked.
-Following the subtraction of excess thermal noise and continuum emission, we search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
+
+Following the subtraction of excess thermal noise, we search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
 This truncated spectrum is then used in the fitting procedure for each spaxel.
 The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by poor subtraction of the sky emission lines.
-A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the fitted parameters flux,$F_{g}$, central wavelength, $\lambda_{g}$ and standard deviation, $\sigma_{g}$.
-These parameters, along with the estimate of the noise in the datacube are used to assess whether the fitting of the OIII line is acceptable or not. 
+A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the fitted parameters flux,$F_{g}$, central wavelength, $\lambda_{g}$, and standard deviation, $\sigma_{g}$.
+These parameters, along with the estimate of the noise in the datacube, are used to assess whether the fitting of the [OIII]$\lambda$5007 line is acceptable or not. 
 The noise in the cube is estimated in two different ways. 
-First, we take the root of the sum of the squares of the flux values in the noise cube over the same extraction region defined for the data cube.
-The noise cube is produced as part of the reduction process, taking into account instrumental effects and the noise reduction due to stacking many individual exposures.
-This is summarised by Equation~\ref{eq:cube_noise}, where $\sigma _{i}$ are the individual flux points in the noise cube and $N_{c}$ denotes noise estimated from the noise cube.
+First, we take the root of the sum of the squares of the flux values in the noisecube in the same spaxel and across the same extraction region as is being considered in the datacube.
+The noisecube is produced as part of the reduction process, taking into account instrumental effects and the $\sqrt{N}$ noise reduction resulting from stacking many individual exposures.
+This is summarised by Equation~\ref{eq:cube_noise}, where $\sigma _{i}$ are the individual flux points in the noisecube and $N_{c}$ denotes noise estimated from the noisecube.
 
@@
 
-In the second method the datacube itself is used to estimate the noise.
-Again, all spaxels containing object flux are masked and the sum of the squares of the flux values in the extaction region is computed for all remaining spaxels inwards of 3 spaxels from the cube border.
-This last constraint is to mitigate edge effects, where the noise increases due to fewer individual exposures constituting the final stack in these regions.
+The second method uses the datacube to estimate the noise.
+All spaxels containing object flux are masked and the sum of the squares of the flux values in the spectral extraction region is computed for all remaining spaxels inwards of 3 spaxels from the cube border.
+This border constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
 The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation~\ref{eq:mask_noise} where $F_{i}$ are the flux values across the extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
 Both noise estimates are quantitatively similar and the conclusions of the following analysis are not dependent on the choice.
-As default we use the noise estimate from masking throughout the rest of the section.
+As default we use the noise estimate from masking within the datacube to compute the S/N acceptance criteria within each spaxel.
 
@@
 
-The criteria for accepting the fit within a given spaxel are as follows.
-1) The uncertainties on the parameters of the gaussian fit must not exceed 30\%
-2) The ratio of the flux recovered from the gaussian fit to the OIII line to the sum of the fluxes within the extraction region must exceed 1.3 or drop below 0.7.
-This helps to minimise the number of spaxels erroneously accepted due to fitting of non-gaussian profiles.
-We found this was an important criterion for `cleaning up' accepted spaxels in the 2D maps which are clearly independent of the main body of the galaxy.
-3) The measured S/N must exceed three.
+The criteria for accepting the fit within a given spaxel are as follows:
+
+\begin{enumerate}
+\item The uncertainties on any of the parameters of the gaussian fit must not exceed 30\%
+\item We must have $ 0.7 < \frac{F_{gauss}}{S} < 1.3 $, where $F_{gauss}$ is the flux from the gaussian fit to the [OIII]$\lambda$5007 line and S is the signal from \ref{eq:signal}.
+This criterion minimises the number of spaxels erroneously accepted due to the fitting of non-gaussian profiles and is important for `cleaning up' accepted spaxels in the 2D maps which are clearly independent of the main body of the galaxy.
+\item $\frac{S}{N} > 3$
+\end{enumerate}
+
 If all three criteria are satisfied, the spaxel is accepted and the gaussian fit is repeated 1000 times with each flux value in the extraction region perturbed by the datacube flux error.
@@
 \begin{equation}\label{eq:velocity_comp}
-   v_{obs} = \frac{\lambda_{c} - (1 + z)\lambda_{OIII}}{(1 + z)\lambda_{OIII}} \times c
+   v_{obs} = \frac{\lambda_{g} - (1 + z)\lambda_{5007}}{(1 + z)\lambda_{5007}} \times c
 \end{equation}
@@
 \begin{equation}\label{eq:dispersion_comp}
-   \sigma_{obs} = \frac{\sigma_{g}}{(1 + z)\lambda_{OIII}} \times c
+   \sigma_{obs} = \frac{\sigma_{g}}{(1 + z)\lambda_{5007}} \times c
 \end{equation}
 
-If a spaxel does not meet the criteria we bin with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
-This is done by median stacking the extraction region spectra in each of the neighbouring spaxels.
+If a spaxel does not meet the criteria we follow the procedure described in \cite{Stott2016} and bin with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
+This is carried out by median stacking the extraction region spectra in each of the neighbouring spaxels.
 The criteria are then re-examined and if satisfied the Monte-Carlo procedure is carried out. 
@@
 
-The process is automated and applied to each of the KDS galaxies.
-We find 54 galaxies with spatially resolved OIII emission, with this defined as being those where the spatial extent of the OIII is equivalent to or greater than the seeing disk, and the distribution of these galaxies across the pointings is shown in Table \ref{tab:pointings}.
+The process is automated and applied to each of the KDS galaxies that have an [OIII]$\lambda$5007 detection across the face of the cube.
+Following the fitting procedure we decide whether the galaxy has spatially resolved [OIII]$\lambda$5007 emission or not, with this defined as being those galaxies where the spatial extent of the accepted spaxels in the [OIII]$\lambda$5007 flux map is equivalent to or greater than the seeing disk.
+For each pointing, this number is added to table \ref{tab:pointings}.
+We do not analyse further the galaxies which are not spatially resolved, due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
+The physical properties of all spatially resolved galaxies in both GOODS-S and SSA22 are listed in table \ref{tab:phys-props}.
+
+\begin{table*}
+\centering
+\begin{threeparttable}
+\caption{Physical properties}
+\label{tab:phys-props}
+\begin{tabular}{ccccccccccc}
+
+ \hline
+ID              & RA       & Dec       & z     & k     & M$_{\star}$ & SFR$_{SED}$ & $\frac{b}{a}$ & i$^{\circ}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(Kpc) \\
+ \hline
+ GOODS-S & & & & & & & & & & \\
+ \hline
+bs009818        & 03:32:20 & -27:53:01 & 3.706        & 24.18  & 9.79  & 33.0 & 0.8         & 37.0        & 148.0   & 1.24      \\
+bs014828        & 03:32:27 & -27:52:26 & 3.562        & 23.58  & 10.15 & 30.0 & 0.31        & 76.0        & 63.0    & 1.61      \\
+lbg\_20         & 03:32:41 & -27:52:21 & 3.225        & 24.97  & 9.61  & 4.7  & 0.64        & 52.0        & 1.0     & 1.28      \\
+lbg\_105        & 03:32:24 & -27:52:16 & 3.092      & 23.79  & 9.79  & 30.0 & 0.56        & 57.0        & 128.0   & 1.72      \\
+bs006541        & 03:32:15 & -27:52:05 & 3.475       & 23.44  & 10.19 & 18.0 & 0.44        & 66.0        & 168.0   & 1.83      \\
+b012141\_012208 & 03:32:23 & -27:51:57 & 3.471        & 24.12  & 10.16 & 59.0 & 0.36        & 72.0        & 9.0     & 1.57      \\
+b15573          & 03:32:28 & -27:51:00 & 3.583        & 23.6   & 10.37 & 27.0 & 0.28        & 78.0        & 146.0   & 0.52      \\
+bs008543        & 03:32:18 & -27:50:50 & 3.474        & 22.73  & 10.67 & 42.0 & 0.5         & 61.0        & 67.0    & 1.59      \\
+bs006516        & 03:32:15 & -27:50:46 & 3.215        & 23.94  & 9.85  & 14.0 & 0.5         & 61.0        & 146.0   & 1.91      \\
+bs016759        & 03:32:29 & -27:48:53 & 3.602       & 23.85  & 9.99  & 8.8  & 0.65        & 50.0        & 49.0    & 0.87      \\
+lbg\_111        & 03:32:42 & -27:45:52 & 3.609       & 24.01  & 9.74  & 27.0 & 0.74        & 42.0        & 80.0    & 0.64      \\
+lbg\_38         & 03:32:22 & -27:44:38 & 3.488       & 24.58  & 10.03 & 7.5  & 0.58        & 56.0        & 137.0   & 0.92      \\
+lbg\_94         & 03:32:29 & -27:44:12 & 3.367       & 24.54  & 10.01 & 8.1  & 0.22        & 84.0        & 81.0    & 1.16      \\
+lbg\_109        & 03:32:21 & -27:43:46 & 3.600       & 24.63  & 9.73  & 9.4  & 0.6         & 54.0        & 119.0   & 1.98      \\
+lbg\_24         & 03:32:40 & -27:39:57 & 3.279       & 24.67  & 9.71  & 5.9  & 0.53        & 60.0        & 34.0    & 1.27      \\
+lbg\_25         & 03:32:29 & -27:40:22 & 3.322        & 24.95  & 9.44  & 5.8  & 0.3         & 76.0        & 78.0    & 1.18      \\
+lbg\_32         & 03:32:34 & -27:41:24 & 3.417      & 23.84  & 10.17 & 52.0 & 0.6         & 54.0        & 40.0    & 1.88      \\
+lbg\_113        & 03:32:36 & -27:41:50 & 3.622      & 24.01  & 9.83  & 41.0 & 0.52        & 60.0        & 15.0    & 0.87      \\
+lbg\_91         & 03:32:27 & -27:41:52 & 3.170       & 24.65  & 9.8   & 5.7  & 0.58        & 56.0        & 79.0    & 0.89 \\
+ \hline
+ SSA22 & & & & & & & & & & \\
+ \hline
+n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.9637 & 9.94  & -            & 0.71        & 46.0        & 94.0    & 0.56      \\
+s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.4618 & 9.88  & -            & 0.39        & 70.0        & 125.0   & 1.78      \\
+n3\_009       & 22:17:28 & +00:12:12 & 3.069 & 99.0    & 8.72  & -            & 0.75        & 42.0        & 84.0    & 1.06      \\
+s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.9103 & 9.74  & -            & 0.57        & 57.0        & 76.0    & 1.59      \\
+lab7\_top     & 22:17:41 & +00:11:28 & 3.095      & 23.8919 & 9.89  & -            & 0.51        & 61.0        & 139.0   & 1.47 \\
+s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.2538 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
+lab18         & 22:17:29 & +00:07:52 & 3.101           & 99.0    & 8.66  & -            & 0.85        & 32.0        & 27.0    & 0.46      \\
+$^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & 99.0    & 8.78  & -            & 0.57         & 57.3        & -    & 2.4      \\
+$^{*}$s\_sa22b-d5  & 22:17:36 & +00:06:10 & 3.175 & 23.7182 & 10.32 & -            & 0.57         & 57.3        & -    & 2.14      \\
+$^{*}$s\_sa22b-md25 & 22:17:42 & +00:06:20 & 3.304     & 24.6174 & 9.05  & -            & 0.57         & 57.3        & -    & 2.14      \\
+$^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.9847 & 10.64 & 50.0 & 0.57         & 57.3        & -    & 2.14
+
+\end{tabular}
+\begin{tablenotes}
+      \small
+      \item $^{*}$ No HST coverage: $PA_{morph}$ unconstrained; $\frac{b}{a}$ and $R_{1/2}$ estimated as derived throughout the text.
+    \end{tablenotes}
+  \end{threeparttable}
+  \end{table*}
 
 \subsection{Deriving Morphological Properties}
-For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from the available high resolution photometry.
-The first of these properties is the galactic axis ratio, $A_{r}$.
-As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a} \equiv A_{r}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $\alpha$ is the axial ratio of an edge-on system, and so is dependent upon an assumption about the `disk thickness'.
+For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from HST high resolution photometry where available.
+This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies but also to help distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
+In the following section we describe the approach we have chosen to recover these parameters.
+
+\subsubsection{Applying GALFIT to the imaging data}\label{subsubsec:galfitting}
+We use GALFIT \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the system PSF, to the observed HST images in both GOODS-S and SSA22 in a consistent way.
+The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z \sim 3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\tiny{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}}.
+For SSA22 we make use of archival HST imaging\footnote{\tiny{\url{https://archive.stsci.edu/hst/search.php}}} data in the WFC3 F160W band (P.I.
+Lehmer: PID 13844, P.I.
+Mannucci: PID 11735) and the ACS F814W band, tracing $\sim$ 2000$\AA$ light at $z\sim 3.5$ (P.I.
+Chapman: PID 10405, P.I.
+Abraham: PID 9760, P.I.
+Siana: PID 12527).
+The HST coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is incomplete, and so we must resort to the bluer ACS F814W data which traces younger stellar populations and may not be sensitive to the majority of the mass distribution within these galaxies.
+Both of these limitations translate to larger systematic uncertainties in the morphological parameters derived in the SSA22 pointings.
+
+We first run SExtractor \citep{Bertin1996} across the full fields to recover initial input parameters and segmentation maps for running GALFIT, and then extract postage stamp regions around the galaxies in the KDS sample.
+At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles with the \Sers index n fixed to the exponential disk value of 1.
+During the fitting process all other morphological parameters, including $R_{1/2}$, (xcen,ycen), PA and inclination, are free to vary.
+This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, n = 4 models and bulge/disk models with both an n=1 and n=4 component following the procedure described in \cite{Bruce2012}.
+We find that the $\chi^{2}$ of the fixed n = 1 fit is quantitatively similar in most cases and we also find good agreement between the morphological parameters reported in the \cite{VanderWel2012} structural properties catalogue.
+The use of exponential profiles also facilitates comparison with recent results from the KROSS survey \citep{Harrison2017} in which beam smearing correction factors are applied to the derived kinematic parameters as function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:param_extraction}).
+In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012}, which has been shown to produce more reliable results than either the Tiny Tim model or an empirical stack alone.
+In the F814W band we use the pure Tiny Tim i-band model.
+
+This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{sec:Kinematic_Properties}, namely the axis ratio $A_{r}$, half-light radius $R_{1/2}$ and the $PA_{morph}$ $PA_{morph}$.
+We used the derived $A_{r}$ values to determine galaxy inclination angles.
+As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a} \equiv A_{r}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
+To derive the inclination, we must select a value for $q_{0}$, and following the discussion in \citep{Law2012a} we choose a value appropriate for thick disks, $q_{0} = 0.2$ (e.g.
+\cite{Epinat2012,Harrison2017}).
+However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values.
 
 \begin{equation}\label{eq:holmberg_i}
-   cos^{2}i = \frac{\left(\frac{b}{a}\right)^{2} - \alpha^{2}}{1 - \alpha^{2}}
+   cos^{2}i = \frac{\left(\frac{b}{a}\right)^{2} - q_{0}^{2}}{1 - q_{0}^{2}}
 \end{equation}
 
-A value for this parameter can be constrained by looking at the distribution of derived axis ratios, which for a draw from disk galaxies randomly orientated on the sky should be flat \citep{Sandage1970}.
-The value of $A_{r}$, then, at which this cuts off can be thought of a population disk thickness and used universally (ignoring variation in disk thickness throughout the sample).
-The inclination angle calculated for each galaxy can be used to correct the observed velocity field to the intrinsic, with this correction factor becoming larger as the galaxy becomes more `face-on'.
-The second important morphological parameter is the Position Angle (PA), which is the direction of the photometric major axis of the galaxy on the sky.
-This would be expected to coincide with the kinematic axis in the case of a rotating disk galaxy.
-The discrepancy between morphologial and kinematic position angles is an important indicator of sub-structure in the morphology \citep{Queyrel2012,Wisnioski2015}.
-These values are expected to agree, particularly for low axial ratios, and deviations can indicate clumps or mergers, which may influence the underlying kinematics. 
-However for compact, unresolved morphologies there are cases where there is simply not enough information to predict the axis along which velocity gradient will be maximised.
+The inclination angle calculated for each galaxy is used to correct the observed velocity field, which is the line of sight component of the intrinsic velocity field, with the correction factor increasing with increasing $A_{r}$.
 
-The third essential morphological parameter we will use is the half-light radius, $r_{H}$, as this provides a way to extract circular velocities at some fiducial distance from the centre of the galaxy.
-As discussed throughout the introduction, there is no universal definition of what the circular velocity is, and so to compare with previous work it is necessary to extract values consistently from the derived rotation curves.
-Connected to this is the issue of extrapolating model rotation curves or two-dimensional rotation maps beyond the last measured datapoints, which may not extend to the rotation curve plateau due to poor S/N in this regions.
-Knowledge of the $r_{H}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made.
-Second, since beam smearing affects all of these measurements and tends to flatten velocity gradients, `Durham' (REFERENCE PROPERLY) have invested time into modelling the extent to which this can be corrected.
-The correction is a function of the ratio between $r_{H}$ and PSF size as shown in Figure DURHAM, and so accurately measuring the effective radius of a galaxy vindicates the use of this curve to recover intrinsic circular velocities.
+The second GALFIT parameter is $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
+This is expected to coincide with the kinematic position axis, $PA_{kin}$, in the case of a rotating disk galaxy, where the stars and the gas are both rotating around the centre of the gravitational potential well.
+Discrepancy between $PA_{morph}$ and $PA_{kin}$ is an important indicator of sub-structure in the morphology \citep{Queyrel2012,Wisnioski2015,Rodrigues2016}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
+The discrepancy, often labelled $Delta PA \equiv |PA_{morph} - PA_{kin}|$, is a function of $A_{r}$, as it becomes increasingly difficult to accurately measure $PA_{morph}$ for very inclined galaxies \citep[e.g.]{Wisnioski2015,Harrison2017}.
+We have visually inspected each of the GALFIT maps to check that the derived $PA_{morph}$ follows the galaxy light distribution, and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class}).
 
-We use the longest wavelength, highest resolution imaging for the fitting of morphological parameters, which in this case is HST F160W band, and opt to use GALFIT \citep{Peng2010_galfit} to recover the parameters as described in section \ref{subsubsec:galfitting}.
+The third morphological parameter is the half-light radius, $R_{1/2}$, which provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
+As discussed throughout the introduction and in \cref{subsubsec:param_extraction}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
+Connected to this is the issue of extrapolating model rotation curves or two-dimensional rotation maps beyond the last measured datapoints, which may not extend to the rotation curve plateau due to poor S/N in these regions.
+Knowledge of $R_{1/2}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made.
+Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d modelling}), which requires knowledge of the $R_{1/2}$ value for each galaxy.
+A final use of the derived $R_{1/2}$ values is to verify our beam smearing correction results through comparison with systematic correction factors presented in Johnson et al.
+(in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:param_extraction}).
+As a result of choosing consistent $V_{C}$ extraction radii and beam smearing analysis methods, we may ultimately compare the KDS sample consistently with the large KROSS sample results at $z \sim 0.9$ described in \citep{Harrison2017}.
 
-\subsubsection{Applying GALFIT to the imaging data}\label{subsubsec:galfitting}
-We use GALFIT to fit 2-D analytic functions, convolved with the system PSF, to the observed HST F160W images in both GOODS-S and SSA22 in a consistent way.
-The adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012}.
-The full procedure involves fitting \citep{Bertin1996}
+The errorbars produced by GALFIT are purely statistical and are determined from the covariance matrix used in the fitting, and this results in unrealistically small uncertainties in the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
+\cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in CANDELS, reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
+We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ recovered from extracting at $R_{1/2}$ and the errors on the intrinsic velocity dispersion, $\sigma_{int}$, the derivation of which requires knowledge of $R_{1/2}$ (\cref{subsec:3d modelling}) are dominated by measurement errors and uncertainties connected with assumptions about the velocity dispersion distribution in high redshift galaxies (see \cref{app:kin_error_estimates}).
 
-INCLUDE TABLE OF THE GALFIT outputs
-HST vs. TENIS imaging of the same galaxies to confirm whether it is okay to report the physical properties of a sample taken from the ground and then GALFIT.
+For the inclination error we adopt a conservative nominal uncertainty of 10$\%$ also, i.e.
+$\Delta i = i / 10$, after examining the typical magnitude of the uncertainties reported following the Monte Carlo procedure described in \cite{Epinat2012}.
+We also note that generally this inclination uncertainty is a function of the recovered axis ratio, since it is more difficult to determine the inclination when the galaxy is more `face-on', but detailed inclination angle uncertainty modelling is beyond the scope of this paper.
+$PA_{morph}$ is well constrained by the fits at small axis ratios, but becomes increasingly uncertain as the galaxy morphology becomes closer to spherical.
+In Figure \ref{fig:delta_pa} we draw attention to this by showing the absolute difference between morphological and kinematic position angles, $\Delta PA$, plotted against the galfit determined axis ratio, with binned median and standard deviation also shown.
+We note that typically the $PA_{morph}$ uncertainties are large in the regime of high axis ratios, but make no attempt to quote a formal uncertainty on this parameter.
 
-\subsection{Dynamical Modelling}
-Constructing model 2D velocity fields and fitting these to the observed data is a powerful tool for determining the set of parameters which best describe the dynamical state of that galaxy.
-HERE IS WHERE TO MENTION SURVEYS WHICH HAVE DONE THIS IN THE PAST.
+In SSA22, 4/21 of the spatially resolved galaxies do not have any HST coverage.
+For these galaxies the inclination angle is set to the theoretical mean of 57.3$^{\circ}$, calculated for a population of galaxies with randomly drawn viewing angles (see e.g.
+the appendix in \cite{Law2009}), we fix $PA_{morph}$ equal to $PA_{kin}$ for the analysis described in \cref{subsec:3d modelling} and fix the $R_{1/2}$ value for these galaxies equal to FWHM$_{obs}$/2.
+These assumptions are based purely on statistical considerations, and the errorbars on the derived quantities for these galaxies are consequently larger.
+Owing to the small number of galaxies without HST imaging, we do not expect this to impact the bulk dynamical properties of the KDS sample.
 
-\subsection{Beam Smearing Correction}
+\begin{figure*}
+    \centering \hspace{-2.0cm}
+    \begin{subfigure}[h!]{0.50\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{axis_ratio_distributions.png}
+        %\caption{axis ratio distributions}
+    \end{subfigure} \hspace{0.4cm}
+    \begin{subfigure}[h!]{0.50\textwidth}
+        \centering
+        \includegraphics[height=3.6in]{size_distributions.png}
+        %\caption{size distributions}
+    \end{subfigure}
+    \caption{We crossmatch publicly available spectroscopic redshifts for SFGs, as discussed in the text, with the morphological catalogue presented in VDW12 in two different redshift slices.
+    This provides a set of reference morphological properties for typical SFGs at different evolutionary stages to which the derived KDS values can be compared.
+    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ parameter, which could partially be explained by the F160W filter tracing a younger stellar population at $z\sim3.5$.
+    The distribution of KDS $R_{1/2}$ values are consistent with those in the higher redshift reference sample.
+    The $A_{r}$ distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < A_{r} < 0.9$.
+    This shows that we have not been biased towards deriving low or high $A_{r}$ values.}
+    \label{fig:morpho-distributions}
+\end{figure*}
 
-\subsection{Sample Statistics}
+In Figure \ref{fig:morpho-distributions} we plot the distributions of the derived morphological properties (for only the KDS galaxies with HST coverage) in comparison to those determined in \cite{VanderWel2012} (VDW12) at low and high redshift.
+At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with the morphological catalogue of \cite{VanderWel2012}.
+This allows us to look at the bulk morphological properties of the SFG population in the two redshift slices in comparison with those determined for the KDS sample.
+The derived KDS $R_{1/2}$ distribution at $z \sim 3.5$ is similar to the wider sample distribution at $3 < z  < 4$, i.e.
+compact when compared to galaxies at lower redshifts and the KDS $A_{r}$ are consistent with being generally uniform between $0.3 < A_{r} < 0.9$, with the peak at $A_{r} = 0.6$ corresponding to i = 55$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$, which is close to the statistical mean for a random galaxy sample.
+This reassures us that we are not biased towards deriving either particularly low or particularly high inclination angles.
 
-Fig.~\ref{fig:distributions}, Table~\ref{tab:KDS}.
+\subsubsection{Morpho-Kinematic Classification}\label{subsec:morpho-kin-class}
+% chancing my luck a bit here with this paragraph
+Classification into different kinematic categories at $z \sim 3.5$ is necessary for quantifying the fraction of KDS galaxies which are isolated `rotation dominated' with $V_{C}/\sigma_{int} > 1$, isolated `dispersion dominated' with $V_{C}/\sigma_{int} < 1$ and the fraction taking part in interactions with other galaxies.
+In the local universe, main sequence galaxies are completely dominated by rotational motions, with the ratio of $V_{C}/\sigma_{int} \sim 10$ or higher \citep{Epinat2008,Epinat2008a}, with this ratio observed to decline over time as random motions increase \citep[e.g.][]{ForsterSchreiber2009,Law2009,Epinat2012,Wisnioski2015,Stott2016}.
+By studying the Rotation Dominated Fraction (RDF) of KDS galaxies, and the mean value of the ratio $V_{C}/\sigma_{int}$ we hope to gain an understanding of balance of gravitational support provided by rotational and random motions.
+$V_{C}$ and $\sigma_{int}$ are both outputs of the dynamical model, so we describe here a pre-modelling morpho-kinematic classification for all KDS galaxies which are spatially resolved in the [OIII]$\lambda$5007 emission line, to inform us which galaxies it is appropriate to attempt dynamical modelling.
 
-\section{ANALYSIS \& RESULTS}\label{sec:results}
+Previous studies have kinematically classified their sample in various ways; The SINS sample uses a Kinemetry approach described for \citep{Shapiro2008,ForsterSchreiber2009,Cresci2009} which quantifies asymmetries in both the velocity and velocity dispersion maps to empirically differentiate between rotating and non-rotating systems.
+In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, with the authors also commenting that the S/N of the data is not sufficient to accurately determine the required kinemetry parameters.
+In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $PA_{kin}$ and $PA_{morph}$ misalignment (i.e.$\Delta PA$) and the degree of rotational support as quantified with $V_{C}/\sigma_{int}$.
+In \cite{Wisnioski2015} a set of 5 criteria are described in their section 4 which assess the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, $\Delta PA$ and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
+
+In this work we are in a similar S/N and redshift regime as \cite{Gnerucci2011} and so we aim to keep the pre-modelling classification criteria simple.
+This involves a joint visual inspection of the velocity fields and associated HST imaging for all spatially resolved KDS galaxies.
+One benefit of studying the high resolution imaging in tandem is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
+These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam smearing or in regions spatially offset from the centre of the galaxy.
+A second benefit is to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective, but are clearly two or more potentially interacting components at slightly different redshift as revealed by higher resolution HST photometry.
+It is difficult to distinguish in some cases between two HST components rotating together in a single disk (i.e.
+clumpy disk galaxies \citep[e.g.][]{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [OIII]$\lambda$5007 emitting blobs which are offset along the line of sight.
+Perhaps the most telling diagnostic is a double peak in the object spectrum at the kinematic centre, which allows for the classification of IFU data with 2 HST flux peaks as mergers.
+
+In 4/23 of the resolved GOODS-S galaxies (one count per merger, 2 mergers in each of the GOODS-S pointings) we clearly identify signs of multiple components or merging in the HST high-resolution imaging.
+In 9/20 of the resolved SSA22 galaxies we identify clear mergers from the HST imaging, noting that 8 of these are in SSA22-a (80$\%$ of the spatially resolved sample in that pointing, although potentially higher as one of the galaxies is without HST coverage), which is the pointing close to the centre of the $z \sim 3.1$ proto-cluster.
+We note that the 1/11 mergers reported in SSA22-b is a lower limit, since there are 3 galaxies which do not have HST coverage in this pointing, although the pointing is spatially offset to the south of the protocluster centre in SSA22-a, and consequently is less dense.
+This observation in SSA22-a is perhaps unsurprising in such a high-density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas and the morphological evolution of these galaxies.
+The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
+We reject these merger candidates from the following dynamical analysis presented in \cref{sec:Kinematic_Properties}, keeping the KDS galaxies with HST coverage with the caveat that we do not have a clear morphological classification.
+In Appendix \cref{app:mergers} we present the HST imaging, kinematic maps and 1-dimensional kinematic extractions of the merger candidates for the KDS galaxies.
+Many of these are rotation doppelg{\"a}ngers and can be fit with the arctangent model (see \cref{subsec:3d modelling}) with a low $\chi ^{2}$ value, highlighting again the importance of the HST photometry for determining true rotation.
+
+For the spatially resolved galaxies which are not merger candidates, we extract in synthetic apertures along an axis joining the velocity extrema to search for the presence of a smooth velocity gradient indicative of rotation within a disk.
+In 1/23 and 3/20 resolved galaxies in GOODS-S and SSA22 respectively we find no such gradient, and do not attempt to fully model the kinematics of the galaxies to determine $V_{C}$ and $\sigma_{int}$.
+We assume that there is very little rotational support in these galaxies and take the $\sigma_{int}$ value as the median of the intrumental resolution corrected velocity dispersion map.
+To sumamrise, galaxies are passed to the full dynamical modelling of \cref{sec:Kinematic_Properties} if:
+\begin{itemize}
+    \item They are spatially resolved in the [OIII]$\lambda5007$ emission line
+    \item They have a clear, monotonic velocity gradient along a single kinematic axis
+    \item They are isolated as revealed by high-resolution HST imaging
+\end{itemize}
+
+The galaxies passing these criteria shall be referred to as the modelling sample throughout the remainder of the paper, and we make no further distinction between galaxies in the SSA22 and GOODS-S fields.
+It is only these galaxies for which we can measure $V_{C}$, and to which the `$V_{C}$ measured' legend titles refer throughout \ref{sec:results}.
+
+\section{KINEMATIC ANALYSIS AND EXTRACTION OF PROPERTIES}\label{sec:Kinematic_Properties}
+As mentioned in the introduction, there is no universal standard for defining $V_{C}$, particularly when it is extrapolated from the data using a fitted model, of which there are several types.
+Some authors use a physically motivated model, taking into account the potential-well of the galaxy through knowledge of the mass distribution (e.g.
+\cite{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015}).
+Another type is a phenomenological model, which assumes a fixed function known to well describe observed galactic rotation curves which flatten at large radii \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016}.
+Both of the above examples fit to 2D fields extracted from the datacubes using line-fitting software.
+Recently, algorithms such as Galpak$^{3D}$ \citep{Bouche2015} and 3D-Barolo \citep{DiTeodoro2015} have emerged, fitting directly to the flux in the datacube in order to constrain the kinematic properties.
+
+In this analysis we seek to minimise the number of fitted parameters, making use of information from HST imaging and assumed a fixed functional form as described in the following subsection.    
+One of our main concerns here is to clearly distinguish between observed velocities and those inferred from modelling.
+This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring some extrapolation to determine $V_{C}$.
+There are thus two clear reasons for constructing model velocity fields and fitting these to the KDS modelling sample galaxies; the first is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the second is to estimate the effect of beam smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
+The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.
+
+\subsection{3D Modelling}\label{subsec:3d modelling}
+By simulating a full datacube and fitting the model parameters to the data, we can measure both $V_{C}$ and $\sigma_{int}$ having removed the effects of beam smearing.
+For each galaxy in the modelling sample we construct a model datacube with the same spatial dimensions as the observed datacube, and populate each spaxel with an [OIII]$\lambda$5007 emission line that has central wavelength determined by the systemic velocity of the galaxy.
+This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model.  
+Following the procedure now of numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe:
+
+\begin{equation}\label{eq:arctangent}
+   v_{r} = \frac{2}{\pi}v_{asym}arctan\left(\frac{r}{r_{t}}\right)
+\end{equation}
+
+\noindent
+with `r' measured as the distance from the centre of rotation, (xcen, ycen).
+This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
+The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
+If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam smearing.
+The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
+In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
+The intrinsic flux profile of these simulated [OIII]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in section \cref{subsubsec:galfitting} (which assumes that the [OIII]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
+This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.
+
+This simulated intrinsic [OIII]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries with the atmospheric seeing profile determined from fitting the collapsed, stacked standard star cube in each pointing with an elliptical gaussian (the recovered seeing values are reported in table \ref{tab:pointings}).
+The velocity and velocity dispersion values are then re-measured in each spaxel to assess the impact of beam smearing.
+Convolution with the seeing profile produces a peak in the modelled velocity dispersion field at the centre of rotation and flattens the observed velocity field perpendicular to $PA_{kin}$.
+The model therefore provides a beam smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the re-measured velocity dispersion after convolution, i.e.
+$\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
+This is computed for each spaxel to provide the 2D $\sigma_{bs}$ correction map.
+The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in section \cref{subsubsec:model_errors}.
+We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce. 
+We fit the beam smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, and seek the combination of parameters which maximises the log-Likelihood function given by equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
+
+\begin{equation}\label{eq:likelihood}
+   ln\Lagr = \frac{-0.5\sum_{i=1}^{N}(d_{i} - M_{i})^{2}}{\delta_{v_{i}}^{2}} - ln\left(\frac{1}{\delta_{v_{i}}^{2}}\right)
+\end{equation}
+
+\noindent
+where $\delta_{v_{i}}$ are the observed velocity errors, $d_{i}$ are the datapoints and $M_{i}$ are the convolved model velocity values.
+In practice we fix the (xcen,ycen) parameters of the galaxy to the location of the stellar continuum, a proxy for the centre of the gravitational potential well, recovered from the collapsed KMOS cube, leaving only 3 free parameters to vary in the MCMC sampling.
+This assumes that the gas and the stars in the galaxy share a common centre of mass, an assumption which is at least verified for the vast majority of SFGs in the local and intermediate redshift universe.
+Due to the faintness of the continuum, there are several galaxies for which we cannot reliably estimate the rotation centre using this method, and instead set (xcen,ycen) to coincide with the peak [OIII]$\lambda$5007 flux location.
+For the SSA22 galaxies, using the continuum to fix the rotation centre is generally more successful, since the use of the HK filter effectively doubles the S/N of this component by collapsing over two wavebands.
+This differs from the method of fixing the rotation centre at the midpoint between the velocity extrema, described in \cite{Wisnioski2015} and \cite{Rodrigues2016}.
+In general the S/N of our sample is low at the galaxy outskirts and for many of the isolated rotating sample we don't observe the flattening of the velocity field.
+This suggests that the velocity midpoint may be biased towards the side of the galaxy which shows the higher velocity value and so we instead use the physically motivated continuum centre where possible, which also matches the approach described in \cite{Harrison2017}.
+
+The MCMC sampling provides a distribution of parameter values around those which give the maximum likelihood.
+We have confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates have converged around the 50th percentile values.
+The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in \cref{subsubsec:model_errors}.
+Following the modelling procedure, the kinematic parameters $V_{C}$ and $\sigma_{int}$ must be extracted from the 2D intrinsic fields.
+There are several choices for how this can be done, and our procedure is built around facilitating comparisons to earlier work, as described in \cref{subsubsec:param_extraction}.
+
+The best fitting smeared and intrinsic models for the modelling sample in both are plotted in \cref{app:kinematics_plots}, where the galaxies have been divided into dispersion and rotation dominated categories as determined by the ratio $V_{C}/\sigma_{int}$, described in more detail throughout \cref{subsubsec:rotation_and_mergers}.
+Overplotted onto the models are the data values and uncertainties extracted along $PA_{kin}$.
+These figures also show the HST imaging for each galaxy, the best fit galfit model and residuals, 2D maps of the [OIII]$\lambda$5007 flux, observed velocity, observed dispersion, best fitting smeared model velocity, data - model residuals, intrinsic velocity dispersion (observed dispersion corrected for beam smearing and instrumental resolution as described in \cref{subsubsec:param_extraction}) as well as a plot of 1D extractions along the observed, intrinsic and beam smeared dispersion maps.
+The galaxies classified as mergers are also plotted in \cref{app:mergers}, as well as the dispersion dominated galaxies which have not been d with the full 3D modelling in \cref{app:dispersion_dominated,app:dispersion_dominated}.
+
+\subsubsection{3D Modelling Kinematic Parameters Extraction}\label{subsubsec:param_extraction}
+The crucial information to extract for the model grids described above for each galaxy, both for this study and for comparison to previous studies, is a measure of the maximum intrinsic circular velocity, $V_{C}$, and a single measurement of the intrinsic velocity dispersion, $\sigma_{int}$, used as a diagnostic for the local random motions of the gas free from large scale velocity gradients \citep[e.g.]{ForsterSchreiber2006,Genzel2008,Gnerucci2011}.
+Previous studies have measured these quantities in several different ways, and it is important to keep this in mind when trying to establish the dynamical evolution of star forming galaxies between different slices of cosmic time.
+Here we briefly mention the measurement techniques of the major surveys we aim to make comparisons to at high redshift, as an attempt to motivate our own method of kinematic parameter extraction.
+The SINS sample \citep{ForsterSchreiber2009} is refined to a high-z robust rotating disk sample \citep{Cresci2009} using a kinemetry approach \citep{Krajnovic2006,Shapiro2008} which searches the moment maps extracted from the SINFONI datacubes for asymmetries which quantify the degree of rotational support against gravity in each galaxy.
+\cite{Cresci2009} model the robust rotators in three dimensions using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
+In this approach the $V_{C}$ value comes from the best fitting model parameter, and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
+
+\begin{equation}\label{eq:sins_sigma}
+\begin{split}
+\sigma_{01} = \sqrt{\frac{v^{2}(R)h_{z}}{R}} \quad OR \quad \sigma_{01} = \frac{v(R)h_{z}}{R} \\
+& \sigma_{int} = \sqrt{\sigma_{01}^{2} + \sigma_{02}^{2}}
+\end{split}
+\end{equation}
+
+In \cite{Law2009}, a study using OSIRIS, the `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
+
+In their survey at z $\sim 3$, closest in redshift to the current work, \cite{Gnerucci2011} et al.
+derive rotation curves and intrinsic velocity dispersions from a modelled exponential mass distribution, varying the parameters of the model to best fit the observed velocity field.
+The extracted $V_{C}$ value is then the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam smearing (see their Eq.
+8).
+
+In the MASSIV sample, \citep{Epinat2012}, spanning $0.9 < z < 1.6$, the authors use a 2D arctangent fit to the data and extract $V_{C}$ from the model at $R_{last}$, this being the radius where the S/N of the data drops below 3.
+The $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the $\sigma_{model}$ value as per \cite{Epinat2010}, which is the contribution from beam smeaing assuming the best-fitting model parameters.
+
+In KMOS$^{3D}$, covering two redshift regions at $z \sim 1.0$ and $z \sim 2.3$, \cite{Wisnioski2015} compute $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is computed from the $\sigma_{obs}$ map far away from the kinematic centre, where the effects of beam smearing should be negligible.
+In the KROSS sample at $z \sim 1$, \cite{Stott2016} also model the 2D velocity field using an arctangent function, and after finding the best fitting parameters using a genetic algorithm, extract $V_{C}$ at a fiducial radius, which they choose to be $2.2R_{d} \sim 1.3R_{1/2}$, where $R_{d}$ is the galaxy disk radius in the case of an exponential light profile.
+The $\sigma_{int}$ value is computed in two different ways; the first facilitates comparison with KMOS$^{3D}$ results by extracting the instrumental resolution corrected $\sigma_{obs}$ far away from the kinematic centre; the second uses Equation \ref{eq:stott_sigma} to first linearly remove the effects of the local beam smeared velocity gradients, and then correct for instrumental resolution in quadrature (an approach which they verify in their Appendix A).
+
+\begin{equation}\label{eq:stott_sigma}
+   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \frac{\Delta V}{\Delta R}\right)^{2} - \sigma_{inst}^{2}}
+\end{equation}
+
+The derived median $\sigma_{int}$ from these two approaches varies considerably, as highlighted in Figure 8 of their paper.
+
+In the most recent KROSS paper, \citep{Harrison2017}, exponential disk models, \cite{Freeman1970}, are fit to the data extracted along $PA_{kin}$ in 1D to facilitate extraction of the observed velocity at $2R_{1/2}$ (where $2R_{1/2} \sim 3.4R_{d}$).
+The $\sigma_{int_{obs}}$ is also extracted at $2R_{1/2}$ when the data extend to this radius, and when they do not $\sigma_{int_{obs}}$ is taken to be the median of the $\sigma_{obs}$ map.
+Using a suite of mock KMOS data with exponential intrinsic flux distributions and $PA_{morph}$ coincident with $PA_{kin}$s, convolved with various atmospheric seeing profiles, beam smearing correction factors are derived as a function of both the velocity gradient and the ratio $R_{d}/R_{PSF}$ Johnson et al.
+in prep.
+This correction factors are applied to compute $V_{C}$, with a median correction factor of 1.2 at $3.4R_{1/2}$.
+The same treatment is applied to the outer $\sigma_{int_{obs}}$ values, with a median correction factor of 0.97, and when unavailable a seperate correction factor is applied to the median of the $\sigma_{obs}$ map with a median value of 0.8 (see also \citep{Burkert2016a} for similar simulations of mock data and derivations of beam smearing correction factors).
+
+Clearly there are many different approaches for computing the same intrinsic kinematic parameters which we hope to compare across cosmic time intervals, but despite the diversity over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam smearing using similar approaches.
+This trend towards consistency is encouraging, and as described in \cref{subsec:3d modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam smearing effects quantified in the modelling.
+Our small sample size has allowed us to compute beam smeared models, and the corresponding intrinsic models, for each galaxy.
+Following the approach of \cite{Harrison2017}, we extract $V_{C}$ at $2R_{1/2}$ to allow for a robust comparison to the large KROSS sample at $z\sim0.9$, and also note that due to the flattening of the intrinsic velocity model at small radii, the velocity value extracted at $1.3R_{1/2}$ does not differ by a large amount.
+To extract the velocity from the intrinsic model we first convolve the measured $R_{1/2}$ values with the PSF of the KMOS observations and read off at $2R_{1/2}$ to give $V_{C}$.
+This $V_{C}$ value is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
+
+To measure the $\sigma_{int}$ value for each galaxy in our sample we first use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{bs}$ is the value detailed in \cref{subsec:3d modelling} and $\sigma_{inst}$ is a measure of the instrumental broadening value averaged across gaussian fits to several skylines.
+This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam smearing correction best recovers the $\sigma_{int}$ values.
+
+\begin{equation}\label{eq:owen_sigma}
+   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{bs} \right)^{2} - \sigma_{inst}^{2}}
+\end{equation}
+
+We then take the median value of this map as the single $\sigma_{int}$ value for that galaxy.
+
+To test the robustness of our modelling approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors detailed in Johnson et al.
+(in prep) and used to evaluate the final kinematic parameters in \cite{Harrison2017}.
+These are in very good agreement within the errorbars, confirming that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.
+The errors on the extracted kinematic parameters are discussed in \cref{subsubsec:model_errors}.
+
+In all of the modelled galaxies in GOODS-S, the $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, with 2 galaxies requiring extrapolation > 0.4$^{\prime\prime}$ with a mean extrapolation of 0.24$^{\prime\prime}$.
+In SSA22, probably as a result of the slightly poorer seeing conditions, only one galaxy requires extrapolation beyond 0.2$^{\prime\prime}$ of the last data radius and the mean extrapolation is 0.12$^{\prime\prime}$.
+This extrapolation is a requirement imposed by the low S/N at the outskirts of the KDS galaxies, limiting the extent to which the ionised gas disk can be observed, with the majority of the observed velocity curves not reaching the point of flattening.
+The extent of the extrapolation for each galaxy is made clear throughout the figures in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radius marked on each velocity thumbnail.
+We present the maximum observed velocity values, $V_{obs}$, and the intrinsic, inclination and beam smearing corrected model velocity values, $V_{C}$, in table \ref{tab:kin_props}.
+
+\begin{table*}
+\centering
+\caption{Dynamical Properties}
+\label{tab:kin_props}
+\begin{tabular}{cccccccccccc}
+
+ \hline
+ID & $V_{obs}$ & $V_{C}$ & $\sigma_{obs}$ & $\sigma_{int}$ & $V_{C}/\sigma_{int}$ & M$_{dyn}$  & $R_{last}$ & 2$R_{1/2}$ & PA$_{kin}$ & $\Delta PA$ & s$_{0.5}$\\
+ \hline
+ GOODS-S & & & & & & & & & & & \\
+ \hline
+bs009818        & 65.0                    & 84.0                     & 95.0                  & 79.0                   & 1.06           & 9.62      & 2.2        & 2.5        & 72.0    & 75.0      & 100 \\
+bs014828        & 32.0                    & 46.0                     & 97.0                  & 88.0                   & 0.53           & 9.22      & 3.1      & 3.3      & 44.0    & 19.0      & 94 \\
+lbg\_20         & 26.0                    & 56.0                     & 55.0                  & 40.0                   & 1.39           & 9.29      & 2.3      & 2.6        & 41.0    & 40.0      & 57 \\
+lbg\_105        & 13.0                    & 32.0                     & 68.0                  & 59.0                   & 0.54           & 8.92      & 2.3      & 3.5       & 170.0   & 42.0      & 64 \\
+bs006541        & 36.0                    & 65.0                     & 96.0                  & 83.0                   & 0.78           & 9.56      & 4.5      & 3.7       & 23.0    & 35.0      & 96 \\
+b012141\_012208 & 34.0                    & 93.0                     & 94.0                  & 63.0                   & 1.47           & 9.81      & 1.4      & 3.2       & 122.0   & 66.0      & 92 \\
+b15573          & 62.0                    & 81.0                     & 111.0                 & 84.0                   & 0.97           & 9.21      & 3.1      & 1.0       & 118.0   & 28.0      & 102 \\
+bs008543        & 77.0                    & 111.0                    & 98.0                  & 71.0                   & 1.56           & 9.97      & 4.5      & 3.2       & 114.0   & 47.0      & 106 \\
+bs006516        & 56.0                    & 61.0                     & 64.0                  & 45.0                   & 1.35           & 9.54      & 4.6      & 3.9       & 144.0   & 1.0       & 63 \\
+bs016759        & 71.0                    & 110.0                    & 82.0                  & 57.0                   & 1.93           & 9.7       & 2.7      & 1.8       & 75.0    & 26.0      & 97  \\
+lbg\_111        & 53.0                    & 58.0                     & 90.0                  & 81.0                   & 0.71           & 9.01      & 3.1      & 1.3        & 168.0   & 87.0      & 91 \\
+lbg\_38         & 31.0                    & 97.0                     & 76.0                  & 53.0                   & 1.82           & 9.62      & 1.8      & 1.9       & 47.0    & 89.0      & 87 \\
+lbg\_94         & 18.0                    & 34.0                     & 65.0                  & 55.0                   & 0.62           & 8.82      & 2.7      & 2.4       & 41.0    & 39.0      & 61 \\
+lbg\_109        & 32.0                    & 53.0                     & 101.0                 & 91.0                   & 0.58           & 9.42      & 3.1      & 4.0        & 157.0   & 38.0      & 99 \\
+lbg\_24         & 30.0                    & 42.0                     & 64.0                  & 51.0                   & 0.82           & 9.03      & 4.6       & 2.6       & 64.0    & 30.0      & 59 \\
+lbg\_25         & 14.0                    & 33.0                     & 53.0                  & 41.0                   & 0.8            & 8.79      & 2.7      & 2.4        & 87.0    & 8.0       & 48 \\
+lbg\_32         & 79.0                    & 121.0                    & 104.0                 & 76.0                   & 1.58           & 10.12     & 2.3      & 3.8       & 11.0    & 29.0      & 116 \\
+lbg\_91         & 58.0                    & 91.0                     & 98.0                  & 71.0                   & 1.28           & 9.54      & 2.3      & 1.8        & 40.0    & 38.0      & 96 \\
+lbg\_113        & 0.0                    & 0.0                      & 116.0                 & 112.0                  & 0.0            & - & 2.7      & 1.8       & 28.0    & 12.0      & 112 \\
+ \hline
+ \hline
+ SSA22 & & & & & & & & & & & \\
+ \hline
+ \hline
+lab25         & 42.0                    & 48.0                     & 80.0                  & 49.0                   & 0.98           & 9.27      & 3.8      & 3.37       & 72.0    & 5.0       & 60 \\
+n\_c3         & 0.0                    & 0.0                      & 96.0                  & 78.0                   & 0.0            & - & 3.7      & 1.13       & 0.0     & 85.0      & 78  \\
+s\_sa22a-d3   & 57.0                    & 109.0                    & 127.0                 & 93.0                   & 1.16           & 10.0      & 5.2      & 3.61       & 30.0    & 84.0      & 121   \\
+n3\_009       & 32.0                    & 47.0                     & 77.0                  & 48.0                   & 1.0            & 9.06      & 3.3      & 2.14       & 20.0    & 63.0      & 59 \\
+n3\_006       & 41.0                    & 81.0                     & 144.0                 & 125.0                  & 0.65           & 9.72      & 6.1      & 3.37       & 156.0   & 89.0      & 138 \\
+s\_sa22b-d9   & 0.0                    & 0.0                      & 99.0                  & 82.0                   & 0.0            & - & 3.8      & 1.01       & 163.0   & 77.0      & 83   \\
+lab18         & 44.0                    & 41.0                     & 87.0                  & 62.0                   & 0.67           & 8.57      & 3.5      & 0.93       & 54.0    & 26.0      & 69 \\
+s\_sa22b-d5   & 31.0                    & 57.0                     & 67.0                  & 23.0                   & 2.45           & 9.41      & 4.2      & 3.33       & 60.0    & 6.0       & 47 \\
+s\_sa22b-md25 & 50.0                    & 57.0                     & 102.0                 & 75.0                   & 0.76           & 9.4       & 4.1      & 3.29       & 9.0     & 57.0      & 86 \\
+s\_sa22b-c20  & 79.0                    & 139.0                    & 112.0                 & 48.0                   & 2.87           & 10.16     & 3.2      & 3.22       & 37.0    & 38.0      & 110 \\
+lab7\_top     & 0.0                    & 0.0                      & 83.0                  & 62.0                   & 0.0            & - & 3.3      & 2.99       & 85.0    & 54.0      & 63  
+\end{tabular}
+\end{table*}
+
+\section{RESULTS \& DISCUSSION}\label{sec:results}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[h!]{0.32\textwidth}
+        \centering
+        \includegraphics[height=2.25in]{vobs_vs_vmax.png}
+        %\caption{V$_{obs}$ vs. intrinsic $V_{C}$}
+    \end{subfigure}%
+    \begin{subfigure}[h!]{0.32\textwidth}
+        \centering
+        \includegraphics[height=2.25in]{sigobs_vs_sigint.png}
+        %\caption{$\sigma_{obs}$ vs. intrinsic $\sigma_{int}$}
+    \end{subfigure}
+    \begin{subfigure}[h!]{0.32\textwidth}
+        \centering
+        \includegraphics[height=2.25in]{sigobs_vs_vmax.png}
+        %\caption{$\sigma_{obs}$ vs. $V_{C}$}
+    \end{subfigure}
+    \caption{Correlations between observed KDS properties (y-axis) and the intrinsic properties (x-axis) recovered following the beam smearing analysis.
+    Plots (a) and (b) highlight the strong positive correlation between the observed and intrinsic velocities and velocity dispersions, verifying that the beam smearing corrections are not generally over-extrapolating beyond the values recovered from the data themselves.
+    Plot (c) shows the positive correlation between velocity dispersion and velocity, demonstrating that the broadening of $\sigma$ in the beam smearing is largely a function of the strength of the velocity gradient in the galaxy.}
+    \label{fig:observed_and_intrinsic}
+\end{figure*}
+
+\subsection{Derived Kinematic Properties}
+Equipped with $PA_{Kin}$, $V_{C}$ and $\sigma_{int}$ for each of the resolved and non-interacting galaxies in the KDS, we first interpret these at $z \sim 3.5$, comparing with the \cite{Gnerucci2011} (G11) results at similar redshift throughout \cref{subsubsec:kin_misalignment}-\cref{subsubsec:dynamical_masses} and then in the context of galaxy evolution by comparing with samples across a wide redshift baseline in \cref{subsubsec:sigma_evolution} - \cref{subsubsec:v_evolution}.
+\subsubsection{Kinematic and Photometric Misalignment}\label{subsubsec:kin_misalignment}
+The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT as described in \cref{subsubsec:galfitting}, to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
+In figure \ref{fig:delta_pa} (a) the absolute difference between the position angles, $\Delta PA = |PA_{Kin}-PA_{morph}|$, is plotted as a function of the axis ratio, $\frac{b}{a}$, also determined by GALFIT from the HST photometry.
+The mean and median $\Delta PA$ values are 46$^{\circ}$ and 26$^{\circ}$ respectively, and $\Delta PA$ tends to increase as the axis ratio increases.
+Similar analysis is described in \citep[e.g.][]{Epinat2012,Wisnioski2015,Harrison2017} wherein rotating galaxies generally have excellent agreement between the position angles, with $\Delta PA$ increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
+This is due to the connection between galaxy inclination and axis ratio, with the lowest inclination galaxies showing the most morphological elongation, and the direction of this elongation on the sky is indicative of the galactic plane of rotation.
+
+\begin{figure*}
+    \centering \hspace{-1.3cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{delta_pa_vs_axis_ratio.png}
+        %\caption{$\Delta PA$ vs. axis ratio}
+    \end{subfigure} \hspace{0.4cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{delta_pa_vs_sigma.png}
+        %\caption{$\Delta PA$ vs. $\sigma_{obs}$}
+    \end{subfigure}
+    \caption{The absolute difference between $PA_{morph}$ and $PA_{kin}$, $\Delta PA$, is plotted in panel (a) against the GALFIT determined galactic minor to major axis ratio for all KDS galaxies with both HST coverage and dynamical modelling.
+The median difference computed in bins of 0.2 x-axis width and the standard deviation in each of these bins are also plotted as the black line and light blue shaded region respectively.
+The misalignment clearly increases as a function of axis ratio, but is also generally larger than reported in previous IFU studies at lower redshift, as described throughout the text.
+In panel (b) we explore the possibility that the photometric and kinematic misalignment may be a function of the observed velocity dispersion.
+There appears to be some suggestion that with increasing $\sigma_{obs}$, larger $\Delta PA$ are observed but we do not quantify this connection and conclude only that the elevated velocity dispersions at high redshift could be a contributing factor in increasing the misalignment between the two axes.}
+    \label{fig:delta_pa}
+\end{figure*}
+
+\cite{Wisnioski2015} report mean and median $\Delta PA$ values of 18$^{\circ}$ and 12$^{\circ}$ respectively and exclude galaxies from their rotating disk sample when $\Delta PA > 30^{\circ}$.
+In the local universe the agreement between morphological and kinematic position angles is generally $\Delta PA < 20^{\circ}$ \citep[e.g.][]{Epinat2008,Barrera-Ballesteros2014,Barrera-Ballesteros2015} and it is shown that significant misalignment is often a signature of galaxy interaction.
+In a recent paper by \cite{Rodrigues2016}, a subset of the KMOS$^{3D}$ galaxies at $z \sim 1$ have been re-analysed to establish the fraction of disk-like galaxies at this redshift given the criteria presented in section 4.1 of \cite{Wisnioski2015}.
+In this paper the authors note that single \Sers fits to the HST photometry can introduce biases when the galaxies show prominent morphological features such as bars, spiral arms and tidal tails, and instead measure $PA_{morph}$ using the outer-most isophote in a series of concentric elliptical isophotes with the IRAF task ELLIPSE.
+The resolved KDS galaxies at $z \sim 3.5$ have generally larger $\Delta PA$ values than those at lower redshift, and this observation has several potential explanations.
+For the majority of galaxies we do not believe we are in a regime where prominent morphological features are resolved in the HST imaging, so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
+However there are some cases where morphological tidal features could affect $PA_{morph}$ such as the GOODS-S galaxies bs006541, bs008543, cdfs\_lbg\_105, cdfs\_lbg\_109 and cdfs\_lbg\_111.
+Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
+This generally does not give the same answer as simply connecting the velocity extrema, as we have verified by rotating $PA_{Kin}$ in 1$^{\circ}$ increments and choosing the value which maximises the velocity gradient, calling this $PA_{rot}$.
+If the direction of the `zero-velocity strip' across the centre of the velocity maps is not perpendicular to the line connecting the velocity extrema, the $PA_{Kin}$ determined from MCMC will be different to the $PA_{Kin}$ determined from rotation (e.g.
+GOODS-S galaxy bs006541).
+The observed velocity map contains meaningful information about $PA_{Kin}$ beyond just a consideration of the velocity extremes, and we believe it is more physically meaningful to allow the $PA_{Kin}$ to explore and choose values which best fit the full 2D observed velocity field.
+As a test, extracting the $V_{C}$ values along $PA_{rot}$ makes xxx difference to the values on average for the sample. 
+The $1-\sigma$ errorbars in Figure \ref{fig:delta_pa} are determined by the 16th and 84th percentile distribution of the MCMC samples.
+For SSA22 the situation is complicated by the lower integration times of the HST data, and the use of ACS 814W imaging in which the galaxies have smaller apparent $R_{1/2}$ values due to observing light from younger stars.
+This is a limitation of this study and the errorbars in $\Delta PA$ reflect the poorer imaging data in this field.
+There do appear to be some galaxies that have low axis ratios, so that $PA_{morph}$ should be well constrained, and $\Delta PA$ values of $\sim$ 90$^{\circ}$ (e.g.
+GOODS-S galaxy cdfs\_lbg\_38 and SSA22 galaxy s\_sa22a-d3).
+There does not appear to be any obvious explanation for why this is the case.
+In practice, since the intrinsic [OIII]$\lambda5007$ profile is determined by the GALFIT model throughout the modelling in \cref{subsec:3d modelling}, the $\Delta PA$ value has an impact on the derived $V_{C}$.
+As $\Delta PA$ increases, the model beam smeared velocity reaches maximum value at larger radii, and so the inferred intrinsic $V_{C}$ becomes larger to provide an adequate fit to the data.
+This effect is small until $\Delta PA$ reaches $\sim 60^{\circ}$, in which case the $V_{C}$ can be up to 30kms$^{-1}$ larger, with this an interesting consequence of modelling the intrinsic light profile with a different position angle to that of the velocity field.
+We have also explored the possibility that $\Delta PA$ is correlated with $\sigma_{obs}$ and that the increased random motions or turbulence within the galaxies are the driving force behind kinematic and morphological misalignment.
+There appears to be some suggestion that the two quantities are connected, although we make no attempt to quantify this, and conclude that the elevated velocity dispersions at high redshift could be a contributing factor in the observation of large mean $\Delta PA$.
+
+We do not restrict the sample on the basis of $\Delta PA$ due to the increased uncertainty in determining both $PA_{morph}$ and $PA_{Kin}$ and due to the appearance of galaxies which have misalignment between $PA_{morph}$ and $PA_{Kin}$ at low axis ratios.
+
+\subsubsection{Observed and Intrinsic Properties}\label{subsubsec:observed_and_intrinsic}
+In Figure \ref{fig:observed_and_intrinsic} we investigate correlations between the observed and intrinsic dynamical properties of the resolved KDS galaxies, to highlight the mean beam smearing correction factors, the mean values of the observed and intrinsic distributions and the factors driving the beam smearing corrections.
+Figure \ref{fig:observed_and_intrinsic} (a) and (c) contain all resolved KDS galaxies with a valid $V_{C}$ measurement from the modelling sample, whereas (b) contains all resolved KDS galaxies, with $\sigma_{int}$ determined by subtracting the instrumental resolution value from $\sigma_{obs}$ for those galaxies without a valid $V_{C}$ measurement.
+
+The mean and median $\sigma_{obs}$ to $\sigma_{int}$ correction factors are 0.79 and 0.77 respectively. 
+The mean and median $V_{C_{smeared}}$, the extrapolated and inclination corrected observed velocity, to $V_{C}$ correction factors, are 1.30 and 1.21 respectively.
+In Figure \ref{fig:observed_and_intrinsic} (a) and (b) we find a strong positive correlation between both the observed and intrinsic velocities and velocity dispersions, which verifies that the beam smearing corrections do not alter the shape of the distributions of $V_{obs}$ and $\sigma_{obs}$ determined from the raw data.
+
+Figure \ref{fig:observed_and_intrinsic} (c) highlights that galaxies with larger $V_{C}$ values tend to have larger $\sigma_{obs}$, which tells us that the broadening of the median velocity dispersion is driven by the strength of the velocity gradient, as assumed throughout the dynamical modelling section.
+
+The most striking observation here is that the mean and median $V_{C}$ values in the KDS sample are substantially lower than reported by \cite{Gnerucci2011} for the AMAZE sample of galaxies at comparable $M_{\star}$.
+This will be discussed further in \cref{subsubsec:sigma_and_v} and throughout \cref{subsec:redshift_evolution}.
+
+\subsubsection{$\sigma_{int}$ and $V_{C}$}\label{subsubsec:sigma_and_v}
+In figure \ref{fig:v_sig_and_v} (a) we plot the distribution of resolved KDS galaxies with $V_{C}$ measurements in $\sigma_{int}$ vs.
+log($V_{C}$) parameter space, along with the galaxies from G11 plotted in grey.
+We also plot the $V_{C}$ = $\sigma_{int}$ line, which roughly bisects the KDS sample, and indicates the kinematic state of the galaxies as described in the following subsection.
+
+\begin{figure*}
+    \centering \hspace{-1.3cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{sigma_versus_v.png}
+        %\caption{$\Delta PA$ vs. axis ratio}
+    \end{subfigure} \hspace{0.4cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{v_over_sigma_versus_v.png}
+        %\caption{$\Delta PA$ vs. $\sigma_{obs}$}
+    \end{subfigure}
+    \caption{In panel (a) the distribution of all KDS galaxies with $V_{C}$ measurements in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols, and AMAZE galaxies from G11 with grey.
+    There is no strong correlation between the two parameters in either of these surveys, however several of the $V_{C}$ values in G11 are substantially larger or have $\sigma_{int}$ values consistent with 0kms$^{-1}$.
+    This is despite the two samples having similar ranges in stellar mass, and is probably a consequence of the different modelling techniques used to infer the dynamical paramters.
+    We assume that $\sigma_{int} = 30kms^{-1}$ for the G11 galaxies with reported $\sigma_{int} = 0kms^{-1}$, which is roughly equal to the spectral resolution of the instrument with which they were observed (SINFONI).
+    The $V_{C}/\sigma_{int} = 1$ divides the galaxies classified as rotation dominated and dispersion dominated, with dispersion dominated galaxies sitting above the line. 
+    The galaxy s\_sa22a-M38, classified here as a merger but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ is marked on the plot.
+    In panel (b) the distribution of all KDS galaxies with $V_{C}$ measurements in the $V_{C}$/$\sigma_{int}$ vs. $V_{C}$ plane is shown.
+    $V_{C}$/$\sigma_{int}$ increases as a function of $V_{C}$ following the beam smearing corrections applied to both quantities.
+    We also mark the $V_{C}$/$\sigma_{int}=1$ line in this panel, finding that half of the KDS galaxies with $V_{C}$ measurements have $V_{C}$/$\sigma_{int} > 1$, despite all showing velocity gradients in the observations.
+    We discuss the rotation dominated fraction with respect to the full sample in the text.}
+    \label{fig:v_sig_and_v}
+\end{figure*}
+
+The KDS galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is excellent agreement between KDS and AMAZE for $ \sim 50\%$ of the G11 rotating sample.
+The other $ \sim 50\%$ generally have much larger $V_{C}$ values, and three galaxies are reported as having $\sigma_{int}$ consistent with 0kms$^{-1}$.
+We note also that one of the KDS galaxies in SSA22-a classified as a merger due to the double peak in the HST morphology, s\_sa22a-m38, is in the G11 rotating sample (highlighted in Figure \ref{fig:v_sig_and_v}), although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk.
+This difference highlights the classification ambiguity for galaxies with double peaks in both ionised emission line and HST F160W profiles, as the galaxy could fall into either of the categories described above.
+However in the case of s\_sa22a-m38 we also observe a double peak in the spectrum at the flux centre, indicative of two blobs at different redshifts and leading to artificial broadening of $\sigma_{obs}$ towards the centre of the galaxy when the dynamics are measured with single gaussian fits.
+Several of the G11 galaxies plotted here also do not have reported errors on the $V_{C}$ values, and due to the lack of tabulated $V_{obs}$ values it is unclear the extent to which these have been extrapolated from the data.
+It is these high $V_{C}$ G11 galaxies which drive the difference in mean and median $V_{C}$ between the samples.
+Further comparison between the KDS and G11 $\sigma_{int}$ and $V_{C}$ values are made throughout \cref{subsec:redshift_evolution}.
+
+\subsubsection{Rotation Dominated Fraction and Merger Fraction}\label{subsubsec:rotation_and_mergers}
+\begin{table}
+    \centering
+\begin{tabular}{ c c c c c c c c }
+
+ \hline
+ & N$_{Res}$ & N$_{Merg}$ & $\%$ Merg & N$_{Disp}$ & $\%$ Disp & N$_{RD}$ & RDF  \\
+ \hline
+G1 & 12 & 2 & 17 & 4 & 33 & 6 & 0.50 \\
+G2 &  11 & 2 & 19 & 6 & 54 & 3 & 0.27\\
+Sa & 9 & 8 & 89 & 1 & 11 & 0 & 0.0 \\
+Sb & 11 & 1 & 9 & 6 & 54 & 4 & 0.37 \\
+ \hline
+\end{tabular}
+\caption{The rotation and merger dominated fractions for each pointing}
+\label{tab:rdf}
+\end{table}
+
+In Figure \ref{fig:v_sig_and_v} (b) we plot the ratio of $V_{C}$/$\sigma_{int}$ against $V_{C}$ for the KDS galaxies, with the former quantity commonly used as an indicator of whether SFGs at different redshifts are rotation dominated $(V_{C}$/$\sigma_{int} > 1)$ or dispersion dominated $(V_{C}$/$\sigma_{int} < 1)$ \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
+In the local universe, disky, SFGs are observed to have $V_{C}/\sigma_{int}$ values in excess of 10 (i.e.
+the disks are `well settled'), due to the decline of velocity dispersion across cosmic time, as gas fractions and disk turbulence decrease \citep[e.g.][]{Epinat2008,Epinat2008a}.
+The KDS galaxies above the black, dashed $V_{C}/\sigma_{int} = 1$ line in figure \ref{fig:v_sig_and_v} are classified as rotation dominated, and we plot the full morpho-kinematic grids for these in \cref{app:rotation_dominated}.
+The remainder are dispersion dominated and are plotted in \cref{app:dispersion_dominated}.
+What is striking about many of the dispersion dominated galaxies is that they show clear velocity gradients across the observed velocity maps, and can generally be well fit with the arctangent model.
+This suggests that, for these galaxies, although rotational motions are present within the disks, they are small or comparable with the elevated $\sigma_{int}$ values observed throughout the $z \sim 3.5$ sample.
+This suggests in turn that the random motions traced by $\sigma_{int}$ are probably providing some degree of gravitational support for the total mass of the system (see \cref{subsubsec:dynamical_masses}), in contrast to the local universe in which late-type galaxies are supported entirely by ordered rotation.
+In table \ref{tab:rdf} we list the merger, dispersion and rotation dominated fractions (RDFs) in each of the 4 pointings across GOODS-S and SSA22.
+For all pointings except SSA22-a the detected merger fraction is low, however, as discussed already in \cref{subsec:morpho-kin-class}, almost every spatially resolved galaxy in SSA22-a is taking part in some kind of interaction event.
+This observation has important consequences for the subsequent kinematic and morphological evolution of galaxies in high density environments, especially protoclusters, where the brightest cluster galaxies grow hierarchically through the aggregation of satellite mass.
+We choose to omit this pointing from the analysis of a total rotation dominated fraction (RDF) since using the numbers from the high density environment would bias the RDF low.
+For the other three pointings we combine the number of rotation dominated galaxies and divide by the total number of spatially resolved galaxies (including mergers and those not in the modelling sample) to arrive at the combined RDF of $0.39\pm 0.08$, where the error is the statistical error on the RDF, computed by generating bootstrapped samples, with replacement, and values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original datapoints.
+For each of the bootstrapped samples we re-compute the RDF and take the errors on the actual RDF as the 16th and 84th percentiles of the resulting distribution.
+We have also calculated upper and lower RDF limits based on the individual $V_{C}/\sigma_{int}$ points and errors, evaluating the maximum and minimum number of galaxies which could scatter above $V_{C}/\sigma_{int} = 1$.
+This leads to a larger error bar of $0.39^{+0.34}_{-0.27}$, plotted as a thin grey shaded region in \ref{fig:rdf_and_v_sigma_w_redshift} and the statisical value is represented by the black error bar.
+This value is in good agreement with the result of G11, however we note that their result of $RDF \sim 0.33$ could be higher if any of the galaxies which were not passed through their dynamical model were rotation dominated.
+The number would also decrease if s\_sa22a-m38 were classified as a merger as described in \cref{subsubsec:sigma_and_v}.
+We interpret these results in the context of the cosmic evolution of the RDF in \cref{subsubsec:RDF_evolution}.
+
+\subsubsection{Lack of Dynamical Mass}\label{subsubsec:dynamical_masses}
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{tf_binned.png}
-\caption{star forming main sequence}
-\label{fig:distributions}
+\includegraphics[width=0.48\textwidth]{rv_squared.png}
+\caption{We plot the ratio $M_{vir}/M_{\star}$ computed using only rotational velocities (Eq.
+13) for the KDS galaxies with $V_{C}$ measurements vs.
+$M_{\star}$, with the black line indicating equality between the two quantities.
+The red symbols show the galaxies with $V_{C}/\sigma_{int} > 1$ and the clear symbols show the galaxies with $V_{C}/\sigma_{int} < 1$, which these galaxies having on average lower $M_{vir}$.
+The majority of the points lie in the unphysical $M_{vir} < M_{\star}$ region.
+This highlights the potential for a combination of random motions, traced by $\sigma_{int}$, and ordered rotation to play a role in supporting the total dynamical mass, an expression for which is given by Eq.
+14 in the text.}
+\label{fig:dyn_masses}
 \end{figure}
 
-\section{DISCUSSION}\label{sec:discussion}
+Further evidence for the provision of gravitational support by random motion traced by $\sigma_{int}$ can be found by comparing the virial mass computed at the convovled 2R$_{1/2}$ radius, $M_{vir}$, with $M_{\star}$.
+It is expected that $M_{vir} > M_{\star}$, as the dynamics trace not only the stellar mass, but also the gas mass and dark matter mass within the radius at which $M_{vir}$ is evaluated.
+At $z \sim 3.5$ the gas reservoirs are on average a much larger fraction of the total galaxy mass than in the local universe \citep[e.g.][]{Tacconi2013,Saintonge2013,Wisnioski2015} as there has not yet been time to convert this gas mass into stellar mass, and so in principle if ordered rotation is tracing the total mass in these systems, $M_{\star}$ should be clearly below $M_{vir}$.
+In figure \ref{fig:dyn_masses}, where we have computed the virial mass from the ordered rotational motions alone, as traced by $V_{C}$, following equation \ref{eq:dyn_mass_v_only}, we find that this is not the case for the modelling sample, with $M_{vir} < M_{\star}$ for the vast majority of galaxies (particularly those with $M_{\star} > 9.5$).
+
+\begin{equation}\label{eq:dyn_mass_v_only}
+   M_{vir} = \frac{2R_{1/2}V_{C}^{2}}{G}
+\end{equation}
+
+This strongly suggests that rotational motions alone are not enough to provide gravitational support for the mass in the system, and random motions contribute to provide gravitational support for some fraction of the total mass contained within these compact galaxies.
+To follow this idea we can compute the contribution to $M_{vir}$ from $\sigma_{int}$ using equation \ref{eq:dyn_mass_sigma} \citep[e.g.][]{Cappellari2006}.
+
+\begin{equation}\label{eq:dyn_mass_sigma}
+   M_{vir} = \frac{2R_{1/2}V_{C}^{2}}{G} + \frac{\beta R_{1/2}\sigma_{int}^{2}}{G}
+\end{equation}
+
+In general the amount gravitational suport provided by $\sigma_{int}$ depends on galaxy geometry and structure \citep[e.g.][]{Cappellari2006,Belli2014}, with this dependence contained in the value of $\beta$ in equation \ref{eq:dyn_mass_sigma}.
+It is possible to derive a relationship between $\beta$ and \Sers index, a proxy for galaxy structure, as detailed in \cite{Cappellari2006} and shown in equation \ref{eq:beta_n}.
+
+\begin{equation}\label{eq:beta_n}
+   \beta(n) = 8.87 - 0.831n + 0.0241n^{2}
+\end{equation}
+
+%Now simply stating that it is possible to find the lower limit on beta to bring the dynamical masses above the stellar masses, BUT that realistically the data do not allow us to figure out the contribution from sigma so just quoted for interest
+
+We have modelled the galaxies throughout the analysis as n = 1 exponential disks, and verified with single \Sers fits in GOODS-S that this is close to the case for most of the galaxies, for which $\beta(n) \sim 8$.
+For galaxies below the $M_{vir} = M_{\star}$ line, we can find the minimum value of $\beta$ required to bring the two quantities to equality.
+In both the $V_{C}/\sigma_{int} > 1$ and $V_{C}/\sigma_{int} < 1$ samples we find that the mean $\beta_{min}\sim 5$, although we do not attempt to use $M_{vir}$ for any further analysis, merely to demonstrate the need for gravitational support that originates in random motions, as characterised by $\sigma_{int}$.
+
+\subsection{The redshift evolution of dynamical properties}\label{subsec:redshift_evolution}
+Having observed low rotational velocities and large velocity dispersions in our $z \sim 3.5$ sample, and compared these with the G11 values at similar redshift, we now aim to place the results in cosmological perspective and interpret the data in the context of galaxy evolution.
+Throughout the following sections we compare the median dynamical properties of several IFU studies over a wide redshift baseline \citep{Green2014,Wisnioski2015,Epinat2012,ForsterSchreiber2009,Cresci2009,Gnerucci2011}, and also compare with Fabry-Perot data from the GHASP sample \citep{Epinat2008,Epinat2008a} as an indicator of the behaviour of SFGs in the local universe.
+The galaxy selection criteria in these surveys, with the exception of \cite{Green2014}, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the $OIII\lambda5007$ or $H\alpha$ ionised gas emission line.
+In \cite{Green2014}, half of the galaxies at $z\sim 0.1$ are selected to have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, providing a local comparison sample to the high redshift universe.
+The galaxies in these surveys have different $M_{\star}$ distributions and we attempt to make clear in the following figures, with the symbols and shaded regions, where the results are directly comparable.
+
+We have made use of the tabulated data and errors in these studies to derive the datapoint values and errorbars plotted in figure \ref{fig:rdf_and_v_sigma_w_redshift} and \ref{fig:sigma_and_v_sigma_w_redshift} in a consistent way, which is to take the fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples (i.e.
+we do not want the derived values with extremely large errors to dominate the averages).
+The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
+In \cref{subsec:3d modelling} we have described the variation in the methodology used to compute $V_{C}$ and $\sigma_{int}$ between different surveys as a way to help disentangle true evolution from offsets between derived dynamical values caused by disparate measurement techniques.
+It appears that choice of dynamical model and dynamical parameter extraction method does still play a large role in understanding the evolution of dynamical parameters, and for this reason we have chosen to closely follow the methods described in \cite{Harrison2017} to allow for a consistent comparison between $z \sim 3.5$ and $z \sim 1$.
+In the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+
+\subsubsection{The evolution of the rotation dominated fraction}\label{subsubsec:RDF_evolution}
+
+\begin{figure*}
+    \centering \hspace{-1.3cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{v_sigma_evolution.png}
+        \caption{$V_{C}/\sigma_{int}$ vs. redshift}
+    \end{subfigure} \hspace{+0.4cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{rdf_evolution.png}
+        \caption{RDF vs. redshift}
+    \end{subfigure}
+    \caption{In panel (a) $V_{C}/\sigma_{int}$ is plotted against redshift for surveys spanning $0 < z < 4$.
+    The filled symbols show the sample mean values, with the KDS mean at $z\sim3.5$ plotted with the red circle, with black errorbars representing the statistical error on the mean computed using bootstrap re-sampling as described in the text.
+    The sample medians and statistical errors on these values are plotted with the coloured and grey horizontal bars, falling in each case below the mean, suggesting that large individual $V_{C}/\sigma_{int}$ measurements may bias the sample mean high.
+    We also plot the 16th and 84th percentiles of the distribution of individual $V_{C}/\sigma_{int}$ measurements as shaded regions to give an indication of the range of values measured in each survey, and indicate the mean stellar mass of each survey in the legend.
+    Lack of tabulated values for KMOS$^{3D}$ and SINS restricted us from computing the $V_{C}/\sigma_{int}$ values in a consistent way, and so we plot only the sample means without errorbars and caution against comparison of these with the other surveys.
+    The DYNAMO point and errors are plotted in white to highlight the difference in selection criteria, with the low redshift galaxies chosen to have similar properties to those at $z\sim2$.
+    There is a clear decline in the mean $V_{C}/\sigma_{int}$ values with redshift, but with wide ranges in the individual measurements.
+    There is also a connection to the mean $M_{\star}$ of the surveys, with larger mean $M_{\star}$ surveys reporting higher mean $V_{C}/\sigma_{int}$.
+    In panel (b) we plot the associated RDF, with this deriving from the fraction of galaxies above the $V_{C}/\sigma_{int} = 1$ dashed line plotted in panel (a).
+    The narrow shaded regions represent the maximum and miminum RDF, computed as described in the text.
+    Again, it was not possible to directly compute the RDF in a consistent way for the KMOS$^{3D}$, SINS and AMAZE galaxies and we simply plot the quoted values for these surveys.
+    It appears that the RDF drops from $\sim 100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\sim 40\%$ at z $\sim 3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher RDFs.
+    Presumably this decline would continue out to the higher redshifts in which galaxies really are assembling their first stellar components are not supported by ordered rotation.
+    The dot-dash line is the RDF $\propto z^{-0.2}$ cosmic decline suggested in \protect\cite{Stott2016}.
+    In both panels the surveys from which the data are drawn are denoted in the legends.
+}
+    \label{fig:rdf_and_v_sigma_w_redshift}
+\end{figure*}
+
+In figure \ref{fig:rdf_and_v_sigma_w_redshift} (a) we plot $V_{C}/\sigma_{int}$ and in (b) we plot the closely connected RDF both as a function of redshift for the KDS modelling sample (omitting the SSA22-a pointing from the RDF calculation as explained in \cref{subsubsec:rotation_and_mergers}).
+The $V_{C}/\sigma_{int}$ values do not change significantly across the individual KDS pointings, and plotting these independently would not change the results.
+We measure the mean $V_{C}/\sigma_{int} = 1.13^{+0.18}_{-0.15}$ and median $V_{C}/\sigma_{int} = 0.99^{+0.14}_{-0.11}$ and RDF = $0.39 \pm 0.08$ for the KDS galaxies.
+For the samples in which tabulated $V_{C}$ and $\sigma_{int}$ values are available we compute the fractional error weighted mean and median of $V_{C}/\sigma_{int}$, along with associated errors, as described in \cref{subsec:redshift_evolution}.
+The samples for which the mean $V_{C}/\sigma_{int}$ and RDF values can be computed in a consistent way to the KDS galaxies are GHASP \citep[E08]{Epinat2008} $log(M_{\star}[M_{\odot}])=10.6$, DYNAMO \citep[G14]{Green2014} $log(M_{\star}[M_{\odot}])=10.3$ (although with the caveat that the selection criteria was designed to pick out SFGs representative of the $z\sim2$ universe), KROSS \citep[H17]{Harrison2017} $log(M_{\star}[M_{\odot}])=9.9$ and MASSIV \citep[E12]{Epinat2012} $log(M_{\star}[M_{\odot}])=10.2$.
+For these surveys, in figure \ref{fig:rdf_and_v_sigma_w_redshift} (a) the filled symbols and black errorbars represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
+The shaded regions give the 16th and 84th percentiles of the distribution on individual $V_{C}/\sigma_{int}$ measurements, plotted here to indicate the range of measurements at each redshift slice.
+In figure \ref{fig:rdf_and_v_sigma_w_redshift} (b) the filled symbols with errorbars denote the surveys for which the RDF is computed as the fraction of galaxies with $V_{C}/\sigma_{int} > 1$.
+We have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the RDF.
+These are shown with the thin grey shaded regions, and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the invidual points.
+The filled symbols without errorbars represent results quoted in other works.
+In both panels (a) and (b) the KDS mean is plotted as the large red circle at $z\sim3.5$.
+
+There is a further caveat when comparing with the G11 ($log(M_{\star}[M_{\odot}])=9.9$) values; since dynamical properties are only computed for 11/33 rotationally dominated galaxies in their sample, the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
+The shaded percentile regions and errors for the AMAZE data in figure \ref{fig:rdf_and_v_sigma_w_redshift} (a) are shown for reference, and we note that for their three galaxies with $\sigma_{int} = 0kms^{-1}$ we assume $\sigma_{int} = 30kms^{-1}$ (roughly equal to the SINFONI spectral resolution) in order to compute the $V_{C}/\sigma_{int}$ ratio and mean and median $\sigma_{int}$ values.
+For those galaxies in G11 that have no errorbars on $V_{C}$ due to the parameter being unconstrained, we assume a fractional error of 1.
+The G11 RDF, taken as 33\% is also difficult to compare against and is a minimum in the sense that some of the galaxies for which dynamical properties have not been computed could be rotation dominated.
+We plot the G11 RDF with the clear symbol and without errorbars in \ref{fig:rdf_and_v_sigma_w_redshift} (b).
+
+Throughout the KMOS$^{3D}$ study of \cite[W15]{Wisnioski2015} two redshift ranges are considered, the first at $z\sim 1$ with $log(M_{\star}[M_{\odot}])=10.65$ and the second at $z\sim 2.2$ with $log(M_{\star}[M_{\odot}])=10.86$.
+No tabulated values are provided, so we plot here the $V_{C}/\sigma_{int}$ and RDF presented in W15 without errorbars.
+For the SINS sample \citep[FS09]{ForsterSchreiber2009} and \citep[C09]{Cresci2009} ($log(M_{\star}[M_{\odot}])=10.6$), we plot without errorbars the mean $V_{C}/\sigma_{int}$ value in figure \ref{fig:rdf_and_v_sigma_w_redshift} (a) for the full sample presented in W15, since this cannot be directly computed from the tabulated integrated velocity dispersions in FS09.
+We plot also in figure \ref{fig:rdf_and_v_sigma_w_redshift} (b) RDF for the full sample, computed in FS09 section 9.5.1, which classifies rotation dominated galaxies as those where $V_{obs}/(2\sigma_{tot}) > 0.4$, with $\sigma_{tot}$ equal to the velocity dispersion measured from the galaxy integrated spectrum.
+In a recent work by \cite[R16]{Rodrigues2016}, a subset of the KMOS$^{3D}$ $z \sim 1$ sample has been re-analysed and a lower RDF of 69\% was recovered, despite the use of identical classification criteria.
+The recovery of this lower fraction is driven mainly by the presence of peaks in the $\sigma_{int}$ maps which do not coincide with the rotation centre, a criteria which we do not impose throughout this work, and spatial offsets between the rotation centre and the centre of stellar mass.
+We also do not impose the coincidence of $PA_{kin}$ and $PA_{morph}$ as described in \cref{subsubsec:kin_misalignment} as a rotation dominated criteria due to the increased uncertainties in measuring both of these quantities, although we note here that our KDS RDF would drop from 38\% to 16\% due to the loss of 7 galaxies from the rotation dominated sample if we require $\Delta PA < 30^{\circ}$.
+The KROSS $z\sim1$ RDF presented in H17 lies between the two extremes of R16 and W15 computed for the KMOS$^{3D}$ sample.
+
+Despite the systematic variations in measurement technique and classification criteria, it is clear that the RDF, as traced simply by the $V_{C}/\sigma_{int}$ inferred from ionised gas emission lines, drops from $\sim 100\%$ of galaxies in the local universe to $\sim 2/3$ of galaxies in the $z \sim 1-2$ universe and to $\sim 1/3$ above $z \sim 3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
+This is highlighted in figure \ref{fig:rdf_and_v_sigma_w_redshift} (b) by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic RDF decline as described in \cite{Stott2016}.
+Scatter above and below the RDF $\propto z^{-0.2}$ evolution line may be attributed in part to the different mean stellar masses of the surveys, with those that have larger stellar masses tending to scatter above this line.
+Higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the sample RDF higher.
+The width of the $V_{C}/\sigma_{int}$ distributions indicates the galaxy diversity at each redshift slice, driven by the collection of galaxy masses, sSFRs, gas fractions, morphologies and evolutionary states which comprise each sample.
+Explanations for the mean decline of $V_{C}/\sigma_{int}$ with cosmic time have been discussed at length in other surveys \citep[e.g][]{ForsterSchreiber2009,Law2009,Wisnioski2015} and we revisit this in the following subsection.
+
+\subsubsection{The evolution of velocity dispersion}\label{subsubsec:sigma_evolution}
+
+\begin{figure*}
+    \centering \hspace{-1.3cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{sigma_evolution.png}
+        \caption{$\sigma_{int}$ vs. redshift}
+    \end{subfigure} \hspace{0.4cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{v_evolution.png}
+        \caption{$V_{C}$ vs. redshift}
+    \end{subfigure}
+    \caption{Panel (a) presents a compilation of literature $\sigma_{int}$ values plotted against redshift for surveys spanning $0 < z < 4$.
+    The filled symbols show the sample mean values, with the KDS mean at $z\sim3.5$ plotted with the red circle, with black errorbars representing the statistical error on the mean computed using bootstrap re-sampling as described in the text.
+    The sample medians and statistical errors on these values are plotted with the coloured and grey horizontal bars, falling in each case below the mean, suggesting that large individual $\sigma_{int}$ measurements may bias the sample mean high.
+    We also plot the 16th and 84th percentiles of the distribution of individual $\sigma_{int}$ measurements as shaded regions to give an indication of the range of values measured in each survey, and indicate the mean stellar mass of each survey in the legend.
+    Lack of tabulated values for KMOS$^{3D}$ restricted us from computing the $\sigma_{int}$ values in a consistent way, and so we plot only the sample means without errorbars and caution against comparison of these with the other surveys.
+    The DYNAMO point and errors are plotted in white to highlight the difference in selection criteria, with the low redshift galaxies chosen to have similar properties to those at $z\sim2$.
+    The $\sigma_{int}(z)$ scaling relation from W15, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values, with the solid line showing $log(M_{\star}[M_{\odot}])=10.0$, the dashed line $log(M_{\star}[M_{\odot}])=10.3$ and the dot-dashed line $log(M_{\star}[M_{\odot}])=10.6$.
+    In each case the scaling relation is plotted for $V_{C} = 150kms^{-1}$.
+    These are intended as indicators of the way in which $\sigma_{int}$ evolves in galaxies in different mean $M_{\star}$, where this on average gives an indication of the extent to which the stellar population has been accumulated, which may provide increased stability for an extended rotating disk.
+    The KDS datapoint appears to be consistent with the scenario proposed in previous work, whereby the mean $\sigma_{int}$ increases over cosmic time, with large scatter between individual galaxies, as a result of increased gas fractions and more efficient accretion of cold gas.
+    The vertical location of the mean datapoints in this plane are mediated by the mean $M_{\star}$ of each survey, which is itself connected to the mean gas fraction. 
+    We note also that the Law 2009 datapoint has not been corrected for beam smearing and so represents an upper limit on $\sigma_{int}$ for that survey. 
+    Panel (b) presents the mean, median and distributions of $V_{C}$ measurements of these surveys between $0 < z < 4$, with the large red circle representing the KDS measurement.
+    We again present the KMOS$^{3D}$ mean points without errors and distributions.} 
+    \label{fig:sigma_and_v_sigma_w_redshift}
+\end{figure*}
+
+The observation that $\sigma_{int}$ becomes increasingly large towards high redshift has now been firmly established in several studies, including all of those from which data has been taken to create figure \ref{fig:sigma_and_v_sigma_w_redshift}.
+To complement the surveys already described throughout \cref{subsubsec:RDF_evolution}, we add data from \cite{Law2009} to explore the evolution of $\sigma_{int}$ values across cosmic time.
+In this study, resolved data are collected with the OSIRIS instrument for 13 SFGs with $log(M_{\star}[M_{\odot}])=10.0$.
+We note that the $\sigma_{mean}$ values and errors tabulated in this paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam smearing in any way.
+These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam smearing corrected, or extracted at the galaxy outskirts where the beam smearing is much smaller.
+\cite{Law2009} attribute the cosmic increase in $\sigma_{int}$ to much larger gas fractions at high redshift, with the gas accumulated through rapid cold-mode accretion along cosmic filaments.
+Systems such as these form roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk.
+Following this, $\sigma_{int}$ decreases over time as ordered rotations begin to dominate.
+\cite{Wisnioski2015} interpret the increase of $\sigma_{int}$ towards high redshift in terms of the equilibrium model, which describes the rough balance between galactic accretion, star-formation and outflows \citep[e.g.][]{Lilly2013}, deriving a scaling relation for $\sigma_{int}$ with redshift appropriate for galaxies which have formed a quasi-stable disk (see their section 5.2).
+This relation gives a prediction for $\sigma_{int}$ in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR, and using observed constraints for these properties leads to $\sigma_{int}$ predictions with redshift that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
+In both viewpoints the increased $\sigma_{int}$ values observed at high redshift are primarily the result of the prevalence and efficiency of gas inflow onto galaxies in this regime.
+In figure \ref{fig:sigma_and_v_sigma_w_redshift} (a) we plot the fractional error weighted mean, median and distribution of $\sigma_{int}$ from tabulated data, as described in detail in the figure caption.
+For the KMOS$^{3D}$ points at $z\sim 1$ and $z\sim 2.2$, there are no tabulated values and so we again plot the mean $\sigma_{int}$ values listed in W15 without errorbars.
+The mean KDS datapoint is shown with the large red symbol with $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ (median $\sigma_{int} = 67.0^{+5.0}_{-4.8} kms^{-1}$) at z = 3.5, which is in agreement with the $\sigma_{int}$ scaling relation presented in W15, plotted with the grey lines for $V_{C} = 150kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$, rather than the $log(M_{\star}[M_{\odot}])=10.5$ value used in \cite{Wisnioski2015} (note we have also not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
+The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ and $V_{C}$ in the equation shown in the top right of figure \ref{fig:sigma_and_v_sigma_w_redshift} (a).
+
+The same caveats apply as described above surrounding the comparison of values derived from different measurement techniques, however it appears that the evolution of $\sigma_{int}$ can be well described in the context of the equilibrium model by the evolution of the gas fraction with redshift \citep{Wisnioski2015}.
+The $M_{\star}$ value of a galaxy is linked to the size of the gas reservoir, since gas is depleted to build the stellar population.
+The location of mean $\sigma_{int}$ values is therefore related to the mean $M_{\star}$ of each survey, with this being an indicator of the accumulation of a stellar population and hence the evolutionary state of the galaxies.
+The tracks plotted in figure \ref{fig:sigma_and_v_sigma_w_redshift} give a rough indication of how $\sigma_{int}$ evolves in galaxies of a particular stellar mass in the context of the equilibrium model, and the KDS galaxies provide a strong observational constraint on the internal dynamics of main sequence galaxies between $z=3-3.7$.
+
+\subsubsection{The evolution of maximum circular velocity}\label{subsubsec:v_evolution}
+In figure \ref{fig:sigma_and_v_sigma_w_redshift} (b) we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the different surveys against redshift, as explained in the caption of figure \ref{fig:sigma_and_v_sigma_w_redshift} to highlight two observations:
+\begin{itemize}
+    \item The KDS $V_{C}$ values appear lower than reported in lower redshift studies with similar mean $M_{\star}$ values, as a result of averaging over a sample with a higher dispersion dominated fraction
+    \item Different modelling and measurement techniques affect the inferred $V_{C}$ values
+\end{itemize}
+
+In a rotationally supported system, the magnitude of $V_{C}$ is set by the requirement to support the mass, $M_{tot}$, in the system, i.e.
+the combination of $M_{gas}$, $M_{\star}$ and $M_{DM}$, against gravitational collapse.
+$V_{C}$ increases as $M_{tot}$ increases and so we would expect the systems with larger average $M_{\star}$, assuming that these are indicative of systems with greater $M_{tot}$, to have larger $V_{C}$, which appears generally to be the case in figure \ref{fig:sigma_and_v_sigma_w_redshift} (b) where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
+Using the average $M_{\star}$ values and velocity extraction radius in the KDS sample, $log(M_{\star}[M_{\odot}])=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of $M_{gas}$ and $M_{DM}$ would raise this estimate).
+Indeed this estimate is similar to the mean value found in the KROSS sample for $log(M_{\star}[M_{\odot}])=10.0$ galaxies at $z\sim1$.
+In figure \ref{fig:sigma_and_v_sigma_w_redshift} (b) we plot the mean and median values and percentiles of the $V_{C}$ distribution for the different surveys, finding wide distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
+The KDS datapoint, represented by the large red circle, has mean $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ and median $V_{C} = 60.0^{+7.5}_{-5.9}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
+This could either be a result of the measurement and modelling technique, which carries significant uncertainties due to modelling assumptions, the S/N of the [OIII]$\lambda5007$ emission line even in very long integrations at this redshift, the spatial coverage of [OIII]$\lambda5007$ may be more compact that $H\alpha$ and consequently may not probe out to the same galactic radii and the sparsity of resolution elements, or could be the result or some real physical process in the galaxies which lowers $V_{C}$ as traced by the ionised gas dynamics.
+Also, since there is a higher fraction of dispersion dominated galaxies at $z\sim3.5$, the mean $V_{C}$ value of the complete sample is likely to be biased low.
+This is easier to see in \cref{subsec:TF} where we revisit the rotational velocities in the context of the inverted stellar mass `Tully-Fisher Relation' \citep[smTFR;][]{Tully1977,Bell2000a}.
+
+It seems likely that the measurement of low $V_{C}$ values in the KDS could be at least in part a consequence of the KMOS data not having the depth to trace the outskirts of the galaxies where the rotation curve begins to flatten.
+Using the 2D arctangent function to extrapolate through the datapoints to $2R_{1/2}$ could underestimate the true $V_{C}$ if the data do not trace close to where the rotation curve begins to flatten.
+We have also assumed that the galaxies are disky in order to compute an inclination angle in each case, which is then used to correct $V_{obs}$ for viewing angle.
+At this redshift and mean $M_{\star}$, the disk assumption may not be correct, as galaxies could have more complicated structures which have not yet stabilised into rotating disks.
+However the distribution of inclination angles is consistent with observing a selection of galaxies with inclinations randomly distributed as $0^{\circ} < i < 90^{\circ}$, with the KDS mean inclination of $59.5^{\circ}$ agreeing well with the theoretical mean of $57.3^{\circ}$ (for a simple derivation of this value see e.g.
+the appendix in \cite{Law2009}).
+There are some galaxies where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
+lbg\_24 with $log(M_{\star}[M_{\odot}])=9.75$), yet the inferred $V_{C}$ is smaller than $\sigma_{int}$.
+This, in combination with figure \ref{fig:dyn_masses}, suggests that the velocity dispersion could be responsible for providing partial dynamical support in these systems.
+\cite{Law2009} observe galaxies with similarly low mean velocity shear and high velocity dispersions (the velocities are not plotted here since the tabulated values are not inclination or beam smearing corrected) and attribute this to instabilities which occur when the cold gas becomes dynamically dominant following efficient accretion and in line with the high gas fractions observed at high redshift.
+We caution that at high redshift these $V_{C}$ measurements are challenging for the reasons stated above, however our data appear to support a scenario in which low $M_{\star}$ galaxies experience elevated random motions related to the rapid accretion of cold gas, which is partially supported gravitationally by these random motions and may contribute to the observation of low $V_{C}$ values.
+At higher $M_{\star}$ the accumulation of a stellar population provides stability, $\sigma_{int}$ decreases and $V_{C}$ increases to provide the additional gravitational support.
+These processes are mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion.
+
+The second point is that it is difficult to assess whether the $V_{C}$ values reported by different surveys (the modelling and extraction techniques differ and are described in \cref{subsubsec:param_extraction}) are directly comparable.
+The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
+In particular the $V_{C}$ parameter reported in G11 is unconstrained for several galaxies, requires large extrapolation from the data and leads to very large rotational velocities for 5/11 of their galaxies.
+The remaining 6/11 galaxies have $V_{C}$ values close to those reported for the KDS sample.
+This is a consequence of the current state of the data quality at high redshifts, and it is important to keep in mind that both $\sigma_{int}$ and $V_{C}$ are still dependent on modelling technique.
+
+\subsection{The z = 3.5 Tully-Fisher Relation}\label{subsec:TF}
+
+\begin{figure*}
+    \centering \hspace{-1.3cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{tully_fisher_standard_log.png}
+        \caption{smTFR}
+    \end{subfigure} \hspace{0.4cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{tully_fisher_s0_log.png}
+        \caption{S$_{0.5}$ Relation}
+    \end{subfigure}
+    \caption{In panel (a) we plot log($V_{C}$) vs.
+$M_{\star}$, i.e.
+the inverted stellar mass Tully-Fisher relation for the KDS galaxies with $V_{C}/\sigma_{int} > 1$ in red and the galaxies with $V_{C}/\sigma_{int} < 1$ with clear symbols.
+    Also plotted with the solid green is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex error on the fit.
+    This $z\sim0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in Reyes 2011.
+    The $V_{C}/\sigma_{int} > 1$ KDS galaxies also show no evolution from this relation within the errorbars, with the $V_{C}/\sigma_{int} < 1$ galaxies scattering below the relation.
+    This highlights the need for careful sample selection when constructing this relation, and explains the low KDS mean $V_{C}$ value as a consequence of averaging over a sample with a high fraction of dispersion dominated galaxies.
+    In panel (b) we plot the $S_{0.5}$ vs. $M_{\star}$ relation, which accounts for a contribution to the total dynamical mass from non-circular motions as traced by $\sigma_{int}$.
+    The symbol convention is the same as panel (a) and we include also the KDS galaxies with only $\sigma_{int}$ measurements as the black symbols.
+    We plot also the K07 relation with the black dashed line, and find that the KDS galaxies agree with this, showing much less separation between the rotation and dispersion dominated galaxies and with less scatter than in panel (a).
+    We caution against over-interpretation of this result, since it is unclear what the physical origins of the random motions traced by $\sigma_{int}$ are, and the extent to which they are contributing to support dynamical mass.}
+    \label{fig:tf_relation}
+\end{figure*}
+
+In the $\Lambda$CDM paradigm the smTFR relates the angular momentum of the dark matter halo within which disk galaxies reside to the $M_{\star}$ content of these galaxies.
+Angular momentum in the halo, which is in turn affected by accretion of gas from the IGM, is transferred to the disk \citep{Fall1983}, where the gas then cools radiatively over time, forming the stellar population of the galaxy.
+Observing the smTFR at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies.
+In principle, studying whether the smTFR evolves with redshift gives us information about how galaxies accumulate their stellar mass and rotational velocities, with offsets from the local relation towards lower $M_{\star}$ values at fixed rotational velocity suggesting that the dynamical mass is in place, but the stellar mass is yet to be formed.
+The main question arising from observations in support of and against evolution of the smTFR with redshift is: Do galaxies evolve along a smTFR which is fixed with redshift (i.e.
+increasing in $V_{C}$ as $M_{\star}$ increases) or is there a shift in the zero-point and/or slope with redshift (i.e.
+as $M_{\star}$ accumulates, $V_{C}$ remains fixed).
+Essentially we'd like to know how an individual, unperturbed point, representing a typical rotation-dominated SFG allowed to evolve without mergers, would move around the $V_{C}$ vs.
+$M_{\star}$ plane over 12Gyr of purely secular evolution.
+Connected to this also is the idea of progenitor bias, in that the SFGs we are selecting and comparing between $z\sim0-3.5$ may not form an evolutionary cohort, and certainly there is much evidence for the quenching of SF at a particular mass scale \citep[e.g.][]{Keres2005,Dekel2006,Peng2010}, leading to morphological and dynamical transformation.
+
+The smTFR has been studied numerous times between $0.5 < z < 2$, giving results consistent with zero evolution of the slope and zero-point \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Harrison2017}.
+Others have reported that as redshift increases, the smTFR shifts towards lower masses at fixed rotational velocity, e.g.
+in \cite{Puech2008,Puech2010} where a -0.34 dex log$(M_{\star})$ offset is observed at $z\sim0.6$, in the \cite{Tiley2016a} KROSS sample at $z\sim0.9$ with a -0.41 dex shift (although in this work a stricter cut than in H17 of $V_{C}/\sigma_{int} > 3$ is applied), in \cite{Cresci2009} a -0.41 dex offset is observed at $z\sim2$ (although the galaxies used to compute this were the highest fidelity rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5)$ and in G11 an offset of -1.29 dex is claimed, although there is large degree of scatter between the individual galaxies, with 50\% of the sample consistent with the $z\sim0$ relation.
+
+To demonstrate the relationship between $V_{C}$ and $M_{\star}$ in individual KDS galaxies from the modelling sample, we plot in figure \ref{fig:tf_relation} (a) the inverted smTFR.
+In this plane, $V_{C}$, a tracer of the dynamical mass of the system, is plotted as a function of the luminous mass for the KDS modelling sample.
+The rotationally dominated galaxies with $V_{C}/\sigma_{int} > 1$ are shown with red circles, whereas the dispersion dominated $V_{C}/\sigma_{int} < 1$  galaxies are shown with the open circles.
+The black errorbars on the individual points reflect the upper and lower errors on the individual $V_{C}$ values, whereas the black errorbar in the bottom left gives the representative 0.2 dex error in measuring $M_{\star}$ for each galaxy from the SED fits.
+In H17, the smTFR relation is fit to $\sim400$ SFGs at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$ and with $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, similar to the KDS galaxies.
+The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
+We plot this best fit relation with the green line in figure \ref{fig:tf_relation} (a), with the green shaded region giving the typical uncertainty on the fit of 0.2 dex along the velocity axis.
+These parameters are consistent with the values $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, measured in \cite{Reyes2011} for a sample of $z<0.1$ disks traced with H$\alpha$, in a similar mass range and where $V_{C}$ has been extracted at the same radius, and we plot this as the dashed black line in figure \ref{fig:tf_relation} (a).
+The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$, where the galaxies span a similar $M_{\star}$ range and the $V_{C}$ values have been computed following a consistent methodology, suggests that there is no evolution in the smTFR between these limits.
+The rotation dominated KDS galaxies with $V_{C}/\sigma_{int} > 1$ and $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ are broadly consistent within the errorbars with the H17 fit, showing a tendency to lie below the relation.
+The dispersion dominated KDS galaxies sit below the H17 relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in H17 and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
+We do not attempt to fit through our data, due to the relatively narrow mass range spanned by the points, and conclude that there does not appear to be evolution in the zero-point of the smTFR between $z\sim1-3.5$ for rotation-dominated galaxies as traced by KROSS and KDS.
+This result is a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotational velocity is observed as a result of omitting rotationally dominated galaxies with lower $V_{C}$ values (as is also the case in \cite{Cresci2009} with the high fidelity disk sample).
+Conversely, fitting the smTFR through a full sample including dispersion dominated galaxies would shift the zero-point in the opposite sense.
+The conclusion from this work is that the smTFR appears to show no evolution across the bulk of cosmic time when the measurement of dynamical properties and selection of rotation dominated galaxies are consistent.
+This comes with the caveat that it is not clear whether main sequence SFGs at difference redshift slices can be considered to form an evolutionary sequence.
+
+For completeness we also include the $S_{0.5} = \sqrt{0.5V_{C}^{2} + \sigma_{int}^{2}}$ vs.
+$M_{\star}$ relation described throughout \cite[K07][]{Kassin2007} in figure \ref{fig:tf_relation} (b) (which is consistent with the absorption-line-based $M_{\star}$ Faber-Jackson relation for nearby elliptical galaxies), where we plot $S_{0.5}$ vs.
+$M_{\star}$.
+This is connected to the idea suggested in figure \ref{fig:dyn_masses}, that the rotational velocities alone may not be a good tracer of the total dynamical mass, with $S_{0.5}$ accounting for the contribution to the dynamical mass from non-circular motions.
+In K07, using $S_{0.5}$ reduced the scatter in the TFR out to $z\sim1.2$, which they attribute to the inclusion of galaxies with peculiar kinematics in the sample with reduced rotational velocities in relation to their stellar mass.
+$S_{0.5}$ has been studied in both C09 and G11, with both reporting an evolution of the K07 trend towards lower $M_{\star}$ at fixed $S_{0.5}$, which is taken as further evidence for the evolution of the smTFR.
+In figure \ref{fig:tf_relation} (b) the KDS galaxies agree with the K07 relation within the errorbars, with reduced scatter in comparison to the smTFR in panel (a), suggesting that their is no evolution in $S_{0.5}-M_{\star}$ relation.
+The symbol convention is the same as in panel (a), and the division now between the rotation and dispersion dominated galaxies is no longer clear. 
+Considering the increase in observed $\sigma_{int}$ values over cosmic time (figure \ref{fig:sigma_and_v_sigma_w_redshift}), this suggests that there is an interplay between the $V_{C}$ values and $\sigma_{int}$ traced by ionised gas emission lines as discussed in \cite{Kassin2012}.
+We caution against over-interpretation of this result, since the origin of $\sigma_{int}$ and the extent to which this quantity traces dynamical mass is unclear, however this trend adds to the evidence that $V_{C}$ alone is an insufficient tracer of the total dynamical mass at this redshift.
+
+The smTFR derives directly from the virial theorem, in which changes to the dynamical mass are driven by changes in both the sizes and velocities of galaxies, prompting authors recently \citep[e.g.][]{Cortese2016,Contini2015a,Burkert2016a,Harrison2017,Swinbank2017} to study the connection between $M_{\star}$ and specific angular momentum, $j_{s} \propto R_{1/2}V_{C}$, with this possibly a more fundamental quantity to describe galaxy evolution.
+We briefly discuss the specific angular momentum of the KDS galaxies in the following subsection.
+
+\subsection{Angular Momentum}\label{subsec:ang_mom}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.8\textwidth]{angular_momentum.png}
+\caption{We plot the specific angular momentum $j_{s} \propto R_{1/2}V_{C}$ against stellar mass, $M_{\star}$, for the KDS galaxies with $V_{C}/\sigma_{int} > 1$ in red and with clear symbols when $V_{C}/\sigma_{int} < 1$.
+Included also are the $j_{s} \propto M_{\star}^{\alpha}$ fits (with $\alpha = 0.6\pm0.2$) reported in H17 for the KROSS full sample in solid green and for the rotation and dispersion dominated subsamples with the dashed green lines.
+The black solid line is the fit presented in \protect\cite{Romanowsky2012} to a sample of $z=0$ disk galaxies ($\alpha = 0.51\pm0.06$), to which the KROSS relation is offset in $j_{s}$ by $\sim0.2-0.3$dex.
+The KDS rotation dominated galaxies are offset from the KROSS relation by a further $\sim0.3-0.4$dex, with the dispersion dominated galaxies scattering to lower $j_{s}$, with both KDS subsets following a roughly similar slope to KROSS and the $z=0$ sample.
+Further, we include the $j_{s} \propto (1+z)^{-1}$ evolution reported in \protect\cite{Swinbank2017} with the red solid line, using the local slope and normalisation, which appears to pass through the KDS rotation dominated galaxies.
+These results are in line with a scenario where the cosmic evolution of $j_{s}$ is driven mainly by the size evolution of galaxies as they accrete cold material to form stars from the IGM, adding to the outer components of the galaxy disks.
+The split between rotation dominated and dispersion dominated galaxies may indicate that these systems are the progenitors of local late-type and early-type galaxies respectively.}
+\label{fig:ang_mom}
+\end{figure*}
+
+In figure \ref{fig:ang_mom} we plot the specific angular momentum, j$_{\star} \equiv J/M_{\star}$ where J is the total angular momentum \citep{Fall1983}, as a function of stellar mass M$_{\star}$.
+This quantity has been described in detail in \cite{Harrison2017} section 4.3 and refer to this for more details about the use of $j_{s}$ as measured from ionised gas kinematics as a tracer of the specific angular momentum content of SFGs.
+
+\begin{equation}\label{eq:ang_mom}
+   j_{n} = k_{n}C_{i}v_{s}R_{1/2}
+\end{equation}
+
+In equation \ref{eq:ang_mom} we list the approximate estimator for specific angular momentum described in \cite{Romanowsky2012} (their equation 6), with k$_{n}$ a numerical coefficient which depends on the \Sers index of the galaxy, n, and is approximated in equation \ref{eq:kn} (see \cite{Romanowsky2012}).
+
+\begin{equation}\label{eq:kn}
+   k_{n} = 1.15 + 0.029n + 0.062n^{2}
+\end{equation}
+
+Due to varying HST coverage and quality, it has not been possible to estimate n for all KDS galaxies.
+However we have verified with both floating \Sers index fits, fixed n = 1 \Sers fits and fixed n = 4 \Sers fits throughout \cref{subsubsec:galfitting} that the vast majority of GOODS-S galaxies ($\sim70\%$ of the KDS modelling sample) are well described by the n = 1 exponential profile (also assumed throughout the modelling procedure in \cref{sec:Kinematic_Properties}).
+Setting n = 1 in equation \ref{eq:kn} leaves $k_{n} = 1.19$ and we continue under this assumption analogous to in \cite{Harrison2017} (although we note that as stated in \cite{Harrison2017} setting n = 1 results in only a $\sim20\%$ difference in the derived $j_{s}$ values).
+In equation \ref{eq:ang_mom} $C_{i}$ is the de-projection factor, assumed to be $1/sin(i)$, and $v_{s}$ is the observed velocity at $2R_{1/2}$.
+The combination $v_{s}C_{i} \equiv V_{C}$ and we can use our measured rotation velocities to leave \ref{eq:ang_mom_final} as the final expression for $j_{s}$ used to calculate the values in figure \ref{fig:ang_mom}.
+
+\begin{equation}\label{eq:ang_mom_final}
+   j_{n=1} \equiv j_{s} = 1.19V_{C}R_{1/2}
+\end{equation}
+
+In figure \ref{fig:ang_mom} we plot the fit to all KROSS galaxies with the solid green line, and also the individual fits to the rotation and dispersion dominated KROSS galaxies with the dashed green and light green lines respectively.
+The fits to the full sample and rotation dominated KROSS galaxies (with fitting relation defined by log$j_{s} =  \beta + \alpha[logM_{\star} - 10.0]$) lie $\sim0.2-0.3$ dex beneath the $z\sim0$ relation from \cite{Romanowsky2012}, in contrast to the smTFR, with the dispersion dominated galaxies scattering around much lower $j_{s}$ values.
+This offset is explained to be a consequence mainly of the size evolution of the disks of SFGs over the redshift range $0-0.9$.
+The local and KROSS relations have comparable slopes, with $\alpha_{z=0}=0.51\pm0.06$ and $\alpha_{z=0.9}=0.6\pm0.2$, in agreement with other studies of the $j_{s}-M_{\star}$ relation \citep{Cortese2016,Contini2015a,Burkert2016a,Swinbank2017}, and also in agreement with predictions for the slope of the relationship between dark matter specific angular momentum and the halo mass (i.e.
+$j_{halo} \propto M_{halo}^{2/3}$ \citep[e.g.][]{Barnes1987}).
+This is widely regarded as a consequence of the baryonic retention of angular momentum following a period in the formation of the proto-galaxy when the dark matter and baryons were well mixed.
+
+The rotation dominated KDS galaxies form a sequence $\sim 0.3-0.4$ dex beneath the KROSS relation, and with similar slope, however the slope is not well constrained due to the scatter and sparsity of the dataset.
+The dispersion dominated KDS galaxies form a sequence with similar slope but offset to lower still $j_{s}$ values.
+We plot also the $\sim j_{s} \propto (1+z)^{-1}$ reported in \cite{Swinbank2017} (using the local slope and normalisation from \cite{Romanowsky2012}), which the rotation dominated KDS galaxies appear to roughly follow.
+These results suggest that there is a continual drop in the specific angular momentum of SFGs with increasing redshift, as governed by the evolution of disk sizes \citep[e.g.][]{Trujillo2007} (see figure \ref{fig:morpho-distributions}) and that the relationship between the angular momentum of the baryons and the halos is constant over time.
+Conversely, the angular momentum of SFGs will increase with decreasing redshift as accretion of cold gas from the IGM which fuels star formation and tidal disruption from satellite galaxies or major mergers conspire to grow disk sizes over time \citep{Trujillo2007,Buitrago2008,VanderWel2014a}.
+Additonally since we observe a bimodal distribution of the rotation and dispersion dominated KDS galaxies in the $j_{s}-M_{\star}$ plane, we are plausibly observing the progenitors of late-type and early-type galaxies at $z\sim3.5$ as revealed by their kinematic signatures, consistent with the idea that early-type galaxies began their lives with less total angular momentum available to them.
+
+\section{CONCLUSIONS}\label{sec:conclusion}
+We have presented new measurements of the dynamical properties of $\sim 45$ spatially resolved SFGs at $z\sim3.5$ as part of the KDS, based on IFU data observed with KMOS.
+These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}[M_{\odot}])< 10.5$ typical main sequence galaxies at these redshifts.
+By using a combined morpho-kinematic classification based on broad-band HST imaging and our IFU data, we have separated probable interacting galaxies from the sample and made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for those remaining.
+The main conclusions of this work are summarised as follows:
 
 \begin{itemize}
-    \item Surface brightness dimming
-    \item beam smearing
-    \item Different modelling techniques
-    \item 
+    \item We observe an increase in $\sigma_{int}$ values in comparison with $z\sim0$ galaxies, with a sample mean of $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$.
+    We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline, finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to boost random motions within high redshift galaxies.
+    \item As a result of the increase in $\sigma_{int}$, most of the resolved galaxies are dispersion dominated, with velocity dispersions greater than their measured rotation velocities.
+    We measure a rotation dominated percentage, $V_{C}/\sigma_{int} > 1$, of $39 \pm 8 \%$ in our sample, substantially lower than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (figure \ref{fig:rdf_and_v_sigma_w_redshift}).
+    \item The mean rotational velocity value of $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ appears low in comparison to surveys at lower redshift, although there is again significant diversity in $V_{C}$ measurements in each survey (figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    This appears to be mainly the result of averaging over a sample with a much higher percentage of dispersion dominated galaxies.
+    \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}[M_{\odot}]) < 11.0$ at $z\sim0.9$ in the KROSS survey (figure \ref{fig:tf_relation}).
+%something else here when finished writing the TF section
+    This relation is consistent with SFGs at $z=0$ and so we report no significant evolution in the slope or zero-point of the smTFR between $z=0-3.5$.
+    Constistency of sample selection and measurement techniques are crucial factors when determining evolution in the $V_{C}$ vs. $M_{\star}$ plane by comparing samples at different redshifts.
+    The dispersion dominated galaxies scatter below the trend.
+    \item The virial mass computed from $V_{C}$ values alone is lower than the stellar mass for the majority of KDS galaxies.
+    We compute an additional component of the virial mass contributed by the velocity dispersion, shifting the virial mass above the stellar mass, and use this as a qualitative indicator that $\sigma_{int}$ is responsible for supporting some fraction of the total mass of the system (figure \ref{fig:dyn_masses}).
+    This is clearly over-simplified, as the lack of correlation between $\sigma_{int}$ and $M_{\star}$ suggests that not all of the random motions support mass, and may originate from turbulence.
+    \item To investigate the possible contribution of $\sigma_{int}$ to the total dynamical mass further, we plot $S_{0.5} = \sqrt{0.5V^{2} + \sigma_{int}^{2}}$ as a function of $M_{\star}$, finding a tighter relationship than in the case of the inverse smTFR, which shows no evidence for evolution from the $z=0$ relation from \cite{Kassin2007} (figure \ref{fig:tf_relation}).
+    We caution again though that there is no clear relationship between $\sigma_{int}$ and $M_{\star}$ and this result should not be over-interpreted.  
+    \item The specific angular momentum (angular momentum divided by stellar mass $M_{\star}$; $j_{s}$) of the KDS galaxies is $\sim$0.3-0.4 dex lower than KROSS galaxies at $z\sim0.9$ at fixed $M_{\star}$, and the slope of the $j_{s}-M_{\star}$ relation appears comparable between the two samples (figure \ref{fig:ang_mom}).
+    This supports a scenario in which the derease in $j_{s} \propto R_{D}V_{C}$ with increasing redshift between $z=0-3.5$ is driven by the gradual size evolution of galaxies over the same redshift interval (figure \ref{fig:morpho-distributions}).
+    \item Almost all of the resolved KDS galaxies in the $z\sim3.1$ high density protocluster pointing SSA22-a are involved in interactions, which has important consequences for the dynamics of and accumulation of stellar populations within these cluster galaxies which sit at the peak of the cosmological density field.
+    The merger fraction computed across the other, lower density pointings is 15\%.
+
 \end{itemize}
-
-\section{CONCLUSIONS}\label{sec:conclusions}
 
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA HST, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+This work is based on observations taken by the 3D-HST Treasury Program (GO 12177 and 12328) with the NASA/ESA HST, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+Based on data obtained with the European Southern Observatory Very Large Telescope, Paranal, Chile, under Large Program 185.A-0791, and made available by the VUDS team at the CESAM data center, Laboratoire d'Astrophysique de Marseille, France.
+The HST data matched to the VUDS-DR1 are described in \cite{Grogin2011} and \cite{Koekemoer2011} for CANDELS and include data from the ERS \cite{Windhorst2011}.
 
@@
 
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Some extra material}
+\section{Kinematics Plots}\label{app:kinematics_plots}
+\subsection{Rotation Dominated ($V_{C}/\sigma_{int} > 1$)}\label{app:rotation_dominated}
 
@@
 \centering
-\includegraphics[width=\textwidth]{combine_sci_reconstructed_bs006516_grid_fixed.png}
-\includegraphics[width=\textwidth]{combine_sci_reconstructed_bs006541_grid_fixed.png}
-\includegraphics[width=\textwidth]{combine_sci_reconstructed_bs008543_grid_fixed.png}
-\caption{Distributions of the physical properties of KDS galaxies in both GOODS-S and SSA22}
-\label{fig:grids}
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs006516_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs008543_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs016759_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_20_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_32_grid_paper.png}
+\label{fig:goods_rot_1}
 \end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_38_grid_paper.png}
+\label{fig:goods_rot_2}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_91_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs009818_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_b012141_012208_grid_paper.png}
+\label{fig:goods_rot_3}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22a-d3_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_ROTATION/combine_sci_reconstructed_n3_009_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-c20_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-d5_grid_paper.png}
+\label{fig:SSA_rot_1}
+\end{figure*}
+
+\subsection{Dispersion Dominated ($V_{C}/\sigma_{int} < 1$)}\label{app:dispersion_dominated}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_bs006541_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_b15573_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_24_grid_paper.png}
+\label{fig:goods_disp_1}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_bs014828_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_25_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_94_grid_paper.png}
+\label{fig:goods_disp_2}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_105_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_109_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_111_grid_paper.png}
+\label{fig:goods_disp_3}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_113_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_lab7_top_grid_paper.png}
+\label{fig:goods_disp_4}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_s_sa22b-md25_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_n3_006_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_lab25_grid_paper.png}
+\label{fig:SSA_disp_2}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_lab18_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_s_sa22b-d9_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_n_c3_grid_paper.png}
+\label{fig:SSA_disp_1}
+\end{figure*}
+
+\subsection{Mergers}\label{app:mergers}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22b-c10_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-md23_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-md46_grid_paper.png}
+\caption{ssa mergers}
+\label{app:ssa_mergers_1}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-m38_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c35_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c30_grid_paper.png}
+\caption{ssa mergers}
+\label{app:ssa_mergers_2}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-aug96m16_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c49_grid_paper.png}
+\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c47_grid_paper.png}
+\caption{ssa mergers}
+\label{app:ssa_mergers_3}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_14_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_23_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_bs010545_grid_paper.png}
+\includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_93_grid_paper.png}
+\caption{High resolution imaging is important not only for reliably recovering the morphological parameters, but also to explain peculiar features in the observed velocity and velocity dispersion fields.
+In the two examples above, multiple components in the HST imaging clearly correspond to marginally different [OIII]$\lambda$5007 emission wavelengths, which manifest as velocity shifts in individual spaxels and broadens the observed dispersion pattern where the emission lines at different wavelengths merge.}
+\label{app:goods_mergers_1}
+\end{figure*}
+
+\section{Table of measurements from different surveys}
+\begin{table*}
+\centering
+\caption{We present here a reference of the mean and median kinematic properties used throughout figures 7 and 8 for the different surveys.
+The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
+\label{tab:evolution_numbers}
+\begin{tabular}{c c c c c c c c c c }
+
+ \hline
+Survey & $\left< z \right> $ & $\left< log\left(\frac{M_{\star}}{M_{\odot}}\right)\right>$ & $\left< \frac{V_{C}}{\sigma_{int}} \right>$ & med$\left(\frac{V_{C}}{\sigma_{int}}\right)$ & RDF & $ \left< \sigma_{int} \right>$ & med$\left(\sigma_{int}\right)$ & $\left<V_{C}\right>$ & med$\left(V_{C}\right)$  \\
+ \hline
+ GHASP & 0.001 & 10.6 & $12.91^{+0.51}_{-0.44}$ & $12.45^{+5.15}_{-5.05}$ & $1.0^{+0.00}_{-0.024}$ & $13.0^{+0.5}_{-0.5}$ & $13.0^{+6.0}_{-4.0}$ & $189.0^{+3.5}_{-3.0}$ & $159.4^{+113.3}_{-79.2}$ \\
+ DYNAMO & 0.1 & 10.3 & $5.06^{+0.18}_{-0.15}$ & $4.55^{+3.06}_{-2.22}$ & $0.96^{+0.02}_{-0.015}$ & $45.9^{+0.3}_{-0.3}$ & $39.0^{+18.2}_{-21.9}$ & $183.0^{+1.0}_{-1.0}$ & $164.0^{+76.0}_{-50.0}$ \\
+ KROSS & 0.9 & 9.9 & $3.05^{+0.17}_{-0.17}$ & $2.36^{+2.64}_{-1.46}$ & $0.81^{+0.05}_{-0.05}$ & - & - & $117.0^{+4.0}_{-4.0}$ & $109^{+77.0}_{-66.0}$ \\
+ KMOS$^{3D}$ & 1.0 & 10.7 & 5.5 & - & 0.93 & 25 & - & 170 & - \\
+ MASSIV & 1.2 & 10.2 & $2.41^{+1.4}_{-0.9}$ & $1.95^{+2.40}_{-1.31}$ & $0.67^{+0.06}_{-0.06}$ & $61.8^{+3.8}_{-4.2}$ & $52.0^{+23.2}_{-20.7}$ & $132.13^{+10.4}_{-8.2}$ & $103.0^{+99.0}_{-61.2}$ \\
+ SINS(C09) & 2.0 & 10.6 & $5.0^{+0.93}_{-0.97}$ & $4.74^{+1.11}_{-0.18}$ & 1.0 & $51.2^{+8.0}_{-7.9}$ & $42.5^{+14.5}_{-3.5}$ & $232.0^{+12.8}_{-12.7}$ & $240.0^{+31.0}_{-60.2}$ \\
+ SINS(F09) & 2.0 & 10.6 & 2.6 & - & 0.60 & - & - & $201.3^{+4.3}_{-4.0}$ & $174.0^{+83.0}_{-58.0}$ \\
+ KMOS$^{3D}$ & 2.2 & 10.9 & 2.6 & - & 0.73 & 55 & - & 170 & - \\
+ AMAZE & 3.0 & 10.0 & $3.59^{+1.45}_{-1.1}$ & $2.1^{+4.7}_{-1.15}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+27.0}_{-48.0}$ & $217^{+59.1}_{-40.2}$ & $129^{+166.0}_{-50.2}$ \\
+ KDS & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.39^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $78.8^{+5.4}_{-5.1}$ & $60.0^{+49.1}_{-18.2}$ \\
+ \hline
+\end{tabular}
+\end{table*}
+
+\section{Kinematic Parameters Error Estimates}\label{app:kin_error_estimates}
+
+\subsubsection{3D modelling kinematic parameter error estimates}\label{subsubsec:model_errors}
+As mentioned above, the MCMC sampling provides distributions for each of the model parameters, from which we can extract the 84th and 16th percentile values as the +/- 1-$\sigma$ errors.
+During the following procedure $PA_{kin}$ is fixed to the maximum likelihood value for all model evaluations.
+We also fold in the uncertainty on measuring the inclination angle at this point, assuming a conservative GALFIT measurement error of $\Delta$i = 10$\%$ following the analysis of EXAMPLE. 
+The beam smeared and intrinsic models are reconstructed using the 16th and 84th percentile parameters, with the lower velocity 16th percentile model using the inclination value closer to edge-on, and the 84th percentile model using the inclination closer to face-on.
+To clearly distinguish the 1-$\sigma$ error regions for both the beam smeared and intrinsic model the region between the 16th and 84th percentile evaluations are shaded blue and red respectively in the figures shown in Appendix A.
+The +/- 1-$\sigma$ error values for both $v_{2.2}$ and $v_{3.0}$ are then calculated using the the equations below, also taking account the measurement errors with $\bar{\sigma}_{v_{obs}}$ equal to the average observational uncertainty extracted along $PA_{kin}$.
+The subscripts `16th' and `84th' denote the model from which the velocity has been extracted.
+
+\begin{equation}\label{eq:v2.2_plus}
+   \delta v_{2.2}+ = \sqrt{(v_{2.2_{84}} - v_{2.2})^{2} + (\bar{\delta}v_{obs})^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:v2.2_minus}
+   \delta v_{2.2}- = \sqrt{(v_{2.2} - v_{2.2_{16}})^{2}  + (\bar{\delta}v_{obs})^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:v3.0_plus}
+   \delta v_{3.0}+ = \sqrt{(v_{3.0_{84}} - v_{3.0})^{2} + (\bar{\delta}v_{obs})^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:v3.0_minus}
+   \delta v_{3.0}- = \sqrt{(v_{3.0} - v_{3.0_{16}})^{2}  + (\bar{\delta}v_{obs})^{2}}
+\end{equation}
+
+The upper and lower errors on the mean velocity dispersion are calculated in a similar fashion.
+To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40kms^{-1}$ and $\sigma_{int} = 80kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values.
+When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam smearing correction decreases, as the impact of convolution with other lines that have a shifted velocity centre is less severe.
+Conversely, assuming $\sigma_{int} = 40km^{-1}$ increases the beam smearing.
+We calculate the minimum and maxmimum intrinsic velocity dispersion, $\sigma_{o-84-40}$ and $\sigma_{o-16-80}$, using equations \ref{eq:sig_84_40} and \ref{eq:sig_16_80} respectively:
+
+\begin{equation}\label{eq:sig_84_40}
+   \sigma_{o-84-40} = \sqrt{(\sigma_{obs} - \sigma_{bs-84-40})^{2} - \sigma_{sky}^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:sig_16_80}
+   \sigma_{o-16-80} = \sqrt{(\sigma_{obs} - \sigma_{bs-16-80})^{2} - \sigma_{sky}^{2}}
+\end{equation}
+
+and then the lower and upper errors on $\sigma_{o}$ are given by the following:
+
+\begin{equation}\label{eq:sig_plus_error}
+   \delta\sigma_{o}+ = \sqrt{(\sigma_{o} - \sigma_{o-84-40})^{2} + (\bar{\sigma}_{\sigma_{obs}})^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:sig_minus_error}
+   \delta\sigma_{o}- = \sqrt{(\sigma_{o-16-80} - \sigma_{o})^{2} + (\bar{\sigma}_{\sigma_{obs}})^{2}}
+\end{equation}
+
+with $\bar{\sigma}_{\sigma_{obs}}$ equal to the average of the velocity dispersion measurement errors.
+Once these quantities have been measured, the upper and lower errors on the ratio $\frac{v_{2.2}}{\sigma{o}}$ can be computed using equations \ref{eq:v_over_sig_plus} and \ref{eq:v_over_sig_minus}, and the same prescription is followed to find the errors on $\frac{v_{3.0}}{\sigma{o}}$.
+
+\begin{equation}\label{eq:v_over_sig_plus}
+   \delta\frac{v_{2.2}}{\sigma_{o}}+ = \frac{v_{2.2}}{\sigma_{o}}\sqrt{\left(\frac{\delta v_{2.2}+}{v_{2.2}}\right)^{2} + \left(\frac{\delta\sigma_{o}+}{\sigma_{o}}\right)^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:v_over_sig_minus}
+   \delta\frac{v_{2.2}}{\sigma_{o}}- = \frac{v_{2.2}}{\sigma_{o}}\sqrt{\left(\frac{\delta v_{2.2}-}{v_{2.2}}\right)^{2} + \left(\frac{\delta\sigma_{o}+-}{\sigma_{o}}\right)^{2}}
+\end{equation}
 

### 2017-02-09 paper.tex
Major structural changes made after Chris comments and more rigour put into descriptions

@@
 
-\usepackage[hyperfootnotes=false]{hyperref}
+\usepackage[draft]{hyperref}
 \hypersetup{
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
+%\author[O.J. Turner et al.]{
+%O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
+%M. Cirasuolo,$^{1,2}$
+%C. M. Harrison,$^{2,3}$
+%J. Dunlop,$^{1}$
+%R. J. McLure,$^{1}$\newauthor
+%A. M. Swinbank$^{4,3}$
+%H. L. Johnson$^{3,4}$
+%\\
+%$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
+%$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
+%$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
+%$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.
+%}
+
 \author[O.J. Turner et al.]{
 O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
-M. Cirasuolo,$^{1,2}$
-C. M. Harrison,$^{2,3}$
-J. Dunlop,$^{1}$
-R. J. McLure,$^{1}$\newauthor
-A. M. Swinbank$^{4,3}$
-H. L. Johnson$^{3,4}$
 \\
 $^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
-$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
-$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
-$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.
+$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany
 }
@@
 \begin{abstract}
-We present dynamical measurements of 44 O[III]$\lambda5007$ resolved main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
-These measurements push back the frontier of dynamical studies utilising Integral-Field Spectroscopy, and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$, and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
-The mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with previous studies which have reported increasing $\sigma_{int}$ values with redshift.
-We find that $39 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
+We present dynamical measurements of 77 [O~{\sc III}]$\lambda5007$ resolved main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
+These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
+We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
+The KDS mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with the increase of $\sigma_{int}$ with redshift reported across the comparison samples.
+However we find that only $39 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
 The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e.
@@
 Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
-To explore this further, we plot the S$_{0.5}$-stellar mass relation, finding that the slope and normalisation are consistent with measurements between $z=0-1.2$, however we caution that there is no clear connection between $\sigma_{int}$ and stellar mass.
 These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
-There is a very high merger fraction of 89\% in a pointing covering the centre of the $z\sim3.1$ protocluster in the SSA22-a field, and merger fraction of 15\% across the remaining pointings.
 \end{abstract}
@@
 This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, and outflows and accretion events maintain a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
-The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sparre2015,Lee2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic star formation rate density in this redshift range \citep{Madau_2014}.
+The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic star formation rate density in this redshift range \citep{Madau_2014}.
 At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs, and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
@@
 
-This study focusses on the final question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotational velocities and velocity dispersions, using the [OIII]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
+This study focusses on the final question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotational velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS we have been able to spatially resolve [OIII]$\lambda$5007 emission in 44 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.
+By making use of KMOS we have been able to spatially resolve [O~{\sc III}]$\lambda$5007 emission in 44 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.
 
@@
 
-\section{SURVEY \& DATA REDUCTION}\label{sec:Survey_and_data}
-\subsection{The KMOS Deep Survey: sample selection and observations}
-Our target selection for the KDS sample is designed to pick out star-forming galaxies at $z = 3-4$, supported by deep multi-wavelength ancillary data and probing both cluster and field environments.
-Within this redshift range the [OIII]$\lambda$4959,$\lambda$5007 doublet and the $H_{\beta}$ emission lines are visible in the K-band and the [OII$\lambda$3727,$\lambda$3729] doublet is visible in the H-band, both of which are observable with KMOS.
-We also want to draw galaxies covering a wide range in the SFR-$M_{\star}$ relation, so that we are ultimately tracking the physical properties of a representative sample of the star-forming population at these redshifts.
+\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
+\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
+The KDS is a KMOS study of the gas kinematics and chemical composition in 77 SFGs with a median redshift of $z\sim3.5$, probing a representative section of the galaxy main sequence.
+The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
+The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks and the degree of disk turbulence, and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
+To achieve this we require very deep exposure times in excess of 7 hours on source for all galaxies, to reach the S/N required to detect line emission in the outskirts of the galaxies, where the rotation curves begin to flatten, and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
+
+\subsubsection{Sample selection}\label{subsubsec:sample_selection}
+Target selection for the KDS sample is designed to pick out SFGs at $z = 3-4$, supported by deep multi-wavelength ancillary data and probing both cluster and field environments.
+Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the K-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the H-band, both of which are observable with KMOS.
+We also want to select a sample of galaxies spanning a representative region of the galaxy main sequence to minimise biases towards a particular subset of the overall star-forming population at these redshifts.
 For these reasons, and to ensure a high detection rate of the ionised gas emission lines in the KDS galaxies, we select galaxies in well studied fields that have a previous spectroscopic detection.
-To avoid biasing the sample towards blue and highly star-forming galaxies we make no secondary cuts on the basis of mass and flux. %FIGURE REFERENCE%
+To avoid biasing the sample towards blue and highly star-forming galaxies we make no secondary cuts on the basis of mass and flux.
 Predominantly, the galaxies have been selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
-However, a subset of the selected cluster galaxies in SSA22 were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
-These `Lyman-Alpha Blobs' (LABs), which are extended and diffuse emission regions associated with but not centred on LBGs \citep{Steidel2000}, and especially LAB01, have been the subject of much previous study, e.g.
-\citep{Bower2004a}, \citep{Matsuda2004,Matsuda2007}, \citep{Geach2006,Geach2014}, \citep{Weijmans2010}, \citep{Hayes2011a} and LAB01 was the study of a recent campaign \citep{Geach2016} using data from MUSE, \citep{Bacon2010}, ALMA, \citep{Wootten2009}, and MOSFIRE, \citep{McLean2012}.
-These studies generally conclude that LABs are observed at the peaks of the cosmic density field and are therefore the progenitors of the most massive galaxy clusters, but the precise origin of the nebulous Ly$\alpha$ line emission is still unknown.
-
-The low-density environment galaxies are selected from the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 F160W imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+However, a subset of the selected cluster galaxies in the SSA22 field were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
+
+\subsubsection{GOODS-S}\label{subsubsec:sample_selection_goods}
+We select two `field' environment pointings with KMOS in the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 F160W imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
 We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
-These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [OIII]$\lambda$5007 or H$_{\beta}$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
+These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$_{\beta}$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
 The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions of spatial overdensity in the south-east (GOODS-S-P1) and north-west (GOODS-S-P2) to fill the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
-% Add the programme ID for HST WFC3 imaging
-The cluster galaxies are selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an extreme overdensity of LBG candidates at $z \sim 3.09$.
-Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS, \citep{Shapley2003}, \citep{Nestor2013}, and when combined with deep B,V,R band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival HST ACS and WFC3 imaging covering large swathes of the field, the ancillary data is in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the CANDELS fields.
-Fortunately at $z \sim 3.09$ the [OIII]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so we also fill the KMOS IFUs with galaxies in two pointings spanning the SSA22 protocluster, one towards the centre of the cluster (SSA22-a) and one to the south (SSA22-b).
-Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during a poor year for Paranal.
-% Physical properties - Waiting on information from ROSS for writing this
-The wealth of ancillary data in both fields allows for a consistent treatment of the SED modelling, providing physical properties which are directly comparable between the cluster and field environments.
-During the SED modelling we assume solar metallicity stellar templates, and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs to compute stellar masses and SFRs for the galaxies in both GOODS-S and SSA22.
-We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
-The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
-% comparisons with the Holden paper - MUST EXPLAIN DIFFERENCES IN PHYSICAL PR
-Ten of the targets in goodsp1 have also been observed with the MOSFIRE spectrograph and were the subject of a recent paper by \cite{Holden2016} concerning the ubiquitous nature of elevated [OIII]/H$\beta$ ratios in LBGs, and the consequences this observation has for the physical conditions of the ISM (in terms of electron density, ionisation parameter and hardness of radiation field).
-The results from the KDS will complement this study, in the sense that spatially resolved dynamical and chemical information provide key insights into the physical processes driving high redshift LBGs into regions of parameter space which only the most extreme galaxies broach in the local universe.
-\subsubsection{Survey Stategy}
-The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks and the degree of disk turbulence, and also to investigate the spatial distribution of metals within these galaxies.
-This will add substantially to the sample of galaxies already observed in integral field spectroscopy at this epoch \citep{Cresci2010,Gnerucci2011}.
-To achieve this we require very deep exposure times in excess of 7 hours on source for all galaxies, to reach the S/N required to detect line emission in the outskirts of the galaxies, where the rotation curves begin to flatten, and to make measurements within individual spatial pixels (spaxels).
-This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the spatially resolved metallicities reserved for a future work.
-To measure the dynamics we must spatially resolve the [OIII]$\lambda$5007emission line, and so the observing strategy has been designed to first reach the required K-band depth before observing in the H-band to complement the [OIII]$\lambda$5007 and $H_{\beta}$ lines with [OII$\lambda$3727,$\lambda$3729] for metallicity measurements.
-After large amounts of time was lost to poor weather conditions we decided to observe the SSA22 galaxies with the HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
-For the remainder of the paper we focus only on the K-band observations, which took place over the first two years of the programme. 
-\subsubsection{Observations}\label{subsub:Obs}
+
+\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
+We select a single `cluster' environment pointing from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an extreme overdensity of LBG candidates at $z \sim 3.09$.
+Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS, \citep{Shapley2003}, \citep{Nestor2013}, and when combined with deep B,V,R band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival HST ACS and WFC3 imaging covering large swathes of the field, the ancillary data is in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
+Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-CLUSTER).
+We also add a further field environment pointing to the south of the main galaxy spatial overdensity (SSA22-FIELD), leaving us with three field environment pointings across GOODS-S and SSA22 and a single cluster environment pointing, as summarised in table \ref{tab:pointings}.
+\footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during a poor year for Paranal.}
+
+\subsection{Observations and data reduction}\label{subsubsec:observations_and_dr}
+\subsubsection{Observations}\label{subsubsec:Obs}
 KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
@@
 Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band filter has spectral resolution of $R \sim 4200$.
-
-We prepare each pointing using $PA_{kin}$RMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsec:datareduction}).
-For all four of the pointings described above, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
-This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsec:datareduction}.
-
-The observations were carried out during August and September of observing semester P92, during August and September of P93 and November of P94.
-The seeing conditions were excellent for goodsp1 and goodsp2, $\sim 0.5^{\prime\prime}$ where we observe 20 and 19 targets respectively, and ranged between $\sim 0.55-0.65^{\prime\prime}$ for ssap1 and ssap2 where 21 and 19 galaxies were observed.
-Note that these numbers are less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92 observing semester and our requirement to observe at least one control star throughout an Observing Block (OB).
-In Figure \ref{fig:main_sequence} we plot the stellar mass (M$_{\star}$) and SFR `main sequence' of the KDS galaxies, in combination with the derived physical properties of $2 < z < 3$ SFGs (based upon the `z\_best classification flag') from the 3D-HST survey \citep{Brammer2012,Momcheva2015}.
-We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-HST data described in \cite{Whitaker2014} and note that the KDS galaxies scatter consistently above and below these lines, suggesting that they are mostly regular SFGs in the process of converting their gas into stars (i.e.
+To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ must be observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and abundance measurements.
+To this end we decided to observe the SSA22 galaxies with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
+This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the spatially resolved metallicities reserved for a future work, and so we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the K-band spectral window.
+
+We prepare each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
+For the four pointings described above and summarised in table \ref{tab:pointings}, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
+This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}.
+
+The observations were carried out during ESO observing periods P92-P95 using Guaranteed Time Observations (Programme IDs: xxx xxx xxx)
+The seeing conditions were excellent for GOODS-S-P1 and GOODS-S-P2 with median K-band seeing of $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
+We observed 19-21 targets in each field (\ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92 observing semester and our requirement to observe at least one control star throughout an Observing Block (OB).
+
+\subsubsection{Data reduction}\label{subsubsec:datareduction}
+The data reduction process relied heavily upon the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
+In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.
+
+The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
+Readout channel bias is addressed using the `LCAL\_XXX.fits' calibration product to identify pixels which are not illuminated during exposures.
+The median values of these pixels are used to correct for varying flux baselines between each 64 pixel wide detector readout column, which if left uncorrected leads to flux bandings over the spatial extent of the reduced cubes.
+Standard star observations are processed to provide a flux calibration for each detector, which is necessary to account for varying sensitivity across the three independent KMOS modules. 
+Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
+Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsub:Obs} which boosts the effective spatial resolution of the observations.
+
+Sky subtraction is enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
+Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general we that the use of the SKYTWEAK option in the K-band greatly reduces the sky-line residuals.
+
+Variations in sky-subtraction quality are monitored over the course of the OBs which constitute the final stacks, as we find that the sky-subtraction performance becomes poorer as the telescope pointing approaches the zenith.
+This is due to the telescope tracking faster whilst looking through very low airmasses, hence scanning more rapidly over regions of sky with spatially and temporally varying OH emission.
+In addition to this we monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged K-band seeing rises above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
+The telescope tends to drift from its acquired position over the course of an OB, and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
+As part of this analysis, we tested whether the drift varies across the three KMOS detectors, finding typically that the difference is negligible, suggesting that it is not necessary to sacrifice more than a single IFU for tracking purposes.
+
+We stack all 300s exposures for each galaxy which pass the sky-subtraction and seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
+We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
+To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux, and then subtracted from each spaxel in turn.
+This assumes that there is no spatial variation in the required correction, which we have found to be valid for our current sample of galaxies.
+
+The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the integrated galaxy spectrum, N$_{[O~{\sc III}]_{Det}}$, the number with spatially resolved [O~{\sc III}]$\lambda$5007 emission, N$_{[O~{\sc III}]_{Res}}$ (see \cref{sec:extracting_properties}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+\footnote{We note that in GOODS-S-P2 we later found that the redshifts for two of our targets were $z < 0.5$ and we omit these from all columns in table \ref{tab:pointings}.}
+
+\begin{table*}
+\centering
+\begin{threeparttable}
+\caption{Summary of KDS pointing statistics}
+\label{tab:pointings}
+\begin{tabular}{c c c c c c c c c c c c c}
+
+ \hline
+Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band(s) & Exp. Time (ks) & Seeing ($^{\prime\prime}$)  \\
+ \hline
+ GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & 2 & 17 & K, H & 32.4 & 0.50 \\
+GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 19 & K, H & 31.8 & 0.52 \\
+SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & 1 & 9 & HK & 27.8 & 0.57 \\
+SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 10 & 46 & 8 & 80 & HK & 38.1 & 0.62 \\
+ \hline
+\end{tabular}
+\begin{tablenotes}
+      \small
+      \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
+    \end{tablenotes}
+  \end{threeparttable}
+  \end{table*}
+
+\subsection{Stellar masses and SFRs}\label{subsec:stellar_masses_and_sfrs}
+The wealth of ancillary data in both fields allows for a consistent treatment of the SED modelling, providing physical properties which are directly comparable between the cluster and field environments.
+These derived properties are considered in the context of the galaxy main sequence, to verify that the KDS sample contains typical SFGs at $z\sim3.5$.
+
+\subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
+We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS.
+During the SED modelling we assume solar metallicity stellar templates, and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
+We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
+The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
+
+In Figure \ref{fig:main_sequence} we plot the stellar mass (M$_{\star}$) and SFR `main sequence' of the KDS galaxies, in combination with the derived physical properties of $\sim 10,000$ $2.5 < z < 3.5$ SFGs (based upon the `z\_best classification flag') from the 3D-HST survey \citep{Brammer2012,Momcheva2016}.
+We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-HST data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the MS relation described in \cite{Speagle2014}: $logSFR(M_{\star}, t) = (0.84 - 0.026 \times t)logM_{\star} - (6.51 - 0.11 \times t)$, evaluated at $z\sim3.5$ where the age of the universe is 1.823Gyr, with the green line.
+The difference in position of these relations highlights the MS evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
+The KDS galaxies scatter, within the errors, consistently above and below these lines, suggesting that they are mostly regular SFGs in the process of converting their gas into stars (i.e.
 they are not especially bursty, or devoid of star formation).
@@
 \includegraphics[width=0.49\textwidth]{main_sequence.png}
-\caption{We plot the location of the KDS galaxies across the four pointings on the star forming `main sequence', with filled symbols showing galaxies detected in the [OIII]$\lambda$5007 emission line galaxies and open symbols those in which no detection has been made.
-Also plotted with the small grey points are individual SFGs from the 3D-HST survey at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
-The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in Whitaker+14.
-The KDS galaxies scatter evenly above and below, suggesting that these are typical SFGs which sample the main sequence of star formation between 9.5 $< log(M_{\star}[M_{\odot}]) <$ 10.5 and have mean $log(M_{\star}[M_{\odot}]) = 10.0$.
-There appears to be no connection between main sequence position and likelihood of detection, where we might have expected it would be harder to detect ionised emission in fainter galaxies that are either below the MS or with low $log(M_{\star}[M_{\odot}])$.
-There are fewer KDS galaxies represented on this plot than observed, due to our inability to constrain SFRs for 29/40 galaxies observed in SSA22 as a result of shorter wavelength baseline and shallower ancillary photometry.
+\caption{We plot the location of the KDS galaxies across the four pointings on the star forming `main sequence', with filled symbols showing galaxies detected in the [O~{\sc III}]$\lambda$5007 emission line galaxies and open symbols those in which no detection has been made.
+Also plotted with the small grey points are individual SFGs from the 3D-HST survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
+The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
+We include the MS relation described in \protect\cite{Speagle2014}: $logSFR(M_{\star}, t) = (0.84 - 0.026 \times t)logM_{\star} - (6.51 - 0.11 \times t)$, evaluated at $z\sim3.5$ where the age of the universe is 1.823Gyr, with the green line.
+Given the errors associated with the computed SFRs and M$_{\star}$ values, the KDS galaxies scatter evenly above and below the plotted relations, suggesting that these are typical SFGs which sample the main sequence of star formation between 9.5 $< log(M_{\star}[M_{\odot}]) <$ 10.5 and have mean $log(M_{\star}[M_{\odot}]) = 10.0$.
+29 of the SSA22 targets do not have SFR measurements due to limited photometry and are not plotted here.
 For these galaxies it is still possible to derive an $M_{\star}$ value and we note that the distribution is consistent with the galaxies plotted in this figure.}
@@
 \end{figure}
-\subsection{Data reduction techniques}\label{subsec:datareduction}
-The data reduction process relied heavily upon the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
-In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.
-
-The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
-The four pixel wide gaps between the IFU lenslets in the raw data are then used to correct for readout channel bias across each detector, which if left uncorrected leads to flux bandings over the spatial extent of the reduced cubes.
-Standard star observations are processed to provide a flux calibration for each detector, which is necessary to account for varying sensitivity across the three independent KMOS modules. 
-Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
-Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsub:Obs} which boosts the effective spatial resolution of the observations.
-Sky subtraction is enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
-Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general we find the quality of the sky-subtraction in the K-band to be excellent.
-% could insert figure to demonstrate
-Variations in sky-subtraction quality are monitored over the course of the OBs which constitute the final stacks, as we find that the sky-subtraction performance becomes poorer as the telescope pointing approaches the zenith.
-This is due to the telescope tracking faster whilst looking through very low airmasses, hence scanning more rapidly over regions of sky with spatially and temporally varying OH emission.
-In addition to this we monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames with unacceptable seeing and to measure the spatial shifts required for the final stack more precisely.
-The telescope tends to drift from its acquired position over the course of an OB, and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
-% insert figure here monitoring drift as function of time?
-Ask Michele here about level of detail
-As part of this analysis, we tested whether the drift varies across the three KMOS detectors, finding typically that the difference is negligible, suggesting that it is not necessary to sacrifice more than a single IFU for tracking purposes.
-
-We stack all 300s exposures for each galaxy which pass the sky-subtraction and seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
-The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [OIII]$\lambda$5007 detected across the stacked cubes from visual inspection using the QFitsView software \citep{Ott2012}, N$_{[OIII]_{Det}}$, the number with spatially resolved [OIII]$\lambda$5007 emission, N$_{[OIII]_{Res}}$ (see \cref{sec:extracting_properties}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
-We note that in goodsp2 we later found that the redshifts for two of our targets, lbg$\_$40 and lbg$\_$64 were $z < 0.5$ and removing these from consideration would raise the genuine detection percentage to $82\%$, and the resolved percentage to $65\%$ in GOODS-S-P2.
+
+\subsubsection{Sample summary}\label{subsubsec:sample_summary}
+We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey, and have derived $M_{\star}$ values for all, and SFRs for 64\% of the sample from SED modelling.
+Three KMOS pointings cover the field environment, and one pointing covers a cluster environment at the heart of the SSA22 protocluster.
+This paper presents the dynamical properties of the KDS \textit{field} sample, with the cluster sample showing a very high merger fraction (as listed in table \ref{tab:pointings} and discussed in \cref{subsec:morpho-kin-class}).
+We omit this cluster pointing, SSA22-CLUSTER, from the dynamical analysis presented in the following sections due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
+Abundance measurements for the KDS galaxies in both the field and cluster environments will be presented in a future work.
+
+\section{ANALYSIS}\label{sec:analysis}
 
@@
 \centering
-\caption{Summary of KDS pointing statistics}
-\label{tab:pointings}
-\begin{tabular}{c c c c c c c c c c c}
-
- \hline
-Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res. & Band(s) & Exp. Time (s) & Seeing ($^{\prime\prime}$)  \\
- \hline
- GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & K, H & 32400 & 0.5 \\
-GOODS-S-P2 & 03:32:35 & -27:43:15 & 19 & 14 & 74 & 11 & 58 & K, H & 31800 & 0.52 \\
-SSA22-a & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 10 & 46 & HK & 38100 & 0.62 \\
-SSA22-b & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & HK & 27800 & 0.57 \\
- \hline
-\end{tabular}
-\end{table*}
-
-\section{MAPPING PHYSICAL PROPERTIES}\label{sec:extracting_properties}
-\subsection{Spaxel Fitting}
-Having produced stacked and calibrated datacubes for each of the galaxies in the sample, we aim to extract 2-dimensional maps of the flux, velocity and velocity dispersion.
-These properties are extracted via modelling of the ionised gas emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
-We concentrate solely on the [OIII]$\lambda$5007 emission line which always has S/N higher than both [OIII]$\lambda$4959 and H$\beta$ and typically extends over a larger area of each IFU.
-Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn, within which we locate the systemic wavelength of the redshifted [OIII]$\lambda$5007 centre, $\lambda_{obs_{5007}}$, using the redshift value determined from fitting the [OIII]$\lambda$5007 line in the integrated galaxy spectrum.
-We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
-To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux, and then subtracted from each spaxel in turn.
-This assumes that there is no spatial variation in the required correction, which we have found to be valid for our current sample of galaxies.
-
-Following the subtraction of excess thermal noise, we search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
-This truncated spectrum is then used in the fitting procedure for each spaxel.
-The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by poor subtraction of the sky emission lines.
-A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the fitted parameters flux,$F_{g}$, central wavelength, $\lambda_{g}$, and standard deviation, $\sigma_{g}$.
-These parameters, along with the estimate of the noise in the datacube, are used to assess whether the fitting of the [OIII]$\lambda$5007 line is acceptable or not. 
-The noise in the cube is estimated in two different ways. 
-First, we take the root of the sum of the squares of the flux values in the noisecube in the same spaxel and across the same extraction region as is being considered in the datacube.
-The noisecube is produced as part of the reduction process, taking into account instrumental effects and the $\sqrt{N}$ noise reduction resulting from stacking many individual exposures.
-This is summarised by Equation~\ref{eq:cube_noise}, where $\sigma _{i}$ are the individual flux points in the noisecube and $N_{c}$ denotes noise estimated from the noisecube.
-
-\begin{equation}\label{eq:cube_noise}
-   N_{c} = \sum_{i}\sigma _{i}^{2}
-\end{equation}
-
-The second method uses the datacube to estimate the noise.
-All spaxels containing object flux are masked and the sum of the squares of the flux values in the spectral extraction region is computed for all remaining spaxels inwards of 3 spaxels from the cube border.
-This border constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
-The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation~\ref{eq:mask_noise} where $F_{i}$ are the flux values across the extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
-Both noise estimates are quantitatively similar and the conclusions of the following analysis are not dependent on the choice.
-As default we use the noise estimate from masking within the datacube to compute the S/N acceptance criteria within each spaxel.
-
-\begin{equation}\label{eq:mask_noise}
-    N_{m} = STD\big(\sum_{i}F_{i}^{2}\big)
-\end{equation}
-
-The signal in each spaxel is taken as the sum of the flux values across the extraction region, as shown in Equation~\ref{eq:signal} where S denotes the signal.
-
-\begin{equation}\label{eq:signal}
-    S = \sum_{i}F_{i}
-\end{equation}
-
-The criteria for accepting the fit within a given spaxel are as follows:
-
-\begin{enumerate}
-\item The uncertainties on any of the parameters of the gaussian fit must not exceed 30\%
-\item We must have $ 0.7 < \frac{F_{gauss}}{S} < 1.3 $, where $F_{gauss}$ is the flux from the gaussian fit to the [OIII]$\lambda$5007 line and S is the signal from \ref{eq:signal}.
-This criterion minimises the number of spaxels erroneously accepted due to the fitting of non-gaussian profiles and is important for `cleaning up' accepted spaxels in the 2D maps which are clearly independent of the main body of the galaxy.
-\item $\frac{S}{N} > 3$
-\end{enumerate}
-
-If all three criteria are satisfied, the spaxel is accepted and the gaussian fit is repeated 1000 times with each flux value in the extraction region perturbed by the datacube flux error.
-This error is computed as the median of the standard deviations in the extraction regions of the unmasked spaxels, as shown in Equation~\ref{eq:cube_error} with $F_{e}$ denoting the flux error.
-
-\begin{equation}\label{eq:cube_error}
-   F_{e} = \big<STD(F _{i})\big>
-\end{equation}
-
-This Monte Carlo procedure gives the fit parameters and associated errors for the accepted spaxels.
-The velocity is computed from the gaussian centre, $\lambda_{g}$, using Equation~\ref{eq:velocity_comp} and the velocity dispersion is computed from the gaussian width, $\sigma_{g}$, using Equation~\ref{eq:dispersion_comp}, where $v_{obs}$ and $\sigma_{obs}$ are the observed rotational velocity and velocity dispersion respectively and c is the speed of light.
-
-\begin{equation}\label{eq:velocity_comp}
-   v_{obs} = \frac{\lambda_{g} - (1 + z)\lambda_{5007}}{(1 + z)\lambda_{5007}} \times c
-\end{equation}
-
-\begin{equation}\label{eq:dispersion_comp}
-   \sigma_{obs} = \frac{\sigma_{g}}{(1 + z)\lambda_{5007}} \times c
-\end{equation}
-
-If a spaxel does not meet the criteria we follow the procedure described in \cite{Stott2016} and bin with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
-This is carried out by median stacking the extraction region spectra in each of the neighbouring spaxels.
-The criteria are then re-examined and if satisfied the Monte-Carlo procedure is carried out. 
-If the binned spaxels fail the criteria, one final iteration is carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$.
-If after the widest binning the criteria aren't satisfied, the value of the spaxel in the 2D maps is set to nan.
-Spaxels which pass the criteria after binning are represented as a single spaxel in the 2D maps, and so a smoothing of the fields are expected in the lowest S/N regions.
-
-The process is automated and applied to each of the KDS galaxies that have an [OIII]$\lambda$5007 detection across the face of the cube.
-Following the fitting procedure we decide whether the galaxy has spatially resolved [OIII]$\lambda$5007 emission or not, with this defined as being those galaxies where the spatial extent of the accepted spaxels in the [OIII]$\lambda$5007 flux map is equivalent to or greater than the seeing disk.
-For each pointing, this number is added to table \ref{tab:pointings}.
-We do not analyse further the galaxies which are not spatially resolved, due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
-The physical properties of all spatially resolved galaxies in both GOODS-S and SSA22 are listed in table \ref{tab:phys-props}.
-
-\begin{table*}
-\centering
 \begin{threeparttable}
-\caption{Physical properties}
+\caption{Physical properties of the KDS field galaxies as measured from SED fitting and from applying GALFIT \protect\citep{Peng2010_galfit}}
 \label{tab:phys-props}
@@
  \hline
-ID              & RA       & Dec       & z     & k     & M$_{\star}$ & SFR$_{SED}$ & $\frac{b}{a}$ & i$^{\circ}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(Kpc) \\
+ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}[M_{\odot}])$ & SFR$_{SED}$($M_{\odot}yr^{-1}$) & $A_{r}$ & i$^{\circ}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc) \\
  \hline
@@
  \hline
-n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.9637 & 9.94  & -            & 0.71        & 46.0        & 94.0    & 0.56      \\
 s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.4618 & 9.88  & -            & 0.39        & 70.0        & 125.0   & 1.78      \\
 n3\_009       & 22:17:28 & +00:12:12 & 3.069 & 99.0    & 8.72  & -            & 0.75        & 42.0        & 84.0    & 1.06      \\
+lab18         & 22:17:29 & +00:07:52 & 3.101           & 99.0    & 8.66  & -            & 0.85        & 32.0        & 27.0    & 0.46      \\
 s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.9103 & 9.74  & -            & 0.57        & 57.0        & 76.0    & 1.59      \\
+n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.9637 & 9.94  & -            & 0.71        & 46.0        & 94.0    & 0.56      \\
+s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.2538 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
 lab7\_top     & 22:17:41 & +00:11:28 & 3.095      & 23.8919 & 9.89  & -            & 0.51        & 61.0        & 139.0   & 1.47 \\
-s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.2538 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
-lab18         & 22:17:29 & +00:07:52 & 3.101           & 99.0    & 8.66  & -            & 0.85        & 32.0        & 27.0    & 0.46      \\
 $^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & 99.0    & 8.78  & -            & 0.57         & 57.3        & -    & 2.4      \\
@@
       \small
-      \item $^{*}$ No HST coverage: $PA_{morph}$ unconstrained; $\frac{b}{a}$ and $R_{1/2}$ estimated as derived throughout the text.
+      \item $^{*}$ No HST coverage: $PA_{morph}$ unconstrained; $A_{r}$ and $R_{1/2}$ estimated as explained throughout the text.
     \end{tablenotes}
@@
 
-\subsection{Deriving Morphological Properties}
-For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from HST high resolution photometry where available.
-This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies but also to help distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
-In the following section we describe the approach we have chosen to recover these parameters.
+\subsection{Morphological Measurements}
+For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high resolution photometry.
+This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies and helps to distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
+In the following sections we describe the approach we have chosen to recover these parameters.
+In section \cref{subsubsection:morph_param_summary} we compare the KDS morphological parameters with those described in \cite{VanderWel2012}, and also with spectroscopically confirmed galaxies in different redshift intervals in order to study the size evolution of SFGs across cosmic time.
 
 \subsubsection{Applying GALFIT to the imaging data}\label{subsubsec:galfitting}
-We use GALFIT \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the system PSF, to the observed HST images in both GOODS-S and SSA22 in a consistent way.
+We use GALFIT \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed HST images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
 The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z \sim 3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\tiny{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}}.
 For SSA22 we make use of archival HST imaging\footnote{\tiny{\url{https://archive.stsci.edu/hst/search.php}}} data in the WFC3 F160W band (P.I.
-Lehmer: PID 13844, P.I.
+Lehmer: PID 13844; P.I.
 Mannucci: PID 11735) and the ACS F814W band, tracing $\sim$ 2000$\AA$ light at $z\sim 3.5$ (P.I.
-Chapman: PID 10405, P.I.
-Abraham: PID 9760, P.I.
+Chapman: PID 10405; P.I.
+Abraham: PID 9760; P.I.
 Siana: PID 12527).
 The HST coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is incomplete, and so we must resort to the bluer ACS F814W data which traces younger stellar populations and may not be sensitive to the majority of the mass distribution within these galaxies.
-Both of these limitations translate to larger systematic uncertainties in the morphological parameters derived in the SSA22 pointings.
 
 We first run SExtractor \citep{Bertin1996} across the full fields to recover initial input parameters and segmentation maps for running GALFIT, and then extract postage stamp regions around the galaxies in the KDS sample.
-At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles with the \Sers index n fixed to the exponential disk value of 1.
-During the fitting process all other morphological parameters, including $R_{1/2}$, (xcen,ycen), PA and inclination, are free to vary.
-This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, n = 4 models and bulge/disk models with both an n=1 and n=4 component following the procedure described in \cite{Bruce2012}.
-We find that the $\chi^{2}$ of the fixed n = 1 fit is quantitatively similar in most cases and we also find good agreement between the morphological parameters reported in the \cite{VanderWel2012} structural properties catalogue.
-The use of exponential profiles also facilitates comparison with recent results from the KROSS survey \citep{Harrison2017} in which beam smearing correction factors are applied to the derived kinematic parameters as function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:param_extraction}).
+At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
+During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.
+This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012} (with the median ratio of $\chi ^{2}$ values equal unity in all cases).
+Additionally, for the corresponding objects in the \cite{VanderWel2012} catalogue the median \Sers index value is 1.2.
+The use of exponential profiles also facilitates comparison with recent large surveys such as KROSS \citep{Harrison2017}, in which beam smearing correction factors are applied to the derived kinematic parameters as function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:param_extraction}), and KMOS$^{3D}$ \citep{Wisnioski2015}.
+
 In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012}, which has been shown to produce more reliable results than either the Tiny Tim model or an empirical stack alone.
@@
 
-This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{sec:Kinematic_Properties}, namely the axis ratio $A_{r}$, half-light radius $R_{1/2}$ and the $PA_{morph}$ $PA_{morph}$.
+This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{sec:Kinematic_Properties}, namely the axis ratio $A_{r}$, half-light radius $R_{1/2}$ and the $PA_{morph}$.
+The errorbars produced by GALFIT are purely statistical and are determined from the covariance matrix used in the fitting, and this results in unrealistically small uncertainties in the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
+Throughout the following subsections we discuss adopted errors on each of the morphological parameters.
+
+\subsubsection{Inclination angle}\label{subsubsection:inclination_angle}
 We used the derived $A_{r}$ values to determine galaxy inclination angles.
 As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a} \equiv A_{r}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
-To derive the inclination, we must select a value for $q_{0}$, and following the discussion in \citep{Law2012a} we choose a value appropriate for thick disks, $q_{0} = 0.2$ (e.g.
-\cite{Epinat2012,Harrison2017}).
-However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values.
+To derive the inclination, we must select a value for $q_{0}$, and following the discussion in \citep{Law2012a} we choose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
+However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values, with the difference $<10\%$ in the case of the KDS galaxies.
 
@@
 The inclination angle calculated for each galaxy is used to correct the observed velocity field, which is the line of sight component of the intrinsic velocity field, with the correction factor increasing with increasing $A_{r}$.
-
-The second GALFIT parameter is $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
-This is expected to coincide with the kinematic position axis, $PA_{kin}$, in the case of a rotating disk galaxy, where the stars and the gas are both rotating around the centre of the gravitational potential well.
-Discrepancy between $PA_{morph}$ and $PA_{kin}$ is an important indicator of sub-structure in the morphology \citep{Queyrel2012,Wisnioski2015,Rodrigues2016}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
-The discrepancy, often labelled $Delta PA \equiv |PA_{morph} - PA_{kin}|$, is a function of $A_{r}$, as it becomes increasingly difficult to accurately measure $PA_{morph}$ for very inclined galaxies \citep[e.g.]{Wisnioski2015,Harrison2017}.
-We have visually inspected each of the GALFIT maps to check that the derived $PA_{morph}$ follows the galaxy light distribution, and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class}).
-
-The third morphological parameter is the half-light radius, $R_{1/2}$, which provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
-As discussed throughout the introduction and in \cref{subsubsec:param_extraction}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
-Connected to this is the issue of extrapolating model rotation curves or two-dimensional rotation maps beyond the last measured datapoints, which may not extend to the rotation curve plateau due to poor S/N in these regions.
-Knowledge of $R_{1/2}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made.
-Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d modelling}), which requires knowledge of the $R_{1/2}$ value for each galaxy.
-A final use of the derived $R_{1/2}$ values is to verify our beam smearing correction results through comparison with systematic correction factors presented in Johnson et al.
-(in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:param_extraction}).
-As a result of choosing consistent $V_{C}$ extraction radii and beam smearing analysis methods, we may ultimately compare the KDS sample consistently with the large KROSS sample results at $z \sim 0.9$ described in \citep{Harrison2017}.
-
-The errorbars produced by GALFIT are purely statistical and are determined from the covariance matrix used in the fitting, and this results in unrealistically small uncertainties in the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
-\cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in CANDELS, reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
-We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ recovered from extracting at $R_{1/2}$ and the errors on the intrinsic velocity dispersion, $\sigma_{int}$, the derivation of which requires knowledge of $R_{1/2}$ (\cref{subsec:3d modelling}) are dominated by measurement errors and uncertainties connected with assumptions about the velocity dispersion distribution in high redshift galaxies (see \cref{app:kin_error_estimates}).
 
@@
 We also note that generally this inclination uncertainty is a function of the recovered axis ratio, since it is more difficult to determine the inclination when the galaxy is more `face-on', but detailed inclination angle uncertainty modelling is beyond the scope of this paper.
+
+\subsubsection{Position angle}\label{subsubsection:position_angle}
+The second GALFIT parameter is $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
+This is expected to coincide with the kinematic position axis, $PA_{kin}$, in the case of a rotating disk galaxy, where the stars and the gas are both rotating around the centre of the gravitational potential well.
+Discrepancy between $PA_{morph}$ and $PA_{kin}$ is an important indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2016}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
+The discrepancy, often labelled $\Delta PA \equiv |PA_{morph} - PA_{kin}|$, is a function of $A_{r}$, as it becomes increasingly difficult to accurately measure $PA_{morph}$ for very inclined galaxies \citep[e.g.][]{Wisnioski2015,Harrison2017}.
+We have visually inspected each of the GALFIT maps to check that the derived $PA_{morph}$ follows the galaxy light distribution, and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class}).
+
 $PA_{morph}$ is well constrained by the fits at small axis ratios, but becomes increasingly uncertain as the galaxy morphology becomes closer to spherical.
-In Figure \ref{fig:delta_pa} we draw attention to this by showing the absolute difference between morphological and kinematic position angles, $\Delta PA$, plotted against the galfit determined axis ratio, with binned median and standard deviation also shown.
 We note that typically the $PA_{morph}$ uncertainties are large in the regime of high axis ratios, but make no attempt to quote a formal uncertainty on this parameter.
 
+\subsubsection{Half-light radii}\label{subsubsection:half-light_radii}
+The third morphological parameter is the half-light radius, $R_{1/2}$, which provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
+As discussed throughout the introduction and in \cref{subsubsec:param_extraction}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
+Knowledge of $R_{1/2}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made, both of which are important when making comparisons to previous IFU studies \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
+Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d modelling}), which requires the $R_{1/2}$ value for each galaxy.
+A final use of the derived $R_{1/2}$ values is to verify our beam smearing correction results through comparison with systematic correction factors presented in Johnson et al.
+(in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:param_extraction}).
+
+\cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in CANDELS, reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
+We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ recovered from extracting at $R_{1/2}$ and the errors on the intrinsic velocity dispersion, $\sigma_{int}$, the derivation of which requires knowledge of $R_{1/2}$ (\cref{subsec:3d modelling}) are dominated by measurement errors and uncertainties connected with assumptions about the velocity dispersion distribution in high redshift galaxies (see \cref{app:kin_error_estimates}).
+
+\subsubsection{Lack of HST Coverage}\label{subsubsection:lack_of_hst}
 In SSA22, 4/21 of the spatially resolved galaxies do not have any HST coverage.
-For these galaxies the inclination angle is set to the theoretical mean of 57.3$^{\circ}$, calculated for a population of galaxies with randomly drawn viewing angles (see e.g.
-the appendix in \cite{Law2009}), we fix $PA_{morph}$ equal to $PA_{kin}$ for the analysis described in \cref{subsec:3d modelling} and fix the $R_{1/2}$ value for these galaxies equal to FWHM$_{obs}$/2.
-These assumptions are based purely on statistical considerations, and the errorbars on the derived quantities for these galaxies are consequently larger.
+For these galaxies the inclination angle is set to the theoretical mean of 57.3$^{\circ}$ calculated for a population of galaxies with randomly drawn viewing angles (see e.g.
+the appendix in \cite{Law2009}).
+This value is in good agreement with the KDS sample median of 57.4$^{\circ}$, see \cref{subsubsection:morph_param_summary}), and for the inclination uncertainty we use the standard deviation of the KDS inclinations, 12.4$^{\circ}$.
+This corresponds to a factor $\sim1.3$ uncertainty in the derived velocities for these galaxies.
+We fix $PA_{morph}$ equal to $PA_{kin}$ for the analysis described in \cref{subsec:3d modelling} and to measure $R_{1/2}$ we first fit the continuum light in the median stacked HK datacubes with a exponential profile, and subtract the PSF from the recovered $R_{1/2}$ value.
+For these galaxies we also adopt a nominal $R_{1/2}$ error of 10$\%$ following the description above, and note that the derived $V_{C}$ values are not sensitive to the precise $R_{1/2}$ values, since we measure at $2R_{1/2}$ where the rotation curves have already flattened.
 Owing to the small number of galaxies without HST imaging, we do not expect this to impact the bulk dynamical properties of the KDS sample.
+
+\subsubsection{Morphological parameter summary}\label{subsubsection:morph_param_summary}
 
@@
     \end{subfigure}
-    \caption{We crossmatch publicly available spectroscopic redshifts for SFGs, as discussed in the text, with the morphological catalogue presented in VDW12 in two different redshift slices.
+    \caption{We crossmatch publicly available spectroscopic redshifts for SFGs, as discussed in the text, with the morphological catalogue presented in \protect\cite{VanderWel2012} in two different redshift slices.
     This provides a set of reference morphological properties for typical SFGs at different evolutionary stages to which the derived KDS values can be compared.
@@
 
-In Figure \ref{fig:morpho-distributions} we plot the distributions of the derived morphological properties (for only the KDS galaxies with HST coverage) in comparison to those determined in \cite{VanderWel2012} (VDW12) at low and high redshift.
+Having derived $R_{1/2}$, $A_{r}$ and $PA_{morph}$ for each of the KDS field galaxies \ref{fig:morpho-distributions} we plot the distributions of these properties, using KDS galaxies with HST coverage, along with distributions of morphological parameters determined in \cite{VanderWel2012} at low and high redshift.
+The KDS galaxies have been identified in the \cite{VanderWel2012} catalogue and the morphological properties show excellent agreement, with median $\Delta A_{r} = 0.0002$, median $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\sim3.5$) and the median \cite{VanderWel2012} $n = 1.2$ value for the KDS values close to our adopted n = 1 exponential disk fits.
+
 At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with the morphological catalogue of \cite{VanderWel2012}.
@@
 The derived KDS $R_{1/2}$ distribution at $z \sim 3.5$ is similar to the wider sample distribution at $3 < z  < 4$, i.e.
-compact when compared to galaxies at lower redshifts and the KDS $A_{r}$ are consistent with being generally uniform between $0.3 < A_{r} < 0.9$, with the peak at $A_{r} = 0.6$ corresponding to i = 55$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$, which is close to the statistical mean for a random galaxy sample.
+compact when compared to galaxies at lower redshifts and the KDS $A_{r}$ are consistent with being generally uniform between $0.3 < A_{r} < 0.9$, with median value of 0.57, corresponding to i = 57.4$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$, which is close to the statistical mean for a random galaxy sample.
 This reassures us that we are not biased towards deriving either particularly low or particularly high inclination angles.
 
-\subsubsection{Morpho-Kinematic Classification}\label{subsec:morpho-kin-class}
+\subsection{Kinematic Measurements}\label{subsection:kinematic_measurements}
+
+We proceed now to extract 2D measurements from the KDS datacubes by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
+We then describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam smearing corrections for each galaxy.
+
+\subsubsection{Spaxel Fitting}\label{subsubsection:spaxel_fitting}
+Having produced stacked and calibrated datacubes for each of the 77 galaxies in the full KDS sample, we aim to extract 2-dimensional maps of the flux, velocity and velocity dispersion.
+These properties are extracted via modelling of the ionised gas emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
+We concentrate solely on the [O~{\sc III}]$\lambda$5007 emission line which always has S/N higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and typically extends over a larger area of each IFU.
+Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn, within which we locate the systemic wavelength of the redshifted [O~{\sc III}]$\lambda$5007 centre, $\lambda_{obs_{5007}}$, using the redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum.
+
+We search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
+This truncated spectrum is then used in the fitting procedure for each spaxel.
+The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by poor subtraction of the sky emission lines.
+A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
+These parameters, along with the estimate of the noise in the datacube, are used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not. 
+The noise is estimated by masking all datacube spaxels containing object flux and computing the sum of the squares of the flux values in the spectral extraction region for all remaining spaxels inwards of 0.3$^{\prime\prime}$ from the cube boundary.
+This boundary constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
+The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation~\ref{eq:mask_noise} where $F_{i}$ are the flux values across the extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
+
+\begin{equation}\label{eq:noise}
+    N_{m} = STD\left(\sum_{i}F_{i}^{2}\right)
+\end{equation}
+
+The signal in each spaxel is taken as the sum of the flux values across the extraction region, as shown in Equation~\ref{eq:signal} where S denotes the signal.
+
+\begin{equation}\label{eq:signal}
+    S = \sum_{i}F_{i}
+\end{equation}
+
+The criteria for accepting the fit within a given spaxel are as follows:
+
+\begin{enumerate}
+\item The uncertainties on any of the parameters of the gaussian fit must not exceed 30\%
+\item $\frac{S}{N} > 3$
+\end{enumerate}
+
+We impose a further criterion to help remove fits to spectral features unrelated to the galaxy (e.g.
+fits to skyline residuals), which is important for `cleaning up' accepted spaxels in the 2D maps which are clearly independent of the main body of the galaxy.
+For this test we subtract the galaxy continuum and impose that the $0.7 < F_{g}/{S} < 1.3$, where $F_{g}$ is the flux from the gaussian fit to the [O~{\sc III}]$\lambda$5007 line and S is the signal in the extraction region from equation \ref{eq:signal}.
+
+If all three criteria are satisfied, the spaxel is accepted and the gaussian fit is repeated 1000 times with each flux value in the extraction region perturbed by the datacube flux error.
+This error is computed as the median of the standard deviations in the extraction regions of the unmasked spaxels, as shown in equation \ref{eq:cube_error} with $F_{e}$ denoting the flux error.
+
+\begin{equation}\label{eq:cube_error}
+   F_{e} = \big<STD(F _{i})\big>
+\end{equation}
+
+This Monte Carlo procedure gives the fit parameters and associated errors for the accepted spaxels.
+The velocity is computed from the gaussian centre, $\lambda_{g}$, using Equation~\ref{eq:velocity_comp} and the velocity dispersion is computed from the gaussian width, $\sigma_{g}$, using Equation~\ref{eq:dispersion_comp}, where $v_{obs}$ and $\sigma_{obs}$ are the observed rotational velocity and velocity dispersion respectively, c is the speed of light and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
+
+\begin{equation}\label{eq:velocity_comp}
+   v_{obs} = \frac{\lambda_{g} - (1 + z)\lambda_{5007}}{(1 + z)\lambda_{5007}} \times c
+\end{equation}
+
+\begin{equation}\label{eq:dispersion_comp}
+   \sigma_{obs} = \frac{\sigma_{g}}{(1 + z)\lambda_{5007}} \times c
+\end{equation}
+
+If a spaxel does not meet the criteria we follow the procedure described in \cite{Stott2016} and bin with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
+This is carried out by median stacking the extraction region spectra in each of the neighbouring spaxels.
+The criteria are then re-examined and if satisfied the Monte-Carlo procedure is carried out. 
+If the binned spaxels fail the criteria, one final iteration is carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$, roughly equivalent to the size of the seeing disk.
+If after the widest binning the criteria aren't satisfied, no value is assigned to that spaxel.
+
+The process is automated and applied to each of the KDS galaxies that have an [O~{\sc III}]$\lambda$5007 detection.
+Following the fitting procedure the galaxies are clasified as spatially resolved in [O~{\sc III}]$\lambda$5007 emission or not, with this defined as  the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map equivalent to or greater than the seeing disk.
+For each pointing, the number of resolved galaxies, $N_{res}$, is added to table \ref{tab:pointings}.
+29\% of the detected KDS galaxies are not spatially resolved, and we do not analyse these further, despite several showing velocity gradients within the seeing disk, due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
+The physical properties of all spatially resolved galaxies in both GOODS-S and SSA22 are listed in table \ref{tab:phys-props}.
+
+\subsubsection{3D modelling and beam smearing corrections}\label{subsec:3d_modelling}
+
+As mentioned in the introduction, there is no universal standard for defining $V_{C}$ and $\sigma_{int}$, particularly when it is extrapolated from the data using a fitted model, of which there are several types.
+Physically motivated models take into account the potential-well of the galaxy through knowledge of the mass distribution \citep[e.g.][]{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015}.
+Phenomenological models assume a fixed function known to well describe observed galactic rotation curves which flatten at large radii \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Harrison2017}.
+Both of the above examples fit to 2D fields extracted from the datacubes using line-fitting software.
+Recently, algorithms such as Galpak$^{3D}$ \citep{Bouche2015} and 3D-Barolo \citep{DiTeodoro2015} have emerged, fitting directly to the flux in the datacube in order to constrain the kinematic properties.
+
+In this analysis we minimise the number of fitted parameters by making use of information from HST imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.
+We seek also to clearly distinguish between observed velocities and those inferred from modelling.
+This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.
+There are thus two clear reasons for constructing model velocity fields; the first is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the second is to estimate the effect of beam smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
+The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.
+
+\subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
+For each galaxy with spatially resolved [O~{\sc III}]$\lambda$5007 emission, we construct a model datacube with the same spatial dimensions as the observed datacube, and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined by the systemic velocity of the galaxy.
+This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
+Following the procedure now of numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe:
+
+\begin{equation}\label{eq:arctangent}
+   v_{r} = \frac{2}{\pi}v_{asym}arctan\left(\frac{r}{r_{t}}\right)
+\end{equation}
+
+\noindent
+with `r' measured as the distance from the centre of rotation, (xcen, ycen).
+This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
+The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
+If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam smearing.
+The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
+In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
+The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in section \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
+This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.
+
+This simulated intrinsic [O~{\sc III}]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries, with the atmospheric seeing profile determined from fitting the collapsed, stacked standard star cube in each pointing with an elliptical gaussian (the recovered seeing values are reported in table \ref{tab:pointings}).
+The velocity and velocity dispersion values are then re-measured in each spaxel to produced `beam-smeared' 2D maps of the kinematic parameters.
+
+We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, and seek the combination of parameters which maximises the log-Likelihood function given by equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
+
+\begin{equation}\label{eq:likelihood}
+   ln\Lagr = \frac{-0.5\sum_{i=1}^{N}(d_{i} - M_{i})^{2}}{\delta_{v_{i}}^{2}} - ln\left(\frac{1}{\delta_{v_{i}}^{2}}\right)
+\end{equation}
+
+\noindent
+where $\delta_{v_{i}}$ are the observed velocity errors, $d_{i}$ are the datapoints and $M_{i}$ are the convolved model velocity values.
+In practice we fix the (xcen,ycen) parameters of the galaxy to the location of the stellar continuum, a proxy for the centre of the gravitational potential well, recovered from the collapsed KMOS cube, leaving only 3 free parameters to vary in the MCMC sampling.
+This assumes that the gas and the stars in the galaxy share a common centre of mass, an assumption which is verified for the vast majority of SFGs in the local and intermediate redshift universe.
+Due to the faintness of the continuum, there are several galaxies for which we cannot reliably estimate the rotation centre using this method, and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location.
+Using the continuum to fix the rotation centre is generally more successful for the SSA22 galaxies, since the use of the HK filter effectively doubles the S/N of this component by collapsing over two wavebands.
+This differs from the method of fixing the rotation centre at the midpoint between the velocity extrema, described in \cite{Wisnioski2015} and \cite{Rodrigues2016}.
+In general the S/N of our sample is low at the galaxy outskirts and for many of the isolated rotating sample we don't observe the flattening of the velocity field.
+This suggests that the velocity midpoint may be biased towards the side of the galaxy which shows the higher velocity value and so we instead use the physically motivated continuum centre where possible, which also matches the approach described in \cite{Harrison2017}.
+
+The MCMC sampling provides a distribution of parameter values around those which give the maximum likelihood.
+We have confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates have converged around the 50th percentile values.
+The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in \cref{appsubsec:model_errors}.
+
+Following the construction of a convolved cube and the measurement of the beam-smeared maps we can extract beam smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
+There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
+We provide an overview of these surveys in section \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of the parameters used for comparison to the KDS throughout results section \cref{subsec:redshift_evolution}).
+
+\subsubsection{KDS beam smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
+We extract $V_{smeared}$ and $V_{C}$ by reading off from the beam-smeared and intrinsic best fitting 2D model grids respectively at $2R_{1/2}$.
+The $R_{1/2}$ value used to extract velocities from the KMOS data is found by convolving the intrinsic $R_{1/2}$ value with the PSF of the observations.
+The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
+The beam smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
+The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in section \cref{subsubsec:observed_and_intrinsic}.
+The $V_{C}$ errors are discussed in \cref{appsubsubsec:model_errors}.
+
+In most of the KDS field sample galaxies, the $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, with 2 galaxies requiring extrapolation > 0.4$^{\prime\prime}$ with a mean extrapolation of 0.17$^{\prime\prime}$.
+This extrapolation is a requirement imposed by the low S/N at the outskirts of the KDS galaxies, limiting the extent to which the ionised gas disk can be observed, with the majority of the observed velocity curves not reaching the point of flattening.
+The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radius marked on each velocity thumbnail.
+We present the maximum observed velocity values, $V_{obs}$, and the intrinsic, inclination and beam smearing corrected model velocity values, $V_{C}$, in table \ref{tab:kin_props}.
+
+\subsubsection{KDS beam smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
+Convolution of the model velocity field with the seeing profile produces a peak in the beam-smeared velocity dispersion map at the centre of rotation.
+The model therefore provides a beam smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the beam-smeared dispersion i.e.
+$\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
+This is computed for each spaxel to provide the 2D $\sigma_{bs}$ correction map.
+The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in section \cref{appsubsubsec:model_errors}.
+We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.
+
+To measure the $\sigma_{int}$ value for each galaxy in our sample we first use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the K-band and 55.4kms$^{-1}$ in the HK-band).
+This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam smearing correction best recovers the $\sigma_{int}$ values.
+
+\begin{equation}\label{eq:owen_sigma}
+   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{bs} \right)^{2} - \sigma_{inst}^{2}}
+\end{equation}
+
+The median value of this map is taken as the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value, with both of these presented in table \ref{tab:kin_props}.
+
+The beam smearing correction factor is then given by the ratio of these two medians, i.e.
+$\sigma_{obs}/\sigma_{int}$, with mean and median values of 0.77 and 0.79 respectively for the morphologically isolated KDS galaxies.
+
+To test the robustness of our beam smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{d}/R_{psf}$, detailed in Johnson et al.
+(in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
+These correction factors are applied to $V_{smeared}$ to reach $V_{C}$ and to $\sigma_{obs}$ to reach $\sigma_{int}$.
+The $V_{C}$ values agree to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities. 
+This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.
+
+\begin{table*}
+\centering
+\begin{threeparttable}
+\caption{Dynamical Properties}
+\label{tab:kin_props}
+\begin{tabular}{cccccccc}
+
+ \hline
+ID & $V_{obs}$(kms$^{-1}$) & $V_{C}$(kms$^{-1}$) & $\sigma_{obs}$(kms$^{-1}$) & $\sigma_{int}$(kms$^{-1}$) & $V_{C}/\sigma_{int}$ & $R_{1/2}$(kpc) & PA$_{kin}^{\circ}$ \\
+ \hline
+ GOODS-S & & & & & & & \\
+ \hline
+bs009818        & 65.0                    & 84.0                     & 95.0                  & 79.0                   & 1.06       & 1.25        & 72.0 \\
+bs014828        & 32.0                    & 46.0                     & 97.0                  & 88.0                   & 0.53       & 1.65      & 44.0   \\
+lbg\_20         & 26.0                    & 56.0                     & 55.0                  & 40.0                   & 1.39      & 1.30        & 41.0  \\
+lbg\_105        & 13.0                    & 32.0                     & 68.0                  & 59.0                   & 0.54       & 1.75       & 170.0 \\
+bs006541        & 36.0                    & 65.0                     & 96.0                  & 83.0                   & 0.78        & 1.85       & 23.0 \\
+b012141\_012208 & 34.0                    & 93.0                     & 94.0                  & 63.0                   & 1.47       & 1.60       & 122.0 \\
+b15573          & 62.0                    & 81.0                     & 111.0                 & 84.0                   & 0.97        & 0.50       & 118.0 \\
+bs008543        & 77.0                    & 111.0                    & 98.0                  & 71.0                   & 1.56       & 1.60       & 114.0 \\
+bs006516        & 56.0                    & 61.0                     & 64.0                  & 45.0                   & 1.35      & 1.95       & 144.0  \\
+bs016759        & 71.0                    & 110.0                    & 82.0                  & 57.0                   & 1.93        & 0.90       & 75.0 \\
+lbg\_111        & 53.0                    & 58.0                     & 90.0                  & 81.0                   & 0.71      & 0.65        & 168.0 \\
+lbg\_38         & 31.0                    & 97.0                     & 76.0                  & 53.0                   & 1.82        & 0.95       & 47.0 \\
+lbg\_94         & 18.0                    & 34.0                     & 65.0                  & 55.0                   & 0.62       & 1.20       & 41.0 \\
+lbg\_109        & 32.0                    & 53.0                     & 101.0                 & 91.0                   & 0.58      & 2.00        & 157.0 \\
+lbg\_24         & 30.0                    & 42.0                     & 64.0                  & 51.0                   & 0.82      & 1.30       & 64.0  \\
+lbg\_25         & 14.0                    & 33.0                     & 53.0                  & 41.0                   & 0.8       & 1.20        & 87.0  \\
+lbg\_32         & 79.0                    & 121.0                    & 104.0                 & 76.0                   & 1.58       & 1.90       & 11.0  \\
+lbg\_91         & 58.0                    & 91.0                     & 98.0                  & 71.0                   & 1.28       & 0.90        & 40.0 \\
+$^{*}$lbg\_113        & 0.0                    & 0.0                      & 116.0                 & 112.0                  & 0.0         & 0.90       & 28.0 \\
+ \hline
+ \hline
+ SSA22 & & & & & & & \\
+ \hline
+ \hline
+s\_sa22a-d3   & 57.0                    & 109.0                    & 127.0                 & 93.0                   & 1.16        & 1.80       & 30.0 \\
+n3\_009       & 32.0                    & 47.0                     & 77.0                  & 48.0                   & 1.0       & 1.07       & 20.0 \\
+lab18         & 44.0                    & 41.0                     & 87.0                  & 62.0                   & 0.67     & 0.45       & 54.0  \\
+s\_sa22b-c20  & 79.0                    & 139.0                    & 112.0                 & 48.0                   & 2.87       & 1.60       & 37.0 \\
+$^{*}$n\_c3         & -                    & -                      & 96.0                  & 78.0                   & -        & 0.55       & -  \\
+$^{*}$s\_sa22b-d9   & -                    & -                      & 99.0                  & 82.0                   & -      & 0.50       & 163.0  \\
+$^{*}$lab7\_top     & -                    & -                      & 83.0                  & 62.0                   & -      & 1.50       & 85.0  \\
+$^{**}$lab25         & 42.0                    & 48.0                     & 80.0                  & 49.0                   & 0.98       & -       & 72.0 \\
+$^{**}$s\_sa22b-d5   & 31.0                    & 57.0                     & 67.0                  & 23.0                   & 2.45      & -       & 60.0 \\
+$^{**}$s\_sa22b-md25 & 50.0                    & 57.0                     & 102.0                 & 75.0                   & 0.76       & -       & 9.0  \\
+$^{**}$n3\_006       & 41.0                    & 81.0                     & 144.0                 & 125.0                  & 0.65      & -       & 156.0
+
+\end{tabular}
+\begin{tablenotes}
+      \small
+      \item $^{*}$ No clearly defined kinematic axis; $V_{obs}$ and $V_{C}$ not defined.
+      \item $^{**}$ No HST coverage; see table \ref{tab:phys-props}
+    \end{tablenotes}
+  \end{threeparttable}
+  \end{table*}
+
+\subsection{Comparison samples}\label{subsubsec:comparison_samples}
+Throughout section \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
+The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission line.
+Given the range of modelling and kinematic parameter extraction methods it is important to verify the extent to which the results from these surveys can be directly compared and treated as forming an evolutionary sequence, which we do in the following subsections by considering each survey in turn.
+We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
+The fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples is computed (i.e.
+we do not want the derived values with extremely large errors to dominate the averages).
+The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
+The same process is applied to compute the errors on the sample medians, and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
+In section \cref{subsec:redshift_evolution} we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+
+\subsubsection{GHASP}\label{subsubsec:GHASP}
+
+\subsubsection{DYNAMO}\label{subsubsec:DYNAMO}
+
+\subsubsection{KROSS}\label{subsubsec:KROSS}
+
+\subsubsection{KMOS$^{3D}$}\label{subsubsec:kmos_3d}
+
+\subsubsection{MASSIV}\label{subsubsec:MASSIV}
+
+\subsubsection{SINS$^{3D}$}\label{subsubsec:SINS}
+
+\subsubsection{LAW\_09}\label{subsubsec:law_09}
+
+\subsubsection{AMAZE}\label{subsubsec:AMAZE}
+
+The SINS sample uses a Kinemetry approach described for \citep{Shapiro2008,ForsterSchreiber2009,Cresci2009} which quantifies asymmetries in both the velocity and velocity dispersion maps to empirically differentiate between rotating and non-rotating systems.
+In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, with the authors also commenting that the S/N of the data is not sufficient to accurately determine the required kinemetry parameters.
+In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $PA_{kin}$ and $PA_{morph}$ misalignment (i.e.$\Delta PA$) and the degree of rotational support as quantified with $V_{C}/\sigma_{int}$.
+In \cite{Wisnioski2015} a set of 5 criteria are described in their section 4 which assess the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, $\Delta PA$ and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
+
+The crucial information to extract for the model grids described above for each galaxy, both for this study and for comparison to previous studies, is a measure of the maximum intrinsic circular velocity, $V_{C}$, and a single measurement of the intrinsic velocity dispersion, $\sigma_{int}$, used as a diagnostic for the local random motions of the gas free from large scale velocity gradients \citep[e.g.]{ForsterSchreiber2006,Genzel2008,Gnerucci2011}.
+Previous studies have measured these quantities in several different ways, and it is important to keep this in mind when trying to establish the dynamical evolution of star forming galaxies between different slices of cosmic time.
+Here we briefly mention the measurement techniques of the major surveys we aim to make comparisons to at high redshift, as an attempt to motivate our own method of kinematic parameter extraction.
+The SINS sample \citep{ForsterSchreiber2009} is refined to a high-z robust rotating disk sample \citep{Cresci2009} using a kinemetry approach \citep{Krajnovic2006,Shapiro2008} which searches the moment maps extracted from the SINFONI datacubes for asymmetries which quantify the degree of rotational support against gravity in each galaxy.
+\cite{Cresci2009} model the robust rotators in three dimensions using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
+In this approach the $V_{C}$ value comes from the best fitting model parameter, and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
+
+\begin{equation}\label{eq:sins_sigma}
+\begin{split}
+\sigma_{01} = \sqrt{\frac{v^{2}(R)h_{z}}{R}} \quad OR \quad \sigma_{01} = \frac{v(R)h_{z}}{R} \\
+& \sigma_{int} = \sqrt{\sigma_{01}^{2} + \sigma_{02}^{2}}
+\end{split}
+\end{equation}
+
+In \cite{Law2009}, a study using OSIRIS, the `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
+
+In their survey at z $\sim 3$, closest in redshift to the current work, \cite{Gnerucci2011} et al.
+derive rotation curves and intrinsic velocity dispersions from a modelled exponential mass distribution, varying the parameters of the model to best fit the observed velocity field.
+The extracted $V_{C}$ value is then the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam smearing (see their Eq.
+8).
+
+In the MASSIV sample, \citep{Epinat2012}, spanning $0.9 < z < 1.6$, the authors use a 2D arctangent fit to the data and extract $V_{C}$ from the model at $R_{last}$, this being the radius where the S/N of the data drops below 3.
+The $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the $\sigma_{model}$ value as per \cite{Epinat2010}, which is the contribution from beam smeaing assuming the best-fitting model parameters.
+
+In KMOS$^{3D}$, covering two redshift regions at $z \sim 1.0$ and $z \sim 2.3$, \cite{Wisnioski2015} compute $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is computed from the $\sigma_{obs}$ map far away from the kinematic centre, where the effects of beam smearing should be negligible.
+In the KROSS sample at $z \sim 1$, \cite{Stott2016} also model the 2D velocity field using an arctangent function, and after finding the best fitting parameters using a genetic algorithm, extract $V_{C}$ at a fiducial radius, which they choose to be $2.2R_{d} \sim 1.3R_{1/2}$, where $R_{d}$ is the galaxy disk radius in the case of an exponential light profile.
+The $\sigma_{int}$ value is computed in two different ways; the first facilitates comparison with KMOS$^{3D}$ results by extracting the instrumental resolution corrected $\sigma_{obs}$ far away from the kinematic centre; the second uses Equation \ref{eq:stott_sigma} to first linearly remove the effects of the local beam smeared velocity gradients, and then correct for instrumental resolution in quadrature (an approach which they verify in their Appendix A).
+
+\begin{equation}\label{eq:stott_sigma}
+   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \frac{\Delta V}{\Delta R}\right)^{2} - \sigma_{inst}^{2}}
+\end{equation}
+
+The derived median $\sigma_{int}$ from these two approaches varies considerably, as highlighted in Figure 8 of their paper.
+
+In the most recent KROSS paper, \citep{Harrison2017}, exponential disk models, \cite{Freeman1970}, are fit to the data extracted along $PA_{kin}$ in 1D to facilitate extraction of the observed velocity at $2R_{1/2}$ (where $2R_{1/2} \sim 3.4R_{d}$).
+The $\sigma_{int_{obs}}$ is also extracted at $2R_{1/2}$ when the data extend to this radius, and when they do not $\sigma_{int_{obs}}$ is taken to be the median of the $\sigma_{obs}$ map.
+Using a suite of mock KMOS data with exponential intrinsic flux distributions and $PA_{morph}$ coincident with $PA_{kin}$s, convolved with various atmospheric seeing profiles, beam smearing correction factors are derived as a function of both the velocity gradient and the ratio $R_{d}/R_{PSF}$ Johnson et al.
+in prep.
+This correction factors are applied to compute $V_{C}$, with a median correction factor of 1.2 at $3.4R_{1/2}$.
+The same treatment is applied to the outer $\sigma_{int_{obs}}$ values, with a median correction factor of 0.97, and when unavailable a seperate correction factor is applied to the median of the $\sigma_{obs}$ map with a median value of 0.8 (see also \citep{Burkert2016a} for similar simulations of mock data and derivations of beam smearing correction factors).
+
+Clearly there are many different approaches for computing the same intrinsic kinematic parameters which we hope to compare across cosmic time intervals, but despite the diversity over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam smearing using similar approaches.
+This trend towards consistency is encouraging, and as described in \cref{subsec:3d modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam smearing effects quantified in the modelling.
+Our small sample size has allowed us to compute beam smeared models, and the corresponding intrinsic models, for each galaxy.
+
+\subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
 % chancing my luck a bit here with this paragraph
@@
 By studying the Rotation Dominated Fraction (RDF) of KDS galaxies, and the mean value of the ratio $V_{C}/\sigma_{int}$ we hope to gain an understanding of balance of gravitational support provided by rotational and random motions.
-$V_{C}$ and $\sigma_{int}$ are both outputs of the dynamical model, so we describe here a pre-modelling morpho-kinematic classification for all KDS galaxies which are spatially resolved in the [OIII]$\lambda$5007 emission line, to inform us which galaxies it is appropriate to attempt dynamical modelling.
-
-Previous studies have kinematically classified their sample in various ways; The SINS sample uses a Kinemetry approach described for \citep{Shapiro2008,ForsterSchreiber2009,Cresci2009} which quantifies asymmetries in both the velocity and velocity dispersion maps to empirically differentiate between rotating and non-rotating systems.
-In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, with the authors also commenting that the S/N of the data is not sufficient to accurately determine the required kinemetry parameters.
-In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $PA_{kin}$ and $PA_{morph}$ misalignment (i.e.$\Delta PA$) and the degree of rotational support as quantified with $V_{C}/\sigma_{int}$.
-In \cite{Wisnioski2015} a set of 5 criteria are described in their section 4 which assess the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, $\Delta PA$ and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
-
-In this work we are in a similar S/N and redshift regime as \cite{Gnerucci2011} and so we aim to keep the pre-modelling classification criteria simple.
+$V_{C}$ and $\sigma_{int}$ are both outputs of the dynamical model, so we describe here a pre-modelling morpho-kinematic classification for all KDS galaxies which are spatially resolved in the [O~{\sc III}]$\lambda$5007 emission line, to inform us which galaxies it is appropriate to attempt dynamical modelling.
+
+In this work we are in a similar S/N and redshift regime as \cite{Gnerucci2011} and so we aim to keep the classification criteria simple.
 This involves a joint visual inspection of the velocity fields and associated HST imaging for all spatially resolved KDS galaxies.
@@
 It is difficult to distinguish in some cases between two HST components rotating together in a single disk (i.e.
-clumpy disk galaxies \citep[e.g.][]{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [OIII]$\lambda$5007 emitting blobs which are offset along the line of sight.
+clumpy disk galaxies \citep[e.g.][]{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
 Perhaps the most telling diagnostic is a double peak in the object spectrum at the kinematic centre, which allows for the classification of IFU data with 2 HST flux peaks as mergers.
@@
 Many of these are rotation doppelg{\"a}ngers and can be fit with the arctangent model (see \cref{subsec:3d modelling}) with a low $\chi ^{2}$ value, highlighting again the importance of the HST photometry for determining true rotation.
+The best fitting smeared and intrinsic models for the modelling sample in both are plotted in \cref{app:kinematics_plots}, where the galaxies have been divided into dispersion and rotation dominated categories as determined by the ratio $V_{C}/\sigma_{int}$, described in more detail throughout \cref{subsubsec:rotation_and_mergers}.
+
+The galaxies classified as mergers are also plotted in \cref{app:mergers}, as well as the dispersion dominated galaxies which have not been d with the full 3D modelling in \cref{app:dispersion_dominated,app:dispersion_dominated}.
 
@@
 \begin{itemize}
-    \item They are spatially resolved in the [OIII]$\lambda5007$ emission line
+    \item They are spatially resolved in the [O~{\sc III}]$\lambda5007$ emission line
     \item They have a clear, monotonic velocity gradient along a single kinematic axis
@@
 
-\section{KINEMATIC ANALYSIS AND EXTRACTION OF PROPERTIES}\label{sec:Kinematic_Properties}
-As mentioned in the introduction, there is no universal standard for defining $V_{C}$, particularly when it is extrapolated from the data using a fitted model, of which there are several types.
-Some authors use a physically motivated model, taking into account the potential-well of the galaxy through knowledge of the mass distribution (e.g.
-\cite{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015}).
-Another type is a phenomenological model, which assumes a fixed function known to well describe observed galactic rotation curves which flatten at large radii \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016}.
-Both of the above examples fit to 2D fields extracted from the datacubes using line-fitting software.
-Recently, algorithms such as Galpak$^{3D}$ \citep{Bouche2015} and 3D-Barolo \citep{DiTeodoro2015} have emerged, fitting directly to the flux in the datacube in order to constrain the kinematic properties.
-
-In this analysis we seek to minimise the number of fitted parameters, making use of information from HST imaging and assumed a fixed functional form as described in the following subsection.    
-One of our main concerns here is to clearly distinguish between observed velocities and those inferred from modelling.
-This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring some extrapolation to determine $V_{C}$.
-There are thus two clear reasons for constructing model velocity fields and fitting these to the KDS modelling sample galaxies; the first is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the second is to estimate the effect of beam smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
-The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.
-
-\subsection{3D Modelling}\label{subsec:3d modelling}
-By simulating a full datacube and fitting the model parameters to the data, we can measure both $V_{C}$ and $\sigma_{int}$ having removed the effects of beam smearing.
-For each galaxy in the modelling sample we construct a model datacube with the same spatial dimensions as the observed datacube, and populate each spaxel with an [OIII]$\lambda$5007 emission line that has central wavelength determined by the systemic velocity of the galaxy.
-This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model.  
-Following the procedure now of numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe:
-
-\begin{equation}\label{eq:arctangent}
-   v_{r} = \frac{2}{\pi}v_{asym}arctan\left(\frac{r}{r_{t}}\right)
-\end{equation}
-
-\noindent
-with `r' measured as the distance from the centre of rotation, (xcen, ycen).
-This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
-The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
-If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam smearing.
-The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
-In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
-The intrinsic flux profile of these simulated [OIII]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in section \cref{subsubsec:galfitting} (which assumes that the [OIII]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
-This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.
-
-This simulated intrinsic [OIII]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries with the atmospheric seeing profile determined from fitting the collapsed, stacked standard star cube in each pointing with an elliptical gaussian (the recovered seeing values are reported in table \ref{tab:pointings}).
-The velocity and velocity dispersion values are then re-measured in each spaxel to assess the impact of beam smearing.
-Convolution with the seeing profile produces a peak in the modelled velocity dispersion field at the centre of rotation and flattens the observed velocity field perpendicular to $PA_{kin}$.
-The model therefore provides a beam smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the re-measured velocity dispersion after convolution, i.e.
-$\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
-This is computed for each spaxel to provide the 2D $\sigma_{bs}$ correction map.
-The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in section \cref{subsubsec:model_errors}.
-We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce. 
-We fit the beam smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, and seek the combination of parameters which maximises the log-Likelihood function given by equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
-
-\begin{equation}\label{eq:likelihood}
-   ln\Lagr = \frac{-0.5\sum_{i=1}^{N}(d_{i} - M_{i})^{2}}{\delta_{v_{i}}^{2}} - ln\left(\frac{1}{\delta_{v_{i}}^{2}}\right)
-\end{equation}
-
-\noindent
-where $\delta_{v_{i}}$ are the observed velocity errors, $d_{i}$ are the datapoints and $M_{i}$ are the convolved model velocity values.
-In practice we fix the (xcen,ycen) parameters of the galaxy to the location of the stellar continuum, a proxy for the centre of the gravitational potential well, recovered from the collapsed KMOS cube, leaving only 3 free parameters to vary in the MCMC sampling.
-This assumes that the gas and the stars in the galaxy share a common centre of mass, an assumption which is at least verified for the vast majority of SFGs in the local and intermediate redshift universe.
-Due to the faintness of the continuum, there are several galaxies for which we cannot reliably estimate the rotation centre using this method, and instead set (xcen,ycen) to coincide with the peak [OIII]$\lambda$5007 flux location.
-For the SSA22 galaxies, using the continuum to fix the rotation centre is generally more successful, since the use of the HK filter effectively doubles the S/N of this component by collapsing over two wavebands.
-This differs from the method of fixing the rotation centre at the midpoint between the velocity extrema, described in \cite{Wisnioski2015} and \cite{Rodrigues2016}.
-In general the S/N of our sample is low at the galaxy outskirts and for many of the isolated rotating sample we don't observe the flattening of the velocity field.
-This suggests that the velocity midpoint may be biased towards the side of the galaxy which shows the higher velocity value and so we instead use the physically motivated continuum centre where possible, which also matches the approach described in \cite{Harrison2017}.
-
-The MCMC sampling provides a distribution of parameter values around those which give the maximum likelihood.
-We have confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates have converged around the 50th percentile values.
-The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in \cref{subsubsec:model_errors}.
-Following the modelling procedure, the kinematic parameters $V_{C}$ and $\sigma_{int}$ must be extracted from the 2D intrinsic fields.
-There are several choices for how this can be done, and our procedure is built around facilitating comparisons to earlier work, as described in \cref{subsubsec:param_extraction}.
-
-The best fitting smeared and intrinsic models for the modelling sample in both are plotted in \cref{app:kinematics_plots}, where the galaxies have been divided into dispersion and rotation dominated categories as determined by the ratio $V_{C}/\sigma_{int}$, described in more detail throughout \cref{subsubsec:rotation_and_mergers}.
-Overplotted onto the models are the data values and uncertainties extracted along $PA_{kin}$.
-These figures also show the HST imaging for each galaxy, the best fit galfit model and residuals, 2D maps of the [OIII]$\lambda$5007 flux, observed velocity, observed dispersion, best fitting smeared model velocity, data - model residuals, intrinsic velocity dispersion (observed dispersion corrected for beam smearing and instrumental resolution as described in \cref{subsubsec:param_extraction}) as well as a plot of 1D extractions along the observed, intrinsic and beam smeared dispersion maps.
-The galaxies classified as mergers are also plotted in \cref{app:mergers}, as well as the dispersion dominated galaxies which have not been d with the full 3D modelling in \cref{app:dispersion_dominated,app:dispersion_dominated}.
-
-\subsubsection{3D Modelling Kinematic Parameters Extraction}\label{subsubsec:param_extraction}
-The crucial information to extract for the model grids described above for each galaxy, both for this study and for comparison to previous studies, is a measure of the maximum intrinsic circular velocity, $V_{C}$, and a single measurement of the intrinsic velocity dispersion, $\sigma_{int}$, used as a diagnostic for the local random motions of the gas free from large scale velocity gradients \citep[e.g.]{ForsterSchreiber2006,Genzel2008,Gnerucci2011}.
-Previous studies have measured these quantities in several different ways, and it is important to keep this in mind when trying to establish the dynamical evolution of star forming galaxies between different slices of cosmic time.
-Here we briefly mention the measurement techniques of the major surveys we aim to make comparisons to at high redshift, as an attempt to motivate our own method of kinematic parameter extraction.
-The SINS sample \citep{ForsterSchreiber2009} is refined to a high-z robust rotating disk sample \citep{Cresci2009} using a kinemetry approach \citep{Krajnovic2006,Shapiro2008} which searches the moment maps extracted from the SINFONI datacubes for asymmetries which quantify the degree of rotational support against gravity in each galaxy.
-\cite{Cresci2009} model the robust rotators in three dimensions using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
-In this approach the $V_{C}$ value comes from the best fitting model parameter, and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
-
-\begin{equation}\label{eq:sins_sigma}
-\begin{split}
-\sigma_{01} = \sqrt{\frac{v^{2}(R)h_{z}}{R}} \quad OR \quad \sigma_{01} = \frac{v(R)h_{z}}{R} \\
-& \sigma_{int} = \sqrt{\sigma_{01}^{2} + \sigma_{02}^{2}}
-\end{split}
-\end{equation}
-
-In \cite{Law2009}, a study using OSIRIS, the `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
-
-In their survey at z $\sim 3$, closest in redshift to the current work, \cite{Gnerucci2011} et al.
-derive rotation curves and intrinsic velocity dispersions from a modelled exponential mass distribution, varying the parameters of the model to best fit the observed velocity field.
-The extracted $V_{C}$ value is then the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam smearing (see their Eq.
-8).
-
-In the MASSIV sample, \citep{Epinat2012}, spanning $0.9 < z < 1.6$, the authors use a 2D arctangent fit to the data and extract $V_{C}$ from the model at $R_{last}$, this being the radius where the S/N of the data drops below 3.
-The $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the $\sigma_{model}$ value as per \cite{Epinat2010}, which is the contribution from beam smeaing assuming the best-fitting model parameters.
-
-In KMOS$^{3D}$, covering two redshift regions at $z \sim 1.0$ and $z \sim 2.3$, \cite{Wisnioski2015} compute $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is computed from the $\sigma_{obs}$ map far away from the kinematic centre, where the effects of beam smearing should be negligible.
-In the KROSS sample at $z \sim 1$, \cite{Stott2016} also model the 2D velocity field using an arctangent function, and after finding the best fitting parameters using a genetic algorithm, extract $V_{C}$ at a fiducial radius, which they choose to be $2.2R_{d} \sim 1.3R_{1/2}$, where $R_{d}$ is the galaxy disk radius in the case of an exponential light profile.
-The $\sigma_{int}$ value is computed in two different ways; the first facilitates comparison with KMOS$^{3D}$ results by extracting the instrumental resolution corrected $\sigma_{obs}$ far away from the kinematic centre; the second uses Equation \ref{eq:stott_sigma} to first linearly remove the effects of the local beam smeared velocity gradients, and then correct for instrumental resolution in quadrature (an approach which they verify in their Appendix A).
-
-\begin{equation}\label{eq:stott_sigma}
-   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \frac{\Delta V}{\Delta R}\right)^{2} - \sigma_{inst}^{2}}
-\end{equation}
-
-The derived median $\sigma_{int}$ from these two approaches varies considerably, as highlighted in Figure 8 of their paper.
-
-In the most recent KROSS paper, \citep{Harrison2017}, exponential disk models, \cite{Freeman1970}, are fit to the data extracted along $PA_{kin}$ in 1D to facilitate extraction of the observed velocity at $2R_{1/2}$ (where $2R_{1/2} \sim 3.4R_{d}$).
-The $\sigma_{int_{obs}}$ is also extracted at $2R_{1/2}$ when the data extend to this radius, and when they do not $\sigma_{int_{obs}}$ is taken to be the median of the $\sigma_{obs}$ map.
-Using a suite of mock KMOS data with exponential intrinsic flux distributions and $PA_{morph}$ coincident with $PA_{kin}$s, convolved with various atmospheric seeing profiles, beam smearing correction factors are derived as a function of both the velocity gradient and the ratio $R_{d}/R_{PSF}$ Johnson et al.
-in prep.
-This correction factors are applied to compute $V_{C}$, with a median correction factor of 1.2 at $3.4R_{1/2}$.
-The same treatment is applied to the outer $\sigma_{int_{obs}}$ values, with a median correction factor of 0.97, and when unavailable a seperate correction factor is applied to the median of the $\sigma_{obs}$ map with a median value of 0.8 (see also \citep{Burkert2016a} for similar simulations of mock data and derivations of beam smearing correction factors).
-
-Clearly there are many different approaches for computing the same intrinsic kinematic parameters which we hope to compare across cosmic time intervals, but despite the diversity over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam smearing using similar approaches.
-This trend towards consistency is encouraging, and as described in \cref{subsec:3d modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam smearing effects quantified in the modelling.
-Our small sample size has allowed us to compute beam smeared models, and the corresponding intrinsic models, for each galaxy.
-Following the approach of \cite{Harrison2017}, we extract $V_{C}$ at $2R_{1/2}$ to allow for a robust comparison to the large KROSS sample at $z\sim0.9$, and also note that due to the flattening of the intrinsic velocity model at small radii, the velocity value extracted at $1.3R_{1/2}$ does not differ by a large amount.
-To extract the velocity from the intrinsic model we first convolve the measured $R_{1/2}$ values with the PSF of the KMOS observations and read off at $2R_{1/2}$ to give $V_{C}$.
-This $V_{C}$ value is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
-
-To measure the $\sigma_{int}$ value for each galaxy in our sample we first use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{bs}$ is the value detailed in \cref{subsec:3d modelling} and $\sigma_{inst}$ is a measure of the instrumental broadening value averaged across gaussian fits to several skylines.
-This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam smearing correction best recovers the $\sigma_{int}$ values.
-
-\begin{equation}\label{eq:owen_sigma}
-   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{bs} \right)^{2} - \sigma_{inst}^{2}}
-\end{equation}
-
-We then take the median value of this map as the single $\sigma_{int}$ value for that galaxy.
-
-To test the robustness of our modelling approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors detailed in Johnson et al.
-(in prep) and used to evaluate the final kinematic parameters in \cite{Harrison2017}.
-These are in very good agreement within the errorbars, confirming that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.
-The errors on the extracted kinematic parameters are discussed in \cref{subsubsec:model_errors}.
-
-In all of the modelled galaxies in GOODS-S, the $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, with 2 galaxies requiring extrapolation > 0.4$^{\prime\prime}$ with a mean extrapolation of 0.24$^{\prime\prime}$.
-In SSA22, probably as a result of the slightly poorer seeing conditions, only one galaxy requires extrapolation beyond 0.2$^{\prime\prime}$ of the last data radius and the mean extrapolation is 0.12$^{\prime\prime}$.
-This extrapolation is a requirement imposed by the low S/N at the outskirts of the KDS galaxies, limiting the extent to which the ionised gas disk can be observed, with the majority of the observed velocity curves not reaching the point of flattening.
-The extent of the extrapolation for each galaxy is made clear throughout the figures in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radius marked on each velocity thumbnail.
-We present the maximum observed velocity values, $V_{obs}$, and the intrinsic, inclination and beam smearing corrected model velocity values, $V_{C}$, in table \ref{tab:kin_props}.
-
-\begin{table*}
-\centering
-\caption{Dynamical Properties}
-\label{tab:kin_props}
-\begin{tabular}{cccccccccccc}
-
- \hline
-ID & $V_{obs}$ & $V_{C}$ & $\sigma_{obs}$ & $\sigma_{int}$ & $V_{C}/\sigma_{int}$ & M$_{dyn}$  & $R_{last}$ & 2$R_{1/2}$ & PA$_{kin}$ & $\Delta PA$ & s$_{0.5}$\\
- \hline
- GOODS-S & & & & & & & & & & & \\
- \hline
-bs009818        & 65.0                    & 84.0                     & 95.0                  & 79.0                   & 1.06           & 9.62      & 2.2        & 2.5        & 72.0    & 75.0      & 100 \\
-bs014828        & 32.0                    & 46.0                     & 97.0                  & 88.0                   & 0.53           & 9.22      & 3.1      & 3.3      & 44.0    & 19.0      & 94 \\
-lbg\_20         & 26.0                    & 56.0                     & 55.0                  & 40.0                   & 1.39           & 9.29      & 2.3      & 2.6        & 41.0    & 40.0      & 57 \\
-lbg\_105        & 13.0                    & 32.0                     & 68.0                  & 59.0                   & 0.54           & 8.92      & 2.3      & 3.5       & 170.0   & 42.0      & 64 \\
-bs006541        & 36.0                    & 65.0                     & 96.0                  & 83.0                   & 0.78           & 9.56      & 4.5      & 3.7       & 23.0    & 35.0      & 96 \\
-b012141\_012208 & 34.0                    & 93.0                     & 94.0                  & 63.0                   & 1.47           & 9.81      & 1.4      & 3.2       & 122.0   & 66.0      & 92 \\
-b15573          & 62.0                    & 81.0                     & 111.0                 & 84.0                   & 0.97           & 9.21      & 3.1      & 1.0       & 118.0   & 28.0      & 102 \\
-bs008543        & 77.0                    & 111.0                    & 98.0                  & 71.0                   & 1.56           & 9.97      & 4.5      & 3.2       & 114.0   & 47.0      & 106 \\
-bs006516        & 56.0                    & 61.0                     & 64.0                  & 45.0                   & 1.35           & 9.54      & 4.6      & 3.9       & 144.0   & 1.0       & 63 \\
-bs016759        & 71.0                    & 110.0                    & 82.0                  & 57.0                   & 1.93           & 9.7       & 2.7      & 1.8       & 75.0    & 26.0      & 97  \\
-lbg\_111        & 53.0                    & 58.0                     & 90.0                  & 81.0                   & 0.71           & 9.01      & 3.1      & 1.3        & 168.0   & 87.0      & 91 \\
-lbg\_38         & 31.0                    & 97.0                     & 76.0                  & 53.0                   & 1.82           & 9.62      & 1.8      & 1.9       & 47.0    & 89.0      & 87 \\
-lbg\_94         & 18.0                    & 34.0                     & 65.0                  & 55.0                   & 0.62           & 8.82      & 2.7      & 2.4       & 41.0    & 39.0      & 61 \\
-lbg\_109        & 32.0                    & 53.0                     & 101.0                 & 91.0                   & 0.58           & 9.42      & 3.1      & 4.0        & 157.0   & 38.0      & 99 \\
-lbg\_24         & 30.0                    & 42.0                     & 64.0                  & 51.0                   & 0.82           & 9.03      & 4.6       & 2.6       & 64.0    & 30.0      & 59 \\
-lbg\_25         & 14.0                    & 33.0                     & 53.0                  & 41.0                   & 0.8            & 8.79      & 2.7      & 2.4        & 87.0    & 8.0       & 48 \\
-lbg\_32         & 79.0                    & 121.0                    & 104.0                 & 76.0                   & 1.58           & 10.12     & 2.3      & 3.8       & 11.0    & 29.0      & 116 \\
-lbg\_91         & 58.0                    & 91.0                     & 98.0                  & 71.0                   & 1.28           & 9.54      & 2.3      & 1.8        & 40.0    & 38.0      & 96 \\
-lbg\_113        & 0.0                    & 0.0                      & 116.0                 & 112.0                  & 0.0            & - & 2.7      & 1.8       & 28.0    & 12.0      & 112 \\
- \hline
- \hline
- SSA22 & & & & & & & & & & & \\
- \hline
- \hline
-lab25         & 42.0                    & 48.0                     & 80.0                  & 49.0                   & 0.98           & 9.27      & 3.8      & 3.37       & 72.0    & 5.0       & 60 \\
-n\_c3         & 0.0                    & 0.0                      & 96.0                  & 78.0                   & 0.0            & - & 3.7      & 1.13       & 0.0     & 85.0      & 78  \\
-s\_sa22a-d3   & 57.0                    & 109.0                    & 127.0                 & 93.0                   & 1.16           & 10.0      & 5.2      & 3.61       & 30.0    & 84.0      & 121   \\
-n3\_009       & 32.0                    & 47.0                     & 77.0                  & 48.0                   & 1.0            & 9.06      & 3.3      & 2.14       & 20.0    & 63.0      & 59 \\
-n3\_006       & 41.0                    & 81.0                     & 144.0                 & 125.0                  & 0.65           & 9.72      & 6.1      & 3.37       & 156.0   & 89.0      & 138 \\
-s\_sa22b-d9   & 0.0                    & 0.0                      & 99.0                  & 82.0                   & 0.0            & - & 3.8      & 1.01       & 163.0   & 77.0      & 83   \\
-lab18         & 44.0                    & 41.0                     & 87.0                  & 62.0                   & 0.67           & 8.57      & 3.5      & 0.93       & 54.0    & 26.0      & 69 \\
-s\_sa22b-d5   & 31.0                    & 57.0                     & 67.0                  & 23.0                   & 2.45           & 9.41      & 4.2      & 3.33       & 60.0    & 6.0       & 47 \\
-s\_sa22b-md25 & 50.0                    & 57.0                     & 102.0                 & 75.0                   & 0.76           & 9.4       & 4.1      & 3.29       & 9.0     & 57.0      & 86 \\
-s\_sa22b-c20  & 79.0                    & 139.0                    & 112.0                 & 48.0                   & 2.87           & 10.16     & 3.2      & 3.22       & 37.0    & 38.0      & 110 \\
-lab7\_top     & 0.0                    & 0.0                      & 83.0                  & 62.0                   & 0.0            & - & 3.3      & 2.99       & 85.0    & 54.0      & 63  
-\end{tabular}
-\end{table*}
+\subsubsection{Kinematic sample summary}\label{subsubsec:kin_sample_summary}
 
@@
 There does not appear to be any obvious explanation for why this is the case.
-In practice, since the intrinsic [OIII]$\lambda5007$ profile is determined by the GALFIT model throughout the modelling in \cref{subsec:3d modelling}, the $\Delta PA$ value has an impact on the derived $V_{C}$.
+In practice, since the intrinsic [O~{\sc III}]$\lambda5007$ profile is determined by the GALFIT model throughout the modelling in \cref{subsec:3d modelling}, the $\Delta PA$ value has an impact on the derived $V_{C}$.
 As $\Delta PA$ increases, the model beam smeared velocity reaches maximum value at larger radii, and so the inferred intrinsic $V_{C}$ becomes larger to provide an adequate fit to the data.
@@
     There is no strong correlation between the two parameters in either of these surveys, however several of the $V_{C}$ values in G11 are substantially larger or have $\sigma_{int}$ values consistent with 0kms$^{-1}$.
-    This is despite the two samples having similar ranges in stellar mass, and is probably a consequence of the different modelling techniques used to infer the dynamical paramters.
+    This is despite the two samples having similar ranges in stellar mass, and is probably a consequence of the different modelling techniques used to infer the dynamical parameters.
     We assume that $\sigma_{int} = 30kms^{-1}$ for the G11 galaxies with reported $\sigma_{int} = 0kms^{-1}$, which is roughly equal to the spectral resolution of the instrument with which they were observed (SINFONI).
@@
 Throughout the following sections we compare the median dynamical properties of several IFU studies over a wide redshift baseline \citep{Green2014,Wisnioski2015,Epinat2012,ForsterSchreiber2009,Cresci2009,Gnerucci2011}, and also compare with Fabry-Perot data from the GHASP sample \citep{Epinat2008,Epinat2008a} as an indicator of the behaviour of SFGs in the local universe.
-The galaxy selection criteria in these surveys, with the exception of \cite{Green2014}, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the $OIII\lambda5007$ or $H\alpha$ ionised gas emission line.
+The galaxy selection criteria in these surveys, with the exception of \cite{Green2014}, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission line.
 In \cite{Green2014}, half of the galaxies at $z\sim 0.1$ are selected to have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, providing a local comparison sample to the high redshift universe.
@@
 The KDS datapoint, represented by the large red circle, has mean $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ and median $V_{C} = 60.0^{+7.5}_{-5.9}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
-This could either be a result of the measurement and modelling technique, which carries significant uncertainties due to modelling assumptions, the S/N of the [OIII]$\lambda5007$ emission line even in very long integrations at this redshift, the spatial coverage of [OIII]$\lambda5007$ may be more compact that $H\alpha$ and consequently may not probe out to the same galactic radii and the sparsity of resolution elements, or could be the result or some real physical process in the galaxies which lowers $V_{C}$ as traced by the ionised gas dynamics.
+This could either be a result of the measurement and modelling technique, which carries significant uncertainties due to modelling assumptions, the S/N of the [O~{\sc III}]$\lambda5007$ emission line even in very long integrations at this redshift, the spatial coverage of [O~{\sc III}]$\lambda5007$ may be more compact that $H\alpha$ and consequently may not probe out to the same galactic radii and the sparsity of resolution elements, or could be the result or some real physical process in the galaxies which lowers $V_{C}$ as traced by the ionised gas dynamics.
 Also, since there is a higher fraction of dispersion dominated galaxies at $z\sim3.5$, the mean $V_{C}$ value of the complete sample is likely to be biased low.
@@
 \caption{High resolution imaging is important not only for reliably recovering the morphological parameters, but also to explain peculiar features in the observed velocity and velocity dispersion fields.
-In the two examples above, multiple components in the HST imaging clearly correspond to marginally different [OIII]$\lambda$5007 emission wavelengths, which manifest as velocity shifts in individual spaxels and broadens the observed dispersion pattern where the emission lines at different wavelengths merge.}
+In the two examples above, multiple components in the HST imaging clearly correspond to marginally different [O~{\sc III}]$\lambda$5007 emission wavelengths, which manifest as velocity shifts in individual spaxels and broadens the observed dispersion pattern where the emission lines at different wavelengths merge.
+Overplotted onto the models are the data values and uncertainties extracted along $PA_{kin}$.
+These figures also show the HST imaging for each galaxy, the best fit galfit model and residuals, 2D maps of the [O~{\sc III}]$\lambda$5007 flux, observed velocity, observed dispersion, best fitting smeared model velocity, data - model residuals, intrinsic velocity dispersion (observed dispersion corrected for beam smearing and instrumental resolution as described in \cref{subsubsec:param_extraction}) as well as a plot of 1D extractions along the observed, intrinsic and beam smeared dispersion maps.}
 \label{app:goods_mergers_1}
@@
 
-\subsubsection{3D modelling kinematic parameter error estimates}\label{subsubsec:model_errors}
+\subsection{3D modelling kinematic parameter error estimates}\label{appsubsec:model_errors}
 As mentioned above, the MCMC sampling provides distributions for each of the model parameters, from which we can extract the 84th and 16th percentile values as the +/- 1-$\sigma$ errors.

### 2017-02-11 paper.tex
Just before tackling the Results section

@@
 There is also an increasing body of work measuring the relationship between the observed maximum rotational velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Tiley2016a,Harrison2017}.
-In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
+In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
 
@@
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS we have been able to spatially resolve [O~{\sc III}]$\lambda$5007 emission in 44 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.
+By making use of KMOS we have been able to spatially resolve [O~{\sc III}]$\lambda$5007 emission in 43 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.
 
@@
 We also define a classification procedure which separates the KDS galaxies into a merger and modelling sample.
-In \cref{sec:Kinematic_Properties} we present the kinematic modelling applied to the KDS galaxies, including the beam smearing correction, and the method chosen to extract the kinematic properties following this modelling procedure.
+In \cref{sec:Kinematic_Properties} we present the kinematic modelling applied to the KDS galaxies, including the beam-smearing correction, and the method chosen to extract the kinematic properties following this modelling procedure.
 \cref{sec:results} presents an analysis of the derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
@@
  GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & 2 & 17 & K, H & 32.4 & 0.50 \\
-GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 19 & K, H & 31.8 & 0.52 \\
-SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & 1 & 9 & HK & 27.8 & 0.57 \\
-SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 10 & 46 & 8 & 80 & HK & 38.1 & 0.62 \\
+GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 18 & K, H & 31.8 & 0.52 \\
+SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & 2 & 18 & HK & 27.8 & 0.57 \\
+SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
  \hline
@@
 \begin{threeparttable}
-\caption{Physical properties of the KDS field galaxies as measured from SED fitting and from applying GALFIT \protect\citep{Peng2010_galfit}}
+\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying GALFIT \protect\citep{Peng2010_galfit}}
 \label{tab:phys-props}
@@
 ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}[M_{\odot}])$ & SFR$_{SED}$($M_{\odot}yr^{-1}$) & $A_{r}$ & i$^{\circ}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc) \\
- \hline
- GOODS-S & & & & & & & & & & \\
  \hline
@@
 lbg\_91         & 03:32:27 & -27:41:52 & 3.170       & 24.65  & 9.8   & 5.7  & 0.58        & 56.0        & 79.0    & 0.89 \\
- \hline
- SSA22 & & & & & & & & & & \\
- \hline
 s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.4618 & 9.88  & -            & 0.39        & 70.0        & 125.0   & 1.78      \\
@@
 s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.2538 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
-lab7\_top     & 22:17:41 & +00:11:28 & 3.095      & 23.8919 & 9.89  & -            & 0.51        & 61.0        & 139.0   & 1.47 \\
 $^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & 99.0    & 8.78  & -            & 0.57         & 57.3        & -    & 2.4      \\
@@
 \subsection{Morphological Measurements}
-For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high resolution photometry.
+For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution photometry.
 This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies and helps to distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
@@
 Additionally, for the corresponding objects in the \cite{VanderWel2012} catalogue the median \Sers index value is 1.2.
-The use of exponential profiles also facilitates comparison with recent large surveys such as KROSS \citep{Harrison2017}, in which beam smearing correction factors are applied to the derived kinematic parameters as function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:param_extraction}), and KMOS$^{3D}$ \citep{Wisnioski2015}.
+The use of exponential profiles also facilitates comparison with recent large surveys such as KROSS \citep{Harrison2017}, in which beam-smearing correction factors are applied to the derived kinematic parameters as function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:param_extraction}), and KMOS$^{3D}$ \citep{Wisnioski2015}.
 
@@
 Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d modelling}), which requires the $R_{1/2}$ value for each galaxy.
-A final use of the derived $R_{1/2}$ values is to verify our beam smearing correction results through comparison with systematic correction factors presented in Johnson et al.
+A final use of the derived $R_{1/2}$ values is to verify our beam-smearing correction results through comparison with systematic correction factors presented in Johnson et al.
 (in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:param_extraction}).
@@
 We proceed now to extract 2D measurements from the KDS datacubes by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
-We then describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam smearing corrections for each galaxy.
+We then describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam-smearing corrections for each galaxy.
 
@@
 
-\subsubsection{3D modelling and beam smearing corrections}\label{subsec:3d_modelling}
+\subsubsection{3D modelling and beam-smearing corrections}\label{subsec:3d_modelling}
 
@@
 This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.
-There are thus two clear reasons for constructing model velocity fields; the first is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the second is to estimate the effect of beam smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
+There are thus two clear reasons for constructing model velocity fields; the first is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the second is to estimate the effect of beam-smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
 The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.
@@
 The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
-If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam smearing.
+If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam-smearing.
 The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
@@
 
-Following the construction of a convolved cube and the measurement of the beam-smeared maps we can extract beam smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
+Following the construction of a convolved cube and the measurement of the beam-smeared maps we can extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
 There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
@@
 
-\subsubsection{KDS beam smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
+\subsubsection{KDS beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
 We extract $V_{smeared}$ and $V_{C}$ by reading off from the beam-smeared and intrinsic best fitting 2D model grids respectively at $2R_{1/2}$.
@@
 The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
-The beam smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
+The beam-smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
 The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in section \cref{subsubsec:observed_and_intrinsic}.
@@
 The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radius marked on each velocity thumbnail.
-We present the maximum observed velocity values, $V_{obs}$, and the intrinsic, inclination and beam smearing corrected model velocity values, $V_{C}$, in table \ref{tab:kin_props}.
-
-\subsubsection{KDS beam smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
+
+\subsubsection{KDS beam-smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
 Convolution of the model velocity field with the seeing profile produces a peak in the beam-smeared velocity dispersion map at the centre of rotation.
-The model therefore provides a beam smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the beam-smeared dispersion i.e.
+The model therefore provides a beam-smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the beam-smeared dispersion i.e.
 $\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
@@
 To measure the $\sigma_{int}$ value for each galaxy in our sample we first use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the K-band and 55.4kms$^{-1}$ in the HK-band).
-This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam smearing correction best recovers the $\sigma_{int}$ values.
+This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam-smearing correction best recovers the $\sigma_{int}$ values.
 
@@
 
-The median value of this map is taken as the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value, with both of these presented in table \ref{tab:kin_props}.
-
-The beam smearing correction factor is then given by the ratio of these two medians, i.e.
+The median value of this map is taken as the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value.
+The beam-smearing correction factor is then given by the ratio of these two medians, i.e.
 $\sigma_{obs}/\sigma_{int}$, with mean and median values of 0.77 and 0.79 respectively for the morphologically isolated KDS galaxies.
 
-To test the robustness of our beam smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{d}/R_{psf}$, detailed in Johnson et al.
+To test the robustness of our beam-smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{d}/R_{psf}$, detailed in Johnson et al.
 (in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
@@
 
+We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for all of the spatially resolved KDS field galaxies classified as morphologically isolated (29, see section \cref{subsec:morpho-kin-class}).
+
 \begin{table*}
@@
 \begin{threeparttable}
-\caption{Dynamical Properties}
+\caption{Dynamical Properties for the resolved and morphologically isolated KDS field galaxies}
 \label{tab:kin_props}
-\begin{tabular}{cccccccc}
+\begin{tabular}{ccccccccc}
 
  \hline
-ID & $V_{obs}$(kms$^{-1}$) & $V_{C}$(kms$^{-1}$) & $\sigma_{obs}$(kms$^{-1}$) & $\sigma_{int}$(kms$^{-1}$) & $V_{C}/\sigma_{int}$ & $R_{1/2}$(kpc) & PA$_{kin}^{\circ}$ \\
+ID & $V_{obs}$(kms$^{-1}$) & $V_{C}$(kms$^{-1}$) & $\sigma_{obs}$(kms$^{-1}$) & $\sigma_{int}$(kms$^{-1}$) & $V_{C}/\sigma_{int}$ & $R_{1/2}$(kpc) & PA$_{kin}^{\circ}$ & Class$^{a}$ \\
  \hline
- GOODS-S & & & & & & & \\
- \hline
-bs009818        & 65.0                    & 84.0                     & 95.0                  & 79.0                   & 1.06       & 1.25        & 72.0 \\
-bs014828        & 32.0                    & 46.0                     & 97.0                  & 88.0                   & 0.53       & 1.65      & 44.0   \\
-lbg\_20         & 26.0                    & 56.0                     & 55.0                  & 40.0                   & 1.39      & 1.30        & 41.0  \\
-lbg\_105        & 13.0                    & 32.0                     & 68.0                  & 59.0                   & 0.54       & 1.75       & 170.0 \\
-bs006541        & 36.0                    & 65.0                     & 96.0                  & 83.0                   & 0.78        & 1.85       & 23.0 \\
-b012141\_012208 & 34.0                    & 93.0                     & 94.0                  & 63.0                   & 1.47       & 1.60       & 122.0 \\
-b15573          & 62.0                    & 81.0                     & 111.0                 & 84.0                   & 0.97        & 0.50       & 118.0 \\
-bs008543        & 77.0                    & 111.0                    & 98.0                  & 71.0                   & 1.56       & 1.60       & 114.0 \\
-bs006516        & 56.0                    & 61.0                     & 64.0                  & 45.0                   & 1.35      & 1.95       & 144.0  \\
-bs016759        & 71.0                    & 110.0                    & 82.0                  & 57.0                   & 1.93        & 0.90       & 75.0 \\
-lbg\_111        & 53.0                    & 58.0                     & 90.0                  & 81.0                   & 0.71      & 0.65        & 168.0 \\
-lbg\_38         & 31.0                    & 97.0                     & 76.0                  & 53.0                   & 1.82        & 0.95       & 47.0 \\
-lbg\_94         & 18.0                    & 34.0                     & 65.0                  & 55.0                   & 0.62       & 1.20       & 41.0 \\
-lbg\_109        & 32.0                    & 53.0                     & 101.0                 & 91.0                   & 0.58      & 2.00        & 157.0 \\
-lbg\_24         & 30.0                    & 42.0                     & 64.0                  & 51.0                   & 0.82      & 1.30       & 64.0  \\
-lbg\_25         & 14.0                    & 33.0                     & 53.0                  & 41.0                   & 0.8       & 1.20        & 87.0  \\
-lbg\_32         & 79.0                    & 121.0                    & 104.0                 & 76.0                   & 1.58       & 1.90       & 11.0  \\
-lbg\_91         & 58.0                    & 91.0                     & 98.0                  & 71.0                   & 1.28       & 0.90        & 40.0 \\
-$^{*}$lbg\_113        & 0.0                    & 0.0                      & 116.0                 & 112.0                  & 0.0         & 0.90       & 28.0 \\
- \hline
- \hline
- SSA22 & & & & & & & \\
- \hline
- \hline
-s\_sa22a-d3   & 57.0                    & 109.0                    & 127.0                 & 93.0                   & 1.16        & 1.80       & 30.0 \\
-n3\_009       & 32.0                    & 47.0                     & 77.0                  & 48.0                   & 1.0       & 1.07       & 20.0 \\
-lab18         & 44.0                    & 41.0                     & 87.0                  & 62.0                   & 0.67     & 0.45       & 54.0  \\
-s\_sa22b-c20  & 79.0                    & 139.0                    & 112.0                 & 48.0                   & 2.87       & 1.60       & 37.0 \\
-$^{*}$n\_c3         & -                    & -                      & 96.0                  & 78.0                   & -        & 0.55       & -  \\
-$^{*}$s\_sa22b-d9   & -                    & -                      & 99.0                  & 82.0                   & -      & 0.50       & 163.0  \\
-$^{*}$lab7\_top     & -                    & -                      & 83.0                  & 62.0                   & -      & 1.50       & 85.0  \\
-$^{**}$lab25         & 42.0                    & 48.0                     & 80.0                  & 49.0                   & 0.98       & -       & 72.0 \\
-$^{**}$s\_sa22b-d5   & 31.0                    & 57.0                     & 67.0                  & 23.0                   & 2.45      & -       & 60.0 \\
-$^{**}$s\_sa22b-md25 & 50.0                    & 57.0                     & 102.0                 & 75.0                   & 0.76       & -       & 9.0  \\
-$^{**}$n3\_006       & 41.0                    & 81.0                     & 144.0                 & 125.0                  & 0.65      & -       & 156.0
+bs009818        & 65.0                    & 84.0                     & 95.0                  & 79.0                   & 1.06       & 1.25        & 72.0 & RD \\
+bs014828        & 32.0                    & 46.0                     & 97.0                  & 88.0                   & 0.53       & 1.65      & 44.0 & DD    \\
+lbg\_20         & 26.0                    & 56.0                     & 55.0                  & 40.0                   & 1.39      & 1.30        & 41.0 & RD  \\
+lbg\_105        & 13.0                    & 32.0                     & 68.0                  & 59.0                   & 0.54       & 1.75       & 170.0 & DD \\
+bs006541        & 36.0                    & 65.0                     & 96.0                  & 83.0                   & 0.78        & 1.85       & 23.0 & DD \\
+b012141\_012208 & 34.0                    & 93.0                     & 94.0                  & 63.0                   & 1.47       & 1.60       & 122.0 & RD \\
+b15573          & 62.0                    & 81.0                     & 111.0                 & 84.0                   & 0.97        & 0.50       & 118.0 & DD \\
+bs008543        & 77.0                    & 111.0                    & 98.0                  & 71.0                   & 1.56       & 1.60       & 114.0 & RD \\
+bs006516        & 56.0                    & 61.0                     & 64.0                  & 45.0                   & 1.35      & 1.95       & 144.0 & RD  \\
+bs016759        & 71.0                    & 110.0                    & 82.0                  & 57.0                   & 1.93        & 0.90       & 75.0 & RD \\
+lbg\_111        & 53.0                    & 58.0                     & 90.0                  & 81.0                   & 0.71      & 0.65        & 168.0 & DD \\
+lbg\_38         & 31.0                    & 97.0                     & 76.0                  & 53.0                   & 1.82        & 0.95       & 47.0 & RD \\
+lbg\_94         & 18.0                    & 34.0                     & 65.0                  & 55.0                   & 0.62       & 1.20       & 41.0 & DD \\
+lbg\_109        & 32.0                    & 53.0                     & 101.0                 & 91.0                   & 0.58      & 2.00        & 157.0 & DD \\
+lbg\_24         & 30.0                    & 42.0                     & 64.0                  & 51.0                   & 0.82      & 1.30       & 64.0 & DD  \\
+lbg\_25         & 14.0                    & 33.0                     & 53.0                  & 41.0                   & 0.8       & 1.20        & 87.0 & DD  \\
+lbg\_32         & 79.0                    & 121.0                    & 104.0                 & 76.0                   & 1.58       & 1.90       & 11.0 & RD  \\
+lbg\_91         & 58.0                    & 91.0                     & 98.0                  & 71.0                   & 1.28       & 0.90        & 40.0 & RD \\
+lbg\_113        & 0.0                    & 0.0                      & 116.0                 & 112.0                  & 0.0         & 0.90       & 28.0 & DD \\
+s\_sa22a-d3   & 57.0                    & 109.0                    & 127.0                 & 93.0                   & 1.16        & 1.80       & 30.0 & RD \\
+n3\_009       & 32.0                    & 47.0                     & 77.0                  & 48.0                   & 1.0       & 1.07       & 20.0 & RD  \\
+lab18         & 44.0                    & 41.0                     & 87.0                  & 62.0                   & 0.67     & 0.45       & 54.0 &  DD  \\
+s\_sa22b-c20  & 79.0                    & 139.0                    & 112.0                 & 48.0                   & 2.87       & 1.60       & 37.0 & RD  \\
+n\_c3         & -                    & -                      & 96.0                  & 78.0                   & -        & 0.55       & -  & DD     \\
+s\_sa22b-d9   & -                    & -                      & 99.0                  & 82.0                   & -      & 0.50       & 163.0 & DD    \\
+$^{*}$lab25         & 42.0                    & 48.0                     & 80.0                  & 49.0                   & 0.98       & -       & 72.0 & DD    \\
+$^{*}$s\_sa22b-d5   & 31.0                    & 57.0                     & 67.0                  & 23.0                   & 2.45      & -       & 60.0 & RD     \\
+$^{*}$s\_sa22b-md25 & 50.0                    & 57.0                     & 102.0                 & 75.0                   & 0.76       & -       & 9.0 & DD      \\
+$^{*}$n3\_006       & 41.0                    & 81.0                     & 144.0                 & 125.0                  & 0.65      & -       & 156.0 & DD
 
@@
       \small
-      \item $^{*}$ No clearly defined kinematic axis; $V_{obs}$ and $V_{C}$ not defined.
-      \item $^{**}$ No HST coverage; see table \ref{tab:phys-props}
+      \item $^{a}$ RD = Rotation Dominated; DD = Dispersion Dominated
+      \item $^{*}$ No HST coverage; see table \ref{tab:phys-props}
     \end{tablenotes}
@@
   \end{table*}
+
+\subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}
+
+The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT in section \cref{subsubsec:galfitting}, to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
+This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
+Significant misalignment between the two axes can however be a signature of galaxy interaction.
+
+The resolved KDS galaxies at $z \sim 3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 35^{\circ}$), and this observation has several potential explanations.
+For the majority of galaxies we do not believe we are in a regime where prominent morphological features are resolved in the HST imaging, so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
+However there are some cases where morphological tidal features could affect $PA_{morph}$ such as the GOODS-S galaxies bs006541, bs008543, cdfs\_lbg\_105, cdfs\_lbg\_109 and cdfs\_lbg\_111.
+Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
+This generally does not give the same answer as simply connecting the velocity extrema, as we have verified by rotating $PA_{Kin}$ in 1$^{\circ}$ increments and choosing the value which maximises the velocity gradient, calling this $PA_{rot}$.
+If the direction of the `zero-velocity strip' across the centre of the velocity maps is not perpendicular to the line connecting the velocity extrema, the $PA_{Kin}$ determined from MCMC will be different to the $PA_{Kin}$ determined from rotation (e.g.
+GOODS-S galaxy bs006541).
+As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ makes a median difference of xxx to the final $V_{C}$, a difference which does not affect the outcomes of this work.
+
+There do appear to be some galaxies that have low axis ratios, so that $PA_{morph}$ should be well constrained, and $\Delta PA$ values of $\sim$ 90$^{\circ}$ (e.g.
+GOODS-S galaxy cdfs\_lbg\_38 and SSA22 galaxy s\_sa22a-d3).
+At present there does not appear to be any obvious explanation for why this is the case.
 
@@
 The same process is applied to compute the errors on the sample medians, and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
-In section \cref{subsec:redshift_evolution} we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout section \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
 
 \subsubsection{GHASP}\label{subsubsec:GHASP}
+The GHASP survey \citep[E08]{Epinat2008a,Epinat2008} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to derive 3D H$\alpha$ datacubes.
+The data extend out to several half-light radii and in each case an analytic function is fit to determine $V_{C}$, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
+We use the tabulated values from this survey as a local comparison sample.
 
 \subsubsection{DYNAMO}\label{subsubsec:DYNAMO}
+In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
+The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, making this an excellent sample for comparisons to high redshift.
+$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.3R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
+We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.
 
 \subsubsection{KROSS}\label{subsubsec:KROSS}
+We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}[M_{\odot}])=9.9$ and $z\sim0.9$.
+$V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) and the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius, and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
+These quantities are then beam-smearing corrected as described in H17 section 3.3.3. 
+Due to the consistency of modelling and measurement techniques these form a robust $z\sim0.9$ comparison sample.
 
 \subsubsection{KMOS$^{3D}$}\label{subsubsec:kmos_3d}
+The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
+At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.
+The rotational velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
+No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the section \cref{subsec:redshift_evolution} plots.
 
 \subsubsection{MASSIV}\label{subsubsec:MASSIV}
-
-\subsubsection{SINS$^{3D}$}\label{subsubsec:SINS}
-
-\subsubsection{LAW\_09}\label{subsubsec:law_09}
-
-\subsubsection{AMAZE}\label{subsubsec:AMAZE}
-
-The SINS sample uses a Kinemetry approach described for \citep{Shapiro2008,ForsterSchreiber2009,Cresci2009} which quantifies asymmetries in both the velocity and velocity dispersion maps to empirically differentiate between rotating and non-rotating systems.
-In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, with the authors also commenting that the S/N of the data is not sufficient to accurately determine the required kinemetry parameters.
-In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $PA_{kin}$ and $PA_{morph}$ misalignment (i.e.$\Delta PA$) and the degree of rotational support as quantified with $V_{C}/\sigma_{int}$.
-In \cite{Wisnioski2015} a set of 5 criteria are described in their section 4 which assess the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, $\Delta PA$ and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
-
-The crucial information to extract for the model grids described above for each galaxy, both for this study and for comparison to previous studies, is a measure of the maximum intrinsic circular velocity, $V_{C}$, and a single measurement of the intrinsic velocity dispersion, $\sigma_{int}$, used as a diagnostic for the local random motions of the gas free from large scale velocity gradients \citep[e.g.]{ForsterSchreiber2006,Genzel2008,Gnerucci2011}.
-Previous studies have measured these quantities in several different ways, and it is important to keep this in mind when trying to establish the dynamical evolution of star forming galaxies between different slices of cosmic time.
-Here we briefly mention the measurement techniques of the major surveys we aim to make comparisons to at high redshift, as an attempt to motivate our own method of kinematic parameter extraction.
-The SINS sample \citep{ForsterSchreiber2009} is refined to a high-z robust rotating disk sample \citep{Cresci2009} using a kinemetry approach \citep{Krajnovic2006,Shapiro2008} which searches the moment maps extracted from the SINFONI datacubes for asymmetries which quantify the degree of rotational support against gravity in each galaxy.
-\cite{Cresci2009} model the robust rotators in three dimensions using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
+The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
+An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per section \cref{subsubsec:beam_smearing_corrected_dispersions}.
+We make use of tabulated values presented in E12.
+
+\subsubsection{SINS}\label{subsubsec:SINS}
+The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ at $z\sim2.0$.
+Galaxies in this sample are classified as rotation or dispersion dominated following FS09 section 9.5.1 which classifies rotation dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
+$V_{C}$ values for rotation dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion dominated galaxies using the velocity width.
+Only integrated velocity dispersions are presented for the full sample.
+In addition, \cite[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
 In this approach the $V_{C}$ value comes from the best fitting model parameter, and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
@@
 
-In \cite{Law2009}, a study using OSIRIS, the `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
-
-In their survey at z $\sim 3$, closest in redshift to the current work, \cite{Gnerucci2011} et al.
-derive rotation curves and intrinsic velocity dispersions from a modelled exponential mass distribution, varying the parameters of the model to best fit the observed velocity field.
-The extracted $V_{C}$ value is then the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam smearing (see their Eq.
+It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness, and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
+We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in section \cref{subsec:redshift_evolution} plots.
+
+\subsubsection{LAW 09}\label{subsubsec:law_09}
+In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}[M_{\odot}])=10.0$ at $z\sim2.3$.
+The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
+Beam-smearing corrections are not applied to these quantities.
+We use tabulated data in L09 to compare with the $\sigma_{int}$ distribution, but make no comparisons with the observed velocity-shear values.
+
+\subsubsection{AMAZE}\label{subsubsec:AMAZE}
+The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
+In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq.
 8).
-
-In the MASSIV sample, \citep{Epinat2012}, spanning $0.9 < z < 1.6$, the authors use a 2D arctangent fit to the data and extract $V_{C}$ from the model at $R_{last}$, this being the radius where the S/N of the data drops below 3.
-The $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the $\sigma_{model}$ value as per \cite{Epinat2010}, which is the contribution from beam smeaing assuming the best-fitting model parameters.
-
-In KMOS$^{3D}$, covering two redshift regions at $z \sim 1.0$ and $z \sim 2.3$, \cite{Wisnioski2015} compute $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is computed from the $\sigma_{obs}$ map far away from the kinematic centre, where the effects of beam smearing should be negligible.
-In the KROSS sample at $z \sim 1$, \cite{Stott2016} also model the 2D velocity field using an arctangent function, and after finding the best fitting parameters using a genetic algorithm, extract $V_{C}$ at a fiducial radius, which they choose to be $2.2R_{d} \sim 1.3R_{1/2}$, where $R_{d}$ is the galaxy disk radius in the case of an exponential light profile.
-The $\sigma_{int}$ value is computed in two different ways; the first facilitates comparison with KMOS$^{3D}$ results by extracting the instrumental resolution corrected $\sigma_{obs}$ far away from the kinematic centre; the second uses Equation \ref{eq:stott_sigma} to first linearly remove the effects of the local beam smeared velocity gradients, and then correct for instrumental resolution in quadrature (an approach which they verify in their Appendix A).
-
-\begin{equation}\label{eq:stott_sigma}
-   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \frac{\Delta V}{\Delta R}\right)^{2} - \sigma_{inst}^{2}}
-\end{equation}
-
-The derived median $\sigma_{int}$ from these two approaches varies considerably, as highlighted in Figure 8 of their paper.
-
-In the most recent KROSS paper, \citep{Harrison2017}, exponential disk models, \cite{Freeman1970}, are fit to the data extracted along $PA_{kin}$ in 1D to facilitate extraction of the observed velocity at $2R_{1/2}$ (where $2R_{1/2} \sim 3.4R_{d}$).
-The $\sigma_{int_{obs}}$ is also extracted at $2R_{1/2}$ when the data extend to this radius, and when they do not $\sigma_{int_{obs}}$ is taken to be the median of the $\sigma_{obs}$ map.
-Using a suite of mock KMOS data with exponential intrinsic flux distributions and $PA_{morph}$ coincident with $PA_{kin}$s, convolved with various atmospheric seeing profiles, beam smearing correction factors are derived as a function of both the velocity gradient and the ratio $R_{d}/R_{PSF}$ Johnson et al.
-in prep.
-This correction factors are applied to compute $V_{C}$, with a median correction factor of 1.2 at $3.4R_{1/2}$.
-The same treatment is applied to the outer $\sigma_{int_{obs}}$ values, with a median correction factor of 0.97, and when unavailable a seperate correction factor is applied to the median of the $\sigma_{obs}$ map with a median value of 0.8 (see also \citep{Burkert2016a} for similar simulations of mock data and derivations of beam smearing correction factors).
-
-Clearly there are many different approaches for computing the same intrinsic kinematic parameters which we hope to compare across cosmic time intervals, but despite the diversity over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam smearing using similar approaches.
-This trend towards consistency is encouraging, and as described in \cref{subsec:3d modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam smearing effects quantified in the modelling.
-Our small sample size has allowed us to compute beam smeared models, and the corresponding intrinsic models, for each galaxy.
+A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
+We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
+Also, for 5 galaxies in G11 $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error equal to 1.
+The $\sigma_{int}$ errors for individual galaxies are generally very small, and for 3 galaxies the $\sigma_{int}$ value is consistent with 0kms$^{-1}$.
+For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
+As a result of these selection caveats we denote G11 results with clear symbols throughout the plots in section \cref{subsec:redshift_evolution} and plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated.
+
+This summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
+This trend towards consistency is encouraging, and as described in section \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
+We stress that keeping in mind sample selection, mass ranges and kinematic parameter extraction methods are crucial when comparing results between different surveys.
 
 \subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
-% chancing my luck a bit here with this paragraph
-Classification into different kinematic categories at $z \sim 3.5$ is necessary for quantifying the fraction of KDS galaxies which are isolated `rotation dominated' with $V_{C}/\sigma_{int} > 1$, isolated `dispersion dominated' with $V_{C}/\sigma_{int} < 1$ and the fraction taking part in interactions with other galaxies.
-In the local universe, main sequence galaxies are completely dominated by rotational motions, with the ratio of $V_{C}/\sigma_{int} \sim 10$ or higher \citep{Epinat2008,Epinat2008a}, with this ratio observed to decline over time as random motions increase \citep[e.g.][]{ForsterSchreiber2009,Law2009,Epinat2012,Wisnioski2015,Stott2016}.
-By studying the Rotation Dominated Fraction (RDF) of KDS galaxies, and the mean value of the ratio $V_{C}/\sigma_{int}$ we hope to gain an understanding of balance of gravitational support provided by rotational and random motions.
-$V_{C}$ and $\sigma_{int}$ are both outputs of the dynamical model, so we describe here a pre-modelling morpho-kinematic classification for all KDS galaxies which are spatially resolved in the [O~{\sc III}]$\lambda$5007 emission line, to inform us which galaxies it is appropriate to attempt dynamical modelling.
-
-In this work we are in a similar S/N and redshift regime as \cite{Gnerucci2011} and so we aim to keep the classification criteria simple.
-This involves a joint visual inspection of the velocity fields and associated HST imaging for all spatially resolved KDS galaxies.
-One benefit of studying the high resolution imaging in tandem is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
-These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam smearing or in regions spatially offset from the centre of the galaxy.
-A second benefit is to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective, but are clearly two or more potentially interacting components at slightly different redshift as revealed by higher resolution HST photometry.
+We proceed to make use of the morphological and kinematic information described above to classify resolved KDS galaxies into three categories; \textbf{(1)} Rotation Dominated; \textbf{(2)} Dispersion Dominated; \textbf{(3)} Mergers.
+Previous studies have used various classification schemes of varying complexity to identify which galaxies fall into these categories, and also to identify galaxy which appear `disky'.
+The includes the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in FS09 and C09.
+In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies in by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
+In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
+In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in section \cref{subsubsec:AMAZE}.
+
+\subsubsection{KDS merger candidates}\label{subsubsection:merger_candidates}
+KDS galaxies are classified as mergers when more than one component is identified in the high-resolution imaging.  
+One benefit of studying the HST photometry in tandem is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
+These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
+A second benefit is to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
+can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging.
+In short, the galaxies with multiple photometric components do not always have disordered kinematics, and so the kinematics alone are not sufficient for classification.
 It is difficult to distinguish in some cases between two HST components rotating together in a single disk (i.e.
@@
 
-In 4/23 of the resolved GOODS-S galaxies (one count per merger, 2 mergers in each of the GOODS-S pointings) we clearly identify signs of multiple components or merging in the HST high-resolution imaging.
-In 9/20 of the resolved SSA22 galaxies we identify clear mergers from the HST imaging, noting that 8 of these are in SSA22-a (80$\%$ of the spatially resolved sample in that pointing, although potentially higher as one of the galaxies is without HST coverage), which is the pointing close to the centre of the $z \sim 3.1$ proto-cluster.
-We note that the 1/11 mergers reported in SSA22-b is a lower limit, since there are 3 galaxies which do not have HST coverage in this pointing, although the pointing is spatially offset to the south of the protocluster centre in SSA22-a, and consequently is less dense.
-This observation in SSA22-a is perhaps unsurprising in such a high-density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas and the morphological evolution of these galaxies.
+In 6/34 of the resolved KDS field galaxies (one count per merger) we clearly identify signs of multiple components or merging in the HST high-resolution imaging, which translates into a merger rate of 18\%.
+In 8/9 resolved KDS cluster galaxies we identify multiple photometric components, translating into a merger rate of 89\%  (see table \ref{tab:pointings}).
+The higher cluster galaxy merger rate is perhaps unsurprising in such a high-density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas and the morphological evolution of these galaxies.
 The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
-We reject these merger candidates from the following dynamical analysis presented in \cref{sec:Kinematic_Properties}, keeping the KDS galaxies with HST coverage with the caveat that we do not have a clear morphological classification.
+We do not consider these merger candidates in the results section \cref{sec:results}, but keep the KDS galaxies without HST coverage on the basis that we do not identify double components in the galaxy continuum maps.
 In Appendix \cref{app:mergers} we present the HST imaging, kinematic maps and 1-dimensional kinematic extractions of the merger candidates for the KDS galaxies.
-Many of these are rotation doppelg{\"a}ngers and can be fit with the arctangent model (see \cref{subsec:3d modelling}) with a low $\chi ^{2}$ value, highlighting again the importance of the HST photometry for determining true rotation.
-The best fitting smeared and intrinsic models for the modelling sample in both are plotted in \cref{app:kinematics_plots}, where the galaxies have been divided into dispersion and rotation dominated categories as determined by the ratio $V_{C}/\sigma_{int}$, described in more detail throughout \cref{subsubsec:rotation_and_mergers}.
-
-The galaxies classified as mergers are also plotted in \cref{app:mergers}, as well as the dispersion dominated galaxies which have not been d with the full 3D modelling in \cref{app:dispersion_dominated,app:dispersion_dominated}.
-
-For the spatially resolved galaxies which are not merger candidates, we extract in synthetic apertures along an axis joining the velocity extrema to search for the presence of a smooth velocity gradient indicative of rotation within a disk.
-In 1/23 and 3/20 resolved galaxies in GOODS-S and SSA22 respectively we find no such gradient, and do not attempt to fully model the kinematics of the galaxies to determine $V_{C}$ and $\sigma_{int}$.
-We assume that there is very little rotational support in these galaxies and take the $\sigma_{int}$ value as the median of the intrumental resolution corrected velocity dispersion map.
-To sumamrise, galaxies are passed to the full dynamical modelling of \cref{sec:Kinematic_Properties} if:
-\begin{itemize}
-    \item They are spatially resolved in the [O~{\sc III}]$\lambda5007$ emission line
-    \item They have a clear, monotonic velocity gradient along a single kinematic axis
-    \item They are isolated as revealed by high-resolution HST imaging
-\end{itemize}
-
-The galaxies passing these criteria shall be referred to as the modelling sample throughout the remainder of the paper, and we make no further distinction between galaxies in the SSA22 and GOODS-S fields.
-It is only these galaxies for which we can measure $V_{C}$, and to which the `$V_{C}$ measured' legend titles refer throughout \ref{sec:results}.
-
-\subsubsection{Kinematic sample summary}\label{subsubsec:kin_sample_summary}
+
+\subsubsection{Isolated KDS classification}\label{subsubsection:isolated_classification}
+As a result of the unusually high density of mergers in the cluster environment, we omit these galaxies from further analysis and calculate rotation and dispersion dominated percentages with repsect to the total number of resolved galaxies in the field environment (34, see table \ref{tab:pointings}).
+The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/34 or 38\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$,15/34 or 44\% of the sample, as indicated in table \ref{tab:kin_props}.
+We plot the best fitting smeared and intrinsic models for the resolved KDS field galaxies \cref{app:kinematics_plots}, where the galaxies have been divided into dispersion and rotation dominated categories respectively in sections \cref{app:rotation_dominated} and \cref{app:dispersion_dominated}.
+
+\subsubsection{Summary of the final sample for further analyses}\label{subsubsec:kin_sample_summary}
+In summary, we have analysed the 77 $z\sim3.5$ SFGs initially targetted as part of the KDS, finding spatially resolved [O~{\sc III}]$\lambda$5007 emission in 43 galaxies (56\%).
+These resolved galaxies cover both cluster and field environments and due to the unusually high merger rate of 89\% in the cluster environment, we omit the 9 spatially resolved galaxies in this pointing from further consideration.
+
+In the remaining sample of 34 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 18\%, and following the classification described in section \cref{subsubsection:isolated_classification} we find 13 rotation dominated galaxies (38\%) and 15 dispersion dominated galaxies (44\%) in the field sample.
+For these 28 galaxies we have measured morphological parameters using GALFIT to fit exponential disks to the HST imaging (see table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$, $V_{C}$, and the intrinsic velocity, $\sigma_{int}$ (see table \ref{tab:kin_props}).
+Throughout the remainder of the paper we discuss the derived kinematic properties of these 28 galaxies in further detail.
 
@@
     \end{subfigure}
-    \caption{Correlations between observed KDS properties (y-axis) and the intrinsic properties (x-axis) recovered following the beam smearing analysis.
-    Plots (a) and (b) highlight the strong positive correlation between the observed and intrinsic velocities and velocity dispersions, verifying that the beam smearing corrections are not generally over-extrapolating beyond the values recovered from the data themselves.
-    Plot (c) shows the positive correlation between velocity dispersion and velocity, demonstrating that the broadening of $\sigma$ in the beam smearing is largely a function of the strength of the velocity gradient in the galaxy.}
+    \caption{Correlations between observed KDS properties (y-axis) and the intrinsic properties (x-axis) recovered following the beam-smearing analysis.
+    Plots (a) and (b) highlight the strong positive correlation between the observed and intrinsic velocities and velocity dispersions, verifying that the beam-smearing corrections are not generally over-extrapolating beyond the values recovered from the data themselves.
+    Plot (c) shows the positive correlation between velocity dispersion and velocity, demonstrating that the broadening of $\sigma$ in the beam-smearing is largely a function of the strength of the velocity gradient in the galaxy.}
     \label{fig:observed_and_intrinsic}
@@
 \subsection{Derived Kinematic Properties}
-Equipped with $PA_{Kin}$, $V_{C}$ and $\sigma_{int}$ for each of the resolved and non-interacting galaxies in the KDS, we first interpret these at $z \sim 3.5$, comparing with the \cite{Gnerucci2011} (G11) results at similar redshift throughout \cref{subsubsec:kin_misalignment}-\cref{subsubsec:dynamical_masses} and then in the context of galaxy evolution by comparing with samples across a wide redshift baseline in \cref{subsubsec:sigma_evolution} - \cref{subsubsec:v_evolution}.
-\subsubsection{Kinematic and Photometric Misalignment}\label{subsubsec:kin_misalignment}
-The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT as described in \cref{subsubsec:galfitting}, to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
-In figure \ref{fig:delta_pa} (a) the absolute difference between the position angles, $\Delta PA = |PA_{Kin}-PA_{morph}|$, is plotted as a function of the axis ratio, $\frac{b}{a}$, also determined by GALFIT from the HST photometry.
-The mean and median $\Delta PA$ values are 46$^{\circ}$ and 26$^{\circ}$ respectively, and $\Delta PA$ tends to increase as the axis ratio increases.
-Similar analysis is described in \citep[e.g.][]{Epinat2012,Wisnioski2015,Harrison2017} wherein rotating galaxies generally have excellent agreement between the position angles, with $\Delta PA$ increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
-This is due to the connection between galaxy inclination and axis ratio, with the lowest inclination galaxies showing the most morphological elongation, and the direction of this elongation on the sky is indicative of the galactic plane of rotation.
-
-\begin{figure*}
-    \centering \hspace{-1.3cm}
-    \begin{subfigure}[h!]{0.5\textwidth}
-        \centering
-        \includegraphics[height=3.5in]{delta_pa_vs_axis_ratio.png}
-        %\caption{$\Delta PA$ vs. axis ratio}
-    \end{subfigure} \hspace{0.4cm}
-    \begin{subfigure}[h!]{0.5\textwidth}
-        \centering
-        \includegraphics[height=3.5in]{delta_pa_vs_sigma.png}
-        %\caption{$\Delta PA$ vs. $\sigma_{obs}$}
-    \end{subfigure}
-    \caption{The absolute difference between $PA_{morph}$ and $PA_{kin}$, $\Delta PA$, is plotted in panel (a) against the GALFIT determined galactic minor to major axis ratio for all KDS galaxies with both HST coverage and dynamical modelling.
-The median difference computed in bins of 0.2 x-axis width and the standard deviation in each of these bins are also plotted as the black line and light blue shaded region respectively.
-The misalignment clearly increases as a function of axis ratio, but is also generally larger than reported in previous IFU studies at lower redshift, as described throughout the text.
-In panel (b) we explore the possibility that the photometric and kinematic misalignment may be a function of the observed velocity dispersion.
-There appears to be some suggestion that with increasing $\sigma_{obs}$, larger $\Delta PA$ are observed but we do not quantify this connection and conclude only that the elevated velocity dispersions at high redshift could be a contributing factor in increasing the misalignment between the two axes.}
-    \label{fig:delta_pa}
-\end{figure*}
-
-\cite{Wisnioski2015} report mean and median $\Delta PA$ values of 18$^{\circ}$ and 12$^{\circ}$ respectively and exclude galaxies from their rotating disk sample when $\Delta PA > 30^{\circ}$.
-In the local universe the agreement between morphological and kinematic position angles is generally $\Delta PA < 20^{\circ}$ \citep[e.g.][]{Epinat2008,Barrera-Ballesteros2014,Barrera-Ballesteros2015} and it is shown that significant misalignment is often a signature of galaxy interaction.
-In a recent paper by \cite{Rodrigues2016}, a subset of the KMOS$^{3D}$ galaxies at $z \sim 1$ have been re-analysed to establish the fraction of disk-like galaxies at this redshift given the criteria presented in section 4.1 of \cite{Wisnioski2015}.
-In this paper the authors note that single \Sers fits to the HST photometry can introduce biases when the galaxies show prominent morphological features such as bars, spiral arms and tidal tails, and instead measure $PA_{morph}$ using the outer-most isophote in a series of concentric elliptical isophotes with the IRAF task ELLIPSE.
-The resolved KDS galaxies at $z \sim 3.5$ have generally larger $\Delta PA$ values than those at lower redshift, and this observation has several potential explanations.
-For the majority of galaxies we do not believe we are in a regime where prominent morphological features are resolved in the HST imaging, so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
-However there are some cases where morphological tidal features could affect $PA_{morph}$ such as the GOODS-S galaxies bs006541, bs008543, cdfs\_lbg\_105, cdfs\_lbg\_109 and cdfs\_lbg\_111.
-Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
-This generally does not give the same answer as simply connecting the velocity extrema, as we have verified by rotating $PA_{Kin}$ in 1$^{\circ}$ increments and choosing the value which maximises the velocity gradient, calling this $PA_{rot}$.
-If the direction of the `zero-velocity strip' across the centre of the velocity maps is not perpendicular to the line connecting the velocity extrema, the $PA_{Kin}$ determined from MCMC will be different to the $PA_{Kin}$ determined from rotation (e.g.
-GOODS-S galaxy bs006541).
-The observed velocity map contains meaningful information about $PA_{Kin}$ beyond just a consideration of the velocity extremes, and we believe it is more physically meaningful to allow the $PA_{Kin}$ to explore and choose values which best fit the full 2D observed velocity field.
-As a test, extracting the $V_{C}$ values along $PA_{rot}$ makes xxx difference to the values on average for the sample. 
-The $1-\sigma$ errorbars in Figure \ref{fig:delta_pa} are determined by the 16th and 84th percentile distribution of the MCMC samples.
-For SSA22 the situation is complicated by the lower integration times of the HST data, and the use of ACS 814W imaging in which the galaxies have smaller apparent $R_{1/2}$ values due to observing light from younger stars.
-This is a limitation of this study and the errorbars in $\Delta PA$ reflect the poorer imaging data in this field.
-There do appear to be some galaxies that have low axis ratios, so that $PA_{morph}$ should be well constrained, and $\Delta PA$ values of $\sim$ 90$^{\circ}$ (e.g.
-GOODS-S galaxy cdfs\_lbg\_38 and SSA22 galaxy s\_sa22a-d3).
-There does not appear to be any obvious explanation for why this is the case.
-In practice, since the intrinsic [O~{\sc III}]$\lambda5007$ profile is determined by the GALFIT model throughout the modelling in \cref{subsec:3d modelling}, the $\Delta PA$ value has an impact on the derived $V_{C}$.
-As $\Delta PA$ increases, the model beam smeared velocity reaches maximum value at larger radii, and so the inferred intrinsic $V_{C}$ becomes larger to provide an adequate fit to the data.
-This effect is small until $\Delta PA$ reaches $\sim 60^{\circ}$, in which case the $V_{C}$ can be up to 30kms$^{-1}$ larger, with this an interesting consequence of modelling the intrinsic light profile with a different position angle to that of the velocity field.
-We have also explored the possibility that $\Delta PA$ is correlated with $\sigma_{obs}$ and that the increased random motions or turbulence within the galaxies are the driving force behind kinematic and morphological misalignment.
-There appears to be some suggestion that the two quantities are connected, although we make no attempt to quantify this, and conclude that the elevated velocity dispersions at high redshift could be a contributing factor in the observation of large mean $\Delta PA$.
-
-We do not restrict the sample on the basis of $\Delta PA$ due to the increased uncertainty in determining both $PA_{morph}$ and $PA_{Kin}$ and due to the appearance of galaxies which have misalignment between $PA_{morph}$ and $PA_{Kin}$ at low axis ratios.
+In the previous sections we have presented our morphological and kinematic analysis for the 77 galaxies representative of both cluster and field environments in the KDS survey.
+These galaxies are representative of typical SFGs $z\sim3.5$ as verified by comparing to fits to the galaxy main sequence at this redshift.
+Through a combined morpho-kinematic classification described in section \cref{subsec:morpho-kin-class} we reduce the sample to 28 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
+not merger candidates).
+For these galaxies we have measured morphological properties as listed in table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
+The full analysis grids for these 28 galaxies and the merger candidates are plotted in appendix \cref{app:kinematics_plots}.
+
+Throughout the following sections we analyse the derived kinematic parameters for these 28 galaxies, placing them in the context of galaxy evolution using the comparison samples described in section \cref{subsubsec:comparison_samples} which span a wide redshift baseline.
 
 \subsubsection{Observed and Intrinsic Properties}\label{subsubsec:observed_and_intrinsic}
-In Figure \ref{fig:observed_and_intrinsic} we investigate correlations between the observed and intrinsic dynamical properties of the resolved KDS galaxies, to highlight the mean beam smearing correction factors, the mean values of the observed and intrinsic distributions and the factors driving the beam smearing corrections.
+In Figure \ref{fig:observed_and_intrinsic} we investigate correlations between the observed and intrinsic dynamical properties of the resolved KDS galaxies, to highlight the mean beam-smearing correction factors, the mean values of the observed and intrinsic distributions and the factors driving the beam-smearing corrections.
 Figure \ref{fig:observed_and_intrinsic} (a) and (c) contain all resolved KDS galaxies with a valid $V_{C}$ measurement from the modelling sample, whereas (b) contains all resolved KDS galaxies, with $\sigma_{int}$ determined by subtracting the instrumental resolution value from $\sigma_{obs}$ for those galaxies without a valid $V_{C}$ measurement.
@@
 The mean and median $V_{C_{smeared}}$, the extrapolated and inclination corrected observed velocity, to $V_{C}$ correction factors, are 1.30 and 1.21 respectively.
-In Figure \ref{fig:observed_and_intrinsic} (a) and (b) we find a strong positive correlation between both the observed and intrinsic velocities and velocity dispersions, which verifies that the beam smearing corrections do not alter the shape of the distributions of $V_{obs}$ and $\sigma_{obs}$ determined from the raw data.
+In Figure \ref{fig:observed_and_intrinsic} (a) and (b) we find a strong positive correlation between both the observed and intrinsic velocities and velocity dispersions, which verifies that the beam-smearing corrections do not alter the shape of the distributions of $V_{obs}$ and $\sigma_{obs}$ determined from the raw data.
 
@@
         \centering
-        \includegraphics[height=3.5in]{v_over_sigma_versus_v.png}
+        \includegraphics[height=3.5in]{v_over_sigma_versus_mass.png}
         %\caption{$\Delta PA$ vs. $\sigma_{obs}$}
@@
     In panel (b) the distribution of all KDS galaxies with $V_{C}$ measurements in the $V_{C}$/$\sigma_{int}$ vs. $V_{C}$ plane is shown.
-    $V_{C}$/$\sigma_{int}$ increases as a function of $V_{C}$ following the beam smearing corrections applied to both quantities.
+    $V_{C}$/$\sigma_{int}$ increases as a function of $V_{C}$ following the beam-smearing corrections applied to both quantities.
     We also mark the $V_{C}$/$\sigma_{int}=1$ line in this panel, finding that half of the KDS galaxies with $V_{C}$ measurements have $V_{C}$/$\sigma_{int} > 1$, despite all showing velocity gradients in the observations.
@@
 \centering
-\includegraphics[width=0.48\textwidth]{rv_squared.png}
+\includegraphics[width=0.49\textwidth]{rv_squared.png}
 \caption{We plot the ratio $M_{vir}/M_{\star}$ computed using only rotational velocities (Eq.
@@
     The vertical location of the mean datapoints in this plane are mediated by the mean $M_{\star}$ of each survey, which is itself connected to the mean gas fraction. 
-    We note also that the Law 2009 datapoint has not been corrected for beam smearing and so represents an upper limit on $\sigma_{int}$ for that survey. 
+    We note also that the Law 2009 datapoint has not been corrected for beam-smearing and so represents an upper limit on $\sigma_{int}$ for that survey. 
     Panel (b) presents the mean, median and distributions of $V_{C}$ measurements of these surveys between $0 < z < 4$, with the large red circle representing the KDS measurement.
@@
 To complement the surveys already described throughout \cref{subsubsec:RDF_evolution}, we add data from \cite{Law2009} to explore the evolution of $\sigma_{int}$ values across cosmic time.
-In this study, resolved data are collected with the OSIRIS instrument for 13 SFGs with $log(M_{\star}[M_{\odot}])=10.0$.
-We note that the $\sigma_{mean}$ values and errors tabulated in this paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam smearing in any way.
-These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam smearing corrected, or extracted at the galaxy outskirts where the beam smearing is much smaller.
+We note that the $\sigma_{mean}$ values and errors tabulated in this paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
+These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the beam-smearing is much smaller.
 \cite{Law2009} attribute the cosmic increase in $\sigma_{int}$ to much larger gas fractions at high redshift, with the gas accumulated through rapid cold-mode accretion along cosmic filaments.
@@
 This, in combination with figure \ref{fig:dyn_masses}, suggests that the velocity dispersion could be responsible for providing partial dynamical support in these systems.
-\cite{Law2009} observe galaxies with similarly low mean velocity shear and high velocity dispersions (the velocities are not plotted here since the tabulated values are not inclination or beam smearing corrected) and attribute this to instabilities which occur when the cold gas becomes dynamically dominant following efficient accretion and in line with the high gas fractions observed at high redshift.
+\cite{Law2009} observe galaxies with similarly low mean velocity shear and high velocity dispersions (the velocities are not plotted here since the tabulated values are not inclination or beam-smearing corrected) and attribute this to instabilities which occur when the cold gas becomes dynamically dominant following efficient accretion and in line with the high gas fractions observed at high redshift.
 We caution that at high redshift these $V_{C}$ measurements are challenging for the reasons stated above, however our data appear to support a scenario in which low $M_{\star}$ galaxies experience elevated random motions related to the rapid accretion of cold gas, which is partially supported gravitationally by these random motions and may contribute to the observation of low $V_{C}$ values.
@@
 \includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_93_grid_paper.png}
-\caption{High resolution imaging is important not only for reliably recovering the morphological parameters, but also to explain peculiar features in the observed velocity and velocity dispersion fields.
+\caption{High-resolution imaging is important not only for reliably recovering the morphological parameters, but also to explain peculiar features in the observed velocity and velocity dispersion fields.
 In the two examples above, multiple components in the HST imaging clearly correspond to marginally different [O~{\sc III}]$\lambda$5007 emission wavelengths, which manifest as velocity shifts in individual spaxels and broadens the observed dispersion pattern where the emission lines at different wavelengths merge.
 Overplotted onto the models are the data values and uncertainties extracted along $PA_{kin}$.
-These figures also show the HST imaging for each galaxy, the best fit galfit model and residuals, 2D maps of the [O~{\sc III}]$\lambda$5007 flux, observed velocity, observed dispersion, best fitting smeared model velocity, data - model residuals, intrinsic velocity dispersion (observed dispersion corrected for beam smearing and instrumental resolution as described in \cref{subsubsec:param_extraction}) as well as a plot of 1D extractions along the observed, intrinsic and beam smeared dispersion maps.}
+These figures also show the HST imaging for each galaxy, the best fit galfit model and residuals, 2D maps of the [O~{\sc III}]$\lambda$5007 flux, observed velocity, observed dispersion, best fitting smeared model velocity, data - model residuals, intrinsic velocity dispersion (observed dispersion corrected for beam-smearing and instrumental resolution as described in \cref{subsubsec:param_extraction}) as well as a plot of 1D extractions along the observed, intrinsic and beam smeared dispersion maps.}
 \label{app:goods_mergers_1}
@@
 To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40kms^{-1}$ and $\sigma_{int} = 80kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values.
-When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam smearing correction decreases, as the impact of convolution with other lines that have a shifted velocity centre is less severe.
-Conversely, assuming $\sigma_{int} = 40km^{-1}$ increases the beam smearing.
+When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with other lines that have a shifted velocity centre is less severe.
+Conversely, assuming $\sigma_{int} = 40km^{-1}$ increases the beam-smearing.
 We calculate the minimum and maxmimum intrinsic velocity dispersion, $\sigma_{o-84-40}$ and $\sigma_{o-16-80}$, using equations \ref{eq:sig_84_40} and \ref{eq:sig_16_80} respectively:

### 2017-02-13 paper.tex
finished new draft

@@
 % Keep the title short and informative.
-\title[KDS: dynamical properties of z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
+\title[KDS: dynamical properties of 77 z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
 Programme IDs: }}
@@
 The KDS mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with the increase of $\sigma_{int}$ with redshift reported across the comparison samples.
-However we find that only $39 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
+However we find that only $37 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
 The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e.
@@
 GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 18 & K, H & 31.8 & 0.52 \\
-SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & 2 & 18 & HK & 27.8 & 0.57 \\
+SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
 SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
@@
 In the following sections we describe the approach we have chosen to recover these parameters.
-In section \cref{subsubsection:morph_param_summary} we compare the KDS morphological parameters with those described in \cite{VanderWel2012}, and also with spectroscopically confirmed galaxies in different redshift intervals in order to study the size evolution of SFGs across cosmic time.
+In \cref{subsubsection:morph_param_summary} we compare the KDS morphological parameters with those described in \cite{VanderWel2012}, and also with spectroscopically confirmed galaxies in different redshift intervals in order to study the size evolution of SFGs across cosmic time.
 
@@
 In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
-The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in section \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
+The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
 This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.
@@
 There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
-We provide an overview of these surveys in section \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of the parameters used for comparison to the KDS throughout results section \cref{subsec:redshift_evolution}).
+We provide an overview of these surveys in \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of the parameters used for comparison to the KDS throughout results \cref{subsec:redshift_evolution}).
 
@@
 The beam-smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
-The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in section \cref{subsubsec:observed_and_intrinsic}.
+The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in \cref{subsubsec:observed_and_intrinsic}.
 The $V_{C}$ errors are discussed in \cref{appsubsubsec:model_errors}.
@@
 Convolution of the model velocity field with the seeing profile produces a peak in the beam-smeared velocity dispersion map at the centre of rotation.
-The model therefore provides a beam-smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the beam-smeared dispersion i.e.
+The model therefore provides a beam-smearing correction for the velocity dispersion in every spaxel.
+This is dependent primarily on the magnitude of the velocity gradient across the parameter maps, verified by the positive correlation between observed velocities and velocity dispersions.
+The 2D beam-smearing correction map, $\sigma_{bs}$, is taken as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion i.e.
 $\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
-This is computed for each spaxel to provide the 2D $\sigma_{bs}$ correction map.
-The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in section \cref{appsubsubsec:model_errors}.
+
+The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in \cref{appsubsubsec:model_errors}.
 We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.
@@
 This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.
-
-We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for all of the spatially resolved KDS field galaxies classified as morphologically isolated (29, see section \cref{subsec:morpho-kin-class}).
+We also observe that shape and width of the observed and intrinsic kinematic parameter distributions are equivalent, suggesting that the corrections do not over-extrapolate from the raw numbers.
+
+We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for all of the spatially resolved KDS field galaxies classified as morphologically isolated (29, see \cref{subsec:morpho-kin-class}).
 
@@
 
-The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT in section \cref{subsubsec:galfitting}, to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
+The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT in \cref{subsubsec:galfitting}, to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
 This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
@@
 \subsection{Comparison samples}\label{subsubsec:comparison_samples}
-Throughout section \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
+Throughout \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
 The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission line.
@@
 The same process is applied to compute the errors on the sample medians, and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
-These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout section \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
 
@@
 The rotational velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
-No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the section \cref{subsec:redshift_evolution} plots.
+No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.
 
@@
 The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
-An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per section \cref{subsubsec:beam_smearing_corrected_dispersions}.
+An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
 We make use of tabulated values presented in E12.
@@
 It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness, and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
-We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in section \cref{subsec:redshift_evolution} plots.
+We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in \cref{subsec:redshift_evolution} plots.
 
@@
 For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
-As a result of these selection caveats we denote G11 results with clear symbols throughout the plots in section \cref{subsec:redshift_evolution} and plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated.
+A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{subsec:redshift_evolution}.
+This Unconstrained sample also contains the galaxy s\_sa22a-M38 common between the KDS and G11, classified here as a merger due to double HST components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
+The remaining 5 galaxies we refer to as the AMAZE Clean sample and plot with grey symbols.
+We also plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated.
 
 This summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
-This trend towards consistency is encouraging, and as described in section \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
+This trend towards consistency is encouraging, and as described in \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
 We stress that keeping in mind sample selection, mass ranges and kinematic parameter extraction methods are crucial when comparing results between different surveys.
@@
 In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
-In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in section \cref{subsubsec:AMAZE}.
+In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in \cref{subsubsec:AMAZE}.
 
@@
 The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
-We do not consider these merger candidates in the results section \cref{sec:results}, but keep the KDS galaxies without HST coverage on the basis that we do not identify double components in the galaxy continuum maps.
+We do not consider these merger candidates in the results \cref{sec:results}, but keep the KDS galaxies without HST coverage on the basis that we do not identify double components in the galaxy continuum maps.
 In Appendix \cref{app:mergers} we present the HST imaging, kinematic maps and 1-dimensional kinematic extractions of the merger candidates for the KDS galaxies.
@@
 \subsubsection{Isolated KDS classification}\label{subsubsection:isolated_classification}
-As a result of the unusually high density of mergers in the cluster environment, we omit these galaxies from further analysis and calculate rotation and dispersion dominated percentages with repsect to the total number of resolved galaxies in the field environment (34, see table \ref{tab:pointings}).
-The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/34 or 38\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$,15/34 or 44\% of the sample, as indicated in table \ref{tab:kin_props}.
+As a result of the unusually high density of mergers in the cluster environment, we omit these galaxies from further analysis and calculate rotation and dispersion dominated percentages with repsect to the total number of resolved galaxies in the field environment (35, see table \ref{tab:pointings}).
+The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/35 or 37\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$,15/35 or 43\% of the sample, as indicated in table \ref{tab:kin_props}.
 We plot the best fitting smeared and intrinsic models for the resolved KDS field galaxies \cref{app:kinematics_plots}, where the galaxies have been divided into dispersion and rotation dominated categories respectively in sections \cref{app:rotation_dominated} and \cref{app:dispersion_dominated}.
@@
 
-In the remaining sample of 34 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 18\%, and following the classification described in section \cref{subsubsection:isolated_classification} we find 13 rotation dominated galaxies (38\%) and 15 dispersion dominated galaxies (44\%) in the field sample.
-For these 28 galaxies we have measured morphological parameters using GALFIT to fit exponential disks to the HST imaging (see table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$, $V_{C}$, and the intrinsic velocity, $\sigma_{int}$ (see table \ref{tab:kin_props}).
-Throughout the remainder of the paper we discuss the derived kinematic properties of these 28 galaxies in further detail.
+In the remaining sample of 35 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 17\%, and following the classification described in \cref{subsubsection:isolated_classification} we find 13 rotation dominated galaxies (37\%) and 16 dispersion dominated galaxies (46\%) in the field sample.
+For these 29 galaxies we have measured morphological parameters using GALFIT to fit exponential disks to the HST imaging (see table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$, $V_{C}$, and the intrinsic velocity, $\sigma_{int}$ (see table \ref{tab:kin_props}).
+Throughout the remainder of the paper we discuss the derived kinematic properties of these 29 galaxies in further detail.
 
@@
 
-\begin{figure*}
-    \centering
-    \begin{subfigure}[h!]{0.32\textwidth}
-        \centering
-        \includegraphics[height=2.25in]{vobs_vs_vmax.png}
-        %\caption{V$_{obs}$ vs. intrinsic $V_{C}$}
-    \end{subfigure}%
-    \begin{subfigure}[h!]{0.32\textwidth}
-        \centering
-        \includegraphics[height=2.25in]{sigobs_vs_sigint.png}
-        %\caption{$\sigma_{obs}$ vs. intrinsic $\sigma_{int}$}
-    \end{subfigure}
-    \begin{subfigure}[h!]{0.32\textwidth}
-        \centering
-        \includegraphics[height=2.25in]{sigobs_vs_vmax.png}
-        %\caption{$\sigma_{obs}$ vs. $V_{C}$}
-    \end{subfigure}
-    \caption{Correlations between observed KDS properties (y-axis) and the intrinsic properties (x-axis) recovered following the beam-smearing analysis.
-    Plots (a) and (b) highlight the strong positive correlation between the observed and intrinsic velocities and velocity dispersions, verifying that the beam-smearing corrections are not generally over-extrapolating beyond the values recovered from the data themselves.
-    Plot (c) shows the positive correlation between velocity dispersion and velocity, demonstrating that the broadening of $\sigma$ in the beam-smearing is largely a function of the strength of the velocity gradient in the galaxy.}
-    \label{fig:observed_and_intrinsic}
-\end{figure*}
-
-\subsection{Derived Kinematic Properties}
-In the previous sections we have presented our morphological and kinematic analysis for the 77 galaxies representative of both cluster and field environments in the KDS survey.
+In the previous sections we have presented our morphological and kinematic analysis for the 77 galaxies covering both cluster and field environments in the KDS survey.
 These galaxies are representative of typical SFGs $z\sim3.5$ as verified by comparing to fits to the galaxy main sequence at this redshift.
-Through a combined morpho-kinematic classification described in section \cref{subsec:morpho-kin-class} we reduce the sample to 28 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
+Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 29 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
 not merger candidates).
 For these galaxies we have measured morphological properties as listed in table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
-The full analysis grids for these 28 galaxies and the merger candidates are plotted in appendix \cref{app:kinematics_plots}.
-
-Throughout the following sections we analyse the derived kinematic parameters for these 28 galaxies, placing them in the context of galaxy evolution using the comparison samples described in section \cref{subsubsec:comparison_samples} which span a wide redshift baseline.
-
-\subsubsection{Observed and Intrinsic Properties}\label{subsubsec:observed_and_intrinsic}
-In Figure \ref{fig:observed_and_intrinsic} we investigate correlations between the observed and intrinsic dynamical properties of the resolved KDS galaxies, to highlight the mean beam-smearing correction factors, the mean values of the observed and intrinsic distributions and the factors driving the beam-smearing corrections.
-Figure \ref{fig:observed_and_intrinsic} (a) and (c) contain all resolved KDS galaxies with a valid $V_{C}$ measurement from the modelling sample, whereas (b) contains all resolved KDS galaxies, with $\sigma_{int}$ determined by subtracting the instrumental resolution value from $\sigma_{obs}$ for those galaxies without a valid $V_{C}$ measurement.
-
-The mean and median $\sigma_{obs}$ to $\sigma_{int}$ correction factors are 0.79 and 0.77 respectively. 
-The mean and median $V_{C_{smeared}}$, the extrapolated and inclination corrected observed velocity, to $V_{C}$ correction factors, are 1.30 and 1.21 respectively.
-In Figure \ref{fig:observed_and_intrinsic} (a) and (b) we find a strong positive correlation between both the observed and intrinsic velocities and velocity dispersions, which verifies that the beam-smearing corrections do not alter the shape of the distributions of $V_{obs}$ and $\sigma_{obs}$ determined from the raw data.
-
-Figure \ref{fig:observed_and_intrinsic} (c) highlights that galaxies with larger $V_{C}$ values tend to have larger $\sigma_{obs}$, which tells us that the broadening of the median velocity dispersion is driven by the strength of the velocity gradient, as assumed throughout the dynamical modelling section.
-
-The most striking observation here is that the mean and median $V_{C}$ values in the KDS sample are substantially lower than reported by \cite{Gnerucci2011} for the AMAZE sample of galaxies at comparable $M_{\star}$.
-This will be discussed further in \cref{subsubsec:sigma_and_v} and throughout \cref{subsec:redshift_evolution}.
-
-\subsubsection{$\sigma_{int}$ and $V_{C}$}\label{subsubsec:sigma_and_v}
-In figure \ref{fig:v_sig_and_v} (a) we plot the distribution of resolved KDS galaxies with $V_{C}$ measurements in $\sigma_{int}$ vs.
-log($V_{C}$) parameter space, along with the galaxies from G11 plotted in grey.
-We also plot the $V_{C}$ = $\sigma_{int}$ line, which roughly bisects the KDS sample, and indicates the kinematic state of the galaxies as described in the following subsection.
+The full analyses grids for these 29 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}. \\
+
+Throughout the following sections we analyse the derived kinematic parameters for these 29 galaxies, referred to as the `isolated field sample' in the remainder of the paper, placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{subsubsec:comparison_samples}.
+In \cref{subsubsec:comparison_samples} we have also described the variation in the methodology used to compute $V_{C}$ and $\sigma_{int}$ between different surveys as a way to help disentangle true evolution from offsets between derived dynamical values caused by disparate measurement techniques.
+It appears that choice of dynamical model and dynamical parameter extraction method does still play a large role in understanding the evolution of dynamical parameters, and for this reason we have verified that our modelling and measurement techniques are consistent with KROSS $z\sim0.9$ results described in \cite{Harrison2017}, allowing for robust comparisons between this and the isolated field sample.
 
@@
     \end{subfigure}
-    \caption{In panel (a) the distribution of all KDS galaxies with $V_{C}$ measurements in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols, and AMAZE galaxies from G11 with grey.
-    There is no strong correlation between the two parameters in either of these surveys, however several of the $V_{C}$ values in G11 are substantially larger or have $\sigma_{int}$ values consistent with 0kms$^{-1}$.
-    This is despite the two samples having similar ranges in stellar mass, and is probably a consequence of the different modelling techniques used to infer the dynamical parameters.
-    We assume that $\sigma_{int} = 30kms^{-1}$ for the G11 galaxies with reported $\sigma_{int} = 0kms^{-1}$, which is roughly equal to the spectral resolution of the instrument with which they were observed (SINFONI).
+    \caption{In the left panel the distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
+    The AMAZE Clean sample galaxies are plotted with grey symbols and the unconstrained galaxies are plotted with clear symbols.
+    There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement, with the AMAZE Unconstrained galaxies mostly scattering to high $V_{C}$ values, despite having similar stellar mass range to the KDS, as a result of large extrapolations from the data.
     The $V_{C}/\sigma_{int} = 1$ divides the galaxies classified as rotation dominated and dispersion dominated, with dispersion dominated galaxies sitting above the line. 
     The galaxy s\_sa22a-M38, classified here as a merger but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ is marked on the plot.
-    In panel (b) the distribution of all KDS galaxies with $V_{C}$ measurements in the $V_{C}$/$\sigma_{int}$ vs. $V_{C}$ plane is shown.
-    $V_{C}$/$\sigma_{int}$ increases as a function of $V_{C}$ following the beam-smearing corrections applied to both quantities.
-    We also mark the $V_{C}$/$\sigma_{int}=1$ line in this panel, finding that half of the KDS galaxies with $V_{C}$ measurements have $V_{C}$/$\sigma_{int} > 1$, despite all showing velocity gradients in the observations.
-    We discuss the rotation dominated fraction with respect to the full sample in the text.}
+    In the right panel the distribution of the isolated field sample in the $V_{C}$/$\sigma_{int}$ vs. $M_{\star}$ plane is shown, along with the galaxies in the AMAZE Clean sample.
+    We also mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies in this panel, finding that it is the more massive galaxies which tend to a be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
+    We suggest that as galaxies accumulate their stellar populations and exhaust their gas supplies, this leads to a more stable rotating disk and hence evolution towards higher $V_{C}/\sigma_{int}$ values.}
     \label{fig:v_sig_and_v}
@@
 
-The KDS galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is excellent agreement between KDS and AMAZE for $ \sim 50\%$ of the G11 rotating sample.
-The other $ \sim 50\%$ generally have much larger $V_{C}$ values, and three galaxies are reported as having $\sigma_{int}$ consistent with 0kms$^{-1}$.
-We note also that one of the KDS galaxies in SSA22-a classified as a merger due to the double peak in the HST morphology, s\_sa22a-m38, is in the G11 rotating sample (highlighted in Figure \ref{fig:v_sig_and_v}), although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk.
-This difference highlights the classification ambiguity for galaxies with double peaks in both ionised emission line and HST F160W profiles, as the galaxy could fall into either of the categories described above.
-However in the case of s\_sa22a-m38 we also observe a double peak in the spectrum at the flux centre, indicative of two blobs at different redshifts and leading to artificial broadening of $\sigma_{obs}$ towards the centre of the galaxy when the dynamics are measured with single gaussian fits.
-Several of the G11 galaxies plotted here also do not have reported errors on the $V_{C}$ values, and due to the lack of tabulated $V_{obs}$ values it is unclear the extent to which these have been extrapolated from the data.
-It is these high $V_{C}$ G11 galaxies which drive the difference in mean and median $V_{C}$ between the samples.
-Further comparison between the KDS and G11 $\sigma_{int}$ and $V_{C}$ values are made throughout \cref{subsec:redshift_evolution}.
-
-\subsubsection{Rotation Dominated Fraction and Merger Fraction}\label{subsubsec:rotation_and_mergers}
-\begin{table}
-    \centering
-\begin{tabular}{ c c c c c c c c }
-
- \hline
- & N$_{Res}$ & N$_{Merg}$ & $\%$ Merg & N$_{Disp}$ & $\%$ Disp & N$_{RD}$ & RDF  \\
- \hline
-G1 & 12 & 2 & 17 & 4 & 33 & 6 & 0.50 \\
-G2 &  11 & 2 & 19 & 6 & 54 & 3 & 0.27\\
-Sa & 9 & 8 & 89 & 1 & 11 & 0 & 0.0 \\
-Sb & 11 & 1 & 9 & 6 & 54 & 4 & 0.37 \\
- \hline
-\end{tabular}
-\caption{The rotation and merger dominated fractions for each pointing}
-\label{tab:rdf}
-\end{table}
-
-In Figure \ref{fig:v_sig_and_v} (b) we plot the ratio of $V_{C}$/$\sigma_{int}$ against $V_{C}$ for the KDS galaxies, with the former quantity commonly used as an indicator of whether SFGs at different redshifts are rotation dominated $(V_{C}$/$\sigma_{int} > 1)$ or dispersion dominated $(V_{C}$/$\sigma_{int} < 1)$ \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
+\subsection{Rotation dominated fraction and $V_{C}/\sigma_{int}$}\label{subsec:rdf_v_over_sigma}
+
+In figure \ref{fig:v_sig_and_v} (a) we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane.
+We include galaxies from the AMAZE sample (G11) with the grey and clear symbols (this symbol choice and the other comparison samples are described in more detail throughout \cref{subsubsec:comparison_samples}).
+We also plot the $V_{C}$ = $\sigma_{int}$ line, which roughly bisects the KDS sample, and indicates the dispersion and rotation dominated galaxies.
+The KDS galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is good agreement between the KDS and AMAZE Clean samples.
+The galaxies in the AMAZE Unconstrained sample generally have much larger $V_{C}$ values despite occupying a similar stellar mass range to our isolated field sample, with this being a consequence of large model extrapolations beyond the observed data.
+We follow the bootstrapping procedure described in \cref{subsubsec:comparison_samples} to compute isolated field sample error weighted averages and statistical errors.
+The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015} and the mean and median $V_{C}$ values are $78.8^{+5.4}_{-5.1}kms^{-1}$ $60.0^{+7.5}_{-5.9}kms^{-1}$, which is less than at lower redshift.
+These results are placed in the context of previous work throughout \cref{subsec:TF} and \cref{subsec:redshift_evolution}, where we also discuss possible explanations for the increase in $\sigma_{int}$ with redshift.\\
+
+In Figure \ref{fig:v_sig_and_v} (b) we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean sample for reference.
 In the local universe, disky, SFGs are observed to have $V_{C}/\sigma_{int}$ values in excess of 10 (i.e.
 the disks are `well settled'), due to the decline of velocity dispersion across cosmic time, as gas fractions and disk turbulence decrease \citep[e.g.][]{Epinat2008,Epinat2008a}.
-The KDS galaxies above the black, dashed $V_{C}/\sigma_{int} = 1$ line in figure \ref{fig:v_sig_and_v} are classified as rotation dominated, and we plot the full morpho-kinematic grids for these in \cref{app:rotation_dominated}.
-The remainder are dispersion dominated and are plotted in \cref{app:dispersion_dominated}.
-What is striking about many of the dispersion dominated galaxies is that they show clear velocity gradients across the observed velocity maps, and can generally be well fit with the arctangent model.
+Clearly the isolated field sample galaxies are in a different physical regime, with mean and median $V_{C}/\sigma_{int}$ values of $1.08^{+0.18}_{-0.15}$ and $0.97^{+0.14}_{-0.11}$ respectively.
+This is despite many of the dispersion dominated galaxies showing clear velocity gradients across the observed velocity maps (\cref{app:kinematics_plots}), with the arctangent model providing a good fit to the rotation curves.
 This suggests that, for these galaxies, although rotational motions are present within the disks, they are small or comparable with the elevated $\sigma_{int}$ values observed throughout the $z \sim 3.5$ sample.
-This suggests in turn that the random motions traced by $\sigma_{int}$ are probably providing some degree of gravitational support for the total mass of the system (see \cref{subsubsec:dynamical_masses}), in contrast to the local universe in which late-type galaxies are supported entirely by ordered rotation.
-In table \ref{tab:rdf} we list the merger, dispersion and rotation dominated fractions (RDFs) in each of the 4 pointings across GOODS-S and SSA22.
-For all pointings except SSA22-a the detected merger fraction is low, however, as discussed already in \cref{subsec:morpho-kin-class}, almost every spatially resolved galaxy in SSA22-a is taking part in some kind of interaction event.
-This observation has important consequences for the subsequent kinematic and morphological evolution of galaxies in high density environments, especially protoclusters, where the brightest cluster galaxies grow hierarchically through the aggregation of satellite mass.
-We choose to omit this pointing from the analysis of a total rotation dominated fraction (RDF) since using the numbers from the high density environment would bias the RDF low.
-For the other three pointings we combine the number of rotation dominated galaxies and divide by the total number of spatially resolved galaxies (including mergers and those not in the modelling sample) to arrive at the combined RDF of $0.39\pm 0.08$, where the error is the statistical error on the RDF, computed by generating bootstrapped samples, with replacement, and values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original datapoints.
-For each of the bootstrapped samples we re-compute the RDF and take the errors on the actual RDF as the 16th and 84th percentiles of the resulting distribution.
-We have also calculated upper and lower RDF limits based on the individual $V_{C}/\sigma_{int}$ points and errors, evaluating the maximum and minimum number of galaxies which could scatter above $V_{C}/\sigma_{int} = 1$.
-This leads to a larger error bar of $0.39^{+0.34}_{-0.27}$, plotted as a thin grey shaded region in \ref{fig:rdf_and_v_sigma_w_redshift} and the statisical value is represented by the black error bar.
+This suggests in turn that the random motions traced by $\sigma_{int}$ are providing some degree of gravitational support for the total mass of the system (see \cref{subsec:dynamical_masses}), in contrast to the local universe in which late-type galaxies are supported entirely by ordered rotation.
+The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies is also marked in the right panel and we find that it is the more massive galaxies which tend to a be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
+We suggest that as galaxies accumulate their stellar populations and exhaust their gas supplies, this leads to a more stable rotating disk and hence evolution towards higher $V_{C}/\sigma_{int}$ values.
+
+As discussed in \cref{subsec:morpho-kin-class}, the isolated field sample Rotation Dominated Fraction (RDF) is xxx, which is substantially lower than in the local and intermediate redshift universe as a result of the increased velocity dispersions.
 This value is in good agreement with the result of G11, however we note that their result of $RDF \sim 0.33$ could be higher if any of the galaxies which were not passed through their dynamical model were rotation dominated.
-The number would also decrease if s\_sa22a-m38 were classified as a merger as described in \cref{subsubsec:sigma_and_v}.
-We interpret these results in the context of the cosmic evolution of the RDF in \cref{subsubsec:RDF_evolution}.
-
-\subsubsection{Lack of Dynamical Mass}\label{subsubsec:dynamical_masses}
+We interpret these results in the context of the cosmic evolution of the RDF in \cref{subsubsec:RDF_evolution}.\\
+
+We proceed now to investigate the connection between rotation velocity and stellar mass for the rotation and dispersion dominated KDS field galaxies as an attempt to understand physical differences between these populations at different cosmic times (i.e.
+do rotation dominated galaxies change in physical properties between different redshift slices).
+We build on both the ideas that accumulating a stellar population contributes to stabilising rotation within typical SFGs at all epochs and that rotation velocities alone may not be a good tracer of the total dynamical mass within a system.
+
+\subsection{Rotation velocity and stellar mass}\label{subsec:TF}
+
+\begin{figure*}
+    \centering \hspace{-1.3cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{tully_fisher_standard_log.png}
+        \caption{smTFR}
+    \end{subfigure} \hspace{0.4cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{tully_fisher_s0_log.png}
+        \caption{S$_{0.5}$ Relation}
+    \end{subfigure}
+    \caption{In the left panel we plot log($V_{C}$) vs.
+$M_{\star}$, i.e.
+the inverted stellar mass Tully-Fisher relation for the isolated field sample with $V_{C}/\sigma_{int} > 1$ in red and the galaxies with $V_{C}/\sigma_{int} < 1$ with clear symbols.
+    Also plotted with the solid green is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex error on the fit.
+    This $z\sim0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in Reyes 2011.
+    The $V_{C}/\sigma_{int} > 1$ KDS galaxies also show no evolution from this relation within the errorbars, with the $V_{C}/\sigma_{int} < 1$ galaxies scattering below the relation.
+    This highlights the need for careful sample selection when constructing this relation, and explains the low KDS mean $V_{C}$ value as a consequence of averaging over a sample with a high fraction of dispersion dominated galaxies.
+    In the right panel we plot the $S_{0.5}$ vs.
+$M_{\star}$ relation using the same symbol choice, with $S_{0.5}$ accounting for a contribution to the total dynamical mass from non-circular motions as traced by $\sigma_{int}$.
+    We plot also the K07 relation with the black dashed line, and find that the KDS galaxies agree with this, showing much less separation between the rotation and dispersion dominated galaxies and with less scatter than in the left panel.
+    We caution against over-interpretation of this result, since it is unclear what the physical origins of the random motions traced by $\sigma_{int}$ are, and the extent to which they are contributing to support dynamical mass.
+    In both panels the y-axis errors show the uncertainties derived for each galaxy, whereas the black errorbar in the bottom left gives the representative 0.2 dex error in measuring $M_{\star}$ for each galaxy from the SED fits.}
+    \label{fig:tf_relation}
+\end{figure*}
+
+In the $\Lambda$CDM paradigm the smTFR relates the angular momentum of the dark matter halo within which disk galaxies reside to the $M_{\star}$ content of these galaxies.
+Angular momentum in the halo, which is in turn affected by accretion of gas from the IGM, is transferred to the disk \citep{Fall1983}, where the gas then cools radiatively over time, forming the stellar population of the galaxy.
+Observing the smTFR at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies.
+In principle, studying whether the smTFR evolves with redshift gives us information about how galaxies accumulate their stellar mass and rotational velocities, with offsets from the local relation towards lower $M_{\star}$ values at fixed rotational velocity suggesting that the dynamical mass is in place, but the stellar mass is yet to be formed.
+\\
+
+The main question arising from observations in support of and against evolution of the smTFR with redshift is: Do galaxies evolve along a smTFR which is fixed with redshift (i.e.
+increasing in $V_{C}$ as $M_{\star}$ increases) or is there a shift in the zero-point and/or slope with redshift (i.e.
+as $M_{\star}$ accumulates, $V_{C}$ remains fixed).
+Essentially we'd like to know how an individual, unperturbed point, representing a typical rotation-dominated SFG allowed to evolve without mergers, would move around the $V_{C}$ vs.
+$M_{\star}$ plane over 12Gyr of purely secular evolution.
+Connected to this also is the idea of progenitor bias, in that the SFGs we are selecting and comparing between $z\sim0-3.5$ may not form an evolutionary cohort, and certainly there is much evidence for the quenching of SF at a particular mass scale \citep[e.g.][]{Keres2005,Dekel2006,Peng2010}, leading to morphological and dynamical transformation.
+\\
+
+The smTFR has been studied numerous times between $0.5 < z < 2$, giving results consistent with zero evolution of the slope and zero-point \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Harrison2017}.
+Others have reported that as redshift increases, the smTFR shifts towards lower masses at fixed rotational velocity, e.g.
+in \cite{Puech2008,Puech2010} where a -0.34 dex log$(M_{\star})$ offset is observed at $z\sim0.6$, in the \cite{Tiley2016a} KROSS sample at $z\sim0.9$ with a -0.41 dex shift (although in this work a stricter cut than in H17 of $V_{C}/\sigma_{int} > 3$ is applied), in \cite{Cresci2009} a -0.41 dex offset is observed at $z\sim2$ (although the galaxies used to compute this were the highest fidelity rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5)$ and in G11 an offset of -1.29 dex is claimed, although there is large degree of scatter between the individual galaxies, with 50\% of the sample consistent with the $z\sim0$ relation.
+\\
+
+To demonstrate the relationship between $V_{C}$ and $M_{\star}$ in individual KDS galaxies from the isolated field sample, we plot in the left panel of figure \ref{fig:tf_relation} the inverted smTFR.
+In this plane, $V_{C}$, a tracer of the dynamical mass of the system, is plotted as a function of the luminous mass for the KDS modelling sample.
+In H17, the smTFR relation is fit to $\sim400$ SFGs at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$ and with $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, similar to the KDS galaxies.
+The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
+We plot this best fit relation with the solid green line, with the green shaded region giving the typical uncertainty on the fit of 0.2 dex along the velocity axis.
+These parameters are consistent with the values $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, measured in \cite{Reyes2011} for a sample of $z<0.1$ disks traced with H$\alpha$, in a similar mass range and where $V_{C}$ has been extracted at the same radius, and we plot this as the dashed black line in the left panel of figure \ref{fig:tf_relation}.
+The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$, where the galaxies span a similar $M_{\star}$ range and the $V_{C}$ values have been computed following a consistent methodology, suggests that there is no evolution in the smTFR between these limits.
+\\
+
+The rotation dominated KDS galaxies with $V_{C}/\sigma_{int} > 1$ and $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ are broadly consistent within the errorbars with the H17 fit, showing a tendency to lie below the relation.
+The dispersion dominated KDS galaxies sit clearly separated and below the H17 relation but with a consistent slope, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in H17 and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
+We do not attempt to fit through our data, due to the relatively narrow mass range spanned by the points, and conclude that there does not appear to be evolution in the zero-point of the smTFR between $z\sim1-3.5$ for rotation-dominated galaxies as traced by KROSS and KDS.
+\\
+
+This result is a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotational velocity is observed as a result of omitting rotationally dominated galaxies with lower $V_{C}$ values (as is also the case in \cite{Cresci2009} with the high fidelity disk sample).
+Conversely, fitting the smTFR through a full sample including dispersion dominated galaxies would shift the zero-point in the opposite sense.
+The conclusion from this work is that the smTFR appears to show no evolution across the bulk of cosmic time when the measurement of dynamical properties and selection of rotation dominated galaxies are consistent.
+This comes with the caveat that it is not clear whether main sequence SFGs at difference redshift slices can be considered to form an evolutionary sequence. \\
+
+For completeness we also include the $S_{0.5} = \sqrt{0.5V_{C}^{2} + \sigma_{int}^{2}}$ vs.
+$M_{\star}$ relation described throughout \cite[K07][]{Kassin2007} in the right panel of figure \ref{fig:tf_relation} (which is consistent with the absorption-line-based $M_{\star}$ Faber-Jackson relation for nearby elliptical galaxies), where we plot $S_{0.5}$ vs.
+$M_{\star}$.
+This is connected to the idea suggested in figure \ref{fig:dyn_masses}, that the rotational velocities alone may not be a good tracer of the total dynamical mass, with $S_{0.5}$ accounting for the contribution to the dynamical mass from non-circular motions.
+In K07, using $S_{0.5}$ reduced the scatter in the TFR out to $z\sim1.2$, which they attribute to the inclusion of galaxies with peculiar kinematics in the sample with reduced rotational velocities in relation to their stellar mass.
+$S_{0.5}$ has been studied in both C09 and G11, with both reporting an evolution of the K07 trend towards lower $M_{\star}$ at fixed $S_{0.5}$, which is taken as further evidence for the evolution of the smTFR.
+In the right panel of figure \ref{fig:tf_relation} the KDS galaxies agree with the K07 relation within the errorbars, with reduced scatter in comparison to the smTFR in the left panel, suggesting that there is no evolution in $S_{0.5}-M_{\star}$ relation.
+The symbol convention is the same as in the left panel, and the division now between the rotation and dispersion dominated galaxies is no longer clear. 
+Considering the increase in observed $\sigma_{int}$ values over cosmic time (figure \ref{fig:sigma_and_v_sigma_w_redshift}), this suggests that there is an interplay between the $V_{C}$ values and $\sigma_{int}$ traced by ionised gas emission lines as discussed in \cite{Kassin2012}.
+We caution against over-interpretation of this result, since the origin of $\sigma_{int}$ and the extent to which this quantity traces dynamical mass is unclear, however this trend adds to the evidence that $V_{C}$ alone is an insufficient tracer of the total dynamical mass at this redshift.
+\\
+
+The smTFR derives directly from the virial theorem, in which changes to the dynamical mass are driven by changes in both the sizes and velocities of galaxies, prompting authors recently \citep[e.g.][]{Cortese2016,Contini2015a,Burkert2016a,Harrison2017,Swinbank2017} to study the connection between $M_{\star}$ and specific angular momentum, $j_{s} \propto R_{1/2}V_{C}$, with this possibly a more fundamental quantity to describe galaxy evolution.
+We briefly discuss the specific angular momentum of the KDS galaxies in \cref{subsec:ang_mom}, continuing now to study the virial masses of the isolated field sample computed from their derived rotational velocities.
+
+\subsection{Lack of virial Mass}\label{subsec:dynamical_masses}
 
@@
 \caption{We plot the ratio $M_{vir}/M_{\star}$ computed using only rotational velocities (Eq.
-13) for the KDS galaxies with $V_{C}$ measurements vs.
+13) for the isolated field sample vs.
 $M_{\star}$, with the black line indicating equality between the two quantities.
-The red symbols show the galaxies with $V_{C}/\sigma_{int} > 1$ and the clear symbols show the galaxies with $V_{C}/\sigma_{int} < 1$, which these galaxies having on average lower $M_{vir}$.
+The red symbols show the galaxies with $V_{C}/\sigma_{int} > 1$ and the clear symbols show the galaxies with $V_{C}/\sigma_{int} < 1$, forming a sequence with lower M$_{vir}$ values that the rotation domianted galaxies.
 The majority of the points lie in the unphysical $M_{vir} < M_{\star}$ region.
-This highlights the potential for a combination of random motions, traced by $\sigma_{int}$, and ordered rotation to play a role in supporting the total dynamical mass, an expression for which is given by Eq.
-14 in the text.}
+This highlights the potential for a combination of random motions, traced by $\sigma_{int}$, and ordered rotation to play a role in supporting the total dynamical mass, an expression for which is given by equation \protect\ref{eq:dyn_mass_sigma} in the text.}
 \label{fig:dyn_masses}
@@
 At $z \sim 3.5$ the gas reservoirs are on average a much larger fraction of the total galaxy mass than in the local universe \citep[e.g.][]{Tacconi2013,Saintonge2013,Wisnioski2015} as there has not yet been time to convert this gas mass into stellar mass, and so in principle if ordered rotation is tracing the total mass in these systems, $M_{\star}$ should be clearly below $M_{vir}$.
-In figure \ref{fig:dyn_masses}, where we have computed the virial mass from the ordered rotational motions alone, as traced by $V_{C}$, following equation \ref{eq:dyn_mass_v_only}, we find that this is not the case for the modelling sample, with $M_{vir} < M_{\star}$ for the vast majority of galaxies (particularly those with $M_{\star} > 9.5$).
+In figure \ref{fig:dyn_masses}, where we have computed the virial mass from the ordered rotational motions alone, as traced by $V_{C}$, following equation \ref{eq:dyn_mass_v_only}, we find that this is not the case for the isolated field sample, with $M_{vir} < M_{\star}$ for the vast majority of galaxies (particularly those with $M_{\star} > 9.5$).
 
@@
 
-We have modelled the galaxies throughout the analysis as n = 1 exponential disks, and verified with single \Sers fits in GOODS-S that this is close to the case for most of the galaxies, for which $\beta(n) \sim 8$.
+We have modelled the galaxies throughout the analysis as n = 1 exponential disks, verifying this assumption throughout \cref{subsubsec:galfitting}, for which $\beta(n) \sim 8$.
 For galaxies below the $M_{vir} = M_{\star}$ line, we can find the minimum value of $\beta$ required to bring the two quantities to equality.
@@
 
+\subsection{Angular Momentum}\label{subsec:ang_mom}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.8\textwidth]{angular_momentum.png}
+\caption{We plot the specific angular momentum $j_{s} \propto R_{1/2}V_{C}$ against stellar mass, $M_{\star}$, for the isolated field sample galaxies with $V_{C}/\sigma_{int} > 1$ in red and with clear symbols when $V_{C}/\sigma_{int} < 1$.
+Included also are the $j_{s} \propto M_{\star}^{\alpha}$ fits (with $\alpha = 0.6\pm0.2$) reported in H17 for the KROSS full sample in solid green and for the rotation and dispersion dominated subsamples with the dashed green lines.
+The black solid line is the fit presented in \protect\cite{Romanowsky2012} to a sample of $z=0$ disk galaxies ($\alpha = 0.51\pm0.06$), to which the KROSS relation is offset in $j_{s}$ by $\sim0.2-0.3$dex.
+The KDS rotation dominated galaxies are offset from the KROSS relation by a further $\sim0.3-0.4$dex, with the dispersion dominated galaxies scattering to lower $j_{s}$, with both KDS subsets following a roughly similar slope to KROSS and the $z=0$ sample.
+Further, we include the $j_{s} \propto (1+z)^{-1}$ evolution reported in \protect\cite{Swinbank2017} with the red solid line, using the local slope and normalisation, which appears to pass through the KDS rotation dominated galaxies.
+These results are in line with a scenario where the cosmic evolution of $j_{s}$ is driven mainly by the size evolution of galaxies as they accrete cold material to form stars from the IGM, adding to the outer components of the galaxy disks.
+The split between rotation dominated and dispersion dominated galaxies may indicate that these systems are the progenitors of local late-type and early-type galaxies respectively.}
+\label{fig:ang_mom}
+\end{figure*}
+
+In figure \ref{fig:ang_mom} we plot the specific angular momentum, j$_{\star} \equiv J/M_{\star}$ where J is the total angular momentum \citep{Fall1983}, as a function of stellar mass M$_{\star}$.
+This quantity has been described in detail in \cite{Harrison2017} section 4.3 and refer to this for more details about the use of $j_{s}$ as measured from ionised gas kinematics as a tracer of the specific angular momentum content of SFGs.
+
+\begin{equation}\label{eq:ang_mom}
+   j_{n} = k_{n}C_{i}v_{s}R_{1/2}
+\end{equation}
+
+In equation \ref{eq:ang_mom} we list the approximate estimator for specific angular momentum described in \cite{Romanowsky2012} (their equation 6), with k$_{n}$ a numerical coefficient which depends on the \Sers index of the galaxy, n, and is approximated in equation \ref{eq:kn} (see \cite{Romanowsky2012}).
+
+\begin{equation}\label{eq:kn}
+   k_{n} = 1.15 + 0.029n + 0.062n^{2}
+\end{equation}
+
+Due to varying HST coverage and quality, it has not been possible to estimate n for all KDS galaxies.
+However we have verified throughout \cref{subsubsec:galfitting} that the GOODS-S galaxies are well described by the n = 1 exponential profile through a combination of GALFIT and comparison to the \Sers index values reported in \cite{VanderWel2012}.
+Setting n = 1 in equation \ref{eq:kn} leaves $k_{n} = 1.19$ and we continue under this assumption analogous to in \cite{Harrison2017} (although we note that as stated in \cite{Harrison2017} setting n = 2 results in only a $\sim20\%$ difference in the derived $j_{s}$ values).
+In equation \ref{eq:ang_mom} $C_{i}$ is the de-projection factor, assumed to be $1/sin(i)$, and $v_{s}$ is the observed velocity at $2R_{1/2}$.
+The combination $v_{s}C_{i} \equiv V_{C}$ and we can use our measured rotation velocities to leave equation \ref{eq:ang_mom_final} as the final expression for $j_{s}$ used to calculate the values in figure \ref{fig:ang_mom}.
+
+\begin{equation}\label{eq:ang_mom_final}
+   j_{n=1} \equiv j_{s} = 1.19V_{C}R_{1/2}
+\end{equation}
+
+In figure \ref{fig:ang_mom} we plot the fit to all KROSS galaxies with the solid green line, and also the individual fits to the rotation and dispersion dominated KROSS galaxies with the dashed green and light green lines respectively.
+The fits to the full sample and rotation dominated KROSS galaxies (with fitting relation defined by log$j_{s} =  \beta + \alpha[logM_{\star} - 10.0]$) lie $\sim0.2-0.3$ dex beneath the $z\sim0$ relation from \cite{Romanowsky2012}, in contrast to the smTFR, with the dispersion dominated galaxies scattering around much lower $j_{s}$ values.
+This offset is explained to be a consequence mainly of the size evolution of the disks of SFGs over the redshift range $z=0-0.9$.
+The local and KROSS relations have comparable slopes, with $\alpha_{z=0}=0.51\pm0.06$ and $\alpha_{z=0.9}=0.6\pm0.2$, in agreement with other studies of the $j_{s}-M_{\star}$ relation \citep{Cortese2016,Contini2015a,Burkert2016a,Swinbank2017}, and also in agreement with predictions for the slope of the relationship between dark matter specific angular momentum and the halo mass (i.e.
+$j_{halo} \propto M_{halo}^{2/3}$ \citep[e.g.][]{Barnes1987}).
+This is widely regarded as a consequence of the baryonic retention of angular momentum following a period in the formation of the proto-galaxy when the dark matter and baryons were well mixed. \\
+
+The rotation dominated KDS galaxies form a sequence $\sim 0.3-0.4$ dex beneath the KROSS relation, and with similar slope, however the slope is not well constrained due to the scatter and sparsity of the dataset.
+The dispersion dominated KDS galaxies form a sequence with similar slope but offset to lower still $j_{s}$ values.
+We plot also the $\sim j_{s} \propto (1+z)^{-1}$ reported in \cite{Swinbank2017} (using the local slope and normalisation from \cite{Romanowsky2012}), which the rotation dominated KDS galaxies appear to roughly follow.
+\\
+
+These results suggest that there is a continual drop in the specific angular momentum of SFGs with increasing redshift, as governed by the evolution of disk sizes \citep[e.g.][]{Trujillo2007} (see figure \ref{fig:morpho-distributions}) and that the relationship between the angular momentum of the baryons and the halos is constant over time.
+Conversely, the angular momentum of SFGs will increase with decreasing redshift as accretion of cold gas from the IGM which fuels star formation and tidal disruption from satellite galaxies or major mergers conspire to grow disk sizes over time \citep{Trujillo2007,Buitrago2008,VanderWel2014a}.
+Additonally since we observe a bimodal distribution of the rotation and dispersion dominated KDS galaxies in the $j_{s}-M_{\star}$ plane, we are plausibly observing the progenitors of late-type and early-type galaxies at $z\sim3.5$ as revealed by their kinematic signatures, consistent with the idea that early-type galaxies began their lives with less total angular momentum available to them.
+
 \subsection{The redshift evolution of dynamical properties}\label{subsec:redshift_evolution}
-Having observed low rotational velocities and large velocity dispersions in our $z \sim 3.5$ sample, and compared these with the G11 values at similar redshift, we now aim to place the results in cosmological perspective and interpret the data in the context of galaxy evolution.
-Throughout the following sections we compare the median dynamical properties of several IFU studies over a wide redshift baseline \citep{Green2014,Wisnioski2015,Epinat2012,ForsterSchreiber2009,Cresci2009,Gnerucci2011}, and also compare with Fabry-Perot data from the GHASP sample \citep{Epinat2008,Epinat2008a} as an indicator of the behaviour of SFGs in the local universe.
-The galaxy selection criteria in these surveys, with the exception of \cite{Green2014}, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission line.
-In \cite{Green2014}, half of the galaxies at $z\sim 0.1$ are selected to have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, providing a local comparison sample to the high redshift universe.
-The galaxies in these surveys have different $M_{\star}$ distributions and we attempt to make clear in the following figures, with the symbols and shaded regions, where the results are directly comparable.
-
+We proceed to investigate further the low rotational velocities and large velocity dispersions observed in the isolated field sample in \cref{subsec:rdf_v_over_sigma} by placing them in cosmological perspective using the comparison samples (see \cref{subsubsec:comparison_samples} for overview and symbol definitions).
 We have made use of the tabulated data and errors in these studies to derive the datapoint values and errorbars plotted in figure \ref{fig:rdf_and_v_sigma_w_redshift} and \ref{fig:sigma_and_v_sigma_w_redshift} in a consistent way, which is to take the fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples (i.e.
@@
 The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
-In \cref{subsec:3d modelling} we have described the variation in the methodology used to compute $V_{C}$ and $\sigma_{int}$ between different surveys as a way to help disentangle true evolution from offsets between derived dynamical values caused by disparate measurement techniques.
-It appears that choice of dynamical model and dynamical parameter extraction method does still play a large role in understanding the evolution of dynamical parameters, and for this reason we have chosen to closely follow the methods described in \cite{Harrison2017} to allow for a consistent comparison between $z \sim 3.5$ and $z \sim 1$.
+\\
+
 In the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
@@
     We also plot the 16th and 84th percentiles of the distribution of individual $V_{C}/\sigma_{int}$ measurements as shaded regions to give an indication of the range of values measured in each survey, and indicate the mean stellar mass of each survey in the legend.
-    Lack of tabulated values for KMOS$^{3D}$ and SINS restricted us from computing the $V_{C}/\sigma_{int}$ values in a consistent way, and so we plot only the sample means without errorbars and caution against comparison of these with the other surveys.
+    Lack of tabulated values for KMOS$^{3D}$ and SINS restricted us from computing the $V_{C}/\sigma_{int}$ values in a consistent way, and so we plot the sample means without errorbars.
     The DYNAMO point and errors are plotted in white to highlight the difference in selection criteria, with the low redshift galaxies chosen to have similar properties to those at $z\sim2$.
-    There is a clear decline in the mean $V_{C}/\sigma_{int}$ values with redshift, but with wide ranges in the individual measurements.
+    In the left panel we see a clear decline in the mean $V_{C}/\sigma_{int}$ values with redshift, but with wide ranges in the individual measurements.
     There is also a connection to the mean $M_{\star}$ of the surveys, with larger mean $M_{\star}$ surveys reporting higher mean $V_{C}/\sigma_{int}$.
-    In panel (b) we plot the associated RDF, with this deriving from the fraction of galaxies above the $V_{C}/\sigma_{int} = 1$ dashed line plotted in panel (a).
+    We plot the associated RDF, with this deriving from the fraction of galaxies above the $V_{C}/\sigma_{int} = 1$ dashed line plotted in the right panel.
     The narrow shaded regions represent the maximum and miminum RDF, computed as described in the text.
-    Again, it was not possible to directly compute the RDF in a consistent way for the KMOS$^{3D}$, SINS and AMAZE galaxies and we simply plot the quoted values for these surveys.
     It appears that the RDF drops from $\sim 100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\sim 40\%$ at z $\sim 3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher RDFs.
@@
 
-In figure \ref{fig:rdf_and_v_sigma_w_redshift} (a) we plot $V_{C}/\sigma_{int}$ and in (b) we plot the closely connected RDF both as a function of redshift for the KDS modelling sample (omitting the SSA22-a pointing from the RDF calculation as explained in \cref{subsubsec:rotation_and_mergers}).
-The $V_{C}/\sigma_{int}$ values do not change significantly across the individual KDS pointings, and plotting these independently would not change the results.
-We measure the mean $V_{C}/\sigma_{int} = 1.13^{+0.18}_{-0.15}$ and median $V_{C}/\sigma_{int} = 0.99^{+0.14}_{-0.11}$ and RDF = $0.39 \pm 0.08$ for the KDS galaxies.
-For the samples in which tabulated $V_{C}$ and $\sigma_{int}$ values are available we compute the fractional error weighted mean and median of $V_{C}/\sigma_{int}$, along with associated errors, as described in \cref{subsec:redshift_evolution}.
-The samples for which the mean $V_{C}/\sigma_{int}$ and RDF values can be computed in a consistent way to the KDS galaxies are GHASP \citep[E08]{Epinat2008} $log(M_{\star}[M_{\odot}])=10.6$, DYNAMO \citep[G14]{Green2014} $log(M_{\star}[M_{\odot}])=10.3$ (although with the caveat that the selection criteria was designed to pick out SFGs representative of the $z\sim2$ universe), KROSS \citep[H17]{Harrison2017} $log(M_{\star}[M_{\odot}])=9.9$ and MASSIV \citep[E12]{Epinat2012} $log(M_{\star}[M_{\odot}])=10.2$.
-For these surveys, in figure \ref{fig:rdf_and_v_sigma_w_redshift} (a) the filled symbols and black errorbars represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
+In the left panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and in the right panel we plot the closely connected RDF both as a function of redshift for the KDS isolated field sample and the comparison samples described in \cref{subsubsec:comparison_samples}.
+In the left panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} the filled symbols and black errorbars represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
 The shaded regions give the 16th and 84th percentiles of the distribution on individual $V_{C}/\sigma_{int}$ measurements, plotted here to indicate the range of measurements at each redshift slice.
-In figure \ref{fig:rdf_and_v_sigma_w_redshift} (b) the filled symbols with errorbars denote the surveys for which the RDF is computed as the fraction of galaxies with $V_{C}/\sigma_{int} > 1$.
-We have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the RDF.
+No tabulated data was available for the points plotted without errors and the clear symbols indicate comparison caveats (see \cref{subsubsec:comparison_samples}).
+In the right panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the RDF.
 These are shown with the thin grey shaded regions, and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the invidual points.
-The filled symbols without errorbars represent results quoted in other works.
-In both panels (a) and (b) the KDS mean is plotted as the large red circle at $z\sim3.5$.
-
-There is a further caveat when comparing with the G11 ($log(M_{\star}[M_{\odot}])=9.9$) values; since dynamical properties are only computed for 11/33 rotationally dominated galaxies in their sample, the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
-The shaded percentile regions and errors for the AMAZE data in figure \ref{fig:rdf_and_v_sigma_w_redshift} (a) are shown for reference, and we note that for their three galaxies with $\sigma_{int} = 0kms^{-1}$ we assume $\sigma_{int} = 30kms^{-1}$ (roughly equal to the SINFONI spectral resolution) in order to compute the $V_{C}/\sigma_{int}$ ratio and mean and median $\sigma_{int}$ values.
-For those galaxies in G11 that have no errorbars on $V_{C}$ due to the parameter being unconstrained, we assume a fractional error of 1.
-The G11 RDF, taken as 33\% is also difficult to compare against and is a minimum in the sense that some of the galaxies for which dynamical properties have not been computed could be rotation dominated.
-We plot the G11 RDF with the clear symbol and without errorbars in \ref{fig:rdf_and_v_sigma_w_redshift} (b).
-
-Throughout the KMOS$^{3D}$ study of \cite[W15]{Wisnioski2015} two redshift ranges are considered, the first at $z\sim 1$ with $log(M_{\star}[M_{\odot}])=10.65$ and the second at $z\sim 2.2$ with $log(M_{\star}[M_{\odot}])=10.86$.
-No tabulated values are provided, so we plot here the $V_{C}/\sigma_{int}$ and RDF presented in W15 without errorbars.
-For the SINS sample \citep[FS09]{ForsterSchreiber2009} and \citep[C09]{Cresci2009} ($log(M_{\star}[M_{\odot}])=10.6$), we plot without errorbars the mean $V_{C}/\sigma_{int}$ value in figure \ref{fig:rdf_and_v_sigma_w_redshift} (a) for the full sample presented in W15, since this cannot be directly computed from the tabulated integrated velocity dispersions in FS09.
-We plot also in figure \ref{fig:rdf_and_v_sigma_w_redshift} (b) RDF for the full sample, computed in FS09 section 9.5.1, which classifies rotation dominated galaxies as those where $V_{obs}/(2\sigma_{tot}) > 0.4$, with $\sigma_{tot}$ equal to the velocity dispersion measured from the galaxy integrated spectrum.
 In a recent work by \cite[R16]{Rodrigues2016}, a subset of the KMOS$^{3D}$ $z \sim 1$ sample has been re-analysed and a lower RDF of 69\% was recovered, despite the use of identical classification criteria.
 The recovery of this lower fraction is driven mainly by the presence of peaks in the $\sigma_{int}$ maps which do not coincide with the rotation centre, a criteria which we do not impose throughout this work, and spatial offsets between the rotation centre and the centre of stellar mass.
-We also do not impose the coincidence of $PA_{kin}$ and $PA_{morph}$ as described in \cref{subsubsec:kin_misalignment} as a rotation dominated criteria due to the increased uncertainties in measuring both of these quantities, although we note here that our KDS RDF would drop from 38\% to 16\% due to the loss of 7 galaxies from the rotation dominated sample if we require $\Delta PA < 30^{\circ}$.
-The KROSS $z\sim1$ RDF presented in H17 lies between the two extremes of R16 and W15 computed for the KMOS$^{3D}$ sample.
-
-Despite the systematic variations in measurement technique and classification criteria, it is clear that the RDF, as traced simply by the $V_{C}/\sigma_{int}$ inferred from ionised gas emission lines, drops from $\sim 100\%$ of galaxies in the local universe to $\sim 2/3$ of galaxies in the $z \sim 1-2$ universe and to $\sim 1/3$ above $z \sim 3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
+The KROSS $z\sim1$ RDF presented in H17 lies between the two extremes of R16 and W15 computed for the KMOS$^{3D}$ sample. \\
+
+Despite the systematic variations in measurement technique and classification criteria between the comparison samples, it is clear that the RDF, as traced simply by the $V_{C}/\sigma_{int}$ inferred from ionised gas emission lines, drops from $\sim 100\%$ of galaxies in the local universe to $\sim 2/3$ of galaxies in the $z \sim 1-2$ universe and to $\sim 1/3$ above $z \sim 3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
 This is highlighted in figure \ref{fig:rdf_and_v_sigma_w_redshift} (b) by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic RDF decline as described in \cite{Stott2016}.
@@
     \end{subfigure}
-    \caption{Panel (a) presents a compilation of literature $\sigma_{int}$ values plotted against redshift for surveys spanning $0 < z < 4$.
-    The filled symbols show the sample mean values, with the KDS mean at $z\sim3.5$ plotted with the red circle, with black errorbars representing the statistical error on the mean computed using bootstrap re-sampling as described in the text.
-    The sample medians and statistical errors on these values are plotted with the coloured and grey horizontal bars, falling in each case below the mean, suggesting that large individual $\sigma_{int}$ measurements may bias the sample mean high.
-    We also plot the 16th and 84th percentiles of the distribution of individual $\sigma_{int}$ measurements as shaded regions to give an indication of the range of values measured in each survey, and indicate the mean stellar mass of each survey in the legend.
-    Lack of tabulated values for KMOS$^{3D}$ restricted us from computing the $\sigma_{int}$ values in a consistent way, and so we plot only the sample means without errorbars and caution against comparison of these with the other surveys.
-    The DYNAMO point and errors are plotted in white to highlight the difference in selection criteria, with the low redshift galaxies chosen to have similar properties to those at $z\sim2$.
-    The $\sigma_{int}(z)$ scaling relation from W15, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values, with the solid line showing $log(M_{\star}[M_{\odot}])=10.0$, the dashed line $log(M_{\star}[M_{\odot}])=10.3$ and the dot-dashed line $log(M_{\star}[M_{\odot}])=10.6$.
+    \caption{The left presents a compilation of literature $\sigma_{int}$ values plotted against redshift for surveys spanning $0 < z < 4$.
+    The symbol convention for both the left and right panels is the same as described for the left panel of figure \protect\ref{fig:rdf_and_v_sigma_w_redshift}.
+    We note also that the Law 2009 datapoint has not been corrected for beam-smearing and so represents an upper limit on $\sigma_{int}$ for that survey. 
+    The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values, with the solid line showing $log(M_{\star}[M_{\odot}])=10.0$, the dashed line $log(M_{\star}[M_{\odot}])=10.3$ and the dot-dashed line $log(M_{\star}[M_{\odot}])=10.6$.
     In each case the scaling relation is plotted for $V_{C} = 150kms^{-1}$.
@@
     The vertical location of the mean datapoints in this plane are mediated by the mean $M_{\star}$ of each survey, which is itself connected to the mean gas fraction. 
-    We note also that the Law 2009 datapoint has not been corrected for beam-smearing and so represents an upper limit on $\sigma_{int}$ for that survey. 
-    Panel (b) presents the mean, median and distributions of $V_{C}$ measurements of these surveys between $0 < z < 4$, with the large red circle representing the KDS measurement.
-    We again present the KMOS$^{3D}$ mean points without errors and distributions.} 
+    The right panel presents the mean, median and distributions of $V_{C}$ measurements of these surveys between $0 < z < 4$.
+    The low mean value of $V_{C}$ in the KDS isolated field sample is driven mainly by averaging over a sample which contains a higher fraction of dispersion dominated galaxies with lower rotation velocities.}
     \label{fig:sigma_and_v_sigma_w_redshift}
@@
 To complement the surveys already described throughout \cref{subsubsec:RDF_evolution}, we add data from \cite{Law2009} to explore the evolution of $\sigma_{int}$ values across cosmic time.
-We note that the $\sigma_{mean}$ values and errors tabulated in this paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
+We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
 These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the beam-smearing is much smaller.
@@
 This relation gives a prediction for $\sigma_{int}$ in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR, and using observed constraints for these properties leads to $\sigma_{int}$ predictions with redshift that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
-In both viewpoints the increased $\sigma_{int}$ values observed at high redshift are primarily the result of the prevalence and efficiency of gas inflow onto galaxies in this regime.
-In figure \ref{fig:sigma_and_v_sigma_w_redshift} (a) we plot the fractional error weighted mean, median and distribution of $\sigma_{int}$ from tabulated data, as described in detail in the figure caption.
-For the KMOS$^{3D}$ points at $z\sim 1$ and $z\sim 2.2$, there are no tabulated values and so we again plot the mean $\sigma_{int}$ values listed in W15 without errorbars.
-The mean KDS datapoint is shown with the large red symbol with $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ (median $\sigma_{int} = 67.0^{+5.0}_{-4.8} kms^{-1}$) at z = 3.5, which is in agreement with the $\sigma_{int}$ scaling relation presented in W15, plotted with the grey lines for $V_{C} = 150kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$, rather than the $log(M_{\star}[M_{\odot}])=10.5$ value used in \cite{Wisnioski2015} (note we have also not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
-The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ and $V_{C}$ in the equation shown in the top right of figure \ref{fig:sigma_and_v_sigma_w_redshift} (a).
+In both viewpoints the increased $\sigma_{int}$ values observed at high redshift are primarily the result of the prevalence and efficiency of gas inflow onto galaxies in this regime. \\
+
+In the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distribution of $\sigma_{int}$ from the comparison and KDS isolated field samples.
+The mean KDS datapoint is in agreement with the $\sigma_{int}$ scaling relation presented in W15, plotted with the grey lines for $V_{C} = 150kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$, rather than the $log(M_{\star}[M_{\odot}])=10.5$ value used in W15 (note we have also not shifted the datapoints to conform with a single $M_{\star}$ value as per W15).
+The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ and $V_{C}$ in the equation shown in the top right of the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}.
 
@@
 The location of mean $\sigma_{int}$ values is therefore related to the mean $M_{\star}$ of each survey, with this being an indicator of the accumulation of a stellar population and hence the evolutionary state of the galaxies.
-The tracks plotted in figure \ref{fig:sigma_and_v_sigma_w_redshift} give a rough indication of how $\sigma_{int}$ evolves in galaxies of a particular stellar mass in the context of the equilibrium model, and the KDS galaxies provide a strong observational constraint on the internal dynamics of main sequence galaxies between $z=3-3.7$.
+The tracks plotted in figure \ref{fig:sigma_and_v_sigma_w_redshift} give a rough indication of how $\sigma_{int}$ evolves in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
 
 \subsubsection{The evolution of maximum circular velocity}\label{subsubsec:v_evolution}
-In figure \ref{fig:sigma_and_v_sigma_w_redshift} (b) we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the different surveys against redshift, as explained in the caption of figure \ref{fig:sigma_and_v_sigma_w_redshift} to highlight two observations:
+In the right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison and KDS isolated field sample to highlight two observations:
 \begin{itemize}
+    \item Different modelling and measurement techniques affect the inferred $V_{C}$ values
     \item The KDS $V_{C}$ values appear lower than reported in lower redshift studies with similar mean $M_{\star}$ values, as a result of averaging over a sample with a higher dispersion dominated fraction
-    \item Different modelling and measurement techniques affect the inferred $V_{C}$ values
 \end{itemize}
@@
 the combination of $M_{gas}$, $M_{\star}$ and $M_{DM}$, against gravitational collapse.
-$V_{C}$ increases as $M_{tot}$ increases and so we would expect the systems with larger average $M_{\star}$, assuming that these are indicative of systems with greater $M_{tot}$, to have larger $V_{C}$, which appears generally to be the case in figure \ref{fig:sigma_and_v_sigma_w_redshift} (b) where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
+$V_{C}$ increases as $M_{tot}$ increases and so we would expect the systems with larger average $M_{\star}$, assuming that these are indicative of systems with greater $M_{tot}$, to have larger $V_{C}$, which appears generally to be the case in the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
 Using the average $M_{\star}$ values and velocity extraction radius in the KDS sample, $log(M_{\star}[M_{\odot}])=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of $M_{gas}$ and $M_{DM}$ would raise this estimate).
-Indeed this estimate is similar to the mean value found in the KROSS sample for $log(M_{\star}[M_{\odot}])=10.0$ galaxies at $z\sim1$.
-In figure \ref{fig:sigma_and_v_sigma_w_redshift} (b) we plot the mean and median values and percentiles of the $V_{C}$ distribution for the different surveys, finding wide distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
-The KDS datapoint, represented by the large red circle, has mean $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ and median $V_{C} = 60.0^{+7.5}_{-5.9}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
+Indeed this estimate is similar to the mean value found in the KROSS sample for $log(M_{\star}[M_{\odot}])=10.0$ galaxies at $z\sim1$. \\
+
+In the right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
+It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in \cref{subsubsec:comparison_samples}) are directly comparable.
+The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
+In particular the $V_{C}$ parameter reported in G11 is unconstrained for several galaxies, requires large extrapolation from the data and leads to very large rotational velocities for 5/11 of their galaxies.
+The remaining 6/11 galaxies have $V_{C}$ values close to those reported for the KDS sample.
+This is a consequence of the current state of the data quality at high redshifts, and it is important to keep in mind that both $\sigma_{int}$ and $V_{C}$ are still dependent on modelling technique.
+\\
+
+The KDS mean and median values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
 This could either be a result of the measurement and modelling technique, which carries significant uncertainties due to modelling assumptions, the S/N of the [O~{\sc III}]$\lambda5007$ emission line even in very long integrations at this redshift, the spatial coverage of [O~{\sc III}]$\lambda5007$ may be more compact that $H\alpha$ and consequently may not probe out to the same galactic radii and the sparsity of resolution elements, or could be the result or some real physical process in the galaxies which lowers $V_{C}$ as traced by the ionised gas dynamics.
-Also, since there is a higher fraction of dispersion dominated galaxies at $z\sim3.5$, the mean $V_{C}$ value of the complete sample is likely to be biased low.
-This is easier to see in \cref{subsec:TF} where we revisit the rotational velocities in the context of the inverted stellar mass `Tully-Fisher Relation' \citep[smTFR;][]{Tully1977,Bell2000a}.
+We believe however that the observation of a low mean $V_{C}$ value in the KDS galaxies is primarily exlainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
+This is easier to see in \cref{subsec:TF} where we revisit the rotation velocities in the context of the inverted stellar mass `Tully-Fisher Relation' \citep[smTFR;][]{Tully1977,Bell2000a}. \\
 
@@
 At this redshift and mean $M_{\star}$, the disk assumption may not be correct, as galaxies could have more complicated structures which have not yet stabilised into rotating disks.
-However the distribution of inclination angles is consistent with observing a selection of galaxies with inclinations randomly distributed as $0^{\circ} < i < 90^{\circ}$, with the KDS mean inclination of $59.5^{\circ}$ agreeing well with the theoretical mean of $57.3^{\circ}$ (for a simple derivation of this value see e.g.
+However the distribution of inclination angles is consistent with observing a selection of galaxies with inclinations randomly distributed as $0^{\circ} < i < 90^{\circ}$, with the KDS mean inclination of $57.4^{\circ}$ (see \cref{subsubsection:inclination_angle}) agreeing well with the theoretical mean of $57.3^{\circ}$ (for a simple derivation of this value see e.g.
 the appendix in \cite{Law2009}).
+\\
+
 There are some galaxies where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
@@
 \cite{Law2009} observe galaxies with similarly low mean velocity shear and high velocity dispersions (the velocities are not plotted here since the tabulated values are not inclination or beam-smearing corrected) and attribute this to instabilities which occur when the cold gas becomes dynamically dominant following efficient accretion and in line with the high gas fractions observed at high redshift.
+
 We caution that at high redshift these $V_{C}$ measurements are challenging for the reasons stated above, however our data appear to support a scenario in which low $M_{\star}$ galaxies experience elevated random motions related to the rapid accretion of cold gas, which is partially supported gravitationally by these random motions and may contribute to the observation of low $V_{C}$ values.
 At higher $M_{\star}$ the accumulation of a stellar population provides stability, $\sigma_{int}$ decreases and $V_{C}$ increases to provide the additional gravitational support.
-These processes are mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion.
-
-The second point is that it is difficult to assess whether the $V_{C}$ values reported by different surveys (the modelling and extraction techniques differ and are described in \cref{subsubsec:param_extraction}) are directly comparable.
-The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
-In particular the $V_{C}$ parameter reported in G11 is unconstrained for several galaxies, requires large extrapolation from the data and leads to very large rotational velocities for 5/11 of their galaxies.
-The remaining 6/11 galaxies have $V_{C}$ values close to those reported for the KDS sample.
-This is a consequence of the current state of the data quality at high redshifts, and it is important to keep in mind that both $\sigma_{int}$ and $V_{C}$ are still dependent on modelling technique.
-
-\subsection{The z = 3.5 Tully-Fisher Relation}\label{subsec:TF}
-
-\begin{figure*}
-    \centering \hspace{-1.3cm}
-    \begin{subfigure}[h!]{0.5\textwidth}
-        \centering
-        \includegraphics[height=3.5in]{tully_fisher_standard_log.png}
-        \caption{smTFR}
-    \end{subfigure} \hspace{0.4cm}
-    \begin{subfigure}[h!]{0.5\textwidth}
-        \centering
-        \includegraphics[height=3.5in]{tully_fisher_s0_log.png}
-        \caption{S$_{0.5}$ Relation}
-    \end{subfigure}
-    \caption{In panel (a) we plot log($V_{C}$) vs.
-$M_{\star}$, i.e.
-the inverted stellar mass Tully-Fisher relation for the KDS galaxies with $V_{C}/\sigma_{int} > 1$ in red and the galaxies with $V_{C}/\sigma_{int} < 1$ with clear symbols.
-    Also plotted with the solid green is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex error on the fit.
-    This $z\sim0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in Reyes 2011.
-    The $V_{C}/\sigma_{int} > 1$ KDS galaxies also show no evolution from this relation within the errorbars, with the $V_{C}/\sigma_{int} < 1$ galaxies scattering below the relation.
-    This highlights the need for careful sample selection when constructing this relation, and explains the low KDS mean $V_{C}$ value as a consequence of averaging over a sample with a high fraction of dispersion dominated galaxies.
-    In panel (b) we plot the $S_{0.5}$ vs. $M_{\star}$ relation, which accounts for a contribution to the total dynamical mass from non-circular motions as traced by $\sigma_{int}$.
-    The symbol convention is the same as panel (a) and we include also the KDS galaxies with only $\sigma_{int}$ measurements as the black symbols.
-    We plot also the K07 relation with the black dashed line, and find that the KDS galaxies agree with this, showing much less separation between the rotation and dispersion dominated galaxies and with less scatter than in panel (a).
-    We caution against over-interpretation of this result, since it is unclear what the physical origins of the random motions traced by $\sigma_{int}$ are, and the extent to which they are contributing to support dynamical mass.}
-    \label{fig:tf_relation}
-\end{figure*}
-
-In the $\Lambda$CDM paradigm the smTFR relates the angular momentum of the dark matter halo within which disk galaxies reside to the $M_{\star}$ content of these galaxies.
-Angular momentum in the halo, which is in turn affected by accretion of gas from the IGM, is transferred to the disk \citep{Fall1983}, where the gas then cools radiatively over time, forming the stellar population of the galaxy.
-Observing the smTFR at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies.
-In principle, studying whether the smTFR evolves with redshift gives us information about how galaxies accumulate their stellar mass and rotational velocities, with offsets from the local relation towards lower $M_{\star}$ values at fixed rotational velocity suggesting that the dynamical mass is in place, but the stellar mass is yet to be formed.
-The main question arising from observations in support of and against evolution of the smTFR with redshift is: Do galaxies evolve along a smTFR which is fixed with redshift (i.e.
-increasing in $V_{C}$ as $M_{\star}$ increases) or is there a shift in the zero-point and/or slope with redshift (i.e.
-as $M_{\star}$ accumulates, $V_{C}$ remains fixed).
-Essentially we'd like to know how an individual, unperturbed point, representing a typical rotation-dominated SFG allowed to evolve without mergers, would move around the $V_{C}$ vs.
-$M_{\star}$ plane over 12Gyr of purely secular evolution.
-Connected to this also is the idea of progenitor bias, in that the SFGs we are selecting and comparing between $z\sim0-3.5$ may not form an evolutionary cohort, and certainly there is much evidence for the quenching of SF at a particular mass scale \citep[e.g.][]{Keres2005,Dekel2006,Peng2010}, leading to morphological and dynamical transformation.
-
-The smTFR has been studied numerous times between $0.5 < z < 2$, giving results consistent with zero evolution of the slope and zero-point \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Harrison2017}.
-Others have reported that as redshift increases, the smTFR shifts towards lower masses at fixed rotational velocity, e.g.
-in \cite{Puech2008,Puech2010} where a -0.34 dex log$(M_{\star})$ offset is observed at $z\sim0.6$, in the \cite{Tiley2016a} KROSS sample at $z\sim0.9$ with a -0.41 dex shift (although in this work a stricter cut than in H17 of $V_{C}/\sigma_{int} > 3$ is applied), in \cite{Cresci2009} a -0.41 dex offset is observed at $z\sim2$ (although the galaxies used to compute this were the highest fidelity rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5)$ and in G11 an offset of -1.29 dex is claimed, although there is large degree of scatter between the individual galaxies, with 50\% of the sample consistent with the $z\sim0$ relation.
-
-To demonstrate the relationship between $V_{C}$ and $M_{\star}$ in individual KDS galaxies from the modelling sample, we plot in figure \ref{fig:tf_relation} (a) the inverted smTFR.
-In this plane, $V_{C}$, a tracer of the dynamical mass of the system, is plotted as a function of the luminous mass for the KDS modelling sample.
-The rotationally dominated galaxies with $V_{C}/\sigma_{int} > 1$ are shown with red circles, whereas the dispersion dominated $V_{C}/\sigma_{int} < 1$  galaxies are shown with the open circles.
-The black errorbars on the individual points reflect the upper and lower errors on the individual $V_{C}$ values, whereas the black errorbar in the bottom left gives the representative 0.2 dex error in measuring $M_{\star}$ for each galaxy from the SED fits.
-In H17, the smTFR relation is fit to $\sim400$ SFGs at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$ and with $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, similar to the KDS galaxies.
-The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
-We plot this best fit relation with the green line in figure \ref{fig:tf_relation} (a), with the green shaded region giving the typical uncertainty on the fit of 0.2 dex along the velocity axis.
-These parameters are consistent with the values $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, measured in \cite{Reyes2011} for a sample of $z<0.1$ disks traced with H$\alpha$, in a similar mass range and where $V_{C}$ has been extracted at the same radius, and we plot this as the dashed black line in figure \ref{fig:tf_relation} (a).
-The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$, where the galaxies span a similar $M_{\star}$ range and the $V_{C}$ values have been computed following a consistent methodology, suggests that there is no evolution in the smTFR between these limits.
-The rotation dominated KDS galaxies with $V_{C}/\sigma_{int} > 1$ and $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ are broadly consistent within the errorbars with the H17 fit, showing a tendency to lie below the relation.
-The dispersion dominated KDS galaxies sit below the H17 relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in H17 and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We do not attempt to fit through our data, due to the relatively narrow mass range spanned by the points, and conclude that there does not appear to be evolution in the zero-point of the smTFR between $z\sim1-3.5$ for rotation-dominated galaxies as traced by KROSS and KDS.
-This result is a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotational velocity is observed as a result of omitting rotationally dominated galaxies with lower $V_{C}$ values (as is also the case in \cite{Cresci2009} with the high fidelity disk sample).
-Conversely, fitting the smTFR through a full sample including dispersion dominated galaxies would shift the zero-point in the opposite sense.
-The conclusion from this work is that the smTFR appears to show no evolution across the bulk of cosmic time when the measurement of dynamical properties and selection of rotation dominated galaxies are consistent.
-This comes with the caveat that it is not clear whether main sequence SFGs at difference redshift slices can be considered to form an evolutionary sequence.
-
-For completeness we also include the $S_{0.5} = \sqrt{0.5V_{C}^{2} + \sigma_{int}^{2}}$ vs.
-$M_{\star}$ relation described throughout \cite[K07][]{Kassin2007} in figure \ref{fig:tf_relation} (b) (which is consistent with the absorption-line-based $M_{\star}$ Faber-Jackson relation for nearby elliptical galaxies), where we plot $S_{0.5}$ vs.
-$M_{\star}$.
-This is connected to the idea suggested in figure \ref{fig:dyn_masses}, that the rotational velocities alone may not be a good tracer of the total dynamical mass, with $S_{0.5}$ accounting for the contribution to the dynamical mass from non-circular motions.
-In K07, using $S_{0.5}$ reduced the scatter in the TFR out to $z\sim1.2$, which they attribute to the inclusion of galaxies with peculiar kinematics in the sample with reduced rotational velocities in relation to their stellar mass.
-$S_{0.5}$ has been studied in both C09 and G11, with both reporting an evolution of the K07 trend towards lower $M_{\star}$ at fixed $S_{0.5}$, which is taken as further evidence for the evolution of the smTFR.
-In figure \ref{fig:tf_relation} (b) the KDS galaxies agree with the K07 relation within the errorbars, with reduced scatter in comparison to the smTFR in panel (a), suggesting that their is no evolution in $S_{0.5}-M_{\star}$ relation.
-The symbol convention is the same as in panel (a), and the division now between the rotation and dispersion dominated galaxies is no longer clear. 
-Considering the increase in observed $\sigma_{int}$ values over cosmic time (figure \ref{fig:sigma_and_v_sigma_w_redshift}), this suggests that there is an interplay between the $V_{C}$ values and $\sigma_{int}$ traced by ionised gas emission lines as discussed in \cite{Kassin2012}.
-We caution against over-interpretation of this result, since the origin of $\sigma_{int}$ and the extent to which this quantity traces dynamical mass is unclear, however this trend adds to the evidence that $V_{C}$ alone is an insufficient tracer of the total dynamical mass at this redshift.
-
-The smTFR derives directly from the virial theorem, in which changes to the dynamical mass are driven by changes in both the sizes and velocities of galaxies, prompting authors recently \citep[e.g.][]{Cortese2016,Contini2015a,Burkert2016a,Harrison2017,Swinbank2017} to study the connection between $M_{\star}$ and specific angular momentum, $j_{s} \propto R_{1/2}V_{C}$, with this possibly a more fundamental quantity to describe galaxy evolution.
-We briefly discuss the specific angular momentum of the KDS galaxies in the following subsection.
-
-\subsection{Angular Momentum}\label{subsec:ang_mom}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.8\textwidth]{angular_momentum.png}
-\caption{We plot the specific angular momentum $j_{s} \propto R_{1/2}V_{C}$ against stellar mass, $M_{\star}$, for the KDS galaxies with $V_{C}/\sigma_{int} > 1$ in red and with clear symbols when $V_{C}/\sigma_{int} < 1$.
-Included also are the $j_{s} \propto M_{\star}^{\alpha}$ fits (with $\alpha = 0.6\pm0.2$) reported in H17 for the KROSS full sample in solid green and for the rotation and dispersion dominated subsamples with the dashed green lines.
-The black solid line is the fit presented in \protect\cite{Romanowsky2012} to a sample of $z=0$ disk galaxies ($\alpha = 0.51\pm0.06$), to which the KROSS relation is offset in $j_{s}$ by $\sim0.2-0.3$dex.
-The KDS rotation dominated galaxies are offset from the KROSS relation by a further $\sim0.3-0.4$dex, with the dispersion dominated galaxies scattering to lower $j_{s}$, with both KDS subsets following a roughly similar slope to KROSS and the $z=0$ sample.
-Further, we include the $j_{s} \propto (1+z)^{-1}$ evolution reported in \protect\cite{Swinbank2017} with the red solid line, using the local slope and normalisation, which appears to pass through the KDS rotation dominated galaxies.
-These results are in line with a scenario where the cosmic evolution of $j_{s}$ is driven mainly by the size evolution of galaxies as they accrete cold material to form stars from the IGM, adding to the outer components of the galaxy disks.
-The split between rotation dominated and dispersion dominated galaxies may indicate that these systems are the progenitors of local late-type and early-type galaxies respectively.}
-\label{fig:ang_mom}
-\end{figure*}
-
-In figure \ref{fig:ang_mom} we plot the specific angular momentum, j$_{\star} \equiv J/M_{\star}$ where J is the total angular momentum \citep{Fall1983}, as a function of stellar mass M$_{\star}$.
-This quantity has been described in detail in \cite{Harrison2017} section 4.3 and refer to this for more details about the use of $j_{s}$ as measured from ionised gas kinematics as a tracer of the specific angular momentum content of SFGs.
-
-\begin{equation}\label{eq:ang_mom}
-   j_{n} = k_{n}C_{i}v_{s}R_{1/2}
-\end{equation}
-
-In equation \ref{eq:ang_mom} we list the approximate estimator for specific angular momentum described in \cite{Romanowsky2012} (their equation 6), with k$_{n}$ a numerical coefficient which depends on the \Sers index of the galaxy, n, and is approximated in equation \ref{eq:kn} (see \cite{Romanowsky2012}).
-
-\begin{equation}\label{eq:kn}
-   k_{n} = 1.15 + 0.029n + 0.062n^{2}
-\end{equation}
-
-Due to varying HST coverage and quality, it has not been possible to estimate n for all KDS galaxies.
-However we have verified with both floating \Sers index fits, fixed n = 1 \Sers fits and fixed n = 4 \Sers fits throughout \cref{subsubsec:galfitting} that the vast majority of GOODS-S galaxies ($\sim70\%$ of the KDS modelling sample) are well described by the n = 1 exponential profile (also assumed throughout the modelling procedure in \cref{sec:Kinematic_Properties}).
-Setting n = 1 in equation \ref{eq:kn} leaves $k_{n} = 1.19$ and we continue under this assumption analogous to in \cite{Harrison2017} (although we note that as stated in \cite{Harrison2017} setting n = 1 results in only a $\sim20\%$ difference in the derived $j_{s}$ values).
-In equation \ref{eq:ang_mom} $C_{i}$ is the de-projection factor, assumed to be $1/sin(i)$, and $v_{s}$ is the observed velocity at $2R_{1/2}$.
-The combination $v_{s}C_{i} \equiv V_{C}$ and we can use our measured rotation velocities to leave \ref{eq:ang_mom_final} as the final expression for $j_{s}$ used to calculate the values in figure \ref{fig:ang_mom}.
-
-\begin{equation}\label{eq:ang_mom_final}
-   j_{n=1} \equiv j_{s} = 1.19V_{C}R_{1/2}
-\end{equation}
-
-In figure \ref{fig:ang_mom} we plot the fit to all KROSS galaxies with the solid green line, and also the individual fits to the rotation and dispersion dominated KROSS galaxies with the dashed green and light green lines respectively.
-The fits to the full sample and rotation dominated KROSS galaxies (with fitting relation defined by log$j_{s} =  \beta + \alpha[logM_{\star} - 10.0]$) lie $\sim0.2-0.3$ dex beneath the $z\sim0$ relation from \cite{Romanowsky2012}, in contrast to the smTFR, with the dispersion dominated galaxies scattering around much lower $j_{s}$ values.
-This offset is explained to be a consequence mainly of the size evolution of the disks of SFGs over the redshift range $0-0.9$.
-The local and KROSS relations have comparable slopes, with $\alpha_{z=0}=0.51\pm0.06$ and $\alpha_{z=0.9}=0.6\pm0.2$, in agreement with other studies of the $j_{s}-M_{\star}$ relation \citep{Cortese2016,Contini2015a,Burkert2016a,Swinbank2017}, and also in agreement with predictions for the slope of the relationship between dark matter specific angular momentum and the halo mass (i.e.
-$j_{halo} \propto M_{halo}^{2/3}$ \citep[e.g.][]{Barnes1987}).
-This is widely regarded as a consequence of the baryonic retention of angular momentum following a period in the formation of the proto-galaxy when the dark matter and baryons were well mixed.
-
-The rotation dominated KDS galaxies form a sequence $\sim 0.3-0.4$ dex beneath the KROSS relation, and with similar slope, however the slope is not well constrained due to the scatter and sparsity of the dataset.
-The dispersion dominated KDS galaxies form a sequence with similar slope but offset to lower still $j_{s}$ values.
-We plot also the $\sim j_{s} \propto (1+z)^{-1}$ reported in \cite{Swinbank2017} (using the local slope and normalisation from \cite{Romanowsky2012}), which the rotation dominated KDS galaxies appear to roughly follow.
-These results suggest that there is a continual drop in the specific angular momentum of SFGs with increasing redshift, as governed by the evolution of disk sizes \citep[e.g.][]{Trujillo2007} (see figure \ref{fig:morpho-distributions}) and that the relationship between the angular momentum of the baryons and the halos is constant over time.
-Conversely, the angular momentum of SFGs will increase with decreasing redshift as accretion of cold gas from the IGM which fuels star formation and tidal disruption from satellite galaxies or major mergers conspire to grow disk sizes over time \citep{Trujillo2007,Buitrago2008,VanderWel2014a}.
-Additonally since we observe a bimodal distribution of the rotation and dispersion dominated KDS galaxies in the $j_{s}-M_{\star}$ plane, we are plausibly observing the progenitors of late-type and early-type galaxies at $z\sim3.5$ as revealed by their kinematic signatures, consistent with the idea that early-type galaxies began their lives with less total angular momentum available to them.
+These processes are mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Wisnioski2015}.
 
 \section{CONCLUSIONS}\label{sec:conclusion}
-We have presented new measurements of the dynamical properties of $\sim 45$ spatially resolved SFGs at $z\sim3.5$ as part of the KDS, based on IFU data observed with KMOS.
+We have presented new measurements of 77 main sequence SFGs spanning both cluster and field environments at $z\sim3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
 These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}[M_{\odot}])< 10.5$ typical main sequence galaxies at these redshifts.
-By using a combined morpho-kinematic classification based on broad-band HST imaging and our IFU data, we have separated probable interacting galaxies from the sample and made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for those remaining.
+By using a combined morpho-kinematic classification based on broad-band HST imaging and our IFU data, we have separated probable interacting galaxies from the sample, finding consistent merger rates in the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
+We proceeded to make made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (\cref{subsubsec:comparison_samples} and table \ref{tab:evolution_numbers}).
 The main conclusions of this work are summarised as follows:
@@
 \begin{itemize}
-    \item We observe an increase in $\sigma_{int}$ values in comparison with $z\sim0$ galaxies, with a sample mean of $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$.
-    We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline, finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to boost random motions within high redshift galaxies.
-    \item As a result of the increase in $\sigma_{int}$, most of the resolved galaxies are dispersion dominated, with velocity dispersions greater than their measured rotation velocities.
-    We measure a rotation dominated percentage, $V_{C}/\sigma_{int} > 1$, of $39 \pm 8 \%$ in our sample, substantially lower than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (figure \ref{fig:rdf_and_v_sigma_w_redshift}).
-    \item The mean rotational velocity value of $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ appears low in comparison to surveys at lower redshift, although there is again significant diversity in $V_{C}$ measurements in each survey (figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    This appears to be mainly the result of averaging over a sample with a much higher percentage of dispersion dominated galaxies.
+    \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ and $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ (left panel of figure \ref{fig:v_sig_and_v}).
+    \item 13/29 isolated field sample galaxies are dispersion dominated and 16/29 are dispersion dominated as indicated by the ratio $V_{C}/\sigma_{int}$, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (left and right panels of figure \ref{fig:v_sig_and_v}).
+    This gives a rotation dominated fraction of $37 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of figure \ref{fig:rdf_and_v_sigma_w_redshift}).
     \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}[M_{\odot}]) < 11.0$ at $z\sim0.9$ in the KROSS survey (figure \ref{fig:tf_relation}).
@@
     Constistency of sample selection and measurement techniques are crucial factors when determining evolution in the $V_{C}$ vs. $M_{\star}$ plane by comparing samples at different redshifts.
-    The dispersion dominated galaxies scatter below the trend.
+    The dispersion dominated galaxies scatter below the trend, with the same slope as the rotation dominated galaxies.
+    \item To investigate the possible contribution of $\sigma_{int}$ to the total dynamical mass, we plot $S_{0.5} = \sqrt{0.5V^{2} + \sigma_{int}^{2}}$ as a function of $M_{\star}$, finding a tighter relationship than in the case of the inverse smTFR, with the $S_{0.5} vs.
+M_{\star}$ relation showing no evidence for evolution from the $z=0$ relation from \cite{Kassin2007} (figure \ref{fig:tf_relation}).
+    We caution again that there is no clear relationship between $\sigma_{int}$ and $M_{\star}$ and this result should not be over-interpreted.
     \item The virial mass computed from $V_{C}$ values alone is lower than the stellar mass for the majority of KDS galaxies.
@@
     This is clearly over-simplified, as the lack of correlation between $\sigma_{int}$ and $M_{\star}$ suggests that not all of the random motions support mass, and may originate from turbulence.
-    \item To investigate the possible contribution of $\sigma_{int}$ to the total dynamical mass further, we plot $S_{0.5} = \sqrt{0.5V^{2} + \sigma_{int}^{2}}$ as a function of $M_{\star}$, finding a tighter relationship than in the case of the inverse smTFR, which shows no evidence for evolution from the $z=0$ relation from \cite{Kassin2007} (figure \ref{fig:tf_relation}).
-    We caution again though that there is no clear relationship between $\sigma_{int}$ and $M_{\star}$ and this result should not be over-interpreted.  
     \item The specific angular momentum (angular momentum divided by stellar mass $M_{\star}$; $j_{s}$) of the KDS galaxies is $\sim$0.3-0.4 dex lower than KROSS galaxies at $z\sim0.9$ at fixed $M_{\star}$, and the slope of the $j_{s}-M_{\star}$ relation appears comparable between the two samples (figure \ref{fig:ang_mom}).
     This supports a scenario in which the derease in $j_{s} \propto R_{D}V_{C}$ with increasing redshift between $z=0-3.5$ is driven by the gradual size evolution of galaxies over the same redshift interval (figure \ref{fig:morpho-distributions}).
-    \item Almost all of the resolved KDS galaxies in the $z\sim3.1$ high density protocluster pointing SSA22-a are involved in interactions, which has important consequences for the dynamics of and accumulation of stellar populations within these cluster galaxies which sit at the peak of the cosmological density field.
-    The merger fraction computed across the other, lower density pointings is 15\%.
+    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in \cref{subsubsec:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to boost random motions within high redshift galaxies.
+    \item We plot the mean $V_{C}$ values of the comparison samples and the KDS isolated field sample, finding significant diversity in $V_{C}$ measurements in each survey (right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    The spread in measurements is a result of the samples containing a mixture of rotation and dispersion dominated galaxies with varying $M_{\star}$ values, and the low mean KDS value is primarily the result of averaging over a sample with a high fraction of dispersion dominated galaxies.
+    At higher $M_{\star}$ the accumulation of a stellar population provides stability, leading to an interplay between $\sigma_{int}$ and $V_{C}$ mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Wisnioski2015}.
 
@@
 \includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_113_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_lab7_top_grid_paper.png}
 \label{fig:goods_disp_4}
@@
  AMAZE & 3.0 & 10.0 & $3.59^{+1.45}_{-1.1}$ & $2.1^{+4.7}_{-1.15}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+27.0}_{-48.0}$ & $217^{+59.1}_{-40.2}$ & $129^{+166.0}_{-50.2}$ \\
- KDS & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.39^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $78.8^{+5.4}_{-5.1}$ & $60.0^{+49.1}_{-18.2}$ \\
+ KDS & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.37^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $78.8^{+5.4}_{-5.1}$ & $60.0^{+49.1}_{-18.2}$ \\
  \hline

### 2017-02-16 paper.tex
19th November

@@
 
-\usepackage[draft]{hyperref}
+\usepackage{hyperref}
 \hypersetup{
@@
 \begin{abstract}
-We present dynamical measurements of 77 [O~{\sc III}]$\lambda5007$ resolved main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
+We present dynamical measurements for 77 main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
 These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
@@
 $V_{C}-M_{\star}$) relation (the inverse of the stellar mass Tully-Fisher relation), although a smaller fraction of the galaxies sit on the relation due to the increase in the dispersion dominated fraction.
-The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this evolution the result of the gradual size evolution of the star-forming population over cosmic time.
+The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this decline the result of the gradual size evolution of the star-forming population over cosmic time.
 Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
@@
 \cite{Mo2010} for a recent review), with these systems constituting the first galaxies.
-One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue (e.g.
-\cite{Fall1983}).
-
-It has been observationally determined that the galaxy population is bimodal in many physical properties at each redshift slice at which it is studied (e.g.
-as listed in \cite{Dekel2006}), with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies.
+One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue \citep[e.g.][]{Fall1983}.
+
+It has been observationally determined that the galaxy population is bimodal in many physical properties at each redshift slice at which it is studied \citep[e.g.
+as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies.
 For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
-This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, and outflows and accretion events maintain a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
+This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
 The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic star formation rate density in this redshift range \citep{Madau_2014}.
-At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs, and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
-This assumes that high redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b}, and also assumes that something can be learned about galaxy evolution (i.e.
+At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
+This assumes that high redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
 how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
-The picture is complicated by the addition of major and minor mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014}, and the relative importance of in-situ, secular stellar mass growth vs.
+The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs.
 stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}.
@@
 Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations which must be reproduced across cosmic time.
-The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons, and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \cite[e.g.][]{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
-Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Bundy2015,Wisnioski2015,Stott2016} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope (HST) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
-In particular, in recent years the multiplexing capabilities of KMOS have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Harrison2016,Mason2016} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
+The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \cite{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
+Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope (HST) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
+In particular, in recent years the multiplexing capabilities of KMOS have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
 
@@
 This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic Star Formation Rate Density (SFRD) \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
-There is also an increasing body of work measuring the relationship between the observed maximum rotational velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Tiley2016a,Harrison2017}.
+There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Tiley2016a,Harrison2017}.
 In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
@@
 
-This study focusses on the final question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotational velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
+This study focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS we have been able to spatially resolve [O~{\sc III}]$\lambda$5007 emission in 43 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.
+By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.
+\\
 
@@
 In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
-In \cref{sec:extracting_properties} we explain how two-dimensional maps of physical properties were extracted from our stacked datacubes and the treatment of the HST imaging to derive the morphological properties of our galaxies.
-We also define a classification procedure which separates the KDS galaxies into a merger and modelling sample.
-In \cref{sec:Kinematic_Properties} we present the kinematic modelling applied to the KDS galaxies, including the beam-smearing correction, and the method chosen to extract the kinematic properties following this modelling procedure.
-\cref{sec:results} presents an analysis of the derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
+In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially resolved in the [O~{\sc III}]$\lambda$5007 emission line.
+\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
 We present our conclusions in \cref{sec:conclusion}.
@@
 We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
-These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$_{\beta}$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
+These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
 The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions of spatial overdensity in the south-east (GOODS-S-P1) and north-west (GOODS-S-P2) to fill the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
@@
 This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the spatially resolved metallicities reserved for a future work, and so we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the K-band spectral window.
+\\
 
@@
 For the four pointings described above and summarised in table \ref{tab:pointings}, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
-This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}.
-
-The observations were carried out during ESO observing periods P92-P95 using Guaranteed Time Observations (Programme IDs: xxx xxx xxx)
-The seeing conditions were excellent for GOODS-S-P1 and GOODS-S-P2 with median K-band seeing of $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
-We observed 19-21 targets in each field (\ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92 observing semester and our requirement to observe at least one control star throughout an Observing Block (OB).
+This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\
+
+The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)).
+The seeing conditions were excellent in GOODS-S-P1 and GOODS-S-P2 with median K-band seeing of $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
+We observed 19-21 targets in each field (see table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
+\\
 
@@
 Readout channel bias is addressed using the `LCAL\_XXX.fits' calibration product to identify pixels which are not illuminated during exposures.
-The median values of these pixels are used to correct for varying flux baselines between each 64 pixel wide detector readout column, which if left uncorrected leads to flux bandings over the spatial extent of the reduced cubes.
+The median values of these pixels are used to correct for varying flux baselines between each 64 pixel wide detector readout channel, which if left uncorrected leads to flux bandings over the spatial extent of the reduced cubes.
 Standard star observations are processed to provide a flux calibration for each detector, which is necessary to account for varying sensitivity across the three independent KMOS modules. 
 Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
-Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsub:Obs} which boosts the effective spatial resolution of the observations.
+Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective spatial resolution of the observations.
+\\
 
 Sky subtraction is enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
-Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general we that the use of the SKYTWEAK option in the K-band greatly reduces the sky-line residuals.
+Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the K-band greatly reduces the sky-line residuals.
 
@@
 In addition to this we monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged K-band seeing rises above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
-The telescope tends to drift from its acquired position over the course of an OB, and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
+The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
 As part of this analysis, we tested whether the drift varies across the three KMOS detectors, finding typically that the difference is negligible, suggesting that it is not necessary to sacrifice more than a single IFU for tracking purposes.
+\\
 
@@
 To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux, and then subtracted from each spaxel in turn.
-This assumes that there is no spatial variation in the required correction, which we have found to be valid for our current sample of galaxies.
-
-The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the integrated galaxy spectrum, N$_{[O~{\sc III}]_{Det}}$, the number with spatially resolved [O~{\sc III}]$\lambda$5007 emission, N$_{[O~{\sc III}]_{Res}}$ (see \cref{sec:extracting_properties}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+This assumes that there is no spatial variation in the required correction, which we have found to be valid for our current sample of galaxies. \\
+
+The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the integrated galaxy spectrum, N[O~{\sc III}]$_{Det}$, the number with spatially resolved [O~{\sc III}]$\lambda$5007 emission, N[O~{\sc III}]$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
 \footnote{We note that in GOODS-S-P2 we later found that the redshifts for two of our targets were $z < 0.5$ and we omit these from all columns in table \ref{tab:pointings}.}
@@
 \begin{threeparttable}
-\caption{Summary of KDS pointing statistics}
+\caption{Summary of KDS pointing statistics for the full observed sample of 77 galaxies}
 \label{tab:pointings}
@@
  \hline
-Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band(s) & Exp. Time (ks) & Seeing ($^{\prime\prime}$)  \\
+Pointing & RA & DEC & N$_{obs}$ & N[O~{\sc III}]$_{Det}$ & $\%$ Det. & N[O~{\sc III}]$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band(s) & Exp(ks) & PSF ($^{\prime\prime}$)  \\
  \hline
@@
 \subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
-We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS.
+We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS galaxies.
 During the SED modelling we assume solar metallicity stellar templates, and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
@@
 
-In Figure \ref{fig:main_sequence} we plot the stellar mass (M$_{\star}$) and SFR `main sequence' of the KDS galaxies, in combination with the derived physical properties of $\sim 10,000$ $2.5 < z < 3.5$ SFGs (based upon the `z\_best classification flag') from the 3D-HST survey \citep{Brammer2012,Momcheva2016}.
+In figure \ref{fig:main_sequence} we plot the stellar mass (M$_{\star}$) and SFR `main sequence' of the KDS galaxies, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-HST survey \citep{Brammer2012,Momcheva2016}.
 We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-HST data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the MS relation described in \cite{Speagle2014}: $logSFR(M_{\star}, t) = (0.84 - 0.026 \times t)logM_{\star} - (6.51 - 0.11 \times t)$, evaluated at $z\sim3.5$ where the age of the universe is 1.823Gyr, with the green line.
@@
 they are not especially bursty, or devoid of star formation).
-There are fewer galaxies plotted in Figure \ref{fig:main_sequence} than observed due to the lack of deep, ground-based J and K-band photometry in SSA22 leaving the SFR unconstrained for several objects.
-We omit from this main sequence plot all objects in SSA22 that have J and K band detections lower than 2-$\sigma$ significance, leaving 64\% of the sample across all pointings, and note that the derived (M$_{\star}$) values for the galaxies which are not plotted are consistent with the distribution shown in figure \ref{fig:main_sequence}.
+There are fewer galaxies plotted in figure \ref{fig:main_sequence} than observed due to the lack of deep, ground-based J and K-band photometry in SSA22 leaving the SFR unconstrained for several objects.
+We omit from this main sequence plot all objects in SSA22 that have J and K band detections lower than 2-$\sigma$ significance, leaving 64\% of the sample across all pointings, and note that the derived M$_{\star}$ values for the galaxies which are not plotted are consistent with the distribution shown in figure \ref{fig:main_sequence}.
 \begin{figure}
@@
 
-\begin{table*}
-\centering
-\begin{threeparttable}
-\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying GALFIT \protect\citep{Peng2010_galfit}}
-\label{tab:phys-props}
-\begin{tabular}{ccccccccccc}
-
- \hline
-ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}[M_{\odot}])$ & SFR$_{SED}$($M_{\odot}yr^{-1}$) & $A_{r}$ & i$^{\circ}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc) \\
- \hline
-bs009818        & 03:32:20 & -27:53:01 & 3.706        & 24.18  & 9.79  & 33.0 & 0.8         & 37.0        & 148.0   & 1.24      \\
-bs014828        & 03:32:27 & -27:52:26 & 3.562        & 23.58  & 10.15 & 30.0 & 0.31        & 76.0        & 63.0    & 1.61      \\
-lbg\_20         & 03:32:41 & -27:52:21 & 3.225        & 24.97  & 9.61  & 4.7  & 0.64        & 52.0        & 1.0     & 1.28      \\
-lbg\_105        & 03:32:24 & -27:52:16 & 3.092      & 23.79  & 9.79  & 30.0 & 0.56        & 57.0        & 128.0   & 1.72      \\
-bs006541        & 03:32:15 & -27:52:05 & 3.475       & 23.44  & 10.19 & 18.0 & 0.44        & 66.0        & 168.0   & 1.83      \\
-b012141\_012208 & 03:32:23 & -27:51:57 & 3.471        & 24.12  & 10.16 & 59.0 & 0.36        & 72.0        & 9.0     & 1.57      \\
-b15573          & 03:32:28 & -27:51:00 & 3.583        & 23.6   & 10.37 & 27.0 & 0.28        & 78.0        & 146.0   & 0.52      \\
-bs008543        & 03:32:18 & -27:50:50 & 3.474        & 22.73  & 10.67 & 42.0 & 0.5         & 61.0        & 67.0    & 1.59      \\
-bs006516        & 03:32:15 & -27:50:46 & 3.215        & 23.94  & 9.85  & 14.0 & 0.5         & 61.0        & 146.0   & 1.91      \\
-bs016759        & 03:32:29 & -27:48:53 & 3.602       & 23.85  & 9.99  & 8.8  & 0.65        & 50.0        & 49.0    & 0.87      \\
-lbg\_111        & 03:32:42 & -27:45:52 & 3.609       & 24.01  & 9.74  & 27.0 & 0.74        & 42.0        & 80.0    & 0.64      \\
-lbg\_38         & 03:32:22 & -27:44:38 & 3.488       & 24.58  & 10.03 & 7.5  & 0.58        & 56.0        & 137.0   & 0.92      \\
-lbg\_94         & 03:32:29 & -27:44:12 & 3.367       & 24.54  & 10.01 & 8.1  & 0.22        & 84.0        & 81.0    & 1.16      \\
-lbg\_109        & 03:32:21 & -27:43:46 & 3.600       & 24.63  & 9.73  & 9.4  & 0.6         & 54.0        & 119.0   & 1.98      \\
-lbg\_24         & 03:32:40 & -27:39:57 & 3.279       & 24.67  & 9.71  & 5.9  & 0.53        & 60.0        & 34.0    & 1.27      \\
-lbg\_25         & 03:32:29 & -27:40:22 & 3.322        & 24.95  & 9.44  & 5.8  & 0.3         & 76.0        & 78.0    & 1.18      \\
-lbg\_32         & 03:32:34 & -27:41:24 & 3.417      & 23.84  & 10.17 & 52.0 & 0.6         & 54.0        & 40.0    & 1.88      \\
-lbg\_113        & 03:32:36 & -27:41:50 & 3.622      & 24.01  & 9.83  & 41.0 & 0.52        & 60.0        & 15.0    & 0.87      \\
-lbg\_91         & 03:32:27 & -27:41:52 & 3.170       & 24.65  & 9.8   & 5.7  & 0.58        & 56.0        & 79.0    & 0.89 \\
-s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.4618 & 9.88  & -            & 0.39        & 70.0        & 125.0   & 1.78      \\
-n3\_009       & 22:17:28 & +00:12:12 & 3.069 & 99.0    & 8.72  & -            & 0.75        & 42.0        & 84.0    & 1.06      \\
-lab18         & 22:17:29 & +00:07:52 & 3.101           & 99.0    & 8.66  & -            & 0.85        & 32.0        & 27.0    & 0.46      \\
-s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.9103 & 9.74  & -            & 0.57        & 57.0        & 76.0    & 1.59      \\
-n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.9637 & 9.94  & -            & 0.71        & 46.0        & 94.0    & 0.56      \\
-s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.2538 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
-$^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & 99.0    & 8.78  & -            & 0.57         & 57.3        & -    & 2.4      \\
-$^{*}$s\_sa22b-d5  & 22:17:36 & +00:06:10 & 3.175 & 23.7182 & 10.32 & -            & 0.57         & 57.3        & -    & 2.14      \\
-$^{*}$s\_sa22b-md25 & 22:17:42 & +00:06:20 & 3.304     & 24.6174 & 9.05  & -            & 0.57         & 57.3        & -    & 2.14      \\
-$^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.9847 & 10.64 & 50.0 & 0.57         & 57.3        & -    & 2.14
-
-\end{tabular}
-\begin{tablenotes}
-      \small
-      \item $^{*}$ No HST coverage: $PA_{morph}$ unconstrained; $A_{r}$ and $R_{1/2}$ estimated as explained throughout the text.
-    \end{tablenotes}
-  \end{threeparttable}
-  \end{table*}
-
-\subsection{Morphological Measurements}
+\subsection{Morphological Measurements}\label{subsec:morphological_measurements}
 For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution photometry.
@@
 We use GALFIT \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed HST images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
-The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z \sim 3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\tiny{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}}.
-For SSA22 we make use of archival HST imaging\footnote{\tiny{\url{https://archive.stsci.edu/hst/search.php}}} data in the WFC3 F160W band (P.I.
+The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z \sim 3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
+For SSA22 we make use of archival HST imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the WFC3 F160W band (P.I.
 Lehmer: PID 13844; P.I.
@@
 Siana: PID 12527).
-The HST coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is incomplete, and so we must resort to the bluer ACS F814W data which traces younger stellar populations and may not be sensitive to the majority of the mass distribution within these galaxies.
+The HST coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is concentrated on SSA22-CLUSTER, and so we must resort to the bluer ACS F814W data for SSA22-FIELD (all of the galaxies with HST coverage listed in table \ref{tab:phys-props}) which traces younger stellar populations and may not be sensitive to the majority of the mass distribution within these galaxies.
+\\
 
@@
 This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012} (with the median ratio of $\chi ^{2}$ values equal unity in all cases).
-Additionally, for the corresponding objects in the \cite{VanderWel2012} catalogue the median \Sers index value is 1.2.
-The use of exponential profiles also facilitates comparison with recent large surveys such as KROSS \citep{Harrison2017}, in which beam-smearing correction factors are applied to the derived kinematic parameters as function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:param_extraction}), and KMOS$^{3D}$ \citep{Wisnioski2015}.
+Additionally, for the corresponding objects in the \cite{VanderWel2012} catalogue the median \Sers index value is n = 1.2.
+The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:KROSS}).
+\\
 
@@
 
-This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{sec:Kinematic_Properties}, namely the axis ratio $A_{r}$, half-light radius $R_{1/2}$ and the $PA_{morph}$.
-The errorbars produced by GALFIT are purely statistical and are determined from the covariance matrix used in the fitting, and this results in unrealistically small uncertainties in the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
-Throughout the following subsections we discuss adopted errors on each of the morphological parameters.
+This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $A_{r}$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
+The errorbars produced by GALFIT are purely statistical and are determined from the covariance matrix used in the fitting, with this resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
+Throughout the following subsections we also discuss adopted errors on each of the morphological parameters in turn.
+
+\begin{table*}
+\centering
+\begin{threeparttable}
+\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying GALFIT \protect\citep{Peng2010_galfit}}
+\label{tab:phys-props}
+\begin{tabular}{ccccccccccc}
+
+ \hline
+ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}[M_{\odot}])^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $A_{r}$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
+ \hline
+b012141\_012208 & 03:32:23 & -27:51:57 & 3.471        & 24.12  & 10.16 & 59.0 & 0.36        & 72.0        & 9.0     & 1.57      \\
+b15573          & 03:32:28 & -27:51:00 & 3.583        & 23.6   & 10.37 & 27.0 & 0.28        & 78.0        & 146.0   & 0.52      \\
+bs006516        & 03:32:15 & -27:50:46 & 3.215        & 23.94  & 9.85  & 14.0 & 0.5         & 61.0        & 146.0   & 1.91      \\
+bs006541        & 03:32:15 & -27:52:05 & 3.475       & 23.44  & 10.19 & 18.0 & 0.44        & 66.0        & 168.0   & 1.83      \\
+bs008543        & 03:32:18 & -27:50:50 & 3.474        & 22.73  & 10.67 & 42.0 & 0.5         & 61.0        & 67.0    & 1.59      \\
+bs009818        & 03:32:20 & -27:53:01 & 3.706        & 24.18  & 9.79  & 33.0 & 0.8         & 37.0        & 148.0   & 1.24      \\
+bs014828        & 03:32:27 & -27:52:26 & 3.562        & 23.58  & 10.15 & 30.0 & 0.31        & 76.0        & 63.0    & 1.61      \\
+bs016759        & 03:32:29 & -27:48:53 & 3.602       & 23.85  & 9.99  & 8.8  & 0.65        & 50.0        & 49.0    & 0.87      \\
+lbg\_20         & 03:32:41 & -27:52:21 & 3.225        & 24.97  & 9.61  & 4.7  & 0.64        & 52.0        & 1.0     & 1.28      \\
+lbg\_24         & 03:32:40 & -27:39:57 & 3.279       & 24.67  & 9.71  & 5.9  & 0.53        & 60.0        & 34.0    & 1.27      \\
+lbg\_25         & 03:32:29 & -27:40:22 & 3.322        & 24.95  & 9.44  & 5.8  & 0.3         & 76.0        & 78.0    & 1.18      \\
+lbg\_32         & 03:32:34 & -27:41:24 & 3.417      & 23.84  & 10.17 & 52.0 & 0.6         & 54.0        & 40.0    & 1.88      \\
+lbg\_38         & 03:32:22 & -27:44:38 & 3.488       & 24.58  & 10.03 & 7.5  & 0.58        & 56.0        & 137.0   & 0.92      \\
+lbg\_91         & 03:32:27 & -27:41:52 & 3.170       & 24.65  & 9.8   & 5.7  & 0.58        & 56.0        & 79.0    & 0.89 \\
+lbg\_94         & 03:32:29 & -27:44:12 & 3.367       & 24.54  & 10.01 & 8.1  & 0.22        & 84.0        & 81.0    & 1.16      \\
+lbg\_105        & 03:32:24 & -27:52:16 & 3.092      & 23.79  & 9.79  & 30.0 & 0.56        & 57.0        & 128.0   & 1.72      \\
+lbg\_109        & 03:32:21 & -27:43:46 & 3.600       & 24.63  & 9.73  & 9.4  & 0.6         & 54.0        & 119.0   & 1.98      \\
+lbg\_111        & 03:32:42 & -27:45:52 & 3.609       & 24.01  & 9.74  & 27.0 & 0.74        & 42.0        & 80.0    & 0.64      \\
+lbg\_113        & 03:32:36 & -27:41:50 & 3.622      & 24.01  & 9.83  & 41.0 & 0.52        & 60.0        & 15.0    & 0.87      \\
+$^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.9847 & 10.64 & 50.0 & 0.57         & 57.3        & -    & 2.52      \\
+n3\_009       & 22:17:28 & +00:12:12 & 3.069 & 99.0    & 8.72  & -            & 0.75        & 42.0        & 84.0    & 1.06      \\
+n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.9637 & 9.94  & -            & 0.71        & 46.0        & 94.0    & 0.56      \\
+lab18         & 22:17:29 & +00:07:52 & 3.101           & 99.0    & 8.66  & -            & 0.85        & 32.0        & 27.0    & 0.46      \\
+$^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & 99.0    & 8.78  & -            & 0.57         & 57.3        & -    & 2.18      \\
+s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.4618 & 9.88  & -            & 0.39        & 70.0        & 125.0   & 1.78      \\
+s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.9103 & 9.74  & -            & 0.57        & 57.0        & 76.0    & 1.59      \\
+$^{*}$s\_sa22b-d5  & 22:17:36 & +00:06:10 & 3.175 & 23.7182 & 10.32 & -            & 0.57         & 57.3        & -    & 3.30      \\
+s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.2538 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
+$^{*}$s\_sa22b-md25 & 22:17:42 & +00:06:20 & 3.304     & 24.6174 & 9.05  & -            & 0.57         & 57.3        & -    & 1.39
+
+\end{tabular}
+\begin{tablenotes}
+      \small
+      \item $^{a}$ Representative error of 0.2dex from SED modelling used throughout this study
+      \item $^{b}$ Representative error of 0.4dex in log(SFR$_{SED}$[$M_{\odot}yr^{-1}$]) from SED modelling used throughout this study
+      \item $^{c}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
+      \item $^{d}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
+      \item $^{*}$ No HST coverage: $PA_{morph}$ unconstrained; $A_{r}$ and $R_{1/2}$ estimated as explained throughout the text.
+    \end{tablenotes}
+  \end{threeparttable}
+  \end{table*}
 
 \subsubsection{Inclination angle}\label{subsubsection:inclination_angle}
-We used the derived $A_{r}$ values to determine galaxy inclination angles.
-As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a} \equiv A_{r}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
+We use the derived $A_{r}$ values to determine galaxy inclination angles.
+As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in equation \ref{eq:holmberg_i}, where $\frac{b}{a} \equiv A_{r}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
 To derive the inclination, we must select a value for $q_{0}$, and following the discussion in \citep{Law2012a} we choose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
@@
 For the inclination error we adopt a conservative nominal uncertainty of 10$\%$ also, i.e.
-$\Delta i = i / 10$, after examining the typical magnitude of the uncertainties reported following the Monte Carlo procedure described in \cite{Epinat2012}.
+$\delta i = i / 10$, after examining the typical magnitude of the uncertainties reported following the Monte Carlo procedure described in \cite{Epinat2012}.
 We also note that generally this inclination uncertainty is a function of the recovered axis ratio, since it is more difficult to determine the inclination when the galaxy is more `face-on', but detailed inclination angle uncertainty modelling is beyond the scope of this paper.
@@
 The third morphological parameter is the half-light radius, $R_{1/2}$, which provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
-As discussed throughout the introduction and in \cref{subsubsec:param_extraction}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
+As discussed throughout the introduction and in \cref{subsubsec:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
 Knowledge of $R_{1/2}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made, both of which are important when making comparisons to previous IFU studies \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
-Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d modelling}), which requires the $R_{1/2}$ value for each galaxy.
+Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d_modelling}), which requires the $R_{1/2}$ value for each galaxy.
 A final use of the derived $R_{1/2}$ values is to verify our beam-smearing correction results through comparison with systematic correction factors presented in Johnson et al.
-(in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:param_extraction}).
+(in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:KROSS}).
 
 \cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in CANDELS, reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
-We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ recovered from extracting at $R_{1/2}$ and the errors on the intrinsic velocity dispersion, $\sigma_{int}$, the derivation of which requires knowledge of $R_{1/2}$ (\cref{subsec:3d modelling}) are dominated by measurement errors and uncertainties connected with assumptions about the velocity dispersion distribution in high redshift galaxies (see \cref{app:kin_error_estimates}).
-
-\subsubsection{Lack of HST Coverage}\label{subsubsection:lack_of_hst}
+We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ recovered from extracting at $R_{1/2}$ and the errors on the intrinsic velocity dispersion, $\sigma_{int}$, the derivation of which requires knowledge of $R_{1/2}$ (\cref{subsec:3d_modelling}) are dominated by measurement errors and uncertainties connected with assumptions about the velocity dispersion distribution in high redshift galaxies (see \cref{app:kin_error_estimates}).
+
+\subsubsection{Galaxies without HST Coverage}\label{subsubsection:lack_of_hst}
 In SSA22, 4/21 of the spatially resolved galaxies do not have any HST coverage.
@@
 This corresponds to a factor $\sim1.3$ uncertainty in the derived velocities for these galaxies.
-We fix $PA_{morph}$ equal to $PA_{kin}$ for the analysis described in \cref{subsec:3d modelling} and to measure $R_{1/2}$ we first fit the continuum light in the median stacked HK datacubes with a exponential profile, and subtract the PSF from the recovered $R_{1/2}$ value.
-For these galaxies we also adopt a nominal $R_{1/2}$ error of 10$\%$ following the description above, and note that the derived $V_{C}$ values are not sensitive to the precise $R_{1/2}$ values, since we measure at $2R_{1/2}$ where the rotation curves have already flattened.
+We fix $PA_{morph}$ equal to $PA_{kin}$ for the analysis described in \cref{subsec:3d_modelling} and to measure $R_{1/2}$ we first fit the [O~{\sc III}]$\lambda$5007 narrowband images with an exponential profile, and subtract the PSF from the recovered $R_{1/2}$ value.
+We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening.
 Owing to the small number of galaxies without HST imaging, we do not expect this to impact the bulk dynamical properties of the KDS sample.
@@
 Having derived $R_{1/2}$, $A_{r}$ and $PA_{morph}$ for each of the KDS field galaxies \ref{fig:morpho-distributions} we plot the distributions of these properties, using KDS galaxies with HST coverage, along with distributions of morphological parameters determined in \cite{VanderWel2012} at low and high redshift.
-The KDS galaxies have been identified in the \cite{VanderWel2012} catalogue and the morphological properties show excellent agreement, with median $\Delta A_{r} = 0.0002$, median $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\sim3.5$) and the median \cite{VanderWel2012} $n = 1.2$ value for the KDS values close to our adopted n = 1 exponential disk fits.
+The GOODS-S KDS galaxies have been identified in the \cite{VanderWel2012} catalogue and the morphological properties show excellent agreement, with median $\Delta A_{r} = 0.0002$, median $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\sim3.5$) and the median \cite{VanderWel2012} $n = 1.2$ value for the KDS values close to our adopted n = 1 exponential disk fits.
 
@@
 The derived KDS $R_{1/2}$ distribution at $z \sim 3.5$ is similar to the wider sample distribution at $3 < z  < 4$, i.e.
-compact when compared to galaxies at lower redshifts and the KDS $A_{r}$ are consistent with being generally uniform between $0.3 < A_{r} < 0.9$, with median value of 0.57, corresponding to i = 57.4$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$, which is close to the statistical mean for a random galaxy sample.
+compact when compared to galaxies at lower redshifts and the KDS $A_{r}$ are consistent with being generally uniform between $0.3 < A_{r} < 0.9$, with median value of 0.57, corresponding to i = 57.4$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$, which is close to the statistical mean of i = 57.3$^{\circ}$ for a random galaxy sample.
 This reassures us that we are not biased towards deriving either particularly low or particularly high inclination angles.
@@
 \subsubsection{Spaxel Fitting}\label{subsubsection:spaxel_fitting}
-Having produced stacked and calibrated datacubes for each of the 77 galaxies in the full KDS sample, we aim to extract 2-dimensional maps of the flux, velocity and velocity dispersion.
+We aim to extract 2-dimensional maps of the flux, velocity and velocity dispersion from each of the 77 stacked and calibrated KDS datacubes.
 These properties are extracted via modelling of the ionised gas emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
@@
 Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn, within which we locate the systemic wavelength of the redshifted [O~{\sc III}]$\lambda$5007 centre, $\lambda_{obs_{5007}}$, using the redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum.
+\\
 
@@
 This boundary constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
-The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation~\ref{eq:mask_noise} where $F_{i}$ are the flux values across the extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
+The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in equation \ref{eq:noise} where $F_{i}$ are the flux values across the extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
 
@@
 fits to skyline residuals), which is important for `cleaning up' accepted spaxels in the 2D maps which are clearly independent of the main body of the galaxy.
-For this test we subtract the galaxy continuum and impose that the $0.7 < F_{g}/{S} < 1.3$, where $F_{g}$ is the flux from the gaussian fit to the [O~{\sc III}]$\lambda$5007 line and S is the signal in the extraction region from equation \ref{eq:signal}.
+For this test we subtract the galaxy continuum and impose that $0.7 < F_{g}/{S} < 1.3$, where $F_{g}$ is the flux from the gaussian fit to the [O~{\sc III}]$\lambda$5007 line and S is the signal in the extraction region from equation \ref{eq:signal}.
 
@@
 This Monte Carlo procedure gives the fit parameters and associated errors for the accepted spaxels.
-The velocity is computed from the gaussian centre, $\lambda_{g}$, using Equation~\ref{eq:velocity_comp} and the velocity dispersion is computed from the gaussian width, $\sigma_{g}$, using Equation~\ref{eq:dispersion_comp}, where $v_{obs}$ and $\sigma_{obs}$ are the observed rotational velocity and velocity dispersion respectively, c is the speed of light and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
+The velocity is computed from the gaussian centre, $\lambda_{g}$, using Equation~\ref{eq:velocity_comp} and the velocity dispersion is computed from the gaussian width, $\sigma_{g}$, using Equation~\ref{eq:dispersion_comp}, where $v_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
 
@@
 If the binned spaxels fail the criteria, one final iteration is carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$, roughly equivalent to the size of the seeing disk.
-If after the widest binning the criteria aren't satisfied, no value is assigned to that spaxel.
+If after the widest binning the criteria aren't satisfied, no value is assigned to that spaxel in the extracted maps. \\
 
@@
 Following the fitting procedure the galaxies are clasified as spatially resolved in [O~{\sc III}]$\lambda$5007 emission or not, with this defined as  the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map equivalent to or greater than the seeing disk.
-For each pointing, the number of resolved galaxies, $N_{res}$, is added to table \ref{tab:pointings}.
+For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, is added to table \ref{tab:pointings}.
 29\% of the detected KDS galaxies are not spatially resolved, and we do not analyse these further, despite several showing velocity gradients within the seeing disk, due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
@@
 
-As mentioned in the introduction, there is no universal standard for defining $V_{C}$ and $\sigma_{int}$, particularly when it is extrapolated from the data using a fitted model, of which there are several types.
+As mentioned in the introduction, there is no universal standard for defining $V_{C}$ and $\sigma_{int}$, particularly a dynamical model is used to provide beam-smearing corrections for $\sigma_{int}$ and extrapolations beyond the data for $V_{C}$.
 Physically motivated models take into account the potential-well of the galaxy through knowledge of the mass distribution \citep[e.g.][]{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015}.
@@
 If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam-smearing.
+
 The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
-In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
-The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
-This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.
+In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination from the HST axis ratio.
+The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
+This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion. \\
 
@@
 This suggests that the velocity midpoint may be biased towards the side of the galaxy which shows the higher velocity value and so we instead use the physically motivated continuum centre where possible, which also matches the approach described in \cite{Harrison2017}.
+\\
 
@@
 There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
-We provide an overview of these surveys in \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of the parameters used for comparison to the KDS throughout results \cref{subsec:redshift_evolution}).
+We provide an overview of these surveys in \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of these parameters used for comparison to the KDS throughout  \cref{subsec:redshift_evolution}).
 
@@
 The $R_{1/2}$ value used to extract velocities from the KMOS data is found by convolving the intrinsic $R_{1/2}$ value with the PSF of the observations.
-The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
-The beam-smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
-The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in \cref{subsubsec:observed_and_intrinsic}.
-The $V_{C}$ errors are discussed in \cref{appsubsubsec:model_errors}.
+The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
+This is similar also to the $V_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}.
+The beam-smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class} for the morpho-kinematic classification).
+The $V_{C}$ errors are discussed in \cref{appsubsec:model_errors}. \\
 
@@
 The model therefore provides a beam-smearing correction for the velocity dispersion in every spaxel.
-This is dependent primarily on the magnitude of the velocity gradient across the parameter maps, verified by the positive correlation between observed velocities and velocity dispersions.
-The 2D beam-smearing correction map, $\sigma_{bs}$, is taken as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion i.e.
+This is dependent primarily on the magnitude of the velocity gradient across the parameter maps, an approach which is verified by the observation of a positive correlation between the KDS velocities and velocity dispersions.
+The 2D beam-smearing correction map, $\sigma_{bs}$, is taken as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50kms$^{-1}$ i.e.
 $\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
-
-The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in \cref{appsubsubsec:model_errors}.
+The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in \cref{appsubsec:model_errors}.
 We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.
@@
 $\sigma_{obs}/\sigma_{int}$, with mean and median values of 0.77 and 0.79 respectively for the morphologically isolated KDS galaxies.
+\\
 
@@
 (in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
-These correction factors are applied to $V_{smeared}$ to reach $V_{C}$ and to $\sigma_{obs}$ to reach $\sigma_{int}$.
+These correction factors are applied to $V_{smeared}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
 The $V_{C}$ values agree to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities. 
@@
 \label{tab:kin_props}
-\begin{tabular}{ccccccccc}
+\begin{tabular}{cccccccc}
 
  \hline
-ID & $V_{obs}$(kms$^{-1}$) & $V_{C}$(kms$^{-1}$) & $\sigma_{obs}$(kms$^{-1}$) & $\sigma_{int}$(kms$^{-1}$) & $V_{C}/\sigma_{int}$ & $R_{1/2}$(kpc) & PA$_{kin}^{\circ}$ & Class$^{a}$ \\
+ID & $V_{obs}$(kms$^{-1}$) & $V_{C}$(kms$^{-1}$) & $\sigma_{obs}$(kms$^{-1}$) & $\sigma_{int}$(kms$^{-1}$) & $V_{C}/\sigma_{int}$ & PA$_{kin}^{\circ}$ & Class$^{a}$ \\
  \hline
-bs009818        & 65.0                    & 84.0                     & 95.0                  & 79.0                   & 1.06       & 1.25        & 72.0 & RD \\
-bs014828        & 32.0                    & 46.0                     & 97.0                  & 88.0                   & 0.53       & 1.65      & 44.0 & DD    \\
-lbg\_20         & 26.0                    & 56.0                     & 55.0                  & 40.0                   & 1.39      & 1.30        & 41.0 & RD  \\
-lbg\_105        & 13.0                    & 32.0                     & 68.0                  & 59.0                   & 0.54       & 1.75       & 170.0 & DD \\
-bs006541        & 36.0                    & 65.0                     & 96.0                  & 83.0                   & 0.78        & 1.85       & 23.0 & DD \\
-b012141\_012208 & 34.0                    & 93.0                     & 94.0                  & 63.0                   & 1.47       & 1.60       & 122.0 & RD \\
-b15573          & 62.0                    & 81.0                     & 111.0                 & 84.0                   & 0.97        & 0.50       & 118.0 & DD \\
-bs008543        & 77.0                    & 111.0                    & 98.0                  & 71.0                   & 1.56       & 1.60       & 114.0 & RD \\
-bs006516        & 56.0                    & 61.0                     & 64.0                  & 45.0                   & 1.35      & 1.95       & 144.0 & RD  \\
-bs016759        & 71.0                    & 110.0                    & 82.0                  & 57.0                   & 1.93        & 0.90       & 75.0 & RD \\
-lbg\_111        & 53.0                    & 58.0                     & 90.0                  & 81.0                   & 0.71      & 0.65        & 168.0 & DD \\
-lbg\_38         & 31.0                    & 97.0                     & 76.0                  & 53.0                   & 1.82        & 0.95       & 47.0 & RD \\
-lbg\_94         & 18.0                    & 34.0                     & 65.0                  & 55.0                   & 0.62       & 1.20       & 41.0 & DD \\
-lbg\_109        & 32.0                    & 53.0                     & 101.0                 & 91.0                   & 0.58      & 2.00        & 157.0 & DD \\
-lbg\_24         & 30.0                    & 42.0                     & 64.0                  & 51.0                   & 0.82      & 1.30       & 64.0 & DD  \\
-lbg\_25         & 14.0                    & 33.0                     & 53.0                  & 41.0                   & 0.8       & 1.20        & 87.0 & DD  \\
-lbg\_32         & 79.0                    & 121.0                    & 104.0                 & 76.0                   & 1.58       & 1.90       & 11.0 & RD  \\
-lbg\_91         & 58.0                    & 91.0                     & 98.0                  & 71.0                   & 1.28       & 0.90        & 40.0 & RD \\
-lbg\_113        & 0.0                    & 0.0                      & 116.0                 & 112.0                  & 0.0         & 0.90       & 28.0 & DD \\
-s\_sa22a-d3   & 57.0                    & 109.0                    & 127.0                 & 93.0                   & 1.16        & 1.80       & 30.0 & RD \\
-n3\_009       & 32.0                    & 47.0                     & 77.0                  & 48.0                   & 1.0       & 1.07       & 20.0 & RD  \\
-lab18         & 44.0                    & 41.0                     & 87.0                  & 62.0                   & 0.67     & 0.45       & 54.0 &  DD  \\
-s\_sa22b-c20  & 79.0                    & 139.0                    & 112.0                 & 48.0                   & 2.87       & 1.60       & 37.0 & RD  \\
-n\_c3         & -                    & -                      & 96.0                  & 78.0                   & -        & 0.55       & -  & DD     \\
-s\_sa22b-d9   & -                    & -                      & 99.0                  & 82.0                   & -      & 0.50       & 163.0 & DD    \\
-$^{*}$lab25         & 42.0                    & 48.0                     & 80.0                  & 49.0                   & 0.98       & -       & 72.0 & DD    \\
-$^{*}$s\_sa22b-d5   & 31.0                    & 57.0                     & 67.0                  & 23.0                   & 2.45      & -       & 60.0 & RD     \\
-$^{*}$s\_sa22b-md25 & 50.0                    & 57.0                     & 102.0                 & 75.0                   & 0.76       & -       & 9.0 & DD      \\
-$^{*}$n3\_006       & 41.0                    & 81.0                     & 144.0                 & 125.0                  & 0.65      & -       & 156.0 & DD
+b012141\_012208 & 32$\pm$13                    & 93$^{+48}_{-40}$                     & 94$\pm$18                 & 63$^{+28}_{-30}$                 & 1.47$^{+48}_{-40}$             & 122$^{+9}_{-9}$ & RD   \\
+b15573          & 61$\pm21$                    & 81$^{+30}_{-33}$                     & 111$\pm23$                 & 84$^{+28}_{-26}$          & 0.97$^{+0.47}_{-0.52}$            & 118$^{+10}_{18}$ & DD   \\
+bs006516        & 49$\pm4$                    & 61$^{+10}_{-9}$                     & 64$\pm8$                  & 45$^{+10}_{-9}$              & 1.35$^{+0.37}_{-0.38}$         & 144$^{+4}_{-4}$ & RD   \\
+bs006541        & 33$\pm8$         & 65$^{+24}_{-20}$          & 96$\pm7$                  & 83$^{+9}_{-16}$             & 0.78$^{+0.34}_{-0.26}$          & 23$^{+3}_{-4}$ & DD    \\
+bs008543        & 68$\pm13$                    & 111$^{+20}_{-16}$                    & 98$\pm7$                  & 71$^{+13}_{-10}$         & 1.56$^{+0.37}_{-0.38}$                & 114$^{+1}_{-1}$  & RD  \\
+bs009818        & 39$\pm16$                    & 84$^{+39}_{-23}$                     & 95$\pm19$                  & 79$^{+21}_{-31}$       & 1.06$^{+0.65}_{-0.41}$                   & 72$^{+13}_{-15}$ & RD    \\
+bs014828        & 31$\pm15$                    & 46$^{+23}_{-23}$                     & 97$\pm15$                  & 88$^{+15}_{-17}$      & 0.53$^{+0.28}_{-0.28}$               & 44$^{+15}_{-11}$  & DD  \\
+bs016759        & 55$\pm9$                    & 110$^{+30}_{-21}$                    & 82$\pm11$                  & 57$^{+17}_{-22}$         & 1.93$^{+0.93}_{-0.7}$               & 75$^{+6}_{-6}$ & RD    \\
+lbg\_20         & 20$\pm$                    & 56$^{+30}_{-19}$                     & 55$\pm6$                  & 40$^{+7}_{-21}$         & 1.39$^{+1.04}_{-0.53}$              & 41$^{+9}_{-10}$ & RD   \\
+lbg\_24         & 26$\pm6$                    & 42$^{+9}_{-7}$                     & 64$\pm5$                  & 51$^{+5}_{-6}$           & 0.82$^{+0.21}_{-0.17}$          & 64$^{+3}_{-4}$ & DD   \\
+lbg\_25         & 14$\pm5$                    & 33$^{+13}_{-13}$                     & 53$\pm6$                  & 41$^{+6}_{-8}$         & 0.8$^{+0.37}_{-0.34}$                  & 87$^{+7}_{-12}$  & DD   \\
+lbg\_32         & 65$\pm5$                    & 121$^{+13}_{-12}$                    & 104$\pm13$                 & 76$^{+16}_{-15}$       & 1.58$^{+0.36}_{-0.37}$               & 11$^{+2}_{-1}$ & RD \\
+lbg\_38         & 26$\pm7$                    & 97$^{+72}_{-34}$                     & 76$\pm10$                  & 53$^{+16}_{-53}$       & 1.82$^{+2.3}_{-0.86}$               & 47$^{+2}_{-3}$  & RD   \\
+lbg\_91         & 48$\pm10$                    & 91$^{+15}_{-18}$                     & 98$\pm8$                  & 71$^{+16}_{-14}$        & 1.28$^{+0.33}_{-0.39}$              & 40$^{+5}_{-3}$  & RD  \\
+lbg\_94         & 18$\pm8$                    & 34$^{+19}_{-15}$                     & 65$\pm6$                  & 55$^{+7}_{-8}$         & 0.62$^{+0.36}_{-0.29}$                & 41$^{+18}_{-9}$  & DD  \\
+lbg\_105        & 11$\pm8$                    & 32$^{+17}_{-16}$                     & 68$\pm18$                  & 59$^{+18}_{-18}$        & 0.54$^{+0.34}_{-0.32}$                & 170$^{+4}_{-7}$ & DD  \\
+lbg\_109        & 26$\pm8$                    & 53$^{+21}_{-15}$                     & 101$\pm16$                 & 91$^{+16}_{-18}$      & 0.58$^{+0.26}_{-0.2}$                & 157$^{+11}_{-11}$ & DD  \\
+lbg\_111        & 36$\pm12$         & 58$^{+24}_{-17}$                     & 90$\pm14$                  & 81$^{+14}_{-16}$                   & 0.71$^{+0.33}_{-0.25}$                 & 168$^{+4}_{-5}$ & DD  \\
+lbg\_113        & 50$\pm20$           & 41$^{+41}_{-29}$                     & 116$\pm22$                 & 108$^{+23}_{-25}$                  & 0.39$^{+0.39}_{-0.29}$                & 1$^{+34}_{-26}$  & DD   \\
+$^{*}$n3\_006         & 36$\pm23$                    & 81$^{+47}_{-29}$                     & 144$\pm26$                 & 125$^{+27}_{-31}$          & 0.65$^{+0.41}_{-0.27}$                & 156$^{+13}_{-12}$ & DD   \\
+n3\_009         & 21$\pm9$                    & 49$^{+26}_{-16}$                     & 77$\pm13$                  & 48$^{+14}_{-45}$          & 1.01$^{+1.1}_{-0.45}$                & 20$^{+28}_{-25}$  & RD   \\
+n\_c3           & 26$\pm$                    & 51$^{+17}_{-18}$                     & 96$\pm11$                  & 72$^{+12}_{-13}$          & 0.72$^{+0.28}_{-0.29}$                & 137$^{+4}_{-15}$  & DD  \\
+lab18           & 23$\pm11$                   & 41$^{+17}_{-14}$                     & 87$\pm6$                  & 62$^{+7}_{-15}$           & 0.67$^{+0.32}_{-0.24}$                 & 54$^{+18}_{-26}$ & DD    \\
+$^{*}$lab25           & 37$\pm11$                    & 48$^{+22}_{-16}$                     & 80$\pm8$                  & 49$^{+10}_{-19}$          & 0.98$^{+0.59}_{-0.4}$                & 72$^{+14}_{-13}$ & DD   \\
+s\_sa22a-d3     & 53$\pm17$                    & 109$^{+52}_{-32}$                    & 127$\pm13$                 & 93$^{+20}_{-36}$          & 1.16$^{+0.72}_{-0.43}$               & 30$^{+2}_{-2}$ & RD    \\
+s\_sa22b-c20    & 66$\pm18$                    & 139$^{+33}_{-30}$                    & 112$\pm17$                 & 48$^{+34}_{-51}$          & 2.87$^{+3.12}_{-2.14}$                & 37$^{+26}_{-11}$ & RD   \\
+$^{*}$s\_sa22b-d5     & 27$\pm10$                    & 57$^{+26}_{-23}$                     & 67$\pm20$                  & 23$^{+23}_{-18}$          & 2.45$^{+3.44}_{-2.41}$               & 60$^{+19}_{-19}$ & RD   \\
+s\_sa22b-d9     & 32$\pm14$                    & 46$^{+22}_{-15}$                     & 99$\pm8$                  & 73$^{+10}_{-17}$             & 0.63$^{+0.33}_{-0.23}$                 & 12$^{+23}_{-7}$ & DD   \\
+$^{*}$s\_sa22b-md25   & 44$\pm15$           & 57$^{+34}_{-24}$                     & 102$\pm19$   & 75$^{+21}_{-30}$                   & 0.76$^{+0.56}_{-0.39}$                & 9$^{+12}_{-7}$ & DD
 
@@
   \end{table*}
-
 \subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}
 
-The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT in \cref{subsubsec:galfitting}, to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
+The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
 This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
@@
 
-The resolved KDS galaxies at $z \sim 3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 35^{\circ}$), and this observation has several potential explanations.
-For the majority of galaxies we do not believe we are in a regime where prominent morphological features are resolved in the HST imaging, so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
+The resolved KDS galaxies at $z \sim 3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
+For the majority of galaxies we do not believe we are in a regime where prominent morphological features are resolved in the HST imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
 However there are some cases where morphological tidal features could affect $PA_{morph}$ such as the GOODS-S galaxies bs006541, bs008543, cdfs\_lbg\_105, cdfs\_lbg\_109 and cdfs\_lbg\_111.
@@
 GOODS-S galaxy bs006541).
-As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ makes a median difference of xxx to the final $V_{C}$, a difference which does not affect the outcomes of this work.
+As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ makes only a small difference to the final $V_{C}$ values, a difference which does not affect the outcomes of this work.
 
@@
 Throughout \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
-The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission line.
-Given the range of modelling and kinematic parameter extraction methods it is important to verify the extent to which the results from these surveys can be directly compared and treated as forming an evolutionary sequence, which we do in the following subsections by considering each survey in turn.
+The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out main sequence SFGs and traces the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission lines.
+Given the range of modelling and kinematic parameter extraction methods it is important to verify the extent to which the results from these surveys can be directly compared and treated as forming an evolutionary sequence, which we test in the following subsections by considering each survey in turn.
+
 We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
@@
 The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
-The same process is applied to compute the errors on the sample medians, and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
+The same process is applied to compute the errors on the sample medians and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
 These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
@@
 \subsubsection{GHASP}\label{subsubsec:GHASP}
-The GHASP survey \citep[E08]{Epinat2008a,Epinat2008} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to derive 3D H$\alpha$ datacubes.
+The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to derive 3D H$\alpha$ datacubes.
 The data extend out to several half-light radii and in each case an analytic function is fit to determine $V_{C}$, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
@@
 We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}[M_{\odot}])=9.9$ and $z\sim0.9$.
-$V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) and the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius, and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
+$V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) with the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
 These quantities are then beam-smearing corrected as described in H17 section 3.3.3. 
@@
 At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.
-The rotational velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
+The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
 No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.
@@
 In addition, \cite[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
-In this approach the $V_{C}$ value comes from the best fitting model parameter, and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
+In this approach the $V_{C}$ value comes from the best fitting model parameter and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
 
@@
 
-It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness, and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
+It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
 We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in \cref{subsec:redshift_evolution} plots.
@@
 The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
-Beam-smearing corrections are not applied to these quantities.
-We use tabulated data in L09 to compare with the $\sigma_{int}$ distribution, but make no comparisons with the observed velocity-shear values.
+We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
+These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
+We use tabulated data $\sigma_{int}$ data in L09 to compare this distribution with other results, but make no comparisons with the observed velocity-shear values.
 
@@
 We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
-Also, for 5 galaxies in G11 $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error equal to 1.
-The $\sigma_{int}$ errors for individual galaxies are generally very small, and for 3 galaxies the $\sigma_{int}$ value is consistent with 0kms$^{-1}$.
+\\
+
+Also, for 5 galaxies in G11 $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error on $V_{C}$ equal to 1 when computing the sample averages.
+The $\sigma_{int}$ errors for individual galaxies are generally very small and for 3 galaxies the $\sigma_{int}$ value is consistent with 0kms$^{-1}$.
 For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
@@
 The remaining 5 galaxies we refer to as the AMAZE Clean sample and plot with grey symbols.
-We also plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated.
-
-This summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
+We also plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated. \\
+
+This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
 This trend towards consistency is encouraging, and as described in \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
@@
 \subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
-We proceed to make use of the morphological and kinematic information described above to classify resolved KDS galaxies into three categories; \textbf{(1)} Rotation Dominated; \textbf{(2)} Dispersion Dominated; \textbf{(3)} Mergers.
+We proceed to make use of the morphological and kinematic information described above to classify resolved KDS galaxies into three categories; \textbf{(1)} Rotation dominated; \textbf{(2)} Dispersion dominated; \textbf{(3)} Merger candidates.
 Previous studies have used various classification schemes of varying complexity to identify which galaxies fall into these categories, and also to identify galaxy which appear `disky'.
-The includes the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in FS09 and C09.
-In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies in by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
+This includes the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in FS09 and C09.
+In W15 a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
 In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
 In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in \cref{subsubsec:AMAZE}.
+
+We describe our simple classification criteria for the KDS galaxies based on a joint consideration of the high-resolution photometry and derived kinematic parameters in the following subsections.
 
@@
 can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging.
-In short, the galaxies with multiple photometric components do not always have disordered kinematics, and so the kinematics alone are not sufficient for classification.
+In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
 It is difficult to distinguish in some cases between two HST components rotating together in a single disk (i.e.
 clumpy disk galaxies \citep[e.g.][]{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
-Perhaps the most telling diagnostic is a double peak in the object spectrum at the kinematic centre, which allows for the classification of IFU data with 2 HST flux peaks as mergers.
-
-In 6/34 of the resolved KDS field galaxies (one count per merger) we clearly identify signs of multiple components or merging in the HST high-resolution imaging, which translates into a merger rate of 18\%.
+Perhaps the most telling diagnostic are two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map. \\
+
+In 6/35 of the resolved KDS field galaxies (one count per merger) we clearly identify signs of multiple components or merging in the HST high-resolution imaging, which translates into a merger rate of 17\%.
 In 8/9 resolved KDS cluster galaxies we identify multiple photometric components, translating into a merger rate of 89\%  (see table \ref{tab:pointings}).
-The higher cluster galaxy merger rate is perhaps unsurprising in such a high-density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas and the morphological evolution of these galaxies.
+The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they are drawn from a higher density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas as well as the morphological and dynamical evolution within these galaxies.
 The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
 We do not consider these merger candidates in the results \cref{sec:results}, but keep the KDS galaxies without HST coverage on the basis that we do not identify double components in the galaxy continuum maps.
-In Appendix \cref{app:mergers} we present the HST imaging, kinematic maps and 1-dimensional kinematic extractions of the merger candidates for the KDS galaxies.
+In figure \ref{fig:merger_galaxies} we present the HST imaging, kinematic maps and 1-dimensional kinematic extractions of the KDS merger candidates.
 
 \subsubsection{Isolated KDS classification}\label{subsubsection:isolated_classification}
-As a result of the unusually high density of mergers in the cluster environment, we omit these galaxies from further analysis and calculate rotation and dispersion dominated percentages with repsect to the total number of resolved galaxies in the field environment (35, see table \ref{tab:pointings}).
-The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/35 or 37\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$,15/35 or 43\% of the sample, as indicated in table \ref{tab:kin_props}.
-We plot the best fitting smeared and intrinsic models for the resolved KDS field galaxies \cref{app:kinematics_plots}, where the galaxies have been divided into dispersion and rotation dominated categories respectively in sections \cref{app:rotation_dominated} and \cref{app:dispersion_dominated}.
+We calculate rotation and dispersion dominated percentages with repsect to the total number of resolved galaxies in the field environment (35, see table \ref{tab:pointings}).
+The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/35 or 37\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 15/35 or 43\% of the sample, as indicated in table \ref{tab:kin_props}.
+We plot the best fitting smeared and intrinsic models for the resolved KDS field galaxies in \cref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
 
 \subsubsection{Summary of the final sample for further analyses}\label{subsubsec:kin_sample_summary}
-In summary, we have analysed the 77 $z\sim3.5$ SFGs initially targetted as part of the KDS, finding spatially resolved [O~{\sc III}]$\lambda$5007 emission in 43 galaxies (56\%).
+In summary, we have analysed the 77 $z\sim3.5$ SFGs initially targeted as part of the KDS, finding spatially resolved [O~{\sc III}]$\lambda$5007 emission in 44 galaxies (56\%).
 These resolved galaxies cover both cluster and field environments and due to the unusually high merger rate of 89\% in the cluster environment, we omit the 9 spatially resolved galaxies in this pointing from further consideration.
@@
 In the remaining sample of 35 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 17\%, and following the classification described in \cref{subsubsection:isolated_classification} we find 13 rotation dominated galaxies (37\%) and 16 dispersion dominated galaxies (46\%) in the field sample.
-For these 29 galaxies we have measured morphological parameters using GALFIT to fit exponential disks to the HST imaging (see table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$, $V_{C}$, and the intrinsic velocity, $\sigma_{int}$ (see table \ref{tab:kin_props}).
+For these 29 galaxies we have measured morphological parameters using GALFIT to fit exponential disks to the HST imaging (see table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$, $V_{C}$, and the intrinsic velocity dispersions, $\sigma_{int}$ (see table \ref{tab:kin_props}).
 Throughout the remainder of the paper we discuss the derived kinematic properties of these 29 galaxies in further detail.
@@
 Throughout the following sections we analyse the derived kinematic parameters for these 29 galaxies, referred to as the `isolated field sample' in the remainder of the paper, placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{subsubsec:comparison_samples}.
-In \cref{subsubsec:comparison_samples} we have also described the variation in the methodology used to compute $V_{C}$ and $\sigma_{int}$ between different surveys as a way to help disentangle true evolution from offsets between derived dynamical values caused by disparate measurement techniques.
-It appears that choice of dynamical model and dynamical parameter extraction method does still play a large role in understanding the evolution of dynamical parameters, and for this reason we have verified that our modelling and measurement techniques are consistent with KROSS $z\sim0.9$ results described in \cite{Harrison2017}, allowing for robust comparisons between this and the isolated field sample.
+In \cref{subsubsec:comparison_samples} we have also described the variety of methodologies used to compute $V_{C}$ and $\sigma_{int}$ between comparison in an attempt to disentangle true evolution from offsets between derived dynamical values caused by disparate measurement techniques in the following analysis sections.
+It appears that choice of dynamical model and dynamical parameter extraction method does still play a large role in understanding the evolution of dynamical parameters, and for this reason we have verified that our modelling and measurement techniques are consistent with KROSS $z\sim0.9$ results described in \cite{Harrison2017}, allowing for robust comparisons between this and the KDS isolated field sample.
 
@@
     \caption{In the left panel the distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
-    The AMAZE Clean sample galaxies are plotted with grey symbols and the unconstrained galaxies are plotted with clear symbols.
-    There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement, with the AMAZE Unconstrained galaxies mostly scattering to high $V_{C}$ values, despite having similar stellar mass range to the KDS, as a result of large extrapolations from the data.
-    The $V_{C}/\sigma_{int} = 1$ divides the galaxies classified as rotation dominated and dispersion dominated, with dispersion dominated galaxies sitting above the line. 
+    The AMAZE Clean sample galaxies (see \protect\cref{subsubsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
+    There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement, with the AMAZE Unconstrained galaxies mostly scattering to high $V_{C}$ values, despite sharing a common stellar mass range to the KDS, as a result of large extrapolations from the data.
+    The $V_{C}/\sigma_{int} = 1$ line divides the galaxies classified as rotation dominated and dispersion dominated, with dispersion dominated galaxies sitting above the line. 
     The galaxy s\_sa22a-M38, classified here as a merger but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ is marked on the plot.
@@
 
-In figure \ref{fig:v_sig_and_v} (a) we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane.
+In the left panel of figure \ref{fig:v_sig_and_v} we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane.
 We include galaxies from the AMAZE sample (G11) with the grey and clear symbols (this symbol choice and the other comparison samples are described in more detail throughout \cref{subsubsec:comparison_samples}).
@@
 We follow the bootstrapping procedure described in \cref{subsubsec:comparison_samples} to compute isolated field sample error weighted averages and statistical errors.
-The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015} and the mean and median $V_{C}$ values are $78.8^{+5.4}_{-5.1}kms^{-1}$ $60.0^{+7.5}_{-5.9}kms^{-1}$, which is less than at lower redshift.
+The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015} and the mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ $57.0^{+6.6}_{-6.3}kms^{-1}$, which is less than at lower redshift.
 These results are placed in the context of previous work throughout \cref{subsec:TF} and \cref{subsec:redshift_evolution}, where we also discuss possible explanations for the increase in $\sigma_{int}$ with redshift.\\
 
-In Figure \ref{fig:v_sig_and_v} (b) we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean sample for reference.
+In the right panel figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean sample for reference.
 In the local universe, disky, SFGs are observed to have $V_{C}/\sigma_{int}$ values in excess of 10 (i.e.
@@
 
-As discussed in \cref{subsec:morpho-kin-class}, the isolated field sample Rotation Dominated Fraction (RDF) is xxx, which is substantially lower than in the local and intermediate redshift universe as a result of the increased velocity dispersions.
+As discussed in \cref{subsec:morpho-kin-class}, the isolated field sample Rotation Dominated Fraction (RDF) is 0.37$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe, as a result of the increased velocity dispersions.
 This value is in good agreement with the result of G11, however we note that their result of $RDF \sim 0.33$ could be higher if any of the galaxies which were not passed through their dynamical model were rotation dominated.
@@
 
-We proceed now to investigate the connection between rotation velocity and stellar mass for the rotation and dispersion dominated KDS field galaxies as an attempt to understand physical differences between these populations at different cosmic times (i.e.
+We proceed now to investigate the connection between rotation velocity and stellar mass for the rotation and dispersion dominated KDS field galaxies as an attempt to understand the physical differences between galaxies falling into these categories at different cosmic times (i.e.
 do rotation dominated galaxies change in physical properties between different redshift slices).
@@
 $M_{\star}$, i.e.
-the inverted stellar mass Tully-Fisher relation for the isolated field sample with $V_{C}/\sigma_{int} > 1$ in red and the galaxies with $V_{C}/\sigma_{int} < 1$ with clear symbols.
-    Also plotted with the solid green is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex error on the fit.
+the inverted stellar mass Tully-Fisher relation, for the isolated field sample, plotting rotation domianted galaxies in red and dispersion dominated galaxies with with clear symbols.
+    Also plotted with the solid green line is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex error on the fit.
     This $z\sim0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in Reyes 2011.
-    The $V_{C}/\sigma_{int} > 1$ KDS galaxies also show no evolution from this relation within the errorbars, with the $V_{C}/\sigma_{int} < 1$ galaxies scattering below the relation.
-    This highlights the need for careful sample selection when constructing this relation, and explains the low KDS mean $V_{C}$ value as a consequence of averaging over a sample with a high fraction of dispersion dominated galaxies.
+    The rotation dominated KDS galaxies also show no evolution from this relation within the errorbars, with the dispersion dominated galaxies scattering below the relation.
+    This highlights the need for careful sample selection when constructing this relation and explains the low KDS mean $V_{C}$ value as a consequence of averaging over a sample with a high fraction of dispersion dominated galaxies.
     In the right panel we plot the $S_{0.5}$ vs.
@@
 Observing the smTFR at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies.
-In principle, studying whether the smTFR evolves with redshift gives us information about how galaxies accumulate their stellar mass and rotational velocities, with offsets from the local relation towards lower $M_{\star}$ values at fixed rotational velocity suggesting that the dynamical mass is in place, but the stellar mass is yet to be formed.
-\\
-
-The main question arising from observations in support of and against evolution of the smTFR with redshift is: Do galaxies evolve along a smTFR which is fixed with redshift (i.e.
-increasing in $V_{C}$ as $M_{\star}$ increases) or is there a shift in the zero-point and/or slope with redshift (i.e.
-as $M_{\star}$ accumulates, $V_{C}$ remains fixed).
+In principle, studying whether the smTFR evolves with redshift gives us information about how galaxies accumulate their stellar mass and rotation velocities, with offsets from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggesting that the dynamical mass is in place, but the stellar mass is yet to be formed.
+\\
+
+The main question arising from observations in support of and against evolution of the smTFR with redshift is: Do galaxies evolve along a smTFR which is fixed or is there a shift in the zero-point and/or slope with decreasing redshift (i.e.
+is the connection between $V_{C}$ and the accumulating $M_{\star}$ fixed at all times)?
 Essentially we'd like to know how an individual, unperturbed point, representing a typical rotation-dominated SFG allowed to evolve without mergers, would move around the $V_{C}$ vs.
 $M_{\star}$ plane over 12Gyr of purely secular evolution.
-Connected to this also is the idea of progenitor bias, in that the SFGs we are selecting and comparing between $z\sim0-3.5$ may not form an evolutionary cohort, and certainly there is much evidence for the quenching of SF at a particular mass scale \citep[e.g.][]{Keres2005,Dekel2006,Peng2010}, leading to morphological and dynamical transformation.
+Connected to this also is the idea of progenitor bias, in that the SFGs we are selecting and comparing between $z\sim0-3.5$ may not form an evolutionary cohort, with the quenching of SF accuring at a particular mass scale \citep[e.g.][]{Keres2005,Dekel2006,Peng2010}, leading to morphological and dynamical transformation.
 \\
@@
 The smTFR has been studied numerous times between $0.5 < z < 2$, giving results consistent with zero evolution of the slope and zero-point \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Harrison2017}.
-Others have reported that as redshift increases, the smTFR shifts towards lower masses at fixed rotational velocity, e.g.
-in \cite{Puech2008,Puech2010} where a -0.34 dex log$(M_{\star})$ offset is observed at $z\sim0.6$, in the \cite{Tiley2016a} KROSS sample at $z\sim0.9$ with a -0.41 dex shift (although in this work a stricter cut than in H17 of $V_{C}/\sigma_{int} > 3$ is applied), in \cite{Cresci2009} a -0.41 dex offset is observed at $z\sim2$ (although the galaxies used to compute this were the highest fidelity rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5)$ and in G11 an offset of -1.29 dex is claimed, although there is large degree of scatter between the individual galaxies, with 50\% of the sample consistent with the $z\sim0$ relation.
+Others have reported that as redshift increases, the smTFR shifts towards lower masses at fixed rotation velocity, for example in \cite{Puech2008,Puech2010} where a -0.34 dex log$(M_{\star})$ offset is observed at $z\sim0.6$, in the \cite{Tiley2016a} KROSS sample at $z\sim0.9$ with a -0.41 dex shift (although in this work a stricter cut than in H17 of $V_{C}/\sigma_{int} > 3$ is applied), in \cite{Cresci2009} a -0.41 dex offset is observed at $z\sim2$ (although the galaxies used to compute this were the highest fidelity rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5)$ and in G11 an offset of -1.29 dex is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample consistent with the $z\sim0$ relation.
 \\
@@
 We plot this best fit relation with the solid green line, with the green shaded region giving the typical uncertainty on the fit of 0.2 dex along the velocity axis.
-These parameters are consistent with the values $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, measured in \cite{Reyes2011} for a sample of $z<0.1$ disks traced with H$\alpha$, in a similar mass range and where $V_{C}$ has been extracted at the same radius, and we plot this as the dashed black line in the left panel of figure \ref{fig:tf_relation}.
-The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$, where the galaxies span a similar $M_{\star}$ range and the $V_{C}$ values have been computed following a consistent methodology, suggests that there is no evolution in the smTFR between these limits.
-\\
-
-The rotation dominated KDS galaxies with $V_{C}/\sigma_{int} > 1$ and $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ are broadly consistent within the errorbars with the H17 fit, showing a tendency to lie below the relation.
+These parameters are consistent with coefficients measured in the local universe $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, from \cite{Reyes2011}, in which the dynamics of a sample of $z<0.1$ disks in a similar mass range to KROSS are traced with H$\alpha$ emission.
+In this study $V_{C}$ has been extracted at the same radius and we plot this local relation as the dashed black line in the left panel of figure \ref{fig:tf_relation}.
+The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$suggests that there is no evolution in the smTFR between these limits. \\
+
+The rotation dominated KDS galaxies are broadly consistent within the errorbars with the H17 fit, showing a tendency to lie below the relation.
 The dispersion dominated KDS galaxies sit clearly separated and below the H17 relation but with a consistent slope, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in H17 and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We do not attempt to fit through our data, due to the relatively narrow mass range spanned by the points, and conclude that there does not appear to be evolution in the zero-point of the smTFR between $z\sim1-3.5$ for rotation-dominated galaxies as traced by KROSS and KDS.
-\\
-
-This result is a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotational velocity is observed as a result of omitting rotationally dominated galaxies with lower $V_{C}$ values (as is also the case in \cite{Cresci2009} with the high fidelity disk sample).
+We do not attempt to fit through our data, due to the relatively narrow mass range spanned by the points and conclude that there does not appear to be evolution in the zero-point of the smTFR between $z\sim1-3.5$ for rotation-dominated galaxies as traced by KROSS and KDS.
+\\
+
+This result is a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed as a result of omitting rotationally dominated galaxies with lower $V_{C}$ values (as is also the case in \cite{Cresci2009} with the high fidelity disk sample).
 Conversely, fitting the smTFR through a full sample including dispersion dominated galaxies would shift the zero-point in the opposite sense.
-The conclusion from this work is that the smTFR appears to show no evolution across the bulk of cosmic time when the measurement of dynamical properties and selection of rotation dominated galaxies are consistent.
+The conclusion from this work is that the smTFR appears to show no evolution across the bulk of cosmic history when the measurement of dynamical properties and the selection of rotation dominated galaxies are performed consistently.
 This comes with the caveat that it is not clear whether main sequence SFGs at difference redshift slices can be considered to form an evolutionary sequence. \\
@@
 $M_{\star}$.
-This is connected to the idea suggested in figure \ref{fig:dyn_masses}, that the rotational velocities alone may not be a good tracer of the total dynamical mass, with $S_{0.5}$ accounting for the contribution to the dynamical mass from non-circular motions.
-In K07, using $S_{0.5}$ reduced the scatter in the TFR out to $z\sim1.2$, which they attribute to the inclusion of galaxies with peculiar kinematics in the sample with reduced rotational velocities in relation to their stellar mass.
+This is connected to the idea that the rotation velocities alone may not be a good tracer of the total dynamical mass, with $S_{0.5}$ accounting for the contribution to the dynamical mass from non-circular motions.
+In K07, using $S_{0.5}$ reduced the scatter in the TFR out to $z\sim1.2$, which they attribute to the inclusion of galaxies with peculiar kinematics in the sample with reduced rotation velocities in relation to their stellar mass.
 $S_{0.5}$ has been studied in both C09 and G11, with both reporting an evolution of the K07 trend towards lower $M_{\star}$ at fixed $S_{0.5}$, which is taken as further evidence for the evolution of the smTFR.
 In the right panel of figure \ref{fig:tf_relation} the KDS galaxies agree with the K07 relation within the errorbars, with reduced scatter in comparison to the smTFR in the left panel, suggesting that there is no evolution in $S_{0.5}-M_{\star}$ relation.
-The symbol convention is the same as in the left panel, and the division now between the rotation and dispersion dominated galaxies is no longer clear. 
-Considering the increase in observed $\sigma_{int}$ values over cosmic time (figure \ref{fig:sigma_and_v_sigma_w_redshift}), this suggests that there is an interplay between the $V_{C}$ values and $\sigma_{int}$ traced by ionised gas emission lines as discussed in \cite{Kassin2012}.
+The symbol convention is the same as in the left panel and the division now between the rotation and dispersion dominated galaxies is no longer clear. 
+Considering the increase in observed $\sigma_{int}$ values over cosmic time (discussed in \cref{subsec:redshift_evolution}), this suggests that there is an interplay between the $V_{C}$ values and $\sigma_{int}$ traced by ionised gas emission lines as discussed in \cite{Kassin2012}.
 We caution against over-interpretation of this result, since the origin of $\sigma_{int}$ and the extent to which this quantity traces dynamical mass is unclear, however this trend adds to the evidence that $V_{C}$ alone is an insufficient tracer of the total dynamical mass at this redshift.
@@
 The smTFR derives directly from the virial theorem, in which changes to the dynamical mass are driven by changes in both the sizes and velocities of galaxies, prompting authors recently \citep[e.g.][]{Cortese2016,Contini2015a,Burkert2016a,Harrison2017,Swinbank2017} to study the connection between $M_{\star}$ and specific angular momentum, $j_{s} \propto R_{1/2}V_{C}$, with this possibly a more fundamental quantity to describe galaxy evolution.
-We briefly discuss the specific angular momentum of the KDS galaxies in \cref{subsec:ang_mom}, continuing now to study the virial masses of the isolated field sample computed from their derived rotational velocities.
+We briefly discuss the specific angular momentum of the KDS galaxies in \cref{subsec:ang_mom}, continuing now to study the virial masses of the isolated field sample computed from their derived rotation velocities.
 
@@
 \includegraphics[width=0.49\textwidth]{rv_squared.png}
-\caption{We plot the ratio $M_{vir}/M_{\star}$ computed using only rotational velocities (Eq.
+\caption{We plot the ratio $M_{vir}/M_{\star}$ computed using only rotation velocities (Eq.
 13) for the isolated field sample vs.
@@
 It is expected that $M_{vir} > M_{\star}$, as the dynamics trace not only the stellar mass, but also the gas mass and dark matter mass within the radius at which $M_{vir}$ is evaluated.
-At $z \sim 3.5$ the gas reservoirs are on average a much larger fraction of the total galaxy mass than in the local universe \citep[e.g.][]{Tacconi2013,Saintonge2013,Wisnioski2015} as there has not yet been time to convert this gas mass into stellar mass, and so in principle if ordered rotation is tracing the total mass in these systems, $M_{\star}$ should be clearly below $M_{vir}$.
+At $z \sim 3.5$ the gas reservoirs are on average a much larger fraction of the total galaxy mass than in the local universe \citep[e.g.][]{Tacconi2013,Saintonge2013,Wisnioski2015} as there has not yet been time to convert this gas mass into stellar mass and so in principle if ordered rotation is tracing the total mass in these systems, $M_{\star}$ should be clearly below $M_{vir}$.
 In figure \ref{fig:dyn_masses}, where we have computed the virial mass from the ordered rotational motions alone, as traced by $V_{C}$, following equation \ref{eq:dyn_mass_v_only}, we find that this is not the case for the isolated field sample, with $M_{vir} < M_{\star}$ for the vast majority of galaxies (particularly those with $M_{\star} > 9.5$).
@@
 
-This strongly suggests that rotational motions alone are not enough to provide gravitational support for the mass in the system, and random motions contribute to provide gravitational support for some fraction of the total mass contained within these compact galaxies.
+This strongly suggests that rotational motions alone are not enough to provide gravitational support for the mass in the system and random motions contribute to provide gravitational support for some fraction of the total mass contained within these compact galaxies.
 To follow this idea we can compute the contribution to $M_{vir}$ from $\sigma_{int}$ using equation \ref{eq:dyn_mass_sigma} \citep[e.g.][]{Cappellari2006}.
@@
 In figure \ref{fig:ang_mom} we plot the specific angular momentum, j$_{\star} \equiv J/M_{\star}$ where J is the total angular momentum \citep{Fall1983}, as a function of stellar mass M$_{\star}$.
-This quantity has been described in detail in \cite{Harrison2017} section 4.3 and refer to this for more details about the use of $j_{s}$ as measured from ionised gas kinematics as a tracer of the specific angular momentum content of SFGs.
+This quantity has been described in detail in \cite{Harrison2017} section 4.3 and we refer to this for more details about the use of $j_{s}$ as measured from ionised gas kinematics as a tracer of the specific angular momentum content of SFGs.
 
@@
 However we have verified throughout \cref{subsubsec:galfitting} that the GOODS-S galaxies are well described by the n = 1 exponential profile through a combination of GALFIT and comparison to the \Sers index values reported in \cite{VanderWel2012}.
-Setting n = 1 in equation \ref{eq:kn} leaves $k_{n} = 1.19$ and we continue under this assumption analogous to in \cite{Harrison2017} (although we note that as stated in \cite{Harrison2017} setting n = 2 results in only a $\sim20\%$ difference in the derived $j_{s}$ values).
+Setting n = 1 in equation \ref{eq:kn} leaves $k_{n} = 1.19$ and we continue under this assumption analogous to in \cite{Harrison2017} (although we note that as stated in \cite{Harrison2017} setting n = 2 results in $\sim20\%$ difference in the derived $j_{s}$ values).
 In equation \ref{eq:ang_mom} $C_{i}$ is the de-projection factor, assumed to be $1/sin(i)$, and $v_{s}$ is the observed velocity at $2R_{1/2}$.
-The combination $v_{s}C_{i} \equiv V_{C}$ and we can use our measured rotation velocities to leave equation \ref{eq:ang_mom_final} as the final expression for $j_{s}$ used to calculate the values in figure \ref{fig:ang_mom}.
+The combination $v_{s}C_{i} \equiv V_{C}$ and we can use our measured rotation velocities to leave equation \ref{eq:ang_mom_final} as the final expression for $j_{s}$.
 
@@
 The dispersion dominated KDS galaxies form a sequence with similar slope but offset to lower still $j_{s}$ values.
-We plot also the $\sim j_{s} \propto (1+z)^{-1}$ reported in \cite{Swinbank2017} (using the local slope and normalisation from \cite{Romanowsky2012}), which the rotation dominated KDS galaxies appear to roughly follow.
+We plot also the $j_{s} \propto (1+z)^{-1}$ evolution line reported in \cite{Swinbank2017} (using the local slope and normalisation from \cite{Romanowsky2012}), which the rotation dominated KDS galaxies appear to roughly follow.
 \\
@@
 \subsection{The redshift evolution of dynamical properties}\label{subsec:redshift_evolution}
-We proceed to investigate further the low rotational velocities and large velocity dispersions observed in the isolated field sample in \cref{subsec:rdf_v_over_sigma} by placing them in cosmological perspective using the comparison samples (see \cref{subsubsec:comparison_samples} for overview and symbol definitions).
+We proceed to investigate further the low rotation velocities and large velocity dispersions observed in the isolated field sample in \cref{subsec:rdf_v_over_sigma} by placing them in cosmological perspective using the comparison samples (see \cref{subsubsec:comparison_samples} for overview and symbol definitions).
 We have made use of the tabulated data and errors in these studies to derive the datapoint values and errorbars plotted in figure \ref{fig:rdf_and_v_sigma_w_redshift} and \ref{fig:sigma_and_v_sigma_w_redshift} in a consistent way, which is to take the fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples (i.e.
@@
 In the right panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the RDF.
-These are shown with the thin grey shaded regions, and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the invidual points.
-In a recent work by \cite[R16]{Rodrigues2016}, a subset of the KMOS$^{3D}$ $z \sim 1$ sample has been re-analysed and a lower RDF of 69\% was recovered, despite the use of identical classification criteria.
-The recovery of this lower fraction is driven mainly by the presence of peaks in the $\sigma_{int}$ maps which do not coincide with the rotation centre, a criteria which we do not impose throughout this work, and spatial offsets between the rotation centre and the centre of stellar mass.
+These are shown with the thin grey shaded regions and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the invidual points.
+In the KMOS$^{3D}$ $z \sim 1$ sample re-analysis presented in \cite{Rodrigues2016}, a lower RDF of 69\% was recovered, despite the use of identical classification criteria.
+The recovery of this lower fraction is driven mainly by the presence of peaks in the $\sigma_{int}$ maps which do not coincide with the rotation centre, a criteria which we do not impose throughout this work and spatial offsets between the rotation centre and the centre of stellar mass.
 The KROSS $z\sim1$ RDF presented in H17 lies between the two extremes of R16 and W15 computed for the KMOS$^{3D}$ sample. \\
@@
 Despite the systematic variations in measurement technique and classification criteria between the comparison samples, it is clear that the RDF, as traced simply by the $V_{C}/\sigma_{int}$ inferred from ionised gas emission lines, drops from $\sim 100\%$ of galaxies in the local universe to $\sim 2/3$ of galaxies in the $z \sim 1-2$ universe and to $\sim 1/3$ above $z \sim 3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
-This is highlighted in figure \ref{fig:rdf_and_v_sigma_w_redshift} (b) by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic RDF decline as described in \cite{Stott2016}.
+This is highlighted in the right panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic RDF decline as described in \cite{Stott2016}.
 Scatter above and below the RDF $\propto z^{-0.2}$ evolution line may be attributed in part to the different mean stellar masses of the surveys, with those that have larger stellar masses tending to scatter above this line.
@@
 The observation that $\sigma_{int}$ becomes increasingly large towards high redshift has now been firmly established in several studies, including all of those from which data has been taken to create figure \ref{fig:sigma_and_v_sigma_w_redshift}.
-To complement the surveys already described throughout \cref{subsubsec:RDF_evolution}, we add data from \cite{Law2009} to explore the evolution of $\sigma_{int}$ values across cosmic time.
-We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
-These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the beam-smearing is much smaller.
 \cite{Law2009} attribute the cosmic increase in $\sigma_{int}$ to much larger gas fractions at high redshift, with the gas accumulated through rapid cold-mode accretion along cosmic filaments.
@@
 The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
-In particular the $V_{C}$ parameter reported in G11 is unconstrained for several galaxies, requires large extrapolation from the data and leads to very large rotational velocities for 5/11 of their galaxies.
+In particular the $V_{C}$ parameter reported in G11 is unconstrained for several galaxies, requires large extrapolation from the data and leads to very large rotation velocities for 5/11 of their galaxies.
 The remaining 6/11 galaxies have $V_{C}$ values close to those reported for the KDS sample.
@@
 This could either be a result of the measurement and modelling technique, which carries significant uncertainties due to modelling assumptions, the S/N of the [O~{\sc III}]$\lambda5007$ emission line even in very long integrations at this redshift, the spatial coverage of [O~{\sc III}]$\lambda5007$ may be more compact that $H\alpha$ and consequently may not probe out to the same galactic radii and the sparsity of resolution elements, or could be the result or some real physical process in the galaxies which lowers $V_{C}$ as traced by the ionised gas dynamics.
-We believe however that the observation of a low mean $V_{C}$ value in the KDS galaxies is primarily exlainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
-This is easier to see in \cref{subsec:TF} where we revisit the rotation velocities in the context of the inverted stellar mass `Tully-Fisher Relation' \citep[smTFR;][]{Tully1977,Bell2000a}. \\
+We believe however that the observation of a low mean $V_{C}$ value in the KDS galaxies is primarily explainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
+This is easier to see in \cref{subsec:TF} where we have cast the rotation velocities in the context of the inverted stellar mass `Tully-Fisher Relation' \citep[smTFR;][]{Tully1977,Bell2000a}. \\
 
@@
 At this redshift and mean $M_{\star}$, the disk assumption may not be correct, as galaxies could have more complicated structures which have not yet stabilised into rotating disks.
-However the distribution of inclination angles is consistent with observing a selection of galaxies with inclinations randomly distributed as $0^{\circ} < i < 90^{\circ}$, with the KDS mean inclination of $57.4^{\circ}$ (see \cref{subsubsection:inclination_angle}) agreeing well with the theoretical mean of $57.3^{\circ}$ (for a simple derivation of this value see e.g.
-the appendix in \cite{Law2009}).
+However the distribution of inclination angles is consistent with observing a selection of galaxies with inclinations randomly distributed as $0^{\circ} < i < 90^{\circ}$, with the KDS mean inclination of $57.4^{\circ}$ (see \cref{subsubsection:inclination_angle}) agreeing well with the theoretical mean of $57.3^{\circ}$ \citep[for a simple derivation of this value see e.g.
+the appendix in][]{Law2009}.
 \\
@@
 
-\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Kinematics Plots}\label{app:kinematics_plots}
-\subsection{Rotation Dominated ($V_{C}/\sigma_{int} > 1$)}\label{app:rotation_dominated}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs006516_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs008543_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs016759_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_20_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_32_grid_paper.png}
-\label{fig:goods_rot_1}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_38_grid_paper.png}
-\label{fig:goods_rot_2}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_91_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs009818_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_b012141_012208_grid_paper.png}
-\label{fig:goods_rot_3}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22a-d3_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_ROTATION/combine_sci_reconstructed_n3_009_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-c20_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-d5_grid_paper.png}
-\label{fig:SSA_rot_1}
-\end{figure*}
-
-\subsection{Dispersion Dominated ($V_{C}/\sigma_{int} < 1$)}\label{app:dispersion_dominated}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_bs006541_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_b15573_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_24_grid_paper.png}
-\label{fig:goods_disp_1}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_bs014828_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_25_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_94_grid_paper.png}
-\label{fig:goods_disp_2}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_105_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_109_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_111_grid_paper.png}
-\label{fig:goods_disp_3}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_113_grid_paper.png}
-\label{fig:goods_disp_4}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_s_sa22b-md25_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_n3_006_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_lab25_grid_paper.png}
-\label{fig:SSA_disp_2}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_lab18_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_s_sa22b-d9_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_n_c3_grid_paper.png}
-\label{fig:SSA_disp_1}
-\end{figure*}
-
-\subsection{Mergers}\label{app:mergers}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22b-c10_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-md23_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-md46_grid_paper.png}
-\caption{ssa mergers}
-\label{app:ssa_mergers_1}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-m38_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c35_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c30_grid_paper.png}
-\caption{ssa mergers}
-\label{app:ssa_mergers_2}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-aug96m16_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c49_grid_paper.png}
-\includegraphics[width=\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c47_grid_paper.png}
-\caption{ssa mergers}
-\label{app:ssa_mergers_3}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_14_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_23_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_bs010545_grid_paper.png}
-\includegraphics[width=\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_93_grid_paper.png}
-\caption{High-resolution imaging is important not only for reliably recovering the morphological parameters, but also to explain peculiar features in the observed velocity and velocity dispersion fields.
-In the two examples above, multiple components in the HST imaging clearly correspond to marginally different [O~{\sc III}]$\lambda$5007 emission wavelengths, which manifest as velocity shifts in individual spaxels and broadens the observed dispersion pattern where the emission lines at different wavelengths merge.
-Overplotted onto the models are the data values and uncertainties extracted along $PA_{kin}$.
-These figures also show the HST imaging for each galaxy, the best fit galfit model and residuals, 2D maps of the [O~{\sc III}]$\lambda$5007 flux, observed velocity, observed dispersion, best fitting smeared model velocity, data - model residuals, intrinsic velocity dispersion (observed dispersion corrected for beam-smearing and instrumental resolution as described in \cref{subsubsec:param_extraction}) as well as a plot of 1D extractions along the observed, intrinsic and beam smeared dispersion maps.}
-\label{app:goods_mergers_1}
-\end{figure*}
-
-\section{Table of measurements from different surveys}
 \begin{table*}
 \centering
-\caption{We present here a reference of the mean and median kinematic properties used throughout figures 7 and 8 for the different surveys.
+\begin{threeparttable}
+\caption{We present here a reference of the mean and median kinematic properties used throughout figures \protect\ref{fig:rdf_and_v_sigma_w_redshift} and \protect\ref{fig:sigma_and_v_sigma_w_redshift} for the different surveys.
 The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
@@
 \end{tabular}
+  \end{threeparttable}
   \end{table*}
 
+\appendix
+
+\section{Kinematics Plots}\label{app:kinematics_plots}
+In figures \ref{fig:rotation_dominated_galaxies}, \ref{fig:dispersion_dominated_galaxies} and \ref{fig:merger_galaxies} we plot the kinematic grids for the KDS galaxies classified as rotation dominated, dispersion dominated and merger candidates respectively.
+The figure captions provide more information on each of the panels of these grids.
+
+\begin{figure*}
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs006516_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs008543_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs016759_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_20_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_38_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_32_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_91_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs009818_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_b012141_012208_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22a-d3_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_n3_009_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-c20_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+\centering
+
+    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-d5_grid_paper.png}
+
+\caption{We plot here the kinematic grids for the 13 isolated field sample galaxies classified as rotation dominated.
+For each galaxy we plot the HST image, GALFIT model and GALFIT residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
+On the bottom row we plot the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
+Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
+The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
+The purple symbols represent the extraction along $PA_{kin}$ from the residual map, and the two vertical dashed lines denote the intrinsic (inner) and convolved (outer) $2R_{1/2}$ values, with $V_{C}$ extracted at the convolved value.
+The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
+The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per equation \protect\ref{eq:dispersion_comp}, and the vertical dashed lines have the same meaning as for the velocity extraction plot.
+Also plotted with the blue and red dot-dash horizontal lines are the median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.}
+\label{fig:rotation_dominated_galaxies}
+
+\end{figure*}
+
+\begin{figure*}
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_bs006541_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_b15573_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_24_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_bs014828_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+\centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_25_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_94_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_105_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_109_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_111_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_s_sa22b-md25_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_n3_006_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_lab25_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_113_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_lab18_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_s_sa22b-d9_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_DISPERSION/combine_sci_reconstructed_n_c3_grid_paper.png}
+
+    \caption{The same as in figure \protect\ref{fig:rotation_dominated_galaxies} but for the dispersion dominated galaxies.}
+    \label{fig:dispersion_dominated_galaxies}
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22b-c10_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-md23_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-md46_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-m38_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c35_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c30_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-aug96m16_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c49_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_14_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_23_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_bs010545_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c47_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_93_grid_paper.png}
+
+    \caption{The same as for figure \protect\ref{fig:rotation_dominated_galaxies} but for the merger candidates.
+    In this case we plot only fits to the data in the velocity extraction plot with the blue line, rather than attempting the full beam-smearing analysis.
+    Several of the galaxies here mimic rotation from a purely kinematic perspective, but have two or more HST components and an accompanying double peak in the object spectrum at the object centre, leading to large velocity dispersions when single gaussian fits are attempted.}
+    \label{fig:merger_galaxies}
+\end{figure*}
+
 \section{Kinematic Parameters Error Estimates}\label{app:kin_error_estimates}
@@
 \subsection{3D modelling kinematic parameter error estimates}\label{appsubsec:model_errors}
-As mentioned above, the MCMC sampling provides distributions for each of the model parameters, from which we can extract the 84th and 16th percentile values as the +/- 1-$\sigma$ errors.
+As mentioned in \cref{subsec:3d_modelling}, the MCMC sampling provides distributions for each of the model parameters, from which we can extract the 84th and 16th percentile values as the +/- 1-$\sigma$ errors.
 During the following procedure $PA_{kin}$ is fixed to the maximum likelihood value for all model evaluations.
-We also fold in the uncertainty on measuring the inclination angle at this point, assuming a conservative GALFIT measurement error of $\Delta$i = 10$\%$ following the analysis of EXAMPLE. 
-The beam smeared and intrinsic models are reconstructed using the 16th and 84th percentile parameters, with the lower velocity 16th percentile model using the inclination value closer to edge-on, and the 84th percentile model using the inclination closer to face-on.
-To clearly distinguish the 1-$\sigma$ error regions for both the beam smeared and intrinsic model the region between the 16th and 84th percentile evaluations are shaded blue and red respectively in the figures shown in Appendix A.
-The +/- 1-$\sigma$ error values for both $v_{2.2}$ and $v_{3.0}$ are then calculated using the the equations below, also taking account the measurement errors with $\bar{\sigma}_{v_{obs}}$ equal to the average observational uncertainty extracted along $PA_{kin}$.
+We proceed to reconstruct the beam smeared and intrinsic dynamical models for each of the isolated field galaxies using the 16th and 84th percentile parameters, with the lower velocity 16th percentile model constructed using the upper limit on the inclination, and the 84th percentile model using the lower limit.
+To clearly distinguish the 1-$\sigma$ error regions for both the beam smeared and intrinsic model the region between the 16th and 84th percentile evaluations are shaded blue and red respectively in the figures shown in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies}.
+The +/- 1-$\sigma$ error values for both $V_{C}$ are then calculated using the the equations below, which also take into account the measurement errors with $\bar{\sigma}_{v_{obs}}$ equal to the average observational uncertainty extracted along $PA_{kin}$.
 The subscripts `16th' and `84th' denote the model from which the velocity has been extracted.
 
-\begin{equation}\label{eq:v2.2_plus}
-   \delta v_{2.2}+ = \sqrt{(v_{2.2_{84}} - v_{2.2})^{2} + (\bar{\delta}v_{obs})^{2}}
-\end{equation}
-
-\begin{equation}\label{eq:v2.2_minus}
-   \delta v_{2.2}- = \sqrt{(v_{2.2} - v_{2.2_{16}})^{2}  + (\bar{\delta}v_{obs})^{2}}
-\end{equation}
-
-\begin{equation}\label{eq:v3.0_plus}
-   \delta v_{3.0}+ = \sqrt{(v_{3.0_{84}} - v_{3.0})^{2} + (\bar{\delta}v_{obs})^{2}}
-\end{equation}
-
-\begin{equation}\label{eq:v3.0_minus}
-   \delta v_{3.0}- = \sqrt{(v_{3.0} - v_{3.0_{16}})^{2}  + (\bar{\delta}v_{obs})^{2}}
-\end{equation}
-
-The upper and lower errors on the mean velocity dispersion are calculated in a similar fashion.
-To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40kms^{-1}$ and $\sigma_{int} = 80kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values.
-When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with other lines that have a shifted velocity centre is less severe.
+\begin{equation}\label{eq:VC_plus}
+   \delta V_{C}+ = \sqrt{\left(V_{C-84} - V_{C}\right)^{2} + \left(\bar{\delta}V_{obs}\right)^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:VC_minus}
+   \delta V_{C}- = \sqrt{\left(V_{C} - V_{C-16}\right)^{2}  + \left(\bar{\delta}V_{obs}\right)^{2}}
+\end{equation}
+
+The upper and lower errors on the $\sigma_{int}$ are calculated using a similar approach.
+To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40kms^{-1}$ and $\sigma_{int} = 80kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
+figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.
 Conversely, assuming $\sigma_{int} = 40km^{-1}$ increases the beam-smearing.
-We calculate the minimum and maxmimum intrinsic velocity dispersion, $\sigma_{o-84-40}$ and $\sigma_{o-16-80}$, using equations \ref{eq:sig_84_40} and \ref{eq:sig_16_80} respectively:
+We calculate the minimum and maxmimum intrinsic velocity dispersion, $\sigma_{int-84-40}$ and $\sigma_{int-16-80}$, using equations \ref{eq:sig_84_40} and \ref{eq:sig_16_80} respectively:
 
 \begin{equation}\label{eq:sig_84_40}
-   \sigma_{o-84-40} = \sqrt{(\sigma_{obs} - \sigma_{bs-84-40})^{2} - \sigma_{sky}^{2}}
+   \sigma_{int-84-40} = \sqrt{(\sigma_{obs} - \sigma_{bs-84-40})^{2} - \sigma_{sky}^{2}}
 \end{equation}
@@
 \begin{equation}\label{eq:sig_16_80}
-   \sigma_{o-16-80} = \sqrt{(\sigma_{obs} - \sigma_{bs-16-80})^{2} - \sigma_{sky}^{2}}
-\end{equation}
-
-and then the lower and upper errors on $\sigma_{o}$ are given by the following:
+   \sigma_{int-16-80} = \sqrt{\left(\sigma_{obs} - \sigma_{bs-16-80}\right)^{2} - \sigma_{sky}^{2}}
+\end{equation}
+
+where $\sigma_{bs-84-40} = \sigma_{model-84-40} - 40$ and $\sigma_{bs-16-80} = \sigma_{model16-80} - 80$ are the beam smeared maps.
+The lower and upper errors on $\sigma_{int}$ are then given by the following:
 
 \begin{equation}\label{eq:sig_plus_error}
-   \delta\sigma_{o}+ = \sqrt{(\sigma_{o} - \sigma_{o-84-40})^{2} + (\bar{\sigma}_{\sigma_{obs}})^{2}}
+   \delta\sigma_{int}+ = \sqrt{\left(\sigma_{int} - \sigma_{int-84-40}\right)^{2} + \left(\bar{\sigma}_{\sigma_{obs}}\right)^{2}}
 \end{equation}
@@
 \begin{equation}\label{eq:sig_minus_error}
-   \delta\sigma_{o}- = \sqrt{(\sigma_{o-16-80} - \sigma_{o})^{2} + (\bar{\sigma}_{\sigma_{obs}})^{2}}
+   \delta\sigma_{int}- = \sqrt{\left(\sigma_{int-16-80} - \sigma_{int}\right)^{2} + \left(\bar{\sigma}_{\sigma_{obs}}\right)^{2}}
 \end{equation}
@@
 with $\bar{\sigma}_{\sigma_{obs}}$ equal to the average of the velocity dispersion measurement errors.
-Once these quantities have been measured, the upper and lower errors on the ratio $\frac{v_{2.2}}{\sigma{o}}$ can be computed using equations \ref{eq:v_over_sig_plus} and \ref{eq:v_over_sig_minus}, and the same prescription is followed to find the errors on $\frac{v_{3.0}}{\sigma{o}}$.
+Once these quantities have been measured, the upper and lower errors on the ratio $\frac{v_{2.2}}{\sigma{o}}$ can be computed using equations \ref{eq:v_over_sig_plus} and \ref{eq:v_over_sig_minus}, and the same prescription is followed to find the errors on $\frac{V_{C}}{\sigma{int}}$.
 
 \begin{equation}\label{eq:v_over_sig_plus}
-   \delta\frac{v_{2.2}}{\sigma_{o}}+ = \frac{v_{2.2}}{\sigma_{o}}\sqrt{\left(\frac{\delta v_{2.2}+}{v_{2.2}}\right)^{2} + \left(\frac{\delta\sigma_{o}+}{\sigma_{o}}\right)^{2}}
+   \delta\frac{V_{C}}{\sigma_{int}}+ = \frac{V_{C}}{\sigma_{int}}\sqrt{\left(\frac{\delta V_{C}+}{V_{C}}\right)^{2} + \left(\frac{\delta\sigma_{int}+}{\sigma_{int}}\right)^{2}}
 \end{equation}
@@
 \begin{equation}\label{eq:v_over_sig_minus}
-   \delta\frac{v_{2.2}}{\sigma_{o}}- = \frac{v_{2.2}}{\sigma_{o}}\sqrt{\left(\frac{\delta v_{2.2}-}{v_{2.2}}\right)^{2} + \left(\frac{\delta\sigma_{o}+-}{\sigma_{o}}\right)^{2}}
+   \delta\frac{V_{C}}{\sigma_{int}}- = \frac{V_{C}}{\sigma_{int}}\sqrt{\left(\frac{\delta V_{C}-}{V_{C}}\right)^{2} + \left(\frac{\delta\sigma_{int}+-}{\sigma_{int}}\right)^{2}}
 \end{equation}

### 2017-02-21 paper.tex
Final draft before sending to co-authors
21st February - after draft circulation, comments from Chris and David

@@
 % Keep the title short and informative.
-\title[KDS: dynamical properties of 77 z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
-Programme IDs: }}
+\title[KDS: dynamical properties of 77 z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of typical star forming galaxies at $z\sim3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
+Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)}}
 
@@
 \author[O.J. Turner et al.]{
-O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
+O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk}}$
 \\
@@
 
-In the hierarchical collapse scenario \citep{Rees1977,Fall1980}, matter density perturbations, which originate from some set of cosmological initial conditions, grow over time before condensing out of the general expansion to form dark matter halos \cite{Silk1968,Peebles1970}.
-It is at the centre of these halos that baryons collect, cool and begin to form stars (\cite{Birnboim2003,Keres2005,Dekel2006} and see e.g.
-\cite{Mo2010} for a recent review), with these systems constituting the first galaxies.
+In the hierarchical collapse scenario \citep{Rees1977,Fall1980}, matter density perturbations, which originate from some set of cosmological initial conditions, grow over time before condensing out of the general expansion to form dark matter halos \citep{Silk1968,Peebles1970}.
+It is at the centre of these halos that baryons collect, cool and begin to form stars (\citealt{Birnboim2003,Keres2005,Dekel2006} and see e.g.
+\citealt{Mo2010} for a recent review), with these systems constituting the first galaxies.
 One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue \citep[e.g.][]{Fall1983}.
@@
 This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
-The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic star formation rate density in this redshift range \citep{Madau_2014}.
+The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
 At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
@@
 To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be some process which shuts off star-formation within main sequence galaxies (i.e.
-quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010}.
+quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010,Darvish2016}.
 
@@
 Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations which must be reproduced across cosmic time.
-The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \cite{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
-Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope (HST) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
+The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
+Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope (HST) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
 In particular, in recent years the multiplexing capabilities of KMOS have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
@@
 SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
-This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic Star Formation Rate Density (SFRD) \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
-There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Tiley2016a,Harrison2017}.
+This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
+There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Tiley2016a,Harrison2017}.
 In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
@@
 \textbf{(3)} What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
-\textbf{(4)} What are the connections between the chemical properties and the kinematics of the gas, particularly in terms of inflows and outflows of material?
-
-This study focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
+\textbf{(4)} What is the connection between the gas phase metallicity and  kinematics, particularly in terms of inflows and outflows of material?
+
+This paper focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
@@
 \subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
-The KDS is a KMOS study of the gas kinematics and chemical composition in 77 SFGs with a median redshift of $z\sim3.5$, probing a representative section of the galaxy main sequence.
+The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\sim3.5$, probing a representative section of the galaxy main sequence.
 The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
@@
 Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
-Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective spatial resolution of the observations.
+Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations.
 \\
@@
 lbg\_113        & 03:32:36 & -27:41:50 & 3.622      & 24.01  & 9.83  & 41.0 & 0.52        & 60.0        & 15.0    & 0.87      \\
-$^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.9847 & 10.64 & 50.0 & 0.57         & 57.3        & -    & 2.52      \\
-n3\_009       & 22:17:28 & +00:12:12 & 3.069 & 99.0    & 8.72  & -            & 0.75        & 42.0        & 84.0    & 1.06      \\
-n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.9637 & 9.94  & -            & 0.71        & 46.0        & 94.0    & 0.56      \\
-lab18         & 22:17:29 & +00:07:52 & 3.101           & 99.0    & 8.66  & -            & 0.85        & 32.0        & 27.0    & 0.46      \\
-$^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & 99.0    & 8.78  & -            & 0.57         & 57.3        & -    & 2.18      \\
-s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.4618 & 9.88  & -            & 0.39        & 70.0        & 125.0   & 1.78      \\
-s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.9103 & 9.74  & -            & 0.57        & 57.0        & 76.0    & 1.59      \\
-$^{*}$s\_sa22b-d5  & 22:17:36 & +00:06:10 & 3.175 & 23.7182 & 10.32 & -            & 0.57         & 57.3        & -    & 3.30      \\
-s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.2538 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
-$^{*}$s\_sa22b-md25 & 22:17:42 & +00:06:20 & 3.304     & 24.6174 & 9.05  & -            & 0.57         & 57.3        & -    & 1.39
+$^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.98 & 10.64 & 50.0 & 0.57         & 57.3        & -    & 2.52      \\
+n3\_009       & 22:17:28 & +00:12:12 & 3.069 & -    & 8.72  & -            & 0.75        & 42.0        & 84.0    & 1.06      \\
+n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.96 & 9.94  & -            & 0.71        & 46.0        & 94.0    & 0.56      \\
+lab18         & 22:17:29 & +00:07:52 & 3.101           & -    & 8.66  & -            & 0.85        & 32.0        & 27.0    & 0.46      \\
+$^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & -    & 8.78  & -            & 0.57         & 57.3        & -    & 2.18      \\
+s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.46 & 9.88  & -            & 0.39        & 70.0        & 125.0   & 1.78      \\
+s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.91 & 9.74  & -            & 0.57        & 57.0        & 76.0    & 1.59      \\
+$^{*}$s\_sa22b-d5  & 22:17:36 & +00:06:10 & 3.175 & 23.72 & 10.32 & -            & 0.57         & 57.3        & -    & 3.30      \\
+s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.25 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
+$^{*}$s\_sa22b-md25 & 22:17:42 & +00:06:20 & 3.304     & 24.62 & 9.05  & -            & 0.57         & 57.3        & -    & 1.39
 
@@
 
+\begin{figure*}
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs008543_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_24_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_14_grid_paper.png}
+
+    \caption{We plot here the kinematic grids for one rotation dominated galaxy (top grid), one dispersion dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
+    In \protect\cref{app:kinematics_plots} we include these plots for each of the spatially resolved galaxies in the KDS, divided into rotation dominated, dispersion dominated and merger categories.
+    For both galaxies here we plot the HST image, GALFIT model and GALFIT residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
+    On the bottom row we plot the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
+    Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
+    The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
+    The purple symbols represent the extraction along $PA_{kin}$ from the residual map, and the two vertical dashed lines denote the intrinsic (inner) and convolved (outer) $2R_{1/2}$ values, with $V_{C}$ extracted at the convolved value.
+    The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
+    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per equation \protect\ref{eq:dispersion_comp}, and the vertical dashed lines have the same meaning as for the velocity extraction plot.
+    Also plotted with the blue and red dot-dash horizontal lines are the median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.}
+    \label{fig:main_body_kinematic_grids}
+
+\end{figure*}
+
 \subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
@@
 with `r' measured as the distance from the centre of rotation, (xcen, ycen).
-This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
-The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
-If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam-smearing.
+This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times finer pixel scale than the KMOS raw data before binning back to the previous resolution.
+The pixel scale refinement is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
+If the model is constructed with equivalent pixel scale to the data, the rotation curve has a flatter central profile which mimics the effect of beam-smearing.
 
@@
 In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination from the HST axis ratio.
-The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
+The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times finer pixel scale than the KMOS cube and rebinned for the same reasons and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
 This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion. \\
@@
  \hline
-b012141\_012208 & 32$\pm$13                    & 93$^{+48}_{-40}$                     & 94$\pm$18                 & 63$^{+28}_{-30}$                 & 1.47$^{+48}_{-40}$             & 122$^{+9}_{-9}$ & RD   \\
+b012141\_012208 & 32$\pm$13                    & 93$^{+48}_{-40}$                     & 94$\pm$18                 & 63$^{+28}_{-30}$                 & 1.47$^{+1.04}_{-0.92}$             & 122$^{+9}_{-9}$ & RD   \\
 b15573          & 61$\pm21$                    & 81$^{+30}_{-33}$                     & 111$\pm23$                 & 84$^{+28}_{-26}$          & 0.97$^{+0.47}_{-0.52}$            & 118$^{+10}_{18}$ & DD   \\
@@
 We do not consider these merger candidates in the results \cref{sec:results}, but keep the KDS galaxies without HST coverage on the basis that we do not identify double components in the galaxy continuum maps.
-In figure \ref{fig:merger_galaxies} we present the HST imaging, kinematic maps and 1-dimensional kinematic extractions of the KDS merger candidates.
+In the bottom grid of figure \ref{fig:main_body_kinematic_grids} and throughout \ref{fig:merger_galaxies} we present the HST imaging, kinematic maps and 1-dimensional kinematic extractions of the KDS merger candidates.
 
@@
         \includegraphics[height=3.5in]{tully_fisher_standard_log.png}
-        \caption{smTFR}
     \end{subfigure} \hspace{0.4cm}
@@
         \includegraphics[height=3.5in]{tully_fisher_s0_log.png}
-        \caption{S$_{0.5}$ Relation}
     \end{subfigure}
@@
 $M_{\star}$, i.e.
-the inverted stellar mass Tully-Fisher relation, for the isolated field sample, plotting rotation domianted galaxies in red and dispersion dominated galaxies with with clear symbols.
+the inverted stellar mass Tully-Fisher relation, for the isolated field sample, plotting rotation dominated galaxies in red and dispersion dominated galaxies with with clear symbols.
     Also plotted with the solid green line is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex error on the fit.
@@
         \includegraphics[height=3.5in]{v_sigma_evolution.png}
-        \caption{$V_{C}/\sigma_{int}$ vs. redshift}
     \end{subfigure} \hspace{+0.4cm}
@@
         \includegraphics[height=3.5in]{rdf_evolution.png}
-        \caption{RDF vs. redshift}
     \end{subfigure}
@@
         \includegraphics[height=3.5in]{sigma_evolution.png}
-        \caption{$\sigma_{int}$ vs. redshift}
     \end{subfigure} \hspace{0.4cm}
@@
         \includegraphics[height=3.5in]{v_evolution.png}
-        \caption{$V_{C}$ vs. redshift}
     \end{subfigure}

### 2017-02-24 paper.tex
about to leave ESO - complete up to section 4. About to make structural changes suggested by Chris and Mark to split the paper in two

@@
 The KDS mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with the increase of $\sigma_{int}$ with redshift reported across the comparison samples.
-However we find that only $37 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
+However we find that only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
 The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e.
@@
 The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
-Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope (HST) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
+Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em {\em HST}}) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
 In particular, in recent years the multiplexing capabilities of KMOS have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
@@
 The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
-The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks and the degree of disk turbulence, and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
-To achieve this we require very deep exposure times in excess of 7 hours on source for all galaxies, to reach the S/N required to detect line emission in the outskirts of the galaxies, where the rotation curves begin to flatten, and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
+The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
+We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
+To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
+Consequently, this is some of the deepest spectroscopic data available for this redshift.
 
 \subsubsection{Sample selection}\label{subsubsec:sample_selection}
-Target selection for the KDS sample is designed to pick out SFGs at $z = 3-4$, supported by deep multi-wavelength ancillary data and probing both cluster and field environments.
+Target selection for the KDS sample is designed to pick out SFGs at $z \sim 3.5$, supported by deep multi-wavelength ancillary data.
 Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the K-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the H-band, both of which are observable with KMOS.
-We also want to select a sample of galaxies spanning a representative region of the galaxy main sequence to minimise biases towards a particular subset of the overall star-forming population at these redshifts.
-For these reasons, and to ensure a high detection rate of the ionised gas emission lines in the KDS galaxies, we select galaxies in well studied fields that have a previous spectroscopic detection.
-To avoid biasing the sample towards blue and highly star-forming galaxies we make no secondary cuts on the basis of mass and flux.
+From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest S/N and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
+To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well studied fields that have a previous spectroscopic detection (see details below).
 Predominantly, the galaxies have been selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
 However, a subset of the selected cluster galaxies in the SSA22 field were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
+We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main sequence at this redshift.
 
 \subsubsection{GOODS-S}\label{subsubsec:sample_selection_goods}
-We select two `field' environment pointings with KMOS in the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 F160W imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
 We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
 These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
-The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions of spatial overdensity in the south-east (GOODS-S-P1) and north-west (GOODS-S-P2) to fill the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
+The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions where $\sim 20$ targets can be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
+In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively.\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}
 
 \subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
-We select a single `cluster' environment pointing from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an extreme overdensity of LBG candidates at $z \sim 3.09$.
-Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS, \citep{Shapley2003}, \citep{Nestor2013}, and when combined with deep B,V,R band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival HST ACS and WFC3 imaging covering large swathes of the field, the ancillary data is in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
-Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-CLUSTER).
-We also add a further field environment pointing to the south of the main galaxy spatial overdensity (SSA22-FIELD), leaving us with three field environment pointings across GOODS-S and SSA22 and a single cluster environment pointing, as summarised in table \ref{tab:pointings}.
-\footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during a poor year for Paranal.}
+A single CLUSTER environment pointing (SSA22-P1; see table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
+Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
+A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival {\em HST} ACS and WFC3 provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
+Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
+
+We also add a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
+In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
+In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in table \ref{tab:pointings}.
+\footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}
 
 \subsection{Observations and data reduction}\label{subsubsec:observations_and_dr}
-\subsubsection{Observations}\label{subsubsec:Obs}
+Our data for the 77 KDS targets were observed using KMOS.
 KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
@@
 Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band filter has spectral resolution of $R \sim 4200$.
-To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ must be observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and abundance measurements.
-To this end we decided to observe the SSA22 galaxies with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
-This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the spatially resolved metallicities reserved for a future work, and so we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the K-band spectral window.
+\subsubsection{Observations}\label{subsubsec:Obs}
+To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
+The GOODS-S pointings were observed in the H and K-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
 \\
@@
 
-The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)).
-The seeing conditions were excellent in GOODS-S-P1 and GOODS-S-P2 with median K-band seeing of $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
+The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
+In GOODS-S-P1 and GOODS-S-P2 the median K-band seeing was $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
 We observed 19-21 targets in each field (see table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
 \\
+
+This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the details of the H-band data reduction and corresponding metallicity analyses reserved for a future work.
+Consequently we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the K-band spectral window.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.8\textwidth]{main_sequence_hor.png}
+\caption{We plot the location of 48 KDS galaxies (see \cref{subsubsec:sample_summary}) in the SFR versus M$_{\star}$ plane, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
+Also plotted with the small grey points are individual SFGs from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
+The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
+We include the MS relation described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line. 
+Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3$ SFGs.}
+\label{fig:main_sequence}
+\end{figure*}
 
@@
 
-The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
-Readout channel bias is addressed using the `LCAL\_XXX.fits' calibration product to identify pixels which are not illuminated during exposures.
-The median values of these pixels are used to correct for varying flux baselines between each 64 pixel wide detector readout channel, which if left uncorrected leads to flux bandings over the spatial extent of the reduced cubes.
-Standard star observations are processed to provide a flux calibration for each detector, which is necessary to account for varying sensitivity across the three independent KMOS modules. 
+The SPARK recipes are then used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
+An additional step which is not part of the standard reduction process is carried out at this stage, which is to address readout channel bias.
+Differences in the readout process across each 64 pixel wide channel on the detector image lead to difference flux baselines in these channels, which are carried through to subsequent reduction stages.
+We correct back to a uniform flux baseline across each detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting the median value of these pixels.
+Standard star observations were carried out on the same night as the science observations and are processed in an identical manner to the science data.
 Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
@@
 Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the K-band greatly reduces the sky-line residuals.
-
-Variations in sky-subtraction quality are monitored over the course of the OBs which constitute the final stacks, as we find that the sky-subtraction performance becomes poorer as the telescope pointing approaches the zenith.
-This is due to the telescope tracking faster whilst looking through very low airmasses, hence scanning more rapidly over regions of sky with spatially and temporally varying OH emission.
-In addition to this we monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged K-band seeing rises above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
+We monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged K-band seeing rises above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
+The PSF is determined from fitting the K-band collapsed, stacked standard star cube in each pointing with an elliptical gaussian and the values are reported in table \ref{tab:pointings}.
 The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
-As part of this analysis, we tested whether the drift varies across the three KMOS detectors, finding typically that the difference is negligible, suggesting that it is not necessary to sacrifice more than a single IFU for tracking purposes.
 \\
@@
 We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
-To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux, and then subtracted from each spaxel in turn.
-This assumes that there is no spatial variation in the required correction, which we have found to be valid for our current sample of galaxies. \\
-
-The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the integrated galaxy spectrum, N[O~{\sc III}]$_{Det}$, the number with spatially resolved [O~{\sc III}]$\lambda$5007 emission, N[O~{\sc III}]$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
-\footnote{We note that in GOODS-S-P2 we later found that the redshifts for two of our targets were $z < 0.5$ and we omit these from all columns in table \ref{tab:pointings}.}
+To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
+\\
+
+The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det}$, the number with spatially resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
 
@@
 \label{tab:pointings}
-\begin{tabular}{c c c c c c c c c c c c c}
+\begin{tabular}{c c c c c c c c c c c c c c}
 
  \hline
-Pointing & RA & DEC & N$_{obs}$ & N[O~{\sc III}]$_{Det}$ & $\%$ Det. & N[O~{\sc III}]$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band(s) & Exp(ks) & PSF ($^{\prime\prime}$)  \\
+Pointing & Environment & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band$^{a}$ & Exp (ks) & PSF ($^{\prime\prime}$)$^{b}$  \\
  \hline
- GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & 2 & 17 & K, H & 32.4 & 0.50 \\
-GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 18 & K, H & 31.8 & 0.52 \\
-SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
-SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
+ GOODS-S-P1 & FIELD & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & K & 32.4 & 0.50 \\
+GOODS-S-P2 & FIELD & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & K & 31.8 & 0.52 \\
+SSA22-P1 & CLUSTER & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
+SSA22-P2 & FIELD & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
  \hline
@@
       \small
+      \item $^{a}$ We also observed the two GOODS-S pointings in the H-band to cover the [O~{\sc II}]$\lambda$3727,3729 emission lines and a description of these observations will be given in a future work.
+      \item $^{b}$ The PSF values correspond to measurements in the K-band.
       \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
@@
 \subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
-We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS galaxies.
+We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
 During the SED modelling we assume solar metallicity stellar templates, and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
@@
 The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
-
-In figure \ref{fig:main_sequence} we plot the stellar mass (M$_{\star}$) and SFR `main sequence' of the KDS galaxies, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-HST survey \citep{Brammer2012,Momcheva2016}.
-We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-HST data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the MS relation described in \cite{Speagle2014}: $logSFR(M_{\star}, t) = (0.84 - 0.026 \times t)logM_{\star} - (6.51 - 0.11 \times t)$, evaluated at $z\sim3.5$ where the age of the universe is 1.823Gyr, with the green line.
+In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
+For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
+In figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
+We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the MS relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.
+
+\begin{equation}\label{eq:speagle_ms}
+logSFR(M_{\star}, t) = (0.84 - 0.026 \times t)logM_{\star} - (6.51 - 0.11 \times t)
+\end{equation}
+
 The difference in position of these relations highlights the MS evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
-The KDS galaxies scatter, within the errors, consistently above and below these lines, suggesting that they are mostly regular SFGs in the process of converting their gas into stars (i.e.
-they are not especially bursty, or devoid of star formation).
-There are fewer galaxies plotted in figure \ref{fig:main_sequence} than observed due to the lack of deep, ground-based J and K-band photometry in SSA22 leaving the SFR unconstrained for several objects.
-We omit from this main sequence plot all objects in SSA22 that have J and K band detections lower than 2-$\sigma$ significance, leaving 64\% of the sample across all pointings, and note that the derived M$_{\star}$ values for the galaxies which are not plotted are consistent with the distribution shown in figure \ref{fig:main_sequence}.
-\begin{figure}
-\centering
-\includegraphics[width=0.49\textwidth]{main_sequence.png}
-\caption{We plot the location of the KDS galaxies across the four pointings on the star forming `main sequence', with filled symbols showing galaxies detected in the [O~{\sc III}]$\lambda$5007 emission line galaxies and open symbols those in which no detection has been made.
-Also plotted with the small grey points are individual SFGs from the 3D-HST survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
-The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
-We include the MS relation described in \protect\cite{Speagle2014}: $logSFR(M_{\star}, t) = (0.84 - 0.026 \times t)logM_{\star} - (6.51 - 0.11 \times t)$, evaluated at $z\sim3.5$ where the age of the universe is 1.823Gyr, with the green line.
-Given the errors associated with the computed SFRs and M$_{\star}$ values, the KDS galaxies scatter evenly above and below the plotted relations, suggesting that these are typical SFGs which sample the main sequence of star formation between 9.5 $< log(M_{\star}[M_{\odot}]) <$ 10.5 and have mean $log(M_{\star}[M_{\odot}]) = 10.0$.
-29 of the SSA22 targets do not have SFR measurements due to limited photometry and are not plotted here.
-For these galaxies it is still possible to derive an $M_{\star}$ value and we note that the distribution is consistent with the galaxies plotted in this figure.}
-\label{fig:main_sequence}
-\end{figure}
+The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence, indicating that they represent typical SFGs at this redshift.
 
 \subsubsection{Sample summary}\label{subsubsec:sample_summary}
-We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey, and have derived $M_{\star}$ values for all, and SFRs for 64\% of the sample from SED modelling.
-Three KMOS pointings cover the field environment, and one pointing covers a cluster environment at the heart of the SSA22 protocluster.
-This paper presents the dynamical properties of the KDS \textit{field} sample, with the cluster sample showing a very high merger fraction (as listed in table \ref{tab:pointings} and discussed in \cref{subsec:morpho-kin-class}).
-We omit this cluster pointing, SSA22-CLUSTER, from the dynamical analysis presented in the following sections due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
-Abundance measurements for the KDS galaxies in both the field and cluster environments will be presented in a future work.
+We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey and have derived $M_{\star}$ values and SFRs from SED modelling.
+Three KMOS pointings cover the field environment, and one pointing covers a cluster environment at the heart of the SSA22 protocluster and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
+Throughout the following analysis sections we describe the use of high-resolution imaging to make morphological measurements for the KDS galaxies and the extraction of kinematic properties for the galaxies using the [O~{\sc III}]$\lambda$5007 emission line.
+Chemical abundance measurements for the KDS galaxies in both the field and cluster environments will be presented in a future work.
 
@@
 \subsection{Morphological Measurements}\label{subsec:morphological_measurements}
-For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution photometry.
-This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies and helps to distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
-In the following sections we describe the approach we have chosen to recover these parameters.
-In \cref{subsubsection:morph_param_summary} we compare the KDS morphological parameters with those described in \cite{VanderWel2012}, and also with spectroscopically confirmed galaxies in different redshift intervals in order to study the size evolution of SFGs across cosmic time.
-
-\subsubsection{Applying GALFIT to the imaging data}\label{subsubsec:galfitting}
-We use GALFIT \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed HST images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
+For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution images.
+This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $b/a$, of the galaxies.
+In the following sections we describe the approach we have chosen to recover these parameters detailing comparisons with matched galaxies in the morphological parameter catalogue of \cite{VanderWel2012}.
+At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
+This allows us to look at the morphological properties of typical SFG populations at two redshift slices in comparison with those determined for the KDS sample.
+The imaging also helps to distinguish multiple `merging' components with small angular separations from objects which are morphologically isolated, which we discuss in \cref{subsubsection:spaxel_fitting} and \cref{subsec:morpho-kin-class} where we refine our sample for dynamical analysis.
+
+\subsubsection{Applying {\tt GALFIT} to the imaging data}\label{subsubsec:galfitting}
+We use {\tt GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
 The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z \sim 3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
-For SSA22 we make use of archival HST imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the WFC3 F160W band (P.I.
+For SSA22 we make use of archival {\em HST} imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the WFC3 F160W band (P.I.
 Lehmer: PID 13844; P.I.
@@
 Siana: PID 12527).
-The HST coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is concentrated on SSA22-CLUSTER, and so we must resort to the bluer ACS F814W data for SSA22-FIELD (all of the galaxies with HST coverage listed in table \ref{tab:phys-props}) which traces younger stellar populations and may not be sensitive to the majority of the mass distribution within these galaxies.
-\\
-
-We first run SExtractor \citep{Bertin1996} across the full fields to recover initial input parameters and segmentation maps for running GALFIT, and then extract postage stamp regions around the galaxies in the KDS sample.
+The {\em HST} coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is concentrated on SSA22-CLUSTER and so we resort to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage listed in table \ref{tab:phys-props}).
+\\
+
+We first run SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT} and then extract postage stamp regions around the galaxies in the KDS sample.
 At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
 During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.
-This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012} (with the median ratio of $\chi ^{2}$ values equal unity in all cases).
-Additionally, for the corresponding objects in the \cite{VanderWel2012} catalogue the median \Sers index value is n = 1.2.
-The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:KROSS}).
-\\
-
-In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012}, which has been shown to produce more reliable results than either the Tiny Tim model or an empirical stack alone.
-In the F814W band we use the pure Tiny Tim i-band model.
-
-This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $A_{r}$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
-The errorbars produced by GALFIT are purely statistical and are determined from the covariance matrix used in the fitting, with this resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
-Throughout the following subsections we also discuss adopted errors on each of the morphological parameters in turn.
+This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012}, with the median ratio of $\chi ^{2}$ $\sim 1$ between the different fitting methods.
+Additionally 22 GOODS-S objects are also detected in the \cite{VanderWel2012} catalogue the median \Sers index value is n = 1.2.
+The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsec:KROSS}).
+\\
+
+In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012} and in the F814W band we use the pure Tiny Tim ACS high-resolution PSF model.
+
+This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
+Examples of the {\em HST} imaging, {\tt GALFIT} output and residuals are given in figure \ref{fig:main_body_kinematic_grids} and these are given for each of the spatially resolved galaxies (see \cref{subsubsection:spaxel_fitting}) throughout \cref{app:kinematics_plots}.
+The errorbars produced by {\tt GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, with this resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
+Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
+There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we discuss the approach followed to recover the morphological parameter for these galaxies.
+We do not expect that this small number of galaxies without {\em HST} imaging will impact the bulk dynamical properties of the KDS sample.
 
@@
 \begin{threeparttable}
-\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying GALFIT \protect\citep{Peng2010_galfit}}
+\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\tt GALFIT} \protect\citep{Peng2010_galfit}}
 \label{tab:phys-props}
@@
  \hline
-ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}[M_{\odot}])^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $A_{r}$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
+ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}[M_{\odot}])^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
  \hline
@@
       \small
-      \item $^{a}$ Representative error of 0.2dex from SED modelling used throughout this study
-      \item $^{b}$ Representative error of 0.4dex in log(SFR$_{SED}$[$M_{\odot}yr^{-1}$]) from SED modelling used throughout this study
+      \item $^{a}$ Representative error of 0.2 dex from SED modelling used throughout this study
+      \item $^{b}$ Representative error of 0.4 dex in log(SFR$_{SED}$[$M_{\odot}yr^{-1}$]) from SED modelling used throughout this study
       \item $^{c}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
       \item $^{d}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
-      \item $^{*}$ No HST coverage: $PA_{morph}$ unconstrained; $A_{r}$ and $R_{1/2}$ estimated as explained throughout the text.
+      \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ unconstrained; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
     \end{tablenotes}
@@
 \subsubsection{Inclination angle}\label{subsubsection:inclination_angle}
-We use the derived $A_{r}$ values to determine galaxy inclination angles.
+We use the derived $b/a$ values to determine galaxy inclination angles.
 As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in equation \ref{eq:holmberg_i}, where $\frac{b}{a} \equiv A_{r}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
-To derive the inclination, we must select a value for $q_{0}$, and following the discussion in \citep{Law2012a} we choose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
-However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values, with the difference $<10\%$ in the case of the KDS galaxies.
 
@@
 
-The inclination angle calculated for each galaxy is used to correct the observed velocity field, which is the line of sight component of the intrinsic velocity field, with the correction factor increasing with increasing $A_{r}$.
-
-For the inclination error we adopt a conservative nominal uncertainty of 10$\%$ also, i.e.
-$\delta i = i / 10$, after examining the typical magnitude of the uncertainties reported following the Monte Carlo procedure described in \cite{Epinat2012}.
-We also note that generally this inclination uncertainty is a function of the recovered axis ratio, since it is more difficult to determine the inclination when the galaxy is more `face-on', but detailed inclination angle uncertainty modelling is beyond the scope of this paper.
+To derive the inclination, we must select a value for $q_{0}$, and following the discussion in \citep{Law2012a} we choose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
+However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values, with the difference $<10\%$ in the case of the KDS galaxies in the refined sample (see \cref{subsubsec:kin_sample_summary}).
+
+The inclination angle calculated for each galaxy is used to correct the observed velocity field, which is the line of sight component of the intrinsic velocity field, with the correction factor increasing with increasing $b/a$.
+The median difference between the derived $b/a$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta b/a = 0.0002$
+The $b/a$ distribution shown in figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST imaging}, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
+This compares well with the theoretical mean value of 57.3$^{\circ}$ computed for a population of galaxies with randomly drawn viewing angles (see e.g. the appendix in \cite{Law2009}).
+This reassures us that we are not biased towards deriving either particularly low or particularly high inclination angles.
+
+As mentioned in \cref{subsubsec:galfitting}, the error reported by {\tt GALFIT} on the model $b/a$ value is unrealistically small.
+Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopt a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
+For the galaxies without {\em HST} coverage the inclination angle is set to the KDS sample median of 57.0$^{\circ}$ and we use the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
+This corresponds to a factor $\sim1.3$ contribution to the uncertainty in the derived velocities for these galaxies.
 
 \subsubsection{Position angle}\label{subsubsection:position_angle}
-The second GALFIT parameter is $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
-This is expected to coincide with the kinematic position axis, $PA_{kin}$, in the case of a rotating disk galaxy, where the stars and the gas are both rotating around the centre of the gravitational potential well.
-Discrepancy between $PA_{morph}$ and $PA_{kin}$ is an important indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2016}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
-The discrepancy, often labelled $\Delta PA \equiv |PA_{morph} - PA_{kin}|$, is a function of $A_{r}$, as it becomes increasingly difficult to accurately measure $PA_{morph}$ for very inclined galaxies \citep[e.g.][]{Wisnioski2015,Harrison2017}.
-We have visually inspected each of the GALFIT maps to check that the derived $PA_{morph}$ follows the galaxy light distribution, and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class}).
-
-$PA_{morph}$ is well constrained by the fits at small axis ratios, but becomes increasingly uncertain as the galaxy morphology becomes closer to spherical.
-We note that typically the $PA_{morph}$ uncertainties are large in the regime of high axis ratios, but make no attempt to quote a formal uncertainty on this parameter.
+The second {\tt GALFIT} parameter is $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
+We have visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$indicated by the orange dashed line in figure \ref{fig:main_body_kinematic_grids}) and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
+We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2016}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
+We discuss this topic further in \cref{subsubsection:kin_and_phot}.
+For the galaxies without {\em HST} coverage we fix $PA_{morph}$ equal to $PA_{kin}$, following the analysis described in \cref{subsec:3d_modelling}.
 
 \subsubsection{Half-light radii}\label{subsubsection:half-light_radii}
-The third morphological parameter is the half-light radius, $R_{1/2}$, which provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
-As discussed throughout the introduction and in \cref{subsubsec:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
-Knowledge of $R_{1/2}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made, both of which are important when making comparisons to previous IFU studies \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
-Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d_modelling}), which requires the $R_{1/2}$ value for each galaxy.
-A final use of the derived $R_{1/2}$ values is to verify our beam-smearing correction results through comparison with systematic correction factors presented in Johnson et al.
-(in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:KROSS}).
-
-\cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in CANDELS, reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
-We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ recovered from extracting at $R_{1/2}$ and the errors on the intrinsic velocity dispersion, $\sigma_{int}$, the derivation of which requires knowledge of $R_{1/2}$ (\cref{subsec:3d_modelling}) are dominated by measurement errors and uncertainties connected with assumptions about the velocity dispersion distribution in high redshift galaxies (see \cref{app:kin_error_estimates}).
-
-\subsubsection{Galaxies without HST Coverage}\label{subsubsection:lack_of_hst}
-In SSA22, 4/21 of the spatially resolved galaxies do not have any HST coverage.
-For these galaxies the inclination angle is set to the theoretical mean of 57.3$^{\circ}$ calculated for a population of galaxies with randomly drawn viewing angles (see e.g.
-the appendix in \cite{Law2009}).
-This value is in good agreement with the KDS sample median of 57.4$^{\circ}$, see \cref{subsubsection:morph_param_summary}), and for the inclination uncertainty we use the standard deviation of the KDS inclinations, 12.4$^{\circ}$.
-This corresponds to a factor $\sim1.3$ uncertainty in the derived velocities for these galaxies.
-We fix $PA_{morph}$ equal to $PA_{kin}$ for the analysis described in \cref{subsec:3d_modelling} and to measure $R_{1/2}$ we first fit the [O~{\sc III}]$\lambda$5007 narrowband images with an exponential profile, and subtract the PSF from the recovered $R_{1/2}$ value.
+The half-light radius, $R_{1/2}$, provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
+As discussed throughout the introduction and in \cref{app:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
+Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies \citep[see \protect\cref{app:comparison_samples} and e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
+Throughout our dynamical modelling and beam smearing correction (see \cref{subsec:3d_modelling}) we also require the $R_{1/2}$ value for each galaxy.
+The median difference between the derived $R_{1/2}$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\sim3.5$).
+
+In the right panel of figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
+In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation).
+
+\cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploit during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
+We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high redshift galaxies (see \cref{app:kin_error_estimates}).
+
+To measure $R_{1/2}$ in the galaxies without {\em HST} coverage we first fit the [O~{\sc III}]$\lambda$5007 narrowband images with an exponential profile, and subtract the PSF from the recovered $R_{1/2}$ value.
 We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening.
-Owing to the small number of galaxies without HST imaging, we do not expect this to impact the bulk dynamical properties of the KDS sample.
-
-\subsubsection{Morphological parameter summary}\label{subsubsection:morph_param_summary}
+\\
 
@@
     We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ parameter, which could partially be explained by the F160W filter tracing a younger stellar population at $z\sim3.5$.
-    The distribution of KDS $R_{1/2}$ values are consistent with those in the higher redshift reference sample.
-    The $A_{r}$ distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < A_{r} < 0.9$.
-    This shows that we have not been biased towards deriving low or high $A_{r}$ values.}
+    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
+    The $b/a$ distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < A_{r} < 0.9$.
+    This shows that we have not been biased towards deriving low or high $b/a$ values.}
     \label{fig:morpho-distributions}
@@
 
-Having derived $R_{1/2}$, $A_{r}$ and $PA_{morph}$ for each of the KDS field galaxies \ref{fig:morpho-distributions} we plot the distributions of these properties, using KDS galaxies with HST coverage, along with distributions of morphological parameters determined in \cite{VanderWel2012} at low and high redshift.
-The GOODS-S KDS galaxies have been identified in the \cite{VanderWel2012} catalogue and the morphological properties show excellent agreement, with median $\Delta A_{r} = 0.0002$, median $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\sim3.5$) and the median \cite{VanderWel2012} $n = 1.2$ value for the KDS values close to our adopted n = 1 exponential disk fits.
-
-At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with the morphological catalogue of \cite{VanderWel2012}.
-This allows us to look at the bulk morphological properties of the SFG population in the two redshift slices in comparison with those determined for the KDS sample.
-The derived KDS $R_{1/2}$ distribution at $z \sim 3.5$ is similar to the wider sample distribution at $3 < z  < 4$, i.e.
-compact when compared to galaxies at lower redshifts and the KDS $A_{r}$ are consistent with being generally uniform between $0.3 < A_{r} < 0.9$, with median value of 0.57, corresponding to i = 57.4$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$, which is close to the statistical mean of i = 57.3$^{\circ}$ for a random galaxy sample.
-This reassures us that we are not biased towards deriving either particularly low or particularly high inclination angles.
-
 \subsection{Kinematic Measurements}\label{subsection:kinematic_measurements}
 
-We proceed now to extract 2D measurements from the KDS datacubes by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
-We then describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam-smearing corrections for each galaxy.
+We proceed to extract 2D kinematic measurements from the 62 KDS datacubes detected in integrated [O~{\sc III}]$\lambda$5007 emission by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
+This sample is then refined to galaxies which are spatially resolved in the [O~{\sc III}]$\lambda$5007 emission in order to make dynamical measurements.
+We also describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam-smearing corrections for each galaxy.
+We make use of the imaging data described in the previous sections to reduce the number of free parameters in the model, an approach which is necessary when working in this S/N regime.
 
 \subsubsection{Spaxel Fitting}\label{subsubsection:spaxel_fitting}
-We aim to extract 2-dimensional maps of the flux, velocity and velocity dispersion from each of the 77 stacked and calibrated KDS datacubes.
-These properties are extracted via modelling of the ionised gas emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
-We concentrate solely on the [O~{\sc III}]$\lambda$5007 emission line which always has S/N higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and typically extends over a larger area of each IFU.
-Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn, within which we locate the systemic wavelength of the redshifted [O~{\sc III}]$\lambda$5007 centre, $\lambda_{obs_{5007}}$, using the redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum.
-\\
-
+We aim to extract 2-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 62 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
+These properties are extracted via modelling emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
+We concentrate solely on the [O~{\sc III}]$\lambda$5007 emission line which always has S/N higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and is detected over a larger area of each IFU. \\
+
+Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn.
+The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, is used to determine the central wavelength of redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$.
 We search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
 This truncated spectrum is then used in the fitting procedure for each spaxel.
-The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by poor subtraction of the sky emission lines.
+The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky line residuals.
 A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
 These parameters, along with the estimate of the noise in the datacube, are used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not. 
-The noise is estimated by masking all datacube spaxels containing object flux and computing the sum of the squares of the flux values in the spectral extraction region for all remaining spaxels inwards of 0.3$^{\prime\prime}$ from the cube boundary.
+The noise is estimated by masking all datacube spaxels containing object flux and computing the standard deviation of the flux values in the spectral extraction region for all remaining spaxels inwards of 0.3$^{\prime\prime}$ from the cube boundary (over the same spectral region as considered to find the peak object flux).
 This boundary constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
-The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in equation \ref{eq:noise} where $F_{i}$ are the flux values across the extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
+The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in equation \ref{eq:noise} where $F_{i,background}$ are the flux values across the spatial regions containing no object flux and the spectral extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
 
 \begin{equation}\label{eq:noise}
-    N_{m} = STD\left(\sum_{i}F_{i}^{2}\right)
-\end{equation}
-
-The signal in each spaxel is taken as the sum of the flux values across the extraction region, as shown in Equation~\ref{eq:signal} where S denotes the signal.
+    N_{m} = STD\left(\sum_{i}F_{i,background}^{2}\right)
+\end{equation}
+
+The signal in each spaxel is taken as the sum of the flux values across the extraction region, $F_{i,object}$, as shown in equation \ref{eq:signal} where S denotes the signal.
 
 \begin{equation}\label{eq:signal}
-    S = \sum_{i}F_{i}
+    S = \sum_{i}F_{i,object}
 \end{equation}
@@
 \begin{enumerate}
-\item The uncertainties on any of the parameters of the gaussian fit must not exceed 30\%
-\item $\frac{S}{N} > 3$
+\item The uncertainties on any of the parameters of the gaussian fit as returned by {\tt LMFIT} must not exceed 30\%
+\item $\frac{S}{N_{m}} > 3$
 \end{enumerate}
@@
 We impose a further criterion to help remove fits to spectral features unrelated to the galaxy (e.g.
-fits to skyline residuals), which is important for `cleaning up' accepted spaxels in the 2D maps which are clearly independent of the main body of the galaxy.
+fits to skyline residuals), which is important for `cleaning up' accepted spaxels in the 2D maps which are clearly unrelated to the galaxy.
 For this test we subtract the galaxy continuum and impose that $0.7 < F_{g}/{S} < 1.3$, where $F_{g}$ is the flux from the gaussian fit to the [O~{\sc III}]$\lambda$5007 line and S is the signal in the extraction region from equation \ref{eq:signal}.
-
-If all three criteria are satisfied, the spaxel is accepted and the gaussian fit is repeated 1000 times with each flux value in the extraction region perturbed by the datacube flux error.
-This error is computed as the median of the standard deviations in the extraction regions of the unmasked spaxels, as shown in equation \ref{eq:cube_error} with $F_{e}$ denoting the flux error.
-
-\begin{equation}\label{eq:cube_error}
-   F_{e} = \big<STD(F _{i})\big>
-\end{equation}
-
-This Monte Carlo procedure gives the fit parameters and associated errors for the accepted spaxels.
-The velocity is computed from the gaussian centre, $\lambda_{g}$, using Equation~\ref{eq:velocity_comp} and the velocity dispersion is computed from the gaussian width, $\sigma_{g}$, using Equation~\ref{eq:dispersion_comp}, where $v_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
+If all three criteria are satisfied, the spaxel is accepted.
+\\
+
+From the gaussian fit we recover the centre, $\lambda_{g}$, the width, $\sigma_{g}$ and the area, $F_{g}$.
+The velocity is computed from $\lambda_{g}$ using equation \ref{eq:velocity_comp} and the velocity dispersion is computed from $\sigma_{g}$ using equation \ref{eq:dispersion_comp}, where $V_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light, $z_{sys}$ is the redshift determined from the integrated galaxy spectrum and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
 
 \begin{equation}\label{eq:velocity_comp}
-   v_{obs} = \frac{\lambda_{g} - (1 + z)\lambda_{5007}}{(1 + z)\lambda_{5007}} \times c
+   v_{obs} = \frac{\lambda_{g} - (1 + z_{sys})\lambda_{5007}}{(1 + z_{sys})\lambda_{5007}} \times c
 \end{equation}
@@
 \begin{equation}\label{eq:dispersion_comp}
-   \sigma_{obs} = \frac{\sigma_{g}}{(1 + z)\lambda_{5007}} \times c
-\end{equation}
+   \sigma_{obs} = \frac{\sigma_{g}}{(1 + z_{sys})\lambda_{5007}} \times c
+\end{equation}
+
+To estimate the errors on the observed quantities the gaussian fit is repeated 1000 times, with each flux value in the extraction region perturbed by the noise value, $N_{m}$.
+For each of these 1000 fits the gaussian parameters are used to compute the observed properties.
+The resultant distributions of observed quantities are gaussian and we take the median as the final values for $V_{obs}$, $\sigma_{obs}$ and $F_{g}$ for that spaxel and the standard deviation of the distribution as the observational uncertainties.
+A map of each of these observed parameters is constructed by applying this procedure to each spaxel. \\
 
@@
 
-The process is automated and applied to each of the KDS galaxies that have an [O~{\sc III}]$\lambda$5007 detection.
-Following the fitting procedure the galaxies are clasified as spatially resolved in [O~{\sc III}]$\lambda$5007 emission or not, with this defined as  the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map equivalent to or greater than the seeing disk.
+The process is automated and applied to each of the 62 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
+Following the fitting procedure the galaxies are clasified as spatially resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map equivalent to or greater than the seeing disk.
 For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, is added to table \ref{tab:pointings}.
-29\% of the detected KDS galaxies are not spatially resolved, and we do not analyse these further, despite several showing velocity gradients within the seeing disk, due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
-The physical properties of all spatially resolved galaxies in both GOODS-S and SSA22 are listed in table \ref{tab:phys-props}.
+We find that 47 (76\%) of the detected KDS galaxies across both the field and cluster environments are spatially resolved and show clear velocity structure.
+The 15 galaxies which are not spatially resolved are dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
+The physical properties of all spatially resolved galaxies in both GOODS-S and SSA22 are listed in table \ref{tab:phys-props}. \\
+
+The morphological information of \cref{subsec:morphological_measurements} is now combined with this spatially resolved condition to define two galaxy subsamples.
+We find that 6/38 of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicates the interpretation of the observed dynamics for these targets.
+We thus drop the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
+The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
+The 32/38 morphologically isolated field galaxies are referred to as the `isolated field sample'.
 
@@
 As mentioned in the introduction, there is no universal standard for defining $V_{C}$ and $\sigma_{int}$, particularly a dynamical model is used to provide beam-smearing corrections for $\sigma_{int}$ and extrapolations beyond the data for $V_{C}$.
-Physically motivated models take into account the potential-well of the galaxy through knowledge of the mass distribution \citep[e.g.][]{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015}.
+Physically motivated models take into account the potential-well of the galaxy through knowledge of the mass distribution \citep[e.g.][]{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015,Swinbank2017}.
 Phenomenological models assume a fixed function known to well describe observed galactic rotation curves which flatten at large radii \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Harrison2017}.
-Both of the above examples fit to 2D fields extracted from the datacubes using line-fitting software.
+Both of the above examples fit to 1D or 2D fields extracted from the datacubes using line-fitting software.
 Recently, algorithms such as Galpak$^{3D}$ \citep{Bouche2015} and 3D-Barolo \citep{DiTeodoro2015} have emerged, fitting directly to the flux in the datacube in order to constrain the kinematic properties.
 
-In this analysis we minimise the number of fitted parameters by making use of information from HST imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.
-We seek also to clearly distinguish between observed velocities and those inferred from modelling.
+There are three reasons to construct model velocity fields for the isolated field sample galaxies; the first is to interpolate between data points; the second is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the third is to estimate the effect of beam-smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
+As a brief overview, we use a Markov chain Monte Carlo (MCMC) procedure to construct a series of intrinsic model datacubes for each galaxy, convolve these with the atmospheric PSF and then fit to the data.
+The beam-smearing corrected kinematic parameters are then extracted from the intrinsic galaxy models as described in more detail below.
+In this analysis we minimise the number of fitted parameters by making use of information from {\em HST} imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.
 This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.
-There are thus two clear reasons for constructing model velocity fields; the first is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the second is to estimate the effect of beam-smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
 The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.
@@
     In \protect\cref{app:kinematics_plots} we include these plots for each of the spatially resolved galaxies in the KDS, divided into rotation dominated, dispersion dominated and merger categories.
-    For both galaxies here we plot the HST image, GALFIT model and GALFIT residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
+    For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
     On the bottom row we plot the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
@@
     The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per equation \protect\ref{eq:dispersion_comp}, and the vertical dashed lines have the same meaning as for the velocity extraction plot.
-    Also plotted with the blue and red dot-dash horizontal lines are the median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.}
+    Also plotted with the blue and red dot-dash horizontal lines are the median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
+    The merger candidate in the bottom grid requires several {\tt GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
     \label{fig:main_body_kinematic_grids}
@@
 \subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
-For each galaxy with spatially resolved [O~{\sc III}]$\lambda$5007 emission, we construct a model datacube with the same spatial dimensions as the observed datacube, and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined by the systemic velocity of the galaxy.
+For each galaxy with spatially resolved [O~{\sc III}]$\lambda$5007 emission, we construct a series of model datacubes with the same spatial dimensions as the observed datacube and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
 This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
@@
 \noindent
-with `r' measured as the distance from the centre of rotation, (xcen, ycen).
+with `r' measured as the distance from the centre of rotation.
 This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times finer pixel scale than the KMOS raw data before binning back to the previous resolution.
-The pixel scale refinement is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
-If the model is constructed with equivalent pixel scale to the data, the rotation curve has a flatter central profile which mimics the effect of beam-smearing.
+The pixel scale refinement is necessary to capture the steep velocity gradients across the central regions.
 
 The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
-In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination from the HST axis ratio.
-The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times finer pixel scale than the KMOS cube and rebinned for the same reasons and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
-This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion. \\
-
-This simulated intrinsic [O~{\sc III}]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries, with the atmospheric seeing profile determined from fitting the collapsed, stacked standard star cube in each pointing with an elliptical gaussian (the recovered seeing values are reported in table \ref{tab:pointings}).
-The velocity and velocity dispersion values are then re-measured in each spaxel to produced `beam-smeared' 2D maps of the kinematic parameters.
-
+The 6 free parameters of the model; $\{(xcen, ycen), i, PA_{kin}, rt, v_{asym}$, are first reduced to 5 by using the inclination from the {\em HST} axis ratio.
+We also fix the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential well, to leave only 3 free parameters to vary in the MCMC sampling.
+Due to the faintness of the continuum, there are several galaxies for which we cannot reliably estimate the rotation centre using this method and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location (approach described in \citealt{Harrison2017}).
+Using the continuum to fix the rotation centre is generally more successful for the SSA22 galaxies, since the use of the HK filter effectively doubles the S/N of the continuum by collapsing over twice the wavelength range.
+\\
+
+The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
+This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\sim3.0$ velocity dispersions and we discuss the impact of this assumption in \cref{appsubsec:model_errors}) by using sensible alternative values.
+\\
+
+The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries with the K-band atmospheric seeing profile (table \ref{tab:pointings}).
+The velocity and velocity dispersion values are then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
 We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, and seek the combination of parameters which maximises the log-Likelihood function given by equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
@@
 where $\delta_{v_{i}}$ are the observed velocity errors, $d_{i}$ are the datapoints and $M_{i}$ are the convolved model velocity values.
-In practice we fix the (xcen,ycen) parameters of the galaxy to the location of the stellar continuum, a proxy for the centre of the gravitational potential well, recovered from the collapsed KMOS cube, leaving only 3 free parameters to vary in the MCMC sampling.
-This assumes that the gas and the stars in the galaxy share a common centre of mass, an assumption which is verified for the vast majority of SFGs in the local and intermediate redshift universe.
-Due to the faintness of the continuum, there are several galaxies for which we cannot reliably estimate the rotation centre using this method, and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location.
-Using the continuum to fix the rotation centre is generally more successful for the SSA22 galaxies, since the use of the HK filter effectively doubles the S/N of this component by collapsing over two wavebands.
-This differs from the method of fixing the rotation centre at the midpoint between the velocity extrema, described in \cite{Wisnioski2015} and \cite{Rodrigues2016}.
-In general the S/N of our sample is low at the galaxy outskirts and for many of the isolated rotating sample we don't observe the flattening of the velocity field.
-This suggests that the velocity midpoint may be biased towards the side of the galaxy which shows the higher velocity value and so we instead use the physically motivated continuum centre where possible, which also matches the approach described in \cite{Harrison2017}.
-\\
 
@@
 
-Following the construction of a convolved cube and the measurement of the beam-smeared maps we can extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
+Following the construction of a convolved model cube and the measurement of the beam-smeared maps we can extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
 There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
-We provide an overview of these surveys in \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of these parameters used for comparison to the KDS throughout  \cref{subsec:redshift_evolution}).
-
-\subsubsection{KDS beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
-We extract $V_{smeared}$ and $V_{C}$ by reading off from the beam-smeared and intrinsic best fitting 2D model grids respectively at $2R_{1/2}$.
-The $R_{1/2}$ value used to extract velocities from the KMOS data is found by convolving the intrinsic $R_{1/2}$ value with the PSF of the observations.
-The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
-This is similar also to the $V_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}.
-The beam-smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class} for the morpho-kinematic classification).
-The $V_{C}$ errors are discussed in \cref{appsubsec:model_errors}. \\
-
-In most of the KDS field sample galaxies, the $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, with 2 galaxies requiring extrapolation > 0.4$^{\prime\prime}$ with a mean extrapolation of 0.17$^{\prime\prime}$.
-This extrapolation is a requirement imposed by the low S/N at the outskirts of the KDS galaxies, limiting the extent to which the ionised gas disk can be observed, with the majority of the observed velocity curves not reaching the point of flattening.
-The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radius marked on each velocity thumbnail.
-
-\subsubsection{KDS beam-smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
+We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
+An overview of these samples is provided in \cref{app:comparison_samples}, describing also the approach used to compute average parameter values.
+
+\subsubsection{Beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
+The intrinsic velocity $V_{C}$ is found by reading off from the best fitting intrinsic 2D model grid respectively at the intrinsic $2R_{1/2}$ value ($\sim3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
+This extraction radius is shown with the vertical red dashed line in figure \ref{fig:main_body_kinematic_grids}.
+The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
+This is similar also to the $V_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a} ($\sim3R_{D}$).
+
+In order to determine the beam-smearing correction factor, we also extract the velocity from the beam-smeared model, $V_{BS}$, at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in figure \ref{fig:main_body_kinematic_grids}.
+The beam-smearing correction factor ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in \cref{appsubsec:model_errors}.
+\\
+
+In 13 of the isolated field sample galaxies, the intrinsic $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, however only 2 galaxies require extrapolation > 0.4$^{\prime\prime}$ (i.e.
+2 KMOS pixels) with a mean extrapolation of 0.17$^{\prime\prime}$.
+The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radii marked on each velocity thumbnail.
+
+\subsubsection{Beam-smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
 Convolution of the model velocity field with the seeing profile produces a peak in the beam-smeared velocity dispersion map at the centre of rotation.
 The model therefore provides a beam-smearing correction for the velocity dispersion in every spaxel.
-This is dependent primarily on the magnitude of the velocity gradient across the parameter maps, an approach which is verified by the observation of a positive correlation between the KDS velocities and velocity dispersions.
-The 2D beam-smearing correction map, $\sigma_{bs}$, is taken as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50kms$^{-1}$ i.e.
-$\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
-The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in \cref{appsubsec:model_errors}.
+This is dependent primarily on the magnitude of the velocity gradient across the parameter maps, where larger velocity gradients result in larger central velocity dispersions.
+The 2D beam-smearing correction map, $\sigma_{BS}$, is taken as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50kms$^{-1}$ i.e.
+$\sigma_{BS} = \sigma_{model} - \sigma_{assumed}$ (where $\sigma_{assumed}$ is fixed at 50kms$^{-1}$ as described in \cref{subsubec:model_cube}).
+The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS}$ correction is discussed further in \cref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
 We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.
@@
 To measure the $\sigma_{int}$ value for each galaxy in our sample we first use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the K-band and 55.4kms$^{-1}$ in the HK-band).
-This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam-smearing correction best recovers the $\sigma_{int}$ values.
+This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam-smearing correction, followed by the subtraction of the instrumental resolution in quadrature, best recovers the $\sigma_{int}$ values.
 
 \begin{equation}\label{eq:owen_sigma}
-   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{bs} \right)^{2} - \sigma_{inst}^{2}}
+   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{BS} \right)^{2} - \sigma_{inst}^{2}}
 \end{equation}
@@
 The median value of this map is taken as the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value.
-The beam-smearing correction factor is then given by the ratio of these two medians, i.e.
-$\sigma_{obs}/\sigma_{int}$, with mean and median values of 0.77 and 0.79 respectively for the morphologically isolated KDS galaxies.
-\\
-
-To test the robustness of our beam-smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{d}/R_{psf}$, detailed in Johnson et al.
+The beam-smearing correction factor ($\sigma_{obs}/\sigma_{int}$) has a mean and median value of 0.77 and 0.79 respectively for the isolated field sample. \\
+
+To test the robustness of our beam-smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{1/2}/R_{psf}$, detailed in Johnson et al.
 (in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
-These correction factors are applied to $V_{smeared}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
-The $V_{C}$ values agree to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities. 
-This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.
+These correction factors are applied to $V_{BS}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
+When applying this approach to the isolated field sample, the $V_{C}$ values agree with our own corrections to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities.
+This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS methods \citep{Harrison2017}.
 We also observe that shape and width of the observed and intrinsic kinematic parameter distributions are equivalent, suggesting that the corrections do not over-extrapolate from the raw numbers.
 
-We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for all of the spatially resolved KDS field galaxies classified as morphologically isolated (29, see \cref{subsec:morpho-kin-class}).
+We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for the isolated field sample.
 
@@
       \item $^{a}$ RD = Rotation Dominated; DD = Dispersion Dominated
-      \item $^{*}$ No HST coverage; see table \ref{tab:phys-props}
+      \item $^{*}$ No {\em HST} coverage; see table \ref{tab:phys-props}
     \end{tablenotes}
@@
   \end{table*}
+
 \subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}
 
-The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
+The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
 This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
@@
 The resolved KDS galaxies at $z \sim 3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
-For the majority of galaxies we do not believe we are in a regime where prominent morphological features are resolved in the HST imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
-However there are some cases where morphological tidal features could affect $PA_{morph}$ such as the GOODS-S galaxies bs006541, bs008543, cdfs\_lbg\_105, cdfs\_lbg\_109 and cdfs\_lbg\_111.
+For the majority of galaxies we do not believe we are in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
 Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
@@
 
-There do appear to be some galaxies that have low axis ratios, so that $PA_{morph}$ should be well constrained, and $\Delta PA$ values of $\sim$ 90$^{\circ}$ (e.g.
-GOODS-S galaxy cdfs\_lbg\_38 and SSA22 galaxy s\_sa22a-d3).
-At present there does not appear to be any obvious explanation for why this is the case.
-
-\subsection{Comparison samples}\label{subsubsec:comparison_samples}
-Throughout \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
-The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out main sequence SFGs and traces the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission lines.
-Given the range of modelling and kinematic parameter extraction methods it is important to verify the extent to which the results from these surveys can be directly compared and treated as forming an evolutionary sequence, which we test in the following subsections by considering each survey in turn.
-
-We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
-The fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples is computed (i.e.
-we do not want the derived values with extremely large errors to dominate the averages).
-The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
-The same process is applied to compute the errors on the sample medians and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
-These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
-
-\subsubsection{GHASP}\label{subsubsec:GHASP}
-The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to derive 3D H$\alpha$ datacubes.
-The data extend out to several half-light radii and in each case an analytic function is fit to determine $V_{C}$, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
-We use the tabulated values from this survey as a local comparison sample.
-
-\subsubsection{DYNAMO}\label{subsubsec:DYNAMO}
-In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
-The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, making this an excellent sample for comparisons to high redshift.
-$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.3R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
-We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.
-
-\subsubsection{KROSS}\label{subsubsec:KROSS}
-We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}[M_{\odot}])=9.9$ and $z\sim0.9$.
-$V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) with the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
-These quantities are then beam-smearing corrected as described in H17 section 3.3.3. 
-Due to the consistency of modelling and measurement techniques these form a robust $z\sim0.9$ comparison sample.
-
-\subsubsection{KMOS$^{3D}$}\label{subsubsec:kmos_3d}
-The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
-At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.
-The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
-No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.
-
-\subsubsection{MASSIV}\label{subsubsec:MASSIV}
-The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
-An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
-We make use of tabulated values presented in E12.
-
-\subsubsection{SINS}\label{subsubsec:SINS}
-The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ at $z\sim2.0$.
-Galaxies in this sample are classified as rotation or dispersion dominated following FS09 section 9.5.1 which classifies rotation dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
-$V_{C}$ values for rotation dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion dominated galaxies using the velocity width.
-Only integrated velocity dispersions are presented for the full sample.
-In addition, \cite[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
-In this approach the $V_{C}$ value comes from the best fitting model parameter and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
-
-\begin{equation}\label{eq:sins_sigma}
-\begin{split}
-\sigma_{01} = \sqrt{\frac{v^{2}(R)h_{z}}{R}} \quad OR \quad \sigma_{01} = \frac{v(R)h_{z}}{R} \\
-& \sigma_{int} = \sqrt{\sigma_{01}^{2} + \sigma_{02}^{2}}
-\end{split}
-\end{equation}
-
-It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
-We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in \cref{subsec:redshift_evolution} plots.
-
-\subsubsection{LAW 09}\label{subsubsec:law_09}
-In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}[M_{\odot}])=10.0$ at $z\sim2.3$.
-The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
-We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
-These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
-We use tabulated data $\sigma_{int}$ data in L09 to compare this distribution with other results, but make no comparisons with the observed velocity-shear values.
-
-\subsubsection{AMAZE}\label{subsubsec:AMAZE}
-The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
-In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq.
-8).
-A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
-We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
-\\
-
-Also, for 5 galaxies in G11 $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error on $V_{C}$ equal to 1 when computing the sample averages.
-The $\sigma_{int}$ errors for individual galaxies are generally very small and for 3 galaxies the $\sigma_{int}$ value is consistent with 0kms$^{-1}$.
-For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
-A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{subsec:redshift_evolution}.
-This Unconstrained sample also contains the galaxy s\_sa22a-M38 common between the KDS and G11, classified here as a merger due to double HST components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
-The remaining 5 galaxies we refer to as the AMAZE Clean sample and plot with grey symbols.
-We also plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated. \\
-
-This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
-This trend towards consistency is encouraging, and as described in \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
-We stress that keeping in mind sample selection, mass ranges and kinematic parameter extraction methods are crucial when comparing results between different surveys.
-
 \subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
-We proceed to make use of the morphological and kinematic information described above to classify resolved KDS galaxies into three categories; \textbf{(1)} Rotation dominated; \textbf{(2)} Dispersion dominated; \textbf{(3)} Merger candidates.
-Previous studies have used various classification schemes of varying complexity to identify which galaxies fall into these categories, and also to identify galaxy which appear `disky'.
-This includes the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in FS09 and C09.
-In W15 a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
-In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
-In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in \cref{subsubsec:AMAZE}.
-
-We describe our simple classification criteria for the KDS galaxies based on a joint consideration of the high-resolution photometry and derived kinematic parameters in the following subsections.
+We proceed to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
+This is a simple empirical diagnostic for whether a galaxy is `Rotation Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
+a simple way to measure the prevalence of rotational and random motions][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
+Previous studies have used various classification schemes of varying complexity to identify rotation dominated galaxies which also appear to be disk-like and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
+We describe our simple classification criteria for the isolated field sample based on a joint consideration of the high-resolution photometry and derived kinematic parameters in the \cref{subsubsection:isolated_classification} and mention the KDS merger candidates in more detail in the following section.
 
@@
 KDS galaxies are classified as mergers when more than one component is identified in the high-resolution imaging.  
-One benefit of studying the HST photometry in tandem is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
+One benefit of studying the {\em HST} photometry in tandem is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
 These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
 A second benefit is to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
-can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging.
+can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging (e.g.
+the bottom grid in figure \ref{fig:main_body_kinematic_grids}).
 In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
-It is difficult to distinguish in some cases between two HST components rotating together in a single disk (i.e.
+It is difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e.
 clumpy disk galaxies \citep[e.g.][]{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
@@
 
-In 6/35 of the resolved KDS field galaxies (one count per merger) we clearly identify signs of multiple components or merging in the HST high-resolution imaging, which translates into a merger rate of 17\%.
+In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identify signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
 In 8/9 resolved KDS cluster galaxies we identify multiple photometric components, translating into a merger rate of 89\%  (see table \ref{tab:pointings}).
@@
 The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
-We do not consider these merger candidates in the results \cref{sec:results}, but keep the KDS galaxies without HST coverage on the basis that we do not identify double components in the galaxy continuum maps.
-In the bottom grid of figure \ref{fig:main_body_kinematic_grids} and throughout \ref{fig:merger_galaxies} we present the HST imaging, kinematic maps and 1-dimensional kinematic extractions of the KDS merger candidates.
-
-\subsubsection{Isolated KDS classification}\label{subsubsection:isolated_classification}
-We calculate rotation and dispersion dominated percentages with repsect to the total number of resolved galaxies in the field environment (35, see table \ref{tab:pointings}).
-The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/35 or 37\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 15/35 or 43\% of the sample, as indicated in table \ref{tab:kin_props}.
-We plot the best fitting smeared and intrinsic models for the resolved KDS field galaxies in \cref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
+As mentioned above we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
+We keep the KDS galaxies without {\em HST} coverage on the basis that we do not identify double components in the galaxy continuum maps. 
+In the kinematic grids throughout \ref{fig:merger_galaxies} (as well as the bottom grid in \ref{fig:main_body_kinematic_grids}) we present the {\em HST} imaging, kinematic maps and 1-dimensional kinematic extractions for the KDS merger candidates in both the field and cluster environments.
+
+\subsubsection{Isolated field sample classification}\label{subsubsection:isolated_classification}
+As mentioned above, various methods have been used throughout the literature to quantify the kinematic structure of star-forming galaxies at different redshifts. 
+These include the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in \cite{ForsterSchreiber2009} and \cite{Cresci2009}.
+In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
+In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
+In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in \cref{subsec:AMAZE}.
+We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see table \ref{tab:pointings}).
+The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in table \ref{tab:kin_props}.
+We plot the best fitting smeared and intrinsic models for the isolated field galaxies in \cref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
 
 \subsubsection{Summary of the final sample for further analyses}\label{subsubsec:kin_sample_summary}
-In summary, we have analysed the 77 $z\sim3.5$ SFGs initially targeted as part of the KDS, finding spatially resolved [O~{\sc III}]$\lambda$5007 emission in 44 galaxies (56\%).
-These resolved galaxies cover both cluster and field environments and due to the unusually high merger rate of 89\% in the cluster environment, we omit the 9 spatially resolved galaxies in this pointing from further consideration.
-
-In the remaining sample of 35 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 17\%, and following the classification described in \cref{subsubsection:isolated_classification} we find 13 rotation dominated galaxies (37\%) and 16 dispersion dominated galaxies (46\%) in the field sample.
-For these 29 galaxies we have measured morphological parameters using GALFIT to fit exponential disks to the HST imaging (see table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$, $V_{C}$, and the intrinsic velocity dispersions, $\sigma_{int}$ (see table \ref{tab:kin_props}).
-Throughout the remainder of the paper we discuss the derived kinematic properties of these 29 galaxies in further detail.
+In summary, we have analysed 77 typical $z\sim3.5$ SFGs spanning both cluster and field environments, finding 62 with integrated [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsec:datareduction}).
+This sample is refined to 47 galaxies (61\%) with spatially resolved [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsection:spaxel_fitting}).
+Due to the unusually high merger-candidate rate of 89\% in the cluster environment (identified by searching the high-resolution {\em HST} imaging for photometric counterparts), we omit the 9 spatially resolved galaxies in SSA22-P1 from further consideration.
+In the remaining sample of 38 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 16\%, which constitute the `merger field sample'.
+The remaining 32 galaxies constitute the `isolated field sample', for which we have measured morphological parameters using {\tt GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and table \ref{tab:kin_props}).
+\\
+
+The isolated field sample is further divided into 13 rotation dominated galaxies (34\%) and 19 dispersion dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}).
+
+Throughout the remainder of the paper we discuss the derived kinematic properties of the isolated field sample in further detail.
 
@@
 These galaxies are representative of typical SFGs $z\sim3.5$ as verified by comparing to fits to the galaxy main sequence at this redshift.
-Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 29 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
+Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 32 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
 not merger candidates).
 For these galaxies we have measured morphological properties as listed in table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
-The full analyses grids for these 29 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}. \\
-
-Throughout the following sections we analyse the derived kinematic parameters for these 29 galaxies, referred to as the `isolated field sample' in the remainder of the paper, placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{subsubsec:comparison_samples}.
-In \cref{subsubsec:comparison_samples} we have also described the variety of methodologies used to compute $V_{C}$ and $\sigma_{int}$ between comparison in an attempt to disentangle true evolution from offsets between derived dynamical values caused by disparate measurement techniques in the following analysis sections.
+The full analyses grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}. \\
+
+Throughout the following sections we analyse the derived kinematic parameters for these 32 galaxies, referred to as the `isolated field sample' in the remainder of the paper, placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{app:comparison_samples}.
+In \cref{app:comparison_samples} we have also described the variety of methodologies used to compute $V_{C}$ and $\sigma_{int}$ between comparison in an attempt to disentangle true evolution from offsets between derived dynamical values caused by disparate measurement techniques in the following analysis sections.
 It appears that choice of dynamical model and dynamical parameter extraction method does still play a large role in understanding the evolution of dynamical parameters, and for this reason we have verified that our modelling and measurement techniques are consistent with KROSS $z\sim0.9$ results described in \cite{Harrison2017}, allowing for robust comparisons between this and the KDS isolated field sample.
@@
     \caption{In the left panel the distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
-    The AMAZE Clean sample galaxies (see \protect\cref{subsubsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
+    The AMAZE Clean sample galaxies (see \protect\cref{subsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
     There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement, with the AMAZE Unconstrained galaxies mostly scattering to high $V_{C}$ values, despite sharing a common stellar mass range to the KDS, as a result of large extrapolations from the data.
@@
 In the left panel of figure \ref{fig:v_sig_and_v} we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane.
-We include galaxies from the AMAZE sample (G11) with the grey and clear symbols (this symbol choice and the other comparison samples are described in more detail throughout \cref{subsubsec:comparison_samples}).
+We include galaxies from the AMAZE sample (G11) with the grey and clear symbols (this symbol choice and the other comparison samples are described in more detail throughout \cref{app:comparison_samples}).
 We also plot the $V_{C}$ = $\sigma_{int}$ line, which roughly bisects the KDS sample, and indicates the dispersion and rotation dominated galaxies.
@@
 The galaxies in the AMAZE Unconstrained sample generally have much larger $V_{C}$ values despite occupying a similar stellar mass range to our isolated field sample, with this being a consequence of large model extrapolations beyond the observed data.
-We follow the bootstrapping procedure described in \cref{subsubsec:comparison_samples} to compute isolated field sample error weighted averages and statistical errors.
+We follow the bootstrapping procedure described in \cref{app:comparison_samples} to compute isolated field sample error weighted averages and statistical errors.
 The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015} and the mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ $57.0^{+6.6}_{-6.3}kms^{-1}$, which is less than at lower redshift.
@@
 
-Due to varying HST coverage and quality, it has not been possible to estimate n for all KDS galaxies.
-However we have verified throughout \cref{subsubsec:galfitting} that the GOODS-S galaxies are well described by the n = 1 exponential profile through a combination of GALFIT and comparison to the \Sers index values reported in \cite{VanderWel2012}.
+Due to varying {\em HST} coverage and quality, it has not been possible to estimate n for all KDS galaxies.
+However we have verified throughout \cref{subsubsec:galfitting} that the GOODS-S galaxies are well described by the n = 1 exponential profile through a combination of {\tt GALFIT} and comparison to the \Sers index values reported in \cite{VanderWel2012}.
 Setting n = 1 in equation \ref{eq:kn} leaves $k_{n} = 1.19$ and we continue under this assumption analogous to in \cite{Harrison2017} (although we note that as stated in \cite{Harrison2017} setting n = 2 results in $\sim20\%$ difference in the derived $j_{s}$ values).
@@
 \subsection{The redshift evolution of dynamical properties}\label{subsec:redshift_evolution}
-We proceed to investigate further the low rotation velocities and large velocity dispersions observed in the isolated field sample in \cref{subsec:rdf_v_over_sigma} by placing them in cosmological perspective using the comparison samples (see \cref{subsubsec:comparison_samples} for overview and symbol definitions).
+We proceed to investigate further the low rotation velocities and large velocity dispersions observed in the isolated field sample in \cref{subsec:rdf_v_over_sigma} by placing them in cosmological perspective using the comparison samples (see \cref{app:comparison_samples} for overview and symbol definitions).
 We have made use of the tabulated data and errors in these studies to derive the datapoint values and errorbars plotted in figure \ref{fig:rdf_and_v_sigma_w_redshift} and \ref{fig:sigma_and_v_sigma_w_redshift} in a consistent way, which is to take the fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples (i.e.
@@
 
-In the left panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and in the right panel we plot the closely connected RDF both as a function of redshift for the KDS isolated field sample and the comparison samples described in \cref{subsubsec:comparison_samples}.
+In the left panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and in the right panel we plot the closely connected RDF both as a function of redshift for the KDS isolated field sample and the comparison samples described in \cref{app:comparison_samples}.
 In the left panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} the filled symbols and black errorbars represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
 The shaded regions give the 16th and 84th percentiles of the distribution on individual $V_{C}/\sigma_{int}$ measurements, plotted here to indicate the range of measurements at each redshift slice.
-No tabulated data was available for the points plotted without errors and the clear symbols indicate comparison caveats (see \cref{subsubsec:comparison_samples}).
+No tabulated data was available for the points plotted without errors and the clear symbols indicate comparison caveats (see \cref{app:comparison_samples}).
 In the right panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the RDF.
@@
 In the right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
-It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in \cref{subsubsec:comparison_samples}) are directly comparable.
+It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in \cref{app:comparison_samples}) are directly comparable.
 The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
@@
 These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}[M_{\odot}])< 10.5$ typical main sequence galaxies at these redshifts.
-By using a combined morpho-kinematic classification based on broad-band HST imaging and our IFU data, we have separated probable interacting galaxies from the sample, finding consistent merger rates in the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
-We proceeded to make made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (\cref{subsubsec:comparison_samples} and table \ref{tab:evolution_numbers}).
+By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated probable interacting galaxies from the sample, finding consistent merger rates in the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
+We proceeded to make made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (\cref{app:comparison_samples} and table \ref{tab:evolution_numbers}).
 The main conclusions of this work are summarised as follows:
@@
     \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ and $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ (left panel of figure \ref{fig:v_sig_and_v}).
-    \item 13/29 isolated field sample galaxies are dispersion dominated and 16/29 are dispersion dominated as indicated by the ratio $V_{C}/\sigma_{int}$, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (left and right panels of figure \ref{fig:v_sig_and_v}).
-    This gives a rotation dominated fraction of $37 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of figure \ref{fig:rdf_and_v_sigma_w_redshift}).
+    \item 13/32 isolated field sample galaxies are rotation dominated and 19/29 are dispersion dominated as indicated by the ratio $V_{C}/\sigma_{int}$, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (left and right panels of figure \ref{fig:v_sig_and_v}).
+    This gives a rotation dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of figure \ref{fig:rdf_and_v_sigma_w_redshift}).
     \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}[M_{\odot}]) < 11.0$ at $z\sim0.9$ in the KROSS survey (figure \ref{fig:tf_relation}).
@@
     This supports a scenario in which the derease in $j_{s} \propto R_{D}V_{C}$ with increasing redshift between $z=0-3.5$ is driven by the gradual size evolution of galaxies over the same redshift interval (figure \ref{fig:morpho-distributions}).
-    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in \cref{subsubsec:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in \cref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}).
     This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to boost random motions within high redshift galaxies.
@@
 
-This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA HST, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
-This work is based on observations taken by the 3D-HST Treasury Program (GO 12177 and 12328) with the NASA/ESA HST, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+This work is based on observations taken by the 3D-{\em HST} Treasury Program (GO 12177 and 12328) with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
 Based on data obtained with the European Southern Observatory Very Large Telescope, Paranal, Chile, under Large Program 185.A-0791, and made available by the VUDS team at the CESAM data center, Laboratoire d'Astrophysique de Marseille, France.
-The HST data matched to the VUDS-DR1 are described in \cite{Grogin2011} and \cite{Koekemoer2011} for CANDELS and include data from the ERS \cite{Windhorst2011}.
+The {\em HST} data matched to the VUDS-DR1 are described in \cite{Grogin2011} and \cite{Koekemoer2011} for CANDELS and include data from the ERS \cite{Windhorst2011}.
 
@@
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+\section{Kinematics Plots}\label{app:kinematics_plots}
+In figures \ref{fig:rotation_dominated_galaxies}, \ref{fig:dispersion_dominated_galaxies} and \ref{fig:merger_galaxies} we plot the kinematic grids for the KDS galaxies classified as rotation dominated, dispersion dominated and merger candidates respectively.
+The figure captions provide more information on each of the panels of these grids.
+
+\section{Comparison samples}\label{app:comparison_samples}
+
 \begin{table*}
@@
 
-\appendix
-
-\section{Kinematics Plots}\label{app:kinematics_plots}
-In figures \ref{fig:rotation_dominated_galaxies}, \ref{fig:dispersion_dominated_galaxies} and \ref{fig:merger_galaxies} we plot the kinematic grids for the KDS galaxies classified as rotation dominated, dispersion dominated and merger candidates respectively.
-The figure captions provide more information on each of the panels of these grids.
+Throughout \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
+The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently picks out representative star-forming galaxies at each epoch and traces the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission lines.
+
+Given the range of modelling and kinematic parameter extraction methods it is important to verify the extent to which the results from these surveys can be directly compared and treated as forming an evolutionary sequence, which we test in the following subsections by considering each survey in turn.
+
+We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
+Throughout \cref{sec:results} we highlight in the figures which values can be directly compared using filled and hollow symbols.
+The fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples is computed (i.e.
+we do not want the derived values with extremely large errors to dominate the averages).
+The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
+The same process is applied to compute the errors on the sample medians and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
+These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+
+\subsection{GHASP}\label{subsec:GHASP}
+The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to derive 3D H$\alpha$ datacubes.
+The data extend out to several half-light radii and in each case an analytic function is fit to determine $V_{C}$, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
+We use the tabulated values from this survey as a local comparison sample.
+
+\subsection{DYNAMO}\label{subsec:DYNAMO}
+In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
+The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, making this an excellent sample for comparisons to high redshift.
+$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.3R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
+We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.
+
+\subsection{KROSS}\label{subsec:KROSS}
+We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}[M_{\odot}])=9.9$ and $z\sim0.9$.
+$V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) with the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
+These quantities are then beam-smearing corrected as described in H17 section 3.3.3. 
+Due to the consistency of modelling and measurement techniques these form a robust $z\sim0.9$ comparison sample.
+
+\subsection{KMOS$^{3D}$}\label{subsec:kmos_3d}
+The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
+At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.
+The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
+No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.
+
+\subsection{MASSIV}\label{subsec:MASSIV}
+The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
+An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
+We make use of tabulated values presented in E12.
+
+\subsection{SINS}\label{subsec:SINS}
+The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ at $z\sim2.0$.
+Galaxies in this sample are classified as rotation or dispersion dominated following FS09 section 9.5.1 which classifies rotation dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
+$V_{C}$ values for rotation dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion dominated galaxies using the velocity width.
+Only integrated velocity dispersions are presented for the full sample.
+In addition, \cite[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
+In this approach the $V_{C}$ value comes from the best fitting model parameter and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
+
+\begin{equation}\label{eq:sins_sigma}
+\begin{split}
+\sigma_{01} = \sqrt{\frac{v^{2}(R)h_{z}}{R}} \quad OR \quad \sigma_{01} = \frac{v(R)h_{z}}{R} \\
+& \sigma_{int} = \sqrt{\sigma_{01}^{2} + \sigma_{02}^{2}}
+\end{split}
+\end{equation}
+
+It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
+We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in \cref{subsec:redshift_evolution} plots.
+
+\subsection{LAW 09}\label{subsec:law_09}
+In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}[M_{\odot}])=10.0$ at $z\sim2.3$.
+The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
+We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
+These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
+We use tabulated data $\sigma_{int}$ data in L09 to compare this distribution with other results, but make no comparisons with the observed velocity-shear values.
+
+\subsection{AMAZE}\label{subsec:AMAZE}
+The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
+In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq.
+8).
+A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
+We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
+\\
+
+Also, for 5 galaxies in G11 $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error on $V_{C}$ equal to 1 when computing the sample averages.
+The $\sigma_{int}$ errors for individual galaxies are generally very small and for 3 galaxies the $\sigma_{int}$ value is consistent with 0kms$^{-1}$.
+For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
+A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{subsec:redshift_evolution}.
+This Unconstrained sample also contains the galaxy s\_sa22a-M38 common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
+The remaining 5 galaxies we refer to as the AMAZE Clean sample and plot with grey symbols.
+We also plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated. \\
+
+This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
+This trend towards consistency is encouraging, and as described in \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
+We stress that keeping in mind sample selection, mass ranges and kinematic parameter extraction methods are crucial when comparing results between different surveys.
+
+\section{Kinematic Parameters Error Estimates}\label{app:kin_error_estimates}
+
+\subsection{3D modelling kinematic parameter error estimates}\label{appsubsec:model_errors}
+As mentioned in \cref{subsec:3d_modelling}, the MCMC sampling provides distributions for each of the model parameters, from which we can extract the 84th and 16th percentile values as the +/- 1-$\sigma$ errors.
+During the following procedure $PA_{kin}$ is fixed to the maximum likelihood value for all model evaluations.
+We proceed to reconstruct the beam smeared and intrinsic dynamical models for each of the isolated field galaxies using the 16th and 84th percentile parameters, with the lower velocity 16th percentile model constructed using the upper limit on the inclination, and the 84th percentile model using the lower limit.
+To clearly distinguish the 1-$\sigma$ error regions for both the beam smeared and intrinsic model the region between the 16th and 84th percentile evaluations are shaded blue and red respectively in the figures shown in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies}.
+The +/- 1-$\sigma$ error values for both $V_{C}$ are then calculated using the the equations below, which also take into account the measurement errors with $\bar{\sigma}_{v_{obs}}$ equal to the average observational uncertainty extracted along $PA_{kin}$.
+The subscripts `16th' and `84th' denote the model from which the velocity has been extracted.
+
+\begin{equation}\label{eq:VC_plus}
+   \delta V_{C}+ = \sqrt{\left(V_{C-84} - V_{C}\right)^{2} + \left(\bar{\delta}V_{obs}\right)^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:VC_minus}
+   \delta V_{C}- = \sqrt{\left(V_{C} - V_{C-16}\right)^{2}  + \left(\bar{\delta}V_{obs}\right)^{2}}
+\end{equation}
+
+The upper and lower errors on the $\sigma_{int}$ are calculated using a similar approach.
+To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40kms^{-1}$ and $\sigma_{int} = 80kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
+figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.
+Conversely, assuming $\sigma_{int} = 40km^{-1}$ increases the beam-smearing.
+We calculate the minimum and maxmimum intrinsic velocity dispersion, $\sigma_{int-84-40}$ and $\sigma_{int-16-80}$, using equations \ref{eq:sig_84_40} and \ref{eq:sig_16_80} respectively:
+
+\begin{equation}\label{eq:sig_84_40}
+   \sigma_{int-84-40} = \sqrt{(\sigma_{obs} - \sigma_{bs-84-40})^{2} - \sigma_{sky}^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:sig_16_80}
+   \sigma_{int-16-80} = \sqrt{\left(\sigma_{obs} - \sigma_{bs-16-80}\right)^{2} - \sigma_{sky}^{2}}
+\end{equation}
+
+where $\sigma_{bs-84-40} = \sigma_{model-84-40} - 40$ and $\sigma_{bs-16-80} = \sigma_{model16-80} - 80$ are the beam smeared maps.
+The lower and upper errors on $\sigma_{int}$ are then given by the following:
+
+\begin{equation}\label{eq:sig_plus_error}
+   \delta\sigma_{int}+ = \sqrt{\left(\sigma_{int} - \sigma_{int-84-40}\right)^{2} + \left(\bar{\sigma}_{\sigma_{obs}}\right)^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:sig_minus_error}
+   \delta\sigma_{int}- = \sqrt{\left(\sigma_{int-16-80} - \sigma_{int}\right)^{2} + \left(\bar{\sigma}_{\sigma_{obs}}\right)^{2}}
+\end{equation}
+
+with $\bar{\sigma}_{\sigma_{obs}}$ equal to the average of the velocity dispersion measurement errors.
+Once these quantities have been measured, the upper and lower errors on the ratio $\frac{v_{2.2}}{\sigma{o}}$ can be computed using equations \ref{eq:v_over_sig_plus} and \ref{eq:v_over_sig_minus}, and the same prescription is followed to find the errors on $\frac{V_{C}}{\sigma{int}}$.
+
+\begin{equation}\label{eq:v_over_sig_plus}
+   \delta\frac{V_{C}}{\sigma_{int}}+ = \frac{V_{C}}{\sigma_{int}}\sqrt{\left(\frac{\delta V_{C}+}{V_{C}}\right)^{2} + \left(\frac{\delta\sigma_{int}+}{\sigma_{int}}\right)^{2}}
+\end{equation}
+
+\begin{equation}\label{eq:v_over_sig_minus}
+   \delta\frac{V_{C}}{\sigma_{int}}- = \frac{V_{C}}{\sigma_{int}}\sqrt{\left(\frac{\delta V_{C}-}{V_{C}}\right)^{2} + \left(\frac{\delta\sigma_{int}+-}{\sigma_{int}}\right)^{2}}
+\end{equation}
 
@@
 \caption{We plot here the kinematic grids for the 13 isolated field sample galaxies classified as rotation dominated.
-For each galaxy we plot the HST image, GALFIT model and GALFIT residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
+For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
 On the bottom row we plot the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
@@
 
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_112_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_124_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_DISPERSION/combine_sci_reconstructed_cdfs_lbg_30_grid_paper.png}
+
     \caption{The same as in figure \protect\ref{fig:rotation_dominated_galaxies} but for the dispersion dominated galaxies.}
@@
     In this case we plot only fits to the data in the velocity extraction plot with the blue line, rather than attempting the full beam-smearing analysis.
-    Several of the galaxies here mimic rotation from a purely kinematic perspective, but have two or more HST components and an accompanying double peak in the object spectrum at the object centre, leading to large velocity dispersions when single gaussian fits are attempted.}
+    Several of the galaxies here mimic rotation from a purely kinematic perspective, but have two or more {\em HST} components and an accompanying double peak in the object spectrum at the object centre, leading to large velocity dispersions when single gaussian fits are attempted.}
     \label{fig:merger_galaxies}
 \end{figure*}
-
-\section{Kinematic Parameters Error Estimates}\label{app:kin_error_estimates}
-
-\subsection{3D modelling kinematic parameter error estimates}\label{appsubsec:model_errors}
-As mentioned in \cref{subsec:3d_modelling}, the MCMC sampling provides distributions for each of the model parameters, from which we can extract the 84th and 16th percentile values as the +/- 1-$\sigma$ errors.
-During the following procedure $PA_{kin}$ is fixed to the maximum likelihood value for all model evaluations.
-We proceed to reconstruct the beam smeared and intrinsic dynamical models for each of the isolated field galaxies using the 16th and 84th percentile parameters, with the lower velocity 16th percentile model constructed using the upper limit on the inclination, and the 84th percentile model using the lower limit.
-To clearly distinguish the 1-$\sigma$ error regions for both the beam smeared and intrinsic model the region between the 16th and 84th percentile evaluations are shaded blue and red respectively in the figures shown in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies}.
-The +/- 1-$\sigma$ error values for both $V_{C}$ are then calculated using the the equations below, which also take into account the measurement errors with $\bar{\sigma}_{v_{obs}}$ equal to the average observational uncertainty extracted along $PA_{kin}$.
-The subscripts `16th' and `84th' denote the model from which the velocity has been extracted.
-
-\begin{equation}\label{eq:VC_plus}
-   \delta V_{C}+ = \sqrt{\left(V_{C-84} - V_{C}\right)^{2} + \left(\bar{\delta}V_{obs}\right)^{2}}
-\end{equation}
-
-\begin{equation}\label{eq:VC_minus}
-   \delta V_{C}- = \sqrt{\left(V_{C} - V_{C-16}\right)^{2}  + \left(\bar{\delta}V_{obs}\right)^{2}}
-\end{equation}
-
-The upper and lower errors on the $\sigma_{int}$ are calculated using a similar approach.
-To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40kms^{-1}$ and $\sigma_{int} = 80kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
-figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.
-Conversely, assuming $\sigma_{int} = 40km^{-1}$ increases the beam-smearing.
-We calculate the minimum and maxmimum intrinsic velocity dispersion, $\sigma_{int-84-40}$ and $\sigma_{int-16-80}$, using equations \ref{eq:sig_84_40} and \ref{eq:sig_16_80} respectively:
-
-\begin{equation}\label{eq:sig_84_40}
-   \sigma_{int-84-40} = \sqrt{(\sigma_{obs} - \sigma_{bs-84-40})^{2} - \sigma_{sky}^{2}}
-\end{equation}
-
-\begin{equation}\label{eq:sig_16_80}
-   \sigma_{int-16-80} = \sqrt{\left(\sigma_{obs} - \sigma_{bs-16-80}\right)^{2} - \sigma_{sky}^{2}}
-\end{equation}
-
-where $\sigma_{bs-84-40} = \sigma_{model-84-40} - 40$ and $\sigma_{bs-16-80} = \sigma_{model16-80} - 80$ are the beam smeared maps.
-The lower and upper errors on $\sigma_{int}$ are then given by the following:
-
-\begin{equation}\label{eq:sig_plus_error}
-   \delta\sigma_{int}+ = \sqrt{\left(\sigma_{int} - \sigma_{int-84-40}\right)^{2} + \left(\bar{\sigma}_{\sigma_{obs}}\right)^{2}}
-\end{equation}
-
-\begin{equation}\label{eq:sig_minus_error}
-   \delta\sigma_{int}- = \sqrt{\left(\sigma_{int-16-80} - \sigma_{int}\right)^{2} + \left(\bar{\sigma}_{\sigma_{obs}}\right)^{2}}
-\end{equation}
-
-with $\bar{\sigma}_{\sigma_{obs}}$ equal to the average of the velocity dispersion measurement errors.
-Once these quantities have been measured, the upper and lower errors on the ratio $\frac{v_{2.2}}{\sigma{o}}$ can be computed using equations \ref{eq:v_over_sig_plus} and \ref{eq:v_over_sig_minus}, and the same prescription is followed to find the errors on $\frac{V_{C}}{\sigma{int}}$.
-
-\begin{equation}\label{eq:v_over_sig_plus}
-   \delta\frac{V_{C}}{\sigma_{int}}+ = \frac{V_{C}}{\sigma_{int}}\sqrt{\left(\frac{\delta V_{C}+}{V_{C}}\right)^{2} + \left(\frac{\delta\sigma_{int}+}{\sigma_{int}}\right)^{2}}
-\end{equation}
-
-\begin{equation}\label{eq:v_over_sig_minus}
-   \delta\frac{V_{C}}{\sigma_{int}}- = \frac{V_{C}}{\sigma_{int}}\sqrt{\left(\frac{\delta V_{C}-}{V_{C}}\right)^{2} + \left(\frac{\delta\sigma_{int}+-}{\sigma_{int}}\right)^{2}}
-\end{equation}
 

### 2017-02-27 paper.tex
about to start chopping apart the results and discussion section

@@
  AMAZE & 3.0 & 10.0 & $3.59^{+1.45}_{-1.1}$ & $2.1^{+4.7}_{-1.15}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+27.0}_{-48.0}$ & $217^{+59.1}_{-40.2}$ & $129^{+166.0}_{-50.2}$ \\
- KDS & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.37^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $78.8^{+5.4}_{-5.1}$ & $60.0^{+49.1}_{-18.2}$ \\
+ \textbf{KDS} & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.37^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $78.8^{+5.4}_{-5.1}$ & $60.0^{+49.1}_{-18.2}$ \\
  \hline
@@
 
-\subsection{GHASP}\label{subsec:GHASP}
-The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to derive 3D H$\alpha$ datacubes.
-The data extend out to several half-light radii and in each case an analytic function is fit to determine $V_{C}$, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
+\subsection{GHASP ($z\sim0$)}\label{subsec:GHASP}
+The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to produce 3D H$\alpha$ datacubes.
+The data extend out to several half-light radii and in each case tilted ring models are fit to determine $V_{C}$ at large radii where the rotation curves have flattened, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
 We use the tabulated values from this survey as a local comparison sample.
 
-\subsection{DYNAMO}\label{subsec:DYNAMO}
+\subsection{DYNAMO ($z\sim0.1$, but selected with physical properties resembling $z\sim2$)}\label{subsec:DYNAMO}
 In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
-The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, making this an excellent sample for comparisons to high redshift.
-$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.3R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
+The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\sim 2$ SFGs.
+$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.6R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
 We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.
 
-\subsection{KROSS}\label{subsec:KROSS}
+\subsection{KROSS ($z\sim0.9$)}\label{subsec:KROSS}
 We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}[M_{\odot}])=9.9$ and $z\sim0.9$.
@@
 
-\subsection{KMOS$^{3D}$}\label{subsec:kmos_3d}
+\subsection{KMOS$^{3D}$ ($z\sim1.0$ and $z\sim2.3$)}\label{subsec:kmos_3d}
 The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
@@
 
-\subsection{MASSIV}\label{subsec:MASSIV}
+\subsection{MASSIV ($z\sim1.2$)}\label{subsec:MASSIV}
 The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
@@
 
-\subsection{SINS}\label{subsec:SINS}
+\subsection{SINS ($z\sim2.0$)}\label{subsec:SINS}
 The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ at $z\sim2.0$.
@@
 
-\subsection{LAW 09}\label{subsec:law_09}
+\subsection{LAW 09 ($z\sim2.3$)}\label{subsec:law_09}
 In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}[M_{\odot}])=10.0$ at $z\sim2.3$.
@@
 
-\subsection{AMAZE}\label{subsec:AMAZE}
+\subsection{AMAZE ($z\sim3.0$)}\label{subsec:AMAZE}
 The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.

### 2017-03-03 paper.tex
about to start on the discussion

@@
 
-\usepackage{hyperref}
+\usepackage[draft]{hyperref}
 \hypersetup{
@@
 We present dynamical measurements for 77 main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
-These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
+These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift universe.
 We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
@@
 Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
-These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
+These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
 \end{abstract}
@@
 At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
-This assumes that high redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
+This assumes that high-redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
 how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
@@
 There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Tiley2016a,Harrison2017}.
-In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
+In both cases, systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
 
@@
 There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts.
-For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high redshift?
+For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high-redshift?
 \textbf{(2)} What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
@@
 The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
-The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
+The two key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
 We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
@@
 Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
-A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival {\em HST} ACS and WFC3 provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
+A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
 Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
@@
 \subsubsection{Data reduction}\label{subsubsec:datareduction}
-The data reduction process relied heavily upon the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
+The data reduction process primarly makes use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
 In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.
 
-The SPARK recipes are then used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
+The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
 An additional step which is not part of the standard reduction process is carried out at this stage, which is to address readout channel bias.
-Differences in the readout process across each 64 pixel wide channel on the detector image lead to difference flux baselines in these channels, which are carried through to subsequent reduction stages.
-We correct back to a uniform flux baseline across each detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting the median value of these pixels.
+Differences in the readout process across each 64 pixel wide channel on the detector image lead to a varying flux baselines in these channels.
+We correct back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.
+
 Standard star observations were carried out on the same night as the science observations and are processed in an identical manner to the science data.
@@
 
-We stack all 300s exposures for each galaxy which pass the sky-subtraction and seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
+We stack all 300s exposures for each galaxy which pass seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
 We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
@@
 We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
-During the SED modelling we assume solar metallicity stellar templates, and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
+During the SED modelling we assume solar metallicity stellar templates and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
 We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
@@
 In figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
-We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the MS relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.
+We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.
 
@@
 
-The difference in position of these relations highlights the MS evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
+The difference in position of these relations highlights the main sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
 The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence, indicating that they represent typical SFGs at this redshift.
@@
 We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey and have derived $M_{\star}$ values and SFRs from SED modelling.
-Three KMOS pointings cover the field environment, and one pointing covers a cluster environment at the heart of the SSA22 protocluster and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
+Three KMOS pointings cover the field environment and one pointing covers a cluster environment at the heart of the SSA22 protocluster and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
 Throughout the following analysis sections we describe the use of high-resolution imaging to make morphological measurements for the KDS galaxies and the extraction of kinematic properties for the galaxies using the [O~{\sc III}]$\lambda$5007 emission line.
@@
 At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
-This allows us to look at the morphological properties of typical SFG populations at two redshift slices in comparison with those determined for the KDS sample.
+This allows us to look at the morphological properties of typical star-forming galaxy populations at two redshift slices in comparison with those determined for the KDS sample.
 The imaging also helps to distinguish multiple `merging' components with small angular separations from objects which are morphologically isolated, which we discuss in \cref{subsubsection:spaxel_fitting} and \cref{subsec:morpho-kin-class} where we refine our sample for dynamical analysis.
@@
 At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
+In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012} and in the F814W band we use the pure Tiny Tim ACS high-resolution PSF model.
 During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.
+
 This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012}, with the median ratio of $\chi ^{2}$ $\sim 1$ between the different fitting methods.
-Additionally 22 GOODS-S objects are also detected in the \cite{VanderWel2012} catalogue the median \Sers index value is n = 1.2.
+Additionally, 22 GOODS-S objects are also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is n = 1.2.
 The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsec:KROSS}).
@@
 
-In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012} and in the F814W band we use the pure Tiny Tim ACS high-resolution PSF model.
-
 This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
-Examples of the {\em HST} imaging, {\tt GALFIT} output and residuals are given in figure \ref{fig:main_body_kinematic_grids} and these are given for each of the spatially resolved galaxies (see \cref{subsubsection:spaxel_fitting}) throughout \cref{app:kinematics_plots}.
+Example {\em HST} images and {\tt GALFIT} outputs are given in figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout \cref{app:kinematics_plots}.
+
 The errorbars produced by {\tt GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, with this resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
 Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
-There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we discuss the approach followed to recover the morphological parameter for these galaxies.
+There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we discuss the approach followed to recover the morphological parameters for these galaxies.
 We do not expect that this small number of galaxies without {\em HST} imaging will impact the bulk dynamical properties of the KDS sample.
@@
 We use the derived $b/a$ values to determine galaxy inclination angles.
-As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in equation \ref{eq:holmberg_i}, where $\frac{b}{a} \equiv A_{r}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
+As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
 
@@
 The $b/a$ distribution shown in figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST imaging}, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
-This compares well with the theoretical mean value of 57.3$^{\circ}$ computed for a population of galaxies with randomly drawn viewing angles (see e.g. the appendix in \cite{Law2009}).
-This reassures us that we are not biased towards deriving either particularly low or particularly high inclination angles.
+This compares well with the theoretical mean value of 57.3$^{\circ}$ computed for a population of galaxies with randomly drawn viewing angles (see e.g.
+the appendix in \cite{Law2009}), reassuring us that we are not biased towards deriving either particularly low or particularly high inclination angles.
 
@@
 In the right panel of figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
-In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation).
+In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation REF).
 
 \cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploit during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
-We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high redshift galaxies (see \cref{app:kin_error_estimates}).
+We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high-redshift galaxies (see \cref{app:kin_error_estimates}).
 
@@
     \end{subfigure}
-    \caption{We crossmatch publicly available spectroscopic redshifts for SFGs, as discussed in the text, with the morphological catalogue presented in \protect\cite{VanderWel2012} in two different redshift slices.
+    \caption{We crossmatch publicly available spectroscopic redshifts for SFGs in two different redshift slices with the morphological catalogue presented in \protect\cite{VanderWel2012} as discussed in the text.
     This provides a set of reference morphological properties for typical SFGs at different evolutionary stages to which the derived KDS values can be compared.
     We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ parameter, which could partially be explained by the F160W filter tracing a younger stellar population at $z\sim3.5$.
-    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
+    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high-redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
     The $b/a$ distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < A_{r} < 0.9$.
@@
 Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn.
-The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, is used to determine the central wavelength of redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$.
+The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, is used to determine the central wavelength of the redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$.
 We search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
@@
 
-As mentioned in the introduction, there is no universal standard for defining $V_{C}$ and $\sigma_{int}$, particularly a dynamical model is used to provide beam-smearing corrections for $\sigma_{int}$ and extrapolations beyond the data for $V_{C}$.
+As mentioned in the introduction, there is no universal standard for defining $V_{C}$ and $\sigma_{int}$, particularly when a dynamical model is used to provide beam-smearing corrections for $\sigma_{int}$ and extrapolations beyond the data for $V_{C}$.
 Physically motivated models take into account the potential-well of the galaxy through knowledge of the mass distribution \citep[e.g.][]{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015,Swinbank2017}.
@@
     In \protect\cref{app:kinematics_plots} we include these plots for each of the spatially resolved galaxies in the KDS, divided into rotation dominated, dispersion dominated and merger categories.
-    For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
-    On the bottom row we plot the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
+    For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map.
+    On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
     Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
     The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
-    The purple symbols represent the extraction along $PA_{kin}$ from the residual map, and the two vertical dashed lines denote the intrinsic (inner) and convolved (outer) $2R_{1/2}$ values, with $V_{C}$ extracted at the convolved value.
+    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value.
     The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
-    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per equation \protect\ref{eq:dispersion_comp}, and the vertical dashed lines have the same meaning as for the velocity extraction plot.
-    Also plotted with the blue and red dot-dash horizontal lines are the median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
+    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per equation \protect\ref{eq:dispersion_comp}.
+    Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
     The merger candidate in the bottom grid requires several {\tt GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
@@
 \subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
-For each galaxy with spatially resolved [O~{\sc III}]$\lambda$5007 emission, we construct a series of model datacubes with the same spatial dimensions as the observed datacube and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
+For each galaxy with spatially resolved [O~{\sc III}]$\lambda$5007 emission we construct a series of model datacubes with the same spatial dimensions as the observed datacube and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
 This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
@@
 
-The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
+The velocity decreases with a factor of cos($\phi$) from the kinematic position axis, where $\phi$ is the angle measured clockwise from the axis, which points to the direction of the positive side of the velocity field.
 The 6 free parameters of the model; $\{(xcen, ycen), i, PA_{kin}, rt, v_{asym}$, are first reduced to 5 by using the inclination from the {\em HST} axis ratio.
@@
 The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
-This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\sim3.0$ velocity dispersions and we discuss the impact of this assumption in \cref{appsubsec:model_errors}) by using sensible alternative values.
-\\
+This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\sim3.0$ velocity dispersions and we discuss the impact of this assumption in \cref{appsubsec:model_errors} by using sensible alternative values.
+The reported errors on $\sigma_{int}$ take this assumption into account. \\
 
@@
 We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
-An overview of these samples is provided in \cref{app:comparison_samples}, describing also the approach used to compute average parameter values.
+An overview of these comparison samples is provided in \cref{app:comparison_samples}, describing also the approach used to compute average parameter values.
 
 \subsubsection{Beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
-The intrinsic velocity $V_{C}$ is found by reading off from the best fitting intrinsic 2D model grid respectively at the intrinsic $2R_{1/2}$ value ($\sim3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
-This extraction radius is shown with the vertical red dashed line in figure \ref{fig:main_body_kinematic_grids}.
+The intrinsic velocity, $V_{C}$, is found by reading off from the best fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\sim3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
+This extraction radius is shown with the vertical red dashed line in the panels of figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
 The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
-This is similar also to the $V_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a} ($\sim3R_{D}$).
-
-In order to determine the beam-smearing correction factor, we also extract the velocity from the beam-smeared model, $V_{BS}$, at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in figure \ref{fig:main_body_kinematic_grids}.
+This is similar also to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\sim3R_{D}$), \citep{Tiley2016a}.
+
+The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$ respectively, which is less than at lower redshift (see \cref{subsec:results_rotation_vel} for a discussion).
+In order to determine the beam-smearing correction factor, we also extract the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
 The beam-smearing correction factor ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in \cref{appsubsec:model_errors}.
@@
 2 KMOS pixels) with a mean extrapolation of 0.17$^{\prime\prime}$.
-The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radii marked on each velocity thumbnail.
+The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the intrinsic and convolved $2R_{1/2}$ extraction radii marked on each velocity thumbnail.
 
@@
 The median value of this map is taken as the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value.
+The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
 The beam-smearing correction factor ($\sigma_{obs}/\sigma_{int}$) has a mean and median value of 0.77 and 0.79 respectively for the isolated field sample. \\
@@
 These correction factors are applied to $V_{BS}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
-When applying this approach to the isolated field sample, the $V_{C}$ values agree with our own corrections to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities.
+When following this approach for the isolated field sample, the derived $V_{C}$ values agree with our own corrections to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities.
 This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS methods \citep{Harrison2017}.
-We also observe that shape and width of the observed and intrinsic kinematic parameter distributions are equivalent, suggesting that the corrections do not over-extrapolate from the raw numbers.
+We also observe that the shape and width of the observed and intrinsic kinematic parameter distributions are equivalent, suggesting that the corrections do not over-extrapolate from the raw numbers.
 
@@
 This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
-Significant misalignment between the two axes can however be a signature of galaxy interaction.
+Significant misalignment between the two axes can be a signature of galaxy interaction.
 
@@
 This is a simple empirical diagnostic for whether a galaxy is `Rotation Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
-a simple way to measure the prevalence of rotational and random motions][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
-Previous studies have used various classification schemes of varying complexity to identify rotation dominated galaxies which also appear to be disk-like and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
-We describe our simple classification criteria for the isolated field sample based on a joint consideration of the high-resolution photometry and derived kinematic parameters in the \cref{subsubsection:isolated_classification} and mention the KDS merger candidates in more detail in the following section.
+a method to measure the prevalence of rotational and random motions][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
+Previous studies have used various classification schemes of varying complexity to identify rotation dominated galaxies which also appear to be `disk-like' and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
+We describe our simple classification criteria for the isolated field sample based on a joint consideration of the high-resolution photometry and derived kinematic parameters in \cref{subsubsection:isolated_classification} and mention the KDS merger candidates in more detail in the following section.
 
@@
 KDS galaxies are classified as mergers when more than one component is identified in the high-resolution imaging.  
-One benefit of studying the {\em HST} photometry in tandem is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
+One benefit of studying the {\em HST} photometry in tandem with the kinematics is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
 These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
@@
 The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they are drawn from a higher density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas as well as the morphological and dynamical evolution within these galaxies.
-The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
+The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high-redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
 As mentioned above we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
@@
 We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see table \ref{tab:pointings}).
-The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in table \ref{tab:kin_props}.
+The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of table \ref{tab:kin_props}.
 We plot the best fitting smeared and intrinsic models for the isolated field galaxies in \cref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
@@
 
-The isolated field sample is further divided into 13 rotation dominated galaxies (34\%) and 19 dispersion dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}).
+The isolated field sample is further divided into 13 rotation dominated galaxies (34\% with respect to full field sample) and 19 dispersion dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}).
 
@@
 
-\section{RESULTS \& DISCUSSION}\label{sec:results}
+\section{RESULTS}\label{sec:results}
 
@@
 Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 32 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
-not merger candidates).
+not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
 For these galaxies we have measured morphological properties as listed in table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
-The full analyses grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}. \\
-
-Throughout the following sections we analyse the derived kinematic parameters for these 32 galaxies, referred to as the `isolated field sample' in the remainder of the paper, placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{app:comparison_samples}.
-In \cref{app:comparison_samples} we have also described the variety of methodologies used to compute $V_{C}$ and $\sigma_{int}$ between comparison in an attempt to disentangle true evolution from offsets between derived dynamical values caused by disparate measurement techniques in the following analysis sections.
-It appears that choice of dynamical model and dynamical parameter extraction method does still play a large role in understanding the evolution of dynamical parameters, and for this reason we have verified that our modelling and measurement techniques are consistent with KROSS $z\sim0.9$ results described in \cite{Harrison2017}, allowing for robust comparisons between this and the KDS isolated field sample.
+The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}. \\
+
+Throughout the following sections we analyse the derived kinematic parameters for these 32 galaxies, referred to as the `isolated field sample', placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{app:comparison_samples}.
+In \cref{app:comparison_samples} we describe also the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.
+During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+\\
+
+We proceed first to investigate the relationship between rotation velocity and stellar mass for both the rotation and dispersion dominated isolated field galaxies.
+
+\subsection{Rotation velocity and stellar mass}\label{subsec:results_rotation_vel}
 
@@
         \centering
-        \includegraphics[height=3.5in]{sigma_versus_v.png}
-        %\caption{$\Delta PA$ vs. axis ratio}
+        \includegraphics[height=3.5in]{tully_fisher_standard_log.png}
     \end{subfigure} \hspace{0.4cm}
@@
         \centering
-        \includegraphics[height=3.5in]{v_over_sigma_versus_mass.png}
-        %\caption{$\Delta PA$ vs. $\sigma_{obs}$}
+        \includegraphics[height=3.5in]{v_evolution.png}
     \end{subfigure}
-    \caption{In the left panel the distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
-    The AMAZE Clean sample galaxies (see \protect\cref{subsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
-    There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement, with the AMAZE Unconstrained galaxies mostly scattering to high $V_{C}$ values, despite sharing a common stellar mass range to the KDS, as a result of large extrapolations from the data.
-    The $V_{C}/\sigma_{int} = 1$ line divides the galaxies classified as rotation dominated and dispersion dominated, with dispersion dominated galaxies sitting above the line. 
-    The galaxy s\_sa22a-M38, classified here as a merger but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ is marked on the plot.
-    In the right panel the distribution of the isolated field sample in the $V_{C}$/$\sigma_{int}$ vs. $M_{\star}$ plane is shown, along with the galaxies in the AMAZE Clean sample.
-    We also mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies in this panel, finding that it is the more massive galaxies which tend to a be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
-    We suggest that as galaxies accumulate their stellar populations and exhaust their gas supplies, this leads to a more stable rotating disk and hence evolution towards higher $V_{C}/\sigma_{int}$ values.}
-    \label{fig:v_sig_and_v}
-\end{figure*}
-
-\subsection{Rotation dominated fraction and $V_{C}/\sigma_{int}$}\label{subsec:rdf_v_over_sigma}
-
-In the left panel of figure \ref{fig:v_sig_and_v} we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane.
-We include galaxies from the AMAZE sample (G11) with the grey and clear symbols (this symbol choice and the other comparison samples are described in more detail throughout \cref{app:comparison_samples}).
-We also plot the $V_{C}$ = $\sigma_{int}$ line, which roughly bisects the KDS sample, and indicates the dispersion and rotation dominated galaxies.
-The KDS galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is good agreement between the KDS and AMAZE Clean samples.
-The galaxies in the AMAZE Unconstrained sample generally have much larger $V_{C}$ values despite occupying a similar stellar mass range to our isolated field sample, with this being a consequence of large model extrapolations beyond the observed data.
-We follow the bootstrapping procedure described in \cref{app:comparison_samples} to compute isolated field sample error weighted averages and statistical errors.
-The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015} and the mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ $57.0^{+6.6}_{-6.3}kms^{-1}$, which is less than at lower redshift.
-These results are placed in the context of previous work throughout \cref{subsec:TF} and \cref{subsec:redshift_evolution}, where we also discuss possible explanations for the increase in $\sigma_{int}$ with redshift.\\
-
-In the right panel figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean sample for reference.
-In the local universe, disky, SFGs are observed to have $V_{C}/\sigma_{int}$ values in excess of 10 (i.e.
-the disks are `well settled'), due to the decline of velocity dispersion across cosmic time, as gas fractions and disk turbulence decrease \citep[e.g.][]{Epinat2008,Epinat2008a}.
-Clearly the isolated field sample galaxies are in a different physical regime, with mean and median $V_{C}/\sigma_{int}$ values of $1.08^{+0.18}_{-0.15}$ and $0.97^{+0.14}_{-0.11}$ respectively.
-This is despite many of the dispersion dominated galaxies showing clear velocity gradients across the observed velocity maps (\cref{app:kinematics_plots}), with the arctangent model providing a good fit to the rotation curves.
-This suggests that, for these galaxies, although rotational motions are present within the disks, they are small or comparable with the elevated $\sigma_{int}$ values observed throughout the $z \sim 3.5$ sample.
-This suggests in turn that the random motions traced by $\sigma_{int}$ are providing some degree of gravitational support for the total mass of the system (see \cref{subsec:dynamical_masses}), in contrast to the local universe in which late-type galaxies are supported entirely by ordered rotation.
-The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies is also marked in the right panel and we find that it is the more massive galaxies which tend to a be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
-We suggest that as galaxies accumulate their stellar populations and exhaust their gas supplies, this leads to a more stable rotating disk and hence evolution towards higher $V_{C}/\sigma_{int}$ values.
-
-As discussed in \cref{subsec:morpho-kin-class}, the isolated field sample Rotation Dominated Fraction (RDF) is 0.37$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe, as a result of the increased velocity dispersions.
-This value is in good agreement with the result of G11, however we note that their result of $RDF \sim 0.33$ could be higher if any of the galaxies which were not passed through their dynamical model were rotation dominated.
-We interpret these results in the context of the cosmic evolution of the RDF in \cref{subsubsec:RDF_evolution}.\\
-
-We proceed now to investigate the connection between rotation velocity and stellar mass for the rotation and dispersion dominated KDS field galaxies as an attempt to understand the physical differences between galaxies falling into these categories at different cosmic times (i.e.
-do rotation dominated galaxies change in physical properties between different redshift slices).
-We build on both the ideas that accumulating a stellar population contributes to stabilising rotation within typical SFGs at all epochs and that rotation velocities alone may not be a good tracer of the total dynamical mass within a system.
-
-\subsection{Rotation velocity and stellar mass}\label{subsec:TF}
+    \caption{{\it Left:} We plot log($V_{C}$) vs. $M_{\star}$ for the isolated field sample, with the rotation dominated galaxies in red and dispersion dominated galaxies with the hollow symbols.
+    Also plotted with the solid green line is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex scatter on the fit.
+    This $z\sim0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in \protect\cite{Reyes2011}.
+    The rotation dominated KDS galaxies, and galaxies classed as reliable from the AMAZE survey \protect\citep{Gnerucci2011}, also show no evolution from this relation within the scatter, with the dispersion dominated galaxies scattering below the relation.
+    This highlights the need for careful sample selection when constructing this relation.
+    {\it Right:} The mean, median and distributions of the comparison sample $V_{C}$ measurements are plotted against redshift.
+    The $V_{C}$ distributions in each of the individual studies are wide, reflecting the galaxy diversity within each sample.
+    The low mean value of $V_{C}$ in the KDS isolated field sample is driven mainly by averaging over a sample which contains a higher fraction of dispersion dominated galaxies with lower rotation velocities.}
+    \label{fig:tf_relation}
+\end{figure*}
+
+In the $\Lambda CDM$ paradigm, galaxies form when baryons accumulate and cool in the centres of dark matter halos, subsequently forming a rotating disk of stars and gas.
+The relationship between stellar mass and rotation velocity describes the connection between the luminous mass and the total dynamical mass in a system.
+The connection has been studied extensively at low redshift \citep[e.g.][]{Bell2000a,Rhee2003,Reyes2011} with fits to late-type, rotating galaxies in the $V_{C}-M_{\star}$ plane having a well-defined slope and normalisation.
+Observing this `stellar mass Tully-Fisher relation' at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies \citep[e.g.][]{Dubois2014a,Vogelsberger2014b,Schaye2015}.
+In principle, studying whether the stellar mass Tully-Fisher relation evolves with redshift gives us information about when galaxies accumulate their stellar mass and rotation velocities.
+Any offset from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggests that the dynamical mass is in place, but the stellar mass is yet to be formed \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Gnerucci2011,Tiley2016a}.
+\\
+
+The main question arising from observations in support of and against evolution of the stellar mass Tully-Fisher relation with redshift is: Do galaxies evolve along a relation which is fixed or is there a shift in the zero-point and/or slope with decreasing redshift (i.e.
+is the connection between $V_{C}$ and the accumulating $M_{\star}$ fixed at all times)?
+We'd like to know how an individual, unperturbed point, representing a typical rotation-dominated SFG allowed to evolve without mergers, would move around the $V_{C}$ vs.
+$M_{\star}$ plane over 12 Gyr of purely secular evolution.
+
+Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010}.
+However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
+At $z\sim 3$ observations are limited and in \cite{Gnerucci2011} an offset of -1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample defined in \cref{subsec:AMAZE} consistent with the $z\sim0$ relation.
+\\
+
+We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of figure \ref{fig:tf_relation}.
+In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
+The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
+We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
+These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ \citep{Reyes2011}, for a sample of $z<0.1$ disks in a similar mass range to KROSS and traced with H$\alpha$ emission.
+In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of figure \ref{fig:tf_relation}.
+The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these limits.
+\\
+
+The rotation dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\sim 0.9$ relation, but perhaps with a slight tendency to lie below the relation.
+The dispersion dominated KDS galaxies sit clearly separated and below the $z\sim0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\sim0.9$ dispersion dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
+We plot also the five $z\sim3$ galaxies from the AMAZE clean sample, which are consistent within the scatter with the $z\sim0.9$ relation.
+
+Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\sim0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
+Similarly in \cite{Cresci2009} evolution of the normalisation of the stellar mass Tully-Fisher relation is observed at $z\sim2$ using only robust rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5$.
+In both cases the observed evolution is mainly the result of omitting rotationally dominated galaxies with lower $V_{C}$ values.
+Conversely, fitting the stellar mass Tully-Fisher relation through a full sample including dispersion dominated galaxies would shift the zero-point in the opposite sense.
+
+With the inclusion of the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\sim0.1$ and $z\sim3.5$.
+However as we will show in \cref{subsec:rdf_v_over_sigma} the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.
+
+\subsubsection{The evolution of maximum circular velocity}\label{subsubsec:v_evolution}
 
@@
         \centering
-        \includegraphics[height=3.5in]{tully_fisher_standard_log.png}
+        \includegraphics[height=3.5in]{sigma_versus_mass.png}
     \end{subfigure} \hspace{0.4cm}
@@
         \centering
-        \includegraphics[height=3.5in]{tully_fisher_s0_log.png}
+        \includegraphics[height=3.5in]{sigma_evolution.png}
     \end{subfigure}
-    \caption{In the left panel we plot log($V_{C}$) vs.
-$M_{\star}$, i.e.
-the inverted stellar mass Tully-Fisher relation, for the isolated field sample, plotting rotation dominated galaxies in red and dispersion dominated galaxies with with clear symbols.
-    Also plotted with the solid green line is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex error on the fit.
-    This $z\sim0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in Reyes 2011.
-    The rotation dominated KDS galaxies also show no evolution from this relation within the errorbars, with the dispersion dominated galaxies scattering below the relation.
-    This highlights the need for careful sample selection when constructing this relation and explains the low KDS mean $V_{C}$ value as a consequence of averaging over a sample with a high fraction of dispersion dominated galaxies.
-    In the right panel we plot the $S_{0.5}$ vs.
-$M_{\star}$ relation using the same symbol choice, with $S_{0.5}$ accounting for a contribution to the total dynamical mass from non-circular motions as traced by $\sigma_{int}$.
-    We plot also the K07 relation with the black dashed line, and find that the KDS galaxies agree with this, showing much less separation between the rotation and dispersion dominated galaxies and with less scatter than in the left panel.
-    We caution against over-interpretation of this result, since it is unclear what the physical origins of the random motions traced by $\sigma_{int}$ are, and the extent to which they are contributing to support dynamical mass.
-    In both panels the y-axis errors show the uncertainties derived for each galaxy, whereas the black errorbar in the bottom left gives the representative 0.2 dex error in measuring $M_{\star}$ for each galaxy from the SED fits.}
-    \label{fig:tf_relation}
-\end{figure*}
-
-In the $\Lambda$CDM paradigm the smTFR relates the angular momentum of the dark matter halo within which disk galaxies reside to the $M_{\star}$ content of these galaxies.
-Angular momentum in the halo, which is in turn affected by accretion of gas from the IGM, is transferred to the disk \citep{Fall1983}, where the gas then cools radiatively over time, forming the stellar population of the galaxy.
-Observing the smTFR at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies.
-In principle, studying whether the smTFR evolves with redshift gives us information about how galaxies accumulate their stellar mass and rotation velocities, with offsets from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggesting that the dynamical mass is in place, but the stellar mass is yet to be formed.
-\\
-
-The main question arising from observations in support of and against evolution of the smTFR with redshift is: Do galaxies evolve along a smTFR which is fixed or is there a shift in the zero-point and/or slope with decreasing redshift (i.e.
-is the connection between $V_{C}$ and the accumulating $M_{\star}$ fixed at all times)?
-Essentially we'd like to know how an individual, unperturbed point, representing a typical rotation-dominated SFG allowed to evolve without mergers, would move around the $V_{C}$ vs.
-$M_{\star}$ plane over 12Gyr of purely secular evolution.
-Connected to this also is the idea of progenitor bias, in that the SFGs we are selecting and comparing between $z\sim0-3.5$ may not form an evolutionary cohort, with the quenching of SF accuring at a particular mass scale \citep[e.g.][]{Keres2005,Dekel2006,Peng2010}, leading to morphological and dynamical transformation.
-\\
-
-The smTFR has been studied numerous times between $0.5 < z < 2$, giving results consistent with zero evolution of the slope and zero-point \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Harrison2017}.
-Others have reported that as redshift increases, the smTFR shifts towards lower masses at fixed rotation velocity, for example in \cite{Puech2008,Puech2010} where a -0.34 dex log$(M_{\star})$ offset is observed at $z\sim0.6$, in the \cite{Tiley2016a} KROSS sample at $z\sim0.9$ with a -0.41 dex shift (although in this work a stricter cut than in H17 of $V_{C}/\sigma_{int} > 3$ is applied), in \cite{Cresci2009} a -0.41 dex offset is observed at $z\sim2$ (although the galaxies used to compute this were the highest fidelity rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5)$ and in G11 an offset of -1.29 dex is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample consistent with the $z\sim0$ relation.
-\\
-
-To demonstrate the relationship between $V_{C}$ and $M_{\star}$ in individual KDS galaxies from the isolated field sample, we plot in the left panel of figure \ref{fig:tf_relation} the inverted smTFR.
-In this plane, $V_{C}$, a tracer of the dynamical mass of the system, is plotted as a function of the luminous mass for the KDS modelling sample.
-In H17, the smTFR relation is fit to $\sim400$ SFGs at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$ and with $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, similar to the KDS galaxies.
-The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
-We plot this best fit relation with the solid green line, with the green shaded region giving the typical uncertainty on the fit of 0.2 dex along the velocity axis.
-These parameters are consistent with coefficients measured in the local universe $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, from \cite{Reyes2011}, in which the dynamics of a sample of $z<0.1$ disks in a similar mass range to KROSS are traced with H$\alpha$ emission.
-In this study $V_{C}$ has been extracted at the same radius and we plot this local relation as the dashed black line in the left panel of figure \ref{fig:tf_relation}.
-The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$suggests that there is no evolution in the smTFR between these limits. \\
-
-The rotation dominated KDS galaxies are broadly consistent within the errorbars with the H17 fit, showing a tendency to lie below the relation.
-The dispersion dominated KDS galaxies sit clearly separated and below the H17 relation but with a consistent slope, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in H17 and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We do not attempt to fit through our data, due to the relatively narrow mass range spanned by the points and conclude that there does not appear to be evolution in the zero-point of the smTFR between $z\sim1-3.5$ for rotation-dominated galaxies as traced by KROSS and KDS.
-\\
-
-This result is a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed as a result of omitting rotationally dominated galaxies with lower $V_{C}$ values (as is also the case in \cite{Cresci2009} with the high fidelity disk sample).
-Conversely, fitting the smTFR through a full sample including dispersion dominated galaxies would shift the zero-point in the opposite sense.
-The conclusion from this work is that the smTFR appears to show no evolution across the bulk of cosmic history when the measurement of dynamical properties and the selection of rotation dominated galaxies are performed consistently.
-This comes with the caveat that it is not clear whether main sequence SFGs at difference redshift slices can be considered to form an evolutionary sequence. \\
-
-For completeness we also include the $S_{0.5} = \sqrt{0.5V_{C}^{2} + \sigma_{int}^{2}}$ vs.
-$M_{\star}$ relation described throughout \cite[K07][]{Kassin2007} in the right panel of figure \ref{fig:tf_relation} (which is consistent with the absorption-line-based $M_{\star}$ Faber-Jackson relation for nearby elliptical galaxies), where we plot $S_{0.5}$ vs.
-$M_{\star}$.
-This is connected to the idea that the rotation velocities alone may not be a good tracer of the total dynamical mass, with $S_{0.5}$ accounting for the contribution to the dynamical mass from non-circular motions.
-In K07, using $S_{0.5}$ reduced the scatter in the TFR out to $z\sim1.2$, which they attribute to the inclusion of galaxies with peculiar kinematics in the sample with reduced rotation velocities in relation to their stellar mass.
-$S_{0.5}$ has been studied in both C09 and G11, with both reporting an evolution of the K07 trend towards lower $M_{\star}$ at fixed $S_{0.5}$, which is taken as further evidence for the evolution of the smTFR.
-In the right panel of figure \ref{fig:tf_relation} the KDS galaxies agree with the K07 relation within the errorbars, with reduced scatter in comparison to the smTFR in the left panel, suggesting that there is no evolution in $S_{0.5}-M_{\star}$ relation.
-The symbol convention is the same as in the left panel and the division now between the rotation and dispersion dominated galaxies is no longer clear. 
-Considering the increase in observed $\sigma_{int}$ values over cosmic time (discussed in \cref{subsec:redshift_evolution}), this suggests that there is an interplay between the $V_{C}$ values and $\sigma_{int}$ traced by ionised gas emission lines as discussed in \cite{Kassin2012}.
-We caution against over-interpretation of this result, since the origin of $\sigma_{int}$ and the extent to which this quantity traces dynamical mass is unclear, however this trend adds to the evidence that $V_{C}$ alone is an insufficient tracer of the total dynamical mass at this redshift.
-\\
-
-The smTFR derives directly from the virial theorem, in which changes to the dynamical mass are driven by changes in both the sizes and velocities of galaxies, prompting authors recently \citep[e.g.][]{Cortese2016,Contini2015a,Burkert2016a,Harrison2017,Swinbank2017} to study the connection between $M_{\star}$ and specific angular momentum, $j_{s} \propto R_{1/2}V_{C}$, with this possibly a more fundamental quantity to describe galaxy evolution.
-We briefly discuss the specific angular momentum of the KDS galaxies in \cref{subsec:ang_mom}, continuing now to study the virial masses of the isolated field sample computed from their derived rotation velocities.
-
-\subsection{Lack of virial Mass}\label{subsec:dynamical_masses}
+    \caption{{\it Left:} We plot the intrinsic velocity dispersion against stellar mass for the rotation and dispersion dominated isolated field sample galaxies, along with the AMAZE Clean sample.
+    The $\sigma_{int}$ values are typically distributed between $40-90kms^{-1}$ and show no clear correlation with stellar mass, highlighting the complicated relationship between these two quantities.
+    {\it Right:} We present a compilation of literature $\sigma_{int}$ values plotted against redshift for surveys spanning $0 < z < 4$.
+    The mean $\sigma_{int}$ values increase from $\sim 15kms^{-1}$ in the local universe to $> 70kms^{-1}$ at $z > 3$.
+    The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values and in each case for $V_{C} = 150kms^{-1}$.
+    These are intended as indicators of the way in which $\sigma_{int}$ evolves in galaxies in different mean $M_{\star}$, where this on average gives an indication of the extent to which the stellar population has been accumulated, which may provide increased stability for an extended rotating disk.
+    The KDS datapoint appears to be consistent with the scenario proposed in previous work, whereby the mean $\sigma_{int}$ increases over cosmic time, with large scatter between individual galaxies, as a result of increased gas fractions and more efficient accretion of cold gas.
+    The vertical location of the mean datapoints in this plane are mediated by the mean $M_{\star}$ of each survey, which is itself connected to the mean gas fraction.} 
+    \label{fig:sigma_and_v_sigma_w_redshift}
+\end{figure*}
+
+In the right panel of figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see \cref{app:comparison_samples}) and KDS isolated field sample to highlight two observations:
+\begin{itemize}
+    \item At each redshift slice the $V_{C}$ distributions are extremely broad.
+    \item The mean isolated field sample $V_{C}$ value is less than reported in the comparison samples with similar mean $M_{\star}$ values.
+    This is a result of averaging over a sample containing a higher fraction of dispersion dominated galaxies.
+\end{itemize}
+
+In a rotationally supported system, the circular velocity is set by the requirement to support the total mass in the system, i.e.
+the combination of gas mass, stellar mass and dark matter mass, against gravitational collapse.
+$V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
+Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}[M_{\odot}])=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of gas mass and dark matter mass would raise this estimate).
+Indeed this value is similar to the mean $V_{C}$ value found in the KROSS sample for $log(M_{\star}[M_{\odot}])=10.0$ galaxies at $z\sim1$. \\
+
+In the right panel of figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
+It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in \cref{app:comparison_samples}) are directly comparable.
+The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
+\\
+
+The KDS mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
+The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
+This is seen in the left panel of figure \ref{fig:tf_relation} where the dispersion dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
+
+We proceed to consider the cause of the high number of dispersion dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
+Further than this, there are some galaxies where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
+see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}[M_{\odot}])=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
+This suggests that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Tacconi2013,Wisnioski2015}.
+These ideas are explored in the following sections.
+
+\subsection{Velocity dispersions}\label{subsec:results_velocity_dispersions}
+
+In the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation dominated classes, along with the AMAZE Clean sample galaxies in the $\sigma_{int}$ vs.
+$M_{\star}$ plane.
+This is an interesting relationship to explore as it has been suggested that rotational velocity alone may not be a good tracer of total dynamical mass at high-redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Kassin2012}.
+However the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
+All of these processes are also more prevalent at high-redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Wisnioski2015}, leaving $\sigma_{int}$ as a challenging property to interpret. \\
+
+We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high-redshift.
+The beam-smearing corrected $\sigma_{int}$ values, with distribution median, 16th percentile and 84th percentile equal to $71.0kms^{-1}$, $48.0kms^{-1}$ and $85.4kms^{-1}$ respectively, are larger than in the local universe where typically $\sigma_{int} = 10-20kms^{-1}$ \citep{Epinat2008a} (see \cref{subsubsec:sigma_evolution} and \cref{sec:discussion} for a discussion).
+Generally the dispersion dominated galaxies have higher $\sigma_{int}$ values, however the rotation dominated galaxies also span the full distribution width.
+
+\subsubsection{The evolution of velocity dispersion}\label{subsubsec:sigma_evolution}
+
+In the right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
+The values increase sharply from $\sigma_{int} \sim 10-20kms^{-1}$ as traced by $z\sim0$ measurements of typical SFGs to $\sigma_{int} \sim 30-60kms^{-1}$ at $z\sim1$ to $\sigma_{int} \sim 40-90kms^{-1}$ at $z\sim3$.
+
+In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR.
+Using observed constraints for these properties \citep{Tacconi2013,Tacconi2017} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
+The relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
+In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.
+\\
+
+The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 150kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
+The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ and $V_{C}$ in the equation shown in the top right of the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
+The tracks plotted in figure \ref{fig:sigma_and_v_sigma_w_redshift} give a rough indication of how $\sigma_{int}$ evolves in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
+
+We proceed now to consider both the rotation velocities and velocity dispersions in tandem by considering $V_{C}/\sigma_{int}$ and the rotation dominated fraction of galaxies in the isolated field sample.
+
+\subsection{$V_{C}/\sigma_{int}$ and the rotation dominated fraction}\label{subsec:rdf_v_over_sigma}
 
 \begin{figure}
-\centering
-\includegraphics[width=0.49\textwidth]{rv_squared.png}
-\caption{We plot the ratio $M_{vir}/M_{\star}$ computed using only rotation velocities (Eq.
-13) for the isolated field sample vs.
-$M_{\star}$, with the black line indicating equality between the two quantities.
-The red symbols show the galaxies with $V_{C}/\sigma_{int} > 1$ and the clear symbols show the galaxies with $V_{C}/\sigma_{int} < 1$, forming a sequence with lower M$_{vir}$ values that the rotation domianted galaxies.
-The majority of the points lie in the unphysical $M_{vir} < M_{\star}$ region.
-This highlights the potential for a combination of random motions, traced by $\sigma_{int}$, and ordered rotation to play a role in supporting the total dynamical mass, an expression for which is given by equation \protect\ref{eq:dyn_mass_sigma} in the text.}
-\label{fig:dyn_masses}
+    \centering \hspace{-1.13cm}
+    \includegraphics[width=0.49\textwidth]{v_over_sigma_versus_mass.png}
+    \caption{The distribution of galaxies in the $V_{C}$/$\sigma_{int}$ vs. $M_{\star}$ plane is shown for the isolated field sample, along with for the galaxies in the AMAZE Clean sample.
+    We mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies in this panel, finding that more massive galaxies (e.g.
+$log(M_{\star}[M_{\odot}]) > 9.7$) are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.}
+    \label{fig:v_sig_and_v}
 \end{figure}
-
-Further evidence for the provision of gravitational support by random motion traced by $\sigma_{int}$ can be found by comparing the virial mass computed at the convovled 2R$_{1/2}$ radius, $M_{vir}$, with $M_{\star}$.
-It is expected that $M_{vir} > M_{\star}$, as the dynamics trace not only the stellar mass, but also the gas mass and dark matter mass within the radius at which $M_{vir}$ is evaluated.
-At $z \sim 3.5$ the gas reservoirs are on average a much larger fraction of the total galaxy mass than in the local universe \citep[e.g.][]{Tacconi2013,Saintonge2013,Wisnioski2015} as there has not yet been time to convert this gas mass into stellar mass and so in principle if ordered rotation is tracing the total mass in these systems, $M_{\star}$ should be clearly below $M_{vir}$.
-In figure \ref{fig:dyn_masses}, where we have computed the virial mass from the ordered rotational motions alone, as traced by $V_{C}$, following equation \ref{eq:dyn_mass_v_only}, we find that this is not the case for the isolated field sample, with $M_{vir} < M_{\star}$ for the vast majority of galaxies (particularly those with $M_{\star} > 9.5$).
-
-\begin{equation}\label{eq:dyn_mass_v_only}
-   M_{vir} = \frac{2R_{1/2}V_{C}^{2}}{G}
-\end{equation}
-
-This strongly suggests that rotational motions alone are not enough to provide gravitational support for the mass in the system and random motions contribute to provide gravitational support for some fraction of the total mass contained within these compact galaxies.
-To follow this idea we can compute the contribution to $M_{vir}$ from $\sigma_{int}$ using equation \ref{eq:dyn_mass_sigma} \citep[e.g.][]{Cappellari2006}.
-
-\begin{equation}\label{eq:dyn_mass_sigma}
-   M_{vir} = \frac{2R_{1/2}V_{C}^{2}}{G} + \frac{\beta R_{1/2}\sigma_{int}^{2}}{G}
-\end{equation}
-
-In general the amount gravitational suport provided by $\sigma_{int}$ depends on galaxy geometry and structure \citep[e.g.][]{Cappellari2006,Belli2014}, with this dependence contained in the value of $\beta$ in equation \ref{eq:dyn_mass_sigma}.
-It is possible to derive a relationship between $\beta$ and \Sers index, a proxy for galaxy structure, as detailed in \cite{Cappellari2006} and shown in equation \ref{eq:beta_n}.
-
-\begin{equation}\label{eq:beta_n}
-   \beta(n) = 8.87 - 0.831n + 0.0241n^{2}
-\end{equation}
-
-%Now simply stating that it is possible to find the lower limit on beta to bring the dynamical masses above the stellar masses, BUT that realistically the data do not allow us to figure out the contribution from sigma so just quoted for interest
-
-We have modelled the galaxies throughout the analysis as n = 1 exponential disks, verifying this assumption throughout \cref{subsubsec:galfitting}, for which $\beta(n) \sim 8$.
-For galaxies below the $M_{vir} = M_{\star}$ line, we can find the minimum value of $\beta$ required to bring the two quantities to equality.
-In both the $V_{C}/\sigma_{int} > 1$ and $V_{C}/\sigma_{int} < 1$ samples we find that the mean $\beta_{min}\sim 5$, although we do not attempt to use $M_{vir}$ for any further analysis, merely to demonstrate the need for gravitational support that originates in random motions, as characterised by $\sigma_{int}$.
-
-\subsection{Angular Momentum}\label{subsec:ang_mom}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.8\textwidth]{angular_momentum.png}
-\caption{We plot the specific angular momentum $j_{s} \propto R_{1/2}V_{C}$ against stellar mass, $M_{\star}$, for the isolated field sample galaxies with $V_{C}/\sigma_{int} > 1$ in red and with clear symbols when $V_{C}/\sigma_{int} < 1$.
-Included also are the $j_{s} \propto M_{\star}^{\alpha}$ fits (with $\alpha = 0.6\pm0.2$) reported in H17 for the KROSS full sample in solid green and for the rotation and dispersion dominated subsamples with the dashed green lines.
-The black solid line is the fit presented in \protect\cite{Romanowsky2012} to a sample of $z=0$ disk galaxies ($\alpha = 0.51\pm0.06$), to which the KROSS relation is offset in $j_{s}$ by $\sim0.2-0.3$dex.
-The KDS rotation dominated galaxies are offset from the KROSS relation by a further $\sim0.3-0.4$dex, with the dispersion dominated galaxies scattering to lower $j_{s}$, with both KDS subsets following a roughly similar slope to KROSS and the $z=0$ sample.
-Further, we include the $j_{s} \propto (1+z)^{-1}$ evolution reported in \protect\cite{Swinbank2017} with the red solid line, using the local slope and normalisation, which appears to pass through the KDS rotation dominated galaxies.
-These results are in line with a scenario where the cosmic evolution of $j_{s}$ is driven mainly by the size evolution of galaxies as they accrete cold material to form stars from the IGM, adding to the outer components of the galaxy disks.
-The split between rotation dominated and dispersion dominated galaxies may indicate that these systems are the progenitors of local late-type and early-type galaxies respectively.}
-\label{fig:ang_mom}
-\end{figure*}
-
-In figure \ref{fig:ang_mom} we plot the specific angular momentum, j$_{\star} \equiv J/M_{\star}$ where J is the total angular momentum \citep{Fall1983}, as a function of stellar mass M$_{\star}$.
-This quantity has been described in detail in \cite{Harrison2017} section 4.3 and we refer to this for more details about the use of $j_{s}$ as measured from ionised gas kinematics as a tracer of the specific angular momentum content of SFGs.
-
-\begin{equation}\label{eq:ang_mom}
-   j_{n} = k_{n}C_{i}v_{s}R_{1/2}
-\end{equation}
-
-In equation \ref{eq:ang_mom} we list the approximate estimator for specific angular momentum described in \cite{Romanowsky2012} (their equation 6), with k$_{n}$ a numerical coefficient which depends on the \Sers index of the galaxy, n, and is approximated in equation \ref{eq:kn} (see \cite{Romanowsky2012}).
-
-\begin{equation}\label{eq:kn}
-   k_{n} = 1.15 + 0.029n + 0.062n^{2}
-\end{equation}
-
-Due to varying {\em HST} coverage and quality, it has not been possible to estimate n for all KDS galaxies.
-However we have verified throughout \cref{subsubsec:galfitting} that the GOODS-S galaxies are well described by the n = 1 exponential profile through a combination of {\tt GALFIT} and comparison to the \Sers index values reported in \cite{VanderWel2012}.
-Setting n = 1 in equation \ref{eq:kn} leaves $k_{n} = 1.19$ and we continue under this assumption analogous to in \cite{Harrison2017} (although we note that as stated in \cite{Harrison2017} setting n = 2 results in $\sim20\%$ difference in the derived $j_{s}$ values).
-In equation \ref{eq:ang_mom} $C_{i}$ is the de-projection factor, assumed to be $1/sin(i)$, and $v_{s}$ is the observed velocity at $2R_{1/2}$.
-The combination $v_{s}C_{i} \equiv V_{C}$ and we can use our measured rotation velocities to leave equation \ref{eq:ang_mom_final} as the final expression for $j_{s}$.
-
-\begin{equation}\label{eq:ang_mom_final}
-   j_{n=1} \equiv j_{s} = 1.19V_{C}R_{1/2}
-\end{equation}
-
-In figure \ref{fig:ang_mom} we plot the fit to all KROSS galaxies with the solid green line, and also the individual fits to the rotation and dispersion dominated KROSS galaxies with the dashed green and light green lines respectively.
-The fits to the full sample and rotation dominated KROSS galaxies (with fitting relation defined by log$j_{s} =  \beta + \alpha[logM_{\star} - 10.0]$) lie $\sim0.2-0.3$ dex beneath the $z\sim0$ relation from \cite{Romanowsky2012}, in contrast to the smTFR, with the dispersion dominated galaxies scattering around much lower $j_{s}$ values.
-This offset is explained to be a consequence mainly of the size evolution of the disks of SFGs over the redshift range $z=0-0.9$.
-The local and KROSS relations have comparable slopes, with $\alpha_{z=0}=0.51\pm0.06$ and $\alpha_{z=0.9}=0.6\pm0.2$, in agreement with other studies of the $j_{s}-M_{\star}$ relation \citep{Cortese2016,Contini2015a,Burkert2016a,Swinbank2017}, and also in agreement with predictions for the slope of the relationship between dark matter specific angular momentum and the halo mass (i.e.
-$j_{halo} \propto M_{halo}^{2/3}$ \citep[e.g.][]{Barnes1987}).
-This is widely regarded as a consequence of the baryonic retention of angular momentum following a period in the formation of the proto-galaxy when the dark matter and baryons were well mixed. \\
-
-The rotation dominated KDS galaxies form a sequence $\sim 0.3-0.4$ dex beneath the KROSS relation, and with similar slope, however the slope is not well constrained due to the scatter and sparsity of the dataset.
-The dispersion dominated KDS galaxies form a sequence with similar slope but offset to lower still $j_{s}$ values.
-We plot also the $j_{s} \propto (1+z)^{-1}$ evolution line reported in \cite{Swinbank2017} (using the local slope and normalisation from \cite{Romanowsky2012}), which the rotation dominated KDS galaxies appear to roughly follow.
-\\
-
-These results suggest that there is a continual drop in the specific angular momentum of SFGs with increasing redshift, as governed by the evolution of disk sizes \citep[e.g.][]{Trujillo2007} (see figure \ref{fig:morpho-distributions}) and that the relationship between the angular momentum of the baryons and the halos is constant over time.
-Conversely, the angular momentum of SFGs will increase with decreasing redshift as accretion of cold gas from the IGM which fuels star formation and tidal disruption from satellite galaxies or major mergers conspire to grow disk sizes over time \citep{Trujillo2007,Buitrago2008,VanderWel2014a}.
-Additonally since we observe a bimodal distribution of the rotation and dispersion dominated KDS galaxies in the $j_{s}-M_{\star}$ plane, we are plausibly observing the progenitors of late-type and early-type galaxies at $z\sim3.5$ as revealed by their kinematic signatures, consistent with the idea that early-type galaxies began their lives with less total angular momentum available to them.
-
-\subsection{The redshift evolution of dynamical properties}\label{subsec:redshift_evolution}
-We proceed to investigate further the low rotation velocities and large velocity dispersions observed in the isolated field sample in \cref{subsec:rdf_v_over_sigma} by placing them in cosmological perspective using the comparison samples (see \cref{app:comparison_samples} for overview and symbol definitions).
-We have made use of the tabulated data and errors in these studies to derive the datapoint values and errorbars plotted in figure \ref{fig:rdf_and_v_sigma_w_redshift} and \ref{fig:sigma_and_v_sigma_w_redshift} in a consistent way, which is to take the fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples (i.e.
-we do not want the derived values with extremely large errors to dominate the averages).
-The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
-\\
-
-In the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
-
-\subsubsection{The evolution of the rotation dominated fraction}\label{subsubsec:RDF_evolution}
 
@@
     \end{subfigure}
-    \caption{In panel (a) $V_{C}/\sigma_{int}$ is plotted against redshift for surveys spanning $0 < z < 4$.
+    \caption{{\it Left:} $V_{C}/\sigma_{int}$ is plotted against redshift for the comparison samples spanning $0 < z < 4$.
     The filled symbols show the sample mean values, with the KDS mean at $z\sim3.5$ plotted with the red circle, with black errorbars representing the statistical error on the mean computed using bootstrap re-sampling as described in the text.
-    The sample medians and statistical errors on these values are plotted with the coloured and grey horizontal bars, falling in each case below the mean, suggesting that large individual $V_{C}/\sigma_{int}$ measurements may bias the sample mean high.
-    We also plot the 16th and 84th percentiles of the distribution of individual $V_{C}/\sigma_{int}$ measurements as shaded regions to give an indication of the range of values measured in each survey, and indicate the mean stellar mass of each survey in the legend.
-    Lack of tabulated values for KMOS$^{3D}$ and SINS restricted us from computing the $V_{C}/\sigma_{int}$ values in a consistent way, and so we plot the sample means without errorbars.
-    The DYNAMO point and errors are plotted in white to highlight the difference in selection criteria, with the low redshift galaxies chosen to have similar properties to those at $z\sim2$.
-    In the left panel we see a clear decline in the mean $V_{C}/\sigma_{int}$ values with redshift, but with wide ranges in the individual measurements.
+    The sample medians and statistical errors are plotted with the coloured and grey horizontal bars, falling in each case below the mean, suggesting that large individual $V_{C}/\sigma_{int}$ measurements may bias the sample mean high.
+    We also plot the 16th and 84th percentiles of the distribution of individual $V_{C}/\sigma_{int}$ measurements as shaded regions to give an indication of the range of values measured in each survey.
+    We see a clear decline in the mean $V_{C}/\sigma_{int}$ values with redshift, but with wide ranges in the individual measurements.
     There is also a connection to the mean $M_{\star}$ of the surveys, with larger mean $M_{\star}$ surveys reporting higher mean $V_{C}/\sigma_{int}$.
-    We plot the associated RDF, with this deriving from the fraction of galaxies above the $V_{C}/\sigma_{int} = 1$ dashed line plotted in the right panel.
-    The narrow shaded regions represent the maximum and miminum RDF, computed as described in the text.
-    It appears that the RDF drops from $\sim 100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\sim 40\%$ at z $\sim 3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher RDFs.
-    Presumably this decline would continue out to the higher redshifts in which galaxies really are assembling their first stellar components are not supported by ordered rotation.
+    {\it Right:} We plot the associated rotation dominated fraction, defined as the fraction of galaxies in each sample with $V_{C}/\sigma_{int} > 1$.
+    The narrow shaded regions represent the maximum and miminum RDF, computed as described in \protect\cref{app:comparison_samples}.
+    It appears that the rotation dominated fraction drops from $\sim 100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\sim 40\%$ at z $\sim 3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher rotation dominated fractions.
     The dot-dash line is the RDF $\propto z^{-0.2}$ cosmic decline suggested in \protect\cite{Stott2016}.
-    In both panels the surveys from which the data are drawn are denoted in the legends.
 }
@@
 
-In the left panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and in the right panel we plot the closely connected RDF both as a function of redshift for the KDS isolated field sample and the comparison samples described in \cref{app:comparison_samples}.
-In the left panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} the filled symbols and black errorbars represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
+In figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean sample for reference.
+In the local universe, disky, SFGs are observed to have $V_{C}/\sigma_{int}$ values in excess of 10 (i.e.
+the disks are `well settled'), due to the decline of velocity dispersion across cosmic time, as gas fractions and disk turbulence decrease \citep[e.g.][]{Epinat2008,Epinat2008a}.
+Clearly the isolated field sample galaxies are in a different physical regime, with mean and median $V_{C}/\sigma_{int}$ values of $1.08^{+0.18}_{-0.15}$ and $0.97^{+0.14}_{-0.11}$ respectively (see further discussion in \cref{subsubsec:RDF_evolution} and \cref{sec:discussion}).
+This is despite many of the dispersion dominated galaxies showing clear velocity gradients across the observed velocity maps (\cref{app:kinematics_plots}), with the arctangent model providing a good fit to the rotation curves.
+This suggests that although rotational motions are present within the disks, they are small or comparable with the elevated $\sigma_{int}$ values observed throughout the $z \sim 3.5$ sample. \\
+
+The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies is marked on figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}[M_{\odot}]) > 9.7$ which are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
+The Rotation Dominated Fraction (RDF), calculated with respect to the full field sample of 38 galaxies, is 0.34$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
+We interpret these results in the context of the cosmic evolution of the rotation domianted fraction using the comparison samples in \cref{subsubsec:RDF_evolution}.\\
+
+\subsubsection{The evolution of the rotation dominated fraction}\label{subsubsec:RDF_evolution}
+
+In the left and right panels of figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in \cref{app:comparison_samples}.
+The filled symbols and black errorbars in the left panel represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
 The shaded regions give the 16th and 84th percentiles of the distribution on individual $V_{C}/\sigma_{int}$ measurements, plotted here to indicate the range of measurements at each redshift slice.
-No tabulated data was available for the points plotted without errors and the clear symbols indicate comparison caveats (see \cref{app:comparison_samples}).
-In the right panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the RDF.
-These are shown with the thin grey shaded regions and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the invidual points.
-In the KMOS$^{3D}$ $z \sim 1$ sample re-analysis presented in \cite{Rodrigues2016}, a lower RDF of 69\% was recovered, despite the use of identical classification criteria.
-The recovery of this lower fraction is driven mainly by the presence of peaks in the $\sigma_{int}$ maps which do not coincide with the rotation centre, a criteria which we do not impose throughout this work and spatial offsets between the rotation centre and the centre of stellar mass.
-The KROSS $z\sim1$ RDF presented in H17 lies between the two extremes of R16 and W15 computed for the KMOS$^{3D}$ sample. \\
-
-Despite the systematic variations in measurement technique and classification criteria between the comparison samples, it is clear that the RDF, as traced simply by the $V_{C}/\sigma_{int}$ inferred from ionised gas emission lines, drops from $\sim 100\%$ of galaxies in the local universe to $\sim 2/3$ of galaxies in the $z \sim 1-2$ universe and to $\sim 1/3$ above $z \sim 3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
-This is highlighted in the right panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic RDF decline as described in \cite{Stott2016}.
+In the right panel we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the rotation dominated fraction.
+These are shown with the thin grey shaded regions and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the invidual points.\\
+
+The rotation dominated fraction, traced simply by the $V_{C}/\sigma_{int}$ ratio inferred from ionised gas emission lines, drops from $\sim 100\%$ of galaxies in the local universe to $\sim 2/3$ of galaxies in the $z \sim 1-2$ universe and to $\sim 1/3$ above $z \sim 3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
+This is highlighted in the right panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic rotation dominated fraction decline as described in \cite{Stott2016}.
+The width of the $V_{C}/\sigma_{int}$ distributions indicates the galaxy diversity at each redshift slice, driven by the collection of galaxy masses, sSFRs, gas fractions, morphologies and evolutionary states which comprise each sample.
 Scatter above and below the RDF $\propto z^{-0.2}$ evolution line may be attributed in part to the different mean stellar masses of the surveys, with those that have larger stellar masses tending to scatter above this line.
-Higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the sample RDF higher.
-The width of the $V_{C}/\sigma_{int}$ distributions indicates the galaxy diversity at each redshift slice, driven by the collection of galaxy masses, sSFRs, gas fractions, morphologies and evolutionary states which comprise each sample.
-Explanations for the mean decline of $V_{C}/\sigma_{int}$ with cosmic time have been discussed at length in other surveys \citep[e.g][]{ForsterSchreiber2009,Law2009,Wisnioski2015} and we revisit this in the following subsection.
-
-\subsubsection{The evolution of velocity dispersion}\label{subsubsec:sigma_evolution}
-
-\begin{figure*}
-    \centering \hspace{-1.3cm}
-    \begin{subfigure}[h!]{0.5\textwidth}
-        \centering
-        \includegraphics[height=3.5in]{sigma_evolution.png}
-    \end{subfigure} \hspace{0.4cm}
-    \begin{subfigure}[h!]{0.5\textwidth}
-        \centering
-        \includegraphics[height=3.5in]{v_evolution.png}
-    \end{subfigure}
-    \caption{The left presents a compilation of literature $\sigma_{int}$ values plotted against redshift for surveys spanning $0 < z < 4$.
-    The symbol convention for both the left and right panels is the same as described for the left panel of figure \protect\ref{fig:rdf_and_v_sigma_w_redshift}.
-    We note also that the Law 2009 datapoint has not been corrected for beam-smearing and so represents an upper limit on $\sigma_{int}$ for that survey. 
-    The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values, with the solid line showing $log(M_{\star}[M_{\odot}])=10.0$, the dashed line $log(M_{\star}[M_{\odot}])=10.3$ and the dot-dashed line $log(M_{\star}[M_{\odot}])=10.6$.
-    In each case the scaling relation is plotted for $V_{C} = 150kms^{-1}$.
-    These are intended as indicators of the way in which $\sigma_{int}$ evolves in galaxies in different mean $M_{\star}$, where this on average gives an indication of the extent to which the stellar population has been accumulated, which may provide increased stability for an extended rotating disk.
-    The KDS datapoint appears to be consistent with the scenario proposed in previous work, whereby the mean $\sigma_{int}$ increases over cosmic time, with large scatter between individual galaxies, as a result of increased gas fractions and more efficient accretion of cold gas.
-    The vertical location of the mean datapoints in this plane are mediated by the mean $M_{\star}$ of each survey, which is itself connected to the mean gas fraction. 
-    The right panel presents the mean, median and distributions of $V_{C}$ measurements of these surveys between $0 < z < 4$.
-    The low mean value of $V_{C}$ in the KDS isolated field sample is driven mainly by averaging over a sample which contains a higher fraction of dispersion dominated galaxies with lower rotation velocities.}
-    \label{fig:sigma_and_v_sigma_w_redshift}
-\end{figure*}
-
-The observation that $\sigma_{int}$ becomes increasingly large towards high redshift has now been firmly established in several studies, including all of those from which data has been taken to create figure \ref{fig:sigma_and_v_sigma_w_redshift}.
-\cite{Law2009} attribute the cosmic increase in $\sigma_{int}$ to much larger gas fractions at high redshift, with the gas accumulated through rapid cold-mode accretion along cosmic filaments.
+This draws again from the idea that higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the sample rotation dominated fraction higher (see \cref{sec:discussion}).
+In sum, the rotation dominated galaxies in the isolated field sample appear to conform with a redshift invariant $V_{C}$ - $M_{\star}$ relation.
+Due to increased velocity dispersions, these rotation dominated galaxies account for only $34\%$ of the field sample and so are less representative of typical star-forming galaxies at $z\sim3.5$ than at intermediate and low redshifts.
+Explanations for the increase of $\sigma_{int}$ with redshift (and hence the decline of $V_{C}/\sigma_{int}$) with cosmic time have been discussed at length in other surveys \citep[e.g][]{ForsterSchreiber2009,Law2009,Wisnioski2015} and we revisit these in the following discussion.
+
+\section{DISCUSSION}\label{sec:discussion}
+
+Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
+The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion dominated galaxies ($66\%$ of the sample).
+This increased number of dispersion dominated galaxies in comparison to at low and intermediate redshifts appears to be driven by high velocity dispersions at $z\sim3.5$.
+In this section we discuss possible physical origins for these high values.
+
+We build on both the ideas that accumulating a stellar population contributes to stabilising rotation within typical SFGs at all epochs and that rotation velocities alone may not be a good tracer of the total dynamical mass within a system.
+
+Connected to this also is the idea of progenitor bias, in that the SFGs we are selecting and comparing between $z\sim0-3.5$ may not form an evolutionary cohort, with the quenching of SF accuring at a particular mass scale \citep[e.g.][]{Keres2005,Dekel2006,Peng2010}, leading to morphological and dynamical transformation.
+\\
+
+This could either be a result of the measurement and modelling technique, which carries significant uncertainties due to modelling assumptions, the S/N of the [O~{\sc III}]$\lambda5007$ emission line even in very long integrations at this redshift, the spatial coverage of [O~{\sc III}]$\lambda5007$ may be more compact that $H\alpha$ and consequently may not probe out to the same galactic radii and the sparsity of resolution elements, or could be the result or some real physical process in the galaxies which lowers $V_{C}$ as traced by the ionised gas dynamics.
+
+however our data appear to support a scenario in which low $M_{\star}$ galaxies experience elevated random motions related to the rapid accretion of cold gas, which is partially supported gravitationally by these random motions and may contribute to the observation of low $V_{C}$ values.
+At higher $M_{\star}$ the accumulation of a stellar population provides stability, $\sigma_{int}$ decreases and $V_{C}$ increases to provide the additional gravitational support.
+These processes are mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Wisnioski2015}
+
+\cite{Law2009} observe galaxies with similarly low mean velocity shear and high velocity dispersions (the velocities are not plotted here since the tabulated values are not inclination or beam-smearing corrected) and attribute this to instabilities which occur when the cold gas becomes dynamically dominant following efficient accretion and in line with the high gas fractions observed at high-redshift.
+
+\cite{Law2009} attribute the cosmic increase in $\sigma_{int}$ to much larger gas fractions at high-redshift, with the gas accumulated through rapid cold-mode accretion along cosmic filaments.
 Systems such as these form roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk.
 Following this, $\sigma_{int}$ decreases over time as ordered rotations begin to dominate.
-\cite{Wisnioski2015} interpret the increase of $\sigma_{int}$ towards high redshift in terms of the equilibrium model, which describes the rough balance between galactic accretion, star-formation and outflows \citep[e.g.][]{Lilly2013}, deriving a scaling relation for $\sigma_{int}$ with redshift appropriate for galaxies which have formed a quasi-stable disk (see their section 5.2).
-This relation gives a prediction for $\sigma_{int}$ in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR, and using observed constraints for these properties leads to $\sigma_{int}$ predictions with redshift that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
-In both viewpoints the increased $\sigma_{int}$ values observed at high redshift are primarily the result of the prevalence and efficiency of gas inflow onto galaxies in this regime. \\
-
-In the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distribution of $\sigma_{int}$ from the comparison and KDS isolated field samples.
-The mean KDS datapoint is in agreement with the $\sigma_{int}$ scaling relation presented in W15, plotted with the grey lines for $V_{C} = 150kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$, rather than the $log(M_{\star}[M_{\odot}])=10.5$ value used in W15 (note we have also not shifted the datapoints to conform with a single $M_{\star}$ value as per W15).
-The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ and $V_{C}$ in the equation shown in the top right of the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}.
+\cite{Wisnioski2015} interpret the increase of $\sigma_{int}$ towards high-redshift in terms of the equilibrium model, which describes the rough balance between galactic accretion, star-formation and outflows \citep[e.g.][]{Lilly2013}, deriving a scaling relation for $\sigma_{int}$ with redshift appropriate for galaxies which have formed a quasi-stable disk (see their section 5.2).
 
@@
 The location of mean $\sigma_{int}$ values is therefore related to the mean $M_{\star}$ of each survey, with this being an indicator of the accumulation of a stellar population and hence the evolutionary state of the galaxies.
-The tracks plotted in figure \ref{fig:sigma_and_v_sigma_w_redshift} give a rough indication of how $\sigma_{int}$ evolves in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
-
-\subsubsection{The evolution of maximum circular velocity}\label{subsubsec:v_evolution}
-In the right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison and KDS isolated field sample to highlight two observations:
-\begin{itemize}
-    \item Different modelling and measurement techniques affect the inferred $V_{C}$ values
-    \item The KDS $V_{C}$ values appear lower than reported in lower redshift studies with similar mean $M_{\star}$ values, as a result of averaging over a sample with a higher dispersion dominated fraction
-\end{itemize}
-
-In a rotationally supported system, the magnitude of $V_{C}$ is set by the requirement to support the mass, $M_{tot}$, in the system, i.e.
-the combination of $M_{gas}$, $M_{\star}$ and $M_{DM}$, against gravitational collapse.
-$V_{C}$ increases as $M_{tot}$ increases and so we would expect the systems with larger average $M_{\star}$, assuming that these are indicative of systems with greater $M_{tot}$, to have larger $V_{C}$, which appears generally to be the case in the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
-Using the average $M_{\star}$ values and velocity extraction radius in the KDS sample, $log(M_{\star}[M_{\odot}])=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of $M_{gas}$ and $M_{DM}$ would raise this estimate).
-Indeed this estimate is similar to the mean value found in the KROSS sample for $log(M_{\star}[M_{\odot}])=10.0$ galaxies at $z\sim1$. \\
-
-In the right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
-It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in \cref{app:comparison_samples}) are directly comparable.
-The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
-In particular the $V_{C}$ parameter reported in G11 is unconstrained for several galaxies, requires large extrapolation from the data and leads to very large rotation velocities for 5/11 of their galaxies.
-The remaining 6/11 galaxies have $V_{C}$ values close to those reported for the KDS sample.
-This is a consequence of the current state of the data quality at high redshifts, and it is important to keep in mind that both $\sigma_{int}$ and $V_{C}$ are still dependent on modelling technique.
-\\
-
-The KDS mean and median values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
-This could either be a result of the measurement and modelling technique, which carries significant uncertainties due to modelling assumptions, the S/N of the [O~{\sc III}]$\lambda5007$ emission line even in very long integrations at this redshift, the spatial coverage of [O~{\sc III}]$\lambda5007$ may be more compact that $H\alpha$ and consequently may not probe out to the same galactic radii and the sparsity of resolution elements, or could be the result or some real physical process in the galaxies which lowers $V_{C}$ as traced by the ionised gas dynamics.
-We believe however that the observation of a low mean $V_{C}$ value in the KDS galaxies is primarily explainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
-This is easier to see in \cref{subsec:TF} where we have cast the rotation velocities in the context of the inverted stellar mass `Tully-Fisher Relation' \citep[smTFR;][]{Tully1977,Bell2000a}. \\
-
-It seems likely that the measurement of low $V_{C}$ values in the KDS could be at least in part a consequence of the KMOS data not having the depth to trace the outskirts of the galaxies where the rotation curve begins to flatten.
-Using the 2D arctangent function to extrapolate through the datapoints to $2R_{1/2}$ could underestimate the true $V_{C}$ if the data do not trace close to where the rotation curve begins to flatten.
-We have also assumed that the galaxies are disky in order to compute an inclination angle in each case, which is then used to correct $V_{obs}$ for viewing angle.
-At this redshift and mean $M_{\star}$, the disk assumption may not be correct, as galaxies could have more complicated structures which have not yet stabilised into rotating disks.
-However the distribution of inclination angles is consistent with observing a selection of galaxies with inclinations randomly distributed as $0^{\circ} < i < 90^{\circ}$, with the KDS mean inclination of $57.4^{\circ}$ (see \cref{subsubsection:inclination_angle}) agreeing well with the theoretical mean of $57.3^{\circ}$ \citep[for a simple derivation of this value see e.g.
-the appendix in][]{Law2009}.
-\\
-
-There are some galaxies where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
-lbg\_24 with $log(M_{\star}[M_{\odot}])=9.75$), yet the inferred $V_{C}$ is smaller than $\sigma_{int}$.
-This, in combination with figure \ref{fig:dyn_masses}, suggests that the velocity dispersion could be responsible for providing partial dynamical support in these systems.
-\cite{Law2009} observe galaxies with similarly low mean velocity shear and high velocity dispersions (the velocities are not plotted here since the tabulated values are not inclination or beam-smearing corrected) and attribute this to instabilities which occur when the cold gas becomes dynamically dominant following efficient accretion and in line with the high gas fractions observed at high redshift.
-
-We caution that at high redshift these $V_{C}$ measurements are challenging for the reasons stated above, however our data appear to support a scenario in which low $M_{\star}$ galaxies experience elevated random motions related to the rapid accretion of cold gas, which is partially supported gravitationally by these random motions and may contribute to the observation of low $V_{C}$ values.
-At higher $M_{\star}$ the accumulation of a stellar population provides stability, $\sigma_{int}$ decreases and $V_{C}$ increases to provide the additional gravitational support.
-These processes are mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Wisnioski2015}.
+
+We suggest that as galaxies accumulate their stellar populations and exhaust their gas supplies, this leads to a more stable rotating disk and hence evolution towards higher $V_{C}/\sigma_{int}$ values.
 
 \section{CONCLUSIONS}\label{sec:conclusion}
-We have presented new measurements of 77 main sequence SFGs spanning both cluster and field environments at $z\sim3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
+We have presented new measurements of 77 main sequence star forming galaxies spanning both cluster and field environments at $z\sim3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
 These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}[M_{\odot}])< 10.5$ typical main sequence galaxies at these redshifts.
-By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated probable interacting galaxies from the sample, finding consistent merger rates in the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
-We proceeded to make made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (\cref{app:comparison_samples} and table \ref{tab:evolution_numbers}).
+By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding consistent merger rates in the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
+We make made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (\cref{app:comparison_samples} and table \ref{tab:evolution_numbers}).
 The main conclusions of this work are summarised as follows:
@@
     \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in \cref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to boost random motions within high redshift galaxies.
+    This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to boost random motions within high-redshift galaxies.
     \item We plot the mean $V_{C}$ values of the comparison samples and the KDS isolated field sample, finding significant diversity in $V_{C}$ measurements in each survey (right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}).
@@
 \bibliography{/Users/owenturner/Documents/PhD/KMOS/Latex/Bibtex/library.bib}
+\clearpage
 
@@
 We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
-These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
+These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have been beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
 We use tabulated data $\sigma_{int}$ data in L09 to compare this distribution with other results, but make no comparisons with the observed velocity-shear values.
@@
 
-\section{Kinematic Parameters Error Estimates}\label{app:kin_error_estimates}
+\section{Intrinsic parameter distributions}
+
+\begin{figure}
+\centering \hspace{-1.13cm}
+\includegraphics[width=0.49\textwidth]{sigma_versus_v.png}
+\caption{{\it Left:} The distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
+The AMAZE Clean sample galaxies (see \protect\cref{subsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
+There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement.
+The $V_{C}/\sigma_{int} = 1$ line divides the galaxies classified as rotation dominated and dispersion dominated.
+The galaxy s\_sa22a-M38, classified here as a merger but classified in \protect\cite{Gnerucci2011} as a rotating galaxy with $V_{C} = 346kms^{-1}$ is marked on the plot.}
+\label{fig:intrinsic_parameters}
+\end{figure}
+
+In figure \ref{fig:intrinsic_parameters} we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane. 
+The $V_{C}$ = $\sigma_{int}$ line roughly bisects the KDS sample, and separates the dispersion and rotation dominated galaxies by definition.
+The isolated field sample galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is good agreement between the KDS and AMAZE Clean samples.
+The galaxies in the AMAZE Unconstrained sample generally have much larger $V_{C}$ values despite occupying a similar stellar mass range to our isolated field sample, with this being a consequence of large model extrapolations beyond the observed data.
+We follow the bootstrapping procedure described in \cref{app:comparison_samples} to compute error weighted averages and statistical errors.
+
+\section{Kinematic parameters error estimates}\label{app:kin_error_estimates}
 
@@
     \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22b-c10_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_14_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_23_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_bs010545_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_93_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_lab7_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-aug96m16_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c49_grid_paper.png}
+
+    \phantomcaption
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
     \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-md23_grid_paper.png}
@@
     \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-m38_grid_paper.png}    
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c47_grid_paper.png}
 
@@
 
+    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c30_grid_paper.png}
     \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c35_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c30_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-aug96m16_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c49_grid_paper.png}
-
-    \phantomcaption
-
-\end{figure*}
-
-\begin{figure*}\ContinuedFloat
-    \centering
-
-    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_14_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_23_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_bs010545_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_n_c47_grid_paper.png}
-
-    \phantomcaption
-
-\end{figure*}
-
-\begin{figure*}\ContinuedFloat
-    \centering
-
-    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_93_grid_paper.png}
 

### 2017-03-10 paper.tex
draft version 2 sent to co-authors

@@
 %O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
+%R. K. Cochrane,$^{1}$
 %M. Cirasuolo,$^{1,2}$
 %C. M. Harrison,$^{2,3}$
-%J. Dunlop,$^{1}$
-%R. J. McLure,$^{1}$\newauthor
+%J. Dunlop,$^{1}$\newauthor
+%R. J. McLure,$^{1}$
 %A. M. Swinbank$^{4,3}$
@@
 \begin{abstract}
-We present dynamical measurements for 77 main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
-These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift universe.
+We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
+These measurements constrain the internal dynamics, the intrinsic velocity dispersions $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift Universe.
 We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
-The KDS mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with the increase of $\sigma_{int}$ with redshift reported across the comparison samples.
-However we find that only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
+The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
+However only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
 The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e.
-$V_{C}-M_{\star}$) relation (the inverse of the stellar mass Tully-Fisher relation), although a smaller fraction of the galaxies sit on the relation due to the increase in the dispersion dominated fraction.
-The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this decline the result of the gradual size evolution of the star-forming population over cosmic time.
-Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
-These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
+$V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion dominated fraction.
+These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
 \end{abstract}
@@
 
-In the hierarchical collapse scenario \citep{Rees1977,Fall1980}, matter density perturbations, which originate from some set of cosmological initial conditions, grow over time before condensing out of the general expansion to form dark matter halos \citep{Silk1968,Peebles1970}.
-It is at the centre of these halos that baryons collect, cool and begin to form stars (\citealt{Birnboim2003,Keres2005,Dekel2006} and see e.g.
-\citealt{Mo2010} for a recent review), with these systems constituting the first galaxies.
-One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue \citep[e.g.][]{Fall1983}.
-
-It has been observationally determined that the galaxy population is bimodal in many physical properties at each redshift slice at which it is studied \citep[e.g.
+The galaxy population at all redshifts appears to be bimodal in many physical properties \citep[e.g.
 as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies.
 For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
-This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
-The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
-At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
+This correlation, or `main sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
+The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
+At each redshift slice it has been suggested that galaxies on the main sequence evolve secularly as regulated by their gas reservoirs, and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
 This assumes that high-redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
 how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
+
 The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs.
@@
 Recent cosmological volume simulations are able to resolve the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
-Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations which must be reproduced across cosmic time.
+Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
 The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
@@
 This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
-There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Tiley2016a,Harrison2017}.
+
+There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017}.
 In both cases, systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
@@
 \subsubsection{GOODS-S}\label{subsubsec:sample_selection_goods}
-Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see Table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
 We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
@@
 \subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
-A single CLUSTER environment pointing (SSA22-P1; see table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
+A single CLUSTER environment pointing (SSA22-P1; see Table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
 Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
@@
 In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
-In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in table \ref{tab:pointings}.
+In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}.
 \footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}
@@
 \subsection{Observations and data reduction}\label{subsubsec:observations_and_dr}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.8\textwidth]{main_sequence_hor.png}
+\caption{We plot the location of 48 KDS galaxies (see \cref{subsubsec:sample_summary}) in the SFR versus M$_{\star}$ plane, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
+Also plotted with the small grey points are individual SFGs from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
+The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
+We include the MS relation described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line. 
+Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3$ SFGs.}
+\label{fig:main_sequence}
+\end{figure*}
+
 Our data for the 77 KDS targets were observed using KMOS.
@@
 We prepare each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
-For the four pointings described above and summarised in table \ref{tab:pointings}, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
+For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
 This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\
@@
 In GOODS-S-P1 and GOODS-S-P2 the median K-band seeing was $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
-We observed 19-21 targets in each field (see table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
+We observed 19-21 targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
 \\
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.8\textwidth]{main_sequence_hor.png}
-\caption{We plot the location of 48 KDS galaxies (see \cref{subsubsec:sample_summary}) in the SFR versus M$_{\star}$ plane, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
-Also plotted with the small grey points are individual SFGs from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
-The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
-We include the MS relation described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line. 
-Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3$ SFGs.}
-\label{fig:main_sequence}
-\end{figure*}
-
 \subsubsection{Data reduction}\label{subsubsec:datareduction}
-The data reduction process primarly makes use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
-In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.
-
-The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
-An additional step which is not part of the standard reduction process is carried out at this stage, which is to address readout channel bias.
-Differences in the readout process across each 64 pixel wide channel on the detector image lead to a varying flux baselines in these channels.
-We correct back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.
-
-Standard star observations were carried out on the same night as the science observations and are processed in an identical manner to the science data.
-Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
-Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations.
-\\
-
-Sky subtraction is enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
-Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the K-band greatly reduces the sky-line residuals.
-We monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged K-band seeing rises above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
-The PSF is determined from fitting the K-band collapsed, stacked standard star cube in each pointing with an elliptical gaussian and the values are reported in table \ref{tab:pointings}.
-The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
-\\
-
-We stack all 300s exposures for each galaxy which pass seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
-We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
-To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
-\\
-
-The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det}$, the number with spatially resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
 
@@
 
+The data reduction process primarly makes use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
+In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.
+
+The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
+An additional step which is not part of the standard reduction process is carried out at this stage, which is to address readout channel bias.
+Differences in the readout process across each 64 pixel wide channel on the detector image lead to a varying flux baselines in these channels.
+We correct back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.
+
+Standard star observations were carried out on the same night as the science observations and are processed in an identical manner to the science data.
+Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
+Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations.
+\\
+
+Sky subtraction is enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
+Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the K-band greatly reduces the sky-line residuals.
+We monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged K-band seeing rises above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
+The PSF is determined from fitting the K-band collapsed, stacked standard star cube in each pointing with an elliptical gaussian and the values are reported in Table \ref{tab:pointings}.
+The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
+\\
+
+We stack all 300s exposures for each galaxy which pass seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
+We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
+To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
+\\
+
+The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det}$, the number with spatially resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+
 \subsection{Stellar masses and SFRs}\label{subsec:stellar_masses_and_sfrs}
@@
 For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
-In figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
+In Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
 We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.
@@
 At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
-This allows us to look at the morphological properties of typical star-forming galaxy populations at two redshift slices in comparison with those determined for the KDS sample.
+This allows us to investigate the morphological properties of typical star-forming galaxy populations at two redshift slices in comparison with those determined for the KDS sample.
 The imaging also helps to distinguish multiple `merging' components with small angular separations from objects which are morphologically isolated, which we discuss in \cref{subsubsection:spaxel_fitting} and \cref{subsec:morpho-kin-class} where we refine our sample for dynamical analysis.
@@
 Siana: PID 12527).
-The {\em HST} coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is concentrated on SSA22-CLUSTER and so we resort to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage listed in table \ref{tab:phys-props}).
+The {\em HST} coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is concentrated on SSA22-CLUSTER and so we resort to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage listed in Table \ref{tab:phys-props}).
 \\
@@
 This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
-Example {\em HST} images and {\tt GALFIT} outputs are given in figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout \cref{app:kinematics_plots}.
+Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout \cref{app:kinematics_plots}.
 
@@
  \hline
-b012141\_012208 & 03:32:23 & -27:51:57 & 3.471        & 24.12  & 10.16 & 59.0 & 0.36        & 72.0        & 9.0     & 1.57      \\
-b15573          & 03:32:28 & -27:51:00 & 3.583        & 23.6   & 10.37 & 27.0 & 0.28        & 78.0        & 146.0   & 0.52      \\
-bs006516        & 03:32:15 & -27:50:46 & 3.215        & 23.94  & 9.85  & 14.0 & 0.5         & 61.0        & 146.0   & 1.91      \\
-bs006541        & 03:32:15 & -27:52:05 & 3.475       & 23.44  & 10.19 & 18.0 & 0.44        & 66.0        & 168.0   & 1.83      \\
-bs008543        & 03:32:18 & -27:50:50 & 3.474        & 22.73  & 10.67 & 42.0 & 0.5         & 61.0        & 67.0    & 1.59      \\
-bs009818        & 03:32:20 & -27:53:01 & 3.706        & 24.18  & 9.79  & 33.0 & 0.8         & 37.0        & 148.0   & 1.24      \\
-bs014828        & 03:32:27 & -27:52:26 & 3.562        & 23.58  & 10.15 & 30.0 & 0.31        & 76.0        & 63.0    & 1.61      \\
-bs016759        & 03:32:29 & -27:48:53 & 3.602       & 23.85  & 9.99  & 8.8  & 0.65        & 50.0        & 49.0    & 0.87      \\
-lbg\_20         & 03:32:41 & -27:52:21 & 3.225        & 24.97  & 9.61  & 4.7  & 0.64        & 52.0        & 1.0     & 1.28      \\
-lbg\_24         & 03:32:40 & -27:39:57 & 3.279       & 24.67  & 9.71  & 5.9  & 0.53        & 60.0        & 34.0    & 1.27      \\
-lbg\_25         & 03:32:29 & -27:40:22 & 3.322        & 24.95  & 9.44  & 5.8  & 0.3         & 76.0        & 78.0    & 1.18      \\
-lbg\_32         & 03:32:34 & -27:41:24 & 3.417      & 23.84  & 10.17 & 52.0 & 0.6         & 54.0        & 40.0    & 1.88      \\
-lbg\_38         & 03:32:22 & -27:44:38 & 3.488       & 24.58  & 10.03 & 7.5  & 0.58        & 56.0        & 137.0   & 0.92      \\
-lbg\_91         & 03:32:27 & -27:41:52 & 3.170       & 24.65  & 9.8   & 5.7  & 0.58        & 56.0        & 79.0    & 0.89 \\
-lbg\_94         & 03:32:29 & -27:44:12 & 3.367       & 24.54  & 10.01 & 8.1  & 0.22        & 84.0        & 81.0    & 1.16      \\
-lbg\_105        & 03:32:24 & -27:52:16 & 3.092      & 23.79  & 9.79  & 30.0 & 0.56        & 57.0        & 128.0   & 1.72      \\
-lbg\_109        & 03:32:21 & -27:43:46 & 3.600       & 24.63  & 9.73  & 9.4  & 0.6         & 54.0        & 119.0   & 1.98      \\
-lbg\_111        & 03:32:42 & -27:45:52 & 3.609       & 24.01  & 9.74  & 27.0 & 0.74        & 42.0        & 80.0    & 0.64      \\
-lbg\_113        & 03:32:36 & -27:41:50 & 3.622      & 24.01  & 9.83  & 41.0 & 0.52        & 60.0        & 15.0    & 0.87      \\
-$^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.98 & 10.64 & 50.0 & 0.57         & 57.3        & -    & 2.52      \\
-n3\_009       & 22:17:28 & +00:12:12 & 3.069 & -    & 8.72  & -            & 0.75        & 42.0        & 84.0    & 1.06      \\
-n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.96 & 9.94  & -            & 0.71        & 46.0        & 94.0    & 0.56      \\
-lab18         & 22:17:29 & +00:07:52 & 3.101           & -    & 8.66  & -            & 0.85        & 32.0        & 27.0    & 0.46      \\
-$^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & -    & 8.78  & -            & 0.57         & 57.3        & -    & 2.18      \\
-s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.46 & 9.88  & -            & 0.39        & 70.0        & 125.0   & 1.78      \\
-s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.91 & 9.74  & -            & 0.57        & 57.0        & 76.0    & 1.59      \\
-$^{*}$s\_sa22b-d5  & 22:17:36 & +00:06:10 & 3.175 & 23.72 & 10.32 & -            & 0.57         & 57.3        & -    & 3.30      \\
-s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.25 & 10.05 & -            & 0.65        & 50.0        & 60.0    & 0.5       \\
-$^{*}$s\_sa22b-md25 & 22:17:42 & +00:06:20 & 3.304     & 24.62 & 9.05  & -            & 0.57         & 57.3        & -    & 1.39
+b012141\_012208 & 03:32:23 & -27:51:57 & 3.471        & 24.12  & 10.16 & 59 & 0.36        & 72        & 9     & 1.57      \\
+b15573          & 03:32:28 & -27:51:00 & 3.583        & 23.6   & 10.37 & 27 & 0.28        & 78        & 146   & 0.52      \\
+bs006516        & 03:32:15 & -27:50:46 & 3.215        & 23.94  & 9.85  & 14 & 0.50         & 61        & 146   & 1.91      \\
+bs006541        & 03:32:15 & -27:52:05 & 3.475       & 23.44  & 10.19 & 18 & 0.44        & 66        & 168   & 1.83      \\
+bs008543        & 03:32:18 & -27:50:50 & 3.474        & 22.73  & 10.67 & 42 & 0.50         & 61        & 67    & 1.59      \\
+bs009818        & 03:32:20 & -27:53:01 & 3.706        & 24.18  & 9.79  & 33 & 0.80         & 37        & 148   & 1.24      \\
+bs014828        & 03:32:27 & -27:52:26 & 3.562        & 23.58  & 10.15 & 30 & 0.31        & 76        & 63    & 1.61      \\
+bs016759        & 03:32:29 & -27:48:53 & 3.602       & 23.85  & 9.99  & 9  & 0.65        & 50        & 49    & 0.87      \\
+lbg\_20         & 03:32:41 & -27:52:21 & 3.225        & 24.97  & 9.61  & 5  & 0.64        & 52        & 1     & 1.28      \\
+lbg\_24         & 03:32:40 & -27:39:57 & 3.279       & 24.67  & 9.71  & 6  & 0.53        & 60        & 34    & 1.27      \\
+lbg\_25         & 03:32:29 & -27:40:22 & 3.322        & 24.95  & 9.44  & 6  & 0.30         & 76        & 78    & 1.18      \\
+lbg\_30         & 03:32:43 & -27:42:06 & 3.419        & 23.85  & 10.13  & 29  & 0.79         & 38        & 66    & 0.95      \\
+lbg\_32         & 03:32:34 & -27:41:24 & 3.417      & 23.84  & 10.17 & 52 & 0.60         & 54        & 40    & 1.88      \\
+lbg\_38         & 03:32:22 & -27:44:38 & 3.488       & 24.58  & 10.03 & 8  & 0.58        & 56        & 137   & 0.92      \\
+lbg\_91         & 03:32:27 & -27:41:52 & 3.170       & 24.65  & 9.80   & 6  & 0.58        & 56        & 79    & 0.89 \\
+lbg\_94         & 03:32:29 & -27:44:12 & 3.367       & 24.54  & 10.01 & 8  & 0.22        & 84        & 81    & 1.16      \\
+lbg\_105        & 03:32:24 & -27:52:16 & 3.092      & 23.79  & 9.79  & 30 & 0.56        & 57        & 128   & 1.72      \\
+lbg\_109        & 03:32:21 & -27:43:46 & 3.600       & 24.63  & 9.73  & 9  & 0.60         & 54        & 119   & 1.98      \\
+lbg\_111        & 03:32:42 & -27:45:52 & 3.609       & 24.01  & 9.74  & 27 & 0.74        & 42        & 80    & 0.64      \\
+lbg\_112         & 03:32:17 & -27:42:18 & 3.617        & 25.16  & 9.67  & 5  & 0.79         & 38        & 43    & 0.46      \\
+lbg\_113        & 03:32:36 & -27:41:50 & 3.622      & 24.01  & 9.83  & 41 & 0.52        & 60        & 15    & 0.87      \\
+lbg\_124         & 03:32:33 & -27:50:07 & 3.794        & 24.96  & 9.09  & 10  & 0.56         & 57        & 50    & 0.78      \\
+$^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.98 & 10.64 & 50 & 0.57         & 57        & -    & 2.52      \\
+n3\_009       & 22:17:28 & +00:12:12 & 3.069 & -    & 8.72  & -            & 0.75        & 42        & 84    & 1.06      \\
+n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.96 & 9.94  & -            & 0.71        & 46        & 94    & 0.56      \\
+lab18         & 22:17:29 & +00:07:52 & 3.101           & -    & 8.66  & -            & 0.85        & 32        & 27    & 0.46      \\
+$^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & -    & 8.78  & -            & 0.57         & 57        & -    & 2.18      \\
+s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.46 & 9.88  & -            & 0.39        & 70        & 125   & 1.78      \\
+s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.91 & 9.74  & -            & 0.57        & 57        & 76    & 1.59      \\
+$^{*}$s\_sa22b-d5  & 22:17:36 & +00:06:10 & 3.175 & 23.72 & 10.32 & -            & 0.57         & 57        & -    & 3.30      \\
+s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.25 & 10.05 & -            & 0.65        & 50        & 60   & 0.5       \\
+$^{*}$s\_sa22b-md25 & 22:17:42 & +00:06:20 & 3.304     & 24.62 & 9.05  & -            & 0.57         & 57        & -    & 1.39
 
@@
 The median difference between the derived $b/a$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta b/a = 0.0002$
-The $b/a$ distribution shown in figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST imaging}, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
+The $b/a$ distribution shown in Figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST imaging}, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
 This compares well with the theoretical mean value of 57.3$^{\circ}$ computed for a population of galaxies with randomly drawn viewing angles (see e.g.
@@
 The second {\tt GALFIT} parameter is $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
-We have visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$indicated by the orange dashed line in figure \ref{fig:main_body_kinematic_grids}) and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
+We have visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
 We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2016}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
@@
 
-In the right panel of figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
+In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
 In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation REF).
@@
     \end{subfigure}
-    \caption{We crossmatch publicly available spectroscopic redshifts for SFGs in two different redshift slices with the morphological catalogue presented in \protect\cite{VanderWel2012} as discussed in the text.
-    This provides a set of reference morphological properties for typical SFGs at different evolutionary stages to which the derived KDS values can be compared.
-    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ parameter, which could partially be explained by the F160W filter tracing a younger stellar population at $z\sim3.5$.
+    \caption{{\it Left:} The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
+    The axis ratio distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < b/a < 0.9$.
+    This suggests that we are not biased towards deriving a particular value for the axis ratio.
+    {\it Right:} The normalised counts of KDS galaxies in bins of half-light radius is plotted, along with the half-light radii of the same \protect\cite{VanderWel2012} galaxies as the left panel.
+    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\sim3.5$.
     The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high-redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
-    The $b/a$ distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < A_{r} < 0.9$.
-    This shows that we have not been biased towards deriving low or high $b/a$ values.}
+    The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
     \label{fig:morpho-distributions}
@@
 \subsubsection{Spaxel Fitting}\label{subsubsection:spaxel_fitting}
-We aim to extract 2-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 62 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
+We aim to extract two-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 62 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
 These properties are extracted via modelling emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
@@
 Following the fitting procedure the galaxies are clasified as spatially resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map equivalent to or greater than the seeing disk.
-For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, is added to table \ref{tab:pointings}.
+For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, is added to Table \ref{tab:pointings}.
 We find that 47 (76\%) of the detected KDS galaxies across both the field and cluster environments are spatially resolved and show clear velocity structure.
 The 15 galaxies which are not spatially resolved are dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
-The physical properties of all spatially resolved galaxies in both GOODS-S and SSA22 are listed in table \ref{tab:phys-props}. \\
+The physical properties of all spatially resolved galaxies in both GOODS-S and SSA22 are listed in Table \ref{tab:phys-props}. \\
 
@@
 
-The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries with the K-band atmospheric seeing profile (table \ref{tab:pointings}).
+The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries with the K-band atmospheric seeing profile (Table \ref{tab:pointings}).
 The velocity and velocity dispersion values are then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
@@
 The intrinsic velocity, $V_{C}$, is found by reading off from the best fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\sim3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
-This extraction radius is shown with the vertical red dashed line in the panels of figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
-The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
+This extraction radius is shown with the vertical red dashed line in the panels of Figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
+The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017,Swinbank2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
 This is similar also to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\sim3R_{D}$), \citep{Tiley2016a}.
@@
 The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$ respectively, which is less than at lower redshift (see \cref{subsec:results_rotation_vel} for a discussion).
-In order to determine the beam-smearing correction factor, we also extract the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
+In order to determine the beam-smearing correction factor, we also extract the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
 The beam-smearing correction factor ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in \cref{appsubsec:model_errors}.
@@
 
-To measure the $\sigma_{int}$ value for each galaxy in our sample we first use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the K-band and 55.4kms$^{-1}$ in the HK-band).
-This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam-smearing correction, followed by the subtraction of the instrumental resolution in quadrature, best recovers the $\sigma_{int}$ values.
+To measure the $\sigma_{int}$ value for each galaxy in our sample we use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the K-band and 55.4kms$^{-1}$ in the HK-band).
 
 \begin{equation}\label{eq:owen_sigma}
-   \sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{BS} \right)^{2} - \sigma_{inst}^{2}}
+\sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{BS}^{2}\right) - \sigma_{inst}^{2}}
 \end{equation}
@@
 
-We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for the isolated field sample.
+We present the observed and model determined kinematic parameters in Table \ref{tab:kin_props} for the isolated field sample.
 
@@
 bs016759        & 55$\pm9$                    & 110$^{+30}_{-21}$                    & 82$\pm11$                  & 57$^{+17}_{-22}$         & 1.93$^{+0.93}_{-0.7}$               & 75$^{+6}_{-6}$ & RD    \\
-lbg\_20         & 20$\pm$                    & 56$^{+30}_{-19}$                     & 55$\pm6$                  & 40$^{+7}_{-21}$         & 1.39$^{+1.04}_{-0.53}$              & 41$^{+9}_{-10}$ & RD   \\
+lbg\_20         & 20$\pm6$                    & 56$^{+30}_{-19}$                     & 55$\pm6$                  & 40$^{+7}_{-21}$         & 1.39$^{+1.04}_{-0.53}$              & 41$^{+9}_{-10}$ & RD   \\
 lbg\_24         & 26$\pm6$                    & 42$^{+9}_{-7}$                     & 64$\pm5$                  & 51$^{+5}_{-6}$           & 0.82$^{+0.21}_{-0.17}$          & 64$^{+3}_{-4}$ & DD   \\
 lbg\_25         & 14$\pm5$                    & 33$^{+13}_{-13}$                     & 53$\pm6$                  & 41$^{+6}_{-8}$         & 0.8$^{+0.37}_{-0.34}$                  & 87$^{+7}_{-12}$  & DD   \\
+lbg\_30         & 20$\pm6$                    & 66$^{+19}_{-17}$                    & 93$\pm11$                 & 77$^{+14}_{-17}$       & 0.86$^{+0.32}_{-0.27}$               & 46$^{+6}_{-42}$ & DD \\
 lbg\_32         & 65$\pm5$                    & 121$^{+13}_{-12}$                    & 104$\pm13$                 & 76$^{+16}_{-15}$       & 1.58$^{+0.36}_{-0.37}$               & 11$^{+2}_{-1}$ & RD \\
@@
 lbg\_111        & 36$\pm12$         & 58$^{+24}_{-17}$                     & 90$\pm14$                  & 81$^{+14}_{-16}$                   & 0.71$^{+0.33}_{-0.25}$                 & 168$^{+4}_{-5}$ & DD  \\
+lbg\_112         & 27$\pm3$                    & 63$^{+19}_{-11}$                    & 92$\pm5$                 & 78$^{+8}_{-11}$       & 0.81$^{+0.28}_{-0.17}$               & 4$^{+34}_{-12}$ & DD \\
 lbg\_113        & 50$\pm20$           & 41$^{+41}_{-29}$                     & 116$\pm22$                 & 108$^{+23}_{-25}$                  & 0.39$^{+0.39}_{-0.29}$                & 1$^{+34}_{-26}$  & DD   \\
+lbg\_124         & 9$\pm8$                    & 32$^{+27}_{-18}$                    & 58$\pm19$                 & 46$^{+19}_{-23}$       & 0.71$^{+0.69}_{-0.5}$               & 39$^{+20}_{-14}$ & DD \\
 $^{*}$n3\_006         & 36$\pm23$                    & 81$^{+47}_{-29}$                     & 144$\pm26$                 & 125$^{+27}_{-31}$          & 0.65$^{+0.41}_{-0.27}$                & 156$^{+13}_{-12}$ & DD   \\
 n3\_009         & 21$\pm9$                    & 49$^{+26}_{-16}$                     & 77$\pm13$                  & 48$^{+14}_{-45}$          & 1.01$^{+1.1}_{-0.45}$                & 20$^{+28}_{-25}$  & RD   \\
-n\_c3           & 26$\pm$                    & 51$^{+17}_{-18}$                     & 96$\pm11$                  & 72$^{+12}_{-13}$          & 0.72$^{+0.28}_{-0.29}$                & 137$^{+4}_{-15}$  & DD  \\
+n\_c3           & 26$\pm8$                    & 51$^{+17}_{-18}$                     & 96$\pm11$                  & 72$^{+12}_{-13}$          & 0.72$^{+0.28}_{-0.29}$                & 137$^{+4}_{-15}$  & DD  \\
 lab18           & 23$\pm11$                   & 41$^{+17}_{-14}$                     & 87$\pm6$                  & 62$^{+7}_{-15}$           & 0.67$^{+0.32}_{-0.24}$                 & 54$^{+18}_{-26}$ & DD    \\
@@
       \item $^{a}$ RD = Rotation Dominated; DD = Dispersion Dominated
-      \item $^{*}$ No {\em HST} coverage; see table \ref{tab:phys-props}
+      \item $^{*}$ No {\em HST} coverage; see Table \ref{tab:phys-props}
     \end{tablenotes}
@@
 The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
-This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
+This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
 Significant misalignment between the two axes can be a signature of galaxy interaction.
@@
 The resolved KDS galaxies at $z \sim 3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
-For the majority of galaxies we do not believe we are in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
+For the majority of galaxies we are not in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
 Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
@@
 can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging (e.g.
-the bottom grid in figure \ref{fig:main_body_kinematic_grids}).
+the bottom grid in Figure \ref{fig:main_body_kinematic_grids}).
+This has been discussed in \cite{Hung2015}, where redshifted local interacting galaxies are misclassified as single rotating disks on the basis of their kinematics. 
 In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
@@
 In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identify signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
-In 8/9 resolved KDS cluster galaxies we identify multiple photometric components, translating into a merger rate of 89\%  (see table \ref{tab:pointings}).
+In 8/9 resolved KDS cluster galaxies we identify multiple photometric components, translating into a merger rate of 89\%  (see Table \ref{tab:pointings}).
 The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they are drawn from a higher density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas as well as the morphological and dynamical evolution within these galaxies.
@@
 In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in \cref{subsec:AMAZE}.
-We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see table \ref{tab:pointings}).
-The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of table \ref{tab:kin_props}.
+We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
+The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
 We plot the best fitting smeared and intrinsic models for the isolated field galaxies in \cref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
@@
 In the remaining sample of 38 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 16\%, which constitute the `merger field sample'.
-The remaining 32 galaxies constitute the `isolated field sample', for which we have measured morphological parameters using {\tt GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and table \ref{tab:kin_props}).
+The remaining 32 galaxies constitute the `isolated field sample', for which we have measured morphological parameters using {\tt GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and Table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and Table \ref{tab:kin_props}).
 \\
@@
 not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
-For these galaxies we have measured morphological properties as listed in table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
+For these galaxies we have measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
 The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}. \\
@@
 In principle, studying whether the stellar mass Tully-Fisher relation evolves with redshift gives us information about when galaxies accumulate their stellar mass and rotation velocities.
-Any offset from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggests that the dynamical mass is in place, but the stellar mass is yet to be formed \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Gnerucci2011,Tiley2016a}.
+Any offset from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggests that the dynamical mass is in place, but the stellar mass is yet to be formed \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Gnerucci2011,Swinbank2012,Straatman2017}.
 \\
@@
 
-Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010}.
-However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
+Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017}.
+However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Simons2016,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
 At $z\sim 3$ observations are limited and in \cite{Gnerucci2011} an offset of -1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample defined in \cref{subsec:AMAZE} consistent with the $z\sim0$ relation.
@@
 
-We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of figure \ref{fig:tf_relation}.
+We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
 In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
@@
 These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ \citep{Reyes2011}, for a sample of $z<0.1$ disks in a similar mass range to KROSS and traced with H$\alpha$ emission.
-In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of figure \ref{fig:tf_relation}.
+In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
 The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these limits.
@@
 
-In the right panel of figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see \cref{app:comparison_samples}) and KDS isolated field sample to highlight two observations:
+In the right panel of Figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see \cref{app:comparison_samples}) and KDS isolated field sample to highlight two observations:
 \begin{itemize}
@@
 the combination of gas mass, stellar mass and dark matter mass, against gravitational collapse.
-$V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
+$V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
 Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}[M_{\odot}])=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of gas mass and dark matter mass would raise this estimate).
@@
 
-In the right panel of figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
+In the right panel of Figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
 It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in \cref{app:comparison_samples}) are directly comparable.
@@
 The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
-This is seen in the left panel of figure \ref{fig:tf_relation} where the dispersion dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
+This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
 
@@
 
-In the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation dominated classes, along with the AMAZE Clean sample galaxies in the $\sigma_{int}$ vs.
+In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation dominated classes, along with the AMAZE Clean sample galaxies in the $\sigma_{int}$ vs.
 $M_{\star}$ plane.
@@
 
-In the right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
+In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
 The values increase sharply from $\sigma_{int} \sim 10-20kms^{-1}$ as traced by $z\sim0$ measurements of typical SFGs to $\sigma_{int} \sim 30-60kms^{-1}$ at $z\sim1$ to $\sigma_{int} \sim 40-90kms^{-1}$ at $z\sim3$.
@@
 The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 150kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
-The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ and $V_{C}$ in the equation shown in the top right of the left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
-The tracks plotted in figure \ref{fig:sigma_and_v_sigma_w_redshift} give a rough indication of how $\sigma_{int}$ evolves in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
+The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
+The tracks plotted in Figure \ref{fig:sigma_and_v_sigma_w_redshift} suggest the shape of the $\sigma_{int}$ evolution in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
 
@@
 
-In figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean sample for reference.
+In Figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean sample for reference.
 In the local universe, disky, SFGs are observed to have $V_{C}/\sigma_{int}$ values in excess of 10 (i.e.
@@
 
-The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies is marked on figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}[M_{\odot}]) > 9.7$ which are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
+The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}[M_{\odot}]) > 9.7$ which are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
 The Rotation Dominated Fraction (RDF), calculated with respect to the full field sample of 38 galaxies, is 0.34$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
@@
 
-In the left and right panels of figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in \cref{app:comparison_samples}.
+In the left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in \cref{app:comparison_samples}.
 The filled symbols and black errorbars in the left panel represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
@@
 The rotation dominated fraction, traced simply by the $V_{C}/\sigma_{int}$ ratio inferred from ionised gas emission lines, drops from $\sim 100\%$ of galaxies in the local universe to $\sim 2/3$ of galaxies in the $z \sim 1-2$ universe and to $\sim 1/3$ above $z \sim 3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
-This is highlighted in the right panel of figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic rotation dominated fraction decline as described in \cite{Stott2016}.
+This is highlighted in the right panel of Figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic rotation dominated fraction decline as described in \cite{Stott2016}.
 The width of the $V_{C}/\sigma_{int}$ distributions indicates the galaxy diversity at each redshift slice, driven by the collection of galaxy masses, sSFRs, gas fractions, morphologies and evolutionary states which comprise each sample.
@@
 
+\begin{figure*}
+    \centering \hspace{-1.3cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{sigma_shifted.png}
+    \end{subfigure} \hspace{+0.4cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{sigma_shifted_high_mass.png}
+    \end{subfigure}
+    \caption{{\it Left:} We plot the directly comparable $\sigma_{int}$ values (see filled symbols) for the surveys spanning $z=0-3$ as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}[M_{\odot}]) = 10.0$.
+    The dark grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
+    The light grey region encompasses model predictions between `minimum' values with $Q_{crit} = 0.68$,$V_{C}=100kms^{-1}$ and `maximum' values with $Q_{crit} = 0.68$,$V_{C}=150kms^{-1}$.
+    The shifted points are in line with the scenario whereby the sample averaged velocity dispersions increase with redshift as a result of increasing average gas fractions. 
+    {\it Right:} The same as in the left panel for a reference mass of $log(M_{\star}[M_{\odot}]) = 10.6$.
+    The steeper slope beyond $z\sim2$ highlights the model decrease in gas fraction, and hence velocity dispersion, for galaxies which have accumulated a larger stellar population.}
+    \label{fig:sigma_shifted}
+\end{figure*}
+
 Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
@@
 
-We build on both the ideas that accumulating a stellar population contributes to stabilising rotation within typical SFGs at all epochs and that rotation velocities alone may not be a good tracer of the total dynamical mass within a system.
-
-Connected to this also is the idea of progenitor bias, in that the SFGs we are selecting and comparing between $z\sim0-3.5$ may not form an evolutionary cohort, with the quenching of SF accuring at a particular mass scale \citep[e.g.][]{Keres2005,Dekel2006,Peng2010}, leading to morphological and dynamical transformation.
-\\
-
-This could either be a result of the measurement and modelling technique, which carries significant uncertainties due to modelling assumptions, the S/N of the [O~{\sc III}]$\lambda5007$ emission line even in very long integrations at this redshift, the spatial coverage of [O~{\sc III}]$\lambda5007$ may be more compact that $H\alpha$ and consequently may not probe out to the same galactic radii and the sparsity of resolution elements, or could be the result or some real physical process in the galaxies which lowers $V_{C}$ as traced by the ionised gas dynamics.
-
-however our data appear to support a scenario in which low $M_{\star}$ galaxies experience elevated random motions related to the rapid accretion of cold gas, which is partially supported gravitationally by these random motions and may contribute to the observation of low $V_{C}$ values.
-At higher $M_{\star}$ the accumulation of a stellar population provides stability, $\sigma_{int}$ decreases and $V_{C}$ increases to provide the additional gravitational support.
-These processes are mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Wisnioski2015}
-
-\cite{Law2009} observe galaxies with similarly low mean velocity shear and high velocity dispersions (the velocities are not plotted here since the tabulated values are not inclination or beam-smearing corrected) and attribute this to instabilities which occur when the cold gas becomes dynamically dominant following efficient accretion and in line with the high gas fractions observed at high-redshift.
-
-\cite{Law2009} attribute the cosmic increase in $\sigma_{int}$ to much larger gas fractions at high-redshift, with the gas accumulated through rapid cold-mode accretion along cosmic filaments.
-Systems such as these form roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk.
+\subsection{The increase of velocity dispersion with redshift}\label{discussion_increase_in_sigma}
+Previous studies have claimed that the elevated velocity dispersions observed at high redshift are a consequence of both internal and external processes.
+\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\sim2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion which occur when the cold gas becomes dynamically dominant.
+Systems such as these form roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009}.
 Following this, $\sigma_{int}$ decreases over time as ordered rotations begin to dominate.
-\cite{Wisnioski2015} interpret the increase of $\sigma_{int}$ towards high-redshift in terms of the equilibrium model, which describes the rough balance between galactic accretion, star-formation and outflows \citep[e.g.][]{Lilly2013}, deriving a scaling relation for $\sigma_{int}$ with redshift appropriate for galaxies which have formed a quasi-stable disk (see their section 5.2).
-
-The same caveats apply as described above surrounding the comparison of values derived from different measurement techniques, however it appears that the evolution of $\sigma_{int}$ can be well described in the context of the equilibrium model by the evolution of the gas fraction with redshift \citep{Wisnioski2015}.
-The $M_{\star}$ value of a galaxy is linked to the size of the gas reservoir, since gas is depleted to build the stellar population.
-The location of mean $\sigma_{int}$ values is therefore related to the mean $M_{\star}$ of each survey, with this being an indicator of the accumulation of a stellar population and hence the evolutionary state of the galaxies.
-
-We suggest that as galaxies accumulate their stellar populations and exhaust their gas supplies, this leads to a more stable rotating disk and hence evolution towards higher $V_{C}/\sigma_{int}$ values.
+This is in line with the high gas fractions observed at intermediate and high redshift \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.
+
+In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the equilibrium model prescription for the evolution of velocity dispersion with redshift described in section 5.2 of \cite{Wisnioski2015}, using the updated depletion time scaling relation from \cite{Tacconi2017} (i.e.
+$t_{depl} \propto (1 + z)^{-0.57}$).
+The function describing the evolution of the velocity dispersion is shown below in Equation \ref{eq:sigma_increase}, where the gas fraction is a function of redshift and stellar mass, $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964} ($Q_{crit} = 1.0$ for a quasi-stable thin disk \citep{ForsterSchreiber2006,Genzel2011,Wisnioski2015}) and a = $\sqrt{2}$ for a disk with constant rotational velocity \citep{Wisnioski2015}.
+
+\begin{equation}\label{eq:sigma_increase}
+    \sigma(z) = V_{C}f_{gas}(z,M_{\star})Q_{crit}/a
+\end{equation}
+
+In this model the velocity dispersions increase as a result of increasing gas fractions within galaxies, with a steeper increase from $z\sim0$ for galaxies at higher stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
+At higher redshift these lines converge, suggesting that the predictions for the gas fraction become independent of stellar mass in this regime.
+The value $V_{C}=125kms^{-1}$ is chosen as a suitable average for the rotational velocity values reported in the surveys as shown in the right panel of Figure \ref{fig:tf_relation}.
+In general the surveys with higher stellar mass have lower velocity dispersions, in support of the model hypothesis. \\
+
+Since stellar mass appears to be a crucial factor in regulating the velocity dispersions within galaxies, and the comparison samples have disparate stellar mass ranges, we use the model to shift the $\sigma_{int}$ values according to their stellar mass to a reference mass value.
+This is done by computing the difference between the model predicted $\sigma_{int}$ value at the stellar mass of each comparison survey and at the reference mass for the appropriate redshift and shifting the reported $\sigma_{int}$ by this value.
+We do this for two reference mass values; $log(M_{\star}[M_{\odot}]) = 10.0$ (the mean mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}[M_{\odot}]) = 10.6$ (left panel of Figure \ref{fig:sigma_shifted}) and we only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
+In both panels the dark grey shaded regions encompass the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
+The light grey shaded regions encompass model predictions between `minimum' values with $Q_{crit} = 0.68$,$V_{C}=100kms^{-1}$ and `maximum' values with $Q_{crit} = 0.68$,$V_{C}=150kms^{-1}$. \\
+
+The $\sigma_{int}$ shifted galaxies in Figure \ref{fig:sigma_shifted} are consistent with a single relation for the increase in velocity dispersion with redshift as a result of increasing gas fractions, with the difference between the slopes in the left and right panels highlighting the role of stellar mass in the kinematic settling of galaxies between $z\sim2$ and the local universe.
+The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Wisnioski2015}.
+Rotation dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions as shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}, constituting only $\sim1/3$ of the isolated field sample at $z\sim3.5$.
+This suggests we are probing more chaotic and unstable systems in a much more active period of the universe in terms of both accretion and star-formation.
+
+The precise interpretation of the velocity dispersion remains unclear and it has been suggested that the combination of rotation velocity and velocity dispersion better traces dynamical mass in galaxies \citep[e.g.][]{Kassin2007,Kassin2012}.
+This discussion is beyond the scope of this paper, however the future observation of both stellar and gaseous velocity dispersions in tandem at high redshift with {\it JWST} will reveal the connection between these quantities.
+\\
+
+In sum, the isolated field sample galaxies are diverse and kinematically premature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Cresci2009,Gnerucci2011,Kassin2012,Straatman2017}.
+In the context of the equilibrium model explored here, these galaxies will evolve gradually with redshift along the velocity-mass relationship into stable disk galaxies which have converted their gas reservoirs into stellar mass \citep[e.g.][]{Lilly2013,Tacconi2013,Wisnioski2015,Tacconi2017}.
+Future work at higher resolution and redshift will trace the extent to which gas derived velocity dispersions trace the stellar dispersions and will investigate even earlier and more chaotic stages in the lifetimes of late-type galaxies.
 
@@
 By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding consistent merger rates in the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
-We make made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (\cref{app:comparison_samples} and table \ref{tab:evolution_numbers}).
+We make made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (\cref{app:comparison_samples} and Table \ref{tab:evolution_numbers}).
 The main conclusions of this work are summarised as follows:
@@
 \begin{itemize}
-    \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ and $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ (left panel of figure \ref{fig:v_sig_and_v}).
-    \item 13/32 isolated field sample galaxies are rotation dominated and 19/29 are dispersion dominated as indicated by the ratio $V_{C}/\sigma_{int}$, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (left and right panels of figure \ref{fig:v_sig_and_v}).
-    This gives a rotation dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of figure \ref{fig:rdf_and_v_sigma_w_redshift}).
-    \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}[M_{\odot}]) < 11.0$ at $z\sim0.9$ in the KROSS survey (figure \ref{fig:tf_relation}).
+    \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ and $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ (left panel of Figure \ref{fig:v_sig_and_v}).
+    \item 13/32 isolated field sample galaxies are rotation dominated and 19/29 are dispersion dominated as indicated by the ratio $V_{C}/\sigma_{int}$, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (left and right panels of Figure \ref{fig:v_sig_and_v}).
+    This gives a rotation dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
+    \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}[M_{\odot}]) < 11.0$ at $z\sim0.9$ in the KROSS survey (Figure \ref{fig:tf_relation}).
 %something else here when finished writing the TF section
@@
     The dispersion dominated galaxies scatter below the trend, with the same slope as the rotation dominated galaxies.
-    \item To investigate the possible contribution of $\sigma_{int}$ to the total dynamical mass, we plot $S_{0.5} = \sqrt{0.5V^{2} + \sigma_{int}^{2}}$ as a function of $M_{\star}$, finding a tighter relationship than in the case of the inverse smTFR, with the $S_{0.5} vs.
-M_{\star}$ relation showing no evidence for evolution from the $z=0$ relation from \cite{Kassin2007} (figure \ref{fig:tf_relation}).
-    We caution again that there is no clear relationship between $\sigma_{int}$ and $M_{\star}$ and this result should not be over-interpreted.
-    \item The virial mass computed from $V_{C}$ values alone is lower than the stellar mass for the majority of KDS galaxies.
-    We compute an additional component of the virial mass contributed by the velocity dispersion, shifting the virial mass above the stellar mass, and use this as a qualitative indicator that $\sigma_{int}$ is responsible for supporting some fraction of the total mass of the system (figure \ref{fig:dyn_masses}).
-    This is clearly over-simplified, as the lack of correlation between $\sigma_{int}$ and $M_{\star}$ suggests that not all of the random motions support mass, and may originate from turbulence.
-    \item The specific angular momentum (angular momentum divided by stellar mass $M_{\star}$; $j_{s}$) of the KDS galaxies is $\sim$0.3-0.4 dex lower than KROSS galaxies at $z\sim0.9$ at fixed $M_{\star}$, and the slope of the $j_{s}-M_{\star}$ relation appears comparable between the two samples (figure \ref{fig:ang_mom}).
-    This supports a scenario in which the derease in $j_{s} \propto R_{D}V_{C}$ with increasing redshift between $z=0-3.5$ is driven by the gradual size evolution of galaxies over the same redshift interval (figure \ref{fig:morpho-distributions}).
-    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in \cref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (left panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in \cref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
     This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to boost random motions within high-redshift galaxies.
-    \item We plot the mean $V_{C}$ values of the comparison samples and the KDS isolated field sample, finding significant diversity in $V_{C}$ measurements in each survey (right panel of figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    \item We plot the mean $V_{C}$ values of the comparison samples and the KDS isolated field sample, finding significant diversity in $V_{C}$ measurements in each survey (right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
     The spread in measurements is a result of the samples containing a mixture of rotation and dispersion dominated galaxies with varying $M_{\star}$ values, and the low mean KDS value is primarily the result of averaging over a sample with a high fraction of dispersion dominated galaxies.
@@
  DYNAMO & 0.1 & 10.3 & $5.06^{+0.18}_{-0.15}$ & $4.55^{+3.06}_{-2.22}$ & $0.96^{+0.02}_{-0.015}$ & $45.9^{+0.3}_{-0.3}$ & $39.0^{+18.2}_{-21.9}$ & $183.0^{+1.0}_{-1.0}$ & $164.0^{+76.0}_{-50.0}$ \\
+ MUSE+KMOS & 0.65 & 9.4 & $2.92^{+0.08}_{-0.08}$ & $2.21^{+1.73}_{-1.23}$ & $0.83^{+0.023}_{-0.023}$ & $40.0^{+0.3}_{-0.3}$ & $32.0^{+11.0}_{-8.0}$ & $103.8^{+1.52}_{-1.62}$ & $73.0^{+65.0}_{-44.0}$ \\
  KROSS & 0.9 & 9.9 & $3.05^{+0.17}_{-0.17}$ & $2.36^{+2.64}_{-1.46}$ & $0.81^{+0.05}_{-0.05}$ & - & - & $117.0^{+4.0}_{-4.0}$ & $109^{+77.0}_{-66.0}$ \\
@@
  MASSIV & 1.2 & 10.2 & $2.41^{+1.4}_{-0.9}$ & $1.95^{+2.40}_{-1.31}$ & $0.67^{+0.06}_{-0.06}$ & $61.8^{+3.8}_{-4.2}$ & $52.0^{+23.2}_{-20.7}$ & $132.13^{+10.4}_{-8.2}$ & $103.0^{+99.0}_{-61.2}$ \\
+ MUSE+KMOS & 1.25 & 9.8 & $2.21^{+0.98}_{-0.96}$ & $1.59^{+1.30}_{-0.75}$ & $0.78^{+0.04}_{-0.04}$ & $42.0^{+0.5}_{-0.5}$ & $29.5^{+20.1}_{-7.5}$ & $75.5^{+3.04}_{-3.25}$ & $54.0^{+65.32}_{-29.0}$ \\
  SINS(C09) & 2.0 & 10.6 & $5.0^{+0.93}_{-0.97}$ & $4.74^{+1.11}_{-0.18}$ & 1.0 & $51.2^{+8.0}_{-7.9}$ & $42.5^{+14.5}_{-3.5}$ & $232.0^{+12.8}_{-12.7}$ & $240.0^{+31.0}_{-60.2}$ \\
@@
 
-Throughout \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
+Throughout \cref{sec:results} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
 The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently picks out representative star-forming galaxies at each epoch and traces the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission lines.
@@
 The same process is applied to compute the errors on the sample medians and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
-These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+These results are listed in Table \ref{tab:evolution_numbers} and discussed in detail throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
 
@@
 We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.
+
+\subsection{MUSE and KMOS ($z\sim0.65$ and $z\sim1.25$)}\label{subsec:MUSE_and_KMOS}
+In \cite{Swinbank2017} a collection of $\sim400$ star-forming galaxies observed in [O~{\sc II}]$\lambda$3727,3729 with MUSE and H$\alpha$ emission with KMOS is described.
+Of this parent sample, inclination corrected velocities and intrinsic velocity dispersions are derived for 179 galaxies, to which we make comparisons.
+The observations span the redshift range $0.2 < z < 1.6$ and we split the data into two subsets with $z < 1.0$ (129 galaxies with mean redshift of $z = 0.65$, mean stellar mass of $log(M_{\star}[M_{\odot}])=9.80$) and $z > 1.0$ (50 galaxies with mean redshift of $z = 1.25$, mean stellar mass $log(M_{\star}[M_{\odot}])=9.80$).
+The reported velocities are extracted at $3R_{D}$, comparable to the extraction radius for the KDS sample and the intrinsic velocity dispersions have been corrected for beam smearing effects.
+We make use of the tabulated data from this survey and use the results at the two redshift ranges as reliable comparison samples.
 
@@
 It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
-We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in \cref{subsec:redshift_evolution} plots.
+We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in the plots throughout \cref{sec:results}.
 
@@
 
-In figure \ref{fig:intrinsic_parameters} we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane. 
+In Figure \ref{fig:intrinsic_parameters} we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane. 
 The $V_{C}$ = $\sigma_{int}$ line roughly bisects the KDS sample, and separates the dispersion and rotation dominated galaxies by definition.
@@
 To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40kms^{-1}$ and $\sigma_{int} = 80kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
-figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
 When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.

### 2017-03-17 paper.tex
Adding in comments from recent kmos3d splash of papers

@@
 These measurements constrain the internal dynamics, the intrinsic velocity dispersions $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift Universe.
-We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
+We have made careful comparisons to other samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
 The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
@@
 These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
+These random motions are likely to provide significant pressure support against gravity on the galactic disk scale.
 \end{abstract}
@@
 Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em {\em HST}}) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
-In particular, in recent years the multiplexing capabilities of KMOS have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
+In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
 
@@
 
-There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017}.
-In both cases, systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
+There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017,Ubler2017}.
+Systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
+Additionally, there has been increasing focus in the last few years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high-redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
+These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk result in a decrease in the observed rotational velocities \citep{Burkert2010}.
+Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\
 
@@
 The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
-The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RGHgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
-Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band filter has spectral resolution of $R \sim 4200$.
+The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
+Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band grating has spectral resolution of $R \sim 4200$ (H-band $R \sim 4000$).
 \subsubsection{Observations}\label{subsubsec:Obs}
@@
 During the SED modelling we assume solar metallicity stellar templates and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
+A Chabrier IMF is used with a reduced set of BC03 \citep{Bruzual2003} templates in the fitting procedure.
 We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
@@
 This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
-Following the procedure now of numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe:
+Following the procedure now of numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
 
@@
 For these galaxies we have measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
-The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}. \\
+The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}.
 
@@
 In \cref{app:comparison_samples} we describe also the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.
-During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
-\\
+During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that they trace the average properties of typical star-forming galaxies at their respective mean redshifts.
 
@@
 In principle, studying whether the stellar mass Tully-Fisher relation evolves with redshift gives us information about when galaxies accumulate their stellar mass and rotation velocities.
-Any offset from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggests that the dynamical mass is in place, but the stellar mass is yet to be formed \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Gnerucci2011,Swinbank2012,Straatman2017}.
-\\
-
-The main question arising from observations in support of and against evolution of the stellar mass Tully-Fisher relation with redshift is: Do galaxies evolve along a relation which is fixed or is there a shift in the zero-point and/or slope with decreasing redshift (i.e.
-is the connection between $V_{C}$ and the accumulating $M_{\star}$ fixed at all times)?
-We'd like to know how an individual, unperturbed point, representing a typical rotation-dominated SFG allowed to evolve without mergers, would move around the $V_{C}$ vs.
-$M_{\star}$ plane over 12 Gyr of purely secular evolution.
-
-Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017}.
-However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Simons2016,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
+Any offset from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggests that the dynamical mass is in place, but the stellar mass is yet to be formed \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Gnerucci2011,Swinbank2012,Straatman2017,Ubler2017}.
+As has been discussed recently, information about the redshift evolution of gas fractions, $f_{g} = M_{gas}/M_{bar}$ where $M_{bar}$ is the baryonic mass, disk mass fractions, $m_{d} = M_{bar}/M_{H}$  where $M_{H}$ is the halo mass, dark matter fractions, $f_{DM}(R_{1/2}) = V^{2}_{DM}(R_{1/2})/V^{2}_{C}(R_{1/2})$ where $V_{DM}$ is the dark matter circular velocity, may also be encoded in measured offsets from the local stellar mass Tully-Fisher relation \citep{Wuyts2016b,Ubler2017,Genzel2017}.
+\\
+
+Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
+High redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
+Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
+Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
+However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,DiTeodoro2016,Simons2016,Pelliccia2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
 At $z\sim 3$ observations are limited and in \cite{Gnerucci2011} an offset of -1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample defined in \cref{subsec:AMAZE} consistent with the $z\sim0$ relation.
@@
 
-With the inclusion of the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\sim0.1$ and $z\sim3.5$.
+After including data from the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\sim0.1$ and $z\sim3.5$.
 However as we will show in \cref{subsec:rdf_v_over_sigma} the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.
@@
 
-In the right panel of Figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see \cref{app:comparison_samples}) and KDS isolated field sample to highlight two observations:
+In the right panel of Figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see \cref{app:comparison_samples}) and KDS isolated field samples to highlight two observations:
 \begin{itemize}
-    \item At each redshift slice the $V_{C}$ distributions are extremely broad.
+    \item At each redshift slice the $V_{C}$ distributions are extremely broad, with mean values determined by the stellar mass of each survey.
     \item The mean isolated field sample $V_{C}$ value is less than reported in the comparison samples with similar mean $M_{\star}$ values.
@@
 This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
+However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contributes to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
+This topic is discussed further throughout \cref{sec:discussion}.
 
 We proceed to consider the cause of the high number of dispersion dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
-Further than this, there are some galaxies where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
+There are also some galaxies in our sample where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
 see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}[M_{\odot}])=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
-This suggests that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Tacconi2013,Wisnioski2015}.
+This suggests again that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Law2012b,Law2012c,Newman2013,Wisnioski2015}.
 These ideas are explored in the following sections.
@@
 $M_{\star}$ plane.
-This is an interesting relationship to explore as it has been suggested that rotational velocity alone may not be a good tracer of total dynamical mass at high-redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Kassin2012}.
+This is an interesting relationship to explore as it has been suggested that rotational velocity alone may not be a good tracer of total dynamical mass at high-redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
 However the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
-All of these processes are also more prevalent at high-redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Wisnioski2015}, leaving $\sigma_{int}$ as a challenging property to interpret. \\
+All of these processes are also more prevalent at high-redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret.
+\\
 
@@
 In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR.
-Using observed constraints for these properties \citep{Tacconi2013,Tacconi2017} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
+Using observed constraints for these properties from \cite{Tacconi2013} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
 The relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
@@
 
-The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 150kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
-The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
+The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
+The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\sim1$ for the gas-rich disks observed at high-z e.g.
+\citealt{ForsterSchreiber2006,Genzel2011,Newman2013}) and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
 The tracks plotted in Figure \ref{fig:sigma_and_v_sigma_w_redshift} suggest the shape of the $\sigma_{int}$ evolution in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
@@
 
-\subsection{$V_{C}/\sigma_{int}$ and the rotation dominated fraction}\label{subsec:rdf_v_over_sigma}
+\subsection{$\boldsymbol{V_{C}/\sigma_{int}}$ and the rotation dominated fraction}\label{subsec:rdf_v_over_sigma}
 
@@
 the disks are `well settled'), due to the decline of velocity dispersion across cosmic time, as gas fractions and disk turbulence decrease \citep[e.g.][]{Epinat2008,Epinat2008a}.
-Clearly the isolated field sample galaxies are in a different physical regime, with mean and median $V_{C}/\sigma_{int}$ values of $1.08^{+0.18}_{-0.15}$ and $0.97^{+0.14}_{-0.11}$ respectively (see further discussion in \cref{subsubsec:RDF_evolution} and \cref{sec:discussion}).
+Clearly the isolated field sample galaxies are in a different physical regime, with mean and median $V_{C}/\sigma_{int}$ values of $1.08^{+0.18}_{-0.15}$ and $0.97^{+0.14}_{-0.11}$ respectively.
 This is despite many of the dispersion dominated galaxies showing clear velocity gradients across the observed velocity maps (\cref{app:kinematics_plots}), with the arctangent model providing a good fit to the rotation curves.
@@
 In the right panel we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the rotation dominated fraction.
-These are shown with the thin grey shaded regions and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the invidual points.\\
+These are shown with the thin grey shaded regions and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the individual points.\\
 
@@
 Due to increased velocity dispersions, these rotation dominated galaxies account for only $34\%$ of the field sample and so are less representative of typical star-forming galaxies at $z\sim3.5$ than at intermediate and low redshifts.
-Explanations for the increase of $\sigma_{int}$ with redshift (and hence the decline of $V_{C}/\sigma_{int}$) with cosmic time have been discussed at length in other surveys \citep[e.g][]{ForsterSchreiber2009,Law2009,Wisnioski2015} and we revisit these in the following discussion.
+Explanations for the increase of $\sigma_{int}$ with redshift (and hence the decline of $V_{C}/\sigma_{int}$) with cosmic time as well as the nature of dispersion dominated galaxies have been discussed at length throughout other studies \citep[e.g][]{ForsterSchreiber2009,Law2009,Burkert2010,Newman2013,Wisnioski2015} and we revisit these in the following discussion.
 
@@
 This increased number of dispersion dominated galaxies in comparison to at low and intermediate redshifts appears to be driven by high velocity dispersions at $z\sim3.5$.
-In this section we discuss possible physical origins for these high values.
-
-\subsection{The increase of velocity dispersion with redshift}\label{discussion_increase_in_sigma}
+In this section we discuss possible physical origins for the elevated random motions traced by $\sigma_{int}$ and their impact on the galactic dynamics.
+
+\subsection{The origin and impact of increased velocity dispersions at high redshift}\label{discussion_increase_in_sigma}
 Previous studies have claimed that the elevated velocity dispersions observed at high redshift are a consequence of both internal and external processes.
-\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\sim2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion which occur when the cold gas becomes dynamically dominant.
-Systems such as these form roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009}.
-Following this, $\sigma_{int}$ decreases over time as ordered rotations begin to dominate.
-This is in line with the high gas fractions observed at intermediate and high redshift \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.
+\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\sim2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.
+\cite{Genzel2011} show that for dispersion dominated galaxies, the scales susceptible to gravitational collapse are of order the galactic half-light radius. 
+Systems such as these form highly unstable and roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009,Genzel2011}.
+The physical mechanisms responsible for the increase in $\sigma_{int}$ may also result in a reduction in the observed rotational velocities by partially compensating the gravitational force throughout the galactic disk \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
+Following this, $\sigma_{int}$ decreases over time as ordered rotations begin to dominate and pressure support becomes increasingly insignificant \citep[e.g.][]{Burkert2010,Ubler2017,Genzel2017,Lang2017}.
+This is in line with the evolution of gas fractions observed at intermediate and high redshifts \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.
+
+\cite{Burkert2010} show, starting from the hydrostatic equation, that negative pressure gradients sourced by the disk turbulence generated through gravitational instabilities result in a decrease in observed rotational velocities.
+This has prompted others \citep[e.g.][]{Wuyts2016b,Ubler2017,Lang2017} to encorporate a velocity dispersion term in the derivation of maximum circular velocities, which contributes to (but is not entirely responsible for) the observed shift in the zero-point of the stellar mass Tully-Fisher relation between $z\sim0-0.9$.
+\cite{Ubler2017} also claim that without the inclusion of this term incorrect conclusions surrounding the evolution of the Tully-Fisher relation will be drawn.
+We have not encorporated such a term when deriving the rotational velocities of the isolated field sample, but note that as a consequence of our galaxies showing some of the most extreme intrinsic dispersions observed, this would undoubtedly lead to a different distribution in the $V_{C}-M_{\star}$ plane.
+The contribution of pressure to rotation velocity for the KDS sample will be explored in more detail in a future work. 
+\\
 
@@
 $t_{depl} \propto (1 + z)^{-0.57}$).
-The function describing the evolution of the velocity dispersion is shown below in Equation \ref{eq:sigma_increase}, where the gas fraction is a function of redshift and stellar mass, $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964} ($Q_{crit} = 1.0$ for a quasi-stable thin disk \citep{ForsterSchreiber2006,Genzel2011,Wisnioski2015}) and a = $\sqrt{2}$ for a disk with constant rotational velocity \citep{Wisnioski2015}.
+The function describing the evolution of the velocity dispersion is shown below in Equation \ref{eq:sigma_increase}, where the gas fraction is a function of redshift and stellar mass, $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964} ($Q_{crit} = 1.0$ for a quasi-stable thin disk e.g.
+\citealt{ForsterSchreiber2006,Burkert2010,Genzel2011,Wisnioski2015}) and a = $\sqrt{2}$ for a disk with constant rotational velocity \citep{Wisnioski2015}.
 
@@
 The $\sigma_{int}$ shifted galaxies in Figure \ref{fig:sigma_shifted} are consistent with a single relation for the increase in velocity dispersion with redshift as a result of increasing gas fractions, with the difference between the slopes in the left and right panels highlighting the role of stellar mass in the kinematic settling of galaxies between $z\sim2$ and the local universe.
-The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Wisnioski2015}.
+The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Law2012b,Law2012c,Wisnioski2015}.
 Rotation dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions as shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}, constituting only $\sim1/3$ of the isolated field sample at $z\sim3.5$.
-This suggests we are probing more chaotic and unstable systems in a much more active period of the universe in terms of both accretion and star-formation.
-
-The precise interpretation of the velocity dispersion remains unclear and it has been suggested that the combination of rotation velocity and velocity dispersion better traces dynamical mass in galaxies \citep[e.g.][]{Kassin2007,Kassin2012}.
-This discussion is beyond the scope of this paper, however the future observation of both stellar and gaseous velocity dispersions in tandem at high redshift with {\it JWST} will reveal the connection between these quantities.
-\\
-
-In sum, the isolated field sample galaxies are diverse and kinematically premature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Cresci2009,Gnerucci2011,Kassin2012,Straatman2017}.
+This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
+Recent results indicate that these systems become strongly baryon-dominated on the galaxy disk scale at high redshift, which may imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.
+
+The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high-redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
+The nature of dispersion dominated galaxies at high-redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
+The AO observations shows that in some cases galaxies which are clasified as dispersion dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
+This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
+We have attempted to account for beam smearing using half-light radius and velocity gradient dependent dynamical modelling, but we acknowledge that these observations are challenging and cannot rule out the presence of unresolved velocity gradients in our seeing-limited dataset.
+Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity disperion on galaxy size \citep[e.g.][]{Newman2013}.
+Dispersion dominated galaxies are therefore likely to be at an earlier evolutionary stage and unstable to gravitational instabilities which generate turbulence which is then maintained by the potential energy of the gas in the disk \citep{Burkert2010,Newman2013}.
+
+Bringing the above points together, turbulent motions consume an increasingly significant fraction of the energy budget at high-redshift when typical star-forming galaxies are at earlier evolutionary stages.
+The KDS isolated field sample presents an extension of these trends to higher redshift, where galaxies are even more likely to be dispersion dominated, and pressure support may be more significant than explored at $z\sim2.3$ \citep{Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
+However the precise interpretation of $\sigma_{int}$ measured from ionised gas emission lines remains unclear and future observations of both stellar and gaseous velocity dispersions in tandem at high redshift with {\it JWST} will allow for unambigous investigations into the nature of gaseous velocity dispersions at high redshift.
+\\
+
+In sum, the isolated field sample galaxies are diverse and kinematically premature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Cresci2009,Burkert2010,Gnerucci2011,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
 In the context of the equilibrium model explored here, these galaxies will evolve gradually with redshift along the velocity-mass relationship into stable disk galaxies which have converted their gas reservoirs into stellar mass \citep[e.g.][]{Lilly2013,Tacconi2013,Wisnioski2015,Tacconi2017}.
-Future work at higher resolution and redshift will trace the extent to which gas derived velocity dispersions trace the stellar dispersions and will investigate even earlier and more chaotic stages in the lifetimes of late-type galaxies.
+Future work at higher resolution and redshift will trace the extent to which gas-derived velocity dispersions trace the stellar dispersions and will investigate even earlier and more chaotic stages in the lifetimes of late-type galaxies.
 
@@
     \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ and $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ (left panel of Figure \ref{fig:v_sig_and_v}).
-    \item 13/32 isolated field sample galaxies are rotation dominated and 19/29 are dispersion dominated as indicated by the ratio $V_{C}/\sigma_{int}$, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (left and right panels of Figure \ref{fig:v_sig_and_v}).
+    \item 13/32 isolated field sample galaxies are rotation dominated and 19/32 are dispersion dominated as indicated by the ratio $V_{C}/\sigma_{int}$, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (left and right panels of Figure \ref{fig:v_sig_and_v}).
     This gives a rotation dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
@@
     \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in \cref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to boost random motions within high-redshift galaxies.
+    This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to increase random motions within high-redshift galaxies.
     \item We plot the mean $V_{C}$ values of the comparison samples and the KDS isolated field sample, finding significant diversity in $V_{C}$ measurements in each survey (right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    The spread in measurements is a result of the samples containing a mixture of rotation and dispersion dominated galaxies with varying $M_{\star}$ values, and the low mean KDS value is primarily the result of averaging over a sample with a high fraction of dispersion dominated galaxies.
+    The spread in measurements is a result of the samples containing a mixture of rotation and dispersion dominated galaxies with varying $M_{\star}$ values, and the low mean KDS value is primarily the result of averaging over a sample with a high fraction of dispersion dominated galaxies and indicating the impact pressure support may have on reducing rotation velocities.
     At higher $M_{\star}$ the accumulation of a stellar population provides stability, leading to an interplay between $\sigma_{int}$ and $V_{C}$ mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Wisnioski2015}.

### 2017-03-21 paper.tex
March 21

@@
 %O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
-%R. K. Cochrane,$^{1}$
 %M. Cirasuolo,$^{1,2}$
 %C. M. Harrison,$^{2,3}$
-%J. Dunlop,$^{1}$\newauthor
-%R. J. McLure,$^{1}$
-%A. M. Swinbank$^{4,3}$
+%J. Dunlop,$^{1}$
+%R. J. McLure,$^{1}$\newauthor
+%A. M. Swinbank$^{3,4}$
 %H. L. Johnson$^{3,4}$
+%D. Sobral$^{5}$
+%J. Matthee$^{6}$
+%R. M. Sharples$^{3,4}$
 %\\
@@
 %$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
-%$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.
-%}
+%$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
+%$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
+%$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}
 
@@
 stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}.
-To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be some process which shuts off star-formation within main sequence galaxies (i.e.
+To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main sequence galaxies (i.e.
 quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010,Darvish2016}.
 
-Recent cosmological volume simulations are able to resolve the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
+Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
 Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
@@
 
-SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
+Random motions within the interstellar medium of SFGs appear to be increasing with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
 This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
@@
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.
+By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$.
 \\
@@
 \subsubsection{GOODS-S}\label{subsubsec:sample_selection_goods}
-Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see Table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
-We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
-These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
-The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions where $\sim 20$ targets can be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
-In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively.\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}
-
-\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
-A single CLUSTER environment pointing (SSA22-P1; see Table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
-Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
-A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
-Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
-
-We also add a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
-In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
-In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}.
-\footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}
-
-\subsection{Observations and data reduction}\label{subsubsec:observations_and_dr}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.8\textwidth]{main_sequence_hor.png}
-\caption{We plot the location of 48 KDS galaxies (see \cref{subsubsec:sample_summary}) in the SFR versus M$_{\star}$ plane, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
-Also plotted with the small grey points are individual SFGs from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
-The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
-We include the MS relation described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line. 
-Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3$ SFGs.}
-\label{fig:main_sequence}
-\end{figure*}
-
-Our data for the 77 KDS targets were observed using KMOS.
-KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
-The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
-The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
-Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band grating has spectral resolution of $R \sim 4200$ (H-band $R \sim 4000$).
-\subsubsection{Observations}\label{subsubsec:Obs}
-To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
-The GOODS-S pointings were observed in the H and K-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
-\\
-
-We prepare each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
-For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
-This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\
-
-The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
-In GOODS-S-P1 and GOODS-S-P2 the median K-band seeing was $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
-We observed 19-21 targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
-\\
-
-This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the details of the H-band data reduction and corresponding metallicity analyses reserved for a future work.
-Consequently we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the K-band spectral window.
-
-\subsubsection{Data reduction}\label{subsubsec:datareduction}
 
@@
   \end{table*}
+
+Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see Table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
+These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
+The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions where $\sim 20$ targets can be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
+In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively.\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}
+
+\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
+A single CLUSTER environment pointing (SSA22-P1; see Table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
+Hundreds of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
+A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011,Yamada2012a} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
+Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
+
+We also add a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
+In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
+In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}.
+\footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}
+
+\subsection{Observations and data reduction}\label{subsubsec:observations_and_dr}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.8\textwidth]{main_sequence_hor.png}
+\caption{We plot the location of 48 KDS galaxies (see \cref{subsubsec:sample_summary}) in the SFR versus M$_{\star}$ plane, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
+Also plotted with the small grey points are individual SFGs from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
+The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
+We include the MS relation described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line. 
+Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3$ SFGs.}
+\label{fig:main_sequence}
+\end{figure*}
+
+Our data for the 77 KDS targets were observed using KMOS.
+KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
+The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
+The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
+Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band grating has spectral resolution of $R \sim 4200$ (H-band $R \sim 4000$).
+\subsubsection{Observations}\label{subsubsec:Obs}
+To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
+The GOODS-S pointings were observed in the H and K-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
+\\
+
+We prepare each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
+For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
+This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\
+
+The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
+In GOODS-S-P1 and GOODS-S-P2 the median K-band seeing was $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
+We observed 19-21 targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
+\\
+
+This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the details of the H-band data reduction and corresponding metallicity analyses reserved for a future work.
+Consequently we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the K-band spectral window.
+
+\subsubsection{Data reduction}\label{subsubsec:datareduction}
 
@@
 We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
-These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ \citep{Reyes2011}, for a sample of $z<0.1$ disks in a similar mass range to KROSS and traced with H$\alpha$ emission.
+These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to KROSS and traced with H$\alpha$ emission.
 In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
@@
 Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
-The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion dominated galaxies ($66\%$ of the sample).
+The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion dominated galaxies ($66\%$ of the sample) and probable pressure support from turbulent motions \citep[e.g.][]{Burkert2010} partially supporting gravity.
 This increased number of dispersion dominated galaxies in comparison to at low and intermediate redshifts appears to be driven by high velocity dispersions at $z\sim3.5$.
@@
 This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
-Recent results indicate that these systems become strongly baryon-dominated on the galaxy disk scale at high redshift, which may imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.
+Recent results indicate that these systems become strongly baryon-dominated on the galaxy disk scale at high redshift \citep{Ubler2017,Lang2017,Genzel2017}, which may imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.
 
@@
 The nature of dispersion dominated galaxies at high-redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
-The AO observations shows that in some cases galaxies which are clasified as dispersion dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
+The AO observations show that in some cases galaxies which are clasified as dispersion dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
 This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
@@
 
-In sum, the isolated field sample galaxies are diverse and kinematically premature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Cresci2009,Burkert2010,Gnerucci2011,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
+In sum, the isolated field sample galaxies are diverse and kinematically premature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
 In the context of the equilibrium model explored here, these galaxies will evolve gradually with redshift along the velocity-mass relationship into stable disk galaxies which have converted their gas reservoirs into stellar mass \citep[e.g.][]{Lilly2013,Tacconi2013,Wisnioski2015,Tacconi2017}.
@@
 \begin{threeparttable}
-\caption{We present here a reference of the mean and median kinematic properties used throughout figures \protect\ref{fig:rdf_and_v_sigma_w_redshift} and \protect\ref{fig:sigma_and_v_sigma_w_redshift} for the different surveys.
+\caption{We present here a reference of the mean and median kinematic properties used throughout figures \protect\ref{fig:tf_relation}, \protect\ref{fig:sigma_and_v_sigma_w_redshift} and \protect\ref{fig:rdf_and_v_sigma_w_redshift} for the different surveys.
 The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
@@
 The same process is applied to compute the errors on the sample medians and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
-These results are listed in Table \ref{tab:evolution_numbers} and discussed in detail throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+These results are listed in Table \ref{tab:evolution_numbers} and discussed in detail throughout \cref{sec:results}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
 
@@
 $V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.6R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
-We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.
+We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{sec:results} to highlight the difference in selection critera.
 
@@
 The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
-No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.
+No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{sec:results} plots.
 
@@
 For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
-A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{subsec:redshift_evolution}.
+A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{sec:results}.
 This Unconstrained sample also contains the galaxy s\_sa22a-M38 common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).

### 2017-03-22 paper.tex
Just getting started on Ross changes

@@
 %R. J. McLure,$^{1}$\newauthor
-%A. M. Swinbank$^{3,4}$
-%H. L. Johnson$^{3,4}$
-%D. Sobral$^{5}$
-%J. Matthee$^{6}$
+%A. M. Swinbank,$^{3,4}$
+%H. L. Johnson,$^{3,4}$
+%D. Sobral,$^{5}$
+%J. Matthee,$^{6}$
 %R. M. Sharples$^{3,4}$
 %\\
-%$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
+%$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
 %$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
@@
 \\
-$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
+$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
 $^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany
@@
 \begin{abstract}
-We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
-These measurements constrain the internal dynamics, the intrinsic velocity dispersions $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift Universe.
+We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
+These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
 We have made careful comparisons to other samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
@@
 The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
-At each redshift slice it has been suggested that galaxies on the main sequence evolve secularly as regulated by their gas reservoirs, and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
+At each redshift slice it has been suggested that galaxies on the main sequence evolve secularly, as regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
 This assumes that high-redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
@@
 To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main sequence galaxies (i.e.
-quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010,Darvish2016}.
+quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.
 
@@
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$.
+By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$.
 \\
@@
 \begin{figure*}
-\centering
-\includegraphics[width=0.8\textwidth]{main_sequence_hor.png}
-\caption{We plot the location of 48 KDS galaxies (see \cref{subsubsec:sample_summary}) in the SFR versus M$_{\star}$ plane, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
-Also plotted with the small grey points are individual SFGs from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
+    \centering \hspace{-1.3cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{rest_colour.png}
+    \end{subfigure} \hspace{+0.4cm}
+    \begin{subfigure}[h!]{0.5\textwidth}
+        \centering
+        \includegraphics[height=3.5in]{main_sequence.png}
+    \end{subfigure}
+    \caption{{\it Left:} The distribution of 49 KDS galaxies (see \cref{subsubsec:sed_fitting}) in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
+    Also plotted in this plane are $\sim4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey, with the filled squares denoting the density in of galaxies in that region.
+    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
+    {\it Right:} We plot the location of the same 49 KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
+    The same GOODS-S galaxies from the 3D-{\em HST} survey \protect\citep{Brammer2012,Momcheva2016} at $3.0 < z < 3.8$ are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
     The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
-We include the MS relation described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line. 
-Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3$ SFGs.}
+    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line, with the discrepancy between the two relations representating the expected main sequence evolution between these redshifts.
+    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3.5$ SFGs.}
     \label{fig:main_sequence}
@@
 
-Our data for the 77 KDS targets were observed using KMOS.
-KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
+Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
 The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
@@
 We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
-The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
+The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}/M_{\odot}) = 10.0$.
 In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
 For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
-In Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
-We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.
+\\
+
+In the left panel of Figure \ref{fig:main_sequence} we plot the 64\% of KDS galaxies with SFR measurements in the rest-frame {\it U-V} vs. {\it V-J} colour space.
+This is a commonly used diagnostic plane for selecting star-forming and quiescent galaxies \citep[e.g.][]{Williams2009,Brammer2011,Whitaker2012a} with the age gradients of the stars within quiescent galaxies placing them in a different region of the plane to those which are actively forming stars.
+The selection criteria defined in \cite{Whitaker2012a} (which evolve only gently with redshift) separate quiescent and star-forming regions, which are indicated by the black wedge.
+We also make use of the rest-frame colours of $\sim7000$ primarily star-forming galaxies located in GOODS-S between $2.5 < z < 3.5$ from the 3D-{\em HST} survey \citep{Momcheva2016}.
+The filled squares indicate the density of 3D-{\em HST} targets in colour spaceand we observe that the peak density location is consistent with the location of the KDS targets, all of which are in the star-forming region.
+
+In the right panel of Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
+We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.77 Gyr, with the green line.
 
@@
 The difference in position of these relations highlights the main sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
-The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence, indicating that they represent typical SFGs at this redshift.
+The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence.
+
+When taken together, both panels indicate that the KDS sample is representatitve of typical SFGs at $z>3$.
 
@@
  \hline
-ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}[M_{\odot}])^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
+ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
  \hline
@@
 We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
-In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
+In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
 The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
@@
 $V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
-Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}[M_{\odot}])=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of gas mass and dark matter mass would raise this estimate).
-Indeed this value is similar to the mean $V_{C}$ value found in the KROSS sample for $log(M_{\star}[M_{\odot}])=10.0$ galaxies at $z\sim1$. \\
+Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of gas mass and dark matter mass would raise this estimate).
+Indeed this value is similar to the mean $V_{C}$ value found in the KROSS sample for $log(M_{\star}/M_{\odot})=10.0$ galaxies at $z\sim1$. \\
 
@@
 There are also some galaxies in our sample where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
-see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}[M_{\odot}])=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
+see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}/M_{\odot})=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
 This suggests again that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Law2012b,Law2012c,Newman2013,Wisnioski2015}.
@@
 
-The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
+The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}/M_{\odot})=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
 The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\sim1$ for the gas-rich disks observed at high-z e.g.
@@
     We mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies in this panel, finding that more massive galaxies (e.g.
-$log(M_{\star}[M_{\odot}]) > 9.7$) are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.}
+$log(M_{\star}/M_{\odot}) > 9.7$) are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.}
     \label{fig:v_sig_and_v}
@@
 
-The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}[M_{\odot}]) > 9.7$ which are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
+The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}/M_{\odot}) > 9.7$ which are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
 The Rotation Dominated Fraction (RDF), calculated with respect to the full field sample of 38 galaxies, is 0.34$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
@@
     \end{subfigure}
-    \caption{{\it Left:} We plot the directly comparable $\sigma_{int}$ values (see filled symbols) for the surveys spanning $z=0-3$ as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}[M_{\odot}]) = 10.0$.
+    \caption{{\it Left:} We plot the directly comparable $\sigma_{int}$ values (see filled symbols) for the surveys spanning $z=0-3$ as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 10.0$.
     The dark grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
@@
     The shifted points are in line with the scenario whereby the sample averaged velocity dispersions increase with redshift as a result of increasing average gas fractions. 
-    {\it Right:} The same as in the left panel for a reference mass of $log(M_{\star}[M_{\odot}]) = 10.6$.
+    {\it Right:} The same as in the left panel for a reference mass of $log(M_{\star}/M_{\odot}) = 10.6$.
     The steeper slope beyond $z\sim2$ highlights the model decrease in gas fraction, and hence velocity dispersion, for galaxies which have accumulated a larger stellar population.}
@@
 This is done by computing the difference between the model predicted $\sigma_{int}$ value at the stellar mass of each comparison survey and at the reference mass for the appropriate redshift and shifting the reported $\sigma_{int}$ by this value.
-We do this for two reference mass values; $log(M_{\star}[M_{\odot}]) = 10.0$ (the mean mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}[M_{\odot}]) = 10.6$ (left panel of Figure \ref{fig:sigma_shifted}) and we only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
+We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 10.0$ (the mean mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (left panel of Figure \ref{fig:sigma_shifted}) and we only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
 In both panels the dark grey shaded regions encompass the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
@@
 We have presented new measurements of 77 main sequence star forming galaxies spanning both cluster and field environments at $z\sim3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
-These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}[M_{\odot}])< 10.5$ typical main sequence galaxies at these redshifts.
+These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}/M_{\odot})< 10.5$ typical main sequence galaxies at these redshifts.
 By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding consistent merger rates in the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
@@
     This gives a rotation dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
-    \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}[M_{\odot}]) < 11.0$ at $z\sim0.9$ in the KROSS survey (Figure \ref{fig:tf_relation}).
+    \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}/M_{\odot}) < 11.0$ at $z\sim0.9$ in the KROSS survey (Figure \ref{fig:tf_relation}).
 %something else here when finished writing the TF section
@@
 \subsection{GHASP ($z\sim0$)}\label{subsec:GHASP}
-The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to produce 3D H$\alpha$ datacubes.
+The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}/M_{\odot})=10.6$ in the local universe ($z\sim0$) to produce 3D H$\alpha$ datacubes.
 The data extend out to several half-light radii and in each case tilted ring models are fit to determine $V_{C}$ at large radii where the rotation curves have flattened, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
@@
 \subsection{DYNAMO ($z\sim0.1$, but selected with physical properties resembling $z\sim2$)}\label{subsec:DYNAMO}
-In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
+In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}/M_{\odot})=10.3$ at $z\sim0.1$ is presented.
 The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\sim 2$ SFGs.
@@
 Of this parent sample, inclination corrected velocities and intrinsic velocity dispersions are derived for 179 galaxies, to which we make comparisons.
-The observations span the redshift range $0.2 < z < 1.6$ and we split the data into two subsets with $z < 1.0$ (129 galaxies with mean redshift of $z = 0.65$, mean stellar mass of $log(M_{\star}[M_{\odot}])=9.80$) and $z > 1.0$ (50 galaxies with mean redshift of $z = 1.25$, mean stellar mass $log(M_{\star}[M_{\odot}])=9.80$).
+The observations span the redshift range $0.2 < z < 1.6$ and we split the data into two subsets with $z < 1.0$ (129 galaxies with mean redshift of $z = 0.65$, mean stellar mass of $log(M_{\star}/M_{\odot})=9.80$) and $z > 1.0$ (50 galaxies with mean redshift of $z = 1.25$, mean stellar mass $log(M_{\star}/M_{\odot})=9.80$).
 The reported velocities are extracted at $3R_{D}$, comparable to the extraction radius for the KDS sample and the intrinsic velocity dispersions have been corrected for beam smearing effects.
@@
 \subsection{KROSS ($z\sim0.9$)}\label{subsec:KROSS}
-We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}[M_{\odot}])=9.9$ and $z\sim0.9$.
+We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}/M_{\odot})=9.9$ and $z\sim0.9$.
 $V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) with the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
@@
 The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
-At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.
+At $z \sim 1.0$ the galaxies have $log(M_{\star}/M_{\odot})=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}/M_{\odot})=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}/M_{\odot})=10.0$.
 The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
@@
 \subsection{MASSIV ($z\sim1.2$)}\label{subsec:MASSIV}
-The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
+The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}/M_{\odot})=10.2$ at $z\sim1.2$.
 An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
@@
 \subsection{SINS ($z\sim2.0$)}\label{subsec:SINS}
-The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ at $z\sim2.0$.
+The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}/M_{\odot})=10.6$ at $z\sim2.0$.
 Galaxies in this sample are classified as rotation or dispersion dominated following FS09 section 9.5.1 which classifies rotation dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
@@
 \subsection{LAW 09 ($z\sim2.3$)}\label{subsec:law_09}
-In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}[M_{\odot}])=10.0$ at $z\sim2.3$.
+In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}/M_{\odot})=10.0$ at $z\sim2.3$.
 The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
@@
 \subsection{AMAZE ($z\sim3.0$)}\label{subsec:AMAZE}
-The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
+The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}/M_{\odot})=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
 In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq.

### 2017-03-23 paper.tex
finished all basic ross corrections

@@
 \usepackage[LGRgreek]{mathastext}
+\usepackage{enumitem}
 
@@
 \begin{abstract}
-We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
+We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
 These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
@@
 Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
-The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
-Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em {\em HST}}) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
-In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
+The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collapse, mergers and outflows e.g.
+\citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulations to reproduce.
+Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
+When interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em HST}), these data provide information about the range of physical processes which are driving galaxy evolution.
+In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
 
@@
 Additionally, there has been increasing focus in the last few years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high-redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
-These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk result in a decrease in the observed rotational velocities \citep{Burkert2010}.
+These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotational velocities \citep{Burkert2010}.
 Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\
 
-In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focussing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
-There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts.
-For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high-redshift?
-\textbf{(2)} What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
-\textbf{(3)} What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
-\textbf{(4)} What is the connection between the gas phase metallicity and  kinematics, particularly in terms of inflows and outflows of material?
-
-This paper focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
+In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
+There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item How applicable are strong line metallicity calibrators at high redshift?
+\item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
+\item What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
+\item What is the connection between the gas phase metallicity and  kinematics, particularly in terms of inflows and outflows of material? \end{enumerate}
+
+This paper focuses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$.
+By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$.
 \\
@@
 In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially resolved in the [O~{\sc III}]$\lambda$5007 emission line.
-\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
+\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible underlying physical mechanisms.
 We present our conclusions in \cref{sec:conclusion}.
@@
 The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
-The two key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
-We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
+The two key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the peak epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
+We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and a `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
 To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
-Consequently, this is some of the deepest spectroscopic data available for this redshift.
+Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.
 
@@
 Target selection for the KDS sample is designed to pick out SFGs at $z \sim 3.5$, supported by deep multi-wavelength ancillary data.
-Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the K-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the H-band, both of which are observable with KMOS.
+Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
 From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest S/N and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
 To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well studied fields that have a previous spectroscopic detection (see details below).
-Predominantly, the galaxies have been selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
+Predominantly, the galaxies were originally selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
 However, a subset of the selected cluster galaxies in the SSA22 field were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
@@
 \begin{threeparttable}
-\caption{Summary of KDS pointing statistics for the full observed sample of 77 galaxies}
+\caption{This table summarises the KDS pointing statistics for the full observed sample of 77 galaxies.
+The columns list the pointing name, the galaxy environment probed, the central pointing coordinates, the number of observed, detected, resolved and merging objects as described in \protect\cref{subsubsec:datareduction}, the waveband observed with KMOS, the exposure time and the PSF measured in the {\it K}-band.}
 \label{tab:pointings}
@@
  \hline
- GOODS-S-P1 & FIELD & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & K & 32.4 & 0.50 \\
-GOODS-S-P2 & FIELD & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & K & 31.8 & 0.52 \\
-SSA22-P1 & CLUSTER & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
-SSA22-P2 & FIELD & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
+ GOODS-S-P1 & FIELD & 03:32:22 & $-$27:52:51 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & K & 32.4 & 0.50 \\
+GOODS-S-P2 & FIELD & 03:32:35 & $-$27:43:15 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & K & 31.8 & 0.52 \\
+SSA22-P1 & CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
+SSA22-P2 & FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
+
  \hline
@@
       \small
-      \item $^{a}$ We also observed the two GOODS-S pointings in the H-band to cover the [O~{\sc II}]$\lambda$3727,3729 emission lines and a description of these observations will be given in a future work.
-      \item $^{b}$ The PSF values correspond to measurements in the K-band.
+      \item $^{a}$ We also observed the two GOODS-S pointings in the {\it H}-band to cover the [O~{\sc II}]$\lambda$3727,3729 emission lines and a description of these observations will be given in a future work.
+      \item $^{b}$ The PSF values correspond to measurements in the {\it K}-band.
       \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
@@
 
-Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see Table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
-We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
-These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
-The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions where $\sim 20$ targets can be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
-In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively.\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}
+Two of the FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+We selected targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
+These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
+The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\sim 20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
+In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}
 
 \subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
-A single CLUSTER environment pointing (SSA22-P1; see Table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
+A single CLUSTER environment pointing was selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
 Hundreds of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
 A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011,Yamada2012a} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
-Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
-
-We also add a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
+Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the {\it K}-band which is free from OH features and so for the CLUSTER environment pointing we filled the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
+
+We also added a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
 In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
@@
 \subsection{Observations and data reduction}\label{subsubsec:observations_and_dr}
+
+Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
+The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
+The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
+Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R \sim 4200$ ({\it H}-band $R \sim 4000$).
+\subsubsection{Observations}\label{subsubsec:Obs}
 
@@
     The same GOODS-S galaxies from the 3D-{\em HST} survey \protect\citep{Brammer2012,Momcheva2016} at $3.0 < z < 3.8$ are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
-    The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
+    The black solid line and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
     We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line, with the discrepancy between the two relations representating the expected main sequence evolution between these redshifts.
@@
 
-Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
-The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
-The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
-Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band grating has spectral resolution of $R \sim 4200$ (H-band $R \sim 4000$).
-\subsubsection{Observations}\label{subsubsec:Obs}
-To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
-The GOODS-S pointings were observed in the H and K-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously.
-\\
-
-We prepare each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
-For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopt the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
-This will later allow for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\
+To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
+The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously.
+\\
+
+We prepared each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
+For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopted the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
+This procedure allowed for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\
 
 The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
-In GOODS-S-P1 and GOODS-S-P2 the median K-band seeing was $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the K-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
+In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the {\it K}-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
 We observed 19-21 targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
@@
 
-This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the details of the H-band data reduction and corresponding metallicity analyses reserved for a future work.
-Consequently we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the K-band spectral window.
+Consequently we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
+This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the details of the {\it H}-band data reduction and corresponding metallicity analyses reserved for a future work.
 
@@
 
-The data reduction process primarly makes use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
+The data reduction process primarly made use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
 In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.
@@
 The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
-An additional step which is not part of the standard reduction process is carried out at this stage, which is to address readout channel bias.
+An additional step which is not part of the standard reduction process was carried out at this stage, which is to address readout channel bias.
 Differences in the readout process across each 64 pixel wide channel on the detector image lead to a varying flux baselines in these channels.
-We correct back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.
-
-Standard star observations were carried out on the same night as the science observations and are processed in an identical manner to the science data.
-Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
-Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations.
-\\
-
-Sky subtraction is enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
-Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the K-band greatly reduces the sky-line residuals.
-We monitor the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged K-band seeing rises above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
-The PSF is determined from fitting the K-band collapsed, stacked standard star cube in each pointing with an elliptical gaussian and the values are reported in Table \ref{tab:pointings}.
+We corrected back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.
+
+Standard star observations were carried out on the same night as the science observations and were processed in an identical manner to the science data.
+Following this pre-processing, each of the object exposures was reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
+Each 300s exposure was reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations.
+\\
+
+Sky subtraction was enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
+Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the {\it K}-band greatly reduces the sky-line residuals.
+We monitored the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged {\it K}-band seeing rose above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
+The PSF was determined from fitting the {\it K}-band collapsed, stacked standard star cube in each pointing with an elliptical gaussian and the values are reported in Table \ref{tab:pointings}.
 The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
@@
 
-We stack all 300s exposures for each galaxy which pass seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
-We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
-To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
+We stacked all 300s exposures for each galaxy which pass seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
+We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
+To account for this a polynomial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
 \\
@@
 The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}/M_{\odot}) = 10.0$.
-In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
+In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and {\it K}-band detections lower than 2-$\sigma$ significance.
 For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
@@
 The selection criteria defined in \cite{Whitaker2012a} (which evolve only gently with redshift) separate quiescent and star-forming regions, which are indicated by the black wedge.
-We also make use of the rest-frame colours of $\sim7000$ primarily star-forming galaxies located in GOODS-S between $2.5 < z < 3.5$ from the 3D-{\em HST} survey \citep{Momcheva2016}.
-The filled squares indicate the density of 3D-{\em HST} targets in colour spaceand we observe that the peak density location is consistent with the location of the KDS targets, all of which are in the star-forming region.
-
-In the right panel of Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
+We also make use of the rest-frame colours of $\sim4000$ primarily star-forming galaxies located in GOODS-S between $3.0 < z < 3.8$ (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
+The filled squares indicate the density of 3D-{\em HST} targets in colour space and we observe that the peak density location is consistent with the location of the KDS targets, all of which are in the star-forming region.
+
+In the right panel of Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the KDS galaxies with SFR measurements, in combination with the derived physical properties of the same GOODS-S galaxies as in the left panel.
 We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.77 Gyr, with the green line.
@@
 For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution images.
-This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $b/a$, of the galaxies.
+This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$), morphological position angle, $PA_{morph}$, and axis ratio, $b/a$, of the galaxies.
 In the following sections we describe the approach we have chosen to recover these parameters detailing comparisons with matched galaxies in the morphological parameter catalogue of \cite{VanderWel2012}.
@@
 Siana: PID 12527).
-The {\em HST} coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is concentrated on SSA22-CLUSTER and so we resort to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage listed in Table \ref{tab:phys-props}).
+The {\em HST} coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is concentrated on the SSA22-CLUSTER and so we resort to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage are listed in Table \ref{tab:phys-props}).
 \\
@@
 At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
-In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012} and in the F814W band we use the pure Tiny Tim ACS high-resolution PSF model.
+In the F160W band the adopted PSF is a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the F814W band we use the pure Tiny Tim ACS high-resolution PSF model.
 During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.
@@
 This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
-Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout \cref{app:kinematics_plots}.
-
-The errorbars produced by {\tt GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, with this resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
+Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout Appendix \ref{app:kinematics_plots}.
+
+The errorbars produced by {\tt GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
 Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
-There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we discuss the approach followed to recover the morphological parameters for these galaxies.
+There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we also discuss the approach followed to recover the morphological parameters for these galaxies.
 We do not expect that this small number of galaxies without {\em HST} imaging will impact the bulk dynamical properties of the KDS sample.
@@
  \hline
-b012141\_012208 & 03:32:23 & -27:51:57 & 3.471        & 24.12  & 10.16 & 59 & 0.36        & 72        & 9     & 1.57      \\
-b15573          & 03:32:28 & -27:51:00 & 3.583        & 23.6   & 10.37 & 27 & 0.28        & 78        & 146   & 0.52      \\
-bs006516        & 03:32:15 & -27:50:46 & 3.215        & 23.94  & 9.85  & 14 & 0.50         & 61        & 146   & 1.91      \\
-bs006541        & 03:32:15 & -27:52:05 & 3.475       & 23.44  & 10.19 & 18 & 0.44        & 66        & 168   & 1.83      \\
-bs008543        & 03:32:18 & -27:50:50 & 3.474        & 22.73  & 10.67 & 42 & 0.50         & 61        & 67    & 1.59      \\
-bs009818        & 03:32:20 & -27:53:01 & 3.706        & 24.18  & 9.79  & 33 & 0.80         & 37        & 148   & 1.24      \\
-bs014828        & 03:32:27 & -27:52:26 & 3.562        & 23.58  & 10.15 & 30 & 0.31        & 76        & 63    & 1.61      \\
-bs016759        & 03:32:29 & -27:48:53 & 3.602       & 23.85  & 9.99  & 9  & 0.65        & 50        & 49    & 0.87      \\
-lbg\_20         & 03:32:41 & -27:52:21 & 3.225        & 24.97  & 9.61  & 5  & 0.64        & 52        & 1     & 1.28      \\
-lbg\_24         & 03:32:40 & -27:39:57 & 3.279       & 24.67  & 9.71  & 6  & 0.53        & 60        & 34    & 1.27      \\
-lbg\_25         & 03:32:29 & -27:40:22 & 3.322        & 24.95  & 9.44  & 6  & 0.30         & 76        & 78    & 1.18      \\
-lbg\_30         & 03:32:43 & -27:42:06 & 3.419        & 23.85  & 10.13  & 29  & 0.79         & 38        & 66    & 0.95      \\
-lbg\_32         & 03:32:34 & -27:41:24 & 3.417      & 23.84  & 10.17 & 52 & 0.60         & 54        & 40    & 1.88      \\
-lbg\_38         & 03:32:22 & -27:44:38 & 3.488       & 24.58  & 10.03 & 8  & 0.58        & 56        & 137   & 0.92      \\
-lbg\_91         & 03:32:27 & -27:41:52 & 3.170       & 24.65  & 9.80   & 6  & 0.58        & 56        & 79    & 0.89 \\
-lbg\_94         & 03:32:29 & -27:44:12 & 3.367       & 24.54  & 10.01 & 8  & 0.22        & 84        & 81    & 1.16      \\
-lbg\_105        & 03:32:24 & -27:52:16 & 3.092      & 23.79  & 9.79  & 30 & 0.56        & 57        & 128   & 1.72      \\
-lbg\_109        & 03:32:21 & -27:43:46 & 3.600       & 24.63  & 9.73  & 9  & 0.60         & 54        & 119   & 1.98      \\
-lbg\_111        & 03:32:42 & -27:45:52 & 3.609       & 24.01  & 9.74  & 27 & 0.74        & 42        & 80    & 0.64      \\
-lbg\_112         & 03:32:17 & -27:42:18 & 3.617        & 25.16  & 9.67  & 5  & 0.79         & 38        & 43    & 0.46      \\
-lbg\_113        & 03:32:36 & -27:41:50 & 3.622      & 24.01  & 9.83  & 41 & 0.52        & 60        & 15    & 0.87      \\
-lbg\_124         & 03:32:33 & -27:50:07 & 3.794        & 24.96  & 9.09  & 10  & 0.56         & 57        & 50    & 0.78      \\
+b012141\_012208 & 03:32:23 & $-$27:51:57 & 3.471        & 24.12  & 10.16 & 59 & 0.36        & 72        & 9     & 1.57      \\
+b15573          & 03:32:28 & $-$27:51:00 & 3.583        & 23.6   & 10.37 & 27 & 0.28        & 78        & 146   & 0.52      \\
+bs006516        & 03:32:15 & $-$27:50:46 & 3.215        & 23.94  & 9.85  & 14 & 0.50         & 61        & 146   & 1.91      \\
+bs006541        & 03:32:15 & $-$27:52:05 & 3.475       & 23.44  & 10.19 & 18 & 0.44        & 66        & 168   & 1.83      \\
+bs008543        & 03:32:18 & $-$27:50:50 & 3.474        & 22.73  & 10.67 & 42 & 0.50         & 61        & 67    & 1.59      \\
+bs009818        & 03:32:20 & $-$27:53:01 & 3.706        & 24.18  & 9.79  & 33 & 0.80         & 37        & 148   & 1.24      \\
+bs014828        & 03:32:27 & $-$27:52:26 & 3.562        & 23.58  & 10.15 & 30 & 0.31        & 76        & 63    & 1.61      \\
+bs016759        & 03:32:29 & $-$27:48:53 & 3.602       & 23.85  & 9.99  & 9  & 0.65        & 50        & 49    & 0.87      \\
+lbg\_20         & 03:32:41 & $-$27:52:21 & 3.225        & 24.97  & 9.61  & 5  & 0.64        & 52        & 1     & 1.28      \\
+lbg\_24         & 03:32:40 & $-$27:39:57 & 3.279       & 24.67  & 9.71  & 6  & 0.53        & 60        & 34    & 1.27      \\
+lbg\_25         & 03:32:29 & $-$27:40:22 & 3.322        & 24.95  & 9.44  & 6  & 0.30         & 76        & 78    & 1.18      \\
+lbg\_30         & 03:32:43 & $-$27:42:06 & 3.419        & 23.85  & 10.13  & 29  & 0.79         & 38        & 66    & 0.95      \\
+lbg\_32         & 03:32:34 & $-$27:41:24 & 3.417      & 23.84  & 10.17 & 52 & 0.60         & 54        & 40    & 1.88      \\
+lbg\_38         & 03:32:22 & $-$27:44:38 & 3.488       & 24.58  & 10.03 & 8  & 0.58        & 56        & 137   & 0.92      \\
+lbg\_91         & 03:32:27 & $-$27:41:52 & 3.170       & 24.65  & 9.80   & 6  & 0.58        & 56        & 79    & 0.89 \\
+lbg\_94         & 03:32:29 & $-$27:44:12 & 3.367       & 24.54  & 10.01 & 8  & 0.22        & 84        & 81    & 1.16      \\
+lbg\_105        & 03:32:24 & $-$27:52:16 & 3.092      & 23.79  & 9.79  & 30 & 0.56        & 57        & 128   & 1.72      \\
+lbg\_109        & 03:32:21 & $-$27:43:46 & 3.600       & 24.63  & 9.73  & 9  & 0.60         & 54        & 119   & 1.98      \\
+lbg\_111        & 03:32:42 & $-$27:45:52 & 3.609       & 24.01  & 9.74  & 27 & 0.74        & 42        & 80    & 0.64      \\
+lbg\_112         & 03:32:17 & $-$27:42:18 & 3.617        & 25.16  & 9.67  & 5  & 0.79         & 38        & 43    & 0.46      \\
+lbg\_113        & 03:32:36 & $-$27:41:50 & 3.622      & 24.01  & 9.83  & 41 & 0.52        & 60        & 15    & 0.87      \\
+lbg\_124         & 03:32:33 & $-$27:50:07 & 3.794        & 24.96  & 9.09  & 10  & 0.56         & 57        & 50    & 0.78      \\
 $^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.98 & 10.64 & 50 & 0.57         & 57        & -    & 2.52      \\
-n3\_009       & 22:17:28 & +00:12:12 & 3.069 & -    & 8.72  & -            & 0.75        & 42        & 84    & 1.06      \\
-n\_c3         & 22:17:33 & +00:10:57 & 3.096       & 24.96 & 9.94  & -            & 0.71        & 46        & 94    & 0.56      \\
-lab18         & 22:17:29 & +00:07:52 & 3.101           & -    & 8.66  & -            & 0.85        & 32        & 27    & 0.46      \\
-$^{*}$lab25         & 22:17:23 & +00:15:51 & 3.067      & -    & 8.78  & -            & 0.57         & 57        & -    & 2.18      \\
-s\_sa22a-d3   & 22:17:32 & +00:11:33 & 3.069 & 23.46 & 9.88  & -            & 0.39        & 70        & 125   & 1.78      \\
-s\_sa22b-c20  & 22:17:49 & +00:10:14 & 3.196     & 23.91 & 9.74  & -            & 0.57        & 57        & 76    & 1.59      \\
-$^{*}$s\_sa22b-d5  & 22:17:36 & +00:06:10 & 3.175 & 23.72 & 10.32 & -            & 0.57         & 57        & -    & 3.30      \\
-s\_sa22b-d9   & 22:17:22 & +00:08:04 & 3.084    & 24.25 & 10.05 & -            & 0.65        & 50        & 60   & 0.5       \\
-$^{*}$s\_sa22b-md25 & 22:17:42 & +00:06:20 & 3.304     & 24.62 & 9.05  & -            & 0.57         & 57        & -    & 1.39
+n3\_009       & 22:17:28 & $+$00:12:12 & 3.069 & -    & 8.72  & -            & 0.75        & 42        & 84    & 1.06      \\
+n\_c3         & 22:17:33 & $+$00:10:57 & 3.096       & 24.96 & 9.94  & -            & 0.71        & 46        & 94    & 0.56      \\
+lab18         & 22:17:29 & $+$00:07:52 & 3.101           & -    & 8.66  & -            & 0.85        & 32        & 27    & 0.46      \\
+$^{*}$lab25         & 22:17:23 & $+$00:15:51 & 3.067      & -    & 8.78  & -            & 0.57         & 57        & -    & 2.18      \\
+s\_sa22a-d3   & 22:17:32 & $+$00:11:33 & 3.069 & 23.46 & 9.88  & -            & 0.39        & 70        & 125   & 1.78      \\
+s\_sa22b-c20  & 22:17:49 & $+$00:10:14 & 3.196     & 23.91 & 9.74  & -            & 0.57        & 57        & 76    & 1.59      \\
+$^{*}$s\_sa22b-d5  & 22:17:36 & $+$00:06:10 & 3.175 & 23.72 & 10.32 & -            & 0.57         & 57        & -    & 3.30      \\
+s\_sa22b-d9   & 22:17:22 & $+$00:08:04 & 3.084    & 24.25 & 10.05 & -            & 0.65        & 50        & 60   & 0.5       \\
+$^{*}$s\_sa22b-md25 & 22:17:42 & $+$00:06:20 & 3.304     & 24.62 & 9.05  & -            & 0.57         & 57        & -    & 1.39
 
@@
 The inclination angle calculated for each galaxy is used to correct the observed velocity field, which is the line of sight component of the intrinsic velocity field, with the correction factor increasing with increasing $b/a$.
-The median difference between the derived $b/a$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta b/a = 0.0002$
-The $b/a$ distribution shown in Figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST imaging}, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
+The median difference between the derived $b/a$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta b/a = 0.0002$.
+The $b/a$ distribution shown in Figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST} imaging, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with a median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
 This compares well with the theoretical mean value of 57.3$^{\circ}$ computed for a population of galaxies with randomly drawn viewing angles (see e.g.
-the appendix in \cite{Law2009}), reassuring us that we are not biased towards deriving either particularly low or particularly high inclination angles.
+the appendix in \citealt{Law2009}), reassuring us that we are not biased towards deriving either particularly low or particularly high inclination angles.
 
@@
 The half-light radius, $R_{1/2}$, provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
-As discussed throughout the introduction and in \cref{app:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
-Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies \citep[see \protect\cref{app:comparison_samples} and e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
+As discussed throughout the introduction and in Appendix \ref{app:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
+Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies and see Appendix \ref{app:comparison_samples} and \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
 Throughout our dynamical modelling and beam smearing correction (see \cref{subsec:3d_modelling}) we also require the $R_{1/2}$ value for each galaxy.
@@
 In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
-In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation REF).
+In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).
 
 \cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploit during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
-We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high-redshift galaxies (see \cref{app:kin_error_estimates}).
+We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high-redshift galaxies (see Appendix \ref{app:kin_error_estimates}).
 
@@
 The process is automated and applied to each of the 62 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
-Following the fitting procedure the galaxies are clasified as spatially resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map equivalent to or greater than the seeing disk.
+Following the fitting procedure the galaxies are clasified as spatially resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map is equivalent to or greater than the seeing disk.
 For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, is added to Table \ref{tab:pointings}.
@@
 Physically motivated models take into account the potential-well of the galaxy through knowledge of the mass distribution \citep[e.g.][]{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015,Swinbank2017}.
-Phenomenological models assume a fixed function known to well describe observed galactic rotation curves which flatten at large radii \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Harrison2017}.
+Phenomenological models assume a fixed function known to reproduce observed galactic rotation curves which flatten at large radii \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Harrison2017}.
 Both of the above examples fit to 1D or 2D fields extracted from the datacubes using line-fitting software.
@@
     \caption{We plot here the kinematic grids for one rotation dominated galaxy (top grid), one dispersion dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
-    In \protect\cref{app:kinematics_plots} we include these plots for each of the spatially resolved galaxies in the KDS, divided into rotation dominated, dispersion dominated and merger categories.
+    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially resolved galaxies in the KDS, divided into rotation dominated, dispersion dominated and merger categories.
     For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map.
     On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
+    The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.
     Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
     The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
-    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value.
+    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value of the intrinsic and observed profiles respectively.
     The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
@@
 This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
-Following the procedure now of numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
+Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
 
@@
 The velocity decreases with a factor of cos($\phi$) from the kinematic position axis, where $\phi$ is the angle measured clockwise from the axis, which points to the direction of the positive side of the velocity field.
-The 6 free parameters of the model; $\{(xcen, ycen), i, PA_{kin}, rt, v_{asym}$, are first reduced to 5 by using the inclination from the {\em HST} axis ratio.
+The 6 free parameters of the model; $(xcen, ycen), i, PA_{kin}, rt, v_{asym}$, are first reduced to 5 by using the inclination from the {\em HST} axis ratio.
 We also fix the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential well, to leave only 3 free parameters to vary in the MCMC sampling.
@@
 The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
-This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\sim3.0$ velocity dispersions and we discuss the impact of this assumption in \cref{appsubsec:model_errors} by using sensible alternative values.
+This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\sim3.0$ velocity dispersions and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
 The reported errors on $\sigma_{int}$ take this assumption into account. \\
 
-The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries with the K-band atmospheric seeing profile (Table \ref{tab:pointings}).
+The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
 The velocity and velocity dispersion values are then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
@@
 We have confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates have converged around the 50th percentile values.
-The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in \cref{appsubsec:model_errors}.
+The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in Appendix \ref{appsubsec:model_errors}.
 
 Following the construction of a convolved model cube and the measurement of the beam-smeared maps we can extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
-There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
+There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshifts.
 We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
-An overview of these comparison samples is provided in \cref{app:comparison_samples}, describing also the approach used to compute average parameter values.
+An overview of these comparison samples is provided in Appendix \ref{app:comparison_samples}, describing also the approach used to compute average parameter values.
 
@@
 This extraction radius is shown with the vertical red dashed line in the panels of Figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
-The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017,Swinbank2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
-This is similar also to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\sim3R_{D}$), \citep{Tiley2016a}.
+The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Stott2016,Pelliccia2017,Harrison2017,Swinbank2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
+This is similar to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\sim3R_{D}$), \citep{Tiley2016a}.
 
@@
 In order to determine the beam-smearing correction factor, we also extract the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
-The beam-smearing correction factor ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in \cref{appsubsec:model_errors}.
+The beam-smearing correction factor ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in Appendix \ref{appsubsec:model_errors}.
 \\
@@
 2 KMOS pixels) with a mean extrapolation of 0.17$^{\prime\prime}$.
-The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the intrinsic and convolved $2R_{1/2}$ extraction radii marked on each velocity thumbnail.
+The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in Appendix \ref{app:kinematics_plots}, with the intrinsic and convolved $2R_{1/2}$ extraction radii marked on each velocity thumbnail.
 
@@
 $\sigma_{BS} = \sigma_{model} - \sigma_{assumed}$ (where $\sigma_{assumed}$ is fixed at 50kms$^{-1}$ as described in \cref{subsubec:model_cube}).
-The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS}$ correction is discussed further in \cref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
+The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
 We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.
 
-To measure the $\sigma_{int}$ value for each galaxy in our sample we use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the K-band and 55.4kms$^{-1}$ in the HK-band).
+To measure the $\sigma_{int}$ value for each galaxy in our sample we use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the {\it K}-band and 55.4kms$^{-1}$ in the H{\it K}-band).
 
@@
 The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
-The beam-smearing correction factor ($\sigma_{obs}/\sigma_{int}$) has a mean and median value of 0.77 and 0.79 respectively for the isolated field sample. \\
+The beam-smearing correction factor ($\sigma_{int}/\sigma_{obs}$) has a mean and median value of 0.77 and 0.79 respectively for the isolated field sample. \\
 
@@
  \hline
-b012141\_012208 & 32$\pm$13                    & 93$^{+48}_{-40}$                     & 94$\pm$18                 & 63$^{+28}_{-30}$                 & 1.47$^{+1.04}_{-0.92}$             & 122$^{+9}_{-9}$ & RD   \\
-b15573          & 61$\pm21$                    & 81$^{+30}_{-33}$                     & 111$\pm23$                 & 84$^{+28}_{-26}$          & 0.97$^{+0.47}_{-0.52}$            & 118$^{+10}_{18}$ & DD   \\
-bs006516        & 49$\pm4$                    & 61$^{+10}_{-9}$                     & 64$\pm8$                  & 45$^{+10}_{-9}$              & 1.35$^{+0.37}_{-0.38}$         & 144$^{+4}_{-4}$ & RD   \\
-bs006541        & 33$\pm8$         & 65$^{+24}_{-20}$          & 96$\pm7$                  & 83$^{+9}_{-16}$             & 0.78$^{+0.34}_{-0.26}$          & 23$^{+3}_{-4}$ & DD    \\
-bs008543        & 68$\pm13$                    & 111$^{+20}_{-16}$                    & 98$\pm7$                  & 71$^{+13}_{-10}$         & 1.56$^{+0.37}_{-0.38}$                & 114$^{+1}_{-1}$  & RD  \\
-bs009818        & 39$\pm16$                    & 84$^{+39}_{-23}$                     & 95$\pm19$                  & 79$^{+21}_{-31}$       & 1.06$^{+0.65}_{-0.41}$                   & 72$^{+13}_{-15}$ & RD    \\
-bs014828        & 31$\pm15$                    & 46$^{+23}_{-23}$                     & 97$\pm15$                  & 88$^{+15}_{-17}$      & 0.53$^{+0.28}_{-0.28}$               & 44$^{+15}_{-11}$  & DD  \\
-bs016759        & 55$\pm9$                    & 110$^{+30}_{-21}$                    & 82$\pm11$                  & 57$^{+17}_{-22}$         & 1.93$^{+0.93}_{-0.7}$               & 75$^{+6}_{-6}$ & RD    \\
-lbg\_20         & 20$\pm6$                    & 56$^{+30}_{-19}$                     & 55$\pm6$                  & 40$^{+7}_{-21}$         & 1.39$^{+1.04}_{-0.53}$              & 41$^{+9}_{-10}$ & RD   \\
-lbg\_24         & 26$\pm6$                    & 42$^{+9}_{-7}$                     & 64$\pm5$                  & 51$^{+5}_{-6}$           & 0.82$^{+0.21}_{-0.17}$          & 64$^{+3}_{-4}$ & DD   \\
-lbg\_25         & 14$\pm5$                    & 33$^{+13}_{-13}$                     & 53$\pm6$                  & 41$^{+6}_{-8}$         & 0.8$^{+0.37}_{-0.34}$                  & 87$^{+7}_{-12}$  & DD   \\
-lbg\_30         & 20$\pm6$                    & 66$^{+19}_{-17}$                    & 93$\pm11$                 & 77$^{+14}_{-17}$       & 0.86$^{+0.32}_{-0.27}$               & 46$^{+6}_{-42}$ & DD \\
-lbg\_32         & 65$\pm5$                    & 121$^{+13}_{-12}$                    & 104$\pm13$                 & 76$^{+16}_{-15}$       & 1.58$^{+0.36}_{-0.37}$               & 11$^{+2}_{-1}$ & RD \\
-lbg\_38         & 26$\pm7$                    & 97$^{+72}_{-34}$                     & 76$\pm10$                  & 53$^{+16}_{-53}$       & 1.82$^{+2.3}_{-0.86}$               & 47$^{+2}_{-3}$  & RD   \\
-lbg\_91         & 48$\pm10$                    & 91$^{+15}_{-18}$                     & 98$\pm8$                  & 71$^{+16}_{-14}$        & 1.28$^{+0.33}_{-0.39}$              & 40$^{+5}_{-3}$  & RD  \\
-lbg\_94         & 18$\pm8$                    & 34$^{+19}_{-15}$                     & 65$\pm6$                  & 55$^{+7}_{-8}$         & 0.62$^{+0.36}_{-0.29}$                & 41$^{+18}_{-9}$  & DD  \\
-lbg\_105        & 11$\pm8$                    & 32$^{+17}_{-16}$                     & 68$\pm18$                  & 59$^{+18}_{-18}$        & 0.54$^{+0.34}_{-0.32}$                & 170$^{+4}_{-7}$ & DD  \\
-lbg\_109        & 26$\pm8$                    & 53$^{+21}_{-15}$                     & 101$\pm16$                 & 91$^{+16}_{-18}$      & 0.58$^{+0.26}_{-0.2}$                & 157$^{+11}_{-11}$ & DD  \\
-lbg\_111        & 36$\pm12$         & 58$^{+24}_{-17}$                     & 90$\pm14$                  & 81$^{+14}_{-16}$                   & 0.71$^{+0.33}_{-0.25}$                 & 168$^{+4}_{-5}$ & DD  \\
-lbg\_112         & 27$\pm3$                    & 63$^{+19}_{-11}$                    & 92$\pm5$                 & 78$^{+8}_{-11}$       & 0.81$^{+0.28}_{-0.17}$               & 4$^{+34}_{-12}$ & DD \\
-lbg\_113        & 50$\pm20$           & 41$^{+41}_{-29}$                     & 116$\pm22$                 & 108$^{+23}_{-25}$                  & 0.39$^{+0.39}_{-0.29}$                & 1$^{+34}_{-26}$  & DD   \\
-lbg\_124         & 9$\pm8$                    & 32$^{+27}_{-18}$                    & 58$\pm19$                 & 46$^{+19}_{-23}$       & 0.71$^{+0.69}_{-0.5}$               & 39$^{+20}_{-14}$ & DD \\
-$^{*}$n3\_006         & 36$\pm23$                    & 81$^{+47}_{-29}$                     & 144$\pm26$                 & 125$^{+27}_{-31}$          & 0.65$^{+0.41}_{-0.27}$                & 156$^{+13}_{-12}$ & DD   \\
-n3\_009         & 21$\pm9$                    & 49$^{+26}_{-16}$                     & 77$\pm13$                  & 48$^{+14}_{-45}$          & 1.01$^{+1.1}_{-0.45}$                & 20$^{+28}_{-25}$  & RD   \\
-n\_c3           & 26$\pm8$                    & 51$^{+17}_{-18}$                     & 96$\pm11$                  & 72$^{+12}_{-13}$          & 0.72$^{+0.28}_{-0.29}$                & 137$^{+4}_{-15}$  & DD  \\
-lab18           & 23$\pm11$                   & 41$^{+17}_{-14}$                     & 87$\pm6$                  & 62$^{+7}_{-15}$           & 0.67$^{+0.32}_{-0.24}$                 & 54$^{+18}_{-26}$ & DD    \\
-$^{*}$lab25           & 37$\pm11$                    & 48$^{+22}_{-16}$                     & 80$\pm8$                  & 49$^{+10}_{-19}$          & 0.98$^{+0.59}_{-0.4}$                & 72$^{+14}_{-13}$ & DD   \\
-s\_sa22a-d3     & 53$\pm17$                    & 109$^{+52}_{-32}$                    & 127$\pm13$                 & 93$^{+20}_{-36}$          & 1.16$^{+0.72}_{-0.43}$               & 30$^{+2}_{-2}$ & RD    \\
-s\_sa22b-c20    & 66$\pm18$                    & 139$^{+33}_{-30}$                    & 112$\pm17$                 & 48$^{+34}_{-51}$          & 2.87$^{+3.12}_{-2.14}$                & 37$^{+26}_{-11}$ & RD   \\
-$^{*}$s\_sa22b-d5     & 27$\pm10$                    & 57$^{+26}_{-23}$                     & 67$\pm20$                  & 23$^{+23}_{-18}$          & 2.45$^{+3.44}_{-2.41}$               & 60$^{+19}_{-19}$ & RD   \\
-s\_sa22b-d9     & 32$\pm14$                    & 46$^{+22}_{-15}$                     & 99$\pm8$                  & 73$^{+10}_{-17}$             & 0.63$^{+0.33}_{-0.23}$                 & 12$^{+23}_{-7}$ & DD   \\
+b012141\_012208 & 32$\pm$13                    & 93$^{+48}_{-40}$                     & 94$\pm$18                 & 63$^{+28}_{-30}$                 & 1.47$^{+1.04}_{-0.92}$             & 122$^{+9}_{-9}$ & RD   \\[1ex]
+b15573          & 61$\pm21$                    & 81$^{+30}_{-33}$                     & 111$\pm23$                 & 84$^{+28}_{-26}$          & 0.97$^{+0.47}_{-0.52}$            & 118$^{+10}_{18}$ & DD   \\[1ex]
+bs006516        & 49$\pm4$                    & 61$^{+10}_{-9}$                     & 64$\pm8$                  & 45$^{+10}_{-9}$              & 1.35$^{+0.37}_{-0.38}$         & 144$^{+4}_{-4}$ & RD   \\[1ex]
+bs006541        & 33$\pm8$         & 65$^{+24}_{-20}$          & 96$\pm7$                  & 83$^{+9}_{-16}$             & 0.78$^{+0.34}_{-0.26}$          & 23$^{+3}_{-4}$ & DD    \\[1ex]
+bs008543        & 68$\pm13$                    & 111$^{+20}_{-16}$                    & 98$\pm7$                  & 71$^{+13}_{-10}$         & 1.56$^{+0.37}_{-0.38}$                & 114$^{+1}_{-1}$  & RD  \\[1ex]
+bs009818        & 39$\pm16$                    & 84$^{+39}_{-23}$                     & 95$\pm19$                  & 79$^{+21}_{-31}$       & 1.06$^{+0.65}_{-0.41}$                   & 72$^{+13}_{-15}$ & RD    \\[1ex]
+bs014828        & 31$\pm15$                    & 46$^{+23}_{-23}$                     & 97$\pm15$                  & 88$^{+15}_{-17}$      & 0.53$^{+0.28}_{-0.28}$               & 44$^{+15}_{-11}$  & DD  \\[1ex]
+bs016759        & 55$\pm9$                    & 110$^{+30}_{-21}$                    & 82$\pm11$                  & 57$^{+17}_{-22}$         & 1.93$^{+0.93}_{-0.7}$               & 75$^{+6}_{-6}$ & RD    \\[1ex]
+lbg\_20         & 20$\pm6$                    & 56$^{+30}_{-19}$                     & 55$\pm6$                  & 40$^{+7}_{-21}$         & 1.39$^{+1.04}_{-0.53}$              & 41$^{+9}_{-10}$ & RD   \\[1ex]
+lbg\_24         & 26$\pm6$                    & 42$^{+9}_{-7}$                     & 64$\pm5$                  & 51$^{+5}_{-6}$           & 0.82$^{+0.21}_{-0.17}$          & 64$^{+3}_{-4}$ & DD   \\[1ex]
+lbg\_25         & 14$\pm5$                    & 33$^{+13}_{-13}$                     & 53$\pm6$                  & 41$^{+6}_{-8}$         & 0.8$^{+0.37}_{-0.34}$                  & 87$^{+7}_{-12}$  & DD   \\[1ex]
+lbg\_30         & 20$\pm6$                    & 66$^{+19}_{-17}$                    & 93$\pm11$                 & 77$^{+14}_{-17}$       & 0.86$^{+0.32}_{-0.27}$               & 46$^{+6}_{-42}$ & DD \\[1ex]
+lbg\_32         & 65$\pm5$                    & 121$^{+13}_{-12}$                    & 104$\pm13$                 & 76$^{+16}_{-15}$       & 1.58$^{+0.36}_{-0.37}$               & 11$^{+2}_{-1}$ & RD \\[1ex]
+lbg\_38         & 26$\pm7$                    & 97$^{+72}_{-34}$                     & 76$\pm10$                  & 53$^{+16}_{-53}$       & 1.82$^{+2.3}_{-0.86}$               & 47$^{+2}_{-3}$  & RD   \\[1ex]
+lbg\_91         & 48$\pm10$                    & 91$^{+15}_{-18}$                     & 98$\pm8$                  & 71$^{+16}_{-14}$        & 1.28$^{+0.33}_{-0.39}$              & 40$^{+5}_{-3}$  & RD  \\[1ex]
+lbg\_94         & 18$\pm8$                    & 34$^{+19}_{-15}$                     & 65$\pm6$                  & 55$^{+7}_{-8}$         & 0.62$^{+0.36}_{-0.29}$                & 41$^{+18}_{-9}$  & DD  \\[1ex]
+lbg\_105        & 11$\pm8$                    & 32$^{+17}_{-16}$                     & 68$\pm18$                  & 59$^{+18}_{-18}$        & 0.54$^{+0.34}_{-0.32}$                & 170$^{+4}_{-7}$ & DD  \\[1ex]
+lbg\_109        & 26$\pm8$                    & 53$^{+21}_{-15}$                     & 101$\pm16$                 & 91$^{+16}_{-18}$      & 0.58$^{+0.26}_{-0.2}$                & 157$^{+11}_{-11}$ & DD  \\[1ex]
+lbg\_111        & 36$\pm12$         & 58$^{+24}_{-17}$                     & 90$\pm14$                  & 81$^{+14}_{-16}$                   & 0.71$^{+0.33}_{-0.25}$                 & 168$^{+4}_{-5}$ & DD  \\[1ex]
+lbg\_112         & 27$\pm3$                    & 63$^{+19}_{-11}$                    & 92$\pm5$                 & 78$^{+8}_{-11}$       & 0.81$^{+0.28}_{-0.17}$               & 4$^{+34}_{-12}$ & DD \\[1ex]
+lbg\_113        & 50$\pm20$           & 41$^{+41}_{-29}$                     & 116$\pm22$                 & 108$^{+23}_{-25}$                  & 0.39$^{+0.39}_{-0.29}$                & 1$^{+34}_{-26}$  & DD   \\[1ex]
+lbg\_124         & 9$\pm8$                    & 32$^{+27}_{-18}$                    & 58$\pm19$                 & 46$^{+19}_{-23}$       & 0.71$^{+0.69}_{-0.5}$               & 39$^{+20}_{-14}$ & DD \\[1ex]
+$^{*}$n3\_006         & 36$\pm23$                    & 81$^{+47}_{-29}$                     & 144$\pm26$                 & 125$^{+27}_{-31}$          & 0.65$^{+0.41}_{-0.27}$                & 156$^{+13}_{-12}$ & DD   \\[1ex]
+n3\_009         & 21$\pm9$                    & 49$^{+26}_{-16}$                     & 77$\pm13$                  & 48$^{+14}_{-45}$          & 1.01$^{+1.1}_{-0.45}$                & 20$^{+28}_{-25}$  & RD   \\[1ex]
+n\_c3           & 26$\pm8$                    & 51$^{+17}_{-18}$                     & 96$\pm11$                  & 72$^{+12}_{-13}$          & 0.72$^{+0.28}_{-0.29}$                & 137$^{+4}_{-15}$  & DD  \\[1ex]
+lab18           & 23$\pm11$                   & 41$^{+17}_{-14}$                     & 87$\pm6$                  & 62$^{+7}_{-15}$           & 0.67$^{+0.32}_{-0.24}$                 & 54$^{+18}_{-26}$ & DD    \\[1ex]
+$^{*}$lab25           & 37$\pm11$                    & 48$^{+22}_{-16}$                     & 80$\pm8$                  & 49$^{+10}_{-19}$          & 0.98$^{+0.59}_{-0.4}$                & 72$^{+14}_{-13}$ & DD   \\[1ex]
+s\_sa22a-d3     & 53$\pm17$                    & 109$^{+52}_{-32}$                    & 127$\pm13$                 & 93$^{+20}_{-36}$          & 1.16$^{+0.72}_{-0.43}$               & 30$^{+2}_{-2}$ & RD    \\[1ex]
+s\_sa22b-c20    & 66$\pm18$                    & 139$^{+33}_{-30}$                    & 112$\pm17$                 & 48$^{+34}_{-51}$          & 2.87$^{+3.12}_{-2.14}$                & 37$^{+26}_{-11}$ & RD   \\[1ex]
+$^{*}$s\_sa22b-d5     & 27$\pm10$                    & 57$^{+26}_{-23}$                     & 67$\pm20$                  & 23$^{+23}_{-18}$          & 2.45$^{+3.44}_{-2.41}$               & 60$^{+19}_{-19}$ & RD   \\[1ex]
+s\_sa22b-d9     & 32$\pm14$                    & 46$^{+22}_{-15}$                     & 99$\pm8$                  & 73$^{+10}_{-17}$             & 0.63$^{+0.33}_{-0.23}$                 & 12$^{+23}_{-7}$ & DD   \\[1ex]
 $^{*}$s\_sa22b-md25   & 44$\pm15$           & 57$^{+34}_{-24}$                     & 102$\pm19$   & 75$^{+21}_{-30}$                   & 0.76$^{+0.56}_{-0.39}$                & 9$^{+12}_{-7}$ & DD
@@
 This is a simple empirical diagnostic for whether a galaxy is `Rotation Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
-a method to measure the prevalence of rotational and random motions][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
+a method to measure the prevalence of rotational and random motions;][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
 Previous studies have used various classification schemes of varying complexity to identify rotation dominated galaxies which also appear to be `disk-like' and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
@@
 the bottom grid in Figure \ref{fig:main_body_kinematic_grids}).
+
 This has been discussed in \cite{Hung2015}, where redshifted local interacting galaxies are misclassified as single rotating disks on the basis of their kinematics. 
@@
 It is difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e.
-clumpy disk galaxies \citep[e.g.][]{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
+clumpy disk galaxies e.g.
+\citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
 Perhaps the most telling diagnostic are two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map. \\
@@
 In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
-In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
-In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in \cref{subsec:AMAZE}.
+In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification is outlined in their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
+In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in Appendix \ref{subsec:AMAZE}.
 We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
 The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
-We plot the best fitting smeared and intrinsic models for the isolated field galaxies in \cref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
+We plot the best fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
 
@@
 For these galaxies we have measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
-The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}.
-
-Throughout the following sections we analyse the derived kinematic parameters for these 32 galaxies, referred to as the `isolated field sample', placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{app:comparison_samples}.
-In \cref{app:comparison_samples} we describe also the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.
+The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in Appendix \ref{app:kinematics_plots}.
+
+Throughout the following sections we analyse the derived kinematic parameters for these 32 galaxies, referred to as the `isolated field sample', placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in Appendix \ref{app:comparison_samples}.
+In Appendix \ref{app:comparison_samples} we also describe the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.
 During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that they trace the average properties of typical star-forming galaxies at their respective mean redshifts.
@@
     \end{subfigure}
-    \caption{{\it Left:} We plot log($V_{C}$) vs. $M_{\star}$ for the isolated field sample, with the rotation dominated galaxies in red and dispersion dominated galaxies with the hollow symbols.
-    Also plotted with the solid green line is the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey, with the shaded region showing the associated $\sim$0.2 dex scatter on the fit.
+    \caption{{\it Left:} We plot log($V_{C}$) vs.
+log($M_{\star}/M_{\odot}$) for the isolated field sample, with the rotation dominated galaxies in red and dispersion dominated galaxies with the hollow symbols.
+    We also plot with the solid green line the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey \protect\cite{Harrison2017}, with the shaded region showing the associated $\sim$0.2 dex scatter on the fit.
     This $z\sim0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in \protect\cite{Reyes2011}.
@@
 However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,DiTeodoro2016,Simons2016,Pelliccia2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
-At $z\sim 3$ observations are limited and in \cite{Gnerucci2011} an offset of -1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample defined in \cref{subsec:AMAZE} consistent with the $z\sim0$ relation.
+At $z\sim 3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} consistent with the $z\sim0$ relation.
 \\
@@
 We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
-These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to KROSS and traced with H$\alpha$ emission.
-In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
-The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these limits.
-\\
-
-The rotation dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\sim 0.9$ relation, but perhaps with a slight tendency to lie below the relation.
+These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
+In \cite{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
+The agreement between the parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these redshifts.
+\\
+
+The rotation dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\sim 0.9$ relation, but with a tendency to lie below the relation.
+When considered alone, the mean velocity of the rotation dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=10.0$ is $\sim0.1$ dex beneath the KROSS relation at the same mass.
 The dispersion dominated KDS galaxies sit clearly separated and below the $z\sim0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\sim0.9$ dispersion dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We plot also the five $z\sim3$ galaxies from the AMAZE clean sample, which are consistent within the scatter with the $z\sim0.9$ relation.
+We plot also the five $z\sim3$ galaxies from the AMAZE clean sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\sim0.9$ .
 
@@
     The mean $\sigma_{int}$ values increase from $\sim 15kms^{-1}$ in the local universe to $> 70kms^{-1}$ at $z > 3$.
-    The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values and in each case for $V_{C} = 150kms^{-1}$.
+    The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values and in each case for $V_{C} = 125kms^{-1}$.
     These are intended as indicators of the way in which $\sigma_{int}$ evolves in galaxies in different mean $M_{\star}$, where this on average gives an indication of the extent to which the stellar population has been accumulated, which may provide increased stability for an extended rotating disk.
@@
 
-In the right panel of Figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see \cref{app:comparison_samples}) and KDS isolated field samples to highlight two observations:
+In the right panel of Figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see Appendix \ref{app:comparison_samples}) and KDS isolated field samples to highlight two observations:
 \begin{itemize}
@@
 In the right panel of Figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
-It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in \cref{app:comparison_samples}) are directly comparable.
+It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in Appendix \ref{app:comparison_samples}) are directly comparable.
 The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
@@
 The relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
-In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.
+In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.
 \\
@@
     \includegraphics[width=0.49\textwidth]{v_over_sigma_versus_mass.png}
-    \caption{The distribution of galaxies in the $V_{C}$/$\sigma_{int}$ vs. $M_{\star}$ plane is shown for the isolated field sample, along with for the galaxies in the AMAZE Clean sample.
+    \caption{The distribution of galaxies in the $V_{C}$/$\sigma_{int}$ vs. $M_{\star}$ plane is shown for the isolated field sample, along with the galaxies in the AMAZE Clean sample.
     We mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies in this panel, finding that more massive galaxies (e.g.
@@
     {\it Right:} We plot the associated rotation dominated fraction, defined as the fraction of galaxies in each sample with $V_{C}/\sigma_{int} > 1$.
-    The narrow shaded regions represent the maximum and miminum RDF, computed as described in \protect\cref{app:comparison_samples}.
+    The narrow shaded regions represent the maximum and miminum RDF, computed as described in Appendix \protect\ref{app:comparison_samples}.
     It appears that the rotation dominated fraction drops from $\sim 100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\sim 40\%$ at z $\sim 3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher rotation dominated fractions.
@@
 Clearly the isolated field sample galaxies are in a different physical regime, with mean and median $V_{C}/\sigma_{int}$ values of $1.08^{+0.18}_{-0.15}$ and $0.97^{+0.14}_{-0.11}$ respectively.
-This is despite many of the dispersion dominated galaxies showing clear velocity gradients across the observed velocity maps (\cref{app:kinematics_plots}), with the arctangent model providing a good fit to the rotation curves.
+This is despite many of the dispersion dominated galaxies showing clear velocity gradients across the observed velocity maps (Appendix \ref{app:kinematics_plots}), with the arctangent model providing a good fit to the rotation curves.
 This suggests that although rotational motions are present within the disks, they are small or comparable with the elevated $\sigma_{int}$ values observed throughout the $z \sim 3.5$ sample. \\
@@
 
-In the left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in \cref{app:comparison_samples}.
+In the left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in Appendix \ref{app:comparison_samples}.
 The filled symbols and black errorbars in the left panel represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
@@
 This draws again from the idea that higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the sample rotation dominated fraction higher (see \cref{sec:discussion}).
-In sum, the rotation dominated galaxies in the isolated field sample appear to conform with a redshift invariant $V_{C}$ - $M_{\star}$ relation.
+In summary, the rotation dominated galaxies in the isolated field sample appear to conform with a redshift invariant $V_{C}$ - $M_{\star}$ relation.
 Due to increased velocity dispersions, these rotation dominated galaxies account for only $34\%$ of the field sample and so are less representative of typical star-forming galaxies at $z\sim3.5$ than at intermediate and low redshifts.
@@
 The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion dominated galaxies ($66\%$ of the sample) and probable pressure support from turbulent motions \citep[e.g.][]{Burkert2010} partially supporting gravity.
-This increased number of dispersion dominated galaxies in comparison to at low and intermediate redshifts appears to be driven by high velocity dispersions at $z\sim3.5$.
+This increased number of dispersion dominated galaxies in comparison to low and intermediate redshifts appears to be driven by high velocity dispersions at $z\sim3.5$.
 In this section we discuss possible physical origins for the elevated random motions traced by $\sigma_{int}$ and their impact on the galactic dynamics.
@@
 This is done by computing the difference between the model predicted $\sigma_{int}$ value at the stellar mass of each comparison survey and at the reference mass for the appropriate redshift and shifting the reported $\sigma_{int}$ by this value.
-We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 10.0$ (the mean mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (left panel of Figure \ref{fig:sigma_shifted}) and we only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
+We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 10.0$ (the mean mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}) and we only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
 In both panels the dark grey shaded regions encompass the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
@@
 Rotation dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions as shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}, constituting only $\sim1/3$ of the isolated field sample at $z\sim3.5$.
-This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
+This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale length \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
 Recent results indicate that these systems become strongly baryon-dominated on the galaxy disk scale at high redshift \citep{Ubler2017,Lang2017,Genzel2017}, which may imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.
@@
 We have attempted to account for beam smearing using half-light radius and velocity gradient dependent dynamical modelling, but we acknowledge that these observations are challenging and cannot rule out the presence of unresolved velocity gradients in our seeing-limited dataset.
-Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity disperion on galaxy size \citep[e.g.][]{Newman2013}.
+Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity dispersion on galaxy size \citep[e.g.][]{Newman2013}.
 Dispersion dominated galaxies are therefore likely to be at an earlier evolutionary stage and unstable to gravitational instabilities which generate turbulence which is then maintained by the potential energy of the gas in the disk \citep{Burkert2010,Newman2013}.
@@
 
-In sum, the isolated field sample galaxies are diverse and kinematically premature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
+In summary, the isolated field sample galaxies are diverse and kinematically immature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
 In the context of the equilibrium model explored here, these galaxies will evolve gradually with redshift along the velocity-mass relationship into stable disk galaxies which have converted their gas reservoirs into stellar mass \citep[e.g.][]{Lilly2013,Tacconi2013,Wisnioski2015,Tacconi2017}.
@@
 These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}/M_{\odot})< 10.5$ typical main sequence galaxies at these redshifts.
-By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding consistent merger rates in the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
-We make made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (\cref{app:comparison_samples} and Table \ref{tab:evolution_numbers}).
+By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
+We have made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (Appendix \ref{app:comparison_samples} and Table \ref{tab:evolution_numbers}).
 The main conclusions of this work are summarised as follows:
@@
 \begin{itemize}
-    \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ and $V_{C} = 78.8^{+5.4}_{-5.1}kms^{-1}$ (left panel of Figure \ref{fig:v_sig_and_v}).
-    \item 13/32 isolated field sample galaxies are rotation dominated and 19/32 are dispersion dominated as indicated by the ratio $V_{C}/\sigma_{int}$, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (left and right panels of Figure \ref{fig:v_sig_and_v}).
-    This gives a rotation dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
+    \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $V_{C} = 76.7^{+4.9}_{-4.5}kms^{-1}$ and $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ (right panels of Figures \ref{fig:tf_relation} and \ref{fig:sigma_and_v_sigma_w_redshift} respectively).
+    Rotation (dispersion) dominated galaxies are defined as those with $V_{C}/\sigma_{int} > (<) 1$.  
+    \item We plot the mean $V_{C}$ values of the comparison samples and the KDS isolated field sample, finding significant diversity in $V_{C}$ measurements in each survey (right panel of Figure \ref{fig:tf_relation}).
+    The spread in measurements is a result of the samples containing a mixture of rotation and dispersion dominated galaxies with varying $M_{\star}$ values, and the low mean KDS value is primarily the result of averaging over a sample with a high fraction of dispersion dominated galaxies and indicating the impact pressure support may have on reducing rotation velocities.
+    At higher $M_{\star}$, the accumulation of a stellar population provides stability, leading to an interplay between $\sigma_{int}$ and $V_{C}$ mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Law2012b,Wisnioski2015}.
     \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}/M_{\odot}) < 11.0$ at $z\sim0.9$ in the KROSS survey (Figure \ref{fig:tf_relation}).
 %something else here when finished writing the TF section
-    This relation is consistent with SFGs at $z=0$ and so we report no significant evolution in the slope or zero-point of the smTFR between $z=0-3.5$.
+    This relation is consistent with star-forming galaxies at $z=0$ and so we report no significant evolution in the slope or zero-point of the smTFR between $z=0-3.5$.
     Constistency of sample selection and measurement techniques are crucial factors when determining evolution in the $V_{C}$ vs. $M_{\star}$ plane by comparing samples at different redshifts.
     The dispersion dominated galaxies scatter below the trend, with the same slope as the rotation dominated galaxies.
-    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in \cref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    This is in line with a simple equilibrium model prescription in which the gas fractions and impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to increase random motions within high-redshift galaxies.
-    \item We plot the mean $V_{C}$ values of the comparison samples and the KDS isolated field sample, finding significant diversity in $V_{C}$ measurements in each survey (right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    The spread in measurements is a result of the samples containing a mixture of rotation and dispersion dominated galaxies with varying $M_{\star}$ values, and the low mean KDS value is primarily the result of averaging over a sample with a high fraction of dispersion dominated galaxies and indicating the impact pressure support may have on reducing rotation velocities.
-    At higher $M_{\star}$ the accumulation of a stellar population provides stability, leading to an interplay between $\sigma_{int}$ and $V_{C}$ mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Wisnioski2015}.
+    \item When considering the rotation dominated galaxies alone the median and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}kms^{-1}$ respectively, which are lower than expected from a simple virial theorem calculation using the mean mass and half-light radius of the sample.
+    This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in the system \citep[e.g.][]{Burkert2010}.  
+    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in Appendix \ref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    This is in line with a simple equilibrium model prescription in which the gas fractions and the impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to increase random motions within high-redshift galaxies.
+    \item 13/32 isolated field sample galaxies are rotation dominated and 19/32 are dispersion dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
+    This gives a rotation dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
 
@@
  AMAZE & 3.0 & 10.0 & $3.59^{+1.45}_{-1.1}$ & $2.1^{+4.7}_{-1.15}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+27.0}_{-48.0}$ & $217^{+59.1}_{-40.2}$ & $129^{+166.0}_{-50.2}$ \\
- \textbf{KDS} & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.37^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $78.8^{+5.4}_{-5.1}$ & $60.0^{+49.1}_{-18.2}$ \\
+ \textbf{KDS} & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.37^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $76.7^{+4.9}_{-4.5}$ & $57.0^{+49.1}_{-18.2}$ \\
  \hline
@@
 The galaxies in the AMAZE Unconstrained sample generally have much larger $V_{C}$ values despite occupying a similar stellar mass range to our isolated field sample, with this being a consequence of large model extrapolations beyond the observed data.
-We follow the bootstrapping procedure described in \cref{app:comparison_samples} to compute error weighted averages and statistical errors.
+We follow the bootstrapping procedure described in Appendix \ref{app:comparison_samples} to compute error weighted averages and statistical errors.
 

### 2017-03-28 paper.tex
Meeting with Jim and Ross 28th March

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
+
+\author[O.J. Turner et al.]{
+O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
+M. Cirasuolo,$^{1,2}$
+C. M. Harrison,$^{2,3}$
+J. Dunlop,$^{1}$
+R. J. McLure,$^{1}$\newauthor
+A. M. Swinbank,$^{3,4}$
+H. L. Johnson,$^{3,4}$
+D. Sobral,$^{5}$
+J. Matthee,$^{6}$
+R. M. Sharples$^{3,4}$
+\\
+$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
+$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
+$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
+$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
+$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
+$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}
+
 %\author[O.J. Turner et al.]{
-%O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
-%M. Cirasuolo,$^{1,2}$
-%C. M. Harrison,$^{2,3}$
-%J. Dunlop,$^{1}$
-%R. J. McLure,$^{1}$\newauthor
-%A. M. Swinbank,$^{3,4}$
-%H. L. Johnson,$^{3,4}$
-%D. Sobral,$^{5}$
-%J. Matthee,$^{6}$
-%R. M. Sharples$^{3,4}$
+%O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk}}$
 %\\
 %$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
-%$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
-%$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
-%$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
-%$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
-%$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}
-
-\author[O.J. Turner et al.]{
-O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk}}$
-\\
-$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
-$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany
-}
+%$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany
+%}
 
@@
 \caption{This table summarises the KDS pointing statistics for the full observed sample of 77 galaxies.
-The columns list the pointing name, the galaxy environment probed, the central pointing coordinates, the number of observed, detected, resolved and merging objects as described in \protect\cref{subsubsec:datareduction}, the waveband observed with KMOS, the exposure time and the PSF measured in the {\it K}-band.}
+The columns list the pointing name and galaxy environment probed, the central pointing coordinates, the number of observed, detected, resolved and merging objects as described in \protect\cref{subsubsec:datareduction}, the waveband observed with KMOS, the exposure time and the PSF measured in the {\it K}-band.}
 \label{tab:pointings}
-\begin{tabular}{c c c c c c c c c c c c c c}
+\begin{tabular}{l l l l l l l l l l l l l}
 
  \hline
-Pointing & Environment & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band$^{a}$ & Exp (ks) & PSF ($^{\prime\prime}$)$^{b}$  \\
+Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band$^{a}$ & Exp (ks) & PSF ($^{\prime\prime}$)$^{b}$  \\
  \hline
- GOODS-S-P1 & FIELD & 03:32:22 & $-$27:52:51 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & K & 32.4 & 0.50 \\
-GOODS-S-P2 & FIELD & 03:32:35 & $-$27:43:15 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & K & 31.8 & 0.52 \\
-SSA22-P1 & CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
-SSA22-P2 & FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
+ \scriptsize{\bf GOODS-S-P1(FIELD)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & K & 32.4 & 0.50 \\
+\scriptsize{\bf GOODS-S-P2(FIELD)} & 03:32:32.217 & $-$27:43:08.000 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & K & 31.8 & 0.52 \\
+\scriptsize{\bf SSA22-P1(CLUSTER)} & 22:17:11.867 & $+$00:15:44.700 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
+\scriptsize{\bf SSA22-P2(FIELD)} & 22:17:35.120 & $+$00:09:30.500 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
 
@@
     \caption{{\it Left:} The distribution of 49 KDS galaxies (see \cref{subsubsec:sed_fitting}) in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
-    Also plotted in this plane are $\sim4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey, with the filled squares denoting the density in of galaxies in that region.
+    Also plotted in this plane are $\sim4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density in of galaxies in that region.
     We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
-    {\it Right:} We plot the location of the same 49 KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
-    The same GOODS-S galaxies from the 3D-{\em HST} survey \protect\citep{Brammer2012,Momcheva2016} at $3.0 < z < 3.8$ are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
+    {\it Right:} We plot the location of the 49 KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
+    The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
     The black solid line and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
@@
 \subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
-We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
-During the SED modelling we assume solar metallicity stellar templates and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
-A Chabrier IMF is used with a reduced set of BC03 \citep{Bruzual2003} templates in the fitting procedure.
-We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
-The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}/M_{\odot}) = 10.0$.
-In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and {\it K}-band detections lower than 2-$\sigma$ significance.
-For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
-\\
+In order to constrain their SFRs and stellar masses, the available photometry for the KDS targets was analysed using the SED fitting software described in \cite{McLure2011} and \cite{McLeod2015}.
+The photometry for each target was fit with the same set of solar metallicity BC03 \citep{Bruzual2003} templates recommended for reproducing the properties of star-forming galaxies by \cite{Wuyts2011a}, and derived stellar masses and SFRs were based on a Chabrier IMF.
+During the SED fitting process, dust attenuation was accounted for using the \cite{Calzetti2000} reddening law, with dust attenuation allowed to vary freely within the range $0.0<A_{V}<2.5$.
+Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 10.0$. 
+We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq 0.1$ dex, but this change does not affect the conclusions of this work.
+In SSA22, 29 targets (36\% of the full KDS sample) do not have robust SFR measurements due to being undetected at $\geq 2\sigma$ significance in the available $J-$ and $K-$band photometry. \\
 
@@
 
-This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012}, with the median ratio of $\chi ^{2}$ $\sim 1$ between the different fitting methods.
+This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models and bulge/disk models with both an n = 1 and n = 4 component (following the procedure described in \cite{Bruce2012}) with the fixed exponential disk value of n = 1 , with the median ratio of $\chi ^{2}$ $\sim 1$ between the different fitting methods.
 Additionally, 22 GOODS-S objects are also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is n = 1.2.
@@
 \begin{threeparttable}
-\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\tt GALFIT} \protect\citep{Peng2010_galfit}}
+\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\tt GALFIT} \protect\citep{Peng2010_galfit}.}
 \label{tab:phys-props}
-\begin{tabular}{ccccccccccc}
+\begin{tabular}{lllllllllll}
 
@@
  \hline
-b012141\_012208 & 03:32:23 & $-$27:51:57 & 3.471        & 24.12  & 10.16 & 59 & 0.36        & 72        & 9     & 1.57      \\
-b15573          & 03:32:28 & $-$27:51:00 & 3.583        & 23.6   & 10.37 & 27 & 0.28        & 78        & 146   & 0.52      \\
-bs006516        & 03:32:15 & $-$27:50:46 & 3.215        & 23.94  & 9.85  & 14 & 0.50         & 61        & 146   & 1.91      \\
-bs006541        & 03:32:15 & $-$27:52:05 & 3.475       & 23.44  & 10.19 & 18 & 0.44        & 66        & 168   & 1.83      \\
-bs008543        & 03:32:18 & $-$27:50:50 & 3.474        & 22.73  & 10.67 & 42 & 0.50         & 61        & 67    & 1.59      \\
-bs009818        & 03:32:20 & $-$27:53:01 & 3.706        & 24.18  & 9.79  & 33 & 0.80         & 37        & 148   & 1.24      \\
-bs014828        & 03:32:27 & $-$27:52:26 & 3.562        & 23.58  & 10.15 & 30 & 0.31        & 76        & 63    & 1.61      \\
-bs016759        & 03:32:29 & $-$27:48:53 & 3.602       & 23.85  & 9.99  & 9  & 0.65        & 50        & 49    & 0.87      \\
-lbg\_20         & 03:32:41 & $-$27:52:21 & 3.225        & 24.97  & 9.61  & 5  & 0.64        & 52        & 1     & 1.28      \\
-lbg\_24         & 03:32:40 & $-$27:39:57 & 3.279       & 24.67  & 9.71  & 6  & 0.53        & 60        & 34    & 1.27      \\
-lbg\_25         & 03:32:29 & $-$27:40:22 & 3.322        & 24.95  & 9.44  & 6  & 0.30         & 76        & 78    & 1.18      \\
-lbg\_30         & 03:32:43 & $-$27:42:06 & 3.419        & 23.85  & 10.13  & 29  & 0.79         & 38        & 66    & 0.95      \\
-lbg\_32         & 03:32:34 & $-$27:41:24 & 3.417      & 23.84  & 10.17 & 52 & 0.60         & 54        & 40    & 1.88      \\
-lbg\_38         & 03:32:22 & $-$27:44:38 & 3.488       & 24.58  & 10.03 & 8  & 0.58        & 56        & 137   & 0.92      \\
-lbg\_91         & 03:32:27 & $-$27:41:52 & 3.170       & 24.65  & 9.80   & 6  & 0.58        & 56        & 79    & 0.89 \\
-lbg\_94         & 03:32:29 & $-$27:44:12 & 3.367       & 24.54  & 10.01 & 8  & 0.22        & 84        & 81    & 1.16      \\
-lbg\_105        & 03:32:24 & $-$27:52:16 & 3.092      & 23.79  & 9.79  & 30 & 0.56        & 57        & 128   & 1.72      \\
-lbg\_109        & 03:32:21 & $-$27:43:46 & 3.600       & 24.63  & 9.73  & 9  & 0.60         & 54        & 119   & 1.98      \\
-lbg\_111        & 03:32:42 & $-$27:45:52 & 3.609       & 24.01  & 9.74  & 27 & 0.74        & 42        & 80    & 0.64      \\
-lbg\_112         & 03:32:17 & $-$27:42:18 & 3.617        & 25.16  & 9.67  & 5  & 0.79         & 38        & 43    & 0.46      \\
-lbg\_113        & 03:32:36 & $-$27:41:50 & 3.622      & 24.01  & 9.83  & 41 & 0.52        & 60        & 15    & 0.87      \\
-lbg\_124         & 03:32:33 & $-$27:50:07 & 3.794        & 24.96  & 9.09  & 10  & 0.56         & 57        & 50    & 0.78      \\
-$^{*}$n3\_006       & 22:17:25 & +00:11:18 & 3.069     & 22.98 & 10.64 & 50 & 0.57         & 57        & -    & 2.52      \\
-n3\_009       & 22:17:28 & $+$00:12:12 & 3.069 & -    & 8.72  & -            & 0.75        & 42        & 84    & 1.06      \\
-n\_c3         & 22:17:33 & $+$00:10:57 & 3.096       & 24.96 & 9.94  & -            & 0.71        & 46        & 94    & 0.56      \\
-lab18         & 22:17:29 & $+$00:07:52 & 3.101           & -    & 8.66  & -            & 0.85        & 32        & 27    & 0.46      \\
-$^{*}$lab25         & 22:17:23 & $+$00:15:51 & 3.067      & -    & 8.78  & -            & 0.57         & 57        & -    & 2.18      \\
-s\_sa22a-d3   & 22:17:32 & $+$00:11:33 & 3.069 & 23.46 & 9.88  & -            & 0.39        & 70        & 125   & 1.78      \\
-s\_sa22b-c20  & 22:17:49 & $+$00:10:14 & 3.196     & 23.91 & 9.74  & -            & 0.57        & 57        & 76    & 1.59      \\
-$^{*}$s\_sa22b-d5  & 22:17:36 & $+$00:06:10 & 3.175 & 23.72 & 10.32 & -            & 0.57         & 57        & -    & 3.30      \\
-s\_sa22b-d9   & 22:17:22 & $+$00:08:04 & 3.084    & 24.25 & 10.05 & -            & 0.65        & 50        & 60   & 0.5       \\
-$^{*}$s\_sa22b-md25 & 22:17:42 & $+$00:06:20 & 3.304     & 24.62 & 9.05  & -            & 0.57         & 57        & -    & 1.39
+b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 10.2 & 59 & 0.36        & 72        & 9     & 1.57      \\
+b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 10.4 & 27 & 0.28        & 78        & 146   & 0.52      \\
+bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.9  & 14 & 0.50         & 61        & 146   & 1.91      \\
+bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.2 & 18 & 0.44        & 66        & 168   & 1.83      \\
+bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.7 & 42 & 0.50         & 61        & 67    & 1.59      \\
+bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.8  & 33 & 0.80         & 37        & 148   & 1.24      \\
+bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 10.2 & 30 & 0.31        & 76        & 63    & 1.61      \\
+bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 10.0  & 9  & 0.65        & 50        & 49    & 0.87      \\
+lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.6  & 5  & 0.64        & 52        & 1     & 1.28      \\
+lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.7  & 6  & 0.53        & 60        & 34    & 1.27      \\
+lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 6  & 0.30         & 76        & 78    & 1.18      \\
+lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.1  & 29  & 0.79         & 38        & 66    & 0.95      \\
+lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 10.2 & 52 & 0.60         & 54        & 40    & 1.88      \\
+lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 10.0 & 8  & 0.58        & 56        & 137   & 0.92      \\
+lbg\_91         & 03:32:27.202 & $-$27:41:51.756 & 3.170       & 24.65  & 9.8   & 6  & 0.58        & 56        & 79    & 0.89 \\
+lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 10.0 & 8  & 0.22        & 84        & 81    & 1.16      \\
+lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.8  & 30 & 0.56        & 57        & 128   & 1.72      \\
+lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7  & 9  & 0.60         & 54        & 119   & 1.98      \\
+lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7  & 27 & 0.74        & 42        & 80    & 0.64      \\
+lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.7  & 5  & 0.79         & 38        & 43    & 0.46      \\
+lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.8  & 41 & 0.52        & 60        & 15    & 0.87      \\
+lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.1  & 10  & 0.56         & 57        & 50    & 0.78      \\
+$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.6 & 50 & 0.57         & 57        & -    & 2.52      \\
+n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7  & -            & 0.75        & 42        & 84    & 1.06      \\
+n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.9  & -            & 0.71        & 46        & 94    & 0.56      \\
+lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.7  & -            & 0.85        & 32        & 27    & 0.46      \\
+$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.8  & -            & 0.57         & 57        & -    & 2.18      \\
+s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.9  & -            & 0.39        & 70        & 125   & 1.78      \\
+s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.7  & -            & 0.57        & 57        & 76    & 1.59      \\
+$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.3 & -            & 0.57         & 57        & -    & 3.30      \\
+s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1 & -            & 0.65        & 50        & 60   & 0.5       \\
+$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 9.1  & -            & 0.57         & 57        & -    & 1.39
 
@@
 \begin{threeparttable}
-\caption{Dynamical Properties for the resolved and morphologically isolated KDS field galaxies}
+\caption{We present here the dynamical properties for the KDS isolated field sample galaxies.
+The observed properties are measured directly from the extracted two-dimensional maps, whereas $V_{C}$ and $\sigma_{int}$ have been corrected for the effects of beam-smearing as described throughout the text.
+Each galaxy is classified as rotation dominated or dispersion dominated if the ratio $V_{C}/\sigma_{int}$ is greater than or less than 1 respectively, as highlighted in the `Class' column.}
 \label{tab:kin_props}
-\begin{tabular}{cccccccc}
+\begin{tabular}{llllllll}
 
@@
 In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
-The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
+The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
 We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
@@
 The dispersion dominated KDS galaxies sit clearly separated and below the $z\sim0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\sim0.9$ dispersion dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We plot also the five $z\sim3$ galaxies from the AMAZE clean sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\sim0.9$ .
+We plot also the five $z\sim3$ galaxies from the AMAZE clean sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\sim0.9$.
 
@@
 
+CMH, AMS and RMS acknowledge the Science and Technology Facilities Council through grant code ST/L00075X/1.
+RJM acknowledges the support of the European Research Council via the award of a Consolidator Grant (PI: McLure).
+JSD acknowledges the support of the European Research Council via the award of an Advanced Grant (PI J. Dunlop), and the contribution of the EC FP7 SPACE project ASTRODEEP (Ref.No: 312725).
+AMS acknowledges the Leverhulme Foundation.
+JM acknowledges the support of a Huygens PhD fellowship from Leiden University.
+DS acknowledges financial support from the Netherlands Organization for Scientific research (NWO) through a Veni fellowship and from FCT through an FCT Investigator Starting Grant and Start-up Grant (IF/01154/2012/CP0189/CT0010).
 This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.

### 2017-03-28 paper.tex
Post-Jim comments

@@
 % Keep the title short and informative.
-\title[KDS: dynamical properties of 77 z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of typical star forming galaxies at $z\sim3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
+\title[KDS I: dynamical properties of 77 z$\simeq3.5$ galaxies]{The KMOS Deep Survey (KDS) I: dynamical measurements of typical star forming galaxies at $z\simeq3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
 Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)}}
@@
 C. M. Harrison,$^{2,3}$
-J. Dunlop,$^{1}$
-R. J. McLure,$^{1}$\newauthor
+R. J. McLure,$^{1}$
+J. S. Dunlop,$^{1}$\newauthor
 A. M. Swinbank,$^{3,4}$
@@
 \begin{abstract}
-We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
-These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
-We have made careful comparisons to other samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
-The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
-However only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
-The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e.
-$V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion dominated fraction.
-These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
-These random motions are likely to provide significant pressure support against gravity on the galactic disk scale.
+We present dynamical measurements for 77 star-forming galaxies at $z\simeq3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
+These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
+The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\simeq3$ in other samples, to which we have made careful comparisons.
+However only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
+The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e.
+$V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
+These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and may provide significant pressure support against gravity on the galactic disk scale.
 \end{abstract}
@@
 The galaxy population at all redshifts appears to be bimodal in many physical properties \citep[e.g.
-as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies.
+as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie on the red sequence, characterised by red optical colours, low star-formation rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star-formation rates and disky morphologies.
 For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
-This correlation, or `main sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
-The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
-At each redshift slice it has been suggested that galaxies on the main sequence evolve secularly, as regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
-This assumes that high-redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
+This correlation, or `main-sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
+The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
+At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, as regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
+This assumes that high redshift main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
 how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
@@
 stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}.
-To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main sequence galaxies (i.e.
+To account for the growing number density of quiescent galaxies from z$\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e.
 quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.
@@
 Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
-When interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em HST}), these data provide information about the range of physical processes which are driving galaxy evolution.
-In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.
-
-Random motions within the interstellar medium of SFGs appear to be increasing with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
-This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
+When interpreted in tandem with high-resolution imaging data from the {\it Hubble Space Telescope (HST)}, these data provide information about the range of physical processes which are driving galaxy evolution.
+In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high redshift campaigns.
+
+Random motions within the interstellar medium of SFGs appear to increase with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
+This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star-formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
 
 There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017,Ubler2017}.
-Systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
-Additionally, there has been increasing focus in the last few years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high-redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
+Systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
+Additionally, there has been increasing focus in recent years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
 These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotational velocities \citep{Burkert2010}.
@@
 
-In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
-There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item How applicable are strong line metallicity calibrators at high redshift?
+In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
+There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item How applicable are strong-line metallicity calibrators at high redshift?
 \item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
-\item What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
-\item What is the connection between the gas phase metallicity and  kinematics, particularly in terms of inflows and outflows of material? \end{enumerate}
-
-This paper focuses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
+\item What are the dynamical properties of main-sequence galaxies at this early stage in their lifetimes? 
+\item What is the connection between the gas-phase metallicity and  kinematics, particularly in terms of inflows and outflows of material? \end{enumerate}
+
+This paper focuses on the third question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$.
+By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
 \\
@@
 In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
-In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially resolved in the [O~{\sc III}]$\lambda$5007 emission line.
+In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission line.
 \cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible underlying physical mechanisms.
 We present our conclusions in \cref{sec:conclusion}.
-Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).
+Throughout this work we assume a flat $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).
 
@@
 \subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
-The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\sim3.5$, probing a representative section of the galaxy main sequence.
-The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
-The two key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the peak epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
+The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\simeq3.5$, probing a representative section of the galaxy main-sequence.
+The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
+The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation ( particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
 We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and a `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
-To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
+To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
 Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.
@@
 \subsubsection{Sample selection}\label{subsubsec:sample_selection}
-Target selection for the KDS sample is designed to pick out SFGs at $z \sim 3.5$, supported by deep multi-wavelength ancillary data.
+Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep multi-wavelength ancillary data.
 Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
 From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest S/N and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
-To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well studied fields that have a previous spectroscopic detection (see details below).
-Predominantly, the galaxies were originally selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
-However, a subset of the selected cluster galaxies in the SSA22 field were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
-We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main sequence at this redshift.
+To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a previous spectroscopic detection (see details below).
+Predominantly, the galaxies were originally selected for spectroscopic follow-up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
+However, a subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
+We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift.
 
@@
  \hline
- \scriptsize{\bf GOODS-S-P1(FIELD)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & K & 32.4 & 0.50 \\
-\scriptsize{\bf GOODS-S-P2(FIELD)} & 03:32:32.217 & $-$27:43:08.000 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & K & 31.8 & 0.52 \\
-\scriptsize{\bf SSA22-P1(CLUSTER)} & 22:17:11.867 & $+$00:15:44.700 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
-\scriptsize{\bf SSA22-P2(FIELD)} & 22:17:35.120 & $+$00:09:30.500 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
+ \scriptsize{\bf GOODS-S-P1(FIELD)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & {\it K} & 32.4 & 0.50 \\
+\scriptsize{\bf GOODS-S-P2(FIELD)} & 03:32:32.217 & $-$27:43:08.000 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & {\it K} & 31.8 & 0.52 \\
+\scriptsize{\bf SSA22-P1(CLUSTER)} & 22:17:11.867 & $+$00:15:44.700 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & {\it HK} & 38.1 & 0.62 \\
+\scriptsize{\bf SSA22-P2(FIELD)} & 22:17:35.120 & $+$00:09:30.500 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & {\it HK} & 27.8 & 0.57 \\
 
@@
 
-Two of the FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+Two of the FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
 We selected targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
 These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
-The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\sim 20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
+The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\simeq20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
 In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}
@@
 \subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
-A single CLUSTER environment pointing was selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
-Hundreds of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
-A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011,Yamada2012a} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
-Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the {\it K}-band which is free from OH features and so for the CLUSTER environment pointing we filled the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
+A single CLUSTER environment pointing was selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z\simeq3.09$.
+Hundreds of spectroscopic redshifts have been confirmed for these LBGs with follow-up observations using LRIS \citep{Shapley2003,Nestor2013}.
+A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow-band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011,Yamada2012a} and archival {\em HST ACS} and {\it WFC3} imaging provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
+Fortunately at $z\simeq3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the {\it K}-band which is free from OH features and so for the CLUSTER environment pointing we filled the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
 
@@
 
-Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
+Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
 The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
 The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
-Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R \sim 4200$ ({\it H}-band $R \sim 4000$).
+Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$).
 \subsubsection{Observations}\label{subsubsec:Obs}
@@
     \caption{{\it Left:} The distribution of 49 KDS galaxies (see \cref{subsubsec:sed_fitting}) in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
-    Also plotted in this plane are $\sim4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density in of galaxies in that region.
+    Also plotted in this plane are $\simeq4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density in of galaxies in that region.
     We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
@@
     The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
-    The black solid line and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
-    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line, with the discrepancy between the two relations representating the expected main sequence evolution between these redshifts.
-    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3.5$ SFGs.}
+    The black solid line and the dashed line show the $z\simeq2.5$ broken power-law and quadratic fit to the main-sequence respectively, described in \protect\cite{Whitaker2014}.
+    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in Equation \protect\ref{eq:speagle_ms} as the green line, with the discrepancy between the two relations representating the expected main-sequence evolution between these redshifts.
+    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\simeq3.5$ SFGs.}
     \label{fig:main_sequence}
@@
 To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
-The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously.
+The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously.
 \\
@@
 The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
-In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\sim 0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the {\it K}-band seeing ranged between $\sim 0.55-0.65^{\prime\prime}$.
+In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\simeq0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the {\it K}-band seeing ranged between $\simeq0.55-0.65^{\prime\prime}$.
 We observed 19-21 targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
@@
 
-Consequently we now focus exclusively on the spatially resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
-This paper is concerned with the spatially resolved kinematics of the KDS galaxies, with the details of the {\it H}-band data reduction and corresponding metallicity analyses reserved for a future work.
+Consequently, we now focus exclusively on the spatially-resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
+This paper is concerned with the spatially-resolved kinematics of the KDS galaxies, with the details of the {\it H}-band data reduction and corresponding metallicity analyses reserved for a future analysis.
 
@@
 
-The data reduction process primarly made use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
-In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.
-
-The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
+The data reduction process primarly made use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \citealt{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
+In addition to the SPARK recipes, custom Python scripts were run at different stages of the pipeline and are described throughout this section.
+
+The SPARK recipes are used to create dark frames and to flatfield, illumination correct and wavelength calibrate the raw data.
 An additional step which is not part of the standard reduction process was carried out at this stage, which is to address readout channel bias.
-Differences in the readout process across each 64 pixel wide channel on the detector image lead to a varying flux baselines in these channels.
+Differences in the readout process across each 64-pixel wide channel on the detector image lead to varying flux baselines in these channels.
 We corrected back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.
@@
 We monitored the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged {\it K}-band seeing rose above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
-The PSF was determined from fitting the {\it K}-band collapsed, stacked standard star cube in each pointing with an elliptical gaussian and the values are reported in Table \ref{tab:pointings}.
+The PSF was determined from fitting the {\it K}-band collapsed, stacked standard-star cube in each pointing with an elliptical gaussian and the values are reported in Table \ref{tab:pointings}.
 The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
@@
 
-We stacked all 300s exposures for each galaxy which pass seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
+We stacked all 300s exposures for each galaxy which pass seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
 We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
@@
 
-The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det}$, the number with spatially resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det}$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
 
@@
 The wealth of ancillary data in both fields allows for a consistent treatment of the SED modelling, providing physical properties which are directly comparable between the cluster and field environments.
-These derived properties are considered in the context of the galaxy main sequence, to verify that the KDS sample contains typical SFGs at $z\sim3.5$.
-
-\subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
+These derived properties are considered in the context of the galaxy main-sequence, to verify that the KDS sample contains typical SFGs at $z\simeq3.5$.
+
+\subsubsection{SED fitting and main-sequence}\label{subsubsec:sed_fitting}
 In order to constrain their SFRs and stellar masses, the available photometry for the KDS targets was analysed using the SED fitting software described in \cite{McLure2011} and \cite{McLeod2015}.
@@
 Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 10.0$. 
-We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq 0.1$ dex, but this change does not affect the conclusions of this work.
+We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
 In SSA22, 29 targets (36\% of the full KDS sample) do not have robust SFR measurements due to being undetected at $\geq 2\sigma$ significance in the available $J-$ and $K-$band photometry. \\
@@
 The selection criteria defined in \cite{Whitaker2012a} (which evolve only gently with redshift) separate quiescent and star-forming regions, which are indicated by the black wedge.
-We also make use of the rest-frame colours of $\sim4000$ primarily star-forming galaxies located in GOODS-S between $3.0 < z < 3.8$ (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
+We also make use of the rest-frame colours of $\simeq4000$ primarily star-forming galaxies located in GOODS-S between $3.0 < z < 3.8$ (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
 The filled squares indicate the density of 3D-{\em HST} targets in colour space and we observe that the peak density location is consistent with the location of the KDS targets, all of which are in the star-forming region.
 
-In the right panel of Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the KDS galaxies with SFR measurements, in combination with the derived physical properties of the same GOODS-S galaxies as in the left panel.
-We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.77 Gyr, with the green line.
+In the right panel of Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main-sequence' for the KDS galaxies with SFR measurements, in combination with the derived physical properties of the same GOODS-S galaxies as in the left panel.
+We also plot both the linear-break and quadratic $z\simeq2.5$ main-sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main-sequence relation described in \cite{Speagle2014} given in Equation \ref{eq:speagle_ms}, evaluated at $z\simeq3.5$ (where the age of the universe is 1.77 Gyr) with the green line.
 
@@
 
-The difference in position of these relations highlights the main sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
-The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence.
+The difference in position of these relations highlights the main-sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\simeq2.5-3.5$.
+The KDS galaxies scatter, within the errors, consistently above and below the z$\simeq3$ main-sequence.
 
@@
 We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey and have derived $M_{\star}$ values and SFRs from SED modelling.
-Three KMOS pointings cover the field environment and one pointing covers a cluster environment at the heart of the SSA22 protocluster and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
+Three KMOS pointings cover the field environment and one pointing covers a cluster environment at the heart of the SSA22 protocluster, and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
 Throughout the following analysis sections we describe the use of high-resolution imaging to make morphological measurements for the KDS galaxies and the extraction of kinematic properties for the galaxies using the [O~{\sc III}]$\lambda$5007 emission line.
@@
 At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
-This allows us to investigate the morphological properties of typical star-forming galaxy populations at two redshift slices in comparison with those determined for the KDS sample.
-The imaging also helps to distinguish multiple `merging' components with small angular separations from objects which are morphologically isolated, which we discuss in \cref{subsubsection:spaxel_fitting} and \cref{subsec:morpho-kin-class} where we refine our sample for dynamical analysis.
+This allowed us to investigate the morphological properties of typical star-forming galaxy populations at two redshift slices in comparison with those determined for the KDS sample.
+The imaging also helped to distinguish multiple `merging' components with small angular separations from objects which are morphologically isolated, which we discuss in \cref{subsubsection:spaxel_fitting} and \cref{subsec:morpho-kin-class} where we refine our sample for dynamical analysis.
 
@@
 We use {\tt GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
-The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z \sim 3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
+The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z\simeq3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
 For SSA22 we make use of archival {\em HST} imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the WFC3 F160W band (P.I.
 Lehmer: PID 13844; P.I.
-Mannucci: PID 11735) and the ACS F814W band, tracing $\sim$ 2000$\AA$ light at $z\sim 3.5$ (P.I.
+Mannucci: PID 11735) and the ACS F814W band, tracing $\simeq$ 2000$\AA$ light at $z\simeq3.5$ (P.I.
 Chapman: PID 10405; P.I.
@@
 Siana: PID 12527).
-The {\em HST} coverage is shallower in SSA22 (exposure times of $\sim 5$ ks) and the F160W coverage is concentrated on the SSA22-CLUSTER and so we resort to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage are listed in Table \ref{tab:phys-props}).
+The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the F160W coverage is concentrated on the SSA22-CLUSTER and so we resort to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage are listed in Table \ref{tab:phys-props}).
 \\
@@
 
-This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models and bulge/disk models with both an n = 1 and n = 4 component (following the procedure described in \cite{Bruce2012}) with the fixed exponential disk value of n = 1 , with the median ratio of $\chi ^{2}$ $\sim 1$ between the different fitting methods.
+This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models and bulge/disk models with both an n = 1 and n = 4 component (following the procedure described in \cite{Bruce2012}) with the fixed exponential disk value of n = 1 , with the median ratio of $\chi ^{2}$ $\simeq1$ between the different fitting methods.
 Additionally, 22 GOODS-S objects are also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is n = 1.2.
-The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsec:KROSS}).
+The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2}\simeq1.68 R_{D}$ (see \cref{subsec:KROSS}).
 \\
@@
 This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
-Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout Appendix \ref{app:kinematics_plots}.
+Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially-resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout Appendix \ref{app:kinematics_plots}.
 
@@
 We use the derived $b/a$ values to determine galaxy inclination angles.
-As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
+As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
 
@@
 The median difference between the derived $b/a$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta b/a = 0.0002$.
-The $b/a$ distribution shown in Figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST} imaging, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with a median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
+The $b/a$ distribution shown in Figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST} imaging, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with a median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in Equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
 This compares well with the theoretical mean value of 57.3$^{\circ}$ computed for a population of galaxies with randomly drawn viewing angles (see e.g.
@@
 For the galaxies without {\em HST} coverage the inclination angle is set to the KDS sample median of 57.0$^{\circ}$ and we use the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
-This corresponds to a factor $\sim1.3$ contribution to the uncertainty in the derived velocities for these galaxies.
+This corresponds to a factor $\simeq1.3$ contribution to the uncertainty in the derived velocities for these galaxies.
 
@@
 Throughout our dynamical modelling and beam smearing correction (see \cref{subsec:3d_modelling}) we also require the $R_{1/2}$ value for each galaxy.
-The median difference between the derived $R_{1/2}$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\sim3.5$).
+The median difference between the derived $R_{1/2}$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\simeq3.5$).
 
@@
 \cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploit during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
-We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high-redshift galaxies (see Appendix \ref{app:kin_error_estimates}).
-
-To measure $R_{1/2}$ in the galaxies without {\em HST} coverage we first fit the [O~{\sc III}]$\lambda$5007 narrowband images with an exponential profile, and subtract the PSF from the recovered $R_{1/2}$ value.
+We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high redshift galaxies (see Appendix \ref{app:kin_error_estimates}).
+
+To measure $R_{1/2}$ in the galaxies without {\em HST} coverage we first fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtract the PSF from the recovered $R_{1/2}$ value.
 We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening.
@@
     {\it Right:} The normalised counts of KDS galaxies in bins of half-light radius is plotted, along with the half-light radii of the same \protect\cite{VanderWel2012} galaxies as the left panel.
-    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\sim3.5$.
-    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high-redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
+    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\simeq3.5$.
+    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
     The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
@@
 We proceed to extract 2D kinematic measurements from the 62 KDS datacubes detected in integrated [O~{\sc III}]$\lambda$5007 emission by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
-This sample is then refined to galaxies which are spatially resolved in the [O~{\sc III}]$\lambda$5007 emission in order to make dynamical measurements.
+This sample is then refined to galaxies which are spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission in order to make dynamical measurements.
 We also describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam-smearing corrections for each galaxy.
@@
 This boundary constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
-The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in equation \ref{eq:noise} where $F_{i,background}$ are the flux values across the spatial regions containing no object flux and the spectral extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
+The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation \ref{eq:noise} where $F_{i,background}$ are the flux values across the spatial regions containing no object flux and the spectral extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
 
@@
 
-The signal in each spaxel is taken as the sum of the flux values across the extraction region, $F_{i,object}$, as shown in equation \ref{eq:signal} where S denotes the signal.
+The signal in each spaxel is taken as the sum of the flux values across the extraction region, $F_{i,object}$, as shown in Equation \ref{eq:signal} where S denotes the signal.
 
@@
 fits to skyline residuals), which is important for `cleaning up' accepted spaxels in the 2D maps which are clearly unrelated to the galaxy.
-For this test we subtract the galaxy continuum and impose that $0.7 < F_{g}/{S} < 1.3$, where $F_{g}$ is the flux from the gaussian fit to the [O~{\sc III}]$\lambda$5007 line and S is the signal in the extraction region from equation \ref{eq:signal}.
+For this test we subtract the galaxy continuum and impose that $0.7 < F_{g}/{S} < 1.3$, where $F_{g}$ is the flux from the gaussian fit to the [O~{\sc III}]$\lambda$5007 line and S is the signal in the extraction region from Equation \ref{eq:signal}.
 If all three criteria are satisfied, the spaxel is accepted.
@@
 From the gaussian fit we recover the centre, $\lambda_{g}$, the width, $\sigma_{g}$ and the area, $F_{g}$.
-The velocity is computed from $\lambda_{g}$ using equation \ref{eq:velocity_comp} and the velocity dispersion is computed from $\sigma_{g}$ using equation \ref{eq:dispersion_comp}, where $V_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light, $z_{sys}$ is the redshift determined from the integrated galaxy spectrum and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
+The velocity is computed from $\lambda_{g}$ using Equation \ref{eq:velocity_comp} and the velocity dispersion is computed from $\sigma_{g}$ using Equation \ref{eq:dispersion_comp}, where $V_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light, $z_{sys}$ is the redshift determined from the integrated galaxy spectrum and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
 
@@
 The process is automated and applied to each of the 62 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
-Following the fitting procedure the galaxies are clasified as spatially resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map is equivalent to or greater than the seeing disk.
+Following the fitting procedure the galaxies are clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map is equivalent to or greater than the seeing disk.
 For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, is added to Table \ref{tab:pointings}.
-We find that 47 (76\%) of the detected KDS galaxies across both the field and cluster environments are spatially resolved and show clear velocity structure.
-The 15 galaxies which are not spatially resolved are dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
-The physical properties of all spatially resolved galaxies in both GOODS-S and SSA22 are listed in Table \ref{tab:phys-props}. \\
-
-The morphological information of \cref{subsec:morphological_measurements} is now combined with this spatially resolved condition to define two galaxy subsamples.
+We find that 47 (76\%) of the detected KDS galaxies across both the field and cluster environments are spatially-resolved and show clear velocity structure.
+The 15 galaxies which are not spatially-resolved are dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
+The physical properties of all spatially-resolved galaxies in both GOODS-S and SSA22 are listed in Table \ref{tab:phys-props}. \\
+
+The morphological information of \cref{subsec:morphological_measurements} is now combined with this spatially-resolved condition to define two galaxy subsamples.
 We find that 6/38 of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicates the interpretation of the observed dynamics for these targets.
@@
 
-    \caption{We plot here the kinematic grids for one rotation dominated galaxy (top grid), one dispersion dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
-    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially resolved galaxies in the KDS, divided into rotation dominated, dispersion dominated and merger categories.
+    \caption{We plot here the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
+    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated, dispersion-dominated and merger categories.
     For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map.
@@
     The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
-    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per equation \protect\ref{eq:dispersion_comp}.
+    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per Equation \protect\ref{eq:dispersion_comp}.
     Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
@@
 \subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
-For each galaxy with spatially resolved [O~{\sc III}]$\lambda$5007 emission we construct a series of model datacubes with the same spatial dimensions as the observed datacube and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
+For each galaxy with spatially-resolved [O~{\sc III}]$\lambda$5007 emission we construct a series of model datacubes with the same spatial dimensions as the observed datacube and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
 This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
-Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
+Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by Equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
 
@@
 Due to the faintness of the continuum, there are several galaxies for which we cannot reliably estimate the rotation centre using this method and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location (approach described in \citealt{Harrison2017}).
-Using the continuum to fix the rotation centre is generally more successful for the SSA22 galaxies, since the use of the HK filter effectively doubles the S/N of the continuum by collapsing over twice the wavelength range.
+Using the continuum to fix the rotation centre is generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter effectively doubles the S/N of the continuum by collapsing over twice the wavelength range.
 \\
@@
 The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
-This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\sim3.0$ velocity dispersions and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
+This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\simeq3.0$ velocity dispersions and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
 The reported errors on $\sigma_{int}$ take this assumption into account. \\
@@
 The velocity and velocity dispersion values are then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
-We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, and seek the combination of parameters which maximises the log-Likelihood function given by equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
+We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, and seek the combination of parameters which maximises the log-Likelihood function given by Equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
 
@@
 \subsubsection{Beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
-The intrinsic velocity, $V_{C}$, is found by reading off from the best fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\sim3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
+The intrinsic velocity, $V_{C}$, is found by reading off from the best fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\simeq3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
 This extraction radius is shown with the vertical red dashed line in the panels of Figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
 The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Stott2016,Pelliccia2017,Harrison2017,Swinbank2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
-This is similar to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\sim3R_{D}$), \citep{Tiley2016a}.
+This is similar to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\simeq3R_{D}$), \citep{Tiley2016a}.
 
@@
 
-To measure the $\sigma_{int}$ value for each galaxy in our sample we use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the {\it K}-band and 55.4kms$^{-1}$ in the H{\it K}-band).
+To measure the $\sigma_{int}$ value for each galaxy in our sample we use Equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the {\it K}-band and 55.4kms$^{-1}$ in the H{\it K}-band).
 
@@
 These correction factors are applied to $V_{BS}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
-When following this approach for the isolated field sample, the derived $V_{C}$ values agree with our own corrections to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities.
-This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS methods \citep{Harrison2017}.
+When following this approach for the isolated field sample, the derived $V_{C}$ values agree with our own corrections to within $\simeq10\%$, and the $\sigma_{int}$ values to within $\simeq5\%$ which is within the errors on these quantities.
+This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\simeq0.9$ KROSS methods \citep{Harrison2017}.
 We also observe that the shape and width of the observed and intrinsic kinematic parameter distributions are equivalent, suggesting that the corrections do not over-extrapolate from the raw numbers.
@@
 The observed properties are measured directly from the extracted two-dimensional maps, whereas $V_{C}$ and $\sigma_{int}$ have been corrected for the effects of beam-smearing as described throughout the text.
-Each galaxy is classified as rotation dominated or dispersion dominated if the ratio $V_{C}/\sigma_{int}$ is greater than or less than 1 respectively, as highlighted in the `Class' column.}
+Each galaxy is classified as rotation-dominated or dispersion-dominated if the ratio $V_{C}/\sigma_{int}$ is greater than or less than 1 respectively, as highlighted in the `Class' column.}
 \label{tab:kin_props}
@@
       \small
-      \item $^{a}$ RD = Rotation Dominated; DD = Dispersion Dominated
+      \item $^{a}$ RD = Rotation-Dominated; DD = Dispersion-Dominated
       \item $^{*}$ No {\em HST} coverage; see Table \ref{tab:phys-props}
@@
 
-The resolved KDS galaxies at $z \sim 3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
+The resolved KDS galaxies at $z\simeq3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
 For the majority of galaxies we are not in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
@@
 We proceed to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
-This is a simple empirical diagnostic for whether a galaxy is `Rotation Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
+This is a simple empirical diagnostic for whether a galaxy is `Rotation-Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion-Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
 a method to measure the prevalence of rotational and random motions;][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
-Previous studies have used various classification schemes of varying complexity to identify rotation dominated galaxies which also appear to be `disk-like' and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
+Previous studies have used various classification schemes of varying complexity to identify rotation-dominated galaxies which also appear to be `disk-like' and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
 We describe our simple classification criteria for the isolated field sample based on a joint consideration of the high-resolution photometry and derived kinematic parameters in \cref{subsubsection:isolated_classification} and mention the KDS merger candidates in more detail in the following section.
@@
 The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they are drawn from a higher density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas as well as the morphological and dynamical evolution within these galaxies.
-The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high-redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
+The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
 As mentioned above we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
@@
 These include the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in \cite{ForsterSchreiber2009} and \cite{Cresci2009}.
-In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).
+In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\simeq1$ using the same criteria).
 In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification is outlined in their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
 In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in Appendix \ref{subsec:AMAZE}.
-We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
-The morphologically isolated KDS field galaxies are classified as rotation dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
-We plot the best fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
+We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
+The morphologically isolated KDS field galaxies are classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
+We plot the best fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion-dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
 
 \subsubsection{Summary of the final sample for further analyses}\label{subsubsec:kin_sample_summary}
-In summary, we have analysed 77 typical $z\sim3.5$ SFGs spanning both cluster and field environments, finding 62 with integrated [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsec:datareduction}).
-This sample is refined to 47 galaxies (61\%) with spatially resolved [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsection:spaxel_fitting}).
-Due to the unusually high merger-candidate rate of 89\% in the cluster environment (identified by searching the high-resolution {\em HST} imaging for photometric counterparts), we omit the 9 spatially resolved galaxies in SSA22-P1 from further consideration.
+In summary, we have analysed 77 typical $z\simeq3.5$ SFGs spanning both cluster and field environments, finding 62 with integrated [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsec:datareduction}).
+This sample is refined to 47 galaxies (61\%) with spatially-resolved [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsection:spaxel_fitting}).
+Due to the unusually high merger-candidate rate of 89\% in the cluster environment (identified by searching the high-resolution {\em HST} imaging for photometric counterparts), we omit the 9 spatially-resolved galaxies in SSA22-P1 from further consideration.
 In the remaining sample of 38 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 16\%, which constitute the `merger field sample'.
@@
 
-The isolated field sample is further divided into 13 rotation dominated galaxies (34\% with respect to full field sample) and 19 dispersion dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}).
+The isolated field sample is further divided into 13 rotation-dominated galaxies (34\% with respect to full field sample) and 19 dispersion-dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}).
 
@@
 In the previous sections we have presented our morphological and kinematic analysis for the 77 galaxies covering both cluster and field environments in the KDS survey.
-These galaxies are representative of typical SFGs $z\sim3.5$ as verified by comparing to fits to the galaxy main sequence at this redshift.
-Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 32 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
+These galaxies are representative of typical SFGs $z\simeq3.5$ as verified by comparing to fits to the galaxy main-sequence at this redshift.
+Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 32 field galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
 not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
-For these galaxies we have measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
+For these galaxies we have measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion-dominated.
 The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in Appendix \ref{app:kinematics_plots}.
@@
 
-We proceed first to investigate the relationship between rotation velocity and stellar mass for both the rotation and dispersion dominated isolated field galaxies.
+We proceed first to investigate the relationship between rotation velocity and stellar mass for both the rotation and dispersion-dominated isolated field galaxies.
 
@@
     \caption{{\it Left:} We plot log($V_{C}$) vs.
-log($M_{\star}/M_{\odot}$) for the isolated field sample, with the rotation dominated galaxies in red and dispersion dominated galaxies with the hollow symbols.
-    We also plot with the solid green line the $z\sim0.9$ relation recovered from a fit to $\sim400$ rotation dominated galaxies from the KROSS survey \protect\cite{Harrison2017}, with the shaded region showing the associated $\sim$0.2 dex scatter on the fit.
-    This $z\sim0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in \protect\cite{Reyes2011}.
-    The rotation dominated KDS galaxies, and galaxies classed as reliable from the AMAZE survey \protect\citep{Gnerucci2011}, also show no evolution from this relation within the scatter, with the dispersion dominated galaxies scattering below the relation.
+log($M_{\star}/M_{\odot}$) for the isolated field sample, with the rotation-dominated galaxies in red and dispersion-dominated galaxies with the hollow symbols.
+    We also plot with the solid green line the $z\simeq0.9$ relation recovered from a fit to $\simeq400$ rotation-dominated galaxies from the KROSS survey \protect\cite{Harrison2017}, with the shaded region showing the associated $\simeq$0.2 dex scatter on the fit.
+    This $z\simeq0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in \protect\cite{Reyes2011}.
+    The rotation-dominated KDS galaxies, and galaxies classed as reliable from the AMAZE survey \protect\citep{Gnerucci2011}, also show no evolution from this relation within the scatter, with the dispersion-dominated galaxies scattering below the relation.
     This highlights the need for careful sample selection when constructing this relation.
@@
     The $V_{C}$ distributions in each of the individual studies are wide, reflecting the galaxy diversity within each sample.
-    The low mean value of $V_{C}$ in the KDS isolated field sample is driven mainly by averaging over a sample which contains a higher fraction of dispersion dominated galaxies with lower rotation velocities.}
+    The low mean value of $V_{C}$ in the KDS isolated field sample is driven mainly by averaging over a sample which contains a higher fraction of dispersion-dominated galaxies with lower rotation velocities.}
     \label{fig:tf_relation}
@@
 Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
-However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,DiTeodoro2016,Simons2016,Pelliccia2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
-At $z\sim 3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} consistent with the $z\sim0$ relation.
+However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,DiTeodoro2016,Simons2016,Pelliccia2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
+At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} consistent with the $z\simeq0$ relation.
 \\
@@
 We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
-In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
+In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\simeq0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
 The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
 We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
-These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
-In \cite{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
-The agreement between the parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these redshifts.
-\\
-
-The rotation dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\sim 0.9$ relation, but with a tendency to lie below the relation.
-When considered alone, the mean velocity of the rotation dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=10.0$ is $\sim0.1$ dex beneath the KROSS relation at the same mass.
-The dispersion dominated KDS galaxies sit clearly separated and below the $z\sim0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\sim0.9$ dispersion dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We plot also the five $z\sim3$ galaxies from the AMAZE clean sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\sim0.9$.
-
-Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\sim0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
-Similarly in \cite{Cresci2009} evolution of the normalisation of the stellar mass Tully-Fisher relation is observed at $z\sim2$ using only robust rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5$.
+These $z\simeq0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
+In \cite{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
+The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these redshifts.
+\\
+
+The rotation-dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\simeq0.9$ relation, but with a tendency to lie below the relation.
+When considered alone, the mean velocity of the rotation-dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=10.0$ is $\simeq0.1$ dex beneath the KROSS relation at the same mass.
+The dispersion-dominated KDS galaxies sit clearly separated and below the $z\simeq0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\simeq0.9$ dispersion-dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
+We plot also the five $z\simeq3$ galaxies from the AMAZE clean sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$.
+
+Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\simeq0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
+Similarly in \cite{Cresci2009} evolution of the normalisation of the stellar mass Tully-Fisher relation is observed at $z\simeq2$ using only robust rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5$.
 In both cases the observed evolution is mainly the result of omitting rotationally dominated galaxies with lower $V_{C}$ values.
-Conversely, fitting the stellar mass Tully-Fisher relation through a full sample including dispersion dominated galaxies would shift the zero-point in the opposite sense.
-
-After including data from the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\sim0.1$ and $z\sim3.5$.
+Conversely, fitting the stellar mass Tully-Fisher relation through a full sample including dispersion-dominated galaxies would shift the zero-point in the opposite sense.
+
+After including data from the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\simeq0.1$ and $z\simeq3.5$.
 However as we will show in \cref{subsec:rdf_v_over_sigma} the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.
@@
     \end{subfigure}
-    \caption{{\it Left:} We plot the intrinsic velocity dispersion against stellar mass for the rotation and dispersion dominated isolated field sample galaxies, along with the AMAZE Clean sample.
+    \caption{{\it Left:} We plot the intrinsic velocity dispersion against stellar mass for the rotation and dispersion-dominated isolated field sample galaxies, along with the AMAZE Clean sample.
     The $\sigma_{int}$ values are typically distributed between $40-90kms^{-1}$ and show no clear correlation with stellar mass, highlighting the complicated relationship between these two quantities.
     {\it Right:} We present a compilation of literature $\sigma_{int}$ values plotted against redshift for surveys spanning $0 < z < 4$.
-    The mean $\sigma_{int}$ values increase from $\sim 15kms^{-1}$ in the local universe to $> 70kms^{-1}$ at $z > 3$.
+    The mean $\sigma_{int}$ values increase from $\simeq15kms^{-1}$ in the local universe to $> 70kms^{-1}$ at $z > 3$.
     The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values and in each case for $V_{C} = 125kms^{-1}$.
@@
     \item The mean isolated field sample $V_{C}$ value is less than reported in the comparison samples with similar mean $M_{\star}$ values.
-    This is a result of averaging over a sample containing a higher fraction of dispersion dominated galaxies.
+    This is a result of averaging over a sample containing a higher fraction of dispersion-dominated galaxies.
 \end{itemize}
@@
 Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of gas mass and dark matter mass would raise this estimate).
-Indeed this value is similar to the mean $V_{C}$ value found in the KROSS sample for $log(M_{\star}/M_{\odot})=10.0$ galaxies at $z\sim1$. \\
-
-In the right panel of Figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion dominated galaxies which constitute the samples.
+Indeed this value is similar to the mean $V_{C}$ value found in the KROSS sample for $log(M_{\star}/M_{\odot})=10.0$ galaxies at $z\simeq1$. \\
+
+In the right panel of Figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
 It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in Appendix \ref{app:comparison_samples}) are directly comparable.
@@
 The KDS mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
-The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
-This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
+The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
+This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion-dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
 However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contributes to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
@@
 
-We proceed to consider the cause of the high number of dispersion dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
+We proceed to consider the cause of the high number of dispersion-dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
 There are also some galaxies in our sample where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
@@
 
-In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation dominated classes, along with the AMAZE Clean sample galaxies in the $\sigma_{int}$ vs.
+In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation-dominated classes, along with the AMAZE Clean sample galaxies in the $\sigma_{int}$ vs.
 $M_{\star}$ plane.
-This is an interesting relationship to explore as it has been suggested that rotational velocity alone may not be a good tracer of total dynamical mass at high-redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
+This is an interesting relationship to explore as it has been suggested that rotational velocity alone may not be a good tracer of total dynamical mass at high redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
 However the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
-All of these processes are also more prevalent at high-redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret.
-\\
-
-We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high-redshift.
+All of these processes are also more prevalent at high redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret.
+\\
+
+We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high redshift.
 The beam-smearing corrected $\sigma_{int}$ values, with distribution median, 16th percentile and 84th percentile equal to $71.0kms^{-1}$, $48.0kms^{-1}$ and $85.4kms^{-1}$ respectively, are larger than in the local universe where typically $\sigma_{int} = 10-20kms^{-1}$ \citep{Epinat2008a} (see \cref{subsubsec:sigma_evolution} and \cref{sec:discussion} for a discussion).
-Generally the dispersion dominated galaxies have higher $\sigma_{int}$ values, however the rotation dominated galaxies also span the full distribution width.
+Generally the dispersion-dominated galaxies have higher $\sigma_{int}$ values, however the rotation-dominated galaxies also span the full distribution width.
 
@@
 In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
-The values increase sharply from $\sigma_{int} \sim 10-20kms^{-1}$ as traced by $z\sim0$ measurements of typical SFGs to $\sigma_{int} \sim 30-60kms^{-1}$ at $z\sim1$ to $\sigma_{int} \sim 40-90kms^{-1}$ at $z\sim3$.
+The values increase sharply from $\sigma_{int}\simeq10-20kms^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60kms^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90kms^{-1}$ at $z\simeq3$.
 
@@
 Using observed constraints for these properties from \cite{Tacconi2013} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
-The relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
+The relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
 In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.
@@
 The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}/M_{\odot})=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
-The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\sim1$ for the gas-rich disks observed at high-z e.g.
+The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\simeq1$ for the gas-rich disks observed at high-z e.g.
 \citealt{ForsterSchreiber2006,Genzel2011,Newman2013}) and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
-The tracks plotted in Figure \ref{fig:sigma_and_v_sigma_w_redshift} suggest the shape of the $\sigma_{int}$ evolution in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
-
-We proceed now to consider both the rotation velocities and velocity dispersions in tandem by considering $V_{C}/\sigma_{int}$ and the rotation dominated fraction of galaxies in the isolated field sample.
-
-\subsection{$\boldsymbol{V_{C}/\sigma_{int}}$ and the rotation dominated fraction}\label{subsec:rdf_v_over_sigma}
+The tracks plotted in Figure \ref{fig:sigma_and_v_sigma_w_redshift} suggest the shape of the $\sigma_{int}$ evolution in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main-sequence galaxies between $z=3-3.8$.
+
+We proceed now to consider both the rotation velocities and velocity dispersions in tandem by considering $V_{C}/\sigma_{int}$ and the rotation-dominated fraction of galaxies in the isolated field sample.
+
+\subsection{$\boldsymbol{V_{C}/\sigma_{int}}$ and the rotation-dominated fraction}\label{subsec:rdf_v_over_sigma}
 
@@
     \caption{The distribution of galaxies in the $V_{C}$/$\sigma_{int}$ vs. $M_{\star}$ plane is shown for the isolated field sample, along with the galaxies in the AMAZE Clean sample.
-    We mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies in this panel, finding that more massive galaxies (e.g.
-$log(M_{\star}/M_{\odot}) > 9.7$) are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.}
+    We mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies in this panel, finding that more massive galaxies (e.g.
+$log(M_{\star}/M_{\odot}) > 9.7$) are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.}
     \label{fig:v_sig_and_v}
@@
     \caption{{\it Left:} $V_{C}/\sigma_{int}$ is plotted against redshift for the comparison samples spanning $0 < z < 4$.
-    The filled symbols show the sample mean values, with the KDS mean at $z\sim3.5$ plotted with the red circle, with black errorbars representing the statistical error on the mean computed using bootstrap re-sampling as described in the text.
+    The filled symbols show the sample mean values, with the KDS mean at $z\simeq3.5$ plotted with the red circle, with black errorbars representing the statistical error on the mean computed using bootstrap re-sampling as described in the text.
     The sample medians and statistical errors are plotted with the coloured and grey horizontal bars, falling in each case below the mean, suggesting that large individual $V_{C}/\sigma_{int}$ measurements may bias the sample mean high.
@@
     There is also a connection to the mean $M_{\star}$ of the surveys, with larger mean $M_{\star}$ surveys reporting higher mean $V_{C}/\sigma_{int}$.
-    {\it Right:} We plot the associated rotation dominated fraction, defined as the fraction of galaxies in each sample with $V_{C}/\sigma_{int} > 1$.
+    {\it Right:} We plot the associated rotation-dominated fraction, defined as the fraction of galaxies in each sample with $V_{C}/\sigma_{int} > 1$.
     The narrow shaded regions represent the maximum and miminum RDF, computed as described in Appendix \protect\ref{app:comparison_samples}.
-    It appears that the rotation dominated fraction drops from $\sim 100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\sim 40\%$ at z $\sim 3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher rotation dominated fractions.
+    It appears that the rotation-dominated fraction drops from $\simeq100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\simeq40\%$ at z $\simeq3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher rotation-dominated fractions.
     The dot-dash line is the RDF $\propto z^{-0.2}$ cosmic decline suggested in \protect\cite{Stott2016}.
@@
 Clearly the isolated field sample galaxies are in a different physical regime, with mean and median $V_{C}/\sigma_{int}$ values of $1.08^{+0.18}_{-0.15}$ and $0.97^{+0.14}_{-0.11}$ respectively.
-This is despite many of the dispersion dominated galaxies showing clear velocity gradients across the observed velocity maps (Appendix \ref{app:kinematics_plots}), with the arctangent model providing a good fit to the rotation curves.
-This suggests that although rotational motions are present within the disks, they are small or comparable with the elevated $\sigma_{int}$ values observed throughout the $z \sim 3.5$ sample. \\
-
-The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}/M_{\odot}) > 9.7$ which are more likely to be rotation dominated, but with rotation and dispersion dominated galaxies found at all values of $M_{\star}$.
-The Rotation Dominated Fraction (RDF), calculated with respect to the full field sample of 38 galaxies, is 0.34$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
+This is despite many of the dispersion-dominated galaxies showing clear velocity gradients across the observed velocity maps (Appendix \ref{app:kinematics_plots}), with the arctangent model providing a good fit to the rotation curves.
+This suggests that although rotational motions are present within the disks, they are small or comparable with the elevated $\sigma_{int}$ values observed throughout the $z\simeq3.5$ sample. \\
+
+The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation-dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}/M_{\odot}) > 9.7$ which are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.
+The Rotation-Dominated Fraction (RDF), calculated with respect to the full field sample of 38 galaxies, is 0.34$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
 We interpret these results in the context of the cosmic evolution of the rotation domianted fraction using the comparison samples in \cref{subsubsec:RDF_evolution}.\\
 
-\subsubsection{The evolution of the rotation dominated fraction}\label{subsubsec:RDF_evolution}
-
-In the left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in Appendix \ref{app:comparison_samples}.
+\subsubsection{The evolution of the rotation-dominated fraction}\label{subsubsec:RDF_evolution}
+
+In the left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation-dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in Appendix \ref{app:comparison_samples}.
 The filled symbols and black errorbars in the left panel represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
 The shaded regions give the 16th and 84th percentiles of the distribution on individual $V_{C}/\sigma_{int}$ measurements, plotted here to indicate the range of measurements at each redshift slice.
-In the right panel we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the rotation dominated fraction.
+In the right panel we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the rotation-dominated fraction.
 These are shown with the thin grey shaded regions and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the individual points.\\
 
-The rotation dominated fraction, traced simply by the $V_{C}/\sigma_{int}$ ratio inferred from ionised gas emission lines, drops from $\sim 100\%$ of galaxies in the local universe to $\sim 2/3$ of galaxies in the $z \sim 1-2$ universe and to $\sim 1/3$ above $z \sim 3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
-This is highlighted in the right panel of Figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic rotation dominated fraction decline as described in \cite{Stott2016}.
+The rotation-dominated fraction, traced simply by the $V_{C}/\sigma_{int}$ ratio inferred from ionised gas emission lines, drops from $\simeq100\%$ of galaxies in the local universe to $\simeq2/3$ of galaxies in the $z\simeq1-2$ universe and to $\simeq1/3$ above $z\simeq3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
+This is highlighted in the right panel of Figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic rotation-dominated fraction decline as described in \cite{Stott2016}.
 The width of the $V_{C}/\sigma_{int}$ distributions indicates the galaxy diversity at each redshift slice, driven by the collection of galaxy masses, sSFRs, gas fractions, morphologies and evolutionary states which comprise each sample.
 Scatter above and below the RDF $\propto z^{-0.2}$ evolution line may be attributed in part to the different mean stellar masses of the surveys, with those that have larger stellar masses tending to scatter above this line.
-This draws again from the idea that higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the sample rotation dominated fraction higher (see \cref{sec:discussion}).
-In summary, the rotation dominated galaxies in the isolated field sample appear to conform with a redshift invariant $V_{C}$ - $M_{\star}$ relation.
-Due to increased velocity dispersions, these rotation dominated galaxies account for only $34\%$ of the field sample and so are less representative of typical star-forming galaxies at $z\sim3.5$ than at intermediate and low redshifts.
-Explanations for the increase of $\sigma_{int}$ with redshift (and hence the decline of $V_{C}/\sigma_{int}$) with cosmic time as well as the nature of dispersion dominated galaxies have been discussed at length throughout other studies \citep[e.g][]{ForsterSchreiber2009,Law2009,Burkert2010,Newman2013,Wisnioski2015} and we revisit these in the following discussion.
+This draws again from the idea that higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the sample rotation-dominated fraction higher (see \cref{sec:discussion}).
+In summary, the rotation-dominated galaxies in the isolated field sample appear to conform with a redshift invariant $V_{C}$ - $M_{\star}$ relation.
+Due to increased velocity dispersions, these rotation-dominated galaxies account for only $34\%$ of the field sample and so are less representative of typical star-forming galaxies at $z\simeq3.5$ than at intermediate and low redshifts.
+Explanations for the increase of $\sigma_{int}$ with redshift (and hence the decline of $V_{C}/\sigma_{int}$) with cosmic time as well as the nature of dispersion-dominated galaxies have been discussed at length throughout other studies \citep[e.g][]{ForsterSchreiber2009,Law2009,Burkert2010,Newman2013,Wisnioski2015} and we revisit these in the following discussion.
 
@@
     {\it Right:} The same as in the left panel for a reference mass of $log(M_{\star}/M_{\odot}) = 10.6$.
-    The steeper slope beyond $z\sim2$ highlights the model decrease in gas fraction, and hence velocity dispersion, for galaxies which have accumulated a larger stellar population.}
+    The steeper slope beyond $z\simeq2$ highlights the model decrease in gas fraction, and hence velocity dispersion, for galaxies which have accumulated a larger stellar population.}
     \label{fig:sigma_shifted}
@@
 
-Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
-The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion dominated galaxies ($66\%$ of the sample) and probable pressure support from turbulent motions \citep[e.g.][]{Burkert2010} partially supporting gravity.
-This increased number of dispersion dominated galaxies in comparison to low and intermediate redshifts appears to be driven by high velocity dispersions at $z\sim3.5$.
+Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation-dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
+The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion-dominated galaxies ($66\%$ of the sample) and probable pressure support from turbulent motions \citep[e.g.][]{Burkert2010} partially supporting gravity.
+This increased number of dispersion-dominated galaxies in comparison to low and intermediate redshifts appears to be driven by high velocity dispersions at $z\simeq3.5$.
 In this section we discuss possible physical origins for the elevated random motions traced by $\sigma_{int}$ and their impact on the galactic dynamics.
@@
 Previous studies have claimed that the elevated velocity dispersions observed at high redshift are a consequence of both internal and external processes.
-\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\sim2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.
-\cite{Genzel2011} show that for dispersion dominated galaxies, the scales susceptible to gravitational collapse are of order the galactic half-light radius. 
+\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\simeq2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.
+\cite{Genzel2011} show that for dispersion-dominated galaxies, the scales susceptible to gravitational collapse are of order the galactic half-light radius. 
 Systems such as these form highly unstable and roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009,Genzel2011}.
@@
 \cite{Burkert2010} show, starting from the hydrostatic equation, that negative pressure gradients sourced by the disk turbulence generated through gravitational instabilities result in a decrease in observed rotational velocities.
-This has prompted others \citep[e.g.][]{Wuyts2016b,Ubler2017,Lang2017} to encorporate a velocity dispersion term in the derivation of maximum circular velocities, which contributes to (but is not entirely responsible for) the observed shift in the zero-point of the stellar mass Tully-Fisher relation between $z\sim0-0.9$.
+This has prompted others \citep[e.g.][]{Wuyts2016b,Ubler2017,Lang2017} to encorporate a velocity dispersion term in the derivation of maximum circular velocities, which contributes to (but is not entirely responsible for) the observed shift in the zero-point of the stellar mass Tully-Fisher relation between $z\simeq0-0.9$.
 \cite{Ubler2017} also claim that without the inclusion of this term incorrect conclusions surrounding the evolution of the Tully-Fisher relation will be drawn.
@@
 
-In this model the velocity dispersions increase as a result of increasing gas fractions within galaxies, with a steeper increase from $z\sim0$ for galaxies at higher stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
+In this model the velocity dispersions increase as a result of increasing gas fractions within galaxies, with a steeper increase from $z\simeq0$ for galaxies at higher stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
 At higher redshift these lines converge, suggesting that the predictions for the gas fraction become independent of stellar mass in this regime.
@@
 
-The $\sigma_{int}$ shifted galaxies in Figure \ref{fig:sigma_shifted} are consistent with a single relation for the increase in velocity dispersion with redshift as a result of increasing gas fractions, with the difference between the slopes in the left and right panels highlighting the role of stellar mass in the kinematic settling of galaxies between $z\sim2$ and the local universe.
+The $\sigma_{int}$ shifted galaxies in Figure \ref{fig:sigma_shifted} are consistent with a single relation for the increase in velocity dispersion with redshift as a result of increasing gas fractions, with the difference between the slopes in the left and right panels highlighting the role of stellar mass in the kinematic settling of galaxies between $z\simeq2$ and the local universe.
 The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Law2012b,Law2012c,Wisnioski2015}.
-Rotation dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions as shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}, constituting only $\sim1/3$ of the isolated field sample at $z\sim3.5$.
+Rotation-dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions as shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}, constituting only $\simeq1/3$ of the isolated field sample at $z\simeq3.5$.
 This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale length \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
@@
 
-The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high-redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
-The nature of dispersion dominated galaxies at high-redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
-The AO observations show that in some cases galaxies which are clasified as dispersion dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
+The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
+The nature of dispersion-dominated galaxies at high redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
+The AO observations show that in some cases galaxies which are clasified as dispersion-dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
 This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
@@
 Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity dispersion on galaxy size \citep[e.g.][]{Newman2013}.
-Dispersion dominated galaxies are therefore likely to be at an earlier evolutionary stage and unstable to gravitational instabilities which generate turbulence which is then maintained by the potential energy of the gas in the disk \citep{Burkert2010,Newman2013}.
-
-Bringing the above points together, turbulent motions consume an increasingly significant fraction of the energy budget at high-redshift when typical star-forming galaxies are at earlier evolutionary stages.
-The KDS isolated field sample presents an extension of these trends to higher redshift, where galaxies are even more likely to be dispersion dominated, and pressure support may be more significant than explored at $z\sim2.3$ \citep{Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
+Dispersion-dominated galaxies are therefore likely to be at an earlier evolutionary stage and unstable to gravitational instabilities which generate turbulence which is then maintained by the potential energy of the gas in the disk \citep{Burkert2010,Newman2013}.
+
+Bringing the above points together, turbulent motions consume an increasingly significant fraction of the energy budget at high redshift when typical star-forming galaxies are at earlier evolutionary stages.
+The KDS isolated field sample presents an extension of these trends to higher redshift, where galaxies are even more likely to be dispersion-dominated, and pressure support may be more significant than explored at $z\simeq2.3$ \citep{Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
 However the precise interpretation of $\sigma_{int}$ measured from ionised gas emission lines remains unclear and future observations of both stellar and gaseous velocity dispersions in tandem at high redshift with {\it JWST} will allow for unambigous investigations into the nature of gaseous velocity dispersions at high redshift.
@@
 
-In summary, the isolated field sample galaxies are diverse and kinematically immature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
+In summary, the isolated field sample galaxies are diverse and kinematically immature, with $\simeq2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
 In the context of the equilibrium model explored here, these galaxies will evolve gradually with redshift along the velocity-mass relationship into stable disk galaxies which have converted their gas reservoirs into stellar mass \citep[e.g.][]{Lilly2013,Tacconi2013,Wisnioski2015,Tacconi2017}.
@@
 \section{CONCLUSIONS}\label{sec:conclusion}
-We have presented new measurements of 77 main sequence star forming galaxies spanning both cluster and field environments at $z\sim3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
-These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}/M_{\odot})< 10.5$ typical main sequence galaxies at these redshifts.
-By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\sim18\%$) and a very high merger rate in the cluster pointing ($\sim89\%$).
+We have presented new measurements of 77 main-sequence star forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
+These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}/M_{\odot})< 10.5$ typical main-sequence galaxies at these redshifts.
+By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\simeq18\%$) and a very high merger rate in the cluster pointing ($\simeq89\%$).
 We have made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (Appendix \ref{app:comparison_samples} and Table \ref{tab:evolution_numbers}).
@@
     \item We plot the mean $V_{C}$ values of the comparison samples and the KDS isolated field sample, finding significant diversity in $V_{C}$ measurements in each survey (right panel of Figure \ref{fig:tf_relation}).
-    The spread in measurements is a result of the samples containing a mixture of rotation and dispersion dominated galaxies with varying $M_{\star}$ values, and the low mean KDS value is primarily the result of averaging over a sample with a high fraction of dispersion dominated galaxies and indicating the impact pressure support may have on reducing rotation velocities.
+    The spread in measurements is a result of the samples containing a mixture of rotation and dispersion-dominated galaxies with varying $M_{\star}$ values, and the low mean KDS value is primarily the result of averaging over a sample with a high fraction of dispersion-dominated galaxies and indicating the impact pressure support may have on reducing rotation velocities.
     At higher $M_{\star}$, the accumulation of a stellar population provides stability, leading to an interplay between $\sigma_{int}$ and $V_{C}$ mediated across redshift by the cosmic decline of gas fractions, sSFRs and accretion \citep[e.g.][]{Law2012b,Wisnioski2015}.
-    \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation dominated galaxies with $9.0 < log(M_{\star}/M_{\odot}) < 11.0$ at $z\sim0.9$ in the KROSS survey (Figure \ref{fig:tf_relation}).
+    \item When the $V_{C}$ values are viewed as a function of mass in the inverse stellar mass Tully-Fisher Relation, the rotation-dominated galaxies are correlated with mass and lie within the errors on the same relation as derived for rotation-dominated galaxies with $9.0 < log(M_{\star}/M_{\odot}) < 11.0$ at $z\simeq0.9$ in the KROSS survey (Figure \ref{fig:tf_relation}).
 %something else here when finished writing the TF section
     This relation is consistent with star-forming galaxies at $z=0$ and so we report no significant evolution in the slope or zero-point of the smTFR between $z=0-3.5$.
-    Constistency of sample selection and measurement techniques are crucial factors when determining evolution in the $V_{C}$ vs. $M_{\star}$ plane by comparing samples at different redshifts.
-    The dispersion dominated galaxies scatter below the trend, with the same slope as the rotation dominated galaxies.
-    \item When considering the rotation dominated galaxies alone the median and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}kms^{-1}$ respectively, which are lower than expected from a simple virial theorem calculation using the mean mass and half-light radius of the sample.
+    Consistency of sample selection and measurement techniques are crucial factors when determining evolution in the $V_{C}$ vs. $M_{\star}$ plane by comparing samples at different redshifts.
+    The dispersion-dominated galaxies scatter below the trend, with the same slope as the rotation-dominated galaxies.
+    \item When considering the rotation-dominated galaxies alone the median and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}kms^{-1}$ respectively, which are lower than expected from a simple virial theorem calculation using the mean mass and half-light radius of the sample.
     This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in the system \citep[e.g.][]{Burkert2010}.  
-    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in Appendix \ref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{star}$ of the galaxy samples (right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    This is in line with a simple equilibrium model prescription in which the gas fractions and the impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to increase random motions within high-redshift galaxies.
-    \item 13/32 isolated field sample galaxies are rotation dominated and 19/32 are dispersion dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
-    This gives a rotation dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
+    \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in Appendix \ref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{\star}$ of the galaxy samples (right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+    This is in line with a simple equilibrium model prescription in which the gas fractions and the impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to increase random motions within high redshift galaxies.
+    \item 13/32 isolated field sample galaxies are rotation-dominated and 19/32 are dispersion-dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
+    This gives a rotation-dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
 
@@
 \section{Kinematics Plots}\label{app:kinematics_plots}
-In figures \ref{fig:rotation_dominated_galaxies}, \ref{fig:dispersion_dominated_galaxies} and \ref{fig:merger_galaxies} we plot the kinematic grids for the KDS galaxies classified as rotation dominated, dispersion dominated and merger candidates respectively.
+In figures \ref{fig:rotation_dominated_galaxies}, \ref{fig:dispersion_dominated_galaxies} and \ref{fig:merger_galaxies} we plot the kinematic grids for the KDS galaxies classified as rotation-dominated, dispersion-dominated and merger candidates respectively.
 The figure captions provide more information on each of the panels of these grids.
@@
 
-\subsection{GHASP ($z\sim0$)}\label{subsec:GHASP}
-The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}/M_{\odot})=10.6$ in the local universe ($z\sim0$) to produce 3D H$\alpha$ datacubes.
+\subsection{GHASP ($z\simeq0$)}\label{subsec:GHASP}
+The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}/M_{\odot})=10.6$ in the local universe ($z\simeq0$) to produce 3D H$\alpha$ datacubes.
 The data extend out to several half-light radii and in each case tilted ring models are fit to determine $V_{C}$ at large radii where the rotation curves have flattened, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
@@
 
-\subsection{DYNAMO ($z\sim0.1$, but selected with physical properties resembling $z\sim2$)}\label{subsec:DYNAMO}
-In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}/M_{\odot})=10.3$ at $z\sim0.1$ is presented.
-The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\sim 2$ SFGs.
+\subsection{DYNAMO ($z\simeq0.1$, but selected with physical properties resembling $z\simeq2$)}\label{subsec:DYNAMO}
+In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}/M_{\odot})=10.3$ at $z\simeq0.1$ is presented.
+The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\simeq2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\simeq2$ SFGs.
 $V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.6R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
@@
 
-\subsection{MUSE and KMOS ($z\sim0.65$ and $z\sim1.25$)}\label{subsec:MUSE_and_KMOS}
-In \cite{Swinbank2017} a collection of $\sim400$ star-forming galaxies observed in [O~{\sc II}]$\lambda$3727,3729 with MUSE and H$\alpha$ emission with KMOS is described.
+\subsection{MUSE and KMOS ($z\simeq0.65$ and $z\simeq1.25$)}\label{subsec:MUSE_and_KMOS}
+In \cite{Swinbank2017} a collection of $\simeq400$ star-forming galaxies observed in [O~{\sc II}]$\lambda$3727,3729 with MUSE and H$\alpha$ emission with KMOS is described.
 Of this parent sample, inclination corrected velocities and intrinsic velocity dispersions are derived for 179 galaxies, to which we make comparisons.
@@
 
-\subsection{KROSS ($z\sim0.9$)}\label{subsec:KROSS}
-We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}/M_{\odot})=9.9$ and $z\sim0.9$.
+\subsection{KROSS ($z\simeq0.9$)}\label{subsec:KROSS}
+We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\simeq600$ SFGs with median $log(M_{\star}/M_{\odot})=9.9$ and $z\simeq0.9$.
 $V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) with the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
 These quantities are then beam-smearing corrected as described in H17 section 3.3.3. 
-Due to the consistency of modelling and measurement techniques these form a robust $z\sim0.9$ comparison sample.
-
-\subsection{KMOS$^{3D}$ ($z\sim1.0$ and $z\sim2.3$)}\label{subsec:kmos_3d}
-The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
-At $z \sim 1.0$ the galaxies have $log(M_{\star}/M_{\odot})=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}/M_{\odot})=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}/M_{\odot})=10.0$.
+Due to the consistency of modelling and measurement techniques these form a robust $z\simeq0.9$ comparison sample.
+
+\subsection{KMOS$^{3D}$ ($z\simeq1.0$ and $z\simeq2.3$)}\label{subsec:kmos_3d}
+The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\simeq191$ massive SFGs across two redshift slices. 
+At $z\simeq1.0$ the galaxies have $log(M_{\star}/M_{\odot})=10.7$ and at $z\simeq2.3$ the median is $log(M_{\star}/M_{\odot})=10.9$, approaching an order-of-magnitude above the KDS median of $log(M_{\star}/M_{\odot})=10.0$.
 The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
@@
 
-\subsection{MASSIV ($z\sim1.2$)}\label{subsec:MASSIV}
-The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}/M_{\odot})=10.2$ at $z\sim1.2$.
-An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
+\subsection{MASSIV ($z\simeq1.2$)}\label{subsec:MASSIV}
+The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}/M_{\odot})=10.2$ at $z\simeq1.2$.
+An arctangent function is fit to the data and $V_{C}$ is extracted at $\simeq1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
 We make use of tabulated values presented in E12.
 
-\subsection{SINS ($z\sim2.0$)}\label{subsec:SINS}
-The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}/M_{\odot})=10.6$ at $z\sim2.0$.
-Galaxies in this sample are classified as rotation or dispersion dominated following FS09 section 9.5.1 which classifies rotation dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
-$V_{C}$ values for rotation dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion dominated galaxies using the velocity width.
+\subsection{SINS ($z\simeq2.0$)}\label{subsec:SINS}
+The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}/M_{\odot})=10.6$ at $z\simeq2.0$.
+Galaxies in this sample are classified as rotation or dispersion-dominated following FS09 section 9.5.1 which classifies rotation-dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
+$V_{C}$ values for rotation-dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion-dominated galaxies using the velocity width.
 Only integrated velocity dispersions are presented for the full sample.
 In addition, \cite[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
-In this approach the $V_{C}$ value comes from the best fitting model parameter and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
+In this approach the $V_{C}$ value comes from the best fitting model parameter and $\sigma_{int}$ is calculated using Equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
 
@@
 
-It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
-We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in the plots throughout \cref{sec:results}.
-
-\subsection{LAW 09 ($z\sim2.3$)}\label{subsec:law_09}
-In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}/M_{\odot})=10.0$ at $z\sim2.3$.
+It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness and note that the $V_{C}$ values in C09 are likely biased towards rotation-dominated galaxies with a well-settled disk.
+We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation-dominated fraction results listed in W15 without distributions in the plots throughout \cref{sec:results}.
+
+\subsection{LAW 09 ($z\simeq2.3$)}\label{subsec:law_09}
+In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}/M_{\odot})=10.0$ at $z\simeq2.3$.
 The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
@@
 
-\subsection{AMAZE ($z\sim3.0$)}\label{subsec:AMAZE}
-The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}/M_{\odot})=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
+\subsection{AMAZE ($z\simeq3.0$)}\label{subsec:AMAZE}
+The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}/M_{\odot})=9.9$ at z$\simeq3$, closest in redshift to the KDS galaxies.
 In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq.
@@
 A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
-We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
+We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion-dominated galaxies.
 \\
@@
 The remaining 5 galaxies we refer to as the AMAZE Clean sample and plot with grey symbols.
-We also plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated. \\
+We also plot the quoted rotation-dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation-dominated. \\
 
@@
 There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement.
-The $V_{C}/\sigma_{int} = 1$ line divides the galaxies classified as rotation dominated and dispersion dominated.
+The $V_{C}/\sigma_{int} = 1$ line divides the galaxies classified as rotation-dominated and dispersion-dominated.
 The galaxy s\_sa22a-M38, classified here as a merger but classified in \protect\cite{Gnerucci2011} as a rotating galaxy with $V_{C} = 346kms^{-1}$ is marked on the plot.}
@@
 In Figure \ref{fig:intrinsic_parameters} we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane. 
-The $V_{C}$ = $\sigma_{int}$ line roughly bisects the KDS sample, and separates the dispersion and rotation dominated galaxies by definition.
+The $V_{C}$ = $\sigma_{int}$ line roughly bisects the KDS sample, and separates the dispersion and rotation-dominated galaxies by definition.
 The isolated field sample galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is good agreement between the KDS and AMAZE Clean samples.
@@
 
-\caption{We plot here the kinematic grids for the 13 isolated field sample galaxies classified as rotation dominated.
+\caption{We plot here the kinematic grids for the 13 isolated field sample galaxies classified as rotation-dominated.
 For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
@@
 The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
-The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per equation \protect\ref{eq:dispersion_comp}, and the vertical dashed lines have the same meaning as for the velocity extraction plot.
+The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per Equation \protect\ref{eq:dispersion_comp}, and the vertical dashed lines have the same meaning as for the velocity extraction plot.
 Also plotted with the blue and red dot-dash horizontal lines are the median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.}
@@
 
-    \caption{The same as in figure \protect\ref{fig:rotation_dominated_galaxies} but for the dispersion dominated galaxies.}
+    \caption{The same as in figure \protect\ref{fig:rotation_dominated_galaxies} but for the dispersion-dominated galaxies.}
     \label{fig:dispersion_dominated_galaxies}

### 2017-03-29 paper.tex
Post Jim

@@
 We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
-In SSA22, 29 targets (36\% of the full KDS sample) do not have robust SFR measurements due to being undetected at $\geq 2\sigma$ significance in the available $J-$ and $K-$band photometry. \\
+In SSA22, 29 targets (36\% of the full KDS sample) do not have robust SFR measurements due to being undetected at $\geq 2\sigma$ significance in the available $J-$ and $K-$band photometry.
+The median of the ratio of the derived stellar masses in GOODS-S to the matched stellar masses in \cite{Santini2015} (which presents an average result from 10 different sets of analyses) shows that the masses adopted here are $\simeq0.15$ dex larger.
+\\
 
@@
 Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies and see Appendix \ref{app:comparison_samples} and \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
-Throughout our dynamical modelling and beam smearing correction (see \cref{subsec:3d_modelling}) we also require the $R_{1/2}$ value for each galaxy.
+Throughout our dynamical modelling and beam-smearing correction (see \cref{subsec:3d_modelling}) we also require the $R_{1/2}$ value for each galaxy.
 The median difference between the derived $R_{1/2}$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\simeq3.5$).
@@
 The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky line residuals.
-A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
+A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
 These parameters, along with the estimate of the noise in the datacube, are used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not. 
@@
 
-    \caption{We plot here the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
+    \caption{We plot the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
     In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated, dispersion-dominated and merger categories.
@@
 
-The MCMC sampling provides a distribution of parameter values around those which give the maximum likelihood.
+The MCMC sampling provides a distribution of parameter values around those which give the maximum-likelihood.
 We have confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates have converged around the 50th percentile values.
@@
 \subsubsection{Beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
-The intrinsic velocity, $V_{C}$, is found by reading off from the best fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\simeq3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
+The intrinsic velocity, $V_{C}$, is found by reading off from the best-fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\simeq3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
 This extraction radius is shown with the vertical red dashed line in the panels of Figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
@@
 These include the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in \cite{ForsterSchreiber2009} and \cite{Cresci2009}.
-In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\simeq1$ using the same criteria).
+In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotation-dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\simeq1$ using the same criteria).
 In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification is outlined in their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
@@
 The morphologically isolated KDS field galaxies are classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
-We plot the best fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion-dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
+We plot the best-fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion-dominated categories in Figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
 
@@
 We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
-In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\simeq0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
+In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
 The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
@@
 In \cite{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
-The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these redshifts.
+The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotation-dominated star-forming galaxies between these redshifts.
 \\
@@
 Similarly in \cite{Cresci2009} evolution of the normalisation of the stellar mass Tully-Fisher relation is observed at $z\simeq2$ using only robust rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5$.
-In both cases the observed evolution is mainly the result of omitting rotationally dominated galaxies with lower $V_{C}$ values.
+In both cases the observed evolution is mainly the result of omitting rotation-dominated galaxies with lower $V_{C}$ values.
 Conversely, fitting the stellar mass Tully-Fisher relation through a full sample including dispersion-dominated galaxies would shift the zero-point in the opposite sense.
@@
 However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contributes to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
-This topic is discussed further throughout \cref{sec:discussion}.
+This topic is discussed further throughout \cref{sec:discussion}. \\\\
 
@@
 In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR.
-Using observed constraints for these properties from \cite{Tacconi2013} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
+Using observed constraints for these properties from \cite{Tacconi2013} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} Figures 10 and 11).
 The relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
@@
 This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
-We have attempted to account for beam smearing using half-light radius and velocity gradient dependent dynamical modelling, but we acknowledge that these observations are challenging and cannot rule out the presence of unresolved velocity gradients in our seeing-limited dataset.
+We have attempted to account for beam-smearing using half-light radius and velocity gradient dependent dynamical modelling, but we acknowledge that these observations are challenging and cannot rule out the presence of unresolved velocity gradients in our seeing-limited dataset.
 Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity dispersion on galaxy size \citep[e.g.][]{Newman2013}.
@@
 Based on data obtained with the European Southern Observatory Very Large Telescope, Paranal, Chile, under Large Program 185.A-0791, and made available by the VUDS team at the CESAM data center, Laboratoire d'Astrophysique de Marseille, France.
-The {\em HST} data matched to the VUDS-DR1 are described in \cite{Grogin2011} and \cite{Koekemoer2011} for CANDELS and include data from the ERS \cite{Windhorst2011}.
 
@@
 
-\section{Kinematics Plots}\label{app:kinematics_plots}
-In figures \ref{fig:rotation_dominated_galaxies}, \ref{fig:dispersion_dominated_galaxies} and \ref{fig:merger_galaxies} we plot the kinematic grids for the KDS galaxies classified as rotation-dominated, dispersion-dominated and merger candidates respectively.
-The figure captions provide more information on each of the panels of these grids.
-
 \section{Comparison samples}\label{app:comparison_samples}
@@
 \begin{threeparttable}
-\caption{We present here a reference of the mean and median kinematic properties used throughout figures \protect\ref{fig:tf_relation}, \protect\ref{fig:sigma_and_v_sigma_w_redshift} and \protect\ref{fig:rdf_and_v_sigma_w_redshift} for the different surveys.
+\caption{The mean and median kinematic properties used throughout Figures \protect\ref{fig:tf_relation}, \protect\ref{fig:sigma_and_v_sigma_w_redshift} and \protect\ref{fig:rdf_and_v_sigma_w_redshift} for the different surveys.
 The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
 \label{tab:evolution_numbers}
-\begin{tabular}{c c c c c c c c c c }
+\begin{tabular}{llllllllll}
 
  \hline
-Survey & $\left< z \right> $ & $\left< log\left(\frac{M_{\star}}{M_{\odot}}\right)\right>$ & $\left< \frac{V_{C}}{\sigma_{int}} \right>$ & med$\left(\frac{V_{C}}{\sigma_{int}}\right)$ & RDF & $ \left< \sigma_{int} \right>$ & med$\left(\sigma_{int}\right)$ & $\left<V_{C}\right>$ & med$\left(V_{C}\right)$  \\
+Survey & $\left< z \right> $ & $\left< log\left(\frac{M_{\star}}{M_{\odot}}\right)\right>$ & $\left< \frac{V_{C}}{\sigma_{int}} \right>$ & med$\left(\frac{V_{C}}{\sigma_{int}}\right)$ & RDF & $ \left< \sigma_{int} \right>$ & med$\left(\sigma_{int}\right)$ & $\left<V_{C}\right>$ & med$\left(V_{C}\right)$  \\[1ex]
  \hline
- GHASP & 0.001 & 10.6 & $12.91^{+0.51}_{-0.44}$ & $12.45^{+5.15}_{-5.05}$ & $1.0^{+0.00}_{-0.024}$ & $13.0^{+0.5}_{-0.5}$ & $13.0^{+6.0}_{-4.0}$ & $189.0^{+3.5}_{-3.0}$ & $159.4^{+113.3}_{-79.2}$ \\
- DYNAMO & 0.1 & 10.3 & $5.06^{+0.18}_{-0.15}$ & $4.55^{+3.06}_{-2.22}$ & $0.96^{+0.02}_{-0.015}$ & $45.9^{+0.3}_{-0.3}$ & $39.0^{+18.2}_{-21.9}$ & $183.0^{+1.0}_{-1.0}$ & $164.0^{+76.0}_{-50.0}$ \\
- MUSE+KMOS & 0.65 & 9.4 & $2.92^{+0.08}_{-0.08}$ & $2.21^{+1.73}_{-1.23}$ & $0.83^{+0.023}_{-0.023}$ & $40.0^{+0.3}_{-0.3}$ & $32.0^{+11.0}_{-8.0}$ & $103.8^{+1.52}_{-1.62}$ & $73.0^{+65.0}_{-44.0}$ \\
- KROSS & 0.9 & 9.9 & $3.05^{+0.17}_{-0.17}$ & $2.36^{+2.64}_{-1.46}$ & $0.81^{+0.05}_{-0.05}$ & - & - & $117.0^{+4.0}_{-4.0}$ & $109^{+77.0}_{-66.0}$ \\
- KMOS$^{3D}$ & 1.0 & 10.7 & 5.5 & - & 0.93 & 25 & - & 170 & - \\
- MASSIV & 1.2 & 10.2 & $2.41^{+1.4}_{-0.9}$ & $1.95^{+2.40}_{-1.31}$ & $0.67^{+0.06}_{-0.06}$ & $61.8^{+3.8}_{-4.2}$ & $52.0^{+23.2}_{-20.7}$ & $132.13^{+10.4}_{-8.2}$ & $103.0^{+99.0}_{-61.2}$ \\
- MUSE+KMOS & 1.25 & 9.8 & $2.21^{+0.98}_{-0.96}$ & $1.59^{+1.30}_{-0.75}$ & $0.78^{+0.04}_{-0.04}$ & $42.0^{+0.5}_{-0.5}$ & $29.5^{+20.1}_{-7.5}$ & $75.5^{+3.04}_{-3.25}$ & $54.0^{+65.32}_{-29.0}$ \\
- SINS(C09) & 2.0 & 10.6 & $5.0^{+0.93}_{-0.97}$ & $4.74^{+1.11}_{-0.18}$ & 1.0 & $51.2^{+8.0}_{-7.9}$ & $42.5^{+14.5}_{-3.5}$ & $232.0^{+12.8}_{-12.7}$ & $240.0^{+31.0}_{-60.2}$ \\
- SINS(F09) & 2.0 & 10.6 & 2.6 & - & 0.60 & - & - & $201.3^{+4.3}_{-4.0}$ & $174.0^{+83.0}_{-58.0}$ \\
- KMOS$^{3D}$ & 2.2 & 10.9 & 2.6 & - & 0.73 & 55 & - & 170 & - \\
- AMAZE & 3.0 & 10.0 & $3.59^{+1.45}_{-1.1}$ & $2.1^{+4.7}_{-1.15}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+27.0}_{-48.0}$ & $217^{+59.1}_{-40.2}$ & $129^{+166.0}_{-50.2}$ \\
- \textbf{KDS} & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.37^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $76.7^{+4.9}_{-4.5}$ & $57.0^{+49.1}_{-18.2}$ \\
+ GHASP & 0.001 & 10.6 & $12.9^{+0.5}_{-0.4}$ & $12.5^{+0.6}_{-0.6}$ & $1.00^{+0.00}_{-0.02}$ & $13.0^{+0.5}_{-0.5}$ & $13.0^{+0.5}_{-0.5}$ & $189.0^{+3.5}_{-3.0}$ & $159.4^{+12.0}_{-15.0}$ \\[1ex]
+ DYNAMO & 0.1 & 10.3 & $5.1^{+0.2}_{-0.2}$ & $4.6^{+0.2}_{-0.2}$ & $0.96^{+0.02}_{-0.02}$ & $45.9^{+0.3}_{-0.3}$ & $39.0^{+0.9}_{-1.0}$ & $183.0^{+1.0}_{-1.0}$ & $164.0^{+3.0}_{-5.0}$ \\[1ex]
+ MUSE+KMOS & 0.65 & 9.4 & $2.9^{+0.1}_{-0.1}$ & $2.21^{+0.1}_{-0.1}$ & $0.83^{+0.02}_{-0.02}$ & $40.0^{+0.3}_{-0.3}$ & $32.0^{+0.6}_{-0.5}$ & $103.8^{+1.5}_{-1.6}$ & $73.0^{+2.5}_{-2.5}$ \\[1ex]
+ KROSS & 0.9 & 9.9 & $3.1^{+0.2}_{-0.2}$ & $2.4^{+0.1}_{-0.1}$ & $0.81^{+0.05}_{-0.05}$ & - & - & $117.0^{+4.0}_{-4.0}$ & $109.0^{+5.0}_{-5.0}$ \\[1ex]
+ KMOS$^{3D}$ & 1.0 & 10.7 & 5.5 & - & 0.93 & 25.0 & - & 170.0 & - \\[1ex]
+ MASSIV & 1.2 & 10.2 & $2.4^{+1.4}_{-0.9}$ & $2.0^{+0.3}_{-0.2}$ & $0.67^{+0.06}_{-0.06}$ & $61.8^{+3.8}_{-4.2}$ & $52.0^{+5.2}_{-4.7}$ & $132.1^{+10.4}_{-8.2}$ & $103.0^{+13.4}_{-11.0}$ \\[1ex]
+ MUSE+KMOS & 1.25 & 9.8 & $2.2^{+1.0}_{-1.0}$ & $1.59^{+0.1}_{-0.1}$ & $0.78^{+0.04}_{-0.04}$ & $42.0^{+0.5}_{-0.5}$ & $29.5^{+1.0}_{-1.0}$ & $75.5^{+3.0}_{-3.3}$ & $54.0^{+3.0}_{-2.8}$ \\[1ex]
+ SINS(C09) & 2.0 & 10.6 & $5.0^{+0.9}_{-1.0}$ & $4.7^{+1.0}_{-1.0}$ & 1.0 & $51.2^{+8.0}_{-7.9}$ & $42.5^{+9.1}_{-8.5}$ & $232.0^{+12.8}_{-12.7}$ & $240.0^{+18.0}_{-17.2}$ \\[1ex]
+ SINS(F09) & 2.0 & 10.6 & 2.6 & - & 0.60 & - & - & $201.3^{+4.3}_{-4.0}$ & $174.0^{+12.1}_{-10.3}$ \\[1ex]
+ KMOS$^{3D}$ & 2.2 & 10.9 & 2.6 & - & 0.73 & 55.0 & - & 170.0 & - \\[1ex]
+ AMAZE (Full) & 3.0 & 10.0 & $3.6^{+1.5}_{-1.1}$ & $2.1^{+0.6}_{-0.5}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+4.5}_{-4.8}$ & $217.0^{+59.1}_{-40.2}$ & $129.0^{+47.5}_{-42.8}$ \\[1ex]
+ AMAZE (Clean) & 3.0 & 10.0 & $1.4^{+0.3}_{-0.3}$ & $1.1^{+0.3}_{-0.3}$ & - & $95.7^{+2.0}_{-2.0}$ & $95.0^{+2.6}_{-2.6}$ & $140.8^{+40.1}_{-30.2}$ & $129.0^{+45.0}_{-33.4}$ \\[1ex]
+ \textbf{KDS} & 3.5 & 10.0 & $1.1^{+0.2}_{-0.1}$ & $0.84^{+0.1}_{-0.1}$ & $0.37^{+0.08}_{-0.08}$ & $70.3^{+3.3}_{-3.1}$ & $71.0^{+5.0}_{-4.8}$ & $75.7^{+4.4}_{-4.4}$ & $57.5^{+5.5}_{-5.5}$ \\[1ex]
  \hline
@@
 Throughout \cref{sec:results} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
-The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently picks out representative star-forming galaxies at each epoch and traces the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission lines.
+The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out representative star-forming galaxies at each epoch and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission lines.
 
@@
 
-\subsection{GHASP ($z\simeq0$)}\label{subsec:GHASP}
+\subsection{GHASP ($\bmath{z\simeq0}$)}\label{subsec:GHASP}
 The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}/M_{\odot})=10.6$ in the local universe ($z\simeq0$) to produce 3D H$\alpha$ datacubes.
@@
 
-\subsection{DYNAMO ($z\simeq0.1$, but selected with physical properties resembling $z\simeq2$)}\label{subsec:DYNAMO}
-In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}/M_{\odot})=10.3$ at $z\simeq0.1$ is presented.
+\subsection{DYNAMO ($\bmath{z\simeq0.1}$, but selected with physical properties resembling $\bmath{z\simeq2}$)}\label{subsec:DYNAMO}
+In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}/M_{\odot})=10.3$ at $z\simeq0.1$ are presented.
 The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\simeq2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\simeq2$ SFGs.
@@
 
-\subsection{MUSE and KMOS ($z\simeq0.65$ and $z\simeq1.25$)}\label{subsec:MUSE_and_KMOS}
+\subsection{MUSE and KMOS ($\bmath{z\simeq0.65}$ and $\bmath{z\simeq1.25}$)}\label{subsec:MUSE_and_KMOS}
 In \cite{Swinbank2017} a collection of $\simeq400$ star-forming galaxies observed in [O~{\sc II}]$\lambda$3727,3729 with MUSE and H$\alpha$ emission with KMOS is described.
@@
 The observations span the redshift range $0.2 < z < 1.6$ and we split the data into two subsets with $z < 1.0$ (129 galaxies with mean redshift of $z = 0.65$, mean stellar mass of $log(M_{\star}/M_{\odot})=9.80$) and $z > 1.0$ (50 galaxies with mean redshift of $z = 1.25$, mean stellar mass $log(M_{\star}/M_{\odot})=9.80$).
-The reported velocities are extracted at $3R_{D}$, comparable to the extraction radius for the KDS sample and the intrinsic velocity dispersions have been corrected for beam smearing effects.
+The reported velocities are extracted at $3R_{D}$, comparable to the extraction radius for the KDS sample and the intrinsic velocity dispersions have been corrected for beam-smearing effects.
 We make use of the tabulated data from this survey and use the results at the two redshift ranges as reliable comparison samples.
 
-\subsection{KROSS ($z\simeq0.9$)}\label{subsec:KROSS}
+\subsection{KROSS ($\bmath{z\simeq0.9}$)}\label{subsec:KROSS}
 We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\simeq600$ SFGs with median $log(M_{\star}/M_{\odot})=9.9$ and $z\simeq0.9$.
@@
 
-\subsection{KMOS$^{3D}$ ($z\simeq1.0$ and $z\simeq2.3$)}\label{subsec:kmos_3d}
+\subsection{KMOS$^{3D}$ ($\bmath{z\simeq1.0}$ and $\bmath{z\simeq2.3}$)}\label{subsec:kmos_3d}
 The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\simeq191$ massive SFGs across two redshift slices. 
@@
 
-\subsection{MASSIV ($z\simeq1.2$)}\label{subsec:MASSIV}
+\subsection{MASSIV ($\bmath{z\simeq1.2}$)}\label{subsec:MASSIV}
 The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}/M_{\odot})=10.2$ at $z\simeq1.2$.
@@
 
-\subsection{SINS ($z\simeq2.0$)}\label{subsec:SINS}
+\subsection{SINS ($\bmath{z\simeq2.0}$)}\label{subsec:SINS}
 The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}/M_{\odot})=10.6$ at $z\simeq2.0$.
 Galaxies in this sample are classified as rotation or dispersion-dominated following FS09 section 9.5.1 which classifies rotation-dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
+\\
+
 $V_{C}$ values for rotation-dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion-dominated galaxies using the velocity width.
 Only integrated velocity dispersions are presented for the full sample.
-In addition, \cite[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
-In this approach the $V_{C}$ value comes from the best fitting model parameter and $\sigma_{int}$ is calculated using Equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
+In addition, \cite{Cresci2009} (C09) model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
+In this approach the $V_{C}$ value comes from the best-fitting model parameter and $\sigma_{int}$ is calculated using Equation \ref{eq:sins_sigma}, with the best-fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
 
@@
 
-\subsection{LAW 09 ($z\simeq2.3$)}\label{subsec:law_09}
+\subsection{LAW 09 ($\bmath{z\simeq2.3}$)}\label{subsec:law_09}
 In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}/M_{\odot})=10.0$ at $z\simeq2.3$.
 The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
-We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
+We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux-weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
 These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have been beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
@@
 
-\subsection{AMAZE ($z\simeq3.0$)}\label{subsec:AMAZE}
+\subsection{AMAZE ($\bmath{z\simeq3.0}$)}\label{subsec:AMAZE}
 The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}/M_{\odot})=9.9$ at z$\simeq3$, closest in redshift to the KDS galaxies.
-In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq.
-8).
-A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
-We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion-dominated galaxies.
-\\
-
-Also, for 5 galaxies in G11 $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error on $V_{C}$ equal to 1 when computing the sample averages.
-The $\sigma_{int}$ errors for individual galaxies are generally very small and for 3 galaxies the $\sigma_{int}$ value is consistent with 0kms$^{-1}$.
-For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
-A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{sec:results}.
-This Unconstrained sample also contains the galaxy s\_sa22a-M38 common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
+In this study, rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ as the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map (which also takes into account instrumental resolution and beam-smearing; see their Equation 8).
+A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotation-dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
+We use tabulated values from G11, but note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys (which contain a mix of rotation and dispersion-dominated galaxies).
+\\
+
+Also, for 5 galaxies in G11, $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error on $V_{C}$ equal to 1 when computing the sample averages.
+The $\sigma_{int}$ errors for individual galaxies are generally very small, and for 3 galaxies the $\sigma_{int}$ value is consistent with 0 kms$^{-1}$.
+For the mean value computations we set these equal to the SINFONI resolution limit of 30 kms$^{-1}$.
+A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0 kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{sec:results}.
+This Unconstrained sample also contains the galaxy s\_sa22a-M38, common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346 kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
 The remaining 5 galaxies we refer to as the AMAZE Clean sample and plot with grey symbols.
-We also plot the quoted rotation-dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation-dominated. \\
-
-This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
-This trend towards consistency is encouraging, and as described in \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
-We stress that keeping in mind sample selection, mass ranges and kinematic parameter extraction methods are crucial when comparing results between different surveys.
+We plot the quoted rotation-dominated fraction of 33$\%$, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation-dominated. \\
+
+This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, however, despite this diversity, over the past decade the studies appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
+This trend towards consistency is encouraging, and, as described in \cref{subsec:3d_modelling}, we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
+We stress that, keeping in mind sample selection, mass ranges and kinematic parameter extraction methods are crucial when comparing results between different surveys.
 
@@
 \includegraphics[width=0.49\textwidth]{sigma_versus_v.png}
-\caption{{\it Left:} The distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
+\caption{The distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
 The AMAZE Clean sample galaxies (see \protect\cref{subsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
@@
 The $V_{C}/\sigma_{int} = 1$ line divides the galaxies classified as rotation-dominated and dispersion-dominated.
-The galaxy s\_sa22a-M38, classified here as a merger but classified in \protect\cite{Gnerucci2011} as a rotating galaxy with $V_{C} = 346kms^{-1}$ is marked on the plot.}
+The galaxy s\_sa22a-M38, classified here as a merger but classified in \protect\cite{Gnerucci2011} as a rotating galaxy with $V_{C} = 346 kms^{-1}$ is marked on the plot.}
 \label{fig:intrinsic_parameters}
@@
 In Figure \ref{fig:intrinsic_parameters} we plot the distribution of the isolated field sample in the $\sigma_{int}$ vs. log($V_{C}$) plane. 
-The $V_{C}$ = $\sigma_{int}$ line roughly bisects the KDS sample, and separates the dispersion and rotation-dominated galaxies by definition.
+The $V_{C}$ = $\sigma_{int}$ line roughly bisects the KDS sample, and separates the dispersion-dominated and rotation-dominated galaxies by definition.
 The isolated field sample galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is good agreement between the KDS and AMAZE Clean samples.
@@
 As mentioned in \cref{subsec:3d_modelling}, the MCMC sampling provides distributions for each of the model parameters, from which we can extract the 84th and 16th percentile values as the +/- 1-$\sigma$ errors.
-During the following procedure $PA_{kin}$ is fixed to the maximum likelihood value for all model evaluations.
-We proceed to reconstruct the beam smeared and intrinsic dynamical models for each of the isolated field galaxies using the 16th and 84th percentile parameters, with the lower velocity 16th percentile model constructed using the upper limit on the inclination, and the 84th percentile model using the lower limit.
-To clearly distinguish the 1-$\sigma$ error regions for both the beam smeared and intrinsic model the region between the 16th and 84th percentile evaluations are shaded blue and red respectively in the figures shown in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies}.
+During the following procedure $PA_{kin}$ is fixed to the maximum-likelihood value for all model evaluations.
+We proceed to reconstruct the beam-smeared and intrinsic dynamical models for each of the isolated field galaxies using the 16th and 84th percentile parameters, with the lower velocity 16th percentile model constructed using the upper limit on the inclination, and the 84th percentile model using the lower limit.
+To clearly distinguish the 1-$\sigma$ error regions for both the beam-smeared and intrinsic models, the region between the 16th and 84th percentile evaluations is shaded blue and red respectively in the velocity extaction panels throughout Figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies}.
 The +/- 1-$\sigma$ error values for both $V_{C}$ are then calculated using the the equations below, which also take into account the measurement errors with $\bar{\sigma}_{v_{obs}}$ equal to the average observational uncertainty extracted along $PA_{kin}$.
@@
 The upper and lower errors on the $\sigma_{int}$ are calculated using a similar approach.
-To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40kms^{-1}$ and $\sigma_{int} = 80kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
+To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50 kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40 kms^{-1}$ and $\sigma_{int} = 80 kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
 Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-When assuming the broader $\sigma_{int} = 80km^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.
-Conversely, assuming $\sigma_{int} = 40km^{-1}$ increases the beam-smearing.
+When assuming the broader $\sigma_{int} = 80 kms^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.
+Conversely, assuming $\sigma_{int} = 40 kms^{-1}$ increases the beam-smearing.
 We calculate the minimum and maxmimum intrinsic velocity dispersion, $\sigma_{int-84-40}$ and $\sigma_{int-16-80}$, using equations \ref{eq:sig_84_40} and \ref{eq:sig_16_80} respectively:
@@
 
-where $\sigma_{bs-84-40} = \sigma_{model-84-40} - 40$ and $\sigma_{bs-16-80} = \sigma_{model16-80} - 80$ are the beam smeared maps.
+where $\sigma_{bs-84-40} = \sigma_{model-84-40} - 40$ and $\sigma_{bs-16-80} = \sigma_{model16-80} - 80$ are the beam-smeared maps.
 The lower and upper errors on $\sigma_{int}$ are then given by the following:
@@
 \end{equation}
+
+\section{Kinematics Plots}\label{app:kinematics_plots}
+In Figures \ref{fig:rotation_dominated_galaxies}, \ref{fig:dispersion_dominated_galaxies} and \ref{fig:merger_galaxies} we plot the kinematic grids for the KDS galaxies classified as rotation-dominated, dispersion-dominated and merger candidates respectively.
+The figure captions provide more information on each of the panels of these grids.
 
@@
     \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs016759_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_20_grid_paper.png}
-
-    \phantomcaption
-
-\end{figure*}
-
-\begin{figure*}\ContinuedFloat
-    \centering
-
-    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_38_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_32_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_91_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs009818_grid_paper.png}
-
-    \phantomcaption
-
-\end{figure*}
-
-\begin{figure*}\ContinuedFloat
-    \centering
-
-    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_b012141_012208_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22a-d3_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_n3_009_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-c20_grid_paper.png}
-
-    \phantomcaption
-
-\end{figure*}
-
-\begin{figure*}\ContinuedFloat
-\centering
-
-    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-d5_grid_paper.png}
-
-\caption{We plot here the kinematic grids for the 13 isolated field sample galaxies classified as rotation-dominated.
+
+    \caption{We plot the kinematic grids for the 13 isolated field sample galaxies classified as rotation-dominated.
     For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
@@
 
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_38_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_32_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_91_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_bs009818_grid_paper.png}
+
+    \caption{\textbf{Continued.}}
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_b012141_012208_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22a-d3_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_n3_009_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-c20_grid_paper.png}
+
+    \caption{\textbf{Continued.}}
+
+\end{figure*}
+
+\begin{figure*}\ContinuedFloat
+\centering
+
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/combine_sci_reconstructed_cdfs_lbg_20_grid_paper.png}
+    \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-d5_grid_paper.png}
+
+    \caption{\textbf{Continued.}}
+
+\end{figure*}
+
 \begin{figure*}
@@
 
-    \phantomcaption
+    \caption{The same as in figure \protect\ref{fig:rotation_dominated_galaxies} but for the dispersion-dominated galaxies.}
+    \label{fig:dispersion_dominated_galaxies}
 
@@
 
-    \phantomcaption
+    \caption{\textbf{Continued.}}
 
@@
 
-    \caption{The same as in figure \protect\ref{fig:rotation_dominated_galaxies} but for the dispersion-dominated galaxies.}
-    \label{fig:dispersion_dominated_galaxies}
-
-\end{figure*}
-
-\begin{figure*}\ContinuedFloat
+    \caption{\textbf{Continued.}}
+
+\end{figure*}
+
+\begin{figure*}
     \centering
@@
     \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_cdfs_lbg_23_grid_paper.png}
-    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_bs010545_grid_paper.png}
-
-    \phantomcaption
-
+
+    \caption{The same as for figure \protect\ref{fig:rotation_dominated_galaxies} but for the merger candidates.
+    In this case we plot only fits to the data in the velocity extraction plot with the blue line, rather than attempting the full beam-smearing analysis.
+    Several of the galaxies here mimic rotation from a purely kinematic perspective, but have two or more {\em HST} components and an accompanying double peak in the object spectrum at the object centre, leading to large velocity dispersions when single gaussian fits are attempted.}
+    \label{fig:merger_galaxies}
 \end{figure*}
@@
     \includegraphics[width=0.95\textwidth]{SSA_MERGERS/combine_sci_reconstructed_s_sa22a-c35_grid_paper.png}
-
-    \caption{The same as for figure \protect\ref{fig:rotation_dominated_galaxies} but for the merger candidates.
-    In this case we plot only fits to the data in the velocity extraction plot with the blue line, rather than attempting the full beam-smearing analysis.
-    Several of the galaxies here mimic rotation from a purely kinematic perspective, but have two or more {\em HST} components and an accompanying double peak in the object spectrum at the object centre, leading to large velocity dispersions when single gaussian fits are attempted.}
-    \label{fig:merger_galaxies}
+    \includegraphics[width=0.95\textwidth]{GOODS_MERGERS/combine_sci_reconstructed_bs010545_grid_paper.png}
+
+    \caption{\textbf{Continued.}}
+
 \end{figure*}

### 2017-03-29 paper.tex
Removed half-light plot

@@
 
-In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
-In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).
+%In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
+%In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).
 
@@
 
-\begin{figure*}
-    \centering \hspace{-2.0cm}
-    \begin{subfigure}[h!]{0.50\textwidth}
-        \centering
-        \includegraphics[height=3.5in]{axis_ratio_distributions.png}
-        %\caption{axis ratio distributions}
-    \end{subfigure} \hspace{0.4cm}
-    \begin{subfigure}[h!]{0.50\textwidth}
-        \centering
-        \includegraphics[height=3.6in]{size_distributions.png}
-        %\caption{size distributions}
-    \end{subfigure}
-    \caption{{\it Left:} The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
+\begin{figure}
+\centering \hspace{-1.13cm}
+\includegraphics[width=0.49\textwidth]{axis_ratio_distributions.png}
+\caption{The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
     The axis ratio distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < b/a < 0.9$.
-    This suggests that we are not biased towards deriving a particular value for the axis ratio.
-    {\it Right:} The normalised counts of KDS galaxies in bins of half-light radius is plotted, along with the half-light radii of the same \protect\cite{VanderWel2012} galaxies as the left panel.
-    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\simeq3.5$.
-    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
-    The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
+    This suggests that we are not biased towards deriving a particular value for the axis ratio.}
 \label{fig:morpho-distributions}
-\end{figure*}
+\end{figure}
+
+%\begin{figure*}
+%    \centering \hspace{-2.0cm}
+%    \begin{subfigure}[h!]{0.50\textwidth}
+%        \centering
+%        \includegraphics[height=3.5in]{axis_ratio_distributions.png}
+%        %\caption{axis ratio distributions}
+%    \end{subfigure} \hspace{0.4cm}
+%    \begin{subfigure}[h!]{0.50\textwidth}
+%        \centering
+%        \includegraphics[height=3.6in]{size_distributions.png}
+%        %\caption{size distributions}
+%    \end{subfigure}
+%    \caption{{\it Left:} The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
+%    The axis ratio distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < b/a < 0.9$.
+%    This suggests that we are not biased towards deriving a particular value for the axis ratio.
+%    {\it Right:} The normalised counts of KDS galaxies in bins of half-light radius is plotted, along with the half-light radii of the same \protect\cite{VanderWel2012} galaxies as the left panel.
+%    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\simeq3.5$.
+%    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
+%    The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
+%    \label{fig:morpho-distributions}
+%\end{figure*}
 
@@
 \sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{BS}^{2}\right) - \sigma_{inst}^{2}}
-\end{equation}
+\end{equation} \\
 
@@
 We present the observed and model determined kinematic parameters in Table \ref{tab:kin_props} for the isolated field sample.
+
+\subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}
+The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
+This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
+Significant misalignment between the two axes can be a signature of galaxy interaction.
+
+The resolved KDS galaxies at $z\simeq3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
+For the majority of galaxies we are not in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
+Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
+This generally does not give the same answer as simply connecting the velocity extrema, as we have verified by rotating $PA_{Kin}$ in 1$^{\circ}$ increments and choosing the value which maximises the velocity gradient, calling this $PA_{rot}$.
+If the direction of the `zero-velocity strip' across the centre of the velocity maps is not perpendicular to the line connecting the velocity extrema, the $PA_{Kin}$ determined from MCMC will be different to the $PA_{Kin}$ determined from rotation (e.g.
+GOODS-S galaxy bs006541).
+As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ makes only a small difference to the final $V_{C}$ values, a difference which does not affect the outcomes of this work.
+
+\subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
+We proceed to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
+This is a simple empirical diagnostic for whether a galaxy is `Rotation-Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion-Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
+a method to measure the prevalence of rotational and random motions;][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
+Previous studies have used various classification schemes of varying complexity to identify rotation-dominated galaxies which also appear to be `disk-like' and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
+We describe our simple classification criteria for the isolated field sample based on a joint consideration of the high-resolution photometry and derived kinematic parameters in \cref{subsubsection:isolated_classification} and mention the KDS merger candidates in more detail in the following section.
+
+\subsubsection{KDS merger candidates}\label{subsubsection:merger_candidates}
+KDS galaxies are classified as mergers when more than one component is identified in the high-resolution imaging.  
+One benefit of studying the {\em HST} photometry in tandem with the kinematics is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
+These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
+A second benefit is to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
+can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging (e.g.
+the bottom grid in Figure \ref{fig:main_body_kinematic_grids}).
+
+This has been discussed in \cite{Hung2015}, where redshifted local interacting galaxies are misclassified as single rotating disks on the basis of their kinematics. 
+In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
+It is difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e.
+clumpy disk galaxies e.g.
+\citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
+Perhaps the most telling diagnostic are two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map.
 
@@
 
-\subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}
-
-The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
-This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
-Significant misalignment between the two axes can be a signature of galaxy interaction.
-
-The resolved KDS galaxies at $z\simeq3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
-For the majority of galaxies we are not in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
-Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
-This generally does not give the same answer as simply connecting the velocity extrema, as we have verified by rotating $PA_{Kin}$ in 1$^{\circ}$ increments and choosing the value which maximises the velocity gradient, calling this $PA_{rot}$.
-If the direction of the `zero-velocity strip' across the centre of the velocity maps is not perpendicular to the line connecting the velocity extrema, the $PA_{Kin}$ determined from MCMC will be different to the $PA_{Kin}$ determined from rotation (e.g.
-GOODS-S galaxy bs006541).
-As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ makes only a small difference to the final $V_{C}$ values, a difference which does not affect the outcomes of this work.
-
-\subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
-We proceed to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
-This is a simple empirical diagnostic for whether a galaxy is `Rotation-Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion-Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
-a method to measure the prevalence of rotational and random motions;][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
-Previous studies have used various classification schemes of varying complexity to identify rotation-dominated galaxies which also appear to be `disk-like' and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
-We describe our simple classification criteria for the isolated field sample based on a joint consideration of the high-resolution photometry and derived kinematic parameters in \cref{subsubsection:isolated_classification} and mention the KDS merger candidates in more detail in the following section.
-
-\subsubsection{KDS merger candidates}\label{subsubsection:merger_candidates}
-KDS galaxies are classified as mergers when more than one component is identified in the high-resolution imaging.  
-One benefit of studying the {\em HST} photometry in tandem with the kinematics is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
-These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
-A second benefit is to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
-can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging (e.g.
-the bottom grid in Figure \ref{fig:main_body_kinematic_grids}).
-
-This has been discussed in \cite{Hung2015}, where redshifted local interacting galaxies are misclassified as single rotating disks on the basis of their kinematics. 
-In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
-It is difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e.
-clumpy disk galaxies e.g.
-\citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
-Perhaps the most telling diagnostic are two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map. \\
-
 In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identify signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
@@
 \cite{Law2009} observe galaxies with elevated velocity dispersions at $z\simeq2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.
+
 \cite{Genzel2011} show that for dispersion-dominated galaxies, the scales susceptible to gravitational collapse are of order the galactic half-light radius. 

### 2017-03-30 paper.tex
Finished all changes - about to send final draft to co-authors

@@
-\documentclass[fleqn,usenatbib]{mn2e}
+\documentclass[fleqn,usenatbib]{mnras}
 
@@
   linkcolor=red,
-  urlcolor=cyan}
+  urlcolor=blue}
 
@@
 \usepackage{newtxtext,newtxmath}
+\usepackage[compatibility=false]{caption}
 \usepackage{subcaption}
@@
 \\
-$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
+$^{1}SUPA\thanks{Scottish Universities Physics Alliance}$, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
 $^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
@@
 \begin{abstract}
-We present dynamical measurements for 77 star-forming galaxies at $z\simeq3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
+We present dynamical measurements for 77 star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
 These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
@@
 The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs.
-stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}.
+stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2017,Qu2017}.
 To account for the growing number density of quiescent galaxies from z$\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e.
@@
 When interpreted in tandem with high-resolution imaging data from the {\it Hubble Space Telescope (HST)}, these data provide information about the range of physical processes which are driving galaxy evolution.
-In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high redshift campaigns.
+In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2017,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high redshift campaigns.
 
@@
 
-There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017,Ubler2017}.
+There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016,Harrison2017,Straatman2017,Ubler2017}.
 Systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
@@
 We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
+By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
 \\
@@
     \end{subfigure}
-    \caption{{\it Left:} The distribution of 49 KDS galaxies (see \cref{subsubsec:sed_fitting}) in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
+    \caption{{\it Left:} The distribution of all 77 KDS galaxies in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
     Also plotted in this plane are $\simeq4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density in of galaxies in that region.
     We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
-    {\it Right:} We plot the location of the 49 KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
+    {\it Right:} We plot the location of the KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
     The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
@@
 During the SED fitting process, dust attenuation was accounted for using the \cite{Calzetti2000} reddening law, with dust attenuation allowed to vary freely within the range $0.0<A_{V}<2.5$.
-Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 10.0$. 
+Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 9.8$. 
 We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
-In SSA22, 29 targets (36\% of the full KDS sample) do not have robust SFR measurements due to being undetected at $\geq 2\sigma$ significance in the available $J-$ and $K-$band photometry.
-The median of the ratio of the derived stellar masses in GOODS-S to the matched stellar masses in \cite{Santini2015} (which presents an average result from 10 different sets of analyses) shows that the masses adopted here are $\simeq0.15$ dex larger.
-\\
-
-In the left panel of Figure \ref{fig:main_sequence} we plot the 64\% of KDS galaxies with SFR measurements in the rest-frame {\it U-V} vs. {\it V-J} colour space.
+In GOODS-S, we have compared our derived stellar masses to those in \cite{Santini2015} (which presents an average result from 10 different sets of analyses), finding a median difference between the two sets of values of $\Delta \log(M_{\star}/{\rm M}_{\odot}) = 9.8$ \\
+
+In the left panel of Figure \ref{fig:main_sequence} we plot the KDS galaxies in the rest-frame {\it U-V} vs. {\it V-J} colour space.
 This is a commonly used diagnostic plane for selecting star-forming and quiescent galaxies \citep[e.g.][]{Williams2009,Brammer2011,Whitaker2012a} with the age gradients of the stars within quiescent galaxies placing them in a different region of the plane to those which are actively forming stars.
@@
 We also make use of the rest-frame colours of $\simeq4000$ primarily star-forming galaxies located in GOODS-S between $3.0 < z < 3.8$ (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
-The filled squares indicate the density of 3D-{\em HST} targets in colour space and we observe that the peak density location is consistent with the location of the KDS targets, all of which are in the star-forming region.
+The filled squares indicate the density of 3D-{\em HST} targets in colour space and we observe that the peak density location is consistent with the location of the KDS targets, all but one of which are in the star-forming region.
 
@@
  \hline
-b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 10.2 & 59 & 0.36        & 72        & 9     & 1.57      \\
-b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 10.4 & 27 & 0.28        & 78        & 146   & 0.52      \\
-bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.9  & 14 & 0.50         & 61        & 146   & 1.91      \\
-bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.2 & 18 & 0.44        & 66        & 168   & 1.83      \\
-bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.7 & 42 & 0.50         & 61        & 67    & 1.59      \\
-bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.8  & 33 & 0.80         & 37        & 148   & 1.24      \\
-bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 10.2 & 30 & 0.31        & 76        & 63    & 1.61      \\
-bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 10.0  & 9  & 0.65        & 50        & 49    & 0.87      \\
-lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.6  & 5  & 0.64        & 52        & 1     & 1.28      \\
-lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.7  & 6  & 0.53        & 60        & 34    & 1.27      \\
-lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 6  & 0.30         & 76        & 78    & 1.18      \\
-lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.1  & 29  & 0.79         & 38        & 66    & 0.95      \\
-lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 10.2 & 52 & 0.60         & 54        & 40    & 1.88      \\
-lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 10.0 & 8  & 0.58        & 56        & 137   & 0.92      \\
+b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.84 & 97 & 0.36        & 72        & 9     & 1.57      \\
+b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.76 & 172 & 0.28        & 78        & 146   & 0.52      \\
+bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.75  & 14 & 0.50         & 61        & 146   & 1.91      \\
+bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.1 & 10 & 0.44        & 66        & 168   & 1.83      \\
+bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.5 & 20 & 0.50         & 61        & 67    & 1.59      \\
+bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.7  & 33 & 0.80         & 37        & 148   & 1.24      \\
+bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 9.7 & 92 & 0.31        & 76        & 63    & 1.61      \\
+bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 9.9  & 6  & 0.65        & 50        & 49    & 0.87      \\
+lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.5  & 5  & 0.64        & 52        & 1     & 1.28      \\
+lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.6  & 5  & 0.53        & 60        & 34    & 1.27      \\
+lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 5  & 0.30         & 76        & 78    & 1.18      \\
+lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.0  & 18  & 0.79         & 38        & 66    & 0.95      \\
+lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 9.9 & 64 & 0.60         & 54        & 40    & 1.88      \\
+lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 9.9 & 5  & 0.58        & 56        & 137   & 0.92      \\
 lbg\_91         & 03:32:27.202 & $-$27:41:51.756 & 3.170       & 24.65  & 9.8   & 6  & 0.58        & 56        & 79    & 0.89 \\
-lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 10.0 & 8  & 0.22        & 84        & 81    & 1.16      \\
-lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.8  & 30 & 0.56        & 57        & 128   & 1.72      \\
-lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7  & 9  & 0.60         & 54        & 119   & 1.98      \\
-lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7  & 27 & 0.74        & 42        & 80    & 0.64      \\
-lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.7  & 5  & 0.79         & 38        & 43    & 0.46      \\
-lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.8  & 41 & 0.52        & 60        & 15    & 0.87      \\
-lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.1  & 10  & 0.56         & 57        & 50    & 0.78      \\
-$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.6 & 50 & 0.57         & 57        & -    & 2.52      \\
-n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7  & -            & 0.75        & 42        & 84    & 1.06      \\
-n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.9  & -            & 0.71        & 46        & 94    & 0.56      \\
-lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.7  & -            & 0.85        & 32        & 27    & 0.46      \\
-$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.8  & -            & 0.57         & 57        & -    & 2.18      \\
-s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.9  & -            & 0.39        & 70        & 125   & 1.78      \\
-s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.7  & -            & 0.57        & 57        & 76    & 1.59      \\
-$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.3 & -            & 0.57         & 57        & -    & 3.30      \\
-s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1 & -            & 0.65        & 50        & 60   & 0.5       \\
-$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 9.1  & -            & 0.57         & 57        & -    & 1.39
+lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 9.9 & 8  & 0.22        & 84        & 81    & 1.16      \\
+lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.3  & 54 & 0.56        & 57        & 128   & 1.72      \\
+lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7  & 8  & 0.60         & 54        & 119   & 1.98      \\
+lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7  & 18 & 0.74        & 42        & 80    & 0.64      \\
+lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.6  & 6  & 0.79         & 38        & 43    & 0.46      \\
+lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.6  & 56 & 0.52        & 60        & 15    & 0.87      \\
+lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.0  & 13  & 0.56         & 57        & 50    & 0.78      \\
+$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.5 & 14 & 0.57         & 57        & -    & 2.52      \\
+n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7  & 3            & 0.75        & 42        & 84    & 1.06      \\
+n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.8  & 4            & 0.71        & 46        & 94    & 0.56      \\
+lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.2  & 4            & 0.85        & 32        & 27    & 0.46      \\
+$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.4  & 7            & 0.57         & 57        & -    & 2.18      \\
+s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.7  & 60            & 0.39        & 70        & 125   & 1.78      \\
+s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.5  & 45            & 0.57        & 57        & 76    & 1.59      \\
+$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.2 & 9            & 0.57         & 57        & -    & 3.30      \\
+s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1 & 5            & 0.65        & 50        & 60   & 0.5       \\
+$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 8.6  & 10            & 0.57         & 57        & -    & 1.39
 
@@
 We have visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
-We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2016}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
+We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2017}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
 We discuss this topic further in \cref{subsubsection:kin_and_phot}.
@@
 This extraction radius is shown with the vertical red dashed line in the panels of Figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
-The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Stott2016,Pelliccia2017,Harrison2017,Swinbank2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
-This is similar to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\simeq3R_{D}$), \citep{Tiley2016a}.
+The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Stott2016,Pelliccia2017,Harrison2017,Swinbank2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2016,Harrison2017,Swinbank2017}.
+This is similar to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\simeq3R_{D}$), \citep{Tiley2016}.
 
@@
 These include the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in \cite{ForsterSchreiber2009} and \cite{Cresci2009}.
-In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotation-dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\simeq1$ using the same criteria).
+In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotation-dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2017} for a re-analysis of KMOS$^{3D}$ data at z$\simeq1$ using the same criteria).
 In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification is outlined in their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
@@
     {\it Right:} The mean, median and distributions of the comparison sample $V_{C}$ measurements are plotted against redshift.
+    The symbol positions with black errorbars (some not visible) show the mean values and the horizontal filled and grey bars show the median values and associated errors.
+    The mean mass of each survey is listed beside the survey name.
     The $V_{C}$ distributions in each of the individual studies are wide, reflecting the galaxy diversity within each sample.
@@
 Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
-However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,DiTeodoro2016,Simons2016,Pelliccia2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
+However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Simons2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
 At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} consistent with the $z\simeq0$ relation.
@@
 The rotation-dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\simeq0.9$ relation, but with a tendency to lie below the relation.
-When considered alone, the mean velocity of the rotation-dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=10.0$ is $\simeq0.1$ dex beneath the KROSS relation at the same mass.
+When considered alone, the mean velocity of the rotation-dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=9.8$ is $\simeq0.05$ dex beneath the KROSS relation at the same mass.
 The dispersion-dominated KDS galaxies sit clearly separated and below the $z\simeq0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\simeq0.9$ dispersion-dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
@@
     The mean $\sigma_{int}$ values increase from $\simeq15kms^{-1}$ in the local universe to $> 70kms^{-1}$ at $z > 3$.
+    The symbol convention is the same as in the right panel of Figure \protect\ref{fig:tf_relation}.
     The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values and in each case for $V_{C} = 125kms^{-1}$.
@@
 $V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
-Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of gas mass and dark matter mass would raise this estimate).
-Indeed this value is similar to the mean $V_{C}$ value found in the KROSS sample for $log(M_{\star}/M_{\odot})=10.0$ galaxies at $z\simeq1$. \\
+Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
+\\
 
@@
 
-The KDS mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
-The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
+The isolated field sample mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 95kms^{-1}$ lower limit.
+However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}kms^{-1}$ respectively, much closer to the $\left<V_{C}\right> = 95kms^{-1}$ lower limit.
+This implies that the observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
 This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion-dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
-However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contributes to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
-This topic is discussed further throughout \cref{sec:discussion}. \\\\
+However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contribute to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
+This topic is discussed further throughout \cref{sec:discussion}. \\
 
@@
 
-The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}/M_{\odot})=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
+The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}/M_{\odot})=9.8,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
 The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\simeq1$ for the gas-rich disks observed at high-z e.g.
@@
     The dot-dash line is the RDF $\propto z^{-0.2}$ cosmic decline suggested in \protect\cite{Stott2016}.
+    In both panels, the symbol convention is the same as in the right panel of Figure \protect\ref{fig:tf_relation}.
 }
@@
     \end{subfigure}
-    \caption{{\it Left:} We plot the directly comparable $\sigma_{int}$ values (see filled symbols) for the surveys spanning $z=0-3$ as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 10.0$.
+    \caption{{\it Left:} We plot the directly comparable $\sigma_{int}$ values (see filled symbols) for the surveys spanning $z=0-3$ as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 9.8$ (the median of the isolated field sample masses).
     The dark grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
@@
 This is done by computing the difference between the model predicted $\sigma_{int}$ value at the stellar mass of each comparison survey and at the reference mass for the appropriate redshift and shifting the reported $\sigma_{int}$ by this value.
-We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 10.0$ (the mean mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}) and we only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
+We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 9.8$ (the median of the isolated field sample masses) (the mean mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}) and we only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
 In both panels the dark grey shaded regions encompass the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
@@
 We have presented new measurements of 77 main-sequence star forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
-These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.5 < log(M_{\star}/M_{\odot})< 10.5$ typical main-sequence galaxies at these redshifts.
+These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.0 < log(M_{\star}/M_{\odot})< 10.5$ typical main-sequence galaxies at these redshifts.
 By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\simeq18\%$) and a very high merger rate in the cluster pointing ($\simeq89\%$).
@@
     The dispersion-dominated galaxies scatter below the trend, with the same slope as the rotation-dominated galaxies.
-    \item When considering the rotation-dominated galaxies alone the median and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}kms^{-1}$ respectively, which are lower than expected from a simple virial theorem calculation using the mean mass and half-light radius of the sample.
+    \item When considering the rotation-dominated galaxies alone the mean and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}kms^{-1}$ respectively, which are lower than expected from a simple virial theorem calculation using the mean mass and half-light radius of the sample.
     This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in the system \citep[e.g.][]{Burkert2010}.  
@@
 \clearpage 
-\bibliographystyle{apj.bst}
+\bibliographystyle{mnras}
 %\bibliography{/usr/local/texlive/texmf-local/bibtex/bib/ojt.bib}
@@
  AMAZE (Clean) & 3.0 & 10.0 & $1.4^{+0.3}_{-0.3}$ & $1.1^{+0.3}_{-0.3}$ & - & $95.7^{+2.0}_{-2.0}$ & $95.0^{+2.6}_{-2.6}$ & $140.8^{+40.1}_{-30.2}$ & $129.0^{+45.0}_{-33.4}$ \\[1ex]
- \textbf{KDS} & 3.5 & 10.0 & $1.1^{+0.2}_{-0.1}$ & $0.84^{+0.1}_{-0.1}$ & $0.37^{+0.08}_{-0.08}$ & $70.3^{+3.3}_{-3.1}$ & $71.0^{+5.0}_{-4.8}$ & $75.7^{+4.4}_{-4.4}$ & $57.5^{+5.5}_{-5.5}$ \\[1ex]
+ \textbf{KDS} & 3.5 & 9.8 & $1.1^{+0.2}_{-0.1}$ & $0.84^{+0.1}_{-0.1}$ & $0.37^{+0.08}_{-0.08}$ & $70.3^{+3.3}_{-3.1}$ & $71.0^{+5.0}_{-4.8}$ & $75.7^{+4.4}_{-4.4}$ & $57.5^{+5.5}_{-5.5}$ \\[1ex]
  \hline
@@
 The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\simeq191$ massive SFGs across two redshift slices. 
-At $z\simeq1.0$ the galaxies have $log(M_{\star}/M_{\odot})=10.7$ and at $z\simeq2.3$ the median is $log(M_{\star}/M_{\odot})=10.9$, approaching an order-of-magnitude above the KDS median of $log(M_{\star}/M_{\odot})=10.0$.
+At $z\simeq1.0$ the galaxies have $log(M_{\star}/M_{\odot})=10.7$ and at $z\simeq2.3$ the median is $log(M_{\star}/M_{\odot})=10.9$, over an order-of-magnitude above the KDS median of $log(M_{\star}/M_{\odot})=9.8$.
 The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
@@
 
-This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, however, despite this diversity, over the past decade the studies appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
+This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, however, despite this diversity, over the past decade the studies appear to be converging on `modelling out' the effects of beam-smearing using similar approaches (e.g.
+as described in \citealt{Davies2011}, where removing the effects of beam-smearing with spectrally and spatially convolved models is also the least biased approach).
 This trend towards consistency is encouraging, and, as described in \cref{subsec:3d_modelling}, we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.

### 2017-04-03 paper.tex
ABOUT TO ADDRESS CHRIS COMMENTS APRIL 3rd

@@
 % Keep the title short and informative.
-\title[KDS I: dynamical properties of 77 z$\simeq3.5$ galaxies]{The KMOS Deep Survey (KDS) I: dynamical measurements of typical star forming galaxies at $z\simeq3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
+\title[KDS I: dynamical properties of 77 $z\simeq3.5$ galaxies]{The KMOS Deep Survey (KDS) I: dynamical measurements of typical star forming galaxies at $z\simeq3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
 Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)}}
@@
 \author[O.J. Turner et al.]{
-O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
+O. J. Turner,$^{1,2,\thanks{E-mail: ojamesturner@icloud.com (OJT)}}$
 M. Cirasuolo,$^{1,2}$
@@
 \begin{abstract}
-We present dynamical measurements for 77 star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
+We present dynamical measurements from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS), which is comprised of 77 typical star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$.
 These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
@@
 The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
-At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, as regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
+At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
 This assumes that high redshift main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
@@
 stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2017,Qu2017}.
-To account for the growing number density of quiescent galaxies from z$\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e.
+To account for the growing number density of quiescent galaxies from $z\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e.
 quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.
@@
 In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
-There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item How applicable are strong-line metallicity calibrators at high redshift?
-\item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
+With this survey, we aim to complement existent studies by providing deep IFS data for the largest number of galaxies at this redshift.
+By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
+In order to interpret the evolution of the physical properties of typical star-forming galaxies we have carefully constructed a set of comparison samples spanning $0 < z < 3$.
+These samples use integral-field spectroscopy to track the ionised gas emission in star-forming galaxies and follow consistent kinematic parameter extraction methods.  
+By doing this we seek to minimise the impact of systematic differences introduced by differing approaches to defining and extracting kinematic parameters.
+
+There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
 \item What are the dynamical properties of main-sequence galaxies at this early stage in their lifetimes? 
@@
 This paper focuses on the third question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
-We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
-By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
 \\
@@
 \cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible underlying physical mechanisms.
-We present our conclusions in \cref{sec:conclusion}.
+We discuss these results in \cref{sec:discussion} and present our conclusions in \cref{sec:conclusion}.
 Throughout this work we assume a flat $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).
@@
 The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
-The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation ( particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
+The key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation ( particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
 We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and a `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
-To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
+To achieve this we require very deep exposure times in excess of 7 hours on source to reach the signal to noise required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate signal to noise across several ionised emission lines within individual spatial pixels (spaxels).
 Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.
@@
 \subsubsection{Sample selection}\label{subsubsec:sample_selection}
-Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep multi-wavelength ancillary data.
+Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep, multi-wavelength ancillary data.
 Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
-From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest S/N and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
+From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal to noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
 To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a previous spectroscopic detection (see details below).
@@
 However, a subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
-We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift.
+We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift (see Figure \ref{fig:main_sequence}).
 
@@
 
-Two of the FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+Two of the three FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
 We selected targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
@@
 The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\simeq20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
-In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}
+We name these GOODS-S-P1 and GOODS-S-P2, which which we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies quoted for GOODS-S-P2 does not include two observed targets which were later found to have $z < 0.5$.}
 
@@
 
-We also added a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
+We also added a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical of the field environment (SSA22-P2).
 In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
@@
 
-Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
+Our data for the 77 KDS targets were observed using KMOS \citep{Sharples2013}, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
 The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
@@
     \caption{{\it Left:} The distribution of all 77 KDS galaxies in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
-    Also plotted in this plane are $\simeq4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density in of galaxies in that region.
-    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
+    Also plotted in this plane are $\simeq4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density of galaxies in that region.
+    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that all but one of the KDS galaxies are clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
     {\it Right:} We plot the location of the KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
@@
 
-To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
+To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, facilitating both dynamical and chemical abundance measurements.
 The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously.
@@
 
+This paper is concerned with the spatially-resolved kinematics of the KDS galaxies.
 Consequently, we now focus exclusively on the spatially-resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
-This paper is concerned with the spatially-resolved kinematics of the KDS galaxies, with the details of the {\it H}-band data reduction and corresponding metallicity analyses reserved for a future analysis.
+The details of the {\it H}-band data reduction and corresponding metallicity analyses will be described in a future study.
 
@@
 
-The SPARK recipes are used to create dark frames and to flatfield, illumination correct and wavelength calibrate the raw data.
-An additional step which is not part of the standard reduction process was carried out at this stage, which is to address readout channel bias.
+The SPARK recipes were used to create dark frames and to flatfield, illumination correct and wavelength calibrate the raw data.
+An additional step, which is not part of the standard reduction process, was carried out at this stage, which is to address readout channel bias.
 Differences in the readout process across each 64-pixel wide channel on the detector image lead to varying flux baselines in these channels.
@@
 We monitored the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged {\it K}-band seeing rose above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
-The PSF was determined from fitting the {\it K}-band collapsed, stacked standard-star cube in each pointing with an elliptical gaussian and the values are reported in Table \ref{tab:pointings}.
+The PSF was determined from fitting the {\it K}-band collapsed, stacked standard-star cube in each pointing with an elliptical gaussian, with the values reported in Table \ref{tab:pointings}.
 The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
@@
 
-We stacked all 300s exposures for each galaxy which pass seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
+We stacked all 300s exposures for each galaxy which pass the seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
 We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
@@
 In order to constrain their SFRs and stellar masses, the available photometry for the KDS targets was analysed using the SED fitting software described in \cite{McLure2011} and \cite{McLeod2015}.
-The photometry for each target was fit with the same set of solar metallicity BC03 \citep{Bruzual2003} templates recommended for reproducing the properties of star-forming galaxies by \cite{Wuyts2011a}, and derived stellar masses and SFRs were based on a Chabrier IMF.
-During the SED fitting process, dust attenuation was accounted for using the \cite{Calzetti2000} reddening law, with dust attenuation allowed to vary freely within the range $0.0<A_{V}<2.5$.
+The photometry for each target was fit with the same set of solar metallicity BC03 \citep{Bruzual2003} templates adopted by the 3D-HST team \cite{Momcheva2016}, and derived stellar masses and SFRs were based on a Chabrier IMF.
+In addition, the SED fitting software accounts for the presence of strong nebular emission lines according to the line ratios determined by \cite{Cullen2014}.
+During the SED fitting process, dust attenuation was accounted for using the \cite{Calzetti2000} reddening law, with dust attenuation allowed to vary freely within the range $0.0<A_{V}<4.0$.
 Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 9.8$. 
-We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
-In GOODS-S, we have compared our derived stellar masses to those in \cite{Santini2015} (which presents an average result from 10 different sets of analyses), finding a median difference between the two sets of values of $\Delta \log(M_{\star}/{\rm M}_{\odot}) = 9.8$ \\
+We note that fitting the photometry of the KDS targets with 0.2 $Z\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
+In GOODS-S, we have compared our derived stellar masses to those in \cite{Santini2015} (which presents an average result from 10 different sets of analyses), finding a median difference between the two sets of values of $\Delta \log(M_{\star}/{\rm M}_{\odot}) = 0.009$ \\
 
@@
 The difference in position of these relations highlights the main-sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\simeq2.5-3.5$.
-The KDS galaxies scatter, within the errors, consistently above and below the z$\simeq3$ main-sequence.
-
-When taken together, both panels indicate that the KDS sample is representatitve of typical SFGs at $z>3$.
+The KDS galaxies scatter, within the errors, consistently above and below the $z\simeq3$ main-sequence.
+
+When taken together, both panels indicate that the KDS sample is representatitve of typical star-forming galaxies at $z>3$.
 
@@
 This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$), morphological position angle, $PA_{morph}$, and axis ratio, $b/a$, of the galaxies.
-In the following sections we describe the approach we have chosen to recover these parameters detailing comparisons with matched galaxies in the morphological parameter catalogue of \cite{VanderWel2012}.
+In the following sections we describe the approach we have chosen to recover these parameters, also describing comparisons with matched galaxies in the morphological parameter catalogue of \cite{VanderWel2012}.
 At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
@@
 \subsubsection{Applying {\tt GALFIT} to the imaging data}\label{subsubsec:galfitting}
-We use {\tt GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
+We used {\tt GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
 The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z\simeq3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
-For SSA22 we make use of archival {\em HST} imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the WFC3 F160W band (P.I.
+For SSA22 we made use of archival {\em HST} imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the WFC3 F160W band (P.I.
 Lehmer: PID 13844; P.I.
@@
 Siana: PID 12527).
-The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the F160W coverage is concentrated on the SSA22-CLUSTER and so we resort to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage are listed in Table \ref{tab:phys-props}).
-\\
-
-We first run SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT} and then extract postage stamp regions around the galaxies in the KDS sample.
-At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
-In the F160W band the adopted PSF is a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the F814W band we use the pure Tiny Tim ACS high-resolution PSF model.
-During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.
-
-This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models and bulge/disk models with both an n = 1 and n = 4 component (following the procedure described in \cite{Bruce2012}) with the fixed exponential disk value of n = 1 , with the median ratio of $\chi ^{2}$ $\simeq1$ between the different fitting methods.
-Additionally, 22 GOODS-S objects are also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is n = 1.2.
-The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2}\simeq1.68 R_{D}$ (see \cref{subsec:KROSS}).
-\\
-
-This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
-Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially-resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout Appendix \ref{app:kinematics_plots}.
+The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the F160W coverage is concentrated on the SSA22-CLUSTER and so we resorted to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage are listed in Table \ref{tab:phys-props}).
+\\
+
+We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT} and then extracted postage stamp regions around the galaxies in the KDS sample.
+At this redshift, the galaxies are more compact and generally we could not resolve more complicated morphological features such as spiral arms and bars and so we followed the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of $n=1$.
+In the F160W band the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the F814W band we used the pure Tiny Tim ACS high-resolution PSF model.
+During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, were free to vary.
+
+This method was justified by the recovery of similar mean $\chi^{2}$ values when fitting floating \Sers index models and bulge/disk models with both an $n=1$ and $n=4$ component (following the procedure described in \citealt{Bruce2012}) to those recovered from the fixed exponential disk fit.
+Additionally, 22 GOODS-S objects were also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is $n=1.2$.
+The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors were applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2}\simeq1.68 R_{D}$ (see \cref{subsec:KROSS}).
+\\
+
+This analysis provided us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
+Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, and maps for the full isolated field sample (see \cref{subsubsection:spaxel_fitting}) are plotted throughout Appendix \ref{app:kinematics_plots}.
 
@@
 \subsubsection{Inclination angle}\label{subsubsection:inclination_angle}
-We use the derived $b/a$ values to determine galaxy inclination angles.
-As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
+We used the derived $b/a$ values to determine galaxy inclination angles.
+As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid, the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
 
@@
 
-To derive the inclination, we must select a value for $q_{0}$, and following the discussion in \citep{Law2012a} we choose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
-However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values, with the difference $<10\%$ in the case of the KDS galaxies in the refined sample (see \cref{subsubsec:kin_sample_summary}).
+To derive the inclination, we selected a value for $q_{0}$, and following the discussion in \citep{Law2012a} we chose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
+However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values, with the difference $<10\%$ in the case of the KDS galaxies in the isolated field sample (see \cref{subsec:morpho-kin-class}).
 
@@
 The median difference between the derived $b/a$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta b/a = 0.0002$.
-The $b/a$ distribution shown in Figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the refined sample with {\em HST} imaging, \cref{subsubsec:kin_sample_summary}) is consistent with being uniform between $0.3 < b/a < 0.9$, with a median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in Equation \ref{eq:holmberg_i} with $q_{0}=0.2$.
+The $b/a$ distribution shown in Figure \ref{fig:morpho-distributions} (plotted for the 28 galaxies in the isolated field sample with {\em HST} imaging, \cref{subsec:morpho-kin-class}) is consistent with being uniform between $0.3 < b/a < 0.9$, with a median value of 0.58, corresponding to i = 57.0$^{\circ}$ using the conversion given in Equation \ref{eq:holmberg_i}, with $q_{0}=0.2$.
 This compares well with the theoretical mean value of 57.3$^{\circ}$ computed for a population of galaxies with randomly drawn viewing angles (see e.g.
-the appendix in \citealt{Law2009}), reassuring us that we are not biased towards deriving either particularly low or particularly high inclination angles.
+the appendix in \citealt{Law2009}), which reassured us that we were not biased towards deriving either particularly low or particularly high inclination angles.
 
 As mentioned in \cref{subsubsec:galfitting}, the error reported by {\tt GALFIT} on the model $b/a$ value is unrealistically small.
-Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopt a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
-For the galaxies without {\em HST} coverage the inclination angle is set to the KDS sample median of 57.0$^{\circ}$ and we use the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
+Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopted a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
+For the galaxies without {\em HST} coverage the inclination angle was set to the KDS sample median of 57.0$^{\circ}$ and we used the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
 This corresponds to a factor $\simeq1.3$ contribution to the uncertainty in the derived velocities for these galaxies.
@@
 The second {\tt GALFIT} parameter is $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
-We have visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this is not the case it is usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
+We visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this was not the case it was usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
 We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2017}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
 We discuss this topic further in \cref{subsubsection:kin_and_phot}.
-For the galaxies without {\em HST} coverage we fix $PA_{morph}$ equal to $PA_{kin}$, following the analysis described in \cref{subsec:3d_modelling}.
+For the galaxies without {\em HST} coverage we fixed $PA_{morph}$ equal to $PA_{kin}$, for the analysis described in \cref{subsec:3d_modelling}.
 
@@
 As discussed throughout the introduction and in Appendix \ref{app:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
-Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies and see Appendix \ref{app:comparison_samples} and \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
-Throughout our dynamical modelling and beam-smearing correction (see \cref{subsec:3d_modelling}) we also require the $R_{1/2}$ value for each galaxy.
+Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies (see Appendix \ref{app:comparison_samples} and e.g.
+\citealt{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}).
+Throughout our dynamical modelling, and to derive a beam-smearing correction to the rotation velocities and velocity dispersions (see \cref{subsec:3d_modelling}), we also required the $R_{1/2}$ value for each galaxy.
 The median difference between the derived $R_{1/2}$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\simeq3.5$).
@@
 
-\cite{Bruce2012} presents a detailed error analysis for recovering the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploit during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
-We adopt a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high redshift galaxies (see Appendix \ref{app:kin_error_estimates}).
-
-To measure $R_{1/2}$ in the galaxies without {\em HST} coverage we first fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtract the PSF from the recovered $R_{1/2}$ value.
+\cite{Bruce2012} present a detailed error analysis of the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploited during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
+We adopted a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high redshift galaxies (see Appendix \ref{app:kin_error_estimates}).
+
+To measure $R_{1/2}$ for the galaxies without {\em HST} coverage we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
 We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening.
@@
 
-We proceed to extract 2D kinematic measurements from the 62 KDS datacubes detected in integrated [O~{\sc III}]$\lambda$5007 emission by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
-This sample is then refined to galaxies which are spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission in order to make dynamical measurements.
+We proceeded to extract 2D kinematic measurements from the 62 KDS datacubes detected in integrated [O~{\sc III}]$\lambda$5007 emission by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
+The sample is then refined to galaxies which are spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission in order to make dynamical measurements.
 We also describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam-smearing corrections for each galaxy.
-We make use of the imaging data described in the previous sections to reduce the number of free parameters in the model, an approach which is necessary when working in this S/N regime.
+We made use of the imaging data described in the previous sections to reduce the number of free parameters in the model, an approach which is necessary when working in this signal to noise regime.
 
 \subsubsection{Spaxel Fitting}\label{subsubsection:spaxel_fitting}
-We aim to extract two-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 62 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
+We aimed to extract two-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 62 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
 These properties are extracted via modelling emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
-We concentrate solely on the [O~{\sc III}]$\lambda$5007 emission line which always has S/N higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and is detected over a larger area of each IFU. \\
-
-Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn.
-The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, is used to determine the central wavelength of the redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$.
-We search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
-This truncated spectrum is then used in the fitting procedure for each spaxel.
-The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky line residuals.
-A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
-These parameters, along with the estimate of the noise in the datacube, are used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not. 
-The noise is estimated by masking all datacube spaxels containing object flux and computing the standard deviation of the flux values in the spectral extraction region for all remaining spaxels inwards of 0.3$^{\prime\prime}$ from the cube boundary (over the same spectral region as considered to find the peak object flux).
-This boundary constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
-The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation \ref{eq:noise} where $F_{i,background}$ are the flux values across the spatial regions containing no object flux and the spectral extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
+We concentrated solely on the [O~{\sc III}]$\lambda$5007 emission line which always had signal to noise higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and was detected over a larger area of each IFU.
+\\
+
+Each 0.1$^{\prime\prime}$ spaxel across a datacube was considered in turn.
+The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, was used to determine the central wavelength of the redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$.
+We searched a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extracted a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
+This truncated spectrum was then used in the fitting procedure for each spaxel.
+The width of the extraction region was large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky line residuals.
+A single gaussian model was fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
+These parameters, along with the estimate of the noise in the datacube, were used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not. 
+The noise was estimated by masking all datacube spaxels containing object flux and computing the standard deviation of the flux values in the spectral extraction region for all remaining spaxels inwards of 0.3$^{\prime\prime}$ from the cube boundary (over the same spectral region as considered to find the peak object flux).
+This boundary constraint was chosen to mitigate edge effects, where the noise increased sharply due to fewer individual exposures constituting the final stack in these regions.
+The final noise value was then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation \ref{eq:noise} where $F_{i,background}$ are the flux values across the spatial regions containing no object flux and the spectral extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
 
@@
 
-The signal in each spaxel is taken as the sum of the flux values across the extraction region, $F_{i,object}$, as shown in Equation \ref{eq:signal} where S denotes the signal.
+The signal in each spaxel was taken as the sum of the flux values across the extraction region, $F_{i,object}$, as shown in Equation \ref{eq:signal} where S denotes the signal.
 
@@
 
-\begin{enumerate}
-\item The uncertainties on any of the parameters of the gaussian fit as returned by {\tt LMFIT} must not exceed 30\%
+\begin{enumerate}[label=(\roman*)] \item The uncertainties on any of the parameters of the gaussian-fit as returned by {\tt LMFIT} must not exceed 30\%
 \item $\frac{S}{N_{m}} > 3$
@@
 
-We impose a further criterion to help remove fits to spectral features unrelated to the galaxy (e.g.
-fits to skyline residuals), which is important for `cleaning up' accepted spaxels in the 2D maps which are clearly unrelated to the galaxy.
-For this test we subtract the galaxy continuum and impose that $0.7 < F_{g}/{S} < 1.3$, where $F_{g}$ is the flux from the gaussian fit to the [O~{\sc III}]$\lambda$5007 line and S is the signal in the extraction region from Equation \ref{eq:signal}.
-If all three criteria are satisfied, the spaxel is accepted.
-\\
-
-From the gaussian fit we recover the centre, $\lambda_{g}$, the width, $\sigma_{g}$ and the area, $F_{g}$.
-The velocity is computed from $\lambda_{g}$ using Equation \ref{eq:velocity_comp} and the velocity dispersion is computed from $\sigma_{g}$ using Equation \ref{eq:dispersion_comp}, where $V_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light, $z_{sys}$ is the redshift determined from the integrated galaxy spectrum and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
+We imposed a further criterion to help remove fits to spectral features unrelated to the galaxy (e.g.
+fits to skyline residuals), which was important for `cleaning up' accepted spaxels in the 2D maps which were clearly unrelated to the galaxy.
+For this test we subtracted the galaxy continuum and imposed that $0.7 < F_{g}/{S} < 1.3$, where $F_{g}$ is the flux from the gaussian-fit to the [O~{\sc III}]$\lambda$5007 line and S is the signal in the extraction region from Equation \ref{eq:signal}.
+If all three criteria were satisfied, the spaxel was accepted.
+\\
+
+From the gaussian-fit we recovered the centre, $\lambda_{g}$, the width, $\sigma_{g}$ and the area, $F_{g}$.
+The velocity was computed from $\lambda_{g}$ using Equation \ref{eq:velocity_comp} and the velocity dispersion was computed from $\sigma_{g}$ using Equation \ref{eq:dispersion_comp}, where $V_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light, $z_{sys}$ is the redshift determined from the integrated galaxy spectrum and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
 
@@
 
-To estimate the errors on the observed quantities the gaussian fit is repeated 1000 times, with each flux value in the extraction region perturbed by the noise value, $N_{m}$.
-For each of these 1000 fits the gaussian parameters are used to compute the observed properties.
-The resultant distributions of observed quantities are gaussian and we take the median as the final values for $V_{obs}$, $\sigma_{obs}$ and $F_{g}$ for that spaxel and the standard deviation of the distribution as the observational uncertainties.
-A map of each of these observed parameters is constructed by applying this procedure to each spaxel. \\
-
-If a spaxel does not meet the criteria we follow the procedure described in \cite{Stott2016} and bin with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
-This is carried out by median stacking the extraction region spectra in each of the neighbouring spaxels.
-The criteria are then re-examined and if satisfied the Monte-Carlo procedure is carried out. 
-If the binned spaxels fail the criteria, one final iteration is carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$, roughly equivalent to the size of the seeing disk.
-If after the widest binning the criteria aren't satisfied, no value is assigned to that spaxel in the extracted maps. \\
-
-The process is automated and applied to each of the 62 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
-Following the fitting procedure the galaxies are clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map is equivalent to or greater than the seeing disk.
-For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, is added to Table \ref{tab:pointings}.
-We find that 47 (76\%) of the detected KDS galaxies across both the field and cluster environments are spatially-resolved and show clear velocity structure.
-The 15 galaxies which are not spatially-resolved are dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
+To estimate the errors on the observed quantities, the gaussian-fit was repeated 1000 times, with each flux value in the extraction region perturbed by the noise value, $N_{m}$.
+For each of these 1000 fits the gaussian parameters were used to compute the observed properties.
+The resultant distributions of observed quantities were gaussian and we measured the median as the final value for $V_{obs}$, $\sigma_{obs}$ and $F_{g}$ within that spaxel and the standard deviation of the distribution as the observational uncertainty.
+A map of each of these observed parameters was constructed by applying this procedure to each spaxel. \\
+
+If a spaxel did not meet the criteria we follow the procedure described in \cite{Stott2016} and binned with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
+This was carried out by median stacking the extraction region spectra in each of the neighbouring spaxels.
+The criteria were then re-examined, and if satisfied, the Monte-Carlo procedure was carried out. 
+If the binned spaxels fail the criteria, one final iteration was carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$, roughly equivalent to the size of the seeing disk.
+If after the widest binning the criteria weren't satisfied, no value was assigned to that spaxel in the extracted maps. \\
+
+The process was automated and applied to each of the 62 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
+Following the fitting procedure the galaxies were clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map was equivalent to or greater than the seeing disk.
+For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, was added to Table \ref{tab:pointings}.
+We find that 47 (76\%) of the detected KDS galaxies across both the field and cluster environments were spatially-resolved and showed clear velocity structure.
+The 15 galaxies which were not spatially-resolved were dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
 The physical properties of all spatially-resolved galaxies in both GOODS-S and SSA22 are listed in Table \ref{tab:phys-props}. \\
 
-The morphological information of \cref{subsec:morphological_measurements} is now combined with this spatially-resolved condition to define two galaxy subsamples.
-We find that 6/38 of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicates the interpretation of the observed dynamics for these targets.
-We thus drop the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
+The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
+6/38 of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
+We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
 The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
@@
 
-As mentioned in the introduction, there is no universal standard for defining $V_{C}$ and $\sigma_{int}$, particularly when a dynamical model is used to provide beam-smearing corrections for $\sigma_{int}$ and extrapolations beyond the data for $V_{C}$.
+As mentioned in the introduction, there is no universal standard for defining $V_{C}$ and $\sigma_{int}$, particularly when a dynamical model is used to provide beam-smearing corrections for $\sigma_{int}$ and to extrapolate beyond the data in order to measure $V_{C}$.
 Physically motivated models take into account the potential-well of the galaxy through knowledge of the mass distribution \citep[e.g.][]{Genzel2008,ForsterSchreiber2009,Gnerucci2011,Wisnioski2015,Swinbank2017}.
@@
 There are three reasons to construct model velocity fields for the isolated field sample galaxies; the first is to interpolate between data points; the second is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the third is to estimate the effect of beam-smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
-As a brief overview, we use a Markov chain Monte Carlo (MCMC) procedure to construct a series of intrinsic model datacubes for each galaxy, convolve these with the atmospheric PSF and then fit to the data.
-The beam-smearing corrected kinematic parameters are then extracted from the intrinsic galaxy models as described in more detail below.
-In this analysis we minimise the number of fitted parameters by making use of information from {\em HST} imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.
-This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.
+As a brief overview, we used a Markov chain Monte Carlo (MCMC) procedure to construct a series of intrinsic model datacubes for each galaxy, convolved these with the atmospheric PSF and then fit to the data.
+The beam-smearing corrected kinematic parameters were then extracted from the intrinsic galaxy models as described in more detail below.
+In this analysis we minimised the number of free parameters by making use of information from {\em HST} imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.
+This is particularly important when dealing with galaxies at $z > 3$, since often there is not enough signal to noise away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.
 The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.
@@
 \subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
-For each galaxy with spatially-resolved [O~{\sc III}]$\lambda$5007 emission we construct a series of model datacubes with the same spatial dimensions as the observed datacube and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
-This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
-Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by Equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
+For each galaxy with spatially-resolved [O~{\sc III}]$\lambda$5007 emission we constructed a series of model datacubes with the same spatial dimensions as the observed datacube and populated each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
+This central wavelength was then shifted using the velocity derived at each spaxel from the velocity field model described below.  
+Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas was modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by Equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
 
@@
 with `r' measured as the distance from the centre of rotation.
-This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times finer pixel scale than the KMOS raw data before binning back to the previous resolution.
-The pixel scale refinement is necessary to capture the steep velocity gradients across the central regions.
+This model was then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times finer pixel scale than the KMOS raw data before binning back to the previous resolution.
+The pixel scale refinement was necessary to capture the steep velocity gradients across the central regions.
 
 The velocity decreases with a factor of cos($\phi$) from the kinematic position axis, where $\phi$ is the angle measured clockwise from the axis, which points to the direction of the positive side of the velocity field.
-The 6 free parameters of the model; $(xcen, ycen), i, PA_{kin}, rt, v_{asym}$, are first reduced to 5 by using the inclination from the {\em HST} axis ratio.
-We also fix the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential well, to leave only 3 free parameters to vary in the MCMC sampling.
-Due to the faintness of the continuum, there are several galaxies for which we cannot reliably estimate the rotation centre using this method and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location (approach described in \citealt{Harrison2017}).
-Using the continuum to fix the rotation centre is generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter effectively doubles the S/N of the continuum by collapsing over twice the wavelength range.
-\\
-
-The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
-This default line width is selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\simeq3.0$ velocity dispersions and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
+The 6 free parameters of the model; $(xcen, ycen), i, PA_{kin}, rt, v_{asym}$, were first reduced to 5 by using the inclination from the {\em HST} axis ratio.
+We also fixed the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential well, to leave only 3 free parameters to vary in the MCMC sampling.
+Due to the faintness of the continuum, there are several galaxies for which we could not reliably estimate the rotation centre using this method and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location (approach described in \citealt{Harrison2017}).
+Using the continuum to fix the rotation centre was generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter effectively doubles the signal to noise of the continuum by collapsing over twice the wavelength range.
+\\
+
+The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction was determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line was set to follow a uniform distribution with a default width of 50kms$^{-1}$.
+This default line width was selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\simeq3.0$ velocity dispersions, and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
 The reported errors on $\sigma_{int}$ take this assumption into account. \\
 
-The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube is then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
-The velocity and velocity dispersion values are then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
-We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, and seek the combination of parameters which maximises the log-Likelihood function given by Equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
+The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube was then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
+The velocity and velocity dispersion values were then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
+We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, seeking the combination of parameters which maximises the log-Likelihood function given by Equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
 
@@
 
-The MCMC sampling provides a distribution of parameter values around those which give the maximum-likelihood.
-We have confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates have converged around the 50th percentile values.
-The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in Appendix \ref{appsubsec:model_errors}.
-
-Following the construction of a convolved model cube and the measurement of the beam-smeared maps we can extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
+The MCMC sampling provided a distribution of parameter values around those which give the maximum-likelihood.
+We confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates converged around the 50th percentile values.
+The 16th and 84th percentiles of these distributions were used to assess the model uncertainties as described in Appendix \ref{appsubsec:model_errors}.
+
+Following the construction of a convolved model cube and the measurement of the beam-smeared maps we extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
 There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshifts.
 We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
-An overview of these comparison samples is provided in Appendix \ref{app:comparison_samples}, describing also the approach used to compute average parameter values.
+An overview of these comparison samples is provided in Appendix \ref{app:comparison_samples}, which also describes the approach used to compute average parameter values.
 
 \subsubsection{Beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
-The intrinsic velocity, $V_{C}$, is found by reading off from the best-fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\simeq3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
+The intrinsic velocity, $V_{C}$, was found by reading off from the best-fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\simeq3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
 This extraction radius is shown with the vertical red dashed line in the panels of Figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
@@
 The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$ respectively, which is less than at lower redshift (see \cref{subsec:results_rotation_vel} for a discussion).
-In order to determine the beam-smearing correction factor, we also extract the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
+In order to determine the beam-smearing correction factor, we also extracted the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
 The beam-smearing correction factor ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in Appendix \ref{appsubsec:model_errors}.
@@
 This is dependent primarily on the magnitude of the velocity gradient across the parameter maps, where larger velocity gradients result in larger central velocity dispersions.
-The 2D beam-smearing correction map, $\sigma_{BS}$, is taken as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50kms$^{-1}$ i.e.
-$\sigma_{BS} = \sigma_{model} - \sigma_{assumed}$ (where $\sigma_{assumed}$ is fixed at 50kms$^{-1}$ as described in \cref{subsubec:model_cube}).
+The 2D beam-smearing correction map, $\sigma_{BS}$, was taken as the difference between the beam-smeared dispersion produced by the model, and the assumed intrinsic velocity dispersion of 50kms$^{-1}$ i.e.
+$\sigma_{BS} = \sigma_{model} - \sigma_{assumed}$ (where $\sigma_{assumed}$ was fixed at 50kms$^{-1}$ as described in \cref{subsubec:model_cube}).
 The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
-We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.
-
-To measure the $\sigma_{int}$ value for each galaxy in our sample we use Equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the {\it K}-band and 55.4kms$^{-1}$ in the H{\it K}-band).
+We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we did not attempt to fit the velocity dispersions, this is a feature the model could not reproduce.
+
+To measure the $\sigma_{int}$ value for each galaxy in our sample we used Equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian-fits to several skylines (equal to 31.1kms$^{-1}$ in the {\it K}-band and 55.4kms$^{-1}$ in the H{\it K}-band).
 
@@
 
-The median value of this map is taken as the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value.
+The median value of this map is the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value.
 The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
@@
 
-To test the robustness of our beam-smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{1/2}/R_{psf}$, detailed in Johnson et al.
+To test the robustness of our beam-smearing correction approach we also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{1/2}/R_{psf}$, detailed in Johnson et al.
 (in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
-These correction factors are applied to $V_{BS}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
-When following this approach for the isolated field sample, the derived $V_{C}$ values agree with our own corrections to within $\simeq10\%$, and the $\sigma_{int}$ values to within $\simeq5\%$ which is within the errors on these quantities.
-This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\simeq0.9$ KROSS methods \citep{Harrison2017}.
-We also observe that the shape and width of the observed and intrinsic kinematic parameter distributions are equivalent, suggesting that the corrections do not over-extrapolate from the raw numbers.
+These correction factors were applied to $V_{BS}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
+When following this approach, for the isolated field sample, the derived $V_{C}$ values agree with our own corrections to within $\simeq10\%$, and the $\sigma_{int}$ values to within $\simeq5\%$ which is within the errors on these quantities.
+This confirmed that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\simeq0.9$ KROSS methods \citep{Harrison2017}.
+We also observed that the shape and width of the observed and intrinsic kinematic parameter distributions are equivalent, suggesting that the corrections do not over-extrapolate from the raw numbers.
 
@@
 \subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}
-The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
-This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
+The dynamical model parameter $PA_{Kin}$ was compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
+This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 30^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
 Significant misalignment between the two axes can be a signature of galaxy interaction.
@@
 The resolved KDS galaxies at $z\simeq3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
-For the majority of galaxies we are not in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2016}.
+For the majority of galaxies we are not in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2017}.
 Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
-This generally does not give the same answer as simply connecting the velocity extrema, as we have verified by rotating $PA_{Kin}$ in 1$^{\circ}$ increments and choosing the value which maximises the velocity gradient, calling this $PA_{rot}$.
+This generally does not give the same answer as simply connecting the velocity extrema, as we verified by rotating $PA_{Kin}$ in 1$^{\circ}$ increments and choosing the value which maximises the velocity gradient, calling this $PA_{rot}$.
 If the direction of the `zero-velocity strip' across the centre of the velocity maps is not perpendicular to the line connecting the velocity extrema, the $PA_{Kin}$ determined from MCMC will be different to the $PA_{Kin}$ determined from rotation (e.g.
@@
 \subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
-We proceed to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
+We proceeded to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
 This is a simple empirical diagnostic for whether a galaxy is `Rotation-Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion-Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
@@
 \subsubsection{KDS merger candidates}\label{subsubsection:merger_candidates}
-KDS galaxies are classified as mergers when more than one component is identified in the high-resolution imaging.  
-One benefit of studying the {\em HST} photometry in tandem with the kinematics is to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
+The KDS galaxies were classified as mergers when more than one component was identified in the high-resolution imaging.  
+One benefit of studying the {\em HST} photometry in tandem with the kinematics was to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
 These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
-A second benefit is to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
+A second benefit was to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
 can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging (e.g.
@@
 In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
-It is difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e.
+It was difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e.
 clumpy disk galaxies e.g.
 \citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
-Perhaps the most telling diagnostic are two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map.
+Perhaps the most telling diagnostic was the presence of two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map.
 
@@
 
-In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identify signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
-In 8/9 resolved KDS cluster galaxies we identify multiple photometric components, translating into a merger rate of 89\%  (see Table \ref{tab:pointings}).
-The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they are drawn from a higher density environment and these interactions will inevitably have major consequences for the consumption and stripping of gas as well as the morphological and dynamical evolution within these galaxies.
+In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identified signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
+In 8/9 resolved KDS cluster galaxies we identified multiple photometric components, translating into a merger rate of 89\%  (see Table \ref{tab:pointings}).
+The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they were drawn from a higher density environment, and these interactions will inevitably have major consequences for the consumption and stripping of gas as well as the morphological and dynamical evolution within these galaxies.
 The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
-As mentioned above we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
+As mentioned above, we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
 We keep the KDS galaxies without {\em HST} coverage on the basis that we do not identify double components in the galaxy continuum maps. 
@@
 These include the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in \cite{ForsterSchreiber2009} and \cite{Cresci2009}.
-In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotation-dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2017} for a re-analysis of KMOS$^{3D}$ data at z$\simeq1$ using the same criteria).
+In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotation-dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \citealt{Rodrigues2017} for a re-analysis of KMOS$^{3D}$ data at $z\simeq1$ using the same criteria).
 In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification is outlined in their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
 In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in Appendix \ref{subsec:AMAZE}.
-We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
-The morphologically isolated KDS field galaxies are classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
+We used a simple approach (dictated by the signal to noise of the isolated field sample) and calculated rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
+The morphologically isolated KDS field galaxies were classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
 We plot the best-fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion-dominated categories in Figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
@@
 \subsubsection{Summary of the final sample for further analyses}\label{subsubsec:kin_sample_summary}
-In summary, we have analysed 77 typical $z\simeq3.5$ SFGs spanning both cluster and field environments, finding 62 with integrated [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsec:datareduction}).
-This sample is refined to 47 galaxies (61\%) with spatially-resolved [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsection:spaxel_fitting}).
-Due to the unusually high merger-candidate rate of 89\% in the cluster environment (identified by searching the high-resolution {\em HST} imaging for photometric counterparts), we omit the 9 spatially-resolved galaxies in SSA22-P1 from further consideration.
-In the remaining sample of 38 field environment galaxies we identify 6 merger candidates, giving a field galaxy merger rate of 16\%, which constitute the `merger field sample'.
-The remaining 32 galaxies constitute the `isolated field sample', for which we have measured morphological parameters using {\tt GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and Table \ref{tab:phys-props}) and we have derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and Table \ref{tab:kin_props}).
-\\
-
-The isolated field sample is further divided into 13 rotation-dominated galaxies (34\% with respect to full field sample) and 19 dispersion-dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}).
+In summary, we analysed 77 typical $z\simeq3.5$ SFGs spanning both cluster and field environments, finding 62 with integrated [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsec:datareduction}).
+This sample was refined to 47 galaxies (61\%) with spatially-resolved [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsection:spaxel_fitting}).
+Due to the unusually high merger-candidate rate of 89\% in the cluster environment (identified by searching the high-resolution {\em HST} imaging for photometric counterparts), we omitted the 9 spatially-resolved galaxies in SSA22-P1 from further consideration.
+In the remaining sample of 38 field environment galaxies we identified 6 merger candidates, giving a field galaxy merger rate of 16\%, which constitute the `merger field sample'.
+The remaining 32 galaxies constitute the `isolated field sample', for which we measured morphological parameters using {\tt GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and Table \ref{tab:phys-props}) and derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and Table \ref{tab:kin_props}).
+\\
+
+The isolated field sample was further divided into 13 rotation-dominated galaxies (34\% with respect to full field sample) and 19 dispersion-dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}).
 
@@
 
-In the previous sections we have presented our morphological and kinematic analysis for the 77 galaxies covering both cluster and field environments in the KDS survey.
+In the previous sections we presented our morphological and kinematic analysis for the 77 galaxies covering both cluster and field environments in the KDS survey.
 These galaxies are representative of typical SFGs $z\simeq3.5$ as verified by comparing to fits to the galaxy main-sequence at this redshift.
-Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 32 field galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
+Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduced the sample to 32 field galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
 not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
-For these galaxies we have measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion-dominated.
+For these galaxies we measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we used to classify the galaxies as either rotation or dispersion-dominated.
 The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in Appendix \ref{app:kinematics_plots}.
@@
 However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Simons2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
-At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} consistent with the $z\simeq0$ relation.
-\\
-
-We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
-In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
-The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
+At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, and the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} is consistent with the $z\simeq0$ relation.
+\\
+
+We plot the relationship between rotation velocity and stellar mass for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
+In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ star-forming galaxies with $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
+The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a_{z=0.9} = 0.33 \pm 0.11$ and $b_{z=0.9} = 2.12 \pm 0.04$.
 We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
 These $z\simeq0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
-In \cite{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
+In \cite{Reyes2011}, $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
 The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotation-dominated star-forming galaxies between these redshifts.
@@
 The dispersion-dominated KDS galaxies sit clearly separated and below the $z\simeq0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\simeq0.9$ dispersion-dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We plot also the five $z\simeq3$ galaxies from the AMAZE clean sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$.
-
-Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\simeq0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
+We plot also the five galaxies from the AMAZE Clean ($z\simeq3$) sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$.
+
+Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\simeq0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
 Similarly in \cite{Cresci2009} evolution of the normalisation of the stellar mass Tully-Fisher relation is observed at $z\simeq2$ using only robust rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5$.
@@
     \end{subfigure}
-    \caption{{\it Left:} We plot the intrinsic velocity dispersion against stellar mass for the rotation and dispersion-dominated isolated field sample galaxies, along with the AMAZE Clean sample.
+    \caption{{\it Left:} We plot the intrinsic velocity dispersion against stellar mass for the rotation and dispersion-dominated isolated field sample galaxies, along with the AMAZE Clean ($z\simeq3$) sample.
     The $\sigma_{int}$ values are typically distributed between $40-90kms^{-1}$ and show no clear correlation with stellar mass, highlighting the complicated relationship between these two quantities.
@@
 
+In the right panel of Figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
+It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in Appendix \ref{app:comparison_samples}) are directly comparable.
+The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
+\\
+
 In a rotationally supported system, the circular velocity is set by the requirement to support the total mass in the system, i.e.
@@
 Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
-\\
-
-In the right panel of Figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
-It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in Appendix \ref{app:comparison_samples}) are directly comparable.
-The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
-\\
 
@@
 We proceed to consider the cause of the high number of dispersion-dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
-There are also some galaxies in our sample where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g.
+There are also some galaxies in our sample where the observed velocity field has clear rotational structure and reaches flattening (e.g.
 see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}/M_{\odot})=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
@@
 
-In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation-dominated classes, along with the AMAZE Clean sample galaxies in the $\sigma_{int}$ vs.
+In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation-dominated classes, along with the AMAZE Clean ($z\simeq3$) sample galaxies in the $\sigma_{int}$ vs.
 $M_{\star}$ plane.
@@
 
-The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}/M_{\odot})=9.8,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
-The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\simeq1$ for the gas-rich disks observed at high-z e.g.
+The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}/M_{\odot})=9.8,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \citealt{Wisnioski2015}).
+The lower stellar mass tracks suggest a flatter evolution of velocity dispersion with redshift, and indeed the surveys with lower average stellar mass (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher velocity dispersion than the surveys with larger average stellar mass (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\simeq1$ for the gas-rich disks observed at high-z e.g.
 \citealt{ForsterSchreiber2006,Genzel2011,Newman2013}) and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
@@
     \includegraphics[width=0.49\textwidth]{v_over_sigma_versus_mass.png}
-    \caption{The distribution of galaxies in the $V_{C}$/$\sigma_{int}$ vs. $M_{\star}$ plane is shown for the isolated field sample, along with the galaxies in the AMAZE Clean sample.
+    \caption{The distribution of galaxies in the $V_{C}$/$\sigma_{int}$ vs. $M_{\star}$ plane is shown for the isolated field sample, along with the galaxies in the AMAZE Clean ($z\simeq3$) sample.
     We mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies in this panel, finding that more massive galaxies (e.g.
-$log(M_{\star}/M_{\odot}) > 9.7$) are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.}
+$log(M_{\star}/M_{\odot}) > 9.5$) are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.}
     \label{fig:v_sig_and_v}
@@
     \caption{{\it Left:} $V_{C}/\sigma_{int}$ is plotted against redshift for the comparison samples spanning $0 < z < 4$.
-    The filled symbols show the sample mean values, with the KDS mean at $z\simeq3.5$ plotted with the red circle, with black errorbars representing the statistical error on the mean computed using bootstrap re-sampling as described in the text.
-    The sample medians and statistical errors are plotted with the coloured and grey horizontal bars, falling in each case below the mean, suggesting that large individual $V_{C}/\sigma_{int}$ measurements may bias the sample mean high.
-    We also plot the 16th and 84th percentiles of the distribution of individual $V_{C}/\sigma_{int}$ measurements as shaded regions to give an indication of the range of values measured in each survey.
     We see a clear decline in the mean $V_{C}/\sigma_{int}$ values with redshift, but with wide ranges in the individual measurements.
@@
 
-In Figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean sample for reference.
+In Figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean ($z\simeq3$) sample for reference.
 In the local universe, disky, SFGs are observed to have $V_{C}/\sigma_{int}$ values in excess of 10 (i.e.
@@
 
-The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation-dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}/M_{\odot}) > 9.7$ which are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.
+The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation-dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}/M_{\odot}) > 9.5$ which are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.
 The Rotation-Dominated Fraction (RDF), calculated with respect to the full field sample of 38 galaxies, is 0.34$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
@@
 Scatter above and below the RDF $\propto z^{-0.2}$ evolution line may be attributed in part to the different mean stellar masses of the surveys, with those that have larger stellar masses tending to scatter above this line.
-This draws again from the idea that higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the sample rotation-dominated fraction higher (see \cref{sec:discussion}).
+This draws again from the idea that higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the rotation-dominated fraction higher (see \cref{sec:discussion}).
 In summary, the rotation-dominated galaxies in the isolated field sample appear to conform with a redshift invariant $V_{C}$ - $M_{\star}$ relation.
@@
 
+Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation-dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
+The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion-dominated galaxies ($66\%$ of the sample) and probable pressure support from turbulent motions \citep[e.g.][]{Burkert2010}.
+This increased number of dispersion-dominated galaxies in comparison to low and intermediate redshifts appears to be driven by high velocity dispersions at $z\simeq3.5$.
+In this section we discuss possible physical origins for the elevated random motions traced by $\sigma_{int}$ and their impact on the galactic dynamics.
+
+\subsection{The origin and impact of increased velocity dispersions at high redshift}\label{discussion_increase_in_sigma}
+
 \begin{figure*}
@@
     \end{subfigure}
-    \caption{{\it Left:} We plot the directly comparable $\sigma_{int}$ values (see filled symbols) for the surveys spanning $z=0-3$ as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 9.8$ (the median of the isolated field sample masses).
+    \caption{{\it Left:} We plot the directly comparable $\sigma_{int}$ values (see filled symbols) for the surveys spanning $z=0-3$ as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample).
     The dark grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
@@
 
-Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation-dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
-The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion-dominated galaxies ($66\%$ of the sample) and probable pressure support from turbulent motions \citep[e.g.][]{Burkert2010} partially supporting gravity.
-This increased number of dispersion-dominated galaxies in comparison to low and intermediate redshifts appears to be driven by high velocity dispersions at $z\simeq3.5$.
-In this section we discuss possible physical origins for the elevated random motions traced by $\sigma_{int}$ and their impact on the galactic dynamics.
-
-\subsection{The origin and impact of increased velocity dispersions at high redshift}\label{discussion_increase_in_sigma}
 Previous studies have claimed that the elevated velocity dispersions observed at high redshift are a consequence of both internal and external processes.
@@
 In this model the velocity dispersions increase as a result of increasing gas fractions within galaxies, with a steeper increase from $z\simeq0$ for galaxies at higher stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
-At higher redshift these lines converge, suggesting that the predictions for the gas fraction become independent of stellar mass in this regime.
-The value $V_{C}=125kms^{-1}$ is chosen as a suitable average for the rotational velocity values reported in the surveys as shown in the right panel of Figure \ref{fig:tf_relation}.
-In general the surveys with higher stellar mass have lower velocity dispersions, in support of the model hypothesis. \\
+At higher redshift, these lines converge, suggesting that the predictions for the gas fraction become independent of stellar mass in this regime.
+The value $V_{C}=125kms^{-1}$ is chosen as a suitable average of the rotational velocity values reported in the surveys as shown in the right panel of Figure \ref{fig:tf_relation}.
+In general, the surveys with higher stellar mass have lower velocity dispersions, in support of the model hypothesis. \\
 
@@
 This is done by computing the difference between the model predicted $\sigma_{int}$ value at the stellar mass of each comparison survey and at the reference mass for the appropriate redshift and shifting the reported $\sigma_{int}$ by this value.
-We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 9.8$ (the median of the isolated field sample masses) (the mean mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}) and we only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
+We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}) and only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
 In both panels the dark grey shaded regions encompass the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
@@
 The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Law2012b,Law2012c,Wisnioski2015}.
-Rotation-dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions as shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}, constituting only $\simeq1/3$ of the isolated field sample at $z\simeq3.5$.
+Rotation-dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions (shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}), constituting only $\simeq1/3$ of the isolated field sample at $z\simeq3.5$.
 This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale length \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
@@
 \section{CONCLUSIONS}\label{sec:conclusion}
-We have presented new measurements of 77 main-sequence star forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
+We have presented new dynamical measurements of 32 typical star forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
 These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.0 < log(M_{\star}/M_{\odot})< 10.5$ typical main-sequence galaxies at these redshifts.
@@
     The dispersion-dominated galaxies scatter below the trend, with the same slope as the rotation-dominated galaxies.
-    \item When considering the rotation-dominated galaxies alone the mean and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}kms^{-1}$ respectively, which are lower than expected from a simple virial theorem calculation using the mean mass and half-light radius of the sample.
+    \item When considering the rotation-dominated galaxies alone the mean and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}kms^{-1}$ respectively, which are roughly equivalent to a simple lower limit virial theorem calculation using the mean mass and half-light radius of the sample.
     This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in the system \citep[e.g.][]{Burkert2010}.  
@@
 \subsection{AMAZE ($\bmath{z\simeq3.0}$)}\label{subsec:AMAZE}
-The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}/M_{\odot})=9.9$ at z$\simeq3$, closest in redshift to the KDS galaxies.
+The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}/M_{\odot})=9.9$ at $z\simeq3$, closest in redshift to the KDS galaxies.
 In this study, rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ as the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map (which also takes into account instrumental resolution and beam-smearing; see their Equation 8).
@@
 \caption{The distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
-The AMAZE Clean sample galaxies (see \protect\cref{subsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
+The AMAZE Clean ($z\simeq3$) sample galaxies (see \protect\cref{subsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
 There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement.
@@
 The $V_{C}$ = $\sigma_{int}$ line roughly bisects the KDS sample, and separates the dispersion-dominated and rotation-dominated galaxies by definition.
-The isolated field sample galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is good agreement between the KDS and AMAZE Clean samples.
+The isolated field sample galaxies are clustered around a relatively tight region in both $V_{C}$ and $\sigma_{int}$ and there is good agreement between the KDS and AMAZE Clean ($z\simeq3$) samples.
 The galaxies in the AMAZE Unconstrained sample generally have much larger $V_{C}$ values despite occupying a similar stellar mass range to our isolated field sample, with this being a consequence of large model extrapolations beyond the observed data.
@@
     \caption{We plot the kinematic grids for the 13 isolated field sample galaxies classified as rotation-dominated.
-    For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
+    For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian-fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
     On the bottom row we plot the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
@@
     In this case we plot only fits to the data in the velocity extraction plot with the blue line, rather than attempting the full beam-smearing analysis.
-    Several of the galaxies here mimic rotation from a purely kinematic perspective, but have two or more {\em HST} components and an accompanying double peak in the object spectrum at the object centre, leading to large velocity dispersions when single gaussian fits are attempted.}
+    Several of the galaxies here mimic rotation from a purely kinematic perspective, but have two or more {\em HST} components and an accompanying double peak in the object spectrum at the object centre, leading to large velocity dispersions when single gaussian-fits are attempted.}
     \label{fig:merger_galaxies}

### 2017-04-03 paper.tex
UP TO SECTION 4

@@
 The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
-Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$).
+Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$, {\it HK}-band $R\simeq2000$).
 \subsubsection{Observations}\label{subsubsec:Obs}
@@
 In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\simeq0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the {\it K}-band seeing ranged between $\simeq0.55-0.65^{\prime\prime}$.
-We observed 19-21 targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
+We observed 17-21 $z\simeq3.5$ targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
 \\
@@
 
-The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det}$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det} = 62/77$ $(81\%)$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
 
@@
 There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we also discuss the approach followed to recover the morphological parameters for these galaxies.
-We do not expect that this small number of galaxies without {\em HST} imaging will impact the bulk dynamical properties of the KDS sample.
+The interpretation of the sample as a whole is not affected by the small number of galaxies without {\em HST} imaging.
 
@@
 \label{tab:phys-props}
-\begin{tabular}{lllllllllll}
+\begin{tabular}{llllllllll}
 
  \hline
-ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
+ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
  \hline
-b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.84 & 97 & 0.36        & 72        & 9     & 1.57      \\
-b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.76 & 172 & 0.28        & 78        & 146   & 0.52      \\
-bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.75  & 14 & 0.50         & 61        & 146   & 1.91      \\
-bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.1 & 10 & 0.44        & 66        & 168   & 1.83      \\
-bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.5 & 20 & 0.50         & 61        & 67    & 1.59      \\
-bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.7  & 33 & 0.80         & 37        & 148   & 1.24      \\
-bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 9.7 & 92 & 0.31        & 76        & 63    & 1.61      \\
-bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 9.9  & 6  & 0.65        & 50        & 49    & 0.87      \\
-lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.5  & 5  & 0.64        & 52        & 1     & 1.28      \\
-lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.6  & 5  & 0.53        & 60        & 34    & 1.27      \\
-lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 5  & 0.30         & 76        & 78    & 1.18      \\
-lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.0  & 18  & 0.79         & 38        & 66    & 0.95      \\
-lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 9.9 & 64 & 0.60         & 54        & 40    & 1.88      \\
-lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 9.9 & 5  & 0.58        & 56        & 137   & 0.92      \\
-lbg\_91         & 03:32:27.202 & $-$27:41:51.756 & 3.170       & 24.65  & 9.8   & 6  & 0.58        & 56        & 79    & 0.89 \\
-lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 9.9 & 8  & 0.22        & 84        & 81    & 1.16      \\
-lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.3  & 54 & 0.56        & 57        & 128   & 1.72      \\
-lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7  & 8  & 0.60         & 54        & 119   & 1.98      \\
-lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7  & 18 & 0.74        & 42        & 80    & 0.64      \\
-lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.6  & 6  & 0.79         & 38        & 43    & 0.46      \\
-lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.6  & 56 & 0.52        & 60        & 15    & 0.87      \\
-lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.0  & 13  & 0.56         & 57        & 50    & 0.78      \\
-$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.5 & 14 & 0.57         & 57        & -    & 2.52      \\
-n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7  & 3            & 0.75        & 42        & 84    & 1.06      \\
-n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.8  & 4            & 0.71        & 46        & 94    & 0.56      \\
-lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.2  & 4            & 0.85        & 32        & 27    & 0.46      \\
-$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.4  & 7            & 0.57         & 57        & -    & 2.18      \\
-s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.7  & 60            & 0.39        & 70        & 125   & 1.78      \\
-s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.5  & 45            & 0.57        & 57        & 76    & 1.59      \\
-$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.2 & 9            & 0.57         & 57        & -    & 3.30      \\
-s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1 & 5            & 0.65        & 50        & 60   & 0.5       \\
-$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 8.6  & 10            & 0.57         & 57        & -    & 1.39
+b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.84 & 0.36        & 72        & 9     & 1.57      \\
+b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.76  & 0.28        & 78        & 146   & 0.52      \\
+bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.75 & 0.50         & 61        & 146   & 1.91      \\
+bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.1  & 0.44        & 66        & 168   & 1.83      \\
+bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.5 & 0.50         & 61        & 67    & 1.59      \\
+bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.7  & 0.80         & 37        & 148   & 1.24      \\
+bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 9.7  & 0.31        & 76        & 63    & 1.61      \\
+bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 9.9   & 0.65        & 50        & 49    & 0.87      \\
+lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.5  & 0.64        & 52        & 1     & 1.28      \\
+lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.6   & 0.53        & 60        & 34    & 1.27      \\
+lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 0.30         & 76        & 78    & 1.18      \\
+lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.0  & 0.79         & 38        & 66    & 0.95      \\
+lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 9.9    & 0.60         & 54        & 40    & 1.88      \\
+lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 9.9   & 0.58        & 56        & 137   & 0.92      \\
+lbg\_91         & 03:32:27.202 & $-$27:41:51.756 & 3.170       & 24.65  & 9.8   & 0.58        & 56        & 79    & 0.89 \\
+lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 9.9   & 0.22        & 84        & 81    & 1.16      \\
+lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.3    & 0.56        & 57        & 128   & 1.72      \\
+lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7   & 0.60         & 54        & 119   & 1.98      \\
+lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7   & 0.74        & 42        & 80    & 0.64      \\
+lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.6 & 0.79         & 38        & 43    & 0.46      \\
+lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.6    & 0.52        & 60        & 15    & 0.87      \\
+lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.0  & 0.56         & 57        & 50    & 0.78      \\
+$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.5   & 0.57         & 57        & 156    & 2.52      \\
+n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7                       & 0.75        & 42        & 84    & 1.06      \\
+n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.8                & 0.71        & 46        & 94    & 0.56      \\
+lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.2             & 0.85        & 32        & 27    & 0.46      \\
+$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.4            & 0.57         & 57        & 87    & 2.18      \\
+s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.7                       & 0.39        & 70        & 125   & 1.78      \\
+s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.5                   & 0.57        & 57        & 76    & 1.59      \\
+$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.2                & 0.57         & 57        & 60    & 3.30      \\
+s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1                  & 0.65        & 50        & 60   & 0.50       \\
+$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 8.6             & 0.57         & 57        & 9    & 1.39
 
@@
       \item $^{d}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
-      \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ unconstrained; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
+      \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ set to $PA_{kin}$ value; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
     \end{tablenotes}
@@
 For the galaxies without {\em HST} coverage the inclination angle was set to the KDS sample median of 57.0$^{\circ}$ and we used the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
-This corresponds to a factor $\simeq1.3$ contribution to the uncertainty in the derived velocities for these galaxies.
+This adds an additional factor of $\simeq1.3$ to the uncertainty in the derived velocities for these galaxies.
 
@@
 The criteria were then re-examined, and if satisfied, the Monte-Carlo procedure was carried out. 
-If the binned spaxels fail the criteria, one final iteration was carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$, roughly equivalent to the size of the seeing disk.
+If the binned spaxels fail the criteria, one final iteration was carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$, roughly equivalent to the size of the seeing disk (see Table \ref{tab:pointings}).
 If after the widest binning the criteria weren't satisfied, no value was assigned to that spaxel in the extracted maps. \\
 
-The process was automated and applied to each of the 62 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
+The process was automated and applied to each of the 62/77 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
 Following the fitting procedure the galaxies were clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map was equivalent to or greater than the seeing disk.
 For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, was added to Table \ref{tab:pointings}.
-We find that 47 (76\%) of the detected KDS galaxies across both the field and cluster environments were spatially-resolved and showed clear velocity structure.
-The 15 galaxies which were not spatially-resolved were dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
+We find that 47/77 (76\%) of the detected KDS galaxies across both the field (38) and cluster (9) environments were spatially-resolved and showed clear velocity structure.
+The 15/77 galaxies which were not spatially-resolved were dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
 The physical properties of all spatially-resolved galaxies in both GOODS-S and SSA22 are listed in Table \ref{tab:phys-props}. \\
@@
 The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
-6/38 of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
+6/38 (16\%) of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
 We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
 The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
-The 32/38 morphologically isolated field galaxies are referred to as the `isolated field sample'.
+The 32/38 morphologically isolated field galaxies which are spatially resolved are referred to as the `isolated field sample' throughout the remainder of the paper.
 
@@
     \caption{We plot the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
-    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated, dispersion-dominated and merger categories.
+    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated (13/38), dispersion-dominated (19/38) and merger categories (6/38).
     For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map.
@@
 This central wavelength was then shifted using the velocity derived at each spaxel from the velocity field model described below.  
-Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas was modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by Equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
+Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2017} the velocity field of the gas was modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by Equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:
 
@@
 The velocity decreases with a factor of cos($\phi$) from the kinematic position axis, where $\phi$ is the angle measured clockwise from the axis, which points to the direction of the positive side of the velocity field.
-The 6 free parameters of the model; $(xcen, ycen), i, PA_{kin}, rt, v_{asym}$, were first reduced to 5 by using the inclination from the {\em HST} axis ratio.
+The 6 free parameters of the model; $(xcen, ycen), i, PA_{kin}, r_{t}, v_{asym}$, were first reduced to 5 by using the inclination from the {\em HST} axis ratio.
 We also fixed the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential well, to leave only 3 free parameters to vary in the MCMC sampling.
 Due to the faintness of the continuum, there are several galaxies for which we could not reliably estimate the rotation centre using this method and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location (approach described in \citealt{Harrison2017}).
-Using the continuum to fix the rotation centre was generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter effectively doubles the signal to noise of the continuum by collapsing over twice the wavelength range.
+Using the continuum to fix the rotation centre was generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter increases the signal to noise of the continuum by collapsing over twice the wavelength range.
 \\
@@
 We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
-An overview of these comparison samples is provided in Appendix \ref{app:comparison_samples}, which also describes the approach used to compute average parameter values.
+We have re-evaluated the means and medians of the kinematic properties in these samples in order to make fair and reliable comparisons.
+An overview of the comparison samples is provided in Appendix \ref{app:comparison_samples}, which also describes the approach used to compute average parameter values.
 
@@
 
-The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$ respectively, which is less than at lower redshift (see \cref{subsec:results_rotation_vel} for a discussion).
+The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$ respectively, which is less than observed for lower redshift typical star-forming galaxies (see \cref{subsec:results_rotation_vel} for a discussion).
 In order to determine the beam-smearing correction factor, we also extracted the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
-The beam-smearing correction factor ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in Appendix \ref{appsubsec:model_errors}.
-\\
-
-In 13 of the isolated field sample galaxies, the intrinsic $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, however only 2 galaxies require extrapolation > 0.4$^{\prime\prime}$ (i.e.
+The magnitude of the beam-smearing correction ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in Appendix \ref{appsubsec:model_errors}.
+\\
+
+In 13/38 of the isolated field sample galaxies, the intrinsic $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, however only 2 galaxies require extrapolation > 0.4$^{\prime\prime}$ (i.e.
 2 KMOS pixels) with a mean extrapolation of 0.17$^{\prime\prime}$.
@@
 This is dependent primarily on the magnitude of the velocity gradient across the parameter maps, where larger velocity gradients result in larger central velocity dispersions.
-The 2D beam-smearing correction map, $\sigma_{BS}$, was taken as the difference between the beam-smeared dispersion produced by the model, and the assumed intrinsic velocity dispersion of 50kms$^{-1}$ i.e.
-$\sigma_{BS} = \sigma_{model} - \sigma_{assumed}$ (where $\sigma_{assumed}$ was fixed at 50kms$^{-1}$ as described in \cref{subsubec:model_cube}).
-The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
+
+By comparing the best-fitting simulated datacube with the assumption for the isotropic velocity dispersion we recovered the beam-smearing correction for each galaxy.
+The 2D beam-smearing correction map, $\sigma_{BS}$, was computed on a spaxel-by-spaxel basis as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50kms$^{-1}$ i.e.
+$\sigma_{BS,i} = \sigma_{simulated,i} - \sigma_{assumed,i}$ (where $\sigma_{assumed,i}$ was fixed at 50kms$^{-1}$ as described in \cref{subsubec:model_cube} and $\sigma_{simulated,i}$ is the simulated velocity dispersion recovered under this assumption).
+The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS,i}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
 We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we did not attempt to fit the velocity dispersions, this is a feature the model could not reproduce.
 
-To measure the $\sigma_{int}$ value for each galaxy in our sample we used Equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian-fits to several skylines (equal to 31.1kms$^{-1}$ in the {\it K}-band and 55.4kms$^{-1}$ in the H{\it K}-band).
+To measure the $\sigma_{int}$ value for each galaxy in our sample we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian-fits to several skylines (equal to 31.1kms$^{-1}$ in the {\it K}-band and 55.4kms$^{-1}$ in the {\it HK}-band).
 
 \begin{equation}\label{eq:owen_sigma}
-\sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{BS}^{2}\right) - \sigma_{inst}^{2}}
+\sigma_{cor,i} = \sqrt{\left(\sigma_{obs,i} - \sigma_{BS,i}\right)^{2} - \sigma_{inst,i}^{2}}
 \end{equation} \\
 
-The median value of this map is the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value.
-The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
-The beam-smearing correction factor ($\sigma_{int}/\sigma_{obs}$) has a mean and median value of 0.77 and 0.79 respectively for the isolated field sample. \\
+The median of the $\sigma_{cor,i}$ map is taken as the $\sigma_{int}$ value for each galaxy and the median of the observed map is the $\sigma_{obs}$ value (see Table \ref{tab:kin_props}).
+The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than for typical star-forming galaxies at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
+The magnitude of the beam-smearing correction ($\sigma_{int}/\sigma_{obs}$) has a mean and median value of 0.77 and 0.79 respectively for the isolated field sample. \\
 
@@
 If the direction of the `zero-velocity strip' across the centre of the velocity maps is not perpendicular to the line connecting the velocity extrema, the $PA_{Kin}$ determined from MCMC will be different to the $PA_{Kin}$ determined from rotation (e.g.
-GOODS-S galaxy bs006541).
-As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ makes only a small difference to the final $V_{C}$ values, a difference which does not affect the outcomes of this work.
+GOODS-S galaxy bs006541 in Appendix Figure \ref{fig:dispersion_dominated_galaxies}).
+As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ (which differs typically by only a few degrees) makes only a small difference to the final $V_{C}$ values, with the errors dominated by measurement uncertainties and model assumptions.
 
@@
 \begin{threeparttable}
-\caption{We present here the dynamical properties for the KDS isolated field sample galaxies.
+\caption{The dynamical properties for the KDS isolated field sample galaxies.
 The observed properties are measured directly from the extracted two-dimensional maps, whereas $V_{C}$ and $\sigma_{int}$ have been corrected for the effects of beam-smearing as described throughout the text.
@@
 
-The isolated field sample was further divided into 13 rotation-dominated galaxies (34\% with respect to full field sample) and 19 dispersion-dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}).
+The isolated field sample was further divided into 13/38 rotation-dominated galaxies (34\% with respect to full field sample) and 19/38 dispersion-dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}), with the remaining 6/38 (16\%) classified as mergers.
 
@@
 These galaxies are representative of typical SFGs $z\simeq3.5$ as verified by comparing to fits to the galaxy main-sequence at this redshift.
-Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduced the sample to 32 field galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
+Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we first reduced the sample to 38 spatially resolved field environment galaxies and then to 32 isolated field sample galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
 not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
 For these galaxies we measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we used to classify the galaxies as either rotation or dispersion-dominated.
-The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in Appendix \ref{app:kinematics_plots}.
-
-Throughout the following sections we analyse the derived kinematic parameters for these 32 galaxies, referred to as the `isolated field sample', placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in Appendix \ref{app:comparison_samples}.
+The morphological and kinematic grids for these 32/38 isolated field sample galaxies and the 6/38 merger candidates are plotted in Appendix \ref{app:kinematics_plots}.
+
+Throughout the following sections we analyse the derived kinematic parameters of the isolated field sample, placing the galaxies in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in Appendix \ref{app:comparison_samples}.
 In Appendix \ref{app:comparison_samples} we also describe the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.

### 2017-04-04 paper.tex
preliminary finish of Chris suggestions

@@
 \usepackage{enumitem}
+\usepackage{amssymb}% http://ctan.org/pkg/amssymb
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\usepackage{enumitem}
 
@@
 \newcommand\tab[1][1cm]{\hspace*{#1}}
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 
@@
 O. J. Turner,$^{1,2,\thanks{E-mail: ojamesturner@icloud.com (OJT)}}$
-M. Cirasuolo,$^{1,2}$
+M. Cirasuolo,$^{2,1}$
 C. M. Harrison,$^{2,3}$
@@
 
-There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
+There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: 
+\begin{enumerate}[label=(\roman*),align=left]
 \item What are the dynamical properties of main-sequence galaxies at this early stage in their lifetimes?
-\item What is the connection between the gas-phase metallicity and  kinematics, particularly in terms of inflows and outflows of material? \end{enumerate}
-
-This paper focuses on the third question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
+\item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
+\item What is the connection between the gas-phase metallicity and  kinematics, particularly in terms of inflows and outflows of material?
+\end{enumerate}
+
+This paper focuses on the first question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
 \\
@@
 From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal to noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
-To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a previous spectroscopic detection (see details below).
-Predominantly, the galaxies were originally selected for spectroscopic follow-up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
-However, a subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
+To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a wealth of imaging and spectroscopic data.
+Most of the galaxies for the KMOS observations had a confirmed spectroscopic redshift (see below).
+A subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
+In each pointing, few sources had no spectroscopic redshift and were selected on the basis of their photometric redshift.
 We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift (see Figure \ref{fig:main_sequence}).
@@
 
-Our data for the 77 KDS targets were observed using KMOS \citep{Sharples2013}, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
+Our data for the 77 KDS targets were observed using KMOS \citep{Sharples2013}, which is a second generation IFS mounted at the Nasmyth focus of UT1 at the VLT.
 The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
-The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
+The light from a set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
 Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$, {\it HK}-band $R\simeq2000$).
@@
 
-To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, facilitating both dynamical and chemical abundance measurements.
+To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, allowing both dynamical and chemical abundance measurements.
 The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously.
@@
 We monitored the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged {\it K}-band seeing rose above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
-The PSF was determined from fitting the {\it K}-band collapsed, stacked standard-star cube in each pointing with an elliptical gaussian, with the values reported in Table \ref{tab:pointings}.
+The PSF was determined by fitting the collapsed {\it K}-band image of the stacked control stars in each pointing with an elliptical gaussian, with the values reported in Table \ref{tab:pointings}.
 The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack.
@@
 
-To measure $R_{1/2}$ for the galaxies without {\em HST} coverage we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
+To measure $R_{1/2}$ for the 4 galaxies without {\em HST} coverage we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
 We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening.
@@
 
-\begin{enumerate}[label=(\roman*)] \item The uncertainties on any of the parameters of the gaussian-fit as returned by {\tt LMFIT} must not exceed 30\%
+\begin{enumerate}[label=(\roman*),align=left]
+\item The uncertainties on any of the parameters of the gaussian-fit as returned by {\tt LMFIT} must not exceed 30\%
 \item $\frac{S}{N_{m}} > 3$
@@
 The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
-6/38 (16\%) of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
+6/38 (16\%) of the resolved galaxies across the 3 field environment pointings and almost all (8/9) of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
 We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
@@
 Throughout the following sections we analyse the derived kinematic parameters of the isolated field sample, placing the galaxies in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in Appendix \ref{app:comparison_samples}.
-In Appendix \ref{app:comparison_samples} we also describe the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.
+In Appendix \ref{app:comparison_samples} we describe our careful assessment of lower redshift samples from the literature, using tabulated data where possible to re-compute mean and median $V_{C}$ and $\sigma_{int}$ values.
+These fair comparisons help to disentangle true evolution in the kinematic properties of typical star-forming galaxies from systematic effects originating in disparate measurement techniques or galaxy selection criteria.
 During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that they trace the average properties of typical star-forming galaxies at their respective mean redshifts.
@@
     {\it Right:} The mean, median and distributions of the comparison sample $V_{C}$ measurements are plotted against redshift.
-    The symbol positions with black errorbars (some not visible) show the mean values and the horizontal filled and grey bars show the median values and associated errors.
-    The mean mass of each survey is listed beside the survey name.
+    The symbol positions with black errorbars (some not visible) show the mean values and the horizontal filled and grey bars show the median values and associated errors, and the mean mass of each survey (in units of log($M_{\star}/M_{\odot}$)) is listed beside the survey name.
+    Note that the median errors for the AMAZE Clean sample are shaded orange to avoid confusion with the full sample.
     The $V_{C}$ distributions in each of the individual studies are wide, reflecting the galaxy diversity within each sample.
@@
 
-Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
-High redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
-Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
-Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
-However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Simons2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
-At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, and the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} is consistent with the $z\simeq0$ relation.
-\\
-
 We plot the relationship between rotation velocity and stellar mass for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
@@
 The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotation-dominated star-forming galaxies between these redshifts.
-\\
 
@@
 The dispersion-dominated KDS galaxies sit clearly separated and below the $z\simeq0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\simeq0.9$ dispersion-dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We plot also the five galaxies from the AMAZE Clean ($z\simeq3$) sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$.
+We plot also the five galaxies from the AMAZE Clean ($z\simeq3$) sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$. \\
+
+Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
+High redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
+Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
+Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
+However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Simons2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
+At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, and the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} is consistent with the $z\simeq0$ relation.
+\\
 
@@
 
-After including data from the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\simeq0.1$ and $z\simeq3.5$.
-However as we will show in \cref{subsec:rdf_v_over_sigma} the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.
+With the KDS, we have added the largest sample of galaxies observed with integral-field spectroscopy at $z>3$, and with our simple $V_{C}/\sigma_{int} > 1$ cut we conclude that the stellar mass Tully-Fisher relation defined for rotation-dominated star-forming galaxies appears to show no evolution between $z\simeq0.1$ and $z\simeq3.5$.
+However, as we will show in \cref{subsec:rdf_v_over_sigma}, the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.
+We also explore this in the context of the mean rotation velocities of the comparison samples throughout the following subsection.
 
@@
 
-In the right panel of Figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
+The right panel of Figure \ref{fig:tf_relation} indicates that the $V_{C}$ distributions for the comparison and KDS isolated field samples are wide, reflecting the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
+The isolated field sample mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$.
+However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}kms^{-1}$ respectively, suggesting that averaging over a sample containing a large number of dispersion dominated galaxies is bringing the averages down.
+
 It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in Appendix \ref{app:comparison_samples}) are directly comparable.
 The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
-\\
+Despite the wide distributions, the comparison samples generally have higher mean rotation velocities. \\
 
@@
 Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
-
-The isolated field sample mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 95kms^{-1}$ lower limit.
-However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}kms^{-1}$ respectively, much closer to the $\left<V_{C}\right> = 95kms^{-1}$ lower limit.
-This implies that the observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
+This value is above the mean and median values of the isolated field sample, but comparable to the mean and median of the rotation dominated galaxies, suggesting that rotation in these systems could support at most the stellar mass of the galaxy.
+
+As mentioned above, the observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
 This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion-dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
-However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contribute to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
+However, it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contribute to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
 This topic is discussed further throughout \cref{sec:discussion}. \\
@@
 In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
-The values increase sharply from $\sigma_{int}\simeq10-20kms^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60kms^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90kms^{-1}$ at $z\simeq3$.
-
-In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR.
-Using observed constraints for these properties from \cite{Tacconi2013} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} Figures 10 and 11).
-The relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
-In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.
-\\
-
-The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}/M_{\odot})=9.8,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \citealt{Wisnioski2015}).
-The lower stellar mass tracks suggest a flatter evolution of velocity dispersion with redshift, and indeed the surveys with lower average stellar mass (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher velocity dispersion than the surveys with larger average stellar mass (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\simeq1$ for the gas-rich disks observed at high-z e.g.
-\citealt{ForsterSchreiber2006,Genzel2011,Newman2013}) and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
-The tracks plotted in Figure \ref{fig:sigma_and_v_sigma_w_redshift} suggest the shape of the $\sigma_{int}$ evolution in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main-sequence galaxies between $z=3-3.8$.
+The values increase sharply from $\sigma_{int}\simeq10-20kms^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60kms^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90kms^{-1}$ at $z\simeq3$, but with a wide range of values observed at each redshift.
+There appears to be a trend for the surveys with lower average stellar mass (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) to have higher velocity dispersions than the surveys with larger average stellar mass (GHASP, KMOS$^{3D}$, SINS).
+
+The increase of velocity dispersion within typical typical star-forming galaxies with redshift appears to follow the same scaling relation as the increase of gas fractions, as inspired by the model described in \cite{Wisnioski2015} and discussed in \cref{discussion_increase_in_sigma}.
+The gas fraction is a function of both stellar mass and redshift and so we plot tracks in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} for three different mass values which roughly encompass the average masses of the comparison samples, $log(M_{\star}/M_{\odot})=9.8,10.3,10.6$.
+The tracks are each scaled with the same coefficient, which is chosen so that the lowest mass track, equivalent to the isolated field sample mean mass, coincides with the KDS datapoint at $z=3.5$.
+As the data suggest, the lower mass tracks suggest a flatter evolution of velocity dispersion with redshift, with convergence at high redshift.  
+The redshift and mass dependence of these tracks is discussed in \cite{Wisnioski2015} and in more detail throughout \cref{discussion_increase_in_sigma}, where we also discuss possible physical explanations for the increase in velocity dispersions with redshift.
+\\
+
+These new data from the KDS sustain the observation that velocity dispersion is increasing with redshift and provide strong constraints on the internal dynamics of typical star-forming galaxies between $z=3-3.8$.
+When these results are presented in combination with data from the literature in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}, it appears that the stellar mass of galaxies may play a role in mediating the velocity dispersion values (see \cref{discussion_increase_in_sigma}).
 
@@
 In the left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation-dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in Appendix \ref{app:comparison_samples}.
+In each sample, the rotation dominated fraction is computed as the fraction of galaxies with $V_{C}/\sigma_{int} > 1$, which, given the varying data quality across the comparison samples, is a simple and fair way to study the redshift evolution of this quantity.
 The filled symbols and black errorbars in the left panel represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
@@
     \end{subfigure}
-    \caption{{\it Left:} We plot the directly comparable $\sigma_{int}$ values (see filled symbols) for the surveys spanning $z=0-3$ as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample).
-    The dark grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
-    The light grey region encompasses model predictions between `minimum' values with $Q_{crit} = 0.68$,$V_{C}=100kms^{-1}$ and `maximum' values with $Q_{crit} = 0.68$,$V_{C}=150kms^{-1}$.
+    \caption{{\it Left:} We plot the $\sigma_{int}$ values for the comparison samples as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample).
+    The grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 70-200kms^{-1}$ respectively (corresponding roughly to the velocity range spanned by galaxies in the comparison samples).
     The shifted points are in line with the scenario whereby the sample averaged velocity dispersions increase with redshift as a result of increasing average gas fractions. 
@@
 
-\cite{Genzel2011} show that for dispersion-dominated galaxies, the scales susceptible to gravitational collapse are of order the galactic half-light radius. 
+\cite{Genzel2011} show that for dispersion-dominated galaxies, the scales susceptible to gravitational collapse are of the order of the galactic half-light radius. 
 Systems such as these form highly unstable and roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009,Genzel2011}.
@@
 
-In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the equilibrium model prescription for the evolution of velocity dispersion with redshift described in section 5.2 of \cite{Wisnioski2015}, using the updated depletion time scaling relation from \cite{Tacconi2017} (i.e.
+In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties gas fraction, $f_{gas}$, gas depletion timescale, $t_{depl}$, and specific star-formation rate, sSFR.
+The function describing the evolution of the velocity dispersion is shown below in Equation \ref{eq:sigma_increase}, where $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964}, and a is a dimensionless parameter depending on the assumed distribution of gas and gravitational potential \cite{ForsterSchreiber2006}.
+
+\begin{equation}\label{eq:sigma_increase}
+    \sigma(z,M_{\star}) = V_{C}f_{gas}(z,M_{\star})Q_{crit}/a
+\end{equation}
+
+The gas fraction is a function of gas depletion timescale, with an assumed redshift dependence, and specific star-formation rate, with an assumed mass and redshift dependence (see \citealt{Wisnioski2015} Equations 3-6).
+Using observed constraints for these properties from \cite{Tacconi2013} and \cite{Whitaker2014} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \citealt{Wisnioski2015} Figures 10 and 11).
+
+This relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
+In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.
+
+In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot Equation \ref{eq:sigma_increase} for different input mass values (roughly spanning the mass range of the comparison samples), using the updated depletion time scaling relation from \cite{Tacconi2017} (i.e.
 $t_{depl} \propto (1 + z)^{-0.57}$).
-The function describing the evolution of the velocity dispersion is shown below in Equation \ref{eq:sigma_increase}, where the gas fraction is a function of redshift and stellar mass, $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964} ($Q_{crit} = 1.0$ for a quasi-stable thin disk e.g.
-\citealt{ForsterSchreiber2006,Burkert2010,Genzel2011,Wisnioski2015}) and a = $\sqrt{2}$ for a disk with constant rotational velocity \citep{Wisnioski2015}.
-
-\begin{equation}\label{eq:sigma_increase}
-    \sigma(z) = V_{C}f_{gas}(z,M_{\star})Q_{crit}/a
-\end{equation}
-
-In this model the velocity dispersions increase as a result of increasing gas fractions within galaxies, with a steeper increase from $z\simeq0$ for galaxies at higher stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
+The Equation $\sigma(z,M_{\star})\propto f_{gas}(z,M_{\star})$ is scaled so that the lowest mass track conincides with the KDS datapoint, finding a proportionality constant $V_{C}Q_{crit}/a = 90.5kms^{-1}$.
+$Q_{crit} = 1.0$ for a quasi-stable thin disk e.g.
+\citealt{ForsterSchreiber2006,Burkert2010}) and a = $\sqrt{2}$ for a disk with constant rotational velocity \citep{Wisnioski2015}, and assuming these values gives $V_{C} = 128kms^{-1}$ as a best match to our data.
+This is larger than the intrinsic rotation velocities in the isolated field sample, although this could be a result of the assumptions for both $Q_{crit}$ and a. \\
+
+In this model the velocity dispersions increase more steeply with increasing stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
 At higher redshift, these lines converge, suggesting that the predictions for the gas fraction become independent of stellar mass in this regime.
-The value $V_{C}=125kms^{-1}$ is chosen as a suitable average of the rotational velocity values reported in the surveys as shown in the right panel of Figure \ref{fig:tf_relation}.
-In general, the surveys with higher stellar mass have lower velocity dispersions, in support of the model hypothesis. \\
-
-Since stellar mass appears to be a crucial factor in regulating the velocity dispersions within galaxies, and the comparison samples have disparate stellar mass ranges, we use the model to shift the $\sigma_{int}$ values according to their stellar mass to a reference mass value.
+In general, the surveys with higher stellar mass have lower velocity dispersions, in support of the model hypothesis.
+
+Since stellar mass appears to be a crucial factor in regulating the velocity dispersions within galaxies, and the comparison samples have disparate stellar mass ranges, we use the model to shift the $\sigma_{int}$ values according to their stellar mass to a reference mass value as per \cite{Wisnioski2015}.
 This is done by computing the difference between the model predicted $\sigma_{int}$ value at the stellar mass of each comparison survey and at the reference mass for the appropriate redshift and shifting the reported $\sigma_{int}$ by this value.
-We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}) and only consider the surveys deemed directly comparable (denoted by the filled symbols throughout \cref{sec:results}).
-In both panels the dark grey shaded regions encompass the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 100-150kms^{-1}$ respectively.
-The light grey shaded regions encompass model predictions between `minimum' values with $Q_{crit} = 0.68$,$V_{C}=100kms^{-1}$ and `maximum' values with $Q_{crit} = 0.68$,$V_{C}=150kms^{-1}$. \\
-
-The $\sigma_{int}$ shifted galaxies in Figure \ref{fig:sigma_shifted} are consistent with a single relation for the increase in velocity dispersion with redshift as a result of increasing gas fractions, with the difference between the slopes in the left and right panels highlighting the role of stellar mass in the kinematic settling of galaxies between $z\simeq2$ and the local universe.
+We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}).
+In both panels, the grey line denotes the model prediction using $Q_{crit} = 1.0$, a = $\sqrt{2}$ and $V_{C} = 128kms^{-1}$ and the light grey shaded region encompasses the model predictions with lower and upper bounds defined with $V_{C} = 70-200kms^{-1}$ respectively (spanning the velocity values of galaxies in the comparison samples).
+\\
+
+Although the details of the coefficients of Equation \ref{eq:sigma_increase} are unclear (i.e.
+$V_{C}$ is not fixed at one value for the comparison samples and is itself linked to stellar mass and both $Q_{crit}$ and a could vary with redshift), the shape of the velocity dispersion evolution appears to follow that of the gas fraction.
+The difference between the slopes in the left and right panels highlights the role of stellar mass in the kinematic settling of galaxies between $z\simeq2$ and the local universe. 
 The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Law2012b,Law2012c,Wisnioski2015}.
@@
     This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in the system \citep[e.g.][]{Burkert2010}.  
+    \item 13/32 isolated field sample galaxies are rotation-dominated and 19/32 are dispersion-dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
+    This gives a rotation-dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
+    When viewed as a function of redshift, the rotation dominated fraction appears to follow the scaling relation RDF$\propto z^{-0.2}$.
     \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in Appendix \ref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{\star}$ of the galaxy samples (right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
     This is in line with a simple equilibrium model prescription in which the gas fractions and the impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to increase random motions within high redshift galaxies.
-    \item 13/32 isolated field sample galaxies are rotation-dominated and 19/32 are dispersion-dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
-    This gives a rotation-dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
 
@@
 
+MC and OJT acknowledge the KMOS team and all the personnel of the European Southern Observatory Very Large Telescope for outstanding support during the KMOS GTO observations.
 CMH, AMS and RMS acknowledge the Science and Technology Facilities Council through grant code ST/L00075X/1.
@@
 \caption{The mean and median kinematic properties used throughout Figures \protect\ref{fig:tf_relation}, \protect\ref{fig:sigma_and_v_sigma_w_redshift} and \protect\ref{fig:rdf_and_v_sigma_w_redshift} for the different surveys.
-The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
+The errors on the mean and median represent the statistical errors from bootstrap resampling.
+For each of the comparison samples the cross or tick after each of the mean kinematic properties indicates whether we have defined this as a fair value to compare against, with further details provided throughout Appendices \protect\ref{subsec:GHASP} - \protect\ref{subsec:AMAZE}.}
 \label{tab:evolution_numbers}
@@
  \hline
-Survey & $\left< z \right> $ & $\left< log\left(\frac{M_{\star}}{M_{\odot}}\right)\right>$ & $\left< \frac{V_{C}}{\sigma_{int}} \right>$ & med$\left(\frac{V_{C}}{\sigma_{int}}\right)$ & RDF & $ \left< \sigma_{int} \right>$ & med$\left(\sigma_{int}\right)$ & $\left<V_{C}\right>$ & med$\left(V_{C}\right)$  \\[1ex]
+Survey & $\left< z \right> $ & $\left< log\left(\frac{M_{\star}}{M_{\odot}}\right)\right>$ & $\left<V_{C}\right>$ & med$\left(V_{C}\right)$ & $ \left< \sigma_{int} \right>$ & med$\left(\sigma_{int}\right)$ & $\left< \frac{V_{C}}{\sigma_{int}} \right>$ & med$\left(\frac{V_{C}}{\sigma_{int}}\right)$ & RDF  \\[1ex]
  \hline
- GHASP & 0.001 & 10.6 & $12.9^{+0.5}_{-0.4}$ & $12.5^{+0.6}_{-0.6}$ & $1.00^{+0.00}_{-0.02}$ & $13.0^{+0.5}_{-0.5}$ & $13.0^{+0.5}_{-0.5}$ & $189.0^{+3.5}_{-3.0}$ & $159.4^{+12.0}_{-15.0}$ \\[1ex]
- DYNAMO & 0.1 & 10.3 & $5.1^{+0.2}_{-0.2}$ & $4.6^{+0.2}_{-0.2}$ & $0.96^{+0.02}_{-0.02}$ & $45.9^{+0.3}_{-0.3}$ & $39.0^{+0.9}_{-1.0}$ & $183.0^{+1.0}_{-1.0}$ & $164.0^{+3.0}_{-5.0}$ \\[1ex]
- MUSE+KMOS & 0.65 & 9.4 & $2.9^{+0.1}_{-0.1}$ & $2.21^{+0.1}_{-0.1}$ & $0.83^{+0.02}_{-0.02}$ & $40.0^{+0.3}_{-0.3}$ & $32.0^{+0.6}_{-0.5}$ & $103.8^{+1.5}_{-1.6}$ & $73.0^{+2.5}_{-2.5}$ \\[1ex]
- KROSS & 0.9 & 9.9 & $3.1^{+0.2}_{-0.2}$ & $2.4^{+0.1}_{-0.1}$ & $0.81^{+0.05}_{-0.05}$ & - & - & $117.0^{+4.0}_{-4.0}$ & $109.0^{+5.0}_{-5.0}$ \\[1ex]
- KMOS$^{3D}$ & 1.0 & 10.7 & 5.5 & - & 0.93 & 25.0 & - & 170.0 & - \\[1ex]
- MASSIV & 1.2 & 10.2 & $2.4^{+1.4}_{-0.9}$ & $2.0^{+0.3}_{-0.2}$ & $0.67^{+0.06}_{-0.06}$ & $61.8^{+3.8}_{-4.2}$ & $52.0^{+5.2}_{-4.7}$ & $132.1^{+10.4}_{-8.2}$ & $103.0^{+13.4}_{-11.0}$ \\[1ex]
- MUSE+KMOS & 1.25 & 9.8 & $2.2^{+1.0}_{-1.0}$ & $1.59^{+0.1}_{-0.1}$ & $0.78^{+0.04}_{-0.04}$ & $42.0^{+0.5}_{-0.5}$ & $29.5^{+1.0}_{-1.0}$ & $75.5^{+3.0}_{-3.3}$ & $54.0^{+3.0}_{-2.8}$ \\[1ex]
- SINS(C09) & 2.0 & 10.6 & $5.0^{+0.9}_{-1.0}$ & $4.7^{+1.0}_{-1.0}$ & 1.0 & $51.2^{+8.0}_{-7.9}$ & $42.5^{+9.1}_{-8.5}$ & $232.0^{+12.8}_{-12.7}$ & $240.0^{+18.0}_{-17.2}$ \\[1ex]
- SINS(F09) & 2.0 & 10.6 & 2.6 & - & 0.60 & - & - & $201.3^{+4.3}_{-4.0}$ & $174.0^{+12.1}_{-10.3}$ \\[1ex]
- KMOS$^{3D}$ & 2.2 & 10.9 & 2.6 & - & 0.73 & 55.0 & - & 170.0 & - \\[1ex]
- AMAZE (Full) & 3.0 & 10.0 & $3.6^{+1.5}_{-1.1}$ & $2.1^{+0.6}_{-0.5}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+4.5}_{-4.8}$ & $217.0^{+59.1}_{-40.2}$ & $129.0^{+47.5}_{-42.8}$ \\[1ex]
- AMAZE (Clean) & 3.0 & 10.0 & $1.4^{+0.3}_{-0.3}$ & $1.1^{+0.3}_{-0.3}$ & - & $95.7^{+2.0}_{-2.0}$ & $95.0^{+2.6}_{-2.6}$ & $140.8^{+40.1}_{-30.2}$ & $129.0^{+45.0}_{-33.4}$ \\[1ex]
- \textbf{KDS} & 3.5 & 9.8 & $1.1^{+0.2}_{-0.1}$ & $0.84^{+0.1}_{-0.1}$ & $0.37^{+0.08}_{-0.08}$ & $70.3^{+3.3}_{-3.1}$ & $71.0^{+5.0}_{-4.8}$ & $75.7^{+4.4}_{-4.4}$ & $57.5^{+5.5}_{-5.5}$ \\[1ex]
+ GHASP & 0.001 & 10.6   &       $189.0^{+3.5}_{-3.0}$ \cmark  & $159.4^{+12.0}_{-15.0}$ &  $13.0^{+0.5}_{-0.5}$ \cmark & $13.0^{+0.5}_{-0.5}$ & $12.9^{+0.5}_{-0.4}$ \cmark &           $12.5^{+0.6}_{-0.6}$&               $1.00^{+0.00}_{-0.02}$  \cmark   \\[1ex]
+ DYNAMO & 0.1 & 10.3    &       $183.0^{+1.0}_{-1.0}$ \xmark  & $164.0^{+3.0}_{-5.0}$   &  $45.9^{+0.3}_{-0.3}$ \xmark & $39.0^{+0.9}_{-1.0}$ & $5.1^{+0.2}_{-0.2}$  \xmark &           $4.6^{+0.2}_{-0.2}$ &               $0.96^{+0.02}_{-0.02}$  \xmark   \\[1ex]
+ MUSE+KMOS & 0.65 & 9.4 &       $103.8^{+1.5}_{-1.6}$ \cmark  & $73.0^{+2.5}_{-2.5}$    &  $40.0^{+0.3}_{-0.3}$ \cmark & $32.0^{+0.6}_{-0.5}$ & $2.9^{+0.1}_{-0.1}$  \cmark &           $2.21^{+0.1}_{-0.1}$&               $0.83^{+0.02}_{-0.02}$  \cmark   \\[1ex]
+ $^{*}$KROSS & 0.9 & 9.9 &      $117.0^{+4.0}_{-4.0}$ \cmark  & $109.0^{+5.0}_{-5.0}$   &  -                    \cmark & -                    & $3.1^{+0.2}_{-0.2}$  \cmark &           $2.4^{+0.1}_{-0.1}$ &               $0.81^{+0.05}_{-0.05}$  \cmark   \\[1ex]
+ KMOS$^{3D}$ & 1.0 & 10.7  &     170.0                        &  -                      &  25.0                 \xmark &  -                   & 5.5                  \xmark &            -                  &               0.93                    \xmark   \\[1ex]
+ MASSIV & 1.2 & 10.2 &          $132.1^{+10.4}_{-8.2}$ \cmark & $103.0^{+13.4}_{-11.0}$ &  $61.8^{+3.8}_{-4.2}$ \cmark & $52.0^{+5.2}_{-4.7}$ & $2.4^{+1.4}_{-0.9}$  \cmark &           $2.0^{+0.3}_{-0.2}$ &               $0.67^{+0.06}_{-0.06}$  \cmark   \\[1ex]
+ MUSE+KMOS & 1.25 & 9.8 &       $75.5^{+3.0}_{-3.3}$   \cmark & $54.0^{+3.0}_{-2.8}$    &  $42.0^{+0.5}_{-0.5}$ \cmark & $29.5^{+1.0}_{-1.0}$ & $2.2^{+1.0}_{-1.0}$  \cmark &           $1.59^{+0.1}_{-0.1}$&               $0.78^{+0.04}_{-0.04}$  \cmark   \\[1ex]
+ SINS(C09) & 2.0 & 10.6 &       $232.0^{+12.8}_{-12.7}$\cmark & $240.0^{+18.0}_{-17.2}$ &  $51.2^{+8.0}_{-7.9}$ \cmark & $42.5^{+9.1}_{-8.5}$ & $5.0^{+0.9}_{-1.0}$  \xmark &           $4.7^{+1.0}_{-1.0}$ &               1.0                     \cmark   \\[1ex]
+ SINS(F09) & 2.0 & 10.6 &       $201.3^{+4.3}_{-4.0}$  \cmark & $174.0^{+12.1}_{-10.3}$ &  -                    \xmark & -                    & 2.6                  \xmark &           -                   &               0.60                    \xmark   \\[1ex]
+ KMOS$^{3D}$ & 2.2 & 10.9 &     170.0                  \xmark & -                       &  55.0                 \xmark & -                    & 2.6                  \xmark &           -                   &               0.73                    \xmark   \\[1ex]
+ LAW 09 & 2.3 & 10.0 &          -                      \xmark & -                       &  $78.0^{+6.5}_{-6.5}$ \xmark & $69.0^{+8.3}_{-7.5}$ & -                    \xmark &           -                   &               0.73                    \xmark   \\[1ex]
+ AMAZE (Full) & 3.0 & 10.0 &    $217.0^{+59.1}_{-40.2}$\xmark & $129.0^{+47.5}_{-42.8}$ &  $85.9^{+1.5}_{-1.4}$ \xmark & $78.0^{+4.5}_{-4.8}$ & $3.6^{+1.5}_{-1.1}$  \xmark &           $2.1^{+0.6}_{-0.5}$ &               0.33                    \xmark   \\[1ex]
+ AMAZE (Clean) & 3.0 & 10.0 &   $140.8^{+40.1}_{-30.2}$\cmark & $129.0^{+45.0}_{-33.4}$ &  $95.7^{+2.0}_{-2.0}$ \cmark & $95.0^{+2.6}_{-2.6}$ & $1.4^{+0.3}_{-0.3}$  \cmark &           $1.1^{+0.3}_{-0.3}$ &               -                       \xmark   \\[1ex]
+ \textbf{KDS} & 3.5 & 9.8 &     $75.7^{+4.4}_{-4.4}$   \cmark & $57.5^{+5.5}_{-5.5}$    &  $70.3^{+3.3}_{-3.1}$ \cmark & $71.0^{+5.0}_{-4.8}$ & $1.1^{+0.2}_{-0.1}$  \cmark &            $0.84^{+0.1}_{-0.1}$&               $0.37^{+0.08}_{-0.08}$ \cmark    \\[1ex]
  \hline
 \end{tabular}
+\begin{tablenotes}
+      \small
+      \item $^{*}$ The intrinsic velocity dispersion values for the KROSS sample will be presented in Johnson et al. {\it in prep.} 
+    \end{tablenotes}
   \end{threeparttable}
@@
 The data extend out to several half-light radii and in each case tilted ring models are fit to determine $V_{C}$ at large radii where the rotation curves have flattened, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
-We use the tabulated values from this survey as a local comparison sample.
+In this survey, the mean and median kinematic properties computed from the tabulated literature values are directly comparable to the KDS and we used filled symbols in the plots throughout \cref{sec:results} to highlight this.
 
@@
 $V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.6R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
-We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{sec:results} to highlight the difference in selection critera.
+We make use of tabulated data from this survey, but use hollow symbols throughout the plots in \cref{sec:results} to highlight the difference in selection critera.
 
@@
 The reported velocities are extracted at $3R_{D}$, comparable to the extraction radius for the KDS sample and the intrinsic velocity dispersions have been corrected for beam-smearing effects.
-We make use of the tabulated data from this survey and use the results at the two redshift ranges as reliable comparison samples.
+The kinematic properties computed from the tabulated data in this survey are directly comparable to the KDS, reflected by the filled symbols throughout the plots in \cref{sec:results}.
 
@@
 These quantities are then beam-smearing corrected as described in H17 section 3.3.3. 
-Due to the consistency of modelling and measurement techniques these form a robust $z\simeq0.9$ comparison sample.
+Due to the consistency of modelling and measurement techniques, the $z\simeq0.9$ galaxies in this sample are directly comparable to the KDS and are plotted throughout \cref{sec:results} with filled symbols.
 
@@
 The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
-No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{sec:results} plots.
+No tabulated values are provided for this survey, and so we cannot re-compute the mean and median values.
+We make use of values quoted in W15 at both redshift intervals throughout \cref{sec:results}, plotting these with hollow symbols due to the inconsistency of measurement method.
 
@@
 An arctangent function is fit to the data and $V_{C}$ is extracted at $\simeq1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
-We make use of tabulated values presented in E12.
+We make use of tabulated values presented in this survey to compute the mean and median kinematic properties, plotted with filled symbols throughout \cref{sec:results}.
 
@@
 
-It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness and note that the $V_{C}$ values in C09 are likely biased towards rotation-dominated galaxies with a well-settled disk.
-We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation-dominated fraction results listed in W15 without distributions in the plots throughout \cref{sec:results}.
+It is unclear whether the $V_{C}$ values for the full sample from FS09 are directly comparable, but we make use of the tabulated values for completeness and plot these with filled symbols throughout \cref{sec:results}.
+The velocity dispersion values, $V_{C}/\sigma_{int}$ and the rotation dominated fraction from FS09 are plotted with hollow symbols throughout \cref{sec:results} (using the results listed in W15 for the point locations) due to the difference in measurement method for the velocity dispersion values.
+
+The $V_{C}$ and $\sigma_{int}$ values in C09 are likely biased towards rotation-dominated galaxies with a well-settled disk.
+Nonetheless we plot these values with filled symbols in \cref{sec:results} as a directly comparable dataset, omitting the $V_{C}/\sigma_{int}$ values and the rotation dominated fraction, which are listed for the full FS09 sample.
 
@@
 The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
-We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux-weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
+We note that the $\sigma_{mean}$ values and errors tabulated in the \cite{Law2009} paper are the flux-weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
 These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have been beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
-We use tabulated data $\sigma_{int}$ data in L09 to compare this distribution with other results, but make no comparisons with the observed velocity-shear values.
+We use tabulated data $\sigma_{int}$ data in L09 to compare this distribution with other results, but plot with a hollow symbol due to the lack of a beam-smearing correction.
 
@@
 In this study, rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ as the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map (which also takes into account instrumental resolution and beam-smearing; see their Equation 8).
-A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotation-dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
-We use tabulated values from G11, but note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys (which contain a mix of rotation and dispersion-dominated galaxies).
-\\
+A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotation-dominated galaxies in their sample, with the remaining 22 galaxies not analysed. \\
 
@@
 For the mean value computations we set these equal to the SINFONI resolution limit of 30 kms$^{-1}$.
-A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0 kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{sec:results}.
+A total of 6/11 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0 kms$^{-1}$, which we refer to as the AMAZE `Unconstrained' sample and represent these with hollow symbols throughout the plots in \cref{sec:results}.
 This Unconstrained sample also contains the galaxy s\_sa22a-M38, common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346 kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
-The remaining 5 galaxies we refer to as the AMAZE Clean sample and plot with grey symbols.
+We use tabulated values from the full analysed sample of 11 galaxies, plotting these with hollow symbols throughout \cref{sec:results} as a consequence of the caveats listed above.
+The 5/11 galaxies which are not in the Unconstrained sample are referred to as the AMAZE `Clean sample' and are directly comparable to the KDS.
+These are plotted with filled symbols throughout \cref{sec:results}.
 We plot the quoted rotation-dominated fraction of 33$\%$, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation-dominated. \\
@@
 \caption{The distribution of the isolated field sample in the $\sigma_{int}$ vs. $V_{C}$ plane is plotted with the red symbols.
-The AMAZE Clean ($z\simeq3$) sample galaxies (see \protect\cref{subsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with clear symbols.
+The AMAZE Clean ($z\simeq3$) sample galaxies (see \protect\cref{subsec:AMAZE}) are plotted with grey symbols and the AMAZE Unconstrained sample with hollow symbols.
 There is no strong correlation between the two parameters in either of these surveys and we note that the KDS and AMAZE Clean galaxies are generally in agreement.
@@
 
-    \caption{We plot the kinematic grids for the 13 isolated field sample galaxies classified as rotation-dominated.
+    \caption{We plot the kinematic grids for the 13/32 isolated field sample galaxies classified as rotation-dominated.
     For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian-fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
+    The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.
     On the bottom row we plot the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.

### 2017-04-04 paper.tex
sending back to Chris for feedback

@@
 Additionally, there has been increasing focus in recent years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
-These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotational velocities \citep{Burkert2010}.
+These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotation velocities \citep{Burkert2010}.
 Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\
@@
 Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 9.8$. 
-We note that fitting the photometry of the KDS targets with 0.2 $Z\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
-In GOODS-S, we have compared our derived stellar masses to those in \cite{Santini2015} (which presents an average result from 10 different sets of analyses), finding a median difference between the two sets of values of $\Delta \log(M_{\star}/{\rm M}_{\odot}) = 0.009$ \\
+Fitting the photometry of the KDS targets with 0.2 $Z\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
+In GOODS-S, we have compared our derived stellar masses to those in \cite{Santini2015} (which presents an average result from 10 different sets of analyses), finding a median difference between the two sets of values of $\Delta \log(M_{\star}/{\rm M}_{\odot}) = 0.009$.
+We note also that using the star-forming templates described in \cite{Wuyts2011} typically leads to stellar masses which are 0.2 dex higher.
 
@@
 \subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
-We proceeded to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
-This is a simple empirical diagnostic for whether a galaxy is `Rotation-Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion-Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
-a method to measure the prevalence of rotational and random motions;][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
-Previous studies have used various classification schemes of varying complexity to identify rotation-dominated galaxies which also appear to be `disk-like' and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
-We describe our simple classification criteria for the isolated field sample based on a joint consideration of the high-resolution photometry and derived kinematic parameters in \cref{subsubsection:isolated_classification} and mention the KDS merger candidates in more detail in the following section.
-
-\subsubsection{KDS merger candidates}\label{subsubsection:merger_candidates}
-The KDS galaxies were classified as mergers when more than one component was identified in the high-resolution imaging.  
-One benefit of studying the {\em HST} photometry in tandem with the kinematics was to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
-These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
-A second benefit was to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
-can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging (e.g.
-the bottom grid in Figure \ref{fig:main_body_kinematic_grids}).
-
-This has been discussed in \cite{Hung2015}, where redshifted local interacting galaxies are misclassified as single rotating disks on the basis of their kinematics. 
-In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
-It was difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e.
-clumpy disk galaxies e.g.
-\citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
-Perhaps the most telling diagnostic was the presence of two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map.
 
@@
 
+We proceeded to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
+This is a simple empirical diagnostic for whether a galaxy is `Rotation-Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion-Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
+a method to measure the prevalence of rotational and random motions;][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
+Previous studies have used various classification schemes of varying complexity to identify rotation-dominated galaxies which also appear to be `disk-like' and we briefly mention some of these in \cref{subsubsection:isolated_classification}.
+We describe our simple classification criteria for the isolated field sample based on a joint consideration of the high-resolution photometry and derived kinematic parameters in \cref{subsubsection:isolated_classification} and mention the KDS merger candidates in more detail in the following section.
+
+\subsubsection{KDS merger candidates}\label{subsubsection:merger_candidates}
+The KDS galaxies were classified as mergers when more than one component was identified in the high-resolution imaging.  
+One benefit of studying the {\em HST} photometry in tandem with the kinematics was to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
+These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
+A second benefit was to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
+can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging (e.g.
+the bottom grid in Figure \ref{fig:main_body_kinematic_grids}).
+
+This has been discussed in \cite{Hung2015}, where redshifted local interacting galaxies are misclassified as single rotating disks on the basis of their kinematics. 
+In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
+It was difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e.
+clumpy disk galaxies e.g.
+\citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
+Perhaps the most telling diagnostic was the presence of two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map.
+\\
+
 In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identified signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
@@
 see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}/M_{\odot})=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
-This suggests again that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Law2012b,Law2012c,Newman2013,Wisnioski2015}.
+This suggests again that the increase in random motions could influence the rotation velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Law2012b,Law2012c,Newman2013,Wisnioski2015}.
 These ideas are explored in the following sections.
@@
 $M_{\star}$ plane.
-This is an interesting relationship to explore as it has been suggested that rotational velocity alone may not be a good tracer of total dynamical mass at high redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
+This is an interesting relationship to explore as it has been suggested that rotation velocity alone may not be a good tracer of total dynamical mass at high redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
 However the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
@@
 
-The increase of velocity dispersion within typical typical star-forming galaxies with redshift appears to follow the same scaling relation as the increase of gas fractions, as inspired by the model described in \cite{Wisnioski2015} and discussed in \cref{discussion_increase_in_sigma}.
+The increase of velocity dispersion within typical star-forming galaxies with redshift appears to follow the same scaling relation as the increase of gas fractions, as inspired by the model described in \cite{Wisnioski2015} and discussed in \cref{discussion_increase_in_sigma}.
 The gas fraction is a function of both stellar mass and redshift and so we plot tracks in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} for three different mass values which roughly encompass the average masses of the comparison samples, $log(M_{\star}/M_{\odot})=9.8,10.3,10.6$.
 The tracks are each scaled with the same coefficient, which is chosen so that the lowest mass track, equivalent to the isolated field sample mean mass, coincides with the KDS datapoint at $z=3.5$.
-As the data suggest, the lower mass tracks suggest a flatter evolution of velocity dispersion with redshift, with convergence at high redshift.  
+As the data suggest, the lower mass tracks describe a flatter evolution of velocity dispersion with redshift, with the different masses showing converging velocity dispersion predictions at high redshift.
 The redshift and mass dependence of these tracks is discussed in \cite{Wisnioski2015} and in more detail throughout \cref{discussion_increase_in_sigma}, where we also discuss possible physical explanations for the increase in velocity dispersions with redshift.
@@
 These new data from the KDS sustain the observation that velocity dispersion is increasing with redshift and provide strong constraints on the internal dynamics of typical star-forming galaxies between $z=3-3.8$.
-When these results are presented in combination with data from the literature in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}, it appears that the stellar mass of galaxies may play a role in mediating the velocity dispersion values (see \cref{discussion_increase_in_sigma}).
+When considered in conjunction with data from the literature in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}, it appears that the stellar mass of galaxies may play a role in mediating the velocity dispersion values (see \cref{discussion_increase_in_sigma}).
 
@@
 Systems such as these form highly unstable and roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009,Genzel2011}.
-The physical mechanisms responsible for the increase in $\sigma_{int}$ may also result in a reduction in the observed rotational velocities by partially compensating the gravitational force throughout the galactic disk \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
-Following this, $\sigma_{int}$ decreases over time as ordered rotations begin to dominate and pressure support becomes increasingly insignificant \citep[e.g.][]{Burkert2010,Ubler2017,Genzel2017,Lang2017}.
+The physical mechanisms responsible for the increase in $\sigma_{int}$ may also result in a reduction in the observed rotation velocities by partially compensating the gravitational force throughout the galactic disk \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
+Following this, $\sigma_{int}$ decreases over time as ordered rotation begins to dominate and pressure support becomes increasingly insignificant \citep[e.g.][]{Burkert2010,Ubler2017,Genzel2017,Lang2017}.
 This is in line with the evolution of gas fractions observed at intermediate and high redshifts \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.
 
-\cite{Burkert2010} show, starting from the hydrostatic equation, that negative pressure gradients sourced by the disk turbulence generated through gravitational instabilities result in a decrease in observed rotational velocities.
+\cite{Burkert2010} show, starting from the hydrostatic equation, that negative pressure gradients sourced by the disk turbulence generated through gravitational instabilities result in a decrease in observed rotation velocities.
 This has prompted others \citep[e.g.][]{Wuyts2016b,Ubler2017,Lang2017} to encorporate a velocity dispersion term in the derivation of maximum circular velocities, which contributes to (but is not entirely responsible for) the observed shift in the zero-point of the stellar mass Tully-Fisher relation between $z\simeq0-0.9$.
 \cite{Ubler2017} also claim that without the inclusion of this term incorrect conclusions surrounding the evolution of the Tully-Fisher relation will be drawn.
-We have not encorporated such a term when deriving the rotational velocities of the isolated field sample, but note that as a consequence of our galaxies showing some of the most extreme intrinsic dispersions observed, this would undoubtedly lead to a different distribution in the $V_{C}-M_{\star}$ plane.
+We have not encorporated such a term when deriving the rotation velocities of the isolated field sample, but note that as a consequence of our galaxies showing some of the most extreme intrinsic dispersions observed, this would undoubtedly lead to a different distribution in the $V_{C}-M_{\star}$ plane.
 The contribution of pressure to rotation velocity for the KDS sample will be explored in more detail in a future work. 
@@
 
-In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties gas fraction, $f_{gas}$, gas depletion timescale, $t_{depl}$, and specific star-formation rate, sSFR.
-The function describing the evolution of the velocity dispersion is shown below in Equation \ref{eq:sigma_increase}, where $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964}, and a is a dimensionless parameter depending on the assumed distribution of gas and gravitational potential \cite{ForsterSchreiber2006}.
+In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties: gas fraction, $f_{gas}$ gas depletion timescale, $t_{depl}$, and specific star-formation rate, sSFR.
+The function describing the evolution of the velocity dispersion with redshift is shown below in Equation \ref{eq:sigma_increase}, where $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964}, and {\it a} is a dimensionless parameter which depends on the assumed distribution of gas and gravitational potential \cite{ForsterSchreiber2006}.
 
 \begin{equation}\label{eq:sigma_increase}
-    \sigma(z,M_{\star}) = V_{C}f_{gas}(z,M_{\star})Q_{crit}/a
+    \sigma(z,M_{\star}) = V_{C}f_{gas}(z,M_{\star})Q_{crit}/{\it a}
 \end{equation}
@@
 $Q_{crit} = 1.0$ for a quasi-stable thin disk e.g.
-\citealt{ForsterSchreiber2006,Burkert2010}) and a = $\sqrt{2}$ for a disk with constant rotational velocity \citep{Wisnioski2015}, and assuming these values gives $V_{C} = 128kms^{-1}$ as a best match to our data.
-This is larger than the intrinsic rotation velocities in the isolated field sample, although this could be a result of the assumptions for both $Q_{crit}$ and a. \\
+\citealt{ForsterSchreiber2006,Burkert2010}) and {\it a} = $\sqrt{2}$ for a disk with constant rotation velocity \citep{Wisnioski2015}, and assuming these values gives $V_{C} = 128kms^{-1}$ as a best match to our data.
+This is larger than the intrinsic rotation velocities in the isolated field sample, although this could be a result of the assumptions for both $Q_{crit}$ and {\it a}. \\
 
@@
 We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}).
-In both panels, the grey line denotes the model prediction using $Q_{crit} = 1.0$, a = $\sqrt{2}$ and $V_{C} = 128kms^{-1}$ and the light grey shaded region encompasses the model predictions with lower and upper bounds defined with $V_{C} = 70-200kms^{-1}$ respectively (spanning the velocity values of galaxies in the comparison samples).
+In both panels, the grey line denotes the model prediction using $Q_{crit} = 1.0$, {\it a} = $\sqrt{2}$ and $V_{C} = 128kms^{-1}$ and the light grey shaded region encompasses the model predictions with lower and upper bounds defined with $V_{C} = 70-200kms^{-1}$ respectively (spanning the velocity values of galaxies in the comparison samples).
 \\
@@
 Although the details of the coefficients of Equation \ref{eq:sigma_increase} are unclear (i.e.
-$V_{C}$ is not fixed at one value for the comparison samples and is itself linked to stellar mass and both $Q_{crit}$ and a could vary with redshift), the shape of the velocity dispersion evolution appears to follow that of the gas fraction.
-The difference between the slopes in the left and right panels highlights the role of stellar mass in the kinematic settling of galaxies between $z\simeq2$ and the local universe. 
+$V_{C}$ is not fixed at one value for the comparison samples and is itself linked to stellar mass and both $Q_{crit}$ and {\it a} could vary with redshift), the shape of the velocity dispersion evolution appears to follow that of the gas fraction.
+The difference between the slopes in the left and right panels highlights the role of stellar mass in the kinematic settling of galaxies between $z\simeq3$ and the local universe. 
 The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Law2012b,Law2012c,Wisnioski2015}.
@@
 This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale length \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
-Recent results indicate that these systems become strongly baryon-dominated on the galaxy disk scale at high redshift \citep{Ubler2017,Lang2017,Genzel2017}, which may imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.
+Recent results indicate that these systems may become strongly baryon-dominated on the galaxy disk scale at high redshift \citep{Ubler2017,Lang2017,Genzel2017}, which could imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.
 
@@
 We have presented new dynamical measurements of 32 typical star forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
-These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.0 < log(M_{\star}/M_{\odot})< 10.5$ typical main-sequence galaxies at these redshifts.
-By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\simeq18\%$) and a very high merger rate in the cluster pointing ($\simeq89\%$).
+These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.0 < log(M_{\star}/M_{\odot})< 10.5$ typical star-forming galaxies at these redshifts.
+By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\simeq16\%$) and a very high merger rate in the cluster pointing ($\simeq89\%$).
 We have made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (Appendix \ref{app:comparison_samples} and Table \ref{tab:evolution_numbers}).

### 2017-04-05 paper.tex
about to make next round of Chris suggestions (making section 4 even less empirical)

@@
 H. L. Johnson,$^{3,4}$
-D. Sobral,$^{5}$
+D. Sobral,$^{5,6}$
 J. Matthee,$^{6}$
@@
 These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
-The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\simeq3$ in other samples, to which we have made careful comparisons.
-However only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
+The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\simeq3$.
+However, only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
+After carefully selecting comparable star-forming samples at multiple epochs, we find that the rotation-dominated fraction evolves with redshift with a $z^{-0.2}$ dependence. 
 The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e.
@@
 This correlation, or `main-sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
-The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
+The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep[e.g.][]{Madau_2014,Khostovan2015}.
 At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
@@
 
-Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
+Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014,Vogelsberger2014b,Schaye2015}.
 Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
@@
 
+\noindent
 In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
@@
 
-This paper focuses on the first question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
-\\
-
+This paper focuses on (i) by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
+\\
+
+\noindent
 The structure of the paper is as follows.
@@
 The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
-The key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation ( particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
+The key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
 We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and a `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
@@
 Two of the three FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
-We selected targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
+We selected targets from the various spectroscopic campaigns which have targeted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
 These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
@@
 
+\noindent
 We prepared each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
@@
 
+\noindent
 The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
@@
 
+\noindent
 This paper is concerned with the spatially-resolved kinematics of the KDS galaxies.
@@
 
+\noindent
 Sky subtraction was enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
@@
 
+\noindent
 We stacked all 300s exposures for each galaxy which pass the seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
 We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
-To account for this a polynomial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
-\\
-
+To account for this, a polynomial function is fit, using the python package {\tt LMFIT} \citep{Newville2014}, which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
+\\
+
+\noindent
 The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det} = 62/77$ $(81\%)$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
@@
 
+\noindent
 The difference in position of these relations highlights the main-sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\simeq2.5-3.5$.
@@
 \subsection{Morphological Measurements}\label{subsec:morphological_measurements}
-For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution images.
-This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$), morphological position angle, $PA_{morph}$, and axis ratio, $b/a$, of the galaxies.
-In the following sections we describe the approach we have chosen to recover these parameters, also describing comparisons with matched galaxies in the morphological parameter catalogue of \cite{VanderWel2012}.
-At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
+For a robust interpretation of the observed velocity fields, it was necessary to separately determine the morphological properties of the galaxies from high-resolution images.
+This imaging was used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$), morphological position angle, $PA_{morph}$, and axis ratio, $b/a$, of the galaxies.
+In the following sections we describe the approach chosen to recover these parameters, also describing comparisons with matched galaxies in the morphological parameter catalogue of \cite{VanderWel2012}.
+At $3 < z < 4$ and $0.1 < z < 1$ we made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
 This allowed us to investigate the morphological properties of typical star-forming galaxy populations at two redshift slices in comparison with those determined for the KDS sample.
@@
 We used {\tt GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
-The GOODS-S imaging data used is the latest release of the total field in WFC3 F160W band, which traces the rest-frame near-UV at $z\simeq3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
-For SSA22 we made use of archival {\em HST} imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the WFC3 F160W band (P.I.
+The GOODS-S imaging data used is the latest release of the total field in {\it WFC3 F160W} band, which traces the rest-frame near-UV at $z\simeq3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
+For SSA22 we made use of archival {\em HST} imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the {\it WFC3 F160W} band (P.I.
 Lehmer: PID 13844; P.I.
-Mannucci: PID 11735) and the ACS F814W band, tracing $\simeq$ 2000$\AA$ light at $z\simeq3.5$ (P.I.
+Mannucci: PID 11735) and the {\it ACS F814W} band, tracing $\simeq$ 2000$\AA$ light at $z\simeq3.5$ (P.I.
 Chapman: PID 10405; P.I.
@@
 Siana: PID 12527).
-The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the F160W coverage is concentrated on the SSA22-CLUSTER and so we resorted to the bluer ACS F814W data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage are listed in Table \ref{tab:phys-props}).
-\\
-
+The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the {\it F160W} coverage is concentrated on the SSA22-CLUSTER and so we resorted to the bluer {\it ACS F814W} data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage are listed in Table \ref{tab:phys-props}).
+\\
+
+\noindent
 We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT} and then extracted postage stamp regions around the galaxies in the KDS sample.
 At this redshift, the galaxies are more compact and generally we could not resolve more complicated morphological features such as spiral arms and bars and so we followed the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of $n=1$.
-In the F160W band the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the F814W band we used the pure Tiny Tim ACS high-resolution PSF model.
+In the {\it F160W} band the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the {\it F814W} band we used the pure Tiny Tim {\it ACS} high-resolution PSF model.
 During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, were free to vary.
@@
 
+\noindent
 This analysis provided us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
@@
  \hline
-ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
+ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & $b/a$ & i$^{\circ}$$^{b}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{c}$ \\
  \hline
-b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.84 & 0.36        & 72        & 9     & 1.57      \\
-b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.76  & 0.28        & 78        & 146   & 0.52      \\
-bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.75 & 0.50         & 61        & 146   & 1.91      \\
+b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.8 & 0.36        & 72        & 9     & 1.57      \\
+b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.8  & 0.28        & 78        & 146   & 0.52      \\
+bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.8 & 0.50         & 61        & 146   & 1.91      \\
 bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.1  & 0.44        & 66        & 168   & 1.83      \\
@@
       \item $^{a}$ Representative error of 0.2 dex from SED modelling used throughout this study
-      \item $^{b}$ Representative error of 0.4 dex in log(SFR$_{SED}$[$M_{\odot}yr^{-1}$]) from SED modelling used throughout this study
-      \item $^{c}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
-      \item $^{d}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
+      \item $^{b}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
+      \item $^{c}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
       \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ set to $PA_{kin}$ value; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
@@
 
+\noindent
 To derive the inclination, we selected a value for $q_{0}$, and following the discussion in \citep{Law2012a} we chose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
@@
 Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopted a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
-For the galaxies without {\em HST} coverage the inclination angle was set to the KDS sample median of 57.0$^{\circ}$ and we used the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
-This adds an additional factor of $\simeq1.3$ to the uncertainty in the derived velocities for these galaxies.
+For the galaxies without {\em HST} coverage, the inclination angle was set to the KDS sample median of 57.0$^{\circ}$ and we used the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
+This added an additional factor of $\simeq1.3$ to the uncertainty in the derived velocities for these galaxies.
 
 \subsubsection{Position angle}\label{subsubsection:position_angle}
-The second {\tt GALFIT} parameter is $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
-We visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this was not the case it was usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
+The second {\tt GALFIT} parameter was $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
+We visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$ indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this was not the case it was usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
 We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2017}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
@@
 \subsubsection{Half-light radii}\label{subsubsection:half-light_radii}
-The half-light radius, $R_{1/2}$, provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
-As discussed throughout the introduction and in Appendix \ref{app:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
+The half-light radius, $R_{1/2}$, provides an indication of the disk sizes and hence gave us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
+As discussed throughout the introduction and in Appendix \ref{app:comparison_samples}, methods used to derive the intrinsic rotation velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
 Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies (see Appendix \ref{app:comparison_samples} and e.g.
@@
 The median difference between the derived $R_{1/2}$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\simeq3.5$).
+\\
 
@@
 %In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).
-
+\noindent
 \cite{Bruce2012} present a detailed error analysis of the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploited during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
@@
 
+\noindent
 To measure $R_{1/2}$ for the 4 galaxies without {\em HST} coverage we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
 We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening.
-\\
 
@@
 We proceeded to extract 2D kinematic measurements from the 62 KDS datacubes detected in integrated [O~{\sc III}]$\lambda$5007 emission by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
-The sample is then refined to galaxies which are spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission in order to make dynamical measurements.
+The sample was then refined to galaxies which are spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission in order to make dynamical measurements.
 We also describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam-smearing corrections for each galaxy.
@@
 
+\noindent
 Each 0.1$^{\prime\prime}$ spaxel across a datacube was considered in turn.
@@
 These parameters, along with the estimate of the noise in the datacube, were used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not.
+
 The noise was estimated by masking all datacube spaxels containing object flux and computing the standard deviation of the flux values in the spectral extraction region for all remaining spaxels inwards of 0.3$^{\prime\prime}$ from the cube boundary (over the same spectral region as considered to find the peak object flux).
@@
 
+\noindent
 The signal in each spaxel was taken as the sum of the flux values across the extraction region, $F_{i,object}$, as shown in Equation \ref{eq:signal} where S denotes the signal.
@@
 
+\noindent
 The criteria for accepting the fit within a given spaxel are as follows:
@@
 
+\noindent
 We imposed a further criterion to help remove fits to spectral features unrelated to the galaxy (e.g.
@@
 
+\noindent
 From the gaussian-fit we recovered the centre, $\lambda_{g}$, the width, $\sigma_{g}$ and the area, $F_{g}$.
@@
 
+\noindent
 To estimate the errors on the observed quantities, the gaussian-fit was repeated 1000 times, with each flux value in the extraction region perturbed by the noise value, $N_{m}$.
@@
 
+\noindent
 If a spaxel did not meet the criteria we follow the procedure described in \cite{Stott2016} and binned with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
@@
 
+\noindent
 The process was automated and applied to each of the 62/77 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
@@
 For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, was added to Table \ref{tab:pointings}.
-We find that 47/77 (76\%) of the detected KDS galaxies across both the field (38) and cluster (9) environments were spatially-resolved and showed clear velocity structure.
+We find that 47/77 (76\%) of the detected KDS galaxies across both the field (38/47) and cluster (9/47) environments were spatially-resolved and showed clear velocity structure.
 The 15/77 galaxies which were not spatially-resolved were dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
@@
 
+\noindent
 The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
 6/38 (16\%) of the resolved galaxies across the 3 field environment pointings and almost all (8/9) of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
-We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
+We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in Figure \ref{fig:merger_galaxies}.
 The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
@@
 
+\noindent
 The velocity decreases with a factor of cos($\phi$) from the kinematic position axis, where $\phi$ is the angle measured clockwise from the axis, which points to the direction of the positive side of the velocity field.
@@
 
-The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction was determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line was set to follow a uniform distribution with a default width of 50kms$^{-1}$.
+\noindent
+The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction was determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line was set to follow a uniform distribution with a default width of 50 km\,s$^{-1}$.
 This default line width was selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\simeq3.0$ velocity dispersions, and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
@@
 
+\noindent
 The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube was then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
 The velocity and velocity dispersion values were then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
-We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, seeking the combination of parameters which maximises the log-Likelihood function given by Equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field.
+We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, seeking the combination of parameters which maximises the log-Likelihood function given by Equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field:
 
@@
 
-The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$ respectively, which is less than observed for lower redshift typical star-forming galaxies (see \cref{subsec:results_rotation_vel} for a discussion).
+The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}km\,s^{-1}$ and $57.0^{+6.6}_{-6.3}km\,s^{-1}$ respectively, which are less than observed for lower redshift typical star-forming galaxies (see \cref{subsec:results_rotation_vel} for a discussion).
 In order to determine the beam-smearing correction factor, we also extracted the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
@@
 
-In 13/38 of the isolated field sample galaxies, the intrinsic $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, however only 2 galaxies require extrapolation > 0.4$^{\prime\prime}$ (i.e.
+\noindent
+In 13/38 of the isolated field sample galaxies, the intrinsic $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model was greater than the last observed radius, however only 2 galaxies required extrapolation > 0.4$^{\prime\prime}$ (i.e.
 2 KMOS pixels) with a mean extrapolation of 0.17$^{\prime\prime}$.
@@
 By comparing the best-fitting simulated datacube with the assumption for the isotropic velocity dispersion we recovered the beam-smearing correction for each galaxy.
-The 2D beam-smearing correction map, $\sigma_{BS}$, was computed on a spaxel-by-spaxel basis as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50kms$^{-1}$ i.e.
-$\sigma_{BS,i} = \sigma_{simulated,i} - \sigma_{assumed,i}$ (where $\sigma_{assumed,i}$ was fixed at 50kms$^{-1}$ as described in \cref{subsubec:model_cube} and $\sigma_{simulated,i}$ is the simulated velocity dispersion recovered under this assumption).
+The 2D beam-smearing correction map, $\sigma_{BS}$, was computed on a spaxel-by-spaxel basis as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50 km\,s$^{-1}$ i.e.
+$\sigma_{BS,i} = \sigma_{simulated,i} - \sigma_{assumed,i}$ (where $\sigma_{assumed,i}$ was fixed at 50 km\,s$^{-1}$ as described in \cref{subsubec:model_cube} and $\sigma_{simulated,i}$ is the simulated velocity dispersion recovered under this assumption).
 The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS,i}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
@@
 
-To measure the $\sigma_{int}$ value for each galaxy in our sample we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian-fits to several skylines (equal to 31.1kms$^{-1}$ in the {\it K}-band and 55.4kms$^{-1}$ in the {\it HK}-band).
+To measure the $\sigma_{int}$ value for each galaxy in our sample we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian-fits to several skylines (equal to 31.1 km\,s$^{-1}$ in the {\it K}-band and 55.4 km\,s$^{-1}$ in the {\it HK}-band).
 
@@
 \sigma_{cor,i} = \sqrt{\left(\sigma_{obs,i} - \sigma_{BS,i}\right)^{2} - \sigma_{inst,i}^{2}}
-\end{equation} \\
-
+\end{equation}
+
+\noindent
 The median of the $\sigma_{cor,i}$ map is taken as the $\sigma_{int}$ value for each galaxy and the median of the observed map is the $\sigma_{obs}$ value (see Table \ref{tab:kin_props}).
-The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} kms^{-1}$ and $71.0^{+5.0}_{-4.8} kms^{-1}$ respectively, higher than for typical star-forming galaxies at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
+The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} km\,s^{-1}$ and $71.0^{+5.0}_{-4.8} km\,s^{-1}$ respectively, higher than for typical star-forming galaxies at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
 The magnitude of the beam-smearing correction ($\sigma_{int}/\sigma_{obs}$) has a mean and median value of 0.77 and 0.79 respectively for the isolated field sample. \\
 
+\noindent
 To test the robustness of our beam-smearing correction approach we also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{1/2}/R_{psf}$, detailed in Johnson et al.
@@
 These correction factors were applied to $V_{BS}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
-When following this approach, for the isolated field sample, the derived $V_{C}$ values agree with our own corrections to within $\simeq10\%$, and the $\sigma_{int}$ values to within $\simeq5\%$ which is within the errors on these quantities.
+When following this approach, for the isolated field sample, the derived $V_{C}$ values agree with our own corrections to within $\simeq10\%$, and the $\sigma_{int}$ values to within $\simeq5\%$, which is within the errors on these quantities.
 This confirmed that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\simeq0.9$ KROSS methods \citep{Harrison2017}.
@@
  \hline
-ID & $V_{obs}$(kms$^{-1}$) & $V_{C}$(kms$^{-1}$) & $\sigma_{obs}$(kms$^{-1}$) & $\sigma_{int}$(kms$^{-1}$) & $V_{C}/\sigma_{int}$ & PA$_{kin}^{\circ}$ & Class$^{a}$ \\
+ID & $V_{obs}$(km\,s$^{-1}$) & $V_{C}$(km\,s$^{-1}$) & $\sigma_{obs}$(km\,s$^{-1}$) & $\sigma_{int}$(km\,s$^{-1}$) & $V_{C}/\sigma_{int}$ & PA$_{kin}^{\circ}$ & Class$^{a}$ \\
  \hline
@@
 
+\noindent
 In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identified signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
@@
 We keep the KDS galaxies without {\em HST} coverage on the basis that we do not identify double components in the galaxy continuum maps. 
-In the kinematic grids throughout \ref{fig:merger_galaxies} (as well as the bottom grid in \ref{fig:main_body_kinematic_grids}) we present the {\em HST} imaging, kinematic maps and 1-dimensional kinematic extractions for the KDS merger candidates in both the field and cluster environments.
+In the kinematic grids throughout \ref{fig:merger_galaxies} (as well as the bottom grid in \ref{fig:main_body_kinematic_grids}) we present the {\em HST} imaging, kinematic maps and one-dimensional kinematic extractions for the KDS merger candidates in both the field and cluster environments.
 
@@
 
+\noindent
 The isolated field sample was further divided into 13/38 rotation-dominated galaxies (34\% with respect to full field sample) and 19/38 dispersion-dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}), with the remaining 6/38 (16\%) classified as mergers.
@@
 The connection has been studied extensively at low redshift \citep[e.g.][]{Bell2000a,Rhee2003,Reyes2011} with fits to late-type, rotating galaxies in the $V_{C}-M_{\star}$ plane having a well-defined slope and normalisation.
-Observing this `stellar mass Tully-Fisher relation' at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies \citep[e.g.][]{Dubois2014a,Vogelsberger2014b,Schaye2015}.
+Observing this `stellar mass Tully-Fisher relation' at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies \citep[e.g.][]{Dubois2014,Vogelsberger2014b,Schaye2015}.
 In principle, studying whether the stellar mass Tully-Fisher relation evolves with redshift gives us information about when galaxies accumulate their stellar mass and rotation velocities.
@@
 
+\noindent
 We plot the relationship between rotation velocity and stellar mass for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
@@
 The rotation-dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\simeq0.9$ relation, but with a tendency to lie below the relation.
-When considered alone, the mean velocity of the rotation-dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=9.8$ is $\simeq0.05$ dex beneath the KROSS relation at the same mass.
+When considered alone, the mean velocity of the rotation-dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}km\,s^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=9.8$ is $\simeq0.05$ dex beneath the KROSS relation at the same mass.
 The dispersion-dominated KDS galaxies sit clearly separated and below the $z\simeq0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\simeq0.9$ dispersion-dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
@@
 
+\noindent
 Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
@@
 
+\noindent
 Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\simeq0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
@@
     \caption{{\it Left:} We plot the intrinsic velocity dispersion against stellar mass for the rotation and dispersion-dominated isolated field sample galaxies, along with the AMAZE Clean ($z\simeq3$) sample.
-    The $\sigma_{int}$ values are typically distributed between $40-90kms^{-1}$ and show no clear correlation with stellar mass, highlighting the complicated relationship between these two quantities.
+    The $\sigma_{int}$ values are typically distributed between $40-90km\,s^{-1}$ and show no clear correlation with stellar mass, highlighting the complicated relationship between these two quantities.
     {\it Right:} We present a compilation of literature $\sigma_{int}$ values plotted against redshift for surveys spanning $0 < z < 4$.
-    The mean $\sigma_{int}$ values increase from $\simeq15kms^{-1}$ in the local universe to $> 70kms^{-1}$ at $z > 3$.
+    The mean $\sigma_{int}$ values increase from $\simeq15km\,s^{-1}$ in the local universe to $> 70km\,s^{-1}$ at $z > 3$.
     The symbol convention is the same as in the right panel of Figure \protect\ref{fig:tf_relation}.
-    The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values and in each case for $V_{C} = 125kms^{-1}$.
+    The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values and in each case for $V_{C} = 125km\,s^{-1}$.
     These are intended as indicators of the way in which $\sigma_{int}$ evolves in galaxies in different mean $M_{\star}$, where this on average gives an indication of the extent to which the stellar population has been accumulated, which may provide increased stability for an extended rotating disk.
@@
 
+\noindent
 The right panel of Figure \ref{fig:tf_relation} indicates that the $V_{C}$ distributions for the comparison and KDS isolated field samples are wide, reflecting the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
-The isolated field sample mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$.
-However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}kms^{-1}$ respectively, suggesting that averaging over a sample containing a large number of dispersion dominated galaxies is bringing the averages down.
+The isolated field sample mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}km\,s^{-1}$ and $57.0^{+6.6}_{-6.3}km\,s^{-1}$.
+However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}km\,s^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}km\,s^{-1}$ respectively, suggesting that averaging over a sample containing a large number of dispersion dominated galaxies is bringing the averages down.
 
@@
 
+\noindent
 In a rotationally supported system, the circular velocity is set by the requirement to support the total mass in the system, i.e.
@@
 $V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
-Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
+Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95km\,s^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
 This value is above the mean and median values of the isolated field sample, but comparable to the mean and median of the rotation dominated galaxies, suggesting that rotation in these systems could support at most the stellar mass of the galaxy.
@@
 
+\noindent
 We proceed to consider the cause of the high number of dispersion-dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
@@
 
+\noindent
 We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high redshift.
-The beam-smearing corrected $\sigma_{int}$ values, with distribution median, 16th percentile and 84th percentile equal to $71.0kms^{-1}$, $48.0kms^{-1}$ and $85.4kms^{-1}$ respectively, are larger than in the local universe where typically $\sigma_{int} = 10-20kms^{-1}$ \citep{Epinat2008a} (see \cref{subsubsec:sigma_evolution} and \cref{sec:discussion} for a discussion).
+The beam-smearing corrected $\sigma_{int}$ values, with distribution median, 16th percentile and 84th percentile equal to $71.0km\,s^{-1}$, $48.0km\,s^{-1}$ and $85.4km\,s^{-1}$ respectively, are larger than in the local universe where typically $\sigma_{int} = 10-20km\,s^{-1}$ \citep{Epinat2008a} (see \cref{subsubsec:sigma_evolution} and \cref{sec:discussion} for a discussion).
 Generally the dispersion-dominated galaxies have higher $\sigma_{int}$ values, however the rotation-dominated galaxies also span the full distribution width.
@@
 In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
-The values increase sharply from $\sigma_{int}\simeq10-20kms^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60kms^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90kms^{-1}$ at $z\simeq3$, but with a wide range of values observed at each redshift.
+The values increase sharply from $\sigma_{int}\simeq10-20km\,s^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60km\,s^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90km\,s^{-1}$ at $z\simeq3$, but with a wide range of values observed at each redshift.
 There appears to be a trend for the surveys with lower average stellar mass (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) to have higher velocity dispersions than the surveys with larger average stellar mass (GHASP, KMOS$^{3D}$, SINS).
@@
 
+\noindent
 These new data from the KDS sustain the observation that velocity dispersion is increasing with redshift and provide strong constraints on the internal dynamics of typical star-forming galaxies between $z=3-3.8$.
@@
 
+\noindent
 The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation-dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}/M_{\odot}) > 9.5$ which are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.
@@
 
+\noindent
 The rotation-dominated fraction, traced simply by the $V_{C}/\sigma_{int}$ ratio inferred from ionised gas emission lines, drops from $\simeq100\%$ of galaxies in the local universe to $\simeq2/3$ of galaxies in the $z\simeq1-2$ universe and to $\simeq1/3$ above $z\simeq3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
@@
     \caption{{\it Left:} We plot the $\sigma_{int}$ values for the comparison samples as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample).
-    The grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 70-200kms^{-1}$ respectively (corresponding roughly to the velocity range spanned by galaxies in the comparison samples).
+    The grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 70-200km\,s^{-1}$ respectively (corresponding roughly to the velocity range spanned by galaxies in the comparison samples).
     The shifted points are in line with the scenario whereby the sample averaged velocity dispersions increase with redshift as a result of increasing average gas fractions. 
@@
 
-In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties: gas fraction, $f_{gas}$ gas depletion timescale, $t_{depl}$, and specific star-formation rate, sSFR.
+\noindent
+In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties: gas fraction, $f_{gas}$ gas depletion timescale, $t_{dep}$, and specific star-formation rate, sSFR.
 The function describing the evolution of the velocity dispersion with redshift is shown below in Equation \ref{eq:sigma_increase}, where $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964}, and {\it a} is a dimensionless parameter which depends on the assumed distribution of gas and gravitational potential \cite{ForsterSchreiber2006}.
@@
 
-The gas fraction is a function of gas depletion timescale, with an assumed redshift dependence, and specific star-formation rate, with an assumed mass and redshift dependence (see \citealt{Wisnioski2015} Equations 3-6).
+\noindent
+The gas fraction is a function of gas depletion timescale, with an assumed redshift dependence, and specific star-formation rate, with an assumed mass and redshift dependence (see \citealt{Wisnioski2015} Equations 3-6, summarised below by Equations \ref{eq:gas_fractions} and \ref{eq:coefficients}).
+
+\begin{equation}\label{eq:gas_fractions}
+\begin{aligned}
+    f_{gas} & = \frac{1}{1 + \left(t_{dep}sSFR\right)^{-1}} \\[1ex]
+    & = \frac{1}{1 + \left(1.5\times10^{a(M_{\star})}\left(1 + z \right)^{b(M_{\star}) + \alpha}\right)^{-1}}
+\end{aligned}
+\end{equation}
+
+\begin{equation}\label{eq:coefficients}
+\begin{aligned}
+   & a(M_{\star}) = -10.73 + \frac{1.26}{1 + {\it e}^{\left(10.49 - logM_{\star}\right)/(-0.25)}} \\[1ex]
+   & b(M_{\star}) = 1.85 + \frac{1.57}{1 + {\it e}^{\left(10.35 - logM_{\star}\right)/(0.19)}}
+\end{aligned}
+\end{equation}
+
+\noindent
 Using observed constraints for these properties from \cite{Tacconi2013} and \cite{Whitaker2014} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \citealt{Wisnioski2015} Figures 10 and 11).
@@
 In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot Equation \ref{eq:sigma_increase} for different input mass values (roughly spanning the mass range of the comparison samples), using the updated depletion time scaling relation from \cite{Tacconi2017} (i.e.
-$t_{depl} \propto (1 + z)^{-0.57}$).
-The Equation $\sigma(z,M_{\star})\propto f_{gas}(z,M_{\star})$ is scaled so that the lowest mass track conincides with the KDS datapoint, finding a proportionality constant $V_{C}Q_{crit}/a = 90.5kms^{-1}$.
+$t_{dep} \propto (1 + z)^{-0.57}$, meaning $alpha=0.57$ in Equation \ref{eq:gas_fractions}).
+The Equation $\sigma(z,M_{\star})\propto f_{gas}(z,M_{\star})$ is scaled so that the lowest mass track conincides with the KDS datapoint, finding a proportionality constant $V_{C}Q_{crit}/a = 90.5km\,s^{-1}$.
 $Q_{crit} = 1.0$ for a quasi-stable thin disk e.g.
-\citealt{ForsterSchreiber2006,Burkert2010}) and {\it a} = $\sqrt{2}$ for a disk with constant rotation velocity \citep{Wisnioski2015}, and assuming these values gives $V_{C} = 128kms^{-1}$ as a best match to our data.
+\citealt{ForsterSchreiber2006,Burkert2010}) and {\it a} = $\sqrt{2}$ for a disk with constant rotation velocity \citep{Wisnioski2015}, and assuming these values gives $V_{C} = 128km\,s^{-1}$ as a best match to our data.
 This is larger than the intrinsic rotation velocities in the isolated field sample, although this could be a result of the assumptions for both $Q_{crit}$ and {\it a}. \\
 
+\noindent
 In this model the velocity dispersions increase more steeply with increasing stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
@@
 We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}).
-In both panels, the grey line denotes the model prediction using $Q_{crit} = 1.0$, {\it a} = $\sqrt{2}$ and $V_{C} = 128kms^{-1}$ and the light grey shaded region encompasses the model predictions with lower and upper bounds defined with $V_{C} = 70-200kms^{-1}$ respectively (spanning the velocity values of galaxies in the comparison samples).
-\\
-
+In both panels, the grey line denotes the model prediction using $Q_{crit} = 1.0$, {\it a} = $\sqrt{2}$ and $V_{C} = 128km\,s^{-1}$ and the light grey shaded region encompasses the model predictions with lower and upper bounds defined with $V_{C} = 70-200km\,s^{-1}$ respectively (spanning the velocity values of galaxies in the comparison samples).
+\\
+
+\noindent
 Although the details of the coefficients of Equation \ref{eq:sigma_increase} are unclear (i.e.
@@
 
+\noindent
 In summary, the isolated field sample galaxies are diverse and kinematically immature, with $\simeq2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
@@
 \begin{itemize}
-    \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $V_{C} = 76.7^{+4.9}_{-4.5}kms^{-1}$ and $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$ (right panels of Figures \ref{fig:tf_relation} and \ref{fig:sigma_and_v_sigma_w_redshift} respectively).
+    \item We use a fractional error weighted mean to derive the mean kinematic parameters of the KDS isolated field sample of $V_{C} = 76.7^{+4.9}_{-4.5}km\,s^{-1}$ and $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$ (right panels of Figures \ref{fig:tf_relation} and \ref{fig:sigma_and_v_sigma_w_redshift} respectively).
     Rotation (dispersion) dominated galaxies are defined as those with $V_{C}/\sigma_{int} > (<) 1$.  
@@
     The dispersion-dominated galaxies scatter below the trend, with the same slope as the rotation-dominated galaxies.
-    \item When considering the rotation-dominated galaxies alone the mean and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}kms^{-1}$ respectively, which are roughly equivalent to a simple lower limit virial theorem calculation using the mean mass and half-light radius of the sample.
+    \item When considering the rotation-dominated galaxies alone the mean and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}km\,s^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}km\,s^{-1}$ respectively, which are roughly equivalent to a simple lower limit virial theorem calculation using the mean mass and half-light radius of the sample.
     This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in the system \citep[e.g.][]{Burkert2010}.  
@@
 
+OJT acknowledges the support of STFC under grant number ST/L000784/1.
 MC and OJT acknowledge the KMOS team and all the personnel of the European Southern Observatory Very Large Telescope for outstanding support during the KMOS GTO observations.
@@
  DYNAMO & 0.1 & 10.3    &       $183.0^{+1.0}_{-1.0}$ \xmark  & $164.0^{+3.0}_{-5.0}$   &  $45.9^{+0.3}_{-0.3}$ \xmark & $39.0^{+0.9}_{-1.0}$ & $5.1^{+0.2}_{-0.2}$  \xmark &           $4.6^{+0.2}_{-0.2}$ &               $0.96^{+0.02}_{-0.02}$  \xmark   \\[1ex]
- MUSE+KMOS & 0.65 & 9.4 &       $103.8^{+1.5}_{-1.6}$ \cmark  & $73.0^{+2.5}_{-2.5}$    &  $40.0^{+0.3}_{-0.3}$ \cmark & $32.0^{+0.6}_{-0.5}$ & $2.9^{+0.1}_{-0.1}$  \cmark &           $2.21^{+0.1}_{-0.1}$&               $0.83^{+0.02}_{-0.02}$  \cmark   \\[1ex]
+ MUSE+KMOS & 0.65 & 9.4 &       $103.8^{+1.5}_{-1.6}$ \xmark  & $73.0^{+2.5}_{-2.5}$    &  $40.0^{+0.3}_{-0.3}$ \cmark & $32.0^{+0.6}_{-0.5}$ & $2.9^{+0.1}_{-0.1}$  \xmark &           $2.21^{+0.1}_{-0.1}$&               $0.83^{+0.02}_{-0.02}$  \xmark   \\[1ex]
  $^{*}$KROSS & 0.9 & 9.9 &      $117.0^{+4.0}_{-4.0}$ \cmark  & $109.0^{+5.0}_{-5.0}$   &  -                    \cmark & -                    & $3.1^{+0.2}_{-0.2}$  \cmark &           $2.4^{+0.1}_{-0.1}$ &               $0.81^{+0.05}_{-0.05}$  \cmark   \\[1ex]
@@
  MASSIV & 1.2 & 10.2 &          $132.1^{+10.4}_{-8.2}$ \cmark & $103.0^{+13.4}_{-11.0}$ &  $61.8^{+3.8}_{-4.2}$ \cmark & $52.0^{+5.2}_{-4.7}$ & $2.4^{+1.4}_{-0.9}$  \cmark &           $2.0^{+0.3}_{-0.2}$ &               $0.67^{+0.06}_{-0.06}$  \cmark   \\[1ex]
- MUSE+KMOS & 1.25 & 9.8 &       $75.5^{+3.0}_{-3.3}$   \cmark & $54.0^{+3.0}_{-2.8}$    &  $42.0^{+0.5}_{-0.5}$ \cmark & $29.5^{+1.0}_{-1.0}$ & $2.2^{+1.0}_{-1.0}$  \cmark &           $1.59^{+0.1}_{-0.1}$&               $0.78^{+0.04}_{-0.04}$  \cmark   \\[1ex]
+ MUSE+KMOS & 1.25 & 9.8 &       $75.5^{+3.0}_{-3.3}$   \xmark & $54.0^{+3.0}_{-2.8}$    &  $42.0^{+0.5}_{-0.5}$ \cmark & $29.5^{+1.0}_{-1.0}$ & $2.2^{+1.0}_{-1.0}$  \xmark &           $1.59^{+0.1}_{-0.1}$&               $0.78^{+0.04}_{-0.04}$  \xmark   \\[1ex]
  SINS(C09) & 2.0 & 10.6 &       $232.0^{+12.8}_{-12.7}$\cmark & $240.0^{+18.0}_{-17.2}$ &  $51.2^{+8.0}_{-7.9}$ \cmark & $42.5^{+9.1}_{-8.5}$ & $5.0^{+0.9}_{-1.0}$  \xmark &           $4.7^{+1.0}_{-1.0}$ &               1.0                     \cmark   \\[1ex]
@@
 The observations span the redshift range $0.2 < z < 1.6$ and we split the data into two subsets with $z < 1.0$ (129 galaxies with mean redshift of $z = 0.65$, mean stellar mass of $log(M_{\star}/M_{\odot})=9.80$) and $z > 1.0$ (50 galaxies with mean redshift of $z = 1.25$, mean stellar mass $log(M_{\star}/M_{\odot})=9.80$).
-The reported velocities are extracted at $3R_{D}$, comparable to the extraction radius for the KDS sample and the intrinsic velocity dispersions have been corrected for beam-smearing effects.
-The kinematic properties computed from the tabulated data in this survey are directly comparable to the KDS, reflected by the filled symbols throughout the plots in \cref{sec:results}.
+The reported velocities are extracted at $3R_{D}$, comparable to the extraction radius for the KDS sample, but these have not been beam-smearing corrected.
+The intrinsic velocity dispersions have been corrected for beam-smearing effects.
+For this reason the velocity dispersions are deemed directly comparable to the KDS, reflected by the filled symbols throughout the plots in \cref{sec:results}, but the points involving velocity measurements are represented by hollow symbols due to the lack of a beam-smearing correction.
 
@@
 
+\noindent
 $V_{C}$ values for rotation-dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion-dominated galaxies using the velocity width.
@@
 
+\noindent
 It is unclear whether the $V_{C}$ values for the full sample from FS09 are directly comparable, but we make use of the tabulated values for completeness and plot these with filled symbols throughout \cref{sec:results}.
@@
 
+\noindent
 Also, for 5 galaxies in G11, $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error on $V_{C}$ equal to 1 when computing the sample averages.
-The $\sigma_{int}$ errors for individual galaxies are generally very small, and for 3 galaxies the $\sigma_{int}$ value is consistent with 0 kms$^{-1}$.
-For the mean value computations we set these equal to the SINFONI resolution limit of 30 kms$^{-1}$.
-A total of 6/11 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0 kms$^{-1}$, which we refer to as the AMAZE `Unconstrained' sample and represent these with hollow symbols throughout the plots in \cref{sec:results}.
-This Unconstrained sample also contains the galaxy s\_sa22a-M38, common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346 kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
+The $\sigma_{int}$ errors for individual galaxies are generally very small, and for 3 galaxies the $\sigma_{int}$ value is consistent with 0 km\,s$^{-1}$.
+For the mean value computations we set these equal to the SINFONI resolution limit of 30 km\,s$^{-1}$.
+A total of 6/11 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0 km\,s$^{-1}$, which we refer to as the AMAZE `Unconstrained' sample and represent these with hollow symbols throughout the plots in \cref{sec:results}.
+This Unconstrained sample also contains the galaxy s\_sa22a-M38, common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346 km\,s^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
 We use tabulated values from the full analysed sample of 11 galaxies, plotting these with hollow symbols throughout \cref{sec:results} as a consequence of the caveats listed above.
@@
 
+\noindent
 This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, however, despite this diversity, over the past decade the studies appear to be converging on `modelling out' the effects of beam-smearing using similar approaches (e.g.
@@
 The $V_{C}/\sigma_{int} = 1$ line divides the galaxies classified as rotation-dominated and dispersion-dominated.
-The galaxy s\_sa22a-M38, classified here as a merger but classified in \protect\cite{Gnerucci2011} as a rotating galaxy with $V_{C} = 346 kms^{-1}$ is marked on the plot.}
+The galaxy s\_sa22a-M38, classified here as a merger but classified in \protect\cite{Gnerucci2011} as a rotating galaxy with $V_{C} = 346 km\,s^{-1}$ is marked on the plot.}
 \label{fig:intrinsic_parameters}
@@
 
+\noindent
 The upper and lower errors on the $\sigma_{int}$ are calculated using a similar approach.
-To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50 kms^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40 kms^{-1}$ and $\sigma_{int} = 80 kms^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
+To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50 km\,s^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40 km\,s^{-1}$ and $\sigma_{int} = 80 km\,s^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
 Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-When assuming the broader $\sigma_{int} = 80 kms^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.
-Conversely, assuming $\sigma_{int} = 40 kms^{-1}$ increases the beam-smearing.
+When assuming the broader $\sigma_{int} = 80 km\,s^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.
+Conversely, assuming $\sigma_{int} = 40 km\,s^{-1}$ increases the beam-smearing.
 We calculate the minimum and maxmimum intrinsic velocity dispersion, $\sigma_{int-84-40}$ and $\sigma_{int-16-80}$, using equations \ref{eq:sig_84_40} and \ref{eq:sig_16_80} respectively:
@@
 
+\noindent
 where $\sigma_{bs-84-40} = \sigma_{model-84-40} - 40$ and $\sigma_{bs-16-80} = \sigma_{model16-80} - 80$ are the beam-smeared maps.
@@
 
+\noindent
 with $\bar{\sigma}_{\sigma_{obs}}$ equal to the average of the velocity dispersion measurement errors.

### 2017-04-07 paper.tex
Final finished draft before submission - after chris final comments

@@
 % Keep the title short and informative.
-\title[KDS I: dynamical properties of 77 $z\simeq3.5$ galaxies]{The KMOS Deep Survey (KDS) I: dynamical measurements of typical star forming galaxies at $z\simeq3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
+\title[KDS I: dynamical properties of 77 $z\simeq3.5$ galaxies]{The KMOS Deep Survey (KDS) I: dynamical measurements of typical star-forming galaxies at $z\simeq3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory.
 Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)}}
@@
 These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
-The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\simeq3$.
-However, only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
+The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, revealing that the increasing average $\sigma_{int}$ with increasing redshift, reported for $z\lesssim2$, continues out to $z\simeq3.5$.
+Only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
 After carefully selecting comparable star-forming samples at multiple epochs, we find that the rotation-dominated fraction evolves with redshift with a $z^{-0.2}$ dependence. 
@@
 $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
-These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and may provide significant pressure support against gravity on the galactic disk scale.
+These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by a combination of the increasing gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and which may provide significant pressure support against gravity on the galactic disk scale.
 \end{abstract}
@@
 For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
-This correlation, or `main-sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
+This correlation, or `main-sequence', underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
 The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep[e.g.][]{Madau_2014,Khostovan2015}.
 At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
-This assumes that high redshift main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
+This assumes that high redshift, main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
 how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
@@
 stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2017,Qu2017}.
-To account for the growing number density of quiescent galaxies from $z\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e.
+To account for the growing number density of quiescent galaxies from $z\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut-off star-formation within main-sequence galaxies (i.e.
 quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.
@@
 Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
-The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collapse, mergers and outflows e.g.
+The observed dynamical properties of galaxies contain information about the transfer of angular momentum between their dark matter halos and baryons, and the subsequent dissipation of this angular momentum (through gravitational collapse, mergers and outflows e.g.
 \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulations to reproduce.
@@
 Random motions within the interstellar medium of SFGs appear to increase with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
-This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star-formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
+This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star-formation rates (sSFRs) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
 
@@
 \noindent
-In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
+In this paper we present new results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
 With this survey, we aim to complement existent studies by providing deep IFS data for the largest number of galaxies at this redshift.
-By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
+By making use of KMOS (with integration times of 7.5-9 hours), we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
 In order to interpret the evolution of the physical properties of typical star-forming galaxies we have carefully constructed a set of comparison samples spanning $0 < z < 3$.
@@
 The key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
-We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and a `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
-To achieve this we require very deep exposure times in excess of 7 hours on source to reach the signal to noise required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate signal to noise across several ionised emission lines within individual spatial pixels (spaxels).
+We seek to probe both a `field' environment in which the density of galaxies is typical for this redshift and a `cluster' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
+To achieve this we require very deep exposure times in excess of 7 hours on source to reach the signal-to-noise required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate signal-to-noise across several ionised emission lines within individual spatial pixels (spaxels).
 Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.
@@
 Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
-From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal to noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
+From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal-to-noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
 To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a wealth of imaging and spectroscopic data.
@@
  \hline
- \scriptsize{\bf GOODS-S-P1(FIELD)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & {\it K} & 32.4 & 0.50 \\
-\scriptsize{\bf GOODS-S-P2(FIELD)} & 03:32:32.217 & $-$27:43:08.000 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & {\it K} & 31.8 & 0.52 \\
-\scriptsize{\bf SSA22-P1(CLUSTER)} & 22:17:11.867 & $+$00:15:44.700 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & {\it HK} & 38.1 & 0.62 \\
-\scriptsize{\bf SSA22-P2(FIELD)} & 22:17:35.120 & $+$00:09:30.500 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & {\it HK} & 27.8 & 0.57 \\
+ \scriptsize{\bf GOODS-S-P1(field)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & {\it K} & 32.4 & 0.50 \\
+\scriptsize{\bf GOODS-S-P2(field)} & 03:32:32.217 & $-$27:43:08.000 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & {\it K} & 31.8 & 0.52 \\
+\scriptsize{\bf SSA22-P1(cluster)} & 22:17:11.867 & $+$00:15:44.700 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & {\it HK} & 38.1 & 0.62 \\
+\scriptsize{\bf SSA22-P2(field)} & 22:17:35.120 & $+$00:09:30.500 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & {\it HK} & 27.8 & 0.57 \\
 
@@
 
-Two of the three FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
+Two of the three field environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
 We selected targets from the various spectroscopic campaigns which have targeted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
@@
 \subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
-A single CLUSTER environment pointing was selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z\simeq3.09$.
+A single cluster environment pointing was selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z\simeq3.09$.
 Hundreds of spectroscopic redshifts have been confirmed for these LBGs with follow-up observations using LRIS \citep{Shapley2003,Nestor2013}.
 A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow-band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011,Yamada2012a} and archival {\em HST ACS} and {\it WFC3} imaging provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
-Fortunately at $z\simeq3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the {\it K}-band which is free from OH features and so for the CLUSTER environment pointing we filled the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
-
-We also added a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical of the field environment (SSA22-P2).
+Fortunately at $z\simeq3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the {\it K}-band which is free from OH features and so for the cluster environment pointing we filled the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).
+
+We also added a further field environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical of the field environment (SSA22-P2).
 In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
-In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}.
+In summary, we have chosen three field environment pointings and a single cluster environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}.
 \footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}
@@
 \subsubsection{Observations}\label{subsubsec:Obs}
+
+To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, allowing both dynamical and chemical abundance measurements.
+The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however, due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously.
+\\
+
+\noindent
+We prepared each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
+For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopted the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
+This procedure allowed for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\
+
+\noindent
+The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
+In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\simeq0.5^{\prime\prime}$ and for the SSA22-cluster and SSA22-field pointings the {\it K}-band seeing ranged between $\simeq0.55-0.65^{\prime\prime}$.
+We observed 17-21 $z\simeq3.5$ targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
+\\
+
+\noindent
+This paper is concerned with the spatially-resolved kinematics of the KDS galaxies.
+Consequently, we now focus exclusively on the spatially-resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
+The details of the {\it H}-band data reduction and corresponding metallicity analyses will be described in a future study.
+
+\subsubsection{Data reduction}\label{subsubsec:datareduction}
 
@@
     {\it Right:} We plot the location of the KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
-    The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
+    The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares, as a reference for the typical relationship between SFR and $M_{\star}$.
     The black solid line and the dashed line show the $z\simeq2.5$ broken power-law and quadratic fit to the main-sequence respectively, described in \protect\cite{Whitaker2014}.
@@
 
-To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, allowing both dynamical and chemical abundance measurements.
-The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously.
-\\
-
-\noindent
-We prepared each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
-For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopted the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
-This procedure allowed for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\
-
-\noindent
-The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
-In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\simeq0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the {\it K}-band seeing ranged between $\simeq0.55-0.65^{\prime\prime}$.
-We observed 17-21 $z\simeq3.5$ targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB).
-\\
-
-\noindent
-This paper is concerned with the spatially-resolved kinematics of the KDS galaxies.
-Consequently, we now focus exclusively on the spatially-resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
-The details of the {\it H}-band data reduction and corresponding metallicity analyses will be described in a future study.
-
-\subsubsection{Data reduction}\label{subsubsec:datareduction}
-
 The data reduction process primarly made use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \citealt{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
@@
 
+\noindent
 Standard star observations were carried out on the same night as the science observations and were processed in an identical manner to the science data.
@@
 \subsection{Stellar masses and SFRs}\label{subsec:stellar_masses_and_sfrs}
+
 The wealth of ancillary data in both fields allows for a consistent treatment of the SED modelling, providing physical properties which are directly comparable between the cluster and field environments.
@@
 In GOODS-S, we have compared our derived stellar masses to those in \cite{Santini2015} (which presents an average result from 10 different sets of analyses), finding a median difference between the two sets of values of $\Delta \log(M_{\star}/{\rm M}_{\odot}) = 0.009$.
-We note also that using the star-forming templates described in \cite{Wuyts2011} typically leads to stellar masses which are 0.2 dex higher.
+We also note that using the star-forming galaxy templates described in \cite{Wuyts2011} typically leads to stellar masses which are 0.2 dex higher.
 
@@
 This is a commonly used diagnostic plane for selecting star-forming and quiescent galaxies \citep[e.g.][]{Williams2009,Brammer2011,Whitaker2012a} with the age gradients of the stars within quiescent galaxies placing them in a different region of the plane to those which are actively forming stars.
-The selection criteria defined in \cite{Whitaker2012a} (which evolve only gently with redshift) separate quiescent and star-forming regions, which are indicated by the black wedge.
+The selection criteria defined in \cite{Whitaker2012a} (which evolve only gently with redshift), separate quiescent and star-forming regions, which are indicated by the black wedge.
 We also make use of the rest-frame colours of $\simeq4000$ primarily star-forming galaxies located in GOODS-S between $3.0 < z < 3.8$ (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
@@
 \begin{equation}\label{eq:speagle_ms}
-logSFR(M_{\star}, t) = (0.84 - 0.026 \times t)logM_{\star} - (6.51 - 0.11 \times t)
+logSFR(M_{\star}, t) = (0.84 - 0.026 \times t)log(M_{\star}/{\rm M}_{\odot}) - (6.51 - 0.11 \times t)
 \end{equation}
@@
 \subsubsection{Sample summary}\label{subsubsec:sample_summary}
-We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey and have derived $M_{\star}$ values and SFRs from SED modelling.
+We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey.
+By processing the observations, we have constructed a datacube for each of these galaxies, finding integrated [O~{\sc III}]$\lambda$5007 in 62/77 targets.
+We have also derived $M_{\star}$ values and SFRs from SED modelling, finding that these values place the KDS galaxies into regions of parameter space spanned by typical star-forming galaxies at this redshift.
 Three KMOS pointings cover the field environment and one pointing covers a cluster environment at the heart of the SSA22 protocluster, and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
@@
 Lehmer: PID 13844; P.I.
-Mannucci: PID 11735) and the {\it ACS F814W} band, tracing $\simeq$ 2000$\AA$ light at $z\simeq3.5$ (P.I.
+Mannucci: PID 11735) and the {\it ACS F814W} band, tracing $\simeq$ 2500$\AA$ light at $z\simeq3.1$ (P.I.
 Chapman: PID 10405; P.I.
@@
 Siana: PID 12527).
-The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the {\it F160W} coverage is concentrated on the SSA22-CLUSTER and so we resorted to the bluer {\it ACS F814W} data to derive morphological parameters in SSA22-P2 (The galaxies with and without {\em HST} coverage are listed in Table \ref{tab:phys-props}).
-\\
-
-\noindent
-We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT} and then extracted postage stamp regions around the galaxies in the KDS sample.
+The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the {\it F160W} coverage is concentrated on the SSA22-cluster and so we resorted to the bluer {\it ACS F814W} data to derive morphological parameters in SSA22-P2 (also in SSA22-P2, 4 galaxies do not have any {\em HST} coverage as indicated in Table \ref{tab:phys-props}).
+\\
+
+\noindent
+We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT}, and then extracted postage stamp regions around the galaxies in the KDS sample.
 At this redshift, the galaxies are more compact and generally we could not resolve more complicated morphological features such as spiral arms and bars and so we followed the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of $n=1$.
-In the {\it F160W} band the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the {\it F814W} band we used the pure Tiny Tim {\it ACS} high-resolution PSF model.
+In the {\it F160W} band, the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the {\it F814W} band we used the pure Tiny Tim {\it ACS} high-resolution PSF model.
 During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, were free to vary.
@@
 Additionally, 22 GOODS-S objects were also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is $n=1.2$.
-The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors were applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2}\simeq1.68 R_{D}$ (see \cref{subsec:KROSS}).
+The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors were applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2}\simeq1.68 R_{D}$ (see Appendix \ref{subsec:KROSS}).
 \\
@@
 Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
-There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we also discuss the approach followed to recover the morphological parameters for these galaxies.
+In each of the following sections we also discuss the approach followed to recover the morphological parameters for the galaxies without {\em HST} coverage.
 The interpretation of the sample as a whole is not affected by the small number of galaxies without {\em HST} imaging.
@@
 
-\subsubsection{Inclination angle}\label{subsubsection:inclination_angle}
+\subsubsection{Inclination angles}\label{subsubsection:inclination_angle}
 We used the derived $b/a$ values to determine galaxy inclination angles.
-As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid, the inclination angle can be recovered from the observed axial ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axial ratio of an edge-on system.
+As suggested in \cite{Holmberg1958}, by modelling the disk galaxies as an oblate spheroid, the inclination angle can be recovered from the observed axis ratio as shown in Equation \ref{eq:holmberg_i}, where $\frac{b}{a}$ is the ratio of minor to major axis of an ellipse fit to the galaxy profile on the sky, $i$ is the inclination angle and $q_{0}$ is the axis ratio of an edge-on system.
 
@@
 
-\subsubsection{Position angle}\label{subsubsection:position_angle}
+\subsubsection{Position angles}\label{subsubsection:position_angle}
 The second {\tt GALFIT} parameter was $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
@@
 \subsubsection{Half-light radii}\label{subsubsection:half-light_radii}
-The half-light radius, $R_{1/2}$, provides an indication of the disk sizes and hence gave us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
+The half-light radius, $R_{1/2}$, provides an indication of the disk sizes, and hence gave us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
 As discussed throughout the introduction and in Appendix \ref{app:comparison_samples}, methods used to derive the intrinsic rotation velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
@@
 \noindent
-To measure $R_{1/2}$ for the 4 galaxies without {\em HST} coverage we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
+To measure $R_{1/2}$ for the 4 galaxies without {\em HST} coverage, we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
 We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening.
@@
 We proceeded to extract 2D kinematic measurements from the 62 KDS datacubes detected in integrated [O~{\sc III}]$\lambda$5007 emission by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
-The sample was then refined to galaxies which are spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission in order to make dynamical measurements.
+The sample was then refined to galaxies which are spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission line in order to make dynamical measurements.
 We also describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam-smearing corrections for each galaxy.
-We made use of the imaging data described in the previous sections to reduce the number of free parameters in the model, an approach which is necessary when working in this signal to noise regime.
+We made use of the imaging data described in the previous sections to reduce the number of free parameters in the model, an approach which is necessary when working in this signal-to-noise regime.
 
@@
 These properties are extracted via modelling emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
-We concentrated solely on the [O~{\sc III}]$\lambda$5007 emission line which always had signal to noise higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and was detected over a larger area of each IFU.
+We concentrated solely on the [O~{\sc III}]$\lambda$5007 emission line which always had signal-to-noise higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and was detected over a larger area of each IFU.
 \\
@@
 This truncated spectrum was then used in the fitting procedure for each spaxel.
-The width of the extraction region was large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky line residuals.
+The width of the extraction region was large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky-line residuals.
 A single gaussian model was fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
@@
 This boundary constraint was chosen to mitigate edge effects, where the noise increased sharply due to fewer individual exposures constituting the final stack in these regions.
-The final noise value was then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation \ref{eq:noise} where $F_{i,background}$ are the flux values across the spatial regions containing no object flux and the spectral extraction region and $N_{m}$ denotes noise estimated from masking the datacube.
+The final noise value was then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation \ref{eq:noise}, where $F_{i,background}$ are the flux values across the spatial regions containing no object flux in the spectral extraction region, and $N_{m}$ denotes the noise estimated from masking the datacube.
 
@@
 \noindent
-The signal in each spaxel was taken as the sum of the flux values across the extraction region, $F_{i,object}$, as shown in Equation \ref{eq:signal} where S denotes the signal.
+The signal in each spaxel was taken as the sum of the flux values across the spectral extraction region, $F_{i,object}$, as shown in Equation \ref{eq:signal}, where S denotes the signal.
 
@@
 \noindent
-From the gaussian-fit we recovered the centre, $\lambda_{g}$, the width, $\sigma_{g}$ and the area, $F_{g}$.
-The velocity was computed from $\lambda_{g}$ using Equation \ref{eq:velocity_comp} and the velocity dispersion was computed from $\sigma_{g}$ using Equation \ref{eq:dispersion_comp}, where $V_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light, $z_{sys}$ is the redshift determined from the integrated galaxy spectrum and $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum.
+From the gaussian-fit, we recovered the centre, $\lambda_{g}$, the width, $\sigma_{g}$, and the area, $F_{g}$.
+The velocity was computed from $\lambda_{g}$ using Equation \ref{eq:velocity_comp} and the velocity dispersion was computed from $\sigma_{g}$ using Equation \ref{eq:dispersion_comp}, where $V_{obs}$ and $\sigma_{obs}$ are the observed rotation velocity and velocity dispersion respectively, c is the speed of light, $z_{sys}$ is the redshift determined from the integrated galaxy spectrum, $\lambda_{5007} = 0.500824\mu m$ is the rest wavelength of [O~{\sc III}]$\lambda$5007 in vacuum and $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian-fits to several skylines (equal to 31.1 km\,s$^{-1}$ in the {\it K}-band and 55.4 km\,s$^{-1}$ in the {\it HK}-band).
 
@@
 \begin{equation}\label{eq:dispersion_comp}
-   \sigma_{obs} = \frac{\sigma_{g}}{(1 + z_{sys})\lambda_{5007}} \times c
-\end{equation}
+   \sigma_{obs} = \sqrt{\left(\frac{\sigma_{g}}{(1 + z_{sys})\lambda_{5007}} \times c\right)^{2} - \sigma_{inst}^{2}}
+\end{equation} \\
 
@@
 For each of these 1000 fits the gaussian parameters were used to compute the observed properties.
-The resultant distributions of observed quantities were gaussian and we measured the median as the final value for $V_{obs}$, $\sigma_{obs}$ and $F_{g}$ within that spaxel and the standard deviation of the distribution as the observational uncertainty.
+The resultant distributions of observed quantities were gaussian and we measured the median as the final value for $V_{obs}$, $\sigma_{obs}$ and $F_{g}$ within that spaxel, and the standard deviation of the distribution as the observational uncertainty.
 A map of each of these observed parameters was constructed by applying this procedure to each spaxel. \\
@@
 \noindent
-If a spaxel did not meet the criteria we follow the procedure described in \cite{Stott2016} and binned with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
+If a spaxel did not meet the criteria, we follow the procedure described in \cite{Stott2016} and binned with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
 This was carried out by median stacking the extraction region spectra in each of the neighbouring spaxels.
@@
 The process was automated and applied to each of the 62/77 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
-Following the fitting procedure the galaxies were clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map was equivalent to or greater than the seeing disk.
-For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, was added to Table \ref{tab:pointings}.
+Following the fitting procedure, the galaxies were clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map was equivalent to or greater than the seeing disk.
+For each pointing, the number of resolved galaxies, N$_{Res}$, was added to Table \ref{tab:pointings}.
 We find that 47/77 (76\%) of the detected KDS galaxies across both the field (38/47) and cluster (9/47) environments were spatially-resolved and showed clear velocity structure.
@@
 The beam-smearing corrected kinematic parameters were then extracted from the intrinsic galaxy models as described in more detail below.
-In this analysis we minimised the number of free parameters by making use of information from {\em HST} imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.
-This is particularly important when dealing with galaxies at $z > 3$, since often there is not enough signal to noise away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.
+In this analysis, we minimised the number of free parameters by making use of information from {\em HST} imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.
+This is particularly important when dealing with galaxies at $z > 3$, since often there is not enough signal-to-noise away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.
 The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.
@@
 The 6 free parameters of the model; $(xcen, ycen), i, PA_{kin}, r_{t}, v_{asym}$, were first reduced to 5 by using the inclination from the {\em HST} axis ratio.
-We also fixed the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential well, to leave only 3 free parameters to vary in the MCMC sampling.
+We also fixed the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential-well, to leave only 3 free parameters to vary in the MCMC sampling.
 Due to the faintness of the continuum, there are several galaxies for which we could not reliably estimate the rotation centre using this method and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location (approach described in \citealt{Harrison2017}).
-Using the continuum to fix the rotation centre was generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter increases the signal to noise of the continuum by collapsing over twice the wavelength range.
+Using the continuum to fix the rotation centre was generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter increases the signal-to-noise of the continuum by collapsing over twice the wavelength range.
 \\
@@
 
-To measure the $\sigma_{int}$ value for each galaxy in our sample we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian-fits to several skylines (equal to 31.1 km\,s$^{-1}$ in the {\it K}-band and 55.4 km\,s$^{-1}$ in the {\it HK}-band).
+To measure the $\sigma_{int}$ value for each galaxy in our sample we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{g,i}$ is the value in the ith spaxel recovered from the gaussian-fit.
 
 \begin{equation}\label{eq:owen_sigma}
-\sigma_{cor,i} = \sqrt{\left(\sigma_{obs,i} - \sigma_{BS,i}\right)^{2} - \sigma_{inst,i}^{2}}
+\sigma_{cor,i} = \sqrt{\left(\sigma_{g,i} - \sigma_{BS,i}\right)^{2} - \sigma_{inst,i}^{2}}
 \end{equation}
@@
 The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} km\,s^{-1}$ and $71.0^{+5.0}_{-4.8} km\,s^{-1}$ respectively, higher than for typical star-forming galaxies at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
-The magnitude of the beam-smearing correction ($\sigma_{int}/\sigma_{obs}$) has a mean and median value of 0.77 and 0.79 respectively for the isolated field sample. \\
+The magnitude of the beam-smearing correction ($\sigma_{int}/\sigma_{obs}$) has a mean and median value of 0.81 and 0.79 respectively for the isolated field sample. \\
 
@@
 \caption{The dynamical properties for the KDS isolated field sample galaxies.
-The observed properties are measured directly from the extracted two-dimensional maps, whereas $V_{C}$ and $\sigma_{int}$ have been corrected for the effects of beam-smearing as described throughout the text.
+The observed properties are measured directly from the extracted two-dimensional maps (with $\sigma_{obs}$ corrected for the KMOS instrumental resolution), whereas $V_{C}$ and $\sigma_{int}$ have been corrected for the effects of beam-smearing as described throughout the text.
 Each galaxy is classified as rotation-dominated or dispersion-dominated if the ratio $V_{C}/\sigma_{int}$ is greater than or less than 1 respectively, as highlighted in the `Class' column.}
@@
  \hline
-b012141\_012208 & 32$\pm$13                    & 93$^{+48}_{-40}$                     & 94$\pm$18                 & 63$^{+28}_{-30}$                 & 1.47$^{+1.04}_{-0.92}$             & 122$^{+9}_{-9}$ & RD   \\[1ex]
-b15573          & 61$\pm21$                    & 81$^{+30}_{-33}$                     & 111$\pm23$                 & 84$^{+28}_{-26}$          & 0.97$^{+0.47}_{-0.52}$            & 118$^{+10}_{18}$ & DD   \\[1ex]
-bs006516        & 49$\pm4$                    & 61$^{+10}_{-9}$                     & 64$\pm8$                  & 45$^{+10}_{-9}$              & 1.35$^{+0.37}_{-0.38}$         & 144$^{+4}_{-4}$ & RD   \\[1ex]
-bs006541        & 33$\pm8$         & 65$^{+24}_{-20}$          & 96$\pm7$                  & 83$^{+9}_{-16}$             & 0.78$^{+0.34}_{-0.26}$          & 23$^{+3}_{-4}$ & DD    \\[1ex]
-bs008543        & 68$\pm13$                    & 111$^{+20}_{-16}$                    & 98$\pm7$                  & 71$^{+13}_{-10}$         & 1.56$^{+0.37}_{-0.38}$                & 114$^{+1}_{-1}$  & RD  \\[1ex]
-bs009818        & 39$\pm16$                    & 84$^{+39}_{-23}$                     & 95$\pm19$                  & 79$^{+21}_{-31}$       & 1.06$^{+0.65}_{-0.41}$                   & 72$^{+13}_{-15}$ & RD    \\[1ex]
-bs014828        & 31$\pm15$                    & 46$^{+23}_{-23}$                     & 97$\pm15$                  & 88$^{+15}_{-17}$      & 0.53$^{+0.28}_{-0.28}$               & 44$^{+15}_{-11}$  & DD  \\[1ex]
-bs016759        & 55$\pm9$                    & 110$^{+30}_{-21}$                    & 82$\pm11$                  & 57$^{+17}_{-22}$         & 1.93$^{+0.93}_{-0.7}$               & 75$^{+6}_{-6}$ & RD    \\[1ex]
-lbg\_20         & 20$\pm6$                    & 56$^{+30}_{-19}$                     & 55$\pm6$                  & 40$^{+7}_{-21}$         & 1.39$^{+1.04}_{-0.53}$              & 41$^{+9}_{-10}$ & RD   \\[1ex]
-lbg\_24         & 26$\pm6$                    & 42$^{+9}_{-7}$                     & 64$\pm5$                  & 51$^{+5}_{-6}$           & 0.82$^{+0.21}_{-0.17}$          & 64$^{+3}_{-4}$ & DD   \\[1ex]
-lbg\_25         & 14$\pm5$                    & 33$^{+13}_{-13}$                     & 53$\pm6$                  & 41$^{+6}_{-8}$         & 0.8$^{+0.37}_{-0.34}$                  & 87$^{+7}_{-12}$  & DD   \\[1ex]
-lbg\_30         & 20$\pm6$                    & 66$^{+19}_{-17}$                    & 93$\pm11$                 & 77$^{+14}_{-17}$       & 0.86$^{+0.32}_{-0.27}$               & 46$^{+6}_{-42}$ & DD \\[1ex]
-lbg\_32         & 65$\pm5$                    & 121$^{+13}_{-12}$                    & 104$\pm13$                 & 76$^{+16}_{-15}$       & 1.58$^{+0.36}_{-0.37}$               & 11$^{+2}_{-1}$ & RD \\[1ex]
-lbg\_38         & 26$\pm7$                    & 97$^{+72}_{-34}$                     & 76$\pm10$                  & 53$^{+16}_{-53}$       & 1.82$^{+2.3}_{-0.86}$               & 47$^{+2}_{-3}$  & RD   \\[1ex]
-lbg\_91         & 48$\pm10$                    & 91$^{+15}_{-18}$                     & 98$\pm8$                  & 71$^{+16}_{-14}$        & 1.28$^{+0.33}_{-0.39}$              & 40$^{+5}_{-3}$  & RD  \\[1ex]
-lbg\_94         & 18$\pm8$                    & 34$^{+19}_{-15}$                     & 65$\pm6$                  & 55$^{+7}_{-8}$         & 0.62$^{+0.36}_{-0.29}$                & 41$^{+18}_{-9}$  & DD  \\[1ex]
-lbg\_105        & 11$\pm8$                    & 32$^{+17}_{-16}$                     & 68$\pm18$                  & 59$^{+18}_{-18}$        & 0.54$^{+0.34}_{-0.32}$                & 170$^{+4}_{-7}$ & DD  \\[1ex]
-lbg\_109        & 26$\pm8$                    & 53$^{+21}_{-15}$                     & 101$\pm16$                 & 91$^{+16}_{-18}$      & 0.58$^{+0.26}_{-0.2}$                & 157$^{+11}_{-11}$ & DD  \\[1ex]
-lbg\_111        & 36$\pm12$         & 58$^{+24}_{-17}$                     & 90$\pm14$                  & 81$^{+14}_{-16}$                   & 0.71$^{+0.33}_{-0.25}$                 & 168$^{+4}_{-5}$ & DD  \\[1ex]
-lbg\_112         & 27$\pm3$                    & 63$^{+19}_{-11}$                    & 92$\pm5$                 & 78$^{+8}_{-11}$       & 0.81$^{+0.28}_{-0.17}$               & 4$^{+34}_{-12}$ & DD \\[1ex]
-lbg\_113        & 50$\pm20$           & 41$^{+41}_{-29}$                     & 116$\pm22$                 & 108$^{+23}_{-25}$                  & 0.39$^{+0.39}_{-0.29}$                & 1$^{+34}_{-26}$  & DD   \\[1ex]
-lbg\_124         & 9$\pm8$                    & 32$^{+27}_{-18}$                    & 58$\pm19$                 & 46$^{+19}_{-23}$       & 0.71$^{+0.69}_{-0.5}$               & 39$^{+20}_{-14}$ & DD \\[1ex]
-$^{*}$n3\_006         & 36$\pm23$                    & 81$^{+47}_{-29}$                     & 144$\pm26$                 & 125$^{+27}_{-31}$          & 0.65$^{+0.41}_{-0.27}$                & 156$^{+13}_{-12}$ & DD   \\[1ex]
-n3\_009         & 21$\pm9$                    & 49$^{+26}_{-16}$                     & 77$\pm13$                  & 48$^{+14}_{-45}$          & 1.01$^{+1.1}_{-0.45}$                & 20$^{+28}_{-25}$  & RD   \\[1ex]
-n\_c3           & 26$\pm8$                    & 51$^{+17}_{-18}$                     & 96$\pm11$                  & 72$^{+12}_{-13}$          & 0.72$^{+0.28}_{-0.29}$                & 137$^{+4}_{-15}$  & DD  \\[1ex]
-lab18           & 23$\pm11$                   & 41$^{+17}_{-14}$                     & 87$\pm6$                  & 62$^{+7}_{-15}$           & 0.67$^{+0.32}_{-0.24}$                 & 54$^{+18}_{-26}$ & DD    \\[1ex]
-$^{*}$lab25           & 37$\pm11$                    & 48$^{+22}_{-16}$                     & 80$\pm8$                  & 49$^{+10}_{-19}$          & 0.98$^{+0.59}_{-0.4}$                & 72$^{+14}_{-13}$ & DD   \\[1ex]
-s\_sa22a-d3     & 53$\pm17$                    & 109$^{+52}_{-32}$                    & 127$\pm13$                 & 93$^{+20}_{-36}$          & 1.16$^{+0.72}_{-0.43}$               & 30$^{+2}_{-2}$ & RD    \\[1ex]
-s\_sa22b-c20    & 66$\pm18$                    & 139$^{+33}_{-30}$                    & 112$\pm17$                 & 48$^{+34}_{-51}$          & 2.87$^{+3.12}_{-2.14}$                & 37$^{+26}_{-11}$ & RD   \\[1ex]
-$^{*}$s\_sa22b-d5     & 27$\pm10$                    & 57$^{+26}_{-23}$                     & 67$\pm20$                  & 23$^{+23}_{-18}$          & 2.45$^{+3.44}_{-2.41}$               & 60$^{+19}_{-19}$ & RD   \\[1ex]
-s\_sa22b-d9     & 32$\pm14$                    & 46$^{+22}_{-15}$                     & 99$\pm8$                  & 73$^{+10}_{-17}$             & 0.63$^{+0.33}_{-0.23}$                 & 12$^{+23}_{-7}$ & DD   \\[1ex]
-$^{*}$s\_sa22b-md25   & 44$\pm15$           & 57$^{+34}_{-24}$                     & 102$\pm19$   & 75$^{+21}_{-30}$                   & 0.76$^{+0.56}_{-0.39}$                & 9$^{+12}_{-7}$ & DD
+b012141\_012208 & 32$\pm$13                    & 93$^{+48}_{-40}$                     & 90$\pm$18                 & 63$^{+28}_{-30}$                 & 1.47$^{+1.04}_{-0.92}$             & 122$^{+9}_{-9}$ & RD   \\[1ex]
+b15573          & 61$\pm21$                    & 81$^{+30}_{-33}$                     & 107$\pm23$                 & 84$^{+28}_{-26}$          & 0.97$^{+0.47}_{-0.52}$            & 118$^{+10}_{18}$ & DD   \\[1ex]
+bs006516        & 49$\pm4$                    & 61$^{+10}_{-9}$                     & 58$\pm8$                  & 45$^{+10}_{-9}$              & 1.35$^{+0.37}_{-0.38}$         & 144$^{+4}_{-4}$ & RD   \\[1ex]
+bs006541        & 33$\pm8$                      & 65$^{+24}_{-20}$                  & 92$\pm7$                  & 83$^{+9}_{-16}$             & 0.78$^{+0.34}_{-0.26}$          & 23$^{+3}_{-4}$ & DD    \\[1ex]
+bs008543        & 68$\pm13$                    & 111$^{+20}_{-16}$                    & 94$\pm7$                  & 71$^{+13}_{-10}$         & 1.56$^{+0.37}_{-0.38}$                & 114$^{+1}_{-1}$  & RD  \\[1ex]
+bs009818        & 39$\pm16$                    & 84$^{+39}_{-23}$                     & 92$\pm19$                  & 79$^{+21}_{-31}$       & 1.06$^{+0.65}_{-0.41}$                   & 72$^{+13}_{-15}$ & RD    \\[1ex]
+bs014828        & 31$\pm15$                    & 46$^{+23}_{-23}$                     & 93$\pm15$                  & 88$^{+15}_{-17}$      & 0.53$^{+0.28}_{-0.28}$               & 44$^{+15}_{-11}$  & DD  \\[1ex]
+bs016759        & 55$\pm9$                    & 110$^{+30}_{-21}$                    & 77$\pm11$                  & 57$^{+17}_{-22}$         & 1.93$^{+0.93}_{-0.7}$               & 75$^{+6}_{-6}$ & RD    \\[1ex]
+lbg\_20         & 20$\pm6$                    & 56$^{+30}_{-19}$                     & 47$\pm6$                  & 40$^{+7}_{-21}$         & 1.39$^{+1.04}_{-0.53}$              & 41$^{+9}_{-10}$ & RD   \\[1ex]
+lbg\_24         & 26$\pm6$                    & 42$^{+9}_{-7}$                     & 57$\pm5$                  & 51$^{+5}_{-6}$           & 0.82$^{+0.21}_{-0.17}$          & 64$^{+3}_{-4}$ & DD   \\[1ex]
+lbg\_25         & 14$\pm5$                    & 33$^{+13}_{-13}$                     & 47$\pm6$                  & 41$^{+6}_{-8}$         & 0.8$^{+0.37}_{-0.34}$                  & 87$^{+7}_{-12}$  & DD   \\[1ex]
+lbg\_30         & 20$\pm6$                    & 66$^{+19}_{-17}$                    & 89$\pm11$                 & 77$^{+14}_{-17}$       & 0.86$^{+0.32}_{-0.27}$               & 46$^{+6}_{-42}$ & DD \\[1ex]
+lbg\_32         & 65$\pm5$                    & 121$^{+13}_{-12}$                    & 100$\pm13$                 & 76$^{+16}_{-15}$       & 1.58$^{+0.36}_{-0.37}$               & 11$^{+2}_{-1}$ & RD \\[1ex]
+lbg\_38         & 26$\pm7$                    & 97$^{+72}_{-34}$                     & 71$\pm10$                  & 53$^{+16}_{-53}$       & 1.82$^{+2.3}_{-0.86}$               & 47$^{+2}_{-3}$  & RD   \\[1ex]
+lbg\_91         & 48$\pm10$                    & 91$^{+15}_{-18}$                     & 94$\pm8$                  & 71$^{+16}_{-14}$        & 1.28$^{+0.33}_{-0.39}$              & 40$^{+5}_{-3}$  & RD  \\[1ex]
+lbg\_94         & 18$\pm8$                    & 34$^{+19}_{-15}$                     & 60$\pm6$                  & 55$^{+7}_{-8}$         & 0.62$^{+0.36}_{-0.29}$                & 41$^{+18}_{-9}$  & DD  \\[1ex]
+lbg\_105        & 11$\pm8$                    & 32$^{+17}_{-16}$                     & 61$\pm18$                  & 59$^{+18}_{-18}$        & 0.54$^{+0.34}_{-0.32}$                & 170$^{+4}_{-7}$ & DD  \\[1ex]
+lbg\_109        & 26$\pm8$                    & 53$^{+21}_{-15}$                     & 96$\pm16$                 & 91$^{+16}_{-18}$      & 0.58$^{+0.26}_{-0.2}$                & 157$^{+11}_{-11}$ & DD  \\[1ex]
+lbg\_111        & 36$\pm12$         & 58$^{+24}_{-17}$                     & 85$\pm14$                  & 81$^{+14}_{-16}$                   & 0.71$^{+0.33}_{-0.25}$                 & 168$^{+4}_{-5}$ & DD  \\[1ex]
+lbg\_112         & 27$\pm3$                    & 63$^{+19}_{-11}$                    & 88$\pm5$                 & 78$^{+8}_{-11}$       & 0.81$^{+0.28}_{-0.17}$               & 4$^{+34}_{-12}$ & DD \\[1ex]
+lbg\_113        & 50$\pm20$           & 41$^{+41}_{-29}$                     & 113$\pm22$                 & 108$^{+23}_{-25}$                  & 0.39$^{+0.39}_{-0.29}$                & 1$^{+34}_{-26}$  & DD   \\[1ex]
+lbg\_124         & 9$\pm8$                    & 32$^{+27}_{-18}$                    & 52$\pm19$                 & 46$^{+19}_{-23}$       & 0.71$^{+0.69}_{-0.5}$               & 39$^{+20}_{-14}$ & DD \\[1ex]
+$^{*}$n3\_006         & 36$\pm23$                    & 81$^{+47}_{-29}$                     & 133$\pm26$                 & 125$^{+27}_{-31}$          & 0.65$^{+0.41}_{-0.27}$                & 156$^{+13}_{-12}$ & DD   \\[1ex]
+n3\_009         & 21$\pm9$                    & 49$^{+26}_{-16}$                     & 56$\pm13$                  & 48$^{+14}_{-45}$          & 1.01$^{+1.1}_{-0.45}$                & 20$^{+28}_{-25}$  & RD   \\[1ex]
+n\_c3           & 26$\pm8$                    & 51$^{+17}_{-18}$                     & 84$\pm11$                  & 72$^{+12}_{-13}$          & 0.72$^{+0.28}_{-0.29}$                & 137$^{+4}_{-15}$  & DD  \\[1ex]
+lab18           & 23$\pm11$                   & 41$^{+17}_{-14}$                     & 69$\pm6$                  & 62$^{+7}_{-15}$           & 0.67$^{+0.32}_{-0.24}$                 & 54$^{+18}_{-26}$ & DD    \\[1ex]
+$^{*}$lab25           & 37$\pm11$                    & 48$^{+22}_{-16}$                     & 58$\pm8$                  & 49$^{+10}_{-19}$          & 0.98$^{+0.59}_{-0.4}$                & 72$^{+14}_{-13}$ & DD   \\[1ex]
+s\_sa22a-d3     & 53$\pm17$                    & 109$^{+52}_{-32}$                    & 115$\pm13$                 & 93$^{+20}_{-36}$          & 1.16$^{+0.72}_{-0.43}$               & 30$^{+2}_{-2}$ & RD    \\[1ex]
+s\_sa22b-c20    & 66$\pm18$                    & 139$^{+33}_{-30}$                    & 97$\pm17$                 & 48$^{+34}_{-51}$          & 2.87$^{+3.12}_{-2.14}$                & 37$^{+26}_{-11}$ & RD   \\[1ex]
+$^{*}$s\_sa22b-d5     & 27$\pm10$                    & 57$^{+26}_{-23}$                     & 38$\pm20$                  & 23$^{+23}_{-18}$          & 2.45$^{+3.44}_{-2.41}$               & 60$^{+19}_{-19}$ & RD   \\[1ex]
+s\_sa22b-d9     & 32$\pm14$                    & 46$^{+22}_{-15}$                     & 83$\pm8$                  & 73$^{+10}_{-17}$             & 0.63$^{+0.33}_{-0.23}$                 & 12$^{+23}_{-7}$ & DD   \\[1ex]
+$^{*}$s\_sa22b-md25   & 44$\pm15$           & 57$^{+34}_{-24}$                     & 87$\pm19$   & 75$^{+21}_{-30}$                   & 0.76$^{+0.56}_{-0.39}$                & 9$^{+12}_{-7}$ & DD
 
@@
 In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in Appendix \ref{subsec:AMAZE}.
-We used a simple approach (dictated by the signal to noise of the isolated field sample) and calculated rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
+We used a simple approach (dictated by the signal-to-noise of the isolated field sample) and calculated rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
 The morphologically isolated KDS field galaxies were classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
@@
 
-In the previous sections we presented our morphological and kinematic analysis for the 77 galaxies covering both cluster and field environments in the KDS survey.
-These galaxies are representative of typical SFGs $z\simeq3.5$ as verified by comparing to fits to the galaxy main-sequence at this redshift.
-Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we first reduced the sample to 38 spatially resolved field environment galaxies and then to 32 isolated field sample galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
+In the previous sections we presented our morphological and kinematic analyses for the 77 galaxies covering both cluster and field environments in the KDS survey.
+These galaxies are representative of typical star-forming galaxies at $z\simeq3.5$, as verified by comparing with fits to the galaxy main-sequence at this redshift.
+Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class}, we first reduced the sample to 38 spatially resolved field environment galaxies and then to 32 isolated field sample galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
 not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
-For these galaxies we measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we used to classify the galaxies as either rotation or dispersion-dominated.
+For these galaxies we measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$, and velocity dispersions, $\sigma_{int}$, as listed in Table \ref{tab:kin_props}, which we used to classify the galaxies as either rotation or dispersion-dominated.
 The morphological and kinematic grids for these 32/38 isolated field sample galaxies and the 6/38 merger candidates are plotted in Appendix \ref{app:kinematics_plots}.
@@
 We plot the relationship between rotation velocity and stellar mass for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
-In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ star-forming galaxies with $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
+We compare to the relationship from \cite{Harrison2017}, in which the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ star-forming galaxies with $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
 The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a_{z=0.9} = 0.33 \pm 0.11$ and $b_{z=0.9} = 2.12 \pm 0.04$.
 We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
-These $z\simeq0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
-In \cite{Reyes2011}, $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
-The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotation-dominated star-forming galaxies between these redshifts.
-
+
+\noindent
 The rotation-dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\simeq0.9$ relation, but with a tendency to lie below the relation.
@@
 The dispersion-dominated KDS galaxies sit clearly separated and below the $z\simeq0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\simeq0.9$ dispersion-dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}.
-We plot also the five galaxies from the AMAZE Clean ($z\simeq3$) sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$. \\
+We plot also the five galaxies from the AMAZE Clean ($z\simeq3$) sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$.
+The $z\simeq0.9$ fit parameters are consistent with those measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
+In \cite{Reyes2011}, $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
+The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotation-dominated star-forming galaxies between these redshifts.
+\\
 
@@
 Conversely, fitting the stellar mass Tully-Fisher relation through a full sample including dispersion-dominated galaxies would shift the zero-point in the opposite sense.
-
-With the KDS, we have added the largest sample of galaxies observed with integral-field spectroscopy at $z>3$, and with our simple $V_{C}/\sigma_{int} > 1$ cut we conclude that the stellar mass Tully-Fisher relation defined for rotation-dominated star-forming galaxies appears to show no evolution between $z\simeq0.1$ and $z\simeq3.5$.
+This new, robust analyses of typical $z\simeq3.5$ star-forming galaxies is consistent with the majority of work that shows no evolution for rotation-dominated galaxies across all epochs.
+
+\noindent
+In summary, with the KDS, we have added the largest sample of galaxies observed with integral-field spectroscopy at $z>3$, and with our simple $V_{C}/\sigma_{int} > 1$ cut we conclude that the stellar mass Tully-Fisher relation defined for rotation-dominated star-forming galaxies appears to show no evolution between $z\simeq0.1$ and $z\simeq3.5$.
 However, as we will show in \cref{subsec:rdf_v_over_sigma}, the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.
@@
     The symbol convention is the same as in the right panel of Figure \protect\ref{fig:tf_relation}.
-    The $\sigma_{int}(z)$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is shown in the top right equation, is plotted for three different $M_{\star}$ values and in each case for $V_{C} = 125km\,s^{-1}$.
-    These are intended as indicators of the way in which $\sigma_{int}$ evolves in galaxies in different mean $M_{\star}$, where this on average gives an indication of the extent to which the stellar population has been accumulated, which may provide increased stability for an extended rotating disk.
-    The KDS datapoint appears to be consistent with the scenario proposed in previous work, whereby the mean $\sigma_{int}$ increases over cosmic time, with large scatter between individual galaxies, as a result of increased gas fractions and more efficient accretion of cold gas.
-    The vertical location of the mean datapoints in this plane are mediated by the mean $M_{\star}$ of each survey, which is itself connected to the mean gas fraction.} 
+    The $\sigma_{int}(z,M_{\star})\propto f_{gas}(z,M_{\star})$ scaling relation from \protect\cite{Wisnioski2015}, the form of which is discussed in \protect\cref{discussion_increase_in_sigma}, is plotted for three different $M_{\star}$ values.
+    These tracks indicate the way in which $\sigma_{int}$ evolves for samples of star-forming galaxies with different mean $M_{\star}$ values, which is a proxy for the dynamical maturity of the galaxies.
+    The KDS datapoint appears to be consistent with the scenario proposed in previous work, whereby the mean $\sigma_{int}$ increases over cosmic time, with large scatter between individual galaxies, as a result of increased gas fractions \protect\citep{Wisnioski2015} and the more efficient accretion of cold gas driving disk instabilities \protect\citep[e.g.][]{Law2009,Genzel2011}.}
     \label{fig:sigma_and_v_sigma_w_redshift}
@@
 \begin{itemize}
-    \item At each redshift slice the $V_{C}$ distributions are extremely broad, with mean values determined by the stellar mass of each survey.
-    \item The mean isolated field sample $V_{C}$ value is less than reported in the comparison samples with similar mean $M_{\star}$ values.
+    \item At each redshift slice the $V_{C}$ distributions are extremely broad, with mean values sensitive to the average stellar mass of each survey.
+    \item The mean isolated field sample $V_{C}$ value is less than reported in the lower redshift comparison samples with similar mean $M_{\star}$ values.
     This is a result of averaging over a sample containing a higher fraction of dispersion-dominated galaxies.
@@
 It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in Appendix \ref{app:comparison_samples}) are directly comparable.
-The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
+The GHASP, MASSIV, KROSS and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
 Despite the wide distributions, the comparison samples generally have higher mean rotation velocities. \\
@@
 Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95km\,s^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
-This value is above the mean and median values of the isolated field sample, but comparable to the mean and median of the rotation dominated galaxies, suggesting that rotation in these systems could support at most the stellar mass of the galaxy.
+This value is greater than the mean and median values of the isolated field sample, but comparable to the mean and median of the rotation dominated galaxies, suggesting that rotation in these systems could support, at most, the stellar mass of the galaxy.
 
@@
 There are also some galaxies in our sample where the observed velocity field has clear rotational structure and reaches flattening (e.g.
-see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}/M_{\odot})=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
+see Figure \ref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}/M_{\odot})=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
 This suggests again that the increase in random motions could influence the rotation velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Law2012b,Law2012c,Newman2013,Wisnioski2015}.
@@
 
-In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation-dominated classes, along with the AMAZE Clean ($z\simeq3$) sample galaxies in the $\sigma_{int}$ vs.
+In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation-dominated classes, along with the AMAZE Clean ($z\simeq3$) sample, in the $\sigma_{int}$ vs.
 $M_{\star}$ plane.
 This is an interesting relationship to explore as it has been suggested that rotation velocity alone may not be a good tracer of total dynamical mass at high redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
-However the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
+However, the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
 All of these processes are also more prevalent at high redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret.
@@
 The beam-smearing corrected $\sigma_{int}$ values, with distribution median, 16th percentile and 84th percentile equal to $71.0km\,s^{-1}$, $48.0km\,s^{-1}$ and $85.4km\,s^{-1}$ respectively, are larger than in the local universe where typically $\sigma_{int} = 10-20km\,s^{-1}$ \citep{Epinat2008a} (see \cref{subsubsec:sigma_evolution} and \cref{sec:discussion} for a discussion).
-Generally the dispersion-dominated galaxies have higher $\sigma_{int}$ values, however the rotation-dominated galaxies also span the full distribution width.
+Generally, the dispersion-dominated galaxies have higher $\sigma_{int}$ values in the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}, however the rotation-dominated galaxies also span the full distribution width.
 
 \subsubsection{The evolution of velocity dispersion}\label{subsubsec:sigma_evolution}
-
-In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
-The values increase sharply from $\sigma_{int}\simeq10-20km\,s^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60km\,s^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90km\,s^{-1}$ at $z\simeq3$, but with a wide range of values observed at each redshift.
-There appears to be a trend for the surveys with lower average stellar mass (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) to have higher velocity dispersions than the surveys with larger average stellar mass (GHASP, KMOS$^{3D}$, SINS).
-
-The increase of velocity dispersion within typical star-forming galaxies with redshift appears to follow the same scaling relation as the increase of gas fractions, as inspired by the model described in \cite{Wisnioski2015} and discussed in \cref{discussion_increase_in_sigma}.
-The gas fraction is a function of both stellar mass and redshift and so we plot tracks in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} for three different mass values which roughly encompass the average masses of the comparison samples, $log(M_{\star}/M_{\odot})=9.8,10.3,10.6$.
-The tracks are each scaled with the same coefficient, which is chosen so that the lowest mass track, equivalent to the isolated field sample mean mass, coincides with the KDS datapoint at $z=3.5$.
-As the data suggest, the lower mass tracks describe a flatter evolution of velocity dispersion with redshift, with the different masses showing converging velocity dispersion predictions at high redshift.
-The redshift and mass dependence of these tracks is discussed in \cite{Wisnioski2015} and in more detail throughout \cref{discussion_increase_in_sigma}, where we also discuss possible physical explanations for the increase in velocity dispersions with redshift.
-\\
-
-\noindent
-These new data from the KDS sustain the observation that velocity dispersion is increasing with redshift and provide strong constraints on the internal dynamics of typical star-forming galaxies between $z=3-3.8$.
-When considered in conjunction with data from the literature in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}, it appears that the stellar mass of galaxies may play a role in mediating the velocity dispersion values (see \cref{discussion_increase_in_sigma}).
-
-We proceed now to consider both the rotation velocities and velocity dispersions in tandem by considering $V_{C}/\sigma_{int}$ and the rotation-dominated fraction of galaxies in the isolated field sample.
-
-\subsection{$\boldsymbol{V_{C}/\sigma_{int}}$ and the rotation-dominated fraction}\label{subsec:rdf_v_over_sigma}
 
@@
     We mark the $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies in this panel, finding that more massive galaxies (e.g.
-$log(M_{\star}/M_{\odot}) > 9.5$) are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.}
+$log(M_{\star}/M_{\odot}) > 9.5$) are more likely to be rotation-dominated, with dispersion-dominated galaxies spread across the stellar mass range.}
     \label{fig:v_sig_and_v}
 \end{figure}
+
+In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
+The values increase sharply from $\sigma_{int}\simeq10-20km\,s^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60km\,s^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90km\,s^{-1}$ at $z\simeq3$, but with a wide range of values observed at each redshift.
+There appears to be a trend for the surveys with lower average stellar mass (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) to have higher velocity dispersions than the surveys with larger average stellar mass (GHASP, KMOS$^{3D}$, SINS).
+
+In agreement with the evolution of gas fractions described in \cref{discussion_increase_in_sigma} (and see the tracks in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}), we find that the mean velocity dispersion measurements from samples of typical star-forming galaxies are decreasing with redshift, with a dependence on mass such that samples with higher stellar mass have lower velocity dispersions at each epoch.
+The redshift and mass dependence of these tracks is discussed in \cite{Wisnioski2015} and discussed in more detail throughout \cref{discussion_increase_in_sigma}, where we also discuss possible physical explanations for the increase in velocity dispersions with redshift.
+\\
+
+\noindent
+These new data from the KDS sustain the observation that velocity dispersion is increasing with redshift and provide strong constraints on the internal dynamics of typical star-forming galaxies between $z=3-3.8$.
+When considered in conjunction with data from the literature in the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}, it appears that the stellar mass of galaxies may play a role in mediating the velocity dispersion values (see \cref{discussion_increase_in_sigma}).
+
+We proceed now to consider both the rotation velocities and velocity dispersions in tandem by considering $V_{C}/\sigma_{int}$ and the rotation-dominated fraction of galaxies in the isolated field sample.
+
+\subsection{$\boldsymbol{V_{C}/\sigma_{int}}$ and the rotation-dominated fraction}\label{subsec:rdf_v_over_sigma}
 
@@
     We see a clear decline in the mean $V_{C}/\sigma_{int}$ values with redshift, but with wide ranges in the individual measurements.
-    There is also a connection to the mean $M_{\star}$ of the surveys, with larger mean $M_{\star}$ surveys reporting higher mean $V_{C}/\sigma_{int}$.
+    There is a connection between $V_{C}/\sigma_{int}$ and the stellar mass of the surveys, with larger mean $M_{\star}$ surveys reporting higher mean $V_{C}/\sigma_{int}$.
     {\it Right:} We plot the associated rotation-dominated fraction, defined as the fraction of galaxies in each sample with $V_{C}/\sigma_{int} > 1$.
     The narrow shaded regions represent the maximum and miminum RDF, computed as described in Appendix \protect\ref{app:comparison_samples}.
-    It appears that the rotation-dominated fraction drops from $\simeq100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\simeq40\%$ at z $\simeq3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher rotation-dominated fractions.
-    The dot-dash line is the RDF $\propto z^{-0.2}$ cosmic decline suggested in \protect\cite{Stott2016}.
+    It appears that the rotation-dominated fraction drops from $\simeq100\%$ in the local universe to $60\%$ at intermediate redshifts and then to $\simeq35\%$ at z $\simeq3.5$, again with the trend for high $V_{C}/\sigma_{int}$ values in the larger $M_{\star}$ surveys reflected by higher rotation-dominated fractions.
+    The dot-dash line is the RDF $\propto z^{-0.2}$ cosmic decline suggested in \protect\cite{Stott2016}, which appears to follow the redshift decline of the rotation dominated fraction.
     In both panels, the symbol convention is the same as in the right panel of Figure \protect\ref{fig:tf_relation}.
@@
 
-In Figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, including also galaxies from the AMAZE Clean ($z\simeq3$) sample for reference.
+In Figure \ref{fig:v_sig_and_v} we plot the ratio of $V_{C}$/$\sigma_{int}$ against $M_{\star}$ for the isolated field sample, also including galaxies from the AMAZE Clean ($z\simeq3$) sample for reference.
 In the local universe, disky, SFGs are observed to have $V_{C}/\sigma_{int}$ values in excess of 10 (i.e.
-the disks are `well settled'), due to the decline of velocity dispersion across cosmic time, as gas fractions and disk turbulence decrease \citep[e.g.][]{Epinat2008,Epinat2008a}.
+the disks are `well settled'), due to the decline of velocity dispersion across cosmic time, as gas fractions and disk turbulence decrease \citep[e.g.][]{Epinat2008a,Epinat2008}.
 Clearly the isolated field sample galaxies are in a different physical regime, with mean and median $V_{C}/\sigma_{int}$ values of $1.08^{+0.18}_{-0.15}$ and $0.97^{+0.14}_{-0.11}$ respectively.
@@
 \noindent
-The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation-dominated galaxies by definition, and we find that it is the more massive galaxies with $log(M_{\star}/M_{\odot}) > 9.5$ which are more likely to be rotation-dominated, but with rotation and dispersion-dominated galaxies found at all values of $M_{\star}$.
+The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation-dominated galaxies by definition.
+There is a spread of rotation and dispersion-dominated galaxies across the stellar mass range, with rotation-dominated galaxies more likely to be found above $log(M_{\star}/M_{\odot}) > 9.5$.
 The Rotation-Dominated Fraction (RDF), calculated with respect to the full field sample of 38 galaxies, is 0.34$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
-We interpret these results in the context of the cosmic evolution of the rotation domianted fraction using the comparison samples in \cref{subsubsec:RDF_evolution}.\\
+We interpret these results in the context of the cosmic evolution of the rotation dominated fraction using the comparison samples in \cref{subsubsec:RDF_evolution}.\\
 
@@
 In each sample, the rotation dominated fraction is computed as the fraction of galaxies with $V_{C}/\sigma_{int} > 1$, which, given the varying data quality across the comparison samples, is a simple and fair way to study the redshift evolution of this quantity.
-The filled symbols and black errorbars in the left panel represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
-The shaded regions give the 16th and 84th percentiles of the distribution on individual $V_{C}/\sigma_{int}$ measurements, plotted here to indicate the range of measurements at each redshift slice.
-In the right panel we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the rotation-dominated fraction.
+The filled and hollow symbols with black errorbars in the left panel of Figure \ref{fig:rdf_and_v_sigma_w_redshift} represent the mean and error on the mean, and the horizontal lines show the median and error on the median.
+The shaded regions give the 16th and 84th percentiles of the distribution of individual $V_{C}/\sigma_{int}$ measurements, plotted here to indicate the range of measurements at each redshift slice.
+In the right panel of Figure \ref{fig:rdf_and_v_sigma_w_redshift}, we have also computed the maximum and minimum RDF for these surveys by adding and subtracting the $V_{C}/\sigma_{int}$ error values respectively and recomputing the rotation-dominated fraction.
 These are shown with the thin grey shaded regions and are intended to give an indication of the limits of the RDF at different redshift slices given the size of the errors on the individual points.\\
@@
 The rotation-dominated fraction, traced simply by the $V_{C}/\sigma_{int}$ ratio inferred from ionised gas emission lines, drops from $\simeq100\%$ of galaxies in the local universe to $\simeq2/3$ of galaxies in the $z\simeq1-2$ universe and to $\simeq1/3$ above $z\simeq3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
-This is highlighted in the right panel of Figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the cosmic rotation-dominated fraction decline as described in \cite{Stott2016}.
-The width of the $V_{C}/\sigma_{int}$ distributions indicates the galaxy diversity at each redshift slice, driven by the collection of galaxy masses, sSFRs, gas fractions, morphologies and evolutionary states which comprise each sample.
+This is highlighted in the right panel of Figure \ref{fig:rdf_and_v_sigma_w_redshift} by overplotting the RDF $\propto z^{-0.2}$ line which appears to roughly follow the decline of the rotation-dominated with redshift as described in \cite{Stott2016}.
+The width of the $V_{C}/\sigma_{int}$ distributions indicate the galaxy diversity at each redshift slice, driven by the collection of galaxy masses, sSFRs, gas fractions, morphologies and evolutionary states which comprise each sample.
 Scatter above and below the RDF $\propto z^{-0.2}$ evolution line may be attributed in part to the different mean stellar masses of the surveys, with those that have larger stellar masses tending to scatter above this line.
 This draws again from the idea that higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the rotation-dominated fraction higher (see \cref{sec:discussion}).
+\\\\
+\noindent
 In summary, the rotation-dominated galaxies in the isolated field sample appear to conform with a redshift invariant $V_{C}$ - $M_{\star}$ relation.
@@
 
-Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation-dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
+Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that, within the scatter, the rotation-dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
 The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion-dominated galaxies ($66\%$ of the sample) and probable pressure support from turbulent motions \citep[e.g.][]{Burkert2010}.
@@
     \caption{{\it Left:} We plot the $\sigma_{int}$ values for the comparison samples as well as the isolated field sample, shifted as described in the text to a reference mass of $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample).
-    The grey shaded region encompasses the model predictions using a fixed $Q_{crit} = 1.0$ and with lower and upper bounds using $V_{C} = 70-200km\,s^{-1}$ respectively (corresponding roughly to the velocity range spanned by galaxies in the comparison samples).
+    The grey line shows the model prediction with $V_{C}Q_{crit}/a = 90.5km\,s^{-1}$, as dictated by our data.
+    The grey shaded region encompasses the model predictions with lower and upper bounds using $V_{C}Q_{crit}/a = 50-140km\,s^{-1}$ respectively (corresponding roughly to the velocity range $V_{C} = 70-200km\,s^{-1}$, spanned by galaxies in the comparison samples, under the assumption that $Q_{crit} = 1.0$ and {\it a} = $\sqrt{2}$ as discussed in the text).
     The shifted points are in line with the scenario whereby the sample averaged velocity dispersions increase with redshift as a result of increasing average gas fractions. 
@@
 
+\noindent
 \cite{Burkert2010} show, starting from the hydrostatic equation, that negative pressure gradients sourced by the disk turbulence generated through gravitational instabilities result in a decrease in observed rotation velocities.
@@
 \noindent
-In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties: gas fraction, $f_{gas}$ gas depletion timescale, $t_{dep}$, and specific star-formation rate, sSFR.
+In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties: gas fraction, $f_{gas}$, gas depletion timescale, $t_{dep}$, and specific star-formation rate, sSFR.
+Here we explore how well this model describes the evolution in velocity dispersion, incorporating our new measurement at $z\simeq3.5$ from the KDS.
 The function describing the evolution of the velocity dispersion with redshift is shown below in Equation \ref{eq:sigma_increase}, where $Q_{crit}$ is the critical Toomre parameter for stability against gravitational collapse \citep{Toomre1964}, and {\it a} is a dimensionless parameter which depends on the assumed distribution of gas and gravitational potential \cite{ForsterSchreiber2006}.
@@
 \begin{equation}\label{eq:sigma_increase}
-    \sigma(z,M_{\star}) = V_{C}f_{gas}(z,M_{\star})Q_{crit}/{\it a}
+    \sigma(z,M_{\star}) = \frac{V_{C}Q_{crit}}{{\it a}}f_{gas}(z,M_{\star})
 \end{equation}
@@
     f_{gas} & = \frac{1}{1 + \left(t_{dep}sSFR\right)^{-1}} \\[1ex]
-    & = \frac{1}{1 + \left(1.5\times10^{a(M_{\star})}\left(1 + z \right)^{b(M_{\star}) + \alpha}\right)^{-1}}
+    & = \frac{1}{1 + \left(1.5\times10^{a(M_{\star})}(1 + z)^{b(M_{\star}) + \alpha}\right)^{-1}}
 \end{aligned}
@@
 \begin{aligned}
-   & a(M_{\star}) = -10.73 + \frac{1.26}{1 + {\it e}^{\left(10.49 - logM_{\star}\right)/(-0.25)}} \\[1ex]
-   & b(M_{\star}) = 1.85 + \frac{1.57}{1 + {\it e}^{\left(10.35 - logM_{\star}\right)/(0.19)}}
+   & a(M_{\star}) = -10.73 + \frac{1.26}{1 + {\it e}^{\left(10.49 - log(M_{\star}/{\rm M}_{\odot})\right)/(-0.25)}} \\[1ex]
+   & b(M_{\star}) = 1.85 + \frac{1.57}{1 + {\it e}^{\left(10.35 - log(M_{\star}/{\rm M}_{\odot})\right)/(0.19)}}
 \end{aligned}
@@
 \noindent
-Using observed constraints for these properties from \cite{Tacconi2013} and \cite{Whitaker2014} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \citealt{Wisnioski2015} Figures 10 and 11).
-
 This relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
@@
 
-In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot Equation \ref{eq:sigma_increase} for different input mass values (roughly spanning the mass range of the comparison samples), using the updated depletion time scaling relation from \cite{Tacconi2017} (i.e.
-$t_{dep} \propto (1 + z)^{-0.57}$, meaning $alpha=0.57$ in Equation \ref{eq:gas_fractions}).
-The Equation $\sigma(z,M_{\star})\propto f_{gas}(z,M_{\star})$ is scaled so that the lowest mass track conincides with the KDS datapoint, finding a proportionality constant $V_{C}Q_{crit}/a = 90.5km\,s^{-1}$.
-$Q_{crit} = 1.0$ for a quasi-stable thin disk e.g.
-\citealt{ForsterSchreiber2006,Burkert2010}) and {\it a} = $\sqrt{2}$ for a disk with constant rotation velocity \citep{Wisnioski2015}, and assuming these values gives $V_{C} = 128km\,s^{-1}$ as a best match to our data.
-This is larger than the intrinsic rotation velocities in the isolated field sample, although this could be a result of the assumptions for both $Q_{crit}$ and {\it a}. \\
-
-\noindent
-In this model the velocity dispersions increase more steeply with increasing stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
+In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot Equation \ref{eq:sigma_increase} for three different input mass values ($log(M_{\star}/M_{\odot})=9.8,10.3,10.6$, roughly spanning the mass range of the comparison samples), using the updated depletion time scaling relation from \cite{Tacconi2017} (i.e.
+$t_{dep} \propto (1 + z)^{-0.57}$, meaning $\alpha=0.57$ in Equation \ref{eq:gas_fractions}).
+The Equation $\sigma(z,M_{\star})\propto f_{gas}(z,M_{\star})$ is scaled so that the lowest mass track conincides with the KDS datapoint, finding a proportionality constant $V_{C}Q_{crit}/a = 90.5km\,s^{-1}$, which we assume when plotting all three tracks in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
+\\
+
+\noindent
+In this model, the velocity dispersions increase more steeply with increasing stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
 At higher redshift, these lines converge, suggesting that the predictions for the gas fraction become independent of stellar mass in this regime.
@@
 Since stellar mass appears to be a crucial factor in regulating the velocity dispersions within galaxies, and the comparison samples have disparate stellar mass ranges, we use the model to shift the $\sigma_{int}$ values according to their stellar mass to a reference mass value as per \cite{Wisnioski2015}.
-This is done by computing the difference between the model predicted $\sigma_{int}$ value at the stellar mass of each comparison survey and at the reference mass for the appropriate redshift and shifting the reported $\sigma_{int}$ by this value.
+This is done by computing the difference between the model predicted $\sigma_{int}$ value at the stellar mass of each comparison survey, and at the reference mass for the appropriate redshift, and shifting the reported $\sigma_{int}$ by this value.
 We do this for two reference mass values; $log(M_{\star}/M_{\odot}) = 9.8$ (the median mass of the isolated field sample, left panel of Figure \ref{fig:sigma_shifted}) and $log(M_{\star}/M_{\odot}) = 10.6$ (right panel of Figure \ref{fig:sigma_shifted}).
-In both panels, the grey line denotes the model prediction using $Q_{crit} = 1.0$, {\it a} = $\sqrt{2}$ and $V_{C} = 128km\,s^{-1}$ and the light grey shaded region encompasses the model predictions with lower and upper bounds defined with $V_{C} = 70-200km\,s^{-1}$ respectively (spanning the velocity values of galaxies in the comparison samples).
+
+In both panels, the solid grey line denotes the model prediction using the parameter combination determined above; $V_{C}Q_{crit}/a = 90.5km\,s^{-1}$.
+The grey shaded regions encompass model predictions with lower and upper bounds defined by $V_{C}Q_{crit}/a = 50-140km\,s^{-1}$ respectively.
+Assuming that $Q_{crit} = 1.0$ (as for a quasi-stable thin disk e.g.
+\citealt{ForsterSchreiber2006,Burkert2010}) and {\it a} = $\sqrt{2}$ (as for a disk with constant rotation velocity \citealt{Wisnioski2015}), this range corresponds to $V_{C} = 70-200km\,s^{-1}$, which is roughly the velocity range spanned by our comparison samples, and the solid grey line corresponds to $V_{C} = 128km\,s^{-1}$.
+Whilst the KDS mean rotation velocity sits at the bottom of this range, possible explanations are: \textbf{(1)} The rotation velocities of the KDS galaxies are underestimated as a result of the velocity dispersion contribution discussed above; \textbf{(2)} $Q_{crit} \ne 1$ or ${\it a} \ne \sqrt{2}$ as a consequence of changing physical conditions at high redshift.
 \\
@@
 Although the details of the coefficients of Equation \ref{eq:sigma_increase} are unclear (i.e.
-$V_{C}$ is not fixed at one value for the comparison samples and is itself linked to stellar mass and both $Q_{crit}$ and {\it a} could vary with redshift), the shape of the velocity dispersion evolution appears to follow that of the gas fraction.
+$V_{C}$ is not fixed at one value for the comparison samples and is itself linked to stellar mass and both $Q_{crit}$ and {\it a} could vary with redshift), the shape of the velocity dispersion evolution appears to follow that of the gas fraction, as suggested by the model.
 The difference between the slopes in the left and right panels highlights the role of stellar mass in the kinematic settling of galaxies between $z\simeq3$ and the local universe. 
@@
 The KDS isolated field sample presents an extension of these trends to higher redshift, where galaxies are even more likely to be dispersion-dominated, and pressure support may be more significant than explored at $z\simeq2.3$ \citep{Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
-However the precise interpretation of $\sigma_{int}$ measured from ionised gas emission lines remains unclear and future observations of both stellar and gaseous velocity dispersions in tandem at high redshift with {\it JWST} will allow for unambigous investigations into the nature of gaseous velocity dispersions at high redshift.
+However, the precise interpretation of $\sigma_{int}$ measured from ionised gas emission lines remains unclear, and future observations of both stellar and gaseous velocity dispersions in tandem with {\it JWST} will allow for unambigous investigations into the nature of gaseous velocity dispersions at high redshift.
 \\
@@
 \section{CONCLUSIONS}\label{sec:conclusion}
-We have presented new dynamical measurements of 32 typical star forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
+We have presented new dynamical measurements of 32 typical star-forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
 These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.0 < log(M_{\star}/M_{\odot})< 10.5$ typical star-forming galaxies at these redshifts.
 By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\simeq16\%$) and a very high merger rate in the cluster pointing ($\simeq89\%$).
-We have made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies interpreting these in the context of previous dynamical studies using IFU data (Appendix \ref{app:comparison_samples} and Table \ref{tab:evolution_numbers}).
+We have made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies, and we interpret these in the context of previous dynamical studies using IFU data (Appendix \ref{app:comparison_samples} and Table \ref{tab:evolution_numbers}).
 The main conclusions of this work are summarised as follows:
@@
     Consistency of sample selection and measurement techniques are crucial factors when determining evolution in the $V_{C}$ vs. $M_{\star}$ plane by comparing samples at different redshifts.
-    The dispersion-dominated galaxies scatter below the trend, with the same slope as the rotation-dominated galaxies.
-    \item When considering the rotation-dominated galaxies alone the mean and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}km\,s^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}km\,s^{-1}$ respectively, which are roughly equivalent to a simple lower limit virial theorem calculation using the mean mass and half-light radius of the sample.
-    This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in the system \citep[e.g.][]{Burkert2010}.  
+    The dispersion-dominated galaxies in the isolated field sample scatter below the trend.
+    \item When considering the rotation-dominated galaxies alone, the mean and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}km\,s^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}km\,s^{-1}$ respectively, which are roughly equivalent to a simple lower limit virial theorem calculation using the mean mass and half-light radius of the sample.
+    This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in all of the galaxies in the isolated field sample \citep[e.g.][]{Burkert2010}.
     \item 13/32 isolated field sample galaxies are rotation-dominated and 19/32 are dispersion-dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
@@
 The errors on the mean and median represent the statistical errors from bootstrap resampling.
-For each of the comparison samples the cross or tick after each of the mean kinematic properties indicates whether we have defined this as a fair value to compare against, with further details provided throughout Appendices \protect\ref{subsec:GHASP} - \protect\ref{subsec:AMAZE}.}
+For each of the comparison samples, the cross or tick after each of the mean kinematic properties indicates whether we have defined this as a fair value to compare against, with further details provided throughout Appendices \protect\ref{subsec:GHASP} - \protect\ref{subsec:AMAZE}.}
 \label{tab:evolution_numbers}
@@
 
-Throughout \cref{sec:results} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
-The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out representative star-forming galaxies at each epoch and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission lines.
+In \cref{sec:results} we compare the isolated field sample results with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
+The galaxy selection criteria in these surveys, with the exception of DYNAMO \citep{Green2014} as discussed below, consistently picks out representative star-forming galaxies at each epoch and the dynamical properties are traced by observing either the [O~{\sc III}]$\lambda$5007, [O~{\sc II}]$\lambda$3727,3729 or $H\alpha$ ionised gas emission lines.
 
@@
 
-We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
-Throughout \cref{sec:results} we highlight in the figures which values can be directly compared using filled and hollow symbols.
+We make use of tabulated data from the surveys, where available, to compute sample averages using the following method. 
 The fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples is computed (i.e.
@@
 These results are listed in Table \ref{tab:evolution_numbers} and discussed in detail throughout \cref{sec:results}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.
+Throughout the plots in \cref{sec:results} we highlight which values can be directly compared, due to consistency of sample selection and measurement methods, using filled and hollow symbols.
+This is also highlighted with the ticks and crosses beside the mean values in Table \ref{tab:evolution_numbers}.
 
 \subsection{GHASP ($\bmath{z\simeq0}$)}\label{subsec:GHASP}
-The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}/M_{\odot})=10.6$ in the local universe ($z\simeq0$) to produce 3D H$\alpha$ datacubes.
+The GHASP survey \citep[E08]{Epinat2008a,Epinat2008} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}/M_{\odot})=10.6$ in the local universe ($z\simeq0$) to produce 3D H$\alpha$ datacubes.
 The data extend out to several half-light radii and in each case tilted ring models are fit to determine $V_{C}$ at large radii where the rotation curves have flattened, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
@@
 In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}/M_{\odot})=10.3$ at $z\simeq0.1$ are presented.
-The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\simeq2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\simeq2$ SFGs.
+The selection criteria is such that half of the sample have high sSFRs representative of SFGs at $z\simeq2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\simeq2$ SFGs.
 $V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.6R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
@@
 The intrinsic velocity dispersions have been corrected for beam-smearing effects.
-For this reason the velocity dispersions are deemed directly comparable to the KDS, reflected by the filled symbols throughout the plots in \cref{sec:results}, but the points involving velocity measurements are represented by hollow symbols due to the lack of a beam-smearing correction.
+For this reason, the velocity dispersions are deemed directly comparable to the KDS, reflected by the filled symbols throughout the plots in \cref{sec:results}, but the points involving velocity measurements are represented by hollow symbols due to the lack of a beam-smearing correction.
 
@@
 At $z\simeq1.0$ the galaxies have $log(M_{\star}/M_{\odot})=10.7$ and at $z\simeq2.3$ the median is $log(M_{\star}/M_{\odot})=10.9$, over an order-of-magnitude above the KDS median of $log(M_{\star}/M_{\odot})=9.8$.
-The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
+The rotation velocity is taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
 No tabulated values are provided for this survey, and so we cannot re-compute the mean and median values.
@@
 The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}/M_{\odot})=10.2$ at $z\simeq1.2$.
-An arctangent function is fit to the data and $V_{C}$ is extracted at $\simeq1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
+An arctangent function is fit to the data and $V_{C}$ is extracted at $\simeq1.7R_{1/2}$ and the $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
 We make use of tabulated values presented in this survey to compute the mean and median kinematic properties, plotted with filled symbols throughout \cref{sec:results}.
@@
 Only integrated velocity dispersions are presented for the full sample.
-In addition, \cite{Cresci2009} (C09) model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
-In this approach the $V_{C}$ value comes from the best-fitting model parameter and $\sigma_{int}$ is calculated using Equation \ref{eq:sins_sigma}, with the best-fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
+In addition, \citep[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
+In this approach, the $V_{C}$ value comes from the best-fitting model parameter and $\sigma_{int}$ is calculated using Equation \ref{eq:sins_sigma}, with the best-fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.
 
@@
 The $V_{C}$ and $\sigma_{int}$ values in C09 are likely biased towards rotation-dominated galaxies with a well-settled disk.
-Nonetheless we plot these values with filled symbols in \cref{sec:results} as a directly comparable dataset, omitting the $V_{C}/\sigma_{int}$ values and the rotation dominated fraction, which are listed for the full FS09 sample.
+Nonetheless, we plot these values with filled symbols in \cref{sec:results} as a directly comparable dataset, omitting the $V_{C}/\sigma_{int}$ values and the rotation dominated fraction, which are listed for the full FS09 sample.
 
@@
 The $\sigma_{int}$ errors for individual galaxies are generally very small, and for 3 galaxies the $\sigma_{int}$ value is consistent with 0 km\,s$^{-1}$.
-For the mean value computations we set these equal to the SINFONI resolution limit of 30 km\,s$^{-1}$.
+For the mean value computation for the full sample we set these equal to the SINFONI resolution limit of 30 km\,s$^{-1}$.
 A total of 6/11 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0 km\,s$^{-1}$, which we refer to as the AMAZE `Unconstrained' sample and represent these with hollow symbols throughout the plots in \cref{sec:results}.
+
+\noindent
 This Unconstrained sample also contains the galaxy s\_sa22a-M38, common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346 km\,s^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
@@
 These are plotted with filled symbols throughout \cref{sec:results}.
-We plot the quoted rotation-dominated fraction of 33$\%$, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation-dominated. \\
+We plot the quoted rotation-dominated fraction of 33$\%$ as a hollow symbol, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation-dominated. \\
 
@@
 As mentioned in \cref{subsec:3d_modelling}, the MCMC sampling provides distributions for each of the model parameters, from which we can extract the 84th and 16th percentile values as the +/- 1-$\sigma$ errors.
-During the following procedure $PA_{kin}$ is fixed to the maximum-likelihood value for all model evaluations.
+During the following procedure, $PA_{kin}$ is fixed to the maximum-likelihood value for all model evaluations.
 We proceed to reconstruct the beam-smeared and intrinsic dynamical models for each of the isolated field galaxies using the 16th and 84th percentile parameters, with the lower velocity 16th percentile model constructed using the upper limit on the inclination, and the 84th percentile model using the lower limit.
 To clearly distinguish the 1-$\sigma$ error regions for both the beam-smeared and intrinsic models, the region between the 16th and 84th percentile evaluations is shaded blue and red respectively in the velocity extaction panels throughout Figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies}.
-The +/- 1-$\sigma$ error values for both $V_{C}$ are then calculated using the the equations below, which also take into account the measurement errors with $\bar{\sigma}_{v_{obs}}$ equal to the average observational uncertainty extracted along $PA_{kin}$.
-The subscripts `16th' and `84th' denote the model from which the velocity has been extracted.
+The +/- 1-$\sigma$ error values for both $V_{C}$ are then calculated using the equations below, which also take into account the measurement errors, with $\bar{\sigma}_{v_{obs}}$ equal to the average observational uncertainty extracted along $PA_{kin}$.
+The subscripts `16th' and `84th' denote the parameters used to construct the model from which the velocity has been extracted.
 
@@
 with $\bar{\sigma}_{\sigma_{obs}}$ equal to the average of the velocity dispersion measurement errors.
-Once these quantities have been measured, the upper and lower errors on the ratio $\frac{v_{2.2}}{\sigma{o}}$ can be computed using equations \ref{eq:v_over_sig_plus} and \ref{eq:v_over_sig_minus}, and the same prescription is followed to find the errors on $\frac{V_{C}}{\sigma{int}}$.
+Once these quantities have been measured, the upper and lower errors on the ratio $V_{C}/\sigma_{int}$ can be computed using equations \ref{eq:v_over_sig_plus} and \ref{eq:v_over_sig_minus}.
 
@@
     The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
-    The purple symbols represent the extraction along $PA_{kin}$ from the residual map, and the two vertical dashed lines denote the intrinsic (inner) and convolved (outer) $2R_{1/2}$ values, with $V_{C}$ extracted at the convolved value.
+    The purple symbols represent the extraction along $PA_{kin}$ from the residual map, and the two vertical dashed lines denote the intrinsic (inner) and convolved (outer) $2R_{1/2}$ values, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value of the intrinsic and observed profiles respectively.
     The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.

### 2017-04-10 paper.tex
Ready for submission

@@
 Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep, multi-wavelength ancillary data.
-Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
-From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal-to-noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
+Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\,\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
+From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal-to-noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\,\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities.
 To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a wealth of imaging and spectroscopic data.
@@
 We selected targets from the various spectroscopic campaigns which have targeted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
-These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
+These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or $H\,\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
 The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\simeq20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
@@
 
-To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, allowing both dynamical and chemical abundance measurements.
+To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\,\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, allowing both dynamical and chemical abundance measurements.
 The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however, due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously.
@@
 
-\subsubsection{Applying {\tt GALFIT} to the imaging data}\label{subsubsec:galfitting}
-We used {\tt GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
+\subsubsection{Applying {\scriptsize GALFIT} to the imaging data}\label{subsubsec:galfitting}
+We used {\scriptsize GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
 The GOODS-S imaging data used is the latest release of the total field in {\it WFC3 F160W} band, which traces the rest-frame near-UV at $z\simeq3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
@@
 \noindent
-We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT}, and then extracted postage stamp regions around the galaxies in the KDS sample.
+We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\scriptsize GALFIT}, and then extracted postage stamp regions around the galaxies in the KDS sample.
 At this redshift, the galaxies are more compact and generally we could not resolve more complicated morphological features such as spiral arms and bars and so we followed the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of $n=1$.
@@
 This analysis provided us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
-Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, and maps for the full isolated field sample (see \cref{subsubsection:spaxel_fitting}) are plotted throughout Appendix \ref{app:kinematics_plots}.
-
-The errorbars produced by {\tt GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
+Example {\em HST} images and {\scriptsize GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, and maps for the full isolated field sample (see \cref{subsubsection:spaxel_fitting}) are plotted throughout Appendix \ref{app:kinematics_plots}.
+
+The errorbars produced by {\scriptsize GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
 Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
@@
 \begin{threeparttable}
-\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\tt GALFIT} \protect\citep{Peng2010_galfit}.}
+\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\scriptsize GALFIT} \protect\citep{Peng2010_galfit}.}
 \label{tab:phys-props}
@@
 
-As mentioned in \cref{subsubsec:galfitting}, the error reported by {\tt GALFIT} on the model $b/a$ value is unrealistically small.
+As mentioned in \cref{subsubsec:galfitting}, the error reported by {\scriptsize GALFIT} on the model $b/a$ value is unrealistically small.
 Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopted a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
@@
 \subsubsection{Position angles}\label{subsubsection:position_angle}
-The second {\tt GALFIT} parameter was $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
-We visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$ indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this was not the case it was usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
+The second {\scriptsize GALFIT} parameter was $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
+We visually inspected each of the {\scriptsize GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$ indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this was not the case it was usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
 We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2017}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
@@
 These properties are extracted via modelling emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
-We concentrated solely on the [O~{\sc III}]$\lambda$5007 emission line which always had signal-to-noise higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and was detected over a larger area of each IFU.
+We concentrated solely on the [O~{\sc III}]$\lambda$5007 emission line which always had signal-to-noise higher than both [O~{\sc III}]$\lambda$4959 and $H\,\beta$ and was detected over a larger area of each IFU.
 \\
@@
     In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated (13/38), dispersion-dominated (19/38) and merger categories (6/38).
-    For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map.
+    For each galaxy we plot on the top row the {\em HST} image, {\scriptsize GALFIT} model and {\scriptsize GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map.
     On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
@@
     Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
-    The merger candidate in the bottom grid requires several {\tt GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
+    The merger candidate in the bottom grid requires several {\scriptsize GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
     \label{fig:main_body_kinematic_grids}
@@
 \noindent
-The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction was determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line was set to follow a uniform distribution with a default width of 50 km\,s$^{-1}$.
-This default line width was selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\simeq3.0$ velocity dispersions, and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
+The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction was determined using the {\scriptsize GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line was set to follow a uniform distribution with a default width of 50 km\,s$^{-1}$.
+This default line width was selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the velocity dispersions of typical star-forming galaxies at $z\simeq3.0$, and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
 The reported errors on $\sigma_{int}$ take this assumption into account. \\
@@
 \noindent
-The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube was then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
+The simulated, intrinsic [O~{\sc III}]$\lambda$5007 cube was then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
 The velocity and velocity dispersion values were then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
@@
 
-Following the construction of a convolved model cube and the measurement of the beam-smeared maps we extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
+Following the construction of a convolved model cube and the measurement of the beam-smeared maps, we extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
 There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshifts.
@@
 In order to determine the beam-smearing correction factor, we also extracted the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
-The magnitude of the beam-smearing correction ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in Appendix \ref{appsubsec:model_errors}.
+The magnitude of the beam-smearing correction, ($V_{C}/V_{BS}$), has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in Appendix \ref{appsubsec:model_errors}.
 \\
@@
 
-By comparing the best-fitting simulated datacube with the assumption for the isotropic velocity dispersion we recovered the beam-smearing correction for each galaxy.
+By comparing the best-fitting simulated datacube with the assumption for the isotropic velocity dispersion, we recovered the beam-smearing correction for each galaxy.
 The 2D beam-smearing correction map, $\sigma_{BS}$, was computed on a spaxel-by-spaxel basis as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50 km\,s$^{-1}$ i.e.
 $\sigma_{BS,i} = \sigma_{simulated,i} - \sigma_{assumed,i}$ (where $\sigma_{assumed,i}$ was fixed at 50 km\,s$^{-1}$ as described in \cref{subsubec:model_cube} and $\sigma_{simulated,i}$ is the simulated velocity dispersion recovered under this assumption).
-The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS,i}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
+The impact of the value of $\sigma_{assumed}$ on the magnitude of the $\sigma_{BS,i}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
 We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we did not attempt to fit the velocity dispersions, this is a feature the model could not reproduce.
 
-To measure the $\sigma_{int}$ value for each galaxy in our sample we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{g,i}$ is the value in the ith spaxel recovered from the gaussian-fit.
+To measure the $\sigma_{int}$ value for each galaxy in our sample, we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{g,i}$ is the value in the ith spaxel recovered from the gaussian-fit to the [O~{\sc III}]$\lambda$5007 emission line.
 
@@
 The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} km\,s^{-1}$ and $71.0^{+5.0}_{-4.8} km\,s^{-1}$ respectively, higher than for typical star-forming galaxies at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
-The magnitude of the beam-smearing correction ($\sigma_{int}/\sigma_{obs}$) has a mean and median value of 0.81 and 0.79 respectively for the isolated field sample. \\
-
-\noindent
-To test the robustness of our beam-smearing correction approach we also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{1/2}/R_{psf}$, detailed in Johnson et al.
-(in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
+The magnitude of the beam-smearing correction, ($\sigma_{int}/\sigma_{obs}$), has a mean and median value of 0.81 and 0.79 respectively for the isolated field sample. \\
+
+\noindent
+To test the robustness of our beam-smearing correction approach, we also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{1/2}/R_{psf}$, detailed in Johnson et al.
+(in prep) and used to evaluate the final kinematic parameters in \cite{Harrison2017}.
 These correction factors were applied to $V_{BS}$ and $\sigma_{obs}$ in order to compute $V_{C}$ and $\sigma_{int}$.
@@
 \subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}
-The dynamical model parameter $PA_{Kin}$ was compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
-This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 30^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
+The dynamical model parameter $PA_{Kin}$ was compared with $PA_{morph}$ computed by {\scriptsize GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
+This follows the analysis described in e.g.
+\citealt{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017}, where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 30^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
 Significant misalignment between the two axes can be a signature of galaxy interaction.
 
-The resolved KDS galaxies at $z\simeq3.5$ have generally larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
-For the majority of galaxies we are not in a regime where prominent morphological features are resolved in the {\em HST} imaging so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2017}.
+The resolved KDS galaxies at $z\simeq3.5$ generally have larger $\Delta PA$ values than those at lower redshift (median $\Delta PA = 37^{\circ}$) and this observation has several potential explanations.
+For the majority of galaxies we are not in a regime where prominent morphological features are resolved in the {\em HST} imaging, so that $PA_{morph}$ is biased by single \Sers fits as described in \cite{Rodrigues2017}.
 Another factor which could be partially driving increased misalignment in the KDS is the use of the full observed 2D velocity field to determine the kinematic position angle.
@@
 If the direction of the `zero-velocity strip' across the centre of the velocity maps is not perpendicular to the line connecting the velocity extrema, the $PA_{Kin}$ determined from MCMC will be different to the $PA_{Kin}$ determined from rotation (e.g.
-GOODS-S galaxy bs006541 in Appendix Figure \ref{fig:dispersion_dominated_galaxies}).
-As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ (which differs typically by only a few degrees) makes only a small difference to the final $V_{C}$ values, with the errors dominated by measurement uncertainties and model assumptions.
+GOODS-S galaxy bs006541 in Appendix \ref{fig:dispersion_dominated_galaxies}).
+As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ (which differs from $PA_{Kin}$ typically by only a few degrees) makes only a small difference to the final $V_{C}$ values, with the errors dominated by measurement uncertainties and model assumptions.
 
@@
 We proceeded to further divide the isolated field sample galaxies into two subsamples on the basis of the ratio $V_{C}/\sigma_{int}$.
-This is a simple empirical diagnostic for whether a galaxy is `Rotation-Dominated' with $V_{C}/\sigma_{int} > 1$ or `Dispersion-Dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
+This is a simple empirical diagnostic for whether a galaxy is `rotation-dominated' with $V_{C}/\sigma_{int} > 1$, or `dispersion-dominated' with $V_{C}/\sigma_{int} < 1$  \citep[i.e.
 a method to measure the prevalence of rotational and random motions;][]{Epinat2012,Wisnioski2015,Stott2016,Harrison2017}.
@@
 In 8/9 resolved KDS cluster galaxies we identified multiple photometric components, translating into a merger rate of 89\%  (see Table \ref{tab:pointings}).
-The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they were drawn from a higher density environment, and these interactions will inevitably have major consequences for the consumption and stripping of gas as well as the morphological and dynamical evolution within these galaxies.
-The observation of frequent mergers which cause major kinematic disturbances is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
+The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they were drawn from a higher density environment, and these interactions will inevitably have major consequences for the consumption and stripping of gas, as well as the morphological and dynamical evolution within these galaxies.
+The observation of frequent mergers, which cause major kinematic disturbances, is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
 As mentioned above, we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
@@
 In the remaining sample of 38 field environment galaxies we identified 6 merger candidates, giving a field galaxy merger rate of 16\%, which constitute the `merger field sample'.
-The remaining 32 galaxies constitute the `isolated field sample', for which we measured morphological parameters using {\tt GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and Table \ref{tab:phys-props}) and derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and Table \ref{tab:kin_props}).
+The remaining 32 galaxies constitute the `isolated field sample', for which we measured morphological parameters using {\scriptsize GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and Table \ref{tab:phys-props}) and derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and Table \ref{tab:kin_props}).
 \\
@@
     {\it Right:} The mean, median and distributions of the comparison sample $V_{C}$ measurements are plotted against redshift.
-    The symbol positions with black errorbars (some not visible) show the mean values and the horizontal filled and grey bars show the median values and associated errors, and the mean mass of each survey (in units of log($M_{\star}/M_{\odot}$)) is listed beside the survey name.
+    The symbol positions with black errorbars (some not visible), show the mean values and the horizontal filled and grey bars show the median values and associated errors.
     Note that the median errors for the AMAZE Clean sample are shaded orange to avoid confusion with the full sample.
+    The filled symbols and shaded regions denote surveys deemed directly comparable (as explained in Appendix \protect\ref{app:comparison_samples}), and the mean mass of each survey (in units of log($M_{\star}/M_{\odot}$)) is listed beside the survey name.
     The $V_{C}$ distributions in each of the individual studies are wide, reflecting the galaxy diversity within each sample.
@@
 We plot also the five galaxies from the AMAZE Clean ($z\simeq3$) sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$.
-The $z\simeq0.9$ fit parameters are consistent with those measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
+The $z\simeq0.9$ fit parameters are consistent with those measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$, for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\,\alpha$ emission.
 In \cite{Reyes2011}, $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
@@
 $V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
-Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95km\,s^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
+Using the average stellar mass values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95km\,s^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
 This value is greater than the mean and median values of the isolated field sample, but comparable to the mean and median of the rotation dominated galaxies, suggesting that rotation in these systems could support, at most, the stellar mass of the galaxy.
@@
 Scatter above and below the RDF $\propto z^{-0.2}$ evolution line may be attributed in part to the different mean stellar masses of the surveys, with those that have larger stellar masses tending to scatter above this line.
-This draws again from the idea that higher $M_{\star}$ values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the rotation-dominated fraction higher (see \cref{sec:discussion}).
+This draws again from the idea that higher stellar mass values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the rotation-dominated fraction higher (see \cref{sec:discussion}).
 \\\\
@@
 
-OJT acknowledges the support of STFC under grant number ST/L000784/1.
 MC and OJT acknowledge the KMOS team and all the personnel of the European Southern Observatory Very Large Telescope for outstanding support during the KMOS GTO observations.
@@
 In \cref{sec:results} we compare the isolated field sample results with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
-The galaxy selection criteria in these surveys, with the exception of DYNAMO \citep{Green2014} as discussed below, consistently picks out representative star-forming galaxies at each epoch and the dynamical properties are traced by observing either the [O~{\sc III}]$\lambda$5007, [O~{\sc II}]$\lambda$3727,3729 or $H\alpha$ ionised gas emission lines.
+The galaxy selection criteria in these surveys, with the exception of DYNAMO \citep{Green2014} as discussed below, consistently picks out representative star-forming galaxies at each epoch and the dynamical properties are traced by observing either the [O~{\sc III}]$\lambda$5007, [O~{\sc II}]$\lambda$3727,3729 or $H\,\alpha$ ionised gas emission lines.
 
@@
 \subsection{GHASP ($\bmath{z\simeq0}$)}\label{subsec:GHASP}
-The GHASP survey \citep[E08]{Epinat2008a,Epinat2008} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}/M_{\odot})=10.6$ in the local universe ($z\simeq0$) to produce 3D H$\alpha$ datacubes.
+The GHASP survey \citep[E08]{Epinat2008a,Epinat2008} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}/M_{\odot})=10.6$ in the local universe ($z\simeq0$) to produce 3D H$\,\alpha$ datacubes.
 The data extend out to several half-light radii and in each case tilted ring models are fit to determine $V_{C}$ at large radii where the rotation curves have flattened, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
@@
 \subsection{DYNAMO ($\bmath{z\simeq0.1}$, but selected with physical properties resembling $\bmath{z\simeq2}$)}\label{subsec:DYNAMO}
-In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}/M_{\odot})=10.3$ at $z\simeq0.1$ are presented.
+In the DYNAMO survey \citep[G14]{Green2014}, H$\,\alpha$ IFU data of 67 galaxies with median $log(M_{\star}/M_{\odot})=10.3$ at $z\simeq0.1$ are presented.
 The selection criteria is such that half of the sample have high sSFRs representative of SFGs at $z\simeq2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\simeq2$ SFGs.
@@
 \subsection{MUSE and KMOS ($\bmath{z\simeq0.65}$ and $\bmath{z\simeq1.25}$)}\label{subsec:MUSE_and_KMOS}
-In \cite{Swinbank2017} a collection of $\simeq400$ star-forming galaxies observed in [O~{\sc II}]$\lambda$3727,3729 with MUSE and H$\alpha$ emission with KMOS is described.
+In \cite{Swinbank2017} a collection of $\simeq400$ star-forming galaxies observed in [O~{\sc II}]$\lambda$3727,3729 with MUSE and $H\,\alpha$ emission with KMOS is described.
 Of this parent sample, inclination corrected velocities and intrinsic velocity dispersions are derived for 179 galaxies, to which we make comparisons.
@@
 \subsection{KROSS ($\bmath{z\simeq0.9}$)}\label{subsec:KROSS}
-We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\simeq600$ SFGs with median $log(M_{\star}/M_{\odot})=9.9$ and $z\simeq0.9$.
+We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS $H\,\alpha$ observations of $\simeq600$ SFGs with median $log(M_{\star}/M_{\odot})=9.9$ and $z\simeq0.9$.
 $V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) with the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
@@
 \subsection{KMOS$^{3D}$ ($\bmath{z\simeq1.0}$ and $\bmath{z\simeq2.3}$)}\label{subsec:kmos_3d}
-The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\simeq191$ massive SFGs across two redshift slices. 
+The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\,\alpha$ observations of $\simeq191$ massive SFGs across two redshift slices. 
 At $z\simeq1.0$ the galaxies have $log(M_{\star}/M_{\odot})=10.7$ and at $z\simeq2.3$ the median is $log(M_{\star}/M_{\odot})=10.9$, over an order-of-magnitude above the KDS median of $log(M_{\star}/M_{\odot})=9.8$.
@@
 \subsection{MASSIV ($\bmath{z\simeq1.2}$)}\label{subsec:MASSIV}
-The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}/M_{\odot})=10.2$ at $z\simeq1.2$.
+The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\,\alpha$ observations of 50 SFGs with median $log(M_{\star}/M_{\odot})=10.2$ at $z\simeq1.2$.
 An arctangent function is fit to the data and $V_{C}$ is extracted at $\simeq1.7R_{1/2}$ and the $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
@@
 \subsection{SINS ($\bmath{z\simeq2.0}$)}\label{subsec:SINS}
-The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}/M_{\odot})=10.6$ at $z\simeq2.0$.
+The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\,\alpha$ observations of 80 massive galaxies with median $log(M_{\star}/M_{\odot})=10.6$ at $z\simeq2.0$.
 Galaxies in this sample are classified as rotation or dispersion-dominated following FS09 section 9.5.1 which classifies rotation-dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
@@
 \subsection{LAW 09 ($\bmath{z\simeq2.3}$)}\label{subsec:law_09}
-In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}/M_{\odot})=10.0$ at $z\simeq2.3$.
+In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\,\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}/M_{\odot})=10.0$ at $z\simeq2.3$.
 The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
@@
     \caption{We plot the kinematic grids for the 13/32 isolated field sample galaxies classified as rotation-dominated.
-    For each galaxy we plot the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian-fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
+    For each galaxy we plot the {\em HST} image, {\scriptsize GALFIT} model and {\scriptsize GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian-fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
     The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.

### 2017-04-10 paper.tex
submission version

@@
 We present dynamical measurements from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS), which is comprised of 77 typical star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$.
-These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
+These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
 The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, revealing that the increasing average $\sigma_{int}$ with increasing redshift, reported for $z\lesssim2$, continues out to $z\simeq3.5$.
@@
 $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
-These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by a combination of the increasing gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and which may provide significant pressure support against gravity on the galactic disk scale.
+These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by a combination of the increasing gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and which may provide significant pressure support against gravity on the galactic disk scale.
 \end{abstract}
@@
 \begin{keywords}
-galaxies:kinematics and dynamics -- galaxies:evolution -- galaxies:integral field spectroscopy
+galaxies:high-redshift ---- galaxies:kinematics and dynamics ---- galaxies:evolution
 \end{keywords}
@@
 At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
-This assumes that high redshift, main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
+This assumes that high-redshift, main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e.
 how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
@@
 When interpreted in tandem with high-resolution imaging data from the {\it Hubble Space Telescope (HST)}, these data provide information about the range of physical processes which are driving galaxy evolution.
-In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2017,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high redshift campaigns.
+In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2017,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high-redshift campaigns.
 
@@
 There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016,Harrison2017,Straatman2017,Ubler2017}.
-Systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
-Additionally, there has been increasing focus in recent years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
+Systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
+Additionally, there has been increasing focus in recent years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high-redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
 These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotation velocities \citep{Burkert2010}.
@@
 The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
-The key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
+The key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
 We seek to probe both a `field' environment in which the density of galaxies is typical for this redshift and a `cluster' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
@@
 \cite{Bruce2012} present a detailed error analysis of the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploited during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
-We adopted a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high redshift galaxies (see Appendix \ref{app:kin_error_estimates}).
+We adopted a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high-redshift galaxies (see Appendix \ref{app:kin_error_estimates}).
 
@@
 %    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\simeq3.5$.
-%    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
+%    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high-redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
 %    The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
@@
 The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they were drawn from a higher density environment, and these interactions will inevitably have major consequences for the consumption and stripping of gas, as well as the morphological and dynamical evolution within these galaxies.
-The observation of frequent mergers, which cause major kinematic disturbances, is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
+The observation of frequent mergers, which cause major kinematic disturbances, is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high-redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
 As mentioned above, we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
@@
 Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
-High redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
+High-redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
 Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
@@
 $M_{\star}$ plane.
-This is an interesting relationship to explore as it has been suggested that rotation velocity alone may not be a good tracer of total dynamical mass at high redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
+This is an interesting relationship to explore as it has been suggested that rotation velocity alone may not be a good tracer of total dynamical mass at high-redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
 However, the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
-All of these processes are also more prevalent at high redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret.
-\\
-
-\noindent
-We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high redshift.
+All of these processes are also more prevalent at high-redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret.
+\\
+
+\noindent
+We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high-redshift.
 The beam-smearing corrected $\sigma_{int}$ values, with distribution median, 16th percentile and 84th percentile equal to $71.0km\,s^{-1}$, $48.0km\,s^{-1}$ and $85.4km\,s^{-1}$ respectively, are larger than in the local universe where typically $\sigma_{int} = 10-20km\,s^{-1}$ \citep{Epinat2008a} (see \cref{subsubsec:sigma_evolution} and \cref{sec:discussion} for a discussion).
@@
 
-\subsection{The origin and impact of increased velocity dispersions at high redshift}\label{discussion_increase_in_sigma}
+\subsection{The origin and impact of increased velocity dispersions at high-redshift}\label{discussion_increase_in_sigma}
 
@@
 
-Previous studies have claimed that the elevated velocity dispersions observed at high redshift are a consequence of both internal and external processes.
+Previous studies have claimed that the elevated velocity dispersions observed at high-redshift are a consequence of both internal and external processes.
 \cite{Law2009} observe galaxies with elevated velocity dispersions at $z\simeq2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.
@@
 Following this, $\sigma_{int}$ decreases over time as ordered rotation begins to dominate and pressure support becomes increasingly insignificant \citep[e.g.][]{Burkert2010,Ubler2017,Genzel2017,Lang2017}.
-This is in line with the evolution of gas fractions observed at intermediate and high redshifts \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.
+This is in line with the evolution of gas fractions observed at intermediate and high-redshifts \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.
 
@@
 \noindent
-This relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
+This relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
 In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.
@@
 \citealt{ForsterSchreiber2006,Burkert2010}) and {\it a} = $\sqrt{2}$ (as for a disk with constant rotation velocity \citealt{Wisnioski2015}), this range corresponds to $V_{C} = 70-200km\,s^{-1}$, which is roughly the velocity range spanned by our comparison samples, and the solid grey line corresponds to $V_{C} = 128km\,s^{-1}$.
-Whilst the KDS mean rotation velocity sits at the bottom of this range, possible explanations are: \textbf{(1)} The rotation velocities of the KDS galaxies are underestimated as a result of the velocity dispersion contribution discussed above; \textbf{(2)} $Q_{crit} \ne 1$ or ${\it a} \ne \sqrt{2}$ as a consequence of changing physical conditions at high redshift.
+Whilst the KDS mean rotation velocity sits at the bottom of this range, possible explanations are: \textbf{(1)} The rotation velocities of the KDS galaxies are underestimated as a result of the velocity dispersion contribution discussed above; \textbf{(2)} $Q_{crit} \ne 1$ or ${\it a} \ne \sqrt{2}$ as a consequence of changing physical conditions at high-redshift.
 \\
@@
 Although the details of the coefficients of Equation \ref{eq:sigma_increase} are unclear (i.e.
-$V_{C}$ is not fixed at one value for the comparison samples and is itself linked to stellar mass and both $Q_{crit}$ and {\it a} could vary with redshift), the shape of the velocity dispersion evolution appears to follow that of the gas fraction, as suggested by the model.
+$V_{C}$ is not fixed at one value for the comparison samples and is itself linked to stellar mass, and both $Q_{crit}$ and {\it a} could vary with redshift), the shape of the velocity dispersion evolution appears to follow that of the gas fraction, as suggested by the model.
 The difference between the slopes in the left and right panels highlights the role of stellar mass in the kinematic settling of galaxies between $z\simeq3$ and the local universe. 
@@
 Rotation-dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions (shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}), constituting only $\simeq1/3$ of the isolated field sample at $z\simeq3.5$.
-This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale length \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
-Recent results indicate that these systems may become strongly baryon-dominated on the galaxy disk scale at high redshift \citep{Ubler2017,Lang2017,Genzel2017}, which could imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.
-
-The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
-The nature of dispersion-dominated galaxies at high redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
-The AO observations show that in some cases galaxies which are clasified as dispersion-dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
+This suggests that we are probing more chaotic and unstable systems, subject to gravitational instabilities and collapse on the disk scale length \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
+Recent results indicate that these systems may become strongly baryon-dominated on the galaxy disk scale at high-redshift \citep{Ubler2017,Lang2017,Genzel2017}, which could imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.
+
+The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high-redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
+The nature of dispersion-dominated galaxies at high-redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
+The AO observations show that, in some cases, galaxies which are clasified as dispersion-dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
 This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
@@
 
-Bringing the above points together, turbulent motions consume an increasingly significant fraction of the energy budget at high redshift when typical star-forming galaxies are at earlier evolutionary stages.
+Bringing the above points together, turbulent motions consume an increasingly significant fraction of the energy budget at high-redshift when typical star-forming galaxies are at earlier evolutionary stages.
 The KDS isolated field sample presents an extension of these trends to higher redshift, where galaxies are even more likely to be dispersion-dominated, and pressure support may be more significant than explored at $z\simeq2.3$ \citep{Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
-However, the precise interpretation of $\sigma_{int}$ measured from ionised gas emission lines remains unclear, and future observations of both stellar and gaseous velocity dispersions in tandem with {\it JWST} will allow for unambigous investigations into the nature of gaseous velocity dispersions at high redshift.
+However, the precise interpretation of $\sigma_{int}$ measured from ionised gas emission lines remains unclear, and future observations of both stellar and gaseous velocity dispersions in tandem with {\it JWST} will allow for unambigous investigations into the nature of gaseous velocity dispersions at high-redshift.
 \\
@@
     \item When considering the rotation-dominated galaxies alone, the mean and median rotation velocities are $V_{C} = 96.7^{+7.3}_{-7.2}km\,s^{-1}$ and $V_{C} = 93.0^{+12.0}_{-12.5}km\,s^{-1}$ respectively, which are roughly equivalent to a simple lower limit virial theorem calculation using the mean mass and half-light radius of the sample.
-    This suggests that pressure forces, which are more significant at high redshift, may play a role in supporting the total mass in all of the galaxies in the isolated field sample \citep[e.g.][]{Burkert2010}.
+    This suggests that pressure forces, which are more significant at high-redshift, may play a role in supporting the total mass in all of the galaxies in the isolated field sample \citep[e.g.][]{Burkert2010}.
     \item 13/32 isolated field sample galaxies are rotation-dominated and 19/32 are dispersion-dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
@@
     \item We plot mean $\sigma_{int}$ values computed in a consistent way for SFG samples spanning a wide redshift baseline (the comparison samples described in Appendix \ref{app:comparison_samples}), finding a sharp increase in $\sigma_{int}$ values between $z=0-1$ and a fairly shallow increase thereafter, mediated by the mean $M_{\star}$ of the galaxy samples (right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
-    This is in line with a simple equilibrium model prescription in which the gas fractions and the impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to increase random motions within high redshift galaxies.
+    This is in line with a simple equilibrium model prescription in which the gas fractions and the impact of several physical mechanisms such as accretion of gas from the IGM, stellar feedback and turbulence increase with redshift and combine to increase random motions within high-redshift galaxies.
 

### 2017-05-16 paper.tex
About to address referee comments and other comments

@@
 We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
-To account for this, a polynomial function is fit, using the python package {\tt LMFIT} \citep{Newville2014}, which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
+To account for this, a polynomial function is fit, using the python package {\scriptsize LMFIT} \citep{Newville2014}, which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn.
 \\
@@
 The width of the extraction region was large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky-line residuals.
-A single gaussian model was fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
+A single gaussian model was fit to the extraction region, again using {\scriptsize LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
 These parameters, along with the estimate of the noise in the datacube, were used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not.
@@
 \begin{enumerate}[label=(\roman*),align=left]
-\item The uncertainties on any of the parameters of the gaussian-fit as returned by {\tt LMFIT} must not exceed 30\%
+\item The uncertainties on any of the parameters of the gaussian-fit as returned by {\scriptsize LMFIT} must not exceed 30\%
 \item $\frac{S}{N_{m}} > 3$
@@
 Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
-However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Simons2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
+However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
 At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, and the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} is consistent with the $z\simeq0$ relation.
@@
 
+OJT acknowledges the financial support of the Science and Technology Facilities Council through a studentship award. 
 MC and OJT acknowledge the KMOS team and all the personnel of the European Southern Observatory Very Large Telescope for outstanding support during the KMOS GTO observations.

### 2017-05-19 paper.tex
highlighted and ready for re-submission

@@
 The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, revealing that the increasing average $\sigma_{int}$ with increasing redshift, reported for $z\lesssim2$, continues out to $z\simeq3.5$.
-Only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
+Only $36 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
 After carefully selecting comparable star-forming samples at multiple epochs, we find that the rotation-dominated fraction evolves with redshift with a $z^{-0.2}$ dependence. 
@@
 
-\noindent
 In this paper we present new results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
 With this survey, we aim to complement existent studies by providing deep IFS data for the largest number of galaxies at this redshift.
-By making use of KMOS (with integration times of 7.5-9 hours), we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
+By making use of KMOS (with integration times of 7.5-9 hours), we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly \textbf{doubling} the number of galaxies observed via IFS at $z > 3$.
 In order to interpret the evolution of the physical properties of typical star-forming galaxies we have carefully constructed a set of comparison samples spanning $0 < z < 3$.
@@
 
-\noindent
 The structure of the paper is as follows.
@@
 The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\simeq3.5$, probing a representative section of the galaxy main-sequence.
-The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
+The addition of these data approximately \textbf{doubles} the number of galaxies observed via IFS at this redshift \textbf{\citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011,Troncoso_2014}}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution.
 The key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
@@
  \hline
- \scriptsize{\bf GOODS-S-P1(field)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & {\it K} & 32.4 & 0.50 \\
+ \scriptsize{\bf GOODS-S-P1(field)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 17 & 85 & 14 & 70 & 2 & 17 & {\it K} & 32.4 & 0.50 \\
 \scriptsize{\bf GOODS-S-P2(field)} & 03:32:32.217 & $-$27:43:08.000 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & {\it K} & 31.8 & 0.52 \\
@@
 
-\noindent
 We prepared each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
@@
 
-\noindent
 The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
@@
 
-\noindent
 This paper is concerned with the spatially-resolved kinematics of the KDS galaxies.
@@
 The SPARK recipes were used to create dark frames and to flatfield, illumination correct and wavelength calibrate the raw data.
-An additional step, which is not part of the standard reduction process, was carried out at this stage, which is to address readout channel bias.
-Differences in the readout process across each 64-pixel wide channel on the detector image lead to varying flux baselines in these channels.
+An additional step, which is not part of the standard reduction process, was carried out at this stage, to address readout channel bias.
+Differences in the readout process within each 64-pixel wide channel on the detector image lead to varying flux baselines \textbf{across each of the individual exposures}.
 We corrected back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.
-
-\noindent
+\textbf{This is a separate issue to non-uniform illumination across the detectors, which is corrected by applying the illumination correction frame to the stacked datacubes}.
+
 Standard star observations were carried out on the same night as the science observations and were processed in an identical manner to the science data.
@@
 
-\noindent
 Sky subtraction was enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
@@
 
-\noindent
 We stacked all 300s exposures for each galaxy which pass the seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
@@
 
-\noindent
-The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det} = 62/77$ $(81\%)$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
+The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det} = 63/77$ $(82\%)$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.
 
@@
 
-\noindent
 The difference in position of these relations highlights the main-sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\simeq2.5-3.5$.
@@
 When taken together, both panels indicate that the KDS sample is representatitve of typical star-forming galaxies at $z>3$.
-
-\subsubsection{Sample summary}\label{subsubsec:sample_summary}
-We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey.
-By processing the observations, we have constructed a datacube for each of these galaxies, finding integrated [O~{\sc III}]$\lambda$5007 in 62/77 targets.
-We have also derived $M_{\star}$ values and SFRs from SED modelling, finding that these values place the KDS galaxies into regions of parameter space spanned by typical star-forming galaxies at this redshift.
-Three KMOS pointings cover the field environment and one pointing covers a cluster environment at the heart of the SSA22 protocluster, and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
-Throughout the following analysis sections we describe the use of high-resolution imaging to make morphological measurements for the KDS galaxies and the extraction of kinematic properties for the galaxies using the [O~{\sc III}]$\lambda$5007 emission line.
-Chemical abundance measurements for the KDS galaxies in both the field and cluster environments will be presented in a future work.
 
@@
 
-\noindent
 We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\scriptsize GALFIT}, and then extracted postage stamp regions around the galaxies in the KDS sample.
@@
 This method was justified by the recovery of similar mean $\chi^{2}$ values when fitting floating \Sers index models and bulge/disk models with both an $n=1$ and $n=4$ component (following the procedure described in \citealt{Bruce2012}) to those recovered from the fixed exponential disk fit.
-Additionally, 22 GOODS-S objects were also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is $n=1.2$.
+Additionally, \textbf{24} GOODS-S objects were also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is $n=1.2$.
+\textbf{Of these 24 galaxies, 2 are found to have $n>2.5$ (lbg\_32 and lbg\_109, see Appendix \ref{app:kinematics_plots}), although both show disk-like kinematics with a monotonic velocity gradient.
+The galaxy lbg\_32 can be fit with an $n=1$ \Sers profile with small residuals, however lbg\_109 has a centrally concentrated light distribution which is not well captured by the $n=1$ profile.
+This demonstrates that fitting exponential flux distributions is a valid approach for the sample at large.}
 The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors were applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2}\simeq1.68 R_{D}$ (see Appendix \ref{subsec:KROSS}).
@@
 
-\noindent
 This analysis provided us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
@@
  \hline
-ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & $b/a$ & i$^{\circ}$$^{b}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{c}$ \\
+ID              & RA       & Dec       & z     & K$_{AB}^{a}$     & $log(M_{\star}/M_{\odot})^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\
  \hline
 b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.8 & 0.36        & 72        & 9     & 1.57      \\
-b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.8  & 0.28        & 78        & 146   & 0.52      \\
+b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.60   & 9.8  & 0.28        & 78        & 146   & 0.52      \\
 bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.8 & 0.50         & 61        & 146   & 1.91      \\
@@
 lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.6    & 0.52        & 60        & 15    & 0.87      \\
+lbg\_121        & 03:32:19.606 & $-$27:48:40.032 & 3.708      & 25.36  & 9.1    & 0.65        & 50        & 106    & 0.42      \\
 lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.0  & 0.56         & 57        & 50    & 0.78      \\
@@
       \small
-      \item $^{a}$ Representative error of 0.2 dex from SED modelling used throughout this study
-      \item $^{b}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
-      \item $^{c}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
+      \item $^{a}$ \textbf{K-band magnitude errors are typically $\pm0.05$ magnitudes.}
+      \item $^{b}$ Representative error of 0.2 dex from SED modelling used throughout this study \textbf{(see \cref{subsubsec:sed_fitting})}.
+      \item $^{c}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
+      \item $^{d}$ Fixed 10 percent $R_{1/2}$ error assumed (see \protect\cref{subsubsection:half-light_radii}).
       \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ set to $PA_{kin}$ value; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
@@
 
-\noindent
 To derive the inclination, we selected a value for $q_{0}$, and following the discussion in \citep{Law2012a} we chose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
@@
 %In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).
-\noindent
+
 \cite{Bruce2012} present a detailed error analysis of the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploited during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
@@
 
-\noindent
 To measure $R_{1/2}$ for the 4 galaxies without {\em HST} coverage, we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
@@
 
-We proceeded to extract 2D kinematic measurements from the 62 KDS datacubes detected in integrated [O~{\sc III}]$\lambda$5007 emission by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
+We proceeded to extract 2D kinematic measurements from the 63 KDS datacubes detected in integrated [O~{\sc III}]$\lambda$5007 emission by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
 The sample was then refined to galaxies which are spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission line in order to make dynamical measurements.
@@
 \subsubsection{Spaxel Fitting}\label{subsubsection:spaxel_fitting}
-We aimed to extract two-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 62 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
+We aimed to extract two-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 63 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
 These properties are extracted via modelling emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
@@
 
-\noindent
 Each 0.1$^{\prime\prime}$ spaxel across a datacube was considered in turn.
@@
 
-\noindent
 The signal in each spaxel was taken as the sum of the flux values across the spectral extraction region, $F_{i,object}$, as shown in Equation \ref{eq:signal}, where S denotes the signal.
@@
 
-\noindent
 The criteria for accepting the fit within a given spaxel are as follows:
@@
 
-\noindent
 We imposed a further criterion to help remove fits to spectral features unrelated to the galaxy (e.g.
@@
 
-\noindent
 From the gaussian-fit, we recovered the centre, $\lambda_{g}$, the width, $\sigma_{g}$, and the area, $F_{g}$.
@@
 
-\noindent
 To estimate the errors on the observed quantities, the gaussian-fit was repeated 1000 times, with each flux value in the extraction region perturbed by the noise value, $N_{m}$.
@@
 
-\noindent
 If a spaxel did not meet the criteria, we follow the procedure described in \cite{Stott2016} and binned with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
@@
 
-\noindent
-The process was automated and applied to each of the 62/77 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
+The process was automated and applied to each of the 63/77 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
 Following the fitting procedure, the galaxies were clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map was equivalent to or greater than the seeing disk.
 For each pointing, the number of resolved galaxies, N$_{Res}$, was added to Table \ref{tab:pointings}.
-We find that 47/77 (76\%) of the detected KDS galaxies across both the field (38/47) and cluster (9/47) environments were spatially-resolved and showed clear velocity structure.
-The 15/77 galaxies which were not spatially-resolved were dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
+We find that 48/63 (76\%) of the detected KDS galaxies across both the field (39/48) and cluster (9/48) environments were spatially-resolved and showed clear velocity structure.
+The 15/63 (24\%) galaxies which were not spatially-resolved were dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
 The physical properties of all spatially-resolved galaxies in both GOODS-S and SSA22 are listed in Table \ref{tab:phys-props}. \\
 
-\noindent
 The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
-6/38 (16\%) of the resolved galaxies across the 3 field environment pointings and almost all (8/9) of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
+6/39 (15\%) of the resolved galaxies across the 3 field environment pointings and almost all (8/9) of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
 We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in Figure \ref{fig:merger_galaxies}.
-The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
-The 32/38 morphologically isolated field galaxies which are spatially resolved are referred to as the `isolated field sample' throughout the remainder of the paper.
+The remaining 6/39 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
+The 33/39 morphologically isolated field galaxies which are spatially resolved are referred to as the `isolated field sample' throughout the remainder of the paper.
 
@@
     \caption{We plot the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
-    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated (13/38), dispersion-dominated (19/38) and merger categories (6/38).
+    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated (14/39), dispersion-dominated (19/39) and merger categories (6/39).
     For each galaxy we plot on the top row the {\em HST} image, {\scriptsize GALFIT} model and {\scriptsize GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map.
@@
 
-\noindent
 with `r' measured as the distance from the centre of rotation.
@@
 
-\noindent
 The velocity decreases with a factor of cos($\phi$) from the kinematic position axis, where $\phi$ is the angle measured clockwise from the axis, which points to the direction of the positive side of the velocity field.
@@
 
-\noindent
 The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction was determined using the {\scriptsize GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line was set to follow a uniform distribution with a default width of 50 km\,s$^{-1}$.
@@
 
-\noindent
 The simulated, intrinsic [O~{\sc III}]$\lambda$5007 cube was then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
@@
 
-\noindent
 where $\delta_{v_{i}}$ are the observed velocity errors, $d_{i}$ are the datapoints and $M_{i}$ are the convolved model velocity values.
@@
 
-\noindent
-In 13/38 of the isolated field sample galaxies, the intrinsic $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model was greater than the last observed radius, however only 2 galaxies required extrapolation > 0.4$^{\prime\prime}$ (i.e.
+In 14/39 of the isolated field sample galaxies, the intrinsic $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model was greater than the last observed radius, however only 2 galaxies required extrapolation > 0.4$^{\prime\prime}$ (i.e.
 2 KMOS pixels) with a mean extrapolation of 0.17$^{\prime\prime}$.
@@
 
-\noindent
+\textbf{In Equation \ref{eq:owen_sigma} we have subtracted the beam-smearing correction linearly following the analysis presented in Appendix A of \cite{Stott2016}, which shows that linear subtraction recovers input velocity dispersion values more accurately than subtraction in quadrature.
+However, we note that if quadrature subtraction is applied the sample mean velocity dispersion increases by $\simeq 5\%$, which does not affect the results of this paper.}
 The median of the $\sigma_{cor,i}$ map is taken as the $\sigma_{int}$ value for each galaxy and the median of the observed map is the $\sigma_{obs}$ value (see Table \ref{tab:kin_props}).
@@
 
-\noindent
 To test the robustness of our beam-smearing correction approach, we also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{1/2}/R_{psf}$, detailed in Johnson et al.
@@
 As a test, we have verified that extracting $V_{C}$ values along $PA_{rot}$ (which differs from $PA_{Kin}$ typically by only a few degrees) makes only a small difference to the final $V_{C}$ values, with the errors dominated by measurement uncertainties and model assumptions.
+\textbf{Further, the increased prevalence of random motions at $z\simeq3.5$ (see \cref{subsubsec:sigma_evolution}), in comparison to at intermediate redshift, could partially explain misalignment of the stellar and gaseous components.}
 
@@
 lbg\_113        & 50$\pm20$           & 41$^{+41}_{-29}$                     & 113$\pm22$                 & 108$^{+23}_{-25}$                  & 0.39$^{+0.39}_{-0.29}$                & 1$^{+34}_{-26}$  & DD   \\[1ex]
+lbg\_121        & 33$\pm9$           & 54$^{+33}_{-24}$                     & 67$\pm18$                 & 50$^{+21}_{-27}$                  & 1.06$^{+0.87}_{-0.65}$                & 55$^{+34}_{-26}$  & RD   \\[1ex]
 lbg\_124         & 9$\pm8$                    & 32$^{+27}_{-18}$                    & 52$\pm19$                 & 46$^{+19}_{-23}$       & 0.71$^{+0.69}_{-0.5}$               & 39$^{+20}_{-14}$ & DD \\[1ex]
@@
 \subsubsection{KDS merger candidates}\label{subsubsection:merger_candidates}
-The KDS galaxies were classified as mergers when more than one component was identified in the high-resolution imaging.  
-One benefit of studying the {\em HST} photometry in tandem with the kinematics was to aid the interpretation of peculiarities in the velocity and velocity dispersion fields.
-These peculiarities are usually unexpected discontinuities in the rotation fields, or extreme broadening of the dispersion field above that expected from beam-smearing or in regions spatially offset from the centre of the galaxy.
-A second benefit was to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
-can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are clearly two or more potentially interacting components at slightly different redshifts in the imaging (e.g.
+\textbf{We considered both the HST imaging and information from the [O~{\sc III}]$\lambda$5007 line within the datacubes when classifying galaxies as mergers, using the following three criteria: i) Multiple components were detected in the high-resolution, HST imaging, which cannot be fit with a single {\scriptsize GALFIT} component; ii) The [O~{\sc III}]$\lambda$5007 flux maps examined in {\scriptsize QFitsView} \citep{Ott2012} had more than one peak across the spatial extent of the cube; iii) The object spectrum showed peaks at multiple wavelengths, rather than a smoothly varying line profile.
+When fit using the procedure described in \cref{subsubsection:spaxel_fitting}, this manifests as extreme rotation velocities and velocity dispersion values in the velocity and velocity dispersion maps.}
+
+\textbf{Galaxies which met all three of these criteria were classed as mergers.}
+One benefit of studying the {\em HST} photometry in tandem with the kinematics was to uncover `rotation doppelg{\"a}ngers', which mimic disk rotation from a purely kinematic perspective (i.e.
+can be fit with the arctangent model (see \cref{subsec:3d_modelling}) with small residuals), but are likely two or more potentially interacting components at slightly different redshifts (e.g.
 the bottom grid in Figure \ref{fig:main_body_kinematic_grids}).
@@
 clumpy disk galaxies e.g.
-\citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
-Perhaps the most telling diagnostic was the presence of two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map.
-\\
-
-\noindent
-In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identified signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
-In 8/9 resolved KDS cluster galaxies we identified multiple photometric components, translating into a merger rate of 89\%  (see Table \ref{tab:pointings}).
+\citealt{Elmegreen2004,Bournaud2007,ForsterSchreiber2009}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
+\textbf{We chose to omit these galaxies from the analysis described in \cref{sec:results}, to minimise the risk of contaminating the kinematics of the sample with mergers}. \\
+
+In 6/39 of the resolved KDS field galaxies (one count per merger) the merging classification criteria were met, which translates into a merger rate of 15\%.
+In 8/9 resolved KDS cluster galaxies the criteria were met, translating into a merger rate of 89\%  (see Table \ref{tab:pointings}).
 The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they were drawn from a higher density environment, and these interactions will inevitably have major consequences for the consumption and stripping of gas, as well as the morphological and dynamical evolution within these galaxies.
@@
 As mentioned above, we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
-We keep the KDS galaxies without {\em HST} coverage on the basis that we do not identify double components in the galaxy continuum maps. 
+We keep the KDS galaxies without {\em HST} coverage on the basis that we do not identify double components in the [O~{\sc III}]$\lambda$5007 maps. 
 In the kinematic grids throughout \ref{fig:merger_galaxies} (as well as the bottom grid in \ref{fig:main_body_kinematic_grids}) we present the {\em HST} imaging, kinematic maps and one-dimensional kinematic extractions for the KDS merger candidates in both the field and cluster environments.
@@
 In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in Appendix \ref{subsec:AMAZE}.
-We used a simple approach (dictated by the signal-to-noise of the isolated field sample) and calculated rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
-The morphologically isolated KDS field galaxies were classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
+
+We used a simple approach (dictated by the signal-to-noise of the isolated field sample) and calculated rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (39, see Table \ref{tab:pointings}).
+The morphologically isolated KDS field galaxies were classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 14/39 or 36\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/39 or 49\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
 We plot the best-fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion-dominated categories in Figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.
@@
 \subsubsection{Summary of the final sample for further analyses}\label{subsubsec:kin_sample_summary}
-In summary, we analysed 77 typical $z\simeq3.5$ SFGs spanning both cluster and field environments, finding 62 with integrated [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsec:datareduction}).
-This sample was refined to 47 galaxies (61\%) with spatially-resolved [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsection:spaxel_fitting}).
+In summary, we analysed 77 typical $z\simeq3.5$ SFGs spanning both cluster and field environments, finding 63 with integrated [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsec:datareduction}).
+This sample was refined to 48 galaxies (62\%) with spatially-resolved [O~{\sc III}]$\lambda$5007 emission (\cref{subsubsection:spaxel_fitting}).
 Due to the unusually high merger-candidate rate of 89\% in the cluster environment (identified by searching the high-resolution {\em HST} imaging for photometric counterparts), we omitted the 9 spatially-resolved galaxies in SSA22-P1 from further consideration.
-In the remaining sample of 38 field environment galaxies we identified 6 merger candidates, giving a field galaxy merger rate of 16\%, which constitute the `merger field sample'.
-The remaining 32 galaxies constitute the `isolated field sample', for which we measured morphological parameters using {\scriptsize GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and Table \ref{tab:phys-props}) and derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and Table \ref{tab:kin_props}).
-\\
-
-\noindent
-The isolated field sample was further divided into 13/38 rotation-dominated galaxies (34\% with respect to full field sample) and 19/38 dispersion-dominated galaxies (50\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}), with the remaining 6/38 (16\%) classified as mergers.
+In the remaining sample of 39 field environment galaxies we identified 6 merger candidates, giving a field galaxy merger rate of 15\%, which constitute the `merger field sample'.
+The remaining 33 galaxies constitute the `isolated field sample', for which we measured morphological parameters using {\scriptsize GALFIT} to fit exponential disks to the {\em HST} imaging (see \cref{subsubsec:galfitting} and Table \ref{tab:phys-props}) and derived beam-smearing corrected measurements of the rotation velocities extracted at $2R_{1/2}$ and the intrinsic velocity dispersions (see \cref{subsec:3d_modelling} and Table \ref{tab:kin_props}).
+\\
+
+The isolated field sample was further divided into 14/39 rotation-dominated galaxies (36\% with respect to full field sample) and 19/39 dispersion-dominated galaxies (49\%) on the basis of the ratio $V_{C}/\sigma_{int}$ (see \cref{subsubsection:isolated_classification}), with the remaining 6/39 (15\%) classified as mergers.
 
@@
 These galaxies are representative of typical star-forming galaxies at $z\simeq3.5$, as verified by comparing with fits to the galaxy main-sequence at this redshift.
-Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class}, we first reduced the sample to 38 spatially resolved field environment galaxies and then to 32 isolated field sample galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
+Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class}, we first reduced the sample to 39 spatially resolved field environment galaxies and then to 33 isolated field sample galaxies which have spatially-resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e.
 not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
 For these galaxies we measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$, and velocity dispersions, $\sigma_{int}$, as listed in Table \ref{tab:kin_props}, which we used to classify the galaxies as either rotation or dispersion-dominated.
-The morphological and kinematic grids for these 32/38 isolated field sample galaxies and the 6/38 merger candidates are plotted in Appendix \ref{app:kinematics_plots}.
+The morphological and kinematic grids for these 33/39 isolated field sample galaxies and the 6/39 merger candidates are plotted in Appendix \ref{app:kinematics_plots}.
 
@@
 As has been discussed recently, information about the redshift evolution of gas fractions, $f_{g} = M_{gas}/M_{bar}$ where $M_{bar}$ is the baryonic mass, disk mass fractions, $m_{d} = M_{bar}/M_{H}$  where $M_{H}$ is the halo mass, dark matter fractions, $f_{DM}(R_{1/2}) = V^{2}_{DM}(R_{1/2})/V^{2}_{C}(R_{1/2})$ where $V_{DM}$ is the dark matter circular velocity, may also be encoded in measured offsets from the local stellar mass Tully-Fisher relation \citep{Wuyts2016b,Ubler2017,Genzel2017}.
-\\
-
-\noindent
+
 We plot the relationship between rotation velocity and stellar mass for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
 We compare to the relationship from \cite{Harrison2017}, in which the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ star-forming galaxies with $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
+\textbf{This is the closest matched sample in terms of analysis and selection criteria, therefore providing a robust comparison.}
 The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a_{z=0.9} = 0.33 \pm 0.11$ and $b_{z=0.9} = 2.12 \pm 0.04$.
@@
 
-\noindent
 The rotation-dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\simeq0.9$ relation, but with a tendency to lie below the relation.
@@
 
-\noindent
 Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
@@
 
-\noindent
 Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\simeq0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
@@
 
-\noindent
 In summary, with the KDS, we have added the largest sample of galaxies observed with integral-field spectroscopy at $z>3$, and with our simple $V_{C}/\sigma_{int} > 1$ cut we conclude that the stellar mass Tully-Fisher relation defined for rotation-dominated star-forming galaxies appears to show no evolution between $z\simeq0.1$ and $z\simeq3.5$.
@@
 
-\noindent
 The right panel of Figure \ref{fig:tf_relation} indicates that the $V_{C}$ distributions for the comparison and KDS isolated field samples are wide, reflecting the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
+\textbf{The mass distribution within each sample drives the location of the mean rotation velocity, with samples that have larger mean stellar mass values showing larger mean rotation velocities.}
 The isolated field sample mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}km\,s^{-1}$ and $57.0^{+6.6}_{-6.3}km\,s^{-1}$.
-However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}km\,s^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}km\,s^{-1}$ respectively, suggesting that averaging over a sample containing a large number of dispersion dominated galaxies is bringing the averages down.
+However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}km\,s^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}km\,s^{-1}$ respectively, suggesting that averaging over a sample containing a large number of dispersion dominated galaxies brings the averages down.
 
@@
 The GHASP, MASSIV, KROSS and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
-Despite the wide distributions, the comparison samples generally have higher mean rotation velocities. \\
-
-\noindent
+\textbf{Further caveats when making comparisons between the velocity distributions of different samples are variations in disk half-light radii and the spatial resolution of the observations. 
+In \cite{Newman2013} it is shown that it is often not possible to resolve rotational structure in seeing-limited conditions, with this effect more severe for compact galaxies. 
+Consequently, the non-uniform disk-sizes and spatial resolution across the comparison samples may result in additional variations between the inferred rotation velocities. 
+As a result, mainly of the differences in mass distribution between the samples, we do not attempt to interpret any evolutionary trends from the right panel of Figure \ref{fig:tf_relation}.
+However, \cite{Simons2017} have demonstrated with a consistently selected and processed sample of star-forming galaxies between $0 < z < 2.5$, that there is a mild drop in rotation velocities with increasing redshift over this interval in both low and high-mass bins.}
+
 In a rotationally supported system, the circular velocity is set by the requirement to support the total mass in the system, i.e.
@@
 
-\noindent
 We proceed to consider the cause of the high number of dispersion-dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
@@
 
-\noindent
 We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high-redshift.
@@
 
-\noindent
 These new data from the KDS sustain the observation that velocity dispersion is increasing with redshift and provide strong constraints on the internal dynamics of typical star-forming galaxies between $z=3-3.8$.
@@
 
-\noindent
 The $V_{C}$/$\sigma_{int}=1$ line dividing rotation and dispersion-dominated galaxies is marked on Figure \ref{fig:v_sig_and_v}, separating the dispersion and rotation-dominated galaxies by definition.
 There is a spread of rotation and dispersion-dominated galaxies across the stellar mass range, with rotation-dominated galaxies more likely to be found above $log(M_{\star}/M_{\odot}) > 9.5$.
-The Rotation-Dominated Fraction (RDF), calculated with respect to the full field sample of 38 galaxies, is 0.34$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
+The Rotation-Dominated Fraction (RDF), calculated with respect to the full field sample of 39 galaxies, is 0.36$\pm0.08$, which is substantially lower than in the local and intermediate redshift universe \citep[e.g.][]{Epinat2008a,Epinat2008,Green2014}.
 We interpret these results in the context of the cosmic evolution of the rotation dominated fraction using the comparison samples in \cref{subsubsec:RDF_evolution}.\\
@@
 
-In the left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation-dominated fraction respectively as a function of redshift for the KDS isolated field sample and the comparison samples described in Appendix \ref{app:comparison_samples}.
+In the left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift} we plot $V_{C}/\sigma_{int}$ and the closely connected rotation-dominated fraction respectively, as a function of redshift, for the KDS isolated field sample and the comparison samples described in Appendix \ref{app:comparison_samples}.
 In each sample, the rotation dominated fraction is computed as the fraction of galaxies with $V_{C}/\sigma_{int} > 1$, which, given the varying data quality across the comparison samples, is a simple and fair way to study the redshift evolution of this quantity.
@@
 
-\noindent
 The rotation-dominated fraction, traced simply by the $V_{C}/\sigma_{int}$ ratio inferred from ionised gas emission lines, drops from $\simeq100\%$ of galaxies in the local universe to $\simeq2/3$ of galaxies in the $z\simeq1-2$ universe and to $\simeq1/3$ above $z\simeq3$, albeit with individual surveys reporting wide $V_{C}/\sigma_{int}$ distributions at each redshift slice.
@@
 This draws again from the idea that higher stellar mass values suggest that the galaxies are more evolved, with more gas having been converted into stars for the bulk of the sample, which provides stability for a rotating disk and pushes the rotation-dominated fraction higher (see \cref{sec:discussion}).
+\textbf{This is shown explicitly in \cite{Simons2017}, where galaxies in higher stellar mass bins have larger $V_{C}/\sigma_{int}$ at every epoch.
+It is important to note that the results in the right panel of Figure \ref{fig:rdf_and_v_sigma_w_redshift} are subject to the same half-light radius and spatial resolution caveats discussed in section \cref{subsubsec:v_evolution}, which may lead to an increase in velocity dispersions and a decrease in rotation velocities when galaxies are compact and the spatial resolution of the observations is poorer.
+Specifically for the KDS sample, the disk sizes are smaller than at intermediate redshift, and so it may be more challenging to fully resolve the rotational structure of the galaxies \citep[e.g.][]{Newman2013}}.
 \\\\
-\noindent
+
 In summary, the rotation-dominated galaxies in the isolated field sample appear to conform with a redshift invariant $V_{C}$ - $M_{\star}$ relation.
-Due to increased velocity dispersions, these rotation-dominated galaxies account for only $34\%$ of the field sample and so are less representative of typical star-forming galaxies at $z\simeq3.5$ than at intermediate and low redshifts.
+Due to increased velocity dispersions, these rotation-dominated galaxies account for only $36\%$ of the field sample and so are less representative of typical star-forming galaxies at $z\simeq3.5$ than at intermediate and low redshifts.
 Explanations for the increase of $\sigma_{int}$ with redshift (and hence the decline of $V_{C}/\sigma_{int}$) with cosmic time as well as the nature of dispersion-dominated galaxies have been discussed at length throughout other studies \citep[e.g][]{ForsterSchreiber2009,Law2009,Burkert2010,Newman2013,Wisnioski2015} and we revisit these in the following discussion.
@@
 
-\noindent
 \cite{Burkert2010} show, starting from the hydrostatic equation, that negative pressure gradients sourced by the disk turbulence generated through gravitational instabilities result in a decrease in observed rotation velocities.
@@
 
-\noindent
 In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties: gas fraction, $f_{gas}$, gas depletion timescale, $t_{dep}$, and specific star-formation rate, sSFR.
@@
 
-\noindent
 The gas fraction is a function of gas depletion timescale, with an assumed redshift dependence, and specific star-formation rate, with an assumed mass and redshift dependence (see \citealt{Wisnioski2015} Equations 3-6, summarised below by Equations \ref{eq:gas_fractions} and \ref{eq:coefficients}).
@@
 
-\noindent
 This relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
@@
 
-\noindent
 In this model, the velocity dispersions increase more steeply with increasing stellar mass, as shown by the solid and dashed lines in Figure \ref{fig:sigma_and_v_sigma_w_redshift}.
@@
 
-\noindent
 Although the details of the coefficients of Equation \ref{eq:sigma_increase} are unclear (i.e.
@@
 
-\noindent
 In summary, the isolated field sample galaxies are diverse and kinematically immature, with $\simeq2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
@@
 \section{CONCLUSIONS}\label{sec:conclusion}
-We have presented new dynamical measurements of 32 typical star-forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
+We have presented new dynamical measurements of 33 typical star-forming galaxies spanning both cluster and field environments at $z\simeq3.5$ as part of the KMOS Deep Survey, based on IFU data observed with KMOS.
 These measurements push back the frontier of IFU observations in the early universe and provide more robust constraints on the internal and rotational dynamics of $9.0 < log(M_{\star}/M_{\odot})< 10.5$ typical star-forming galaxies at these redshifts.
-By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\simeq16\%$) and a very high merger rate in the cluster pointing ($\simeq89\%$).
+By using a combined morpho-kinematic classification based on broad-band {\em HST} imaging and our IFU data, we have separated interacting galaxies from the sample, finding merger rates consistent between the field pointings ($\simeq15\%$) and a very high merger rate in the cluster pointing ($\simeq89\%$).
 We have made beam-smearing corrected measurements of $V_{C}$ and $\sigma_{int}$ for the remaining isolated field galaxies, and we interpret these in the context of previous dynamical studies using IFU data (Appendix \ref{app:comparison_samples} and Table \ref{tab:evolution_numbers}).
@@
     This suggests that pressure forces, which are more significant at high-redshift, may play a role in supporting the total mass in all of the galaxies in the isolated field sample \citep[e.g.][]{Burkert2010}.
-    \item 13/32 isolated field sample galaxies are rotation-dominated and 19/32 are dispersion-dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
-    This gives a rotation-dominated fraction of $34 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
+    \item 14/33 isolated field sample galaxies are rotation-dominated and 19/33 are dispersion-dominated, with a tendency for galaxies with higher $M_{\star}$ to have larger values of $V_{C}/\sigma_{int}$ (Figure \ref{fig:v_sig_and_v}).
+    This gives a rotation-dominated fraction of $36 \pm 8 \%$ in the isolated field sample, substantially less than surveys at lower redshift, although there is significant diversity amongst the individual $V_{C}/\sigma_{int}$ measurements at each redshift slice (left and right panels of Figure \ref{fig:rdf_and_v_sigma_w_redshift}).
     When viewed as a function of redshift, the rotation dominated fraction appears to follow the scaling relation RDF$\propto z^{-0.2}$.
@@
 
+\textbf{We wish to thank the anonymous referee for their comments, which have improved the quality and clarity of this work.}
 OJT acknowledges the financial support of the Science and Technology Facilities Council through a studentship award. 
@@
  AMAZE (Clean) & 3.0 & 10.0 &   $140.8^{+40.1}_{-30.2}$\cmark & $129.0^{+45.0}_{-33.4}$ &  $95.7^{+2.0}_{-2.0}$ \cmark & $95.0^{+2.6}_{-2.6}$ & $1.4^{+0.3}_{-0.3}$  \cmark &           $1.1^{+0.3}_{-0.3}$ &               -                       \xmark   \\[1ex]
- \textbf{KDS} & 3.5 & 9.8 &     $75.7^{+4.4}_{-4.4}$   \cmark & $57.5^{+5.5}_{-5.5}$    &  $70.3^{+3.3}_{-3.1}$ \cmark & $71.0^{+5.0}_{-4.8}$ & $1.1^{+0.2}_{-0.1}$  \cmark &            $0.84^{+0.1}_{-0.1}$&               $0.37^{+0.08}_{-0.08}$ \cmark    \\[1ex]
+ \textbf{KDS} & 3.5 & 9.8 &     $75.7^{+4.4}_{-4.4}$   \cmark & $57.5^{+5.5}_{-5.5}$    &  $70.3^{+3.3}_{-3.1}$ \cmark & $71.0^{+5.0}_{-4.8}$ & $1.1^{+0.2}_{-0.1}$  \cmark &            $0.84^{+0.1}_{-0.1}$&               $0.36^{+0.08}_{-0.08}$ \cmark    \\[1ex]
  \hline
@@
 
-\noindent
 $V_{C}$ values for rotation-dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion-dominated galaxies using the velocity width.
@@
 
-\noindent
 It is unclear whether the $V_{C}$ values for the full sample from FS09 are directly comparable, but we make use of the tabulated values for completeness and plot these with filled symbols throughout \cref{sec:results}.
@@
 
-\noindent
 Also, for 5 galaxies in G11, $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error on $V_{C}$ equal to 1 when computing the sample averages.
@@
 
-\noindent
 This Unconstrained sample also contains the galaxy s\_sa22a-M38, common between the KDS and G11, classified here as a merger due to double {\em HST} components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346 km\,s^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
@@
 
-\noindent
 This comparison sample summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, however, despite this diversity, over the past decade the studies appear to be converging on `modelling out' the effects of beam-smearing using similar approaches (e.g.
@@
 
-\noindent
 The upper and lower errors on the $\sigma_{int}$ are calculated using a similar approach.
-To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50 km\,s^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40 km\,s^{-1}$ and $\sigma_{int} = 80 km\,s^{-1}$, with these representing reasonable minimum and maximum mean instrinsic sigma values (chosen by considering the range in $\sigma_{int}$ at similar redshift, see e.g.
-Figure \ref{fig:sigma_and_v_sigma_w_redshift}).
+To encorporate the uncertainty introduced in the modelling by assuming a fixed value of $\sigma_{int}=50 km\,s^{-1}$, we make two further model evaluations using both the 16th and 84th percentile parameters with $\sigma_{int} = 40 km\,s^{-1}$ and $\sigma_{int} = 80 km\,s^{-1}$, \textbf{with these limits roughly encompassing the range of observed and predicted velocity dispersion values at $z\simeq3.5$ as shown in \cite{Wisnioski2015} figure 10.}
 When assuming the broader $\sigma_{int} = 80 km\,s^{-1}$ value in each spaxel the beam-smearing correction decreases, as the impact of convolution with spectral lines in adjacent spaxels with shifted velocity centres is less severe.
@@
 
-\noindent
 where $\sigma_{bs-84-40} = \sigma_{model-84-40} - 40$ and $\sigma_{bs-16-80} = \sigma_{model16-80} - 80$ are the beam-smeared maps.
@@
 
-\noindent
 with $\bar{\sigma}_{\sigma_{obs}}$ equal to the average of the velocity dispersion measurement errors.
@@
 
-    \caption{We plot the kinematic grids for the 13/32 isolated field sample galaxies classified as rotation-dominated.
+    \caption{We plot the kinematic grids for the 14/33 isolated field sample galaxies classified as rotation-dominated.
     For each galaxy we plot the {\em HST} image, {\scriptsize GALFIT} model and {\scriptsize GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map, dispersion map and velocity map extracted from the datacubes with gaussian-fits to the individual spaxels as described in \protect\cref{subsubsection:spaxel_fitting}.
@@
     \includegraphics[width=0.95\textwidth]{SSA_ROTATION/combine_sci_reconstructed_s_sa22b-d5_grid_paper.png}
-
+    \includegraphics[width=0.95\textwidth]{GOODS_ROTATION/COMBINE_SCI_RECONSTRUCTED_CDFS_LBG_121_grid_paper.png}
     \caption{\textbf{Continued.}}
